### 2019-10-29 analysis/reports/statevars.Rmd
a beginning

---
title: "Max N and S"
output: 
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(drake)
library(ggplot2)

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache.sqlite"))
cache <- storr::storr_dbi("datatable", "keystable", db)

loadd(statevars, cache = cache)

```
```{r s and n plot}

statevars_plot <- ggplot(data = statevars, aes(x = s0, y = n0, color = singletons)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_d(end = .5)

statevars_plot

```

```{r s and n plot facetted}

statevars_plot_facetted <- statevars_plot +
  facet_wrap(vars(dat))

statevars_plot_facetted
```

### 2019-10-29 R/add_singletons.R

@@ -1,0 +1,73 @@
+#' Add singletons
+#'
+#' @param dat dataframe, result of get sad
+#'
+#' @return dataframe with some extra singletons
+#' @export
+#'
+#' @importFrom dplyr select bind_rows mutate arrange row_number group_by n summarise filter
+#' @importFrom vegan estimateR
+add_singletons <- function(dat, use_max =F) {
+  freq = dat %>%
+    dplyr::select(abund) %>%
+    as.matrix() %>%
+    t()
+
+  s0 <- ncol(freq)
+  n0 <- sum(freq)
+
+
+  est <- vegan::estimateR(freq)
+
+  chao_est <- est[2] - s0
+  ace_est <- est[4] - s0
+
+  if(use_max) {
+    chao_est <- chao_est + est[3]
+    ace_est <- ace_est + est[5]
+
+    if(is.nan(ace_est)) {
+      ace_est <- est[4]
+    }
+  }
+
+  ests <- data.frame(est = c(chao_est, ace_est)) %>%
+    dplyr::filter(!is.na(est),
+           !is.nan(est),
+           !is.infinite(est),
+           est >= 0)
+
+  if(nrow(ests) == 0) {
+    return(NA)
+  }
+
+  est_nspp <- ceiling(mean(ests$est))
+
+  if(est_nspp == 0) {
+    dat <- dat %>%
+      dplyr::mutate(singletons = TRUE)
+    return(dat)
+  }
+
+  newdat <- data.frame(
+    abund = rep(1, times = est_nspp)
+  )
+
+  dat <- dat %>%
+    dplyr::select(-rank) %>%
+    dplyr::bind_rows(newdat) %>%
+    dplyr::mutate(
+      sim = sim[1],
+      source = source[1],
+      site = site[1],
+      dat = dat[1]
+    ) %>%
+    dplyr::arrange(abund) %>%
+    dplyr::mutate(
+      rank = dplyr::row_number(),
+      singletons = TRUE
+    )
+
+  return(dat)
+
+}

### 2019-10-29 R/data_handling.R

@@ -25,7 +25,7 @@ download_data <- function(from_url = FALSE, storage_path = here::here("working-d
 
     download.file(url = "https://raw.githubusercontent.com/weecology/sad-comparison/master/sad-data/fia_spab.csv", destfile = file.path(storage_path, "fia_spab.csv"))
 
-    download.file(url = "https://ndownloader.figshare.com/files/3097079", destfile = file.path(storage_path, "misc_abund.csv"))
+    download.file(url = "https://ndownloader.figshare.com/files/3097079", destfile = file.path(storage_path, "misc_abund_spab.csv"))
 
   } else {
     file.copy(inst_path, storage_path, recursive = T)
@@ -34,15 +34,97 @@ download_data <- function(from_url = FALSE, storage_path = here::here("working-d
 
 #' Load sads
 #'
-#' @param dataset
-#' @param site
-#' @param storage_path
+#' @param dataset_name "bbs", "fia", "gentry", "mcdb", or "misc_abund"
+#' @param site_name which site
+#' @param storage_path where the data is living
 #'
 #' @return something
 #' @export
 #'
-load_sads <- function(storage_path = here::here("working-data", "paper")) {
+load_sad <- function(dataset_name, site_name, storage_path = here::here("working-data", "paper")) {
 
-  ### how
+  dataset_path = file.path(storage_path, paste0(dataset_name, "_spab.csv"))
 
+  if(dataset_name != "misc_abund") {
+    dataset <- read.csv(dataset_path, stringsAsFactors = F, header = F, skip = 2)
+
+    colnames(dataset) <- c("site", "year", "species", "abund")
+  } else {
+    dataset <- read.csv(dataset_path, stringsAsFactors = F)
+
+    dataset <- dataset %>%
+      dplyr::rename(site = Site_ID,
+                    abund = Abundance)
+  }
+
+  dataset <- dataset %>%
+    dplyr::mutate(site = as.character(site),
+                  dat = dataset_name) %>%
+    dplyr::filter(site == site_name) %>%
+    dplyr::select(site, abund, dat) %>%
+    dplyr::filter(abund > 0) %>%
+    dplyr::arrange(abund) %>%
+    dplyr::mutate(rank = dplyr::row_number()) %>%
+    dplyr::select(rank, abund, site, dat) %>%
+    dplyr::mutate(singletons = FALSE,
+                  sim = -99,
[…]

### 2019-10-29 R/render_reports.R

@@ -1,0 +1,12 @@
+#' Render a report
+#'
+#' @param report_path file path for report
+#' @param dependencies dependencies for drake
+#'
+#' @return nothing
+#' @export
+#' @importFrom rmarkdown render
+render_report <- function(report_path, dependencies = list()) {
+  rm(dependencies)
+  rmarkdown::render(report_path, output_format = "github_document")
+}

### 2019-10-29 analysis/main.R

@@ -2,4 +2,61 @@ library(drake)
 library(scadsanalysis)
 library(ggplot2)
 
+expose_imports("scadsanalysis")
 
+#sites_list <- lapply(list("mcdb", "gentry", "fia", "bbs", "misc_abund"), FUN = list_sites)
+sites_list <- lapply(list("misc_abund"), FUN = list_sites)
+
+sites_list <- dplyr::bind_rows(sites_list)
+
+dat_plan <- drake_plan(
+  dat = target(load_sad(dataset_name = d, site_name = s),
+               transform = map(
+                 d = !!sites_list$dat,
+                 s = !!sites_list$site
+               )
+  ),
+  singles = target(add_singletons(dat),
+                   transform = map(dat)),
+  all_dat = target(dplyr::bind_rows(dat, singles),
+                   transform = combine(dat, singles)),
+  statevars = target(get_statevars(all_dat)),
+  statevars_report = target(render_report(here::here("analysis", "reports", "statevars.Rmd"), dependencies = statevars))
+)
+
+all <- dat_plan
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+
+## View the graph of the plan
+if (interactive())
+{
+  config <- drake_config(all, cache = cache)
+  sankey_drake_graph(config, build_times = "none")  # requires "networkD3" package
+  vis_drake_graph(config, build_times = "none")     # requires "visNetwork" package
+}
+
+## Run the pipeline
+nodename <- Sys.info()["nodename"]
+if(grepl("ufhpc", nodename)) {
+  library(future.batchtools)
+  print("I know I am on SLURM!")
+  ## Run the pipeline parallelized for HiPerGator
+  future::plan(batchtools_slurm, template = "slurm_batchtools.tmpl")
+  make(all,
+       force = TRUE,
+       cache = cache,
+       cache_log_file = here::here("analysis", "drake", "cache_log.txt"),
+       verbose = 2,
+       parallelism = "future",
+       jobs = 64,
+       caching = "master") # Important for DBI caches!
+} else {
+  # Run the pipeline on a single local core
+  system.time(make(all, cache = cache, cache_log_file = here::here("analysis", "drake", "cache_log.txt")))
+}
+
+
+print("Completed OK")

### 2019-10-29 analysis/reports/statevars.Rmd
setting up for hpg

@@
 ## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache.sqlite"))
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-dat.sqlite"))
 cache <- storr::storr_dbi("datatable", "keystable", db)

### 2019-10-29 analysis/dat_pipeline.R

@@ -27,7 +27,7 @@ dat_plan <- drake_plan(
 all <- dat_plan
 
 ## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache.sqlite"))
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-dat.sqlite"))
 cache <- storr::storr_dbi("datatable", "keystable", db)
 
 ## View the graph of the plan
@@ -48,14 +48,14 @@ if(grepl("ufhpc", nodename)) {
   make(all,
        force = TRUE,
        cache = cache,
-       cache_log_file = here::here("analysis", "drake", "cache_log.txt"),
+       cache_log_file = here::here("analysis", "drake", "cache_log_dat.txt"),
        verbose = 2,
        parallelism = "future",
-       jobs = 64,
+       jobs = 200,
        caching = "master") # Important for DBI caches!
 } else {
   # Run the pipeline on a single local core
-  system.time(make(all, cache = cache, cache_log_file = here::here("analysis", "drake", "cache_log.txt")))
+  system.time(make(all, cache = cache, cache_log_file = here::here("analysis", "drake", "cache_log_dat.txt")))
 }
 
 

### 2019-10-31 analysis/reports/statevars.Rmd
try this

@@
 
-loadd(statevars, cache = cache)
+loadd(all_sv, cache = cache)
 
@@
 
-statevars_plot <- ggplot(data = statevars, aes(x = s0, y = n0, color = singletons)) +
+statevars_plot <- ggplot(data = all_sv, aes(x = s0, y = n0, color = singletons)) +
   geom_point() +
   theme_bw() +
-  scale_color_viridis_d(end = .5)
+  scale_color_viridis_d(end = .5) +
+  geom_vline(xintercept = 62) +
+  geom_hline(yintercept = 15000)
 
@@
 statevars_plot_facetted <- statevars_plot +
-  facet_wrap(vars(dat))
+  facet_wrap(vars(dat), scales = "free")
 

### 2019-10-31 R/data_handling.R

@@ -32,16 +32,15 @@ download_data <- function(from_url = FALSE, storage_path = here::here("working-d
   }
 }
 
-#' Load sads
+#' Load a dataset
 #'
 #' @param dataset_name "bbs", "fia", "gentry", "mcdb", or "misc_abund"
-#' @param site_name which site
 #' @param storage_path where the data is living
 #'
 #' @return something
 #' @export
 #'
-load_sad <- function(dataset_name, site_name, storage_path = here::here("working-data", "paper")) {
+load_dataset <- function(dataset_name, storage_path = here::here("working-data", "paper")) {
 
   dataset_path = file.path(storage_path, paste0(dataset_name, "_spab.csv"))
 
@@ -60,7 +59,6 @@ load_sad <- function(dataset_name, site_name, storage_path = here::here("working
   dataset <- dataset %>%
     dplyr::mutate(site = as.character(site),
                   dat = dataset_name) %>%
-    dplyr::filter(site == site_name) %>%
     dplyr::select(site, abund, dat) %>%
     dplyr::filter(abund > 0) %>%
     dplyr::arrange(abund) %>%
@@ -111,6 +109,31 @@ list_sites <- function(dataset_name, storage_path = here::here("working-data", "
                   site = as.character(site))
 
   return(dataset)
+}
+
+#' Add singletons to a dataset
+#'
+#' @param dataset the dataset
+#' @param use_max use max?
+#'
+#' @return dataset plus singletons
+#' @export
+#'
+#' @importFrom dplyr filter bind_rows
+add_singletons_dataset <- function(dataset, use_max = TRUE) {
+
+  sites <- as.list(unique(dataset$site))
+
+  site_dats <- lapply(sites, FUN = function(site_name, dataset) return(dplyr::filter(dataset, site == site_name)), dataset = dataset)
+
+  site_singletons <- lapply(site_dats, FUN = add_singletons, use_max = use_max)
+
+  site_singletons <- dplyr::bind_rows(site_singletons)
+
+  dataset <- dplyr::bind_rows(dataset, site_singletons)
+
+  return(dataset)
+
 }
 
 #' Retrieve statevars

### 2019-11-08 analysis/reports/dat_report_template.Rmd
generate dat reports from template

---
title: "Dataset-level report"
output: 
  github_document:
    html_preview: false
params:
  dataset_name: ["mcdb"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

this_dataset <- params$dataset_name

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", this_dataset, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
loadd(all_di, cache = cache)

```
# This dataset is `r this_dataset`.

## State variables and change with singletons

Here is a plot of the distribution of S and N in this dataset, and S and N if we estimate the true number of species.

```{r statevars}

sv <- get_statevars(dat)

statevars_plot <- ggplot(data = sv, aes(x = s0, y = n0, color = singletons)) +
  geom_point(alpha = .5) +
  theme_bw() +
  facet_wrap(vars(singletons)) +
  scale_color_viridis_d(end = .5) +
  ggtitle("State variables")

statevars_plot
```

Here is a plot of how many species were added to each dataset by estimating the true number of species.

```{r sv change}
sv_singles <- filter(sv, singletons == TRUE) %>%
  select(-singletons) %>%
  rename(singletons_s0 = s0,
         singletons_n0 = n0)

sv_change <- filter(sv, singletons == FALSE) %>%
  select(-singletons) %>%
  left_join(sv_singles, by = c("site", "dat", "sim", "source")) %>%
  mutate(s0_change = singletons_s0 - s0,
         n0_change = singletons_n0 - n0) %>%
  select(-singletons_s0, -singletons_n0)

sv_change_plot <- ggplot(data = sv_change, aes(x = s0, y = n0, color = log(s0_change))) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .75, direction = -1) +
  ggtitle("State variable change")

sv_change_plot
```

## Position (%ile) of empirical SADs within FS

```{r empirical positions}

skew_plot <- ggplot(data = filter(all_di, source == "observed"), aes(x= singletons, y = skew_percentile)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Skewness percentile") +
  ylim(0, 100)

simpson_plot <- ggplot(data = filter(all_di, source == "observed"), aes(x= singletons, y = simpson_percentile)) +
  geom_boxplot() +
  theme_bw() +
  ggtitle("Simpson percentile") +
  ylim(0, 100)

gridExtra::grid.arrange(grobs = list(skew_plot, simpson_plot), ncol = 2)
```

```{r cleanup}

DBI::dbDisconnect(db)
rm(cache)
```

### 2019-11-08 R/render_reports.R

@@ -2,11 +2,23 @@
 #'
 #' @param report_path file path for report
 #' @param dependencies dependencies for drake
+#' @param is_template is this a template?
+#' @param dat_name if this is a template, need to pass the dataset name to customize the report
 #'
 #' @return nothing
 #' @export
 #' @importFrom rmarkdown render
-render_report <- function(report_path, dependencies = list()) {
+#'
+render_report <- function(report_path, dependencies = list(), is_template = FALSE, dat_name = NULL) {
   rm(dependencies)
-  rmarkdown::render(report_path, output_format = "github_document")
+  if(!is_template) {
+    rmarkdown::render(report_path, output_format = "github_document")
+  } else {
+    if(is.null(dat_name)) {
+      return("Need to provide dat name")
+    } else {
+      rmarkdown::render(report_path, output_format = "github_document",
+                        output_file = paste0(dat_name, "_report.md"), params = list(dataset_name = dat_name))
+    }
+  }
 }

### 2019-11-08 analysis/dat_pipeline.R

@@ -1,102 +1,0 @@
-library(drake)
-library(scadsanalysis)
-library(ggplot2)
-
-expose_imports("scadsanalysis")
-
-datasets <- c("mcdb", "gentry", "bbs", "misc_abund", "fia")
-
-#datasets <- c("mcdb", "bbs")
-
-sites_list <- lapply(as.list(datasets), FUN = list_sites)
-names(sites_list) <- datasets
-#sites_list$mcdb <- sites_list$mcdb[1:10, ]
-ndraws = 100
-
-dat_plan <- drake_plan(
-  dat = target(load_dataset(dataset_name = d),
-               transform = map(
-                 d = !!datasets
-               ),
-               hpc = F
-  ),
-  dat_s = target(add_singletons_dataset(dat),
-                 transform = map(dat),
-                 hpc = F),
-  sv = target(get_statevars(dat_s),
-              transform = map(dat_s),
-              hpc = F),
-  all_sv = target(dplyr::bind_rows(sv),
-                  transform = combine(sv),
-                  hpc = F),
-  sv_report = target(render_report(here::here("analysis", "reports", "statevars.Rmd"), dependencies = all_sv),
-                     trigger = trigger(condition = T),
-                     hpc = F),
-  mamm_p = target(readRDS(here::here("analysis", "masterp_mamm.Rds")),
-                  hpc = F),
-  wide_p = target(readRDS(here::here("analysis", "masterp_wide.Rds")),
-                  hpc = F),
-  fs_mcdb = target(sample_fs_wrapper(dataset = dat_s_dat_mcdb, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = mamm_p),
-                   transform = cross(s = !!sites_list$mcdb$site,
-                                     singletons = !!c(TRUE, FALSE))),
-  # fs_fia = target(sample_fs_wrapper(dataset = dat_s_dat_fia, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = wide_p),
-  #                 transform = cross(s = !!sites_list$fia$site,
-  #                                   singletons = !!c(TRUE, FALSE))),
-  # fs_gentry = target(sample_fs_wrapper(dataset = dat_s_dat_gentry, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = wide_p),
-  #                 transform = cross(s = !!sites_list$gentry$site,
[…]

### 2019-11-08 analysis/fia_pipeline.R

@@ -29,6 +29,9 @@ dat_plan <- drake_plan(
               transform = map(fs)),
   all_di = target(dplyr::bind_rows(di),
                   transform = combine(di),
+                  hpc = F),
+  report = target(render_report(here::here("analysis", "reports", paste0(datasets, "_report.Rmd")), dependencies = all_di),
+                  trigger = trigger(condition = T),
                   hpc = F)
 )
 

### 2019-11-08 analysis/gentry_pipeline.R

@@ -29,9 +29,11 @@ dat_plan <- drake_plan(
               transform = map(fs)),
   all_di = target(dplyr::bind_rows(di),
                   transform = combine(di),
-                  hpc = F)
+                  hpc = F),
+  report = target(render_report(here::here("analysis", "reports", paste0(datasets, "_report.Rmd")), dependencies = all_di),
+                     trigger = trigger(condition = T),
+                     hpc = F)
 )
-
 all <- dat_plan
 
 ## Set up the cache and config

### 2019-11-08 analysis/miscabund_pipeline.R

@@ -28,6 +28,9 @@ dat_plan <- drake_plan(
               transform = map(fs)),
   all_di = target(dplyr::bind_rows(di),
                   transform = combine(di),
+                  hpc = F),
+  report = target(render_report(here::here("analysis", "reports", paste0(datasets, "_report.Rmd")), dependencies = all_di),
+                  trigger = trigger(condition = T),
                   hpc = F)
 )
 

### 2019-11-08 analysis/reports/dat_report_template.Rmd
fix templating

@@
 output: 
-  github_document:
-    html_preview: false
+  github_document
 params:
@@
 
+## Number of samples achieved
+
+```{r number of samples}
+
+site_samples <- all_di %>%
+  select(sim, source, site, singletons) %>%
+  group_by(source, site, singletons) %>%
+  summarize(nsamples = length(unique(sim))) %>%
+  ungroup() %>%
+  filter(source == "sampled") %>%
+  left_join(select(sv, -source, -sim), by = c("site", "singletons"))
+```
+
+#### The maximum number of samples achieved is `r max(site_samples$nsamples)`.
+
+```{r plot nb samples}
+samples_hist <- ggplot(data = site_samples, aes(x = nsamples)) +
+  geom_histogram(binwidth = 10) +
+  theme_bw() +
+  facet_wrap(vars(singletons), nrow = 1) +
+  ggtitle("Number of samples achieved")
+
+samples_hist
+
+sv_samples_plot <- ggplot(data = site_samples, aes(x = s0, y = n0, color = nsamples)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  facet_wrap(vars(singletons), nrow = 1) +
+  scale_color_viridis_c(option = "magma", end = .75) +
+  ggtitle("Number of samples achieved by state variables")
+sv_samples_plot
+
+```
+
 ## Position (%ile) of empirical SADs within FS

### 2019-11-08 analysis/fia_pipeline.R

@@ -30,7 +30,7 @@ dat_plan <- drake_plan(
   all_di = target(dplyr::bind_rows(di),
                   transform = combine(di),
                   hpc = F),
-  report = target(render_report(here::here("analysis", "reports", paste0(datasets, "_report.Rmd")), dependencies = all_di),
+  report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di, is_template = TRUE, dat_name = !!datasets),
                   trigger = trigger(condition = T),
                   hpc = F)
 )

### 2019-11-08 analysis/gentry_pipeline.R

@@ -10,7 +10,7 @@ sites_list <- list_sites("gentry")
 ndraws = 100
 sites_list <- sites_list[1:15, ]
 
-dat_plan <- drake_plan(
+all <- drake_plan(
   dat = target(load_dataset(dataset_name = d),
                transform = map(
                  d = !!datasets
@@ -30,11 +30,10 @@ dat_plan <- drake_plan(
   all_di = target(dplyr::bind_rows(di),
                   transform = combine(di),
                   hpc = F),
-  report = target(render_report(here::here("analysis", "reports", paste0(datasets, "_report.Rmd")), dependencies = all_di),
-                     trigger = trigger(condition = T),
-                     hpc = F)
+  report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di, is_template = TRUE, dat_name = !!datasets),
+                  trigger = trigger(condition = T),
+                  hpc = F)
 )
-all <- dat_plan
 
 ## Set up the cache and config
 db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-gentry.sqlite"))

### 2019-11-08 analysis/mcdb_pipeline.R

@@ -7,9 +7,10 @@ expose_imports("scadsanalysis")
 datasets <- "mcdb"
 
 sites_list <- list_sites("mcdb")
-ndraws = 100
-sites_list <- sites_list[1:15, ]
-dat_plan <- drake_plan(
+ndraws = 10000
+#sites_list <- sites_list[1:15, ]
+
+all <- drake_plan(
   dat = target(load_dataset(dataset_name = d),
                transform = map(
                  d = !!datasets
@@ -29,12 +30,10 @@ dat_plan <- drake_plan(
   all_di = target(dplyr::bind_rows(di),
                   transform = combine(di),
                   hpc = F),
-  report = target(render_report(here::here("analysis", "reports", paste0(datasets, "_report.Rmd")), dependencies = all_di),
+  report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di, is_template = TRUE, dat_name = !!datasets),
                   trigger = trigger(condition = T),
                   hpc = F)
 )
-
-all <- dat_plan
 
 ## Set up the cache and config
 db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-mcdb.sqlite"))

### 2019-11-08 analysis/reports/dat_report_template.Rmd
go to all sites for fia, bbs, gentry, all sites and all draws mcdb, try changing memory opts for misc

@@
   facet_wrap(vars(singletons), nrow = 1) +
-  ggtitle("Number of samples achieved")
+  ggtitle("Number of samples achieved") +
+  xlim = c(-11, max(site_samples$nsamples) + 11)
 
@@
   facet_wrap(vars(singletons), nrow = 1) +
-  scale_color_viridis_c(option = "magma", end = .75) +
+  scale_color_viridis_c(option = "magma", end = .75, limits = c(0, max(site_samples$nsamples))) +
   ggtitle("Number of samples achieved by state variables")

### 2019-11-08 analysis/bbs_pipeline.R

@@ -8,7 +8,7 @@ datasets <- "bbs"
 
 sites_list <- list_sites("bbs")
 ndraws = 100
-sites_list <- sites_list[1:15, ]
+#sites_list <- sites_list[1:15, ]
 dat_plan <- drake_plan(
   dat = target(load_dataset(dataset_name = d),
                transform = map(

### 2019-11-08 analysis/fia_pipeline.R

@@ -8,7 +8,7 @@ datasets <- "fia"
 
 sites_list <- list_sites("fia")
 ndraws = 100
-sites_list <- sites_list[1:15, ]
+#sites_list <- sites_list[1:15, ]
 
 dat_plan <- drake_plan(
   dat = target(load_dataset(dataset_name = d),

### 2019-11-08 analysis/gentry_pipeline.R

@@ -8,7 +8,7 @@ datasets <- "gentry"
 
 sites_list <- list_sites("gentry")
 ndraws = 100
-sites_list <- sites_list[1:15, ]
+#sites_list <- sites_list[1:15, ]
 
 all <- drake_plan(
   dat = target(load_dataset(dataset_name = d),

### 2019-11-08 analysis/miscabund_pipeline.R

@@ -61,7 +61,7 @@ if(grepl("ufhpc", nodename)) {
        cache_log_file = here::here("analysis", "drake", "cache_log_miscabund.txt"),
        verbose = 2,
        parallelism = "clustermq",
-       jobs = 20,
+       jobs = 10,
        caching = "master") # Important for DBI caches!
 } else {
   library(clustermq)

### 2019-11-08 analysis/reports/dat_report_template.Rmd
fix misc abund report issue

@@
 
+if(this_dataset == "misc_abund_short") {
+  cache_loc = "miscabund"
+} else{
+  cache_loc = this_dataset
+}
+
 ## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", this_dataset, ".sqlite")))
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
 cache <- storr::storr_dbi("datatable", "keystable", db)

### 2019-11-08 analysis/miscabund_pipeline.R

@@ -53,7 +53,7 @@ nodename <- Sys.info()["nodename"]
 if(grepl("ufhpc", nodename)) {
   print("I know I am on the HiPerGator!")
   library(clustermq)
-  options(clustermq.scheduler = "slurm", clustermq.template = "slurm_clustermq_tall.tmpl")
+  options(clustermq.scheduler = "slurm", clustermq.template = "slurm_clustermql.tmpl")
   ## Run the pipeline parallelized for HiPerGator
   make(all,
        force = TRUE,
@@ -61,7 +61,7 @@ if(grepl("ufhpc", nodename)) {
        cache_log_file = here::here("analysis", "drake", "cache_log_miscabund.txt"),
        verbose = 2,
        parallelism = "clustermq",
-       jobs = 10,
+       jobs = 20,
        caching = "master") # Important for DBI caches!
 } else {
   library(clustermq)

### 2019-11-08 analysis/reports/dat_report_template.Rmd
fix hist issue

@@
   ggtitle("Number of samples achieved")  +
-  xlim = c(-11, max(site_samples$nsamples) + 11)
+  xlim(c(-11, max(site_samples$nsamples) + 11))
 

### 2019-11-11 analysis/reports/compare_datasets.Rmd
try changing mem strategy

---
title: "Between-dataset comparisons"
output: 
  github_document
params:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

all_statevars <- list()

datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

for(i in 1:6) {

  this_dataset = datasets[i]
  if(this_dataset == "misc_abund_short") {
    cache_loc = "miscabund"
  } else {
    cache_loc = this_dataset
  }

  ## Set up the cache and config
  db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
  cache <- storr::storr_dbi("datatable", "keystable", db)

 this_dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)

 all_statevars[[i]] <- get_statevars(this_dat)

 all_statevars[[i]]$site <- as.character(all_statevars[[i]]$site)

  DBI::dbDisconnect(db)
  rm(cache)
  rm(db)
  rm(this_dat)
}

names(all_statevars) <- datasets

all_statevars <- bind_rows(all_statevars)

all_extremes <- all_statevars %>%
  group_by(dat, singletons) %>%
  summarize(min_s0 = min(s0),
            min_n0 = min(n0),
            max_s0 = max(s0),
            max_n0 = max(n0)) %>%
  ungroup()

```

## Extremes by dataset

Here are the spaces occupied by each dataset
```{r statevars}
extrema_plot <- ggplot(data = all_extremes, aes(x = max_s0, y = max_n0, color = dat)) +
  geom_point(aes(x = min_s0, y = min_n0)) +
  geom_point(aes(x = max_s0, y = max_n0)) +
  facet_wrap(vars(singletons)) +
  scale_color_viridis_d(end = .8) +
  theme_bw() +
  xlim(0, max(all_extremes$max_s0)) +
  ylim(0, max(all_extremes$max_n0))

extrema_plot

```

```{r occupancy}

all_statevars <- all_statevars %>%
  filter(!singletons) %>%
  mutate(in_bbs = between(s0, all_extremes$min_s0[1], all_extremes$max_s0[1]) + between(n0, all_extremes$min_n0[1], all_extremes$max_n0[1]) == 2,
         in_fia = between(s0, all_extremes$min_s0[3], all_extremes$max_s0[3]) + between(n0, all_extremes$min_n0[3], all_extremes$max_n0[3]) == 2,
         in_gentry = between(s0, all_extremes$min_s0[5], all_extremes$max_s0[5]) + between(n0, all_extremes$min_n0[5], all_extremes$max_n0[5]) == 2,
         in_mcdb = between(s0, all_extremes$min_s0[7], all_extremes$max_s0[7]) + between(n0, all_extremes$min_n0[7], all_extremes$max_n0[7]) == 2,
         in_misc = between(s0, all_extremes$min_s0[9], all_extremes$max_s0[9]) + between(n0, all_extremes$min_n0[9], all_extremes$max_n0[9]) == 2,
         in_portal = between(s0, all_extremes$min_s0[11], all_extremes$max_s0[11]) + between(n0, all_extremes$min_n0[11], all_extremes$max_n0[11]) == 2) %>%
  mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)

```

### 2019-11-12 analysis/reports/compare_datasets.Rmd
change memory strategy

@@
   github_document
-params:
 ---
@@
 
-datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
+# datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
 
-for(i in 1:6) {
+datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
+
+for(i in 1:length(datasets)) {
 
@@
   filter(!singletons) %>%
-  mutate(in_bbs = between(s0, all_extremes$min_s0[1], all_extremes$max_s0[1]) + between(n0, all_extremes$min_n0[1], all_extremes$max_n0[1]) == 2,
-         in_fia = between(s0, all_extremes$min_s0[3], all_extremes$max_s0[3]) + between(n0, all_extremes$min_n0[3], all_extremes$max_n0[3]) == 2,
-         in_gentry = between(s0, all_extremes$min_s0[5], all_extremes$max_s0[5]) + between(n0, all_extremes$min_n0[5], all_extremes$max_n0[5]) == 2,
-         in_mcdb = between(s0, all_extremes$min_s0[7], all_extremes$max_s0[7]) + between(n0, all_extremes$min_n0[7], all_extremes$max_n0[7]) == 2,
-         in_misc = between(s0, all_extremes$min_s0[9], all_extremes$max_s0[9]) + between(n0, all_extremes$min_n0[9], all_extremes$max_n0[9]) == 2,
-         in_portal = between(s0, all_extremes$min_s0[11], all_extremes$max_s0[11]) + between(n0, all_extremes$min_n0[11], all_extremes$max_n0[11]) == 2) %>%
-  mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)
+  mutate(
+    # in_bbs = between(s0, filter(all_extremes, dat == "bbs", singletons == F)$min_s0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "bbs", singletons == F)$min_n0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_n0[1]) == 2,
+    in_fia = between(s0, filter(all_extremes, dat == "fia", singletons == F)$min_s0[1], filter(all_extremes, dat == "fia", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "fia", singletons == F)$min_n0[1], filter(all_extremes, dat == "fia", singletons == F)$max_n0[1]) == 2,
+    in_gentry = between(s0, filter(all_extremes, dat == "gentry", singletons == F)$min_s0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "gentry", singletons == F)$min_n0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_n0[1]) == 2,
+    in_mcdb = between(s0, filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "mcdb", singletons == F)$min_n0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_n0[1]) == 2,
+    in_misc = between(s0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$min_n0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_n0[1]) == 2,
+    in_portal = between(s0, filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "portal_plants", singletons == F)$min_n0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_n0[1]) == 2
+    ) %>%
+  # mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)
+  mutate(total_in =in_fia + in_gentry + in_mcdb + in_misc + in_portal)
 
 ```
+
+```{r intersection plot}
+
+intersection_plot <- ggplot(data = filter(all_statevars, singletons == FALSE, total_in > 1), aes(x = s0, y = n0, color = as.factor(total_in))) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  scale_color_viridis_d(option = "plasma", end = .9)
+intersection_plot
+
+```

### 2019-11-12 analysis/bbs_pipeline.R

@@ -62,7 +62,8 @@ if(grepl("ufhpc", nodename)) {
        verbose = 2,
        parallelism = "clustermq",
        jobs = 20,
-       caching = "master") # Important for DBI caches!
+       caching = "master",
+       memory_strategy = "autoclean") # Important for DBI caches!
 } else {
   library(clustermq)
   options(clustermq.scheduler = "multicore")

### 2019-11-13 analysis/reports/compare_datasets.Rmd
dataset intersection report, increase bbs memory

--- 2019-11-11 analysis/reports/compare_datasets.Rmd
@@
 
-for(i in 1:6) {
+#datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
+
+for(i in 1:length(datasets)) {
 
@@
 
+## Overall dataset spaces
+
+```{r overall spaces}
+
+overall <- ggplot(data = filter(all_statevars, !singletons), aes(x = s0, y = n0)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "fixed")
+overall
+```
+
 ## Extremes by dataset
@@
   filter(!singletons) %>%
-  mutate(in_bbs = between(s0, all_extremes$min_s0[1], all_extremes$max_s0[1]) + between(n0, all_extremes$min_n0[1], all_extremes$max_n0[1]) == 2,
-         in_fia = between(s0, all_extremes$min_s0[3], all_extremes$max_s0[3]) + between(n0, all_extremes$min_n0[3], all_extremes$max_n0[3]) == 2,
-         in_gentry = between(s0, all_extremes$min_s0[5], all_extremes$max_s0[5]) + between(n0, all_extremes$min_n0[5], all_extremes$max_n0[5]) == 2,
-         in_mcdb = between(s0, all_extremes$min_s0[7], all_extremes$max_s0[7]) + between(n0, all_extremes$min_n0[7], all_extremes$max_n0[7]) == 2,
-         in_misc = between(s0, all_extremes$min_s0[9], all_extremes$max_s0[9]) + between(n0, all_extremes$min_n0[9], all_extremes$max_n0[9]) == 2,
-         in_portal = between(s0, all_extremes$min_s0[11], all_extremes$max_s0[11]) + between(n0, all_extremes$min_n0[11], all_extremes$max_n0[11]) == 2) %>%
+  mutate(
+     in_bbs = between(s0, filter(all_extremes, dat == "bbs", singletons == F)$min_s0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "bbs", singletons == F)$min_n0[1], filter(all_extremes, dat == "bbs", singletons == F)$max_n0[1]) == 2,
+    in_fia = between(s0, filter(all_extremes, dat == "fia", singletons == F)$min_s0[1], filter(all_extremes, dat == "fia", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "fia", singletons == F)$min_n0[1], filter(all_extremes, dat == "fia", singletons == F)$max_n0[1]) == 2,
+    in_gentry = between(s0, filter(all_extremes, dat == "gentry", singletons == F)$min_s0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "gentry", singletons == F)$min_n0[1], filter(all_extremes, dat == "gentry", singletons == F)$max_n0[1]) == 2,
+    in_mcdb = between(s0, filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "mcdb", singletons == F)$min_n0[1], filter(all_extremes, dat == "mcdb", singletons == F)$max_n0[1]) == 2,
+    in_misc = between(s0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "misc_abund_short", singletons == F)$min_n0[1], filter(all_extremes, dat == "misc_abund_short", singletons == F)$max_n0[1]) == 2,
+    in_portal = between(s0, filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_s0[1]) + between(n0, filter(all_extremes, dat == "portal_plants", singletons == F)$min_n0[1], filter(all_extremes, dat == "portal_plants", singletons == F)$max_n0[1]) == 2
+    ) %>%
    mutate(total_in = in_bbs + in_fia + in_gentry + in_mcdb + in_misc + in_portal)
+  # mutate(total_in =in_fia + in_gentry + in_mcdb + in_misc + in_portal)
 
 ```
+
+```{r intersection plot}
+
+intersection_plot <- ggplot(data = filter(all_statevars, singletons == FALSE, total_in > 1), aes(x = s0, y = n0, color = as.factor(total_in))) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  scale_color_viridis_d(option = "plasma", end = .9)
+intersection_plot
+
+```
+I don't trust that occupancy. Here's another approach.
+
+```{r new occupancy}
+
+max_min_s0 = max(all_extremes$min_s0)
+max_min_n0 = max(all_extremes$min_n0)
+
+min_max_s0 = min(all_extremes$max_s0)
+min_max_n0 = min(all_extremes$max_n0)
+
+all_statevars_within <- all_statevars %>%
+  filter(s0 > max_min_s0, s0 < min_max_s0, n0 > max_min_n0, n0 < min_max_n0, !singletons) %>%
+  select(site, dat, s0, n0) %>%
+  group_by(s0, n0) %>%
+  mutate(ndats = length(unique(dat)),
+         nsites = dplyr::n()) %>%
+  ungroup()
+
+new_occ <- ggplot(data = all_statevars_within, aes(x = s0,y = n0, color = as.factor(ndats))) +
+  geom_point(alpha = .3) +
+  scale_color_viridis_d(option = "plasma", end = .9, direction = -1) +
+  theme_bw()
+new_occ
+```

### 2019-11-13 analysis/reports/dat_report_template.Rmd
break bbs into two

@@
 dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
+if(this_dataset == "bbs") {
+  loadd(all_di_FALSE, cache = cache)
+  loadd(all_di_TRUE, cache = cache)
+  all_di = bind_rows(all_di_FALSE, all_di_TRUE)
+  rm(all_di_FALSE)
+  rm(all_di_TRUE)
+
+  } else {
     loadd(all_di, cache = cache)
+  }
 

### 2019-11-13 analysis/reports/cross_dataset.Rmd
set up for cross dataset comparisons

---
title: "Between-dataset comparisons"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

all_di <- list() 
datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

#datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

for(i in 1:length(datasets)) {

  this_dataset = datasets[i]
  if(this_dataset == "misc_abund_short") {
    cache_loc = "miscabund"
  } else if(this_dataset == "fia_short") {

    cache_loc = "fia"
    } else {
    cache_loc = this_dataset
  }

  ## Set up the cache and config
  db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
  cache <- storr::storr_dbi("datatable", "keystable", db)

 all_di[[i]] <- readd(all_di, cache = cache)
 all_di[[i]] <- filter(all_di[[i]], source == "observed")

   this_dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
sv <- get_statevars(this_dat)
all_di[[i]] <- left_join(all_di[[i]], sv, by = c("sim", "site", "source", "singletons", "dat"))

  DBI::dbDisconnect(db)
  rm(cache)
  rm(db)
}

all_di <- bind_rows(all_di)

```

```{r overall percentile heatmap}

overall_heatmap_skew <- ggplot(data = all_di, aes(x = s0, y = n0, color = skew_percentile)) +
  geom_point(alpha = .2) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", begin = .1, end = .8, direction = -1) +
  facet_wrap(vars(singletons)) +
  ggtitle("Skewness Percentile") +
  theme(legend.position = "bottom")

overall_heatmap_simpson <- ggplot(data = all_di, aes(x = s0, y = n0, color = simpson_percentile)) +
  geom_point(alpha = .2) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", begin = .1, end = .8)+
  facet_wrap(vars(singletons)) +
  ggtitle("Simpson's Percentile")+
  theme(legend.position = "bottom")

overall_heatmap_skew_zoomed <- overall_heatmap_skew +
  ylim(0, 5000) +
  xlim(0, 250)+
  theme(legend.position = "none")

overall_heatmap_simpson_zoomed <- overall_heatmap_simpson +
  ylim(0, 5000) +
  xlim(0, 250)+
  theme(legend.position = "none")

gridExtra::grid.arrange(grobs = list(overall_heatmap_skew, overall_heatmap_skew_zoomed), nrow= 1)
gridExtra::grid.arrange(grobs = list(overall_heatmap_simpson, overall_heatmap_simpson_zoomed), nrow= 1)

```

Broken out by dataset

```{r dataset heatmaps}

dat_heatmap_skew <-  ggplot(data = filter(all_di, !singletons), aes(x = s0, y = n0, color = skew_percentile)) +
  geom_point(alpha = .4) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", begin = .1, end = .8, direction = -1)+
  facet_wrap(vars(dat), scales = "free") +
  ggtitle("Skew Percentile")+
  theme(legend.position = "bottom")
dat_heatmap_skew

dat_heatmap_simpson <-  ggplot(data = filter(all_di, !singletons), aes(x = s0, y = n0, color = simpson_percentile)) +
  geom_point(alpha = .4) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", begin = .1, end = .8)+
  facet_wrap(vars(dat), scales = "free") +
  ggtitle("Simpson's Percentile")+
  theme(legend.position = "bottom")
dat_heatmap_simpson
```

Against S0

```{r s0 percentile}

overall_s0_skew <- ggplot(data = filter(all_di, !singletons), aes(x = s0, y = skew_percentile)) +
  geom_point(alpha = .1) +
  geom_smooth(method = "lm", se = F, color = "pink") +
  theme_bw() +
  ggtitle("Skew percentile")
overall_s0_skew

dat_s0_skew <- overall_s0_skew +
  facet_wrap(vars(dat), scales = "free")
dat_s0_skew

overall_s0_simpson <- ggplot(data = filter(all_di, !singletons), aes(x = s0, y = simpson_percentile)) +
  geom_point(alpha = .1) +
    geom_smooth(method = "lm", se = F, color = "pink") +
  theme_bw() +
  ggtitle("Simpson percentile")
overall_s0_simpson

dat_s0_simpson <- overall_s0_simpson +
  facet_wrap(vars(dat), scales = "free")
dat_s0_simpson

```

### 2019-11-13 analysis/bbs_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "bbs"
 
 sites_list <- list_sites("bbs")
-ndraws = 2500
-#sites_list <- sites_list[1:15, ]
+ndraws = 100
+sites_list <- sites_list[1:15, ]
 dat_plan <- drake_plan(
   dat = target(load_dataset(dataset_name = d),
                transform = map(

### 2019-11-13 analysis/fia_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "fia_short"
 
 sites_list <- list_sites("fia_short")
-ndraws = 2500
-#sites_list <- sites_list[1:1000, ]
+ndraws = 100
+sites_list <- sites_list[1:1000, ]
 
 dat_plan <- drake_plan(
   dat = target(load_dataset(dataset_name = d),

### 2019-11-13 analysis/mcdb_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "mcdb"
 
 sites_list <- list_sites("mcdb")
-ndraws = 2500
-#sites_list <- sites_list[1:15, ]
+ndraws = 100
+sites_list <- sites_list[1:15, ]
 
 all <- drake_plan(
   dat = target(load_dataset(dataset_name = d),

### 2019-11-13 analysis/miscabund_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "misc_abund_short"
 
 sites_list <- list_sites("misc_abund_short")
-ndraws = 2500
-#sites_list <- sites_list[1:15, ]
+ndraws = 100
+sites_list <- sites_list[1:15, ]
 dat_plan <- drake_plan(
   dat = target(load_dataset(dataset_name = d),
                transform = map(

### 2019-11-13 analysis/portal_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "portal_plants"
 
 sites_list <- list_sites("portal_plants")
-ndraws = 2500
-#sites_list <- sites_list[1:15, ]
+ndraws = 100
+sites_list <- sites_list[1:15, ]
 
 all <- drake_plan(
   dat = target(load_dataset(dataset_name = d),

### 2019-11-14 analysis/reports/dat_report_template.Rmd
fix bbs?

--- 2019-11-08 analysis/reports/dat_report_template.Rmd
@@
   cache_loc = "miscabund"
-} else{
+} else if (this_dataset == "fia_short") {
+  cache_loc = "fia" 
+} else {
   cache_loc = this_dataset
@@
 dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
+
 loadd(all_di, cache = cache)

### 2019-11-14 analysis/bbs_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "bbs"
 
 sites_list <- list_sites("bbs")
-ndraws = 100
-sites_list <- sites_list[1:15, ]
+ndraws = 2500
+#sites_list <- sites_list[1:15, ]
 dat_plan <- drake_plan(
   dat = target(load_dataset(dataset_name = d),
                transform = map(
@@ -26,9 +26,10 @@ dat_plan <- drake_plan(
                                      singletons = !!c(TRUE, FALSE))),
   di = target(add_dis(fs),
               transform = map(fs)),
-  all_di = target(dplyr::bind_rows(di),
-                  transform = combine(di),
+  all_di_s = target(dplyr::bind_rows(di),
+                  transform = combine(di, .by = singletons),
                   hpc = F),
+  all_di = target(dplyr::bind_rows(all_di_s_TRUE, all_di_s_FALSE), hpc = F),
   report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di, is_template = TRUE, dat_name = !!datasets),
                   trigger = trigger(condition = T),
                   hpc = F)

### 2019-11-14 analysis/reports/dat_report_template.Rmd
This template should work with BBS, FIA if that becomes problematic

@@
 
+if("all_di" %in% cached(cache = cache)) {
 loadd(all_di, cache = cache)
+} else {
+  all_di_names <- cached(cache = cache)[ which(grepl(cached(cache = cache), pattern = "all_di_s_"))]
+  all_di_list <- lapply(all_di_names, FUN = readd, cache = cache, character_only =T)
+  names(all_di_list) <- all_di_names
+  all_di <- bind_rows(all_di_list)
+  rm(all_di_names)
+  rm(all_di_list)
+}
 

### 2019-11-14 analysis/reports/cross_dataset.Rmd
fix cross dataaset report

@@
 
+  if("all_di" %in% cached(cache = cache)) {
     all_di[[i]] <- readd(all_di, cache = cache)
+  } else {
+    all_di_names <- cached(cache = cache)[ which(grepl(cached(cache = cache), pattern = "all_di_s_"))]
+    all_di_list <- lapply(all_di_names, FUN = readd, cache = cache, character_only =T)
+    names(all_di_list) <- all_di_names
+    all_di[[i]] <- bind_rows(all_di_list)
+    rm(all_di_names)
+    rm(all_di_list)
+  }
   all_di[[i]] <- filter(all_di[[i]], source == "observed")

### 2019-11-14 analysis/bbs_pipeline.R
try different di method for bbs

@@ -29,6 +29,10 @@ dat_plan <- drake_plan(
   all_di_s = target(dplyr::bind_rows(di),
                   transform = combine(di, .by = singletons),
                   hpc = F),
+  di_obs = target(dplyr::filter(di, source == "observed"),
+                  transform = map(fs)),
+  all_di_obs = target(dplyr::bind_rows(di_obs),
+                      transform = combine(di_obs)),
   #all_di = target(dplyr::bind_rows(all_di_s_TRUE, all_di_s_FALSE), hpc = F),
   report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = list(all_di_s_FALSE, all_di_s_TRUE), is_template = TRUE, dat_name = !!datasets),
                   trigger = trigger(condition = T),

### 2019-11-14 analysis/reports/dat_report_template.Rmd
pull dis

--- 2019-11-14 analysis/reports/dat_report_template.Rmd
@@
 
-loadd(all_di, cache = cache)
+all_di <- readd(all_di_obs, cache = cache)
 
@@
 site_samples <- all_di %>%
-  select(sim, source, site, singletons) %>%
-  group_by(source, site, singletons) %>%
-  summarize(nsamples = length(unique(sim))) %>%
-  ungroup() %>%
-  filter(source == "sampled") %>%
   left_join(select(sv, -source, -sim), by = c("site", "singletons"))

### 2019-11-14 R/metrics.R

@@ -128,3 +128,21 @@ get_percentile <- function(a_value, a_vector) {
 
   return(percentile_val)
 }
+
+#' Pull observed diversity indices and nb samples achieved
+#'
+#' @param di_df result of di_wrapper
+#'
+#' @return di_df for observed + n samples
+#' @export
+#'
+#' @importFrom dplyr filter mutate
+pull_di <- function(di_df) {
+
+  di_df <- di_df  %>%
+    dplyr::mutate(nsamples = length(unique(dplyr::filter(di_df, source == "sampled")$sim))) %>%
+    dplyr::filter(source == "observed")
+
+  return(di_df)
+
+}

### 2019-11-14 analysis/bbs_pipeline.R

@@ -26,7 +26,7 @@ dat_plan <- drake_plan(
                                      singletons = !!c(TRUE, FALSE))),
   di = target(add_dis(fs),
               transform = map(fs)),
-  di_obs = target(dplyr::filter(di, source == "observed"),
+  di_obs = target(pull_di(di),
                   transform = map(di)),
   all_di_obs = target(dplyr::bind_rows(di_obs),
                       transform = combine(di_obs)),

### 2019-11-14 analysis/reports/cross_dataset.Rmd
try different di method for bbs
cross dataset report

--- 2019-11-13 analysis/reports/cross_dataset.Rmd
@@
 all_di <- list() 
-datasets <- c("bbs", "fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
+datasets <- c("bbs", "fia_short", "gentry", "mcdb", "misc_abund_short", "portal_plants")
 
@@
 
- all_di[[i]] <- readd(all_di, cache = cache)
+    all_di[[i]] <- readd(all_di_obs, cache = cache)
+
   all_di[[i]] <- filter(all_di[[i]], source == "observed")

### 2019-11-14 analysis/reports/cross_dataset.Rmd
add nsamples plot

@@
 
-```{r dataset heatmaps}
+```{r dataset heatmaps, fig.width = 30, fig.height = 20}
 
@@
 ```
+
+Against nsamples
+
+```{r nsamples}
+
+skew_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  ggtitle("Skew percentile v. nsamples")
+
+skew_nsamples
+
+simp_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = simpson_percentile)) +
+  geom_point(alpha = .1) + 
+  theme_bw() +
+  ggtitle("Simpson percentile v. nsamples")
+
+simp_nsamples
+```

### 2019-11-14 analysis/reports/cross_dataset.Rmd
add trendline

--- 2019-11-14 analysis/reports/cross_dataset.Rmd
@@
 ```
+
+Against nsamples
+
+```{r nsamples}
+
+skew_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = skew_percentile)) +
+  geom_point(alpha = .1) +
+    geom_smooth(method = "lm", se = F, color = "pink") +
+
+  theme_bw() +
+  ggtitle("Skew percentile v. nsamples")
+
+skew_nsamples
+
+simp_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = simpson_percentile)) +
+  geom_point(alpha = .1) + 
+    geom_smooth(method = "lm", se = F, color = "pink") +
+
+  theme_bw() +
+  ggtitle("Simpson percentile v. nsamples")
+
+simp_nsamples
+```

### 2019-11-14 analysis/reports/cross_dataset.Rmd
just get the csv
run more fia

@@
   github_document
+params:
+  on_hpg: [FALSE]
 ---
@@
 library(scadsanalysis)
+
+if(params$on_hpg) {
 
@@
 
+write.csv(all_di, "all_di.csv", row.names = F)
+} else {
+  all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+}
 ```
@@
 
+dat_skew_nsamples <- skew_nsamples +
+  facet_wrap(vars(dat))
+
+dat_skew_nsamples
+
 simp_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = simpson_percentile)) +
@@
 ```
+
+```{r histograms, fig.height = 6, fig.width =6}
+
+skewhists <- ggplot(data = all_di, aes(x = skew_percentile)) +
+  geom_histogram(binwidth = 5, alpha = .3) +
+  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500)) +
+  theme_bw() +
+  facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
+  ggtitle("Skewness")
+skewhists
+
+simpsonhists <- ggplot(data = all_di, aes(x = simpson_percentile)) +
+  geom_histogram(binwidth = 5, alpha = .3) +
+  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500)) +
+  theme_bw() +
+  facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
+  ggtitle("Simpson")
+simpsonhists
+
+```

### 2019-11-14 analysis/fia_pipeline.R

@@ -8,7 +8,7 @@ datasets <- "fia_short"
 
 sites_list <- list_sites("fia_short")
 ndraws = 2500
-sites_list <- sites_list[1:4000, ]
+sites_list <- sites_list[1:6000, ]
 
 dat_plan <- drake_plan(
   dat = target(load_dataset(dataset_name = d),

### 2019-11-14 analysis/reports/cross_dataset.Rmd
cross dataset report stuff

@@
 
-```{r overall percentile heatmap}
-
-overall_heatmap_skew <- ggplot(data = all_di, aes(x = s0, y = n0, color = skew_percentile)) +
-  geom_point(alpha = .2) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", begin = .1, end = .8, direction = -1) +
-  facet_wrap(vars(singletons)) +
-  ggtitle("Skewness Percentile") +
-  theme(legend.position = "bottom")
-
-overall_heatmap_simpson <- ggplot(data = all_di, aes(x = s0, y = n0, color = simpson_percentile)) +
-  geom_point(alpha = .2) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", begin = .1, end = .8)+
-  facet_wrap(vars(singletons)) +
-  ggtitle("Simpson's Percentile")+
-  theme(legend.position = "bottom")
-
-overall_heatmap_skew_zoomed <- overall_heatmap_skew +
-  ylim(0, 5000) +
-  xlim(0, 250)+
-  theme(legend.position = "none")
-
-overall_heatmap_simpson_zoomed <- overall_heatmap_simpson +
-  ylim(0, 5000) +
-  xlim(0, 250)+
-  theme(legend.position = "none")
-
-gridExtra::grid.arrange(grobs = list(overall_heatmap_skew, overall_heatmap_skew_zoomed), nrow= 1)
-gridExtra::grid.arrange(grobs = list(overall_heatmap_simpson, overall_heatmap_simpson_zoomed), nrow= 1)
-
-```
-
-Broken out by dataset
-
-```{r dataset heatmaps, fig.width = 30, fig.height = 20}
-
-dat_heatmap_skew <-  ggplot(data = filter(all_di, !singletons), aes(x = s0, y = n0, color = skew_percentile)) +
-  geom_point(alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", begin = .1, end = .8, direction = -1)+
-  facet_wrap(vars(dat), scales = "free") +
-  ggtitle("Skew Percentile")+
-  theme(legend.position = "bottom")
-dat_heatmap_skew
-
-dat_heatmap_simpson <-  ggplot(data = filter(all_di, !singletons), aes(x = s0, y = n0, color = simpson_percentile)) +
-  geom_point(alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", begin = .1, end = .8)+
-  facet_wrap(vars(dat), scales = "free") +
-  ggtitle("Simpson's Percentile")+
-  theme(legend.position = "bottom")
-dat_heatmap_simpson
-```
-
-Against S0
-
-```{r s0 percentile}
-
-overall_s0_skew <- ggplot(data = filter(all_di, !singletons), aes(x = s0, y = skew_percentile)) +
-  geom_point(alpha = .1) +
-  geom_smooth(method = "lm", se = F, color = "pink") +
-  theme_bw() +
-  ggtitle("Skew percentile")
-overall_s0_skew
-
-dat_s0_skew <- overall_s0_skew +
-  facet_wrap(vars(dat), scales = "free")
-dat_s0_skew
-
-overall_s0_simpson <- ggplot(data = filter(all_di, !singletons), aes(x = s0, y = simpson_percentile)) +
-  geom_point(alpha = .1) +
-  geom_smooth(method = "lm", se = F, color = "pink") +
-  theme_bw() +
-  ggtitle("Simpson percentile")
-overall_s0_simpson
-
-dat_s0_simpson <- overall_s0_simpson +
-  facet_wrap(vars(dat), scales = "free")
-dat_s0_simpson
-
-```
-
-Against nsamples
-
-```{r nsamples}
-
-skew_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = skew_percentile)) +
-  geom_point(alpha = .1) +
-    geom_smooth(method = "lm", se = F, color = "pink") +
-
-  theme_bw() +
-  ggtitle("Skew percentile v. nsamples")
-
-skew_nsamples
-
-dat_skew_nsamples <- skew_nsamples +
-  facet_wrap(vars(dat))
-
-dat_skew_nsamples
-
-simp_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = simpson_percentile)) +
-  geom_point(alpha = .1) + 
-    geom_smooth(method = "lm", se = F, color = "pink") +
-
-  theme_bw() +
-  ggtitle("Simpson percentile v. nsamples")
-
-simp_nsamples
-```
-
 ```{r histograms, fig.height = 6, fig.width =6}
@@
 ```
+
+Observations from these histograms:
+
+* FIA really struggles to get 2500 samples
+* Portal is the *most* concentrated of all the datasets.
+* Then MCDB and misc, then gentry, then bbs. FIA is hard to place but looks idiosyncratic.
+* Curious about how variation in %ile maps on to S and N, *particularly* for Gentry and BBS. 
+* Skewness is less extreme than Simpson (more density in the in-between). 
+* Singletons doesn't appear to be terrifically impactful. From now on filtering to *unaltered* vectors.
+
+```{r s and n mapping, fig.width = 12, fig.height = 10}
+
+all_di <- filter(all_di, !singletons)
+
+skew_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = skew_percentile)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free") + 
+  ggtitle("Skewness") +
+  scale_color_viridis_c(option = "plasma", end= .75)
+
+skew_s_n_maps
+
+simpson_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = simpson_percentile)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free") + 
+  ggtitle("Simpson") +
+  scale_color_viridis_c(option = "plasma", end= .75, direction = -1)
+
+simpson_s_n_maps
+
+```
+
+The less extreme (low skew, high simpson) vectors appear vaguely collected in the lower right for Gentry and BBS.
+Those are the regions with relatively high N/S, aka low average abundance, aka a relatively small feasible set.
+
+Conversely, for MCDB and Misc, it almost looks like the very least skewed elements are way down at tiny abundances?
+
+Do percentiles scan with S/N?
+
+```{r avg abund}
+
+all_di <- mutate(all_di, avg_abund = n0/s0)
+
+skew_avgabund <- ggplot(data = all_di, aes(x = avg_abund, y = skew_percentile)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  ggtitle("Skew") +
+  facet_wrap(vars(dat), scales = "free")
+
+skew_avgabund
+
+simpson_avgabund <- ggplot(data = all_di, aes(x = avg_abund, y = simpson_percentile)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  ggtitle("Simpson") +
+  facet_wrap(vars(dat), scales = "free")
+
+simpson_avgabund
+
+```
+There is perhaps a constraint, but that might be because you rarely get v high average abundances.
+You seem to rarely get low skewness or high Simpson at high average abundance, which scans with the heatmaps.
+
+Do Simpson and skewness correspond?
+```{r do skew and simp correlate}
+
+ss_plot <- ggplot(data = all_di, aes(x= skew_percentile, y = simpson_percentile, color = dat)) +
+  geom_point(alpha = .1) +
+  scale_color_viridis_d(end = .8) +
+  theme_bw() +
+  ggtitle("Skew v Simp")
+
+ss_plot
+
+ss_facet_plot <- ss_plot +
+  facet_wrap(vars(dat))
+
+ss_facet_plot
+```
+
+There's a weak relationship between Simpson and skewness, but a lot of noise. They are not substitutable.
+
+Why is Gentry so strangely bimodal? It's like a U, when all the others tend towards one end or the other.
+
+Why are BBS and mammals less frequently squished than Portal?

### 2019-11-15 analysis/reports/cross_dataset.Rmd
add range plots

@@
 Why are BBS and mammals less frequently squished than Portal?
+
+Looking at range of skewness and Simpsons:
+
+```{r ranges}
+
+skew_range_hist <- ggplot(data = filter(all_di, nsamples > 2000), aes(x = skew_range, y = skew_percentile, color = dat)) +
+  geom_point(alpha = .2) +
+  geom_smooth(method = "lm", se =F) +
+  theme_bw() +
+  scale_color_viridis_d(end = .8) +
+  facet_wrap(vars(dat), scales = "free") + 
+  ggtitle("Skewness")
+
+skew_range_hist
+
+simpson_range_hist <- ggplot(data = filter(all_di, nsamples > 2000), aes(x = simpson_range, y = simpson_percentile, color = dat)) +
+  geom_point(alpha = .2) +
+    geom_smooth(method = "lm", se =F) +
+
+  theme_bw() +
+  scale_color_viridis_d(end = .8) +
+  facet_wrap(vars(dat), scales = "free") +
+  ggtitle("Simpson")
+
+simpson_range_hist
+
+```
+
+I added the ranges because I thought the percentiles might be constrained somewhat by the range of values represented in the feasible set.
+It doesn't look to me like there is a strong relationship between range and %ile.

### 2019-11-15 analysis/reports/cross_dataset.Rmd
add summary plots and set up to run all of fia

@@
 * Singletons doesn't appear to be terrifically impactful. From now on filtering to *unaltered* vectors.
+* I think it's best to filter to at least 2000 samples.
 
-```{r s and n mapping, fig.width = 12, fig.height = 10}
+Some summary statistics:
+```{r summary stats}
+
+di_summary <- all_di %>%
+  filter(nsamples >= 2000) %>%
+  group_by(dat, singletons) %>%
+  summarize(mean_skew = mean(skew_percentile, na.rm=T),
+            sd_skew = sd(skew_percentile, na.rm = T),
+            mean_simpson = mean(simpson_percentile, na.rm = T),
+            sd_simpson = sd(simpson_percentile, na.rm = T),
+            mean_nsamples = mean(nsamples),
+            nsites = length(unique(site))) %>%
+  ungroup()
+
+skew_summary_plot <- ggplot(data = di_summary, aes(x = singletons, y = mean_skew, group = singletons)) +
+  geom_point() +
+  geom_errorbar(aes(x = singletons, ymin = mean_skew - sd_skew, ymax = mean_skew + sd_skew)) +
+  geom_label(aes(x = singletons, y = 10, label = signif(mean_skew, digits = 4))) +
+  theme_bw() +
+  facet_wrap(vars(dat)) +
+  geom_hline(yintercept = 100, linetype = 2, color = "red") +
+  ylim(0, 110) +
+  ggtitle("Skewness, >= 2000 samples")
+skew_summary_plot
+
+simpson_summary_plot <- ggplot(data = di_summary, aes(x = singletons, y = mean_simpson, group = singletons)) +
+  geom_point() +
+  geom_errorbar(aes(x = singletons, ymin = mean_simpson - sd_simpson, ymax = mean_simpson + sd_simpson)) +
+    geom_label(aes(x = singletons, y = 90, label = signif(mean_simpson, digits = 4))) +
+  theme_bw() +
+  facet_wrap(vars(dat)) +
+  geom_hline(yintercept = 0, linetype = 2, color = "red") +
+  ylim(-10, 100) +
+  ggtitle("Simpson's, >= 2000 samples")
+simpson_summary_plot
+
+```
+
+```{r s and n mapping, fig.width = 12, fig.height = 18}
 
@@
 skew_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = skew_percentile)) +
-  geom_point(alpha = .3) +
+  geom_point(alpha = .1, size = .5) +
+  geom_point(data = filter(all_di, nsamples >= 2000), alpha = .2) +
   theme_bw() +
-  facet_wrap(vars(dat), scales = "free") + 
+  facet_wrap(vars(dat), scales = "free", ncol = 2) + 
   ggtitle("Skewness") +
@@
 simpson_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = simpson_percentile)) +
-  geom_point(alpha = .3) +
+  geom_point(alpha =  .1, size = .5) +
+  geom_point(data = filter(all_di, nsamples >= 2000), alpha = .2) +
   theme_bw() +
-  facet_wrap(vars(dat), scales = "free") + 
+  facet_wrap(vars(dat), scales = "free", ncol = 2)  + 
   ggtitle("Simpson") +

### 2019-11-15 analysis/fia_pipeline.R

@@ -8,7 +8,7 @@ datasets <- "fia_short"
 
 sites_list <- list_sites("fia_short")
 ndraws = 2500
-sites_list <- sites_list[1:2000, ]
+#sites_list <- sites_list[1:2000, ]
 set.seed(1978)
 
 dat_plan <- drake_plan(

### 2019-11-15 analysis/reports/dat_report_template.Rmd
update template to include heatmap

@@
 
+Here is a heatmap of an observed + sampled FS:
+
+```{r example heatmap}
+
+a_fs_name <- cached(cache = cache)[ which(substr(cached(cache = cache), 0, 3) == "fs_")[1]]
+
+fs_samples <- readd(a_fs_name, cache = cache, character_only = TRUE)
+
+fs_heatmap <- ggplot(data = fs_samples, aes(x = rank, y = abund, group = sim, color = source)) +
+  geom_line(alpha = .01) +
+  geom_line(data = filter(fs_samples, source == "observed")) +
+  theme_bw() +
+  scale_color_viridis_d(end = .8)
+
+fs_heatmap
+
+```
+
 ```{r cleanup}

### 2019-11-15 analysis/reports/dat_report_template.Rmd
add title to fs plot

@@
   theme_bw() +
-  scale_color_viridis_d(end = .8)
+  scale_color_viridis_d(end = .8) +
+  ggtitle(a_fs_name)
 

### 2019-11-16 analysis/reports/cross_dataset.Rmd
tweaks to cross dataset report

@@
   facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
-  ggtitle("Skewness")
+  ggtitle("Skewness") +
+  geom_vline(xintercept = 95, color = "red")
 skewhists
@@
   facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
-  ggtitle("Simpson")
+  ggtitle("Simpson") +
+    geom_vline(xintercept = 5, color = "red")
+
 simpsonhists
@@
             mean_nsamples = mean(nsamples),
-            nsites = length(unique(site))) %>%
+            nsites = length(unique(site)),
+            prop_skew_high = mean(skew_percentile >= 95),
+            prop_simpson_low = mean(simpson_percentile <= 5)) %>%
   ungroup()
@@
 simpson_summary_plot
+
+print(di_summary)
 

### 2019-11-18 analysis/reports/cross_dataset.Rmd
fix some formatting
boxplots, proportion low and high plots

--- 2019-11-15 analysis/reports/cross_dataset.Rmd
@@
 skewhists <- ggplot(data = all_di, aes(x = skew_percentile)) +
-  geom_histogram(binwidth = 5, alpha = .3) +
-  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500)) +
+  geom_histogram(binwidth = 5, alpha = .3, boundary = 0) +
+  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500), boundary = 0) +
   theme_bw() +
   facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
-  ggtitle("Skewness")
+  ggtitle("Skewness") +
+  geom_vline(xintercept = 95, color = "red")
 skewhists
@@
 simpsonhists <- ggplot(data = all_di, aes(x = simpson_percentile)) +
-  geom_histogram(binwidth = 5, alpha = .3) +
-  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500)) +
+  geom_histogram(binwidth = 5, alpha = .3, boundary = 0) +
+  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500), boundary = 0) +
   theme_bw() +
   facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
-  ggtitle("Simpson")
+  ggtitle("Simpson") +
+  geom_vline(xintercept = 5, color = "red")
+
 simpsonhists
@@
 * Singletons doesn't appear to be terrifically impactful. From now on filtering to *unaltered* vectors.
+* I think it's best to filter to at least 2000 samples.
 
-```{r s and n mapping, fig.width = 12, fig.height = 10}
+Some summary statistics:
+
+```{r summary stats}
+
+di_summary <- all_di %>%
+  filter(nsamples >= 2000) %>%
+  group_by(dat, singletons) %>%
+  summarize(mean_skew = mean(skew_percentile, na.rm=T),
+            sd_skew = sd(skew_percentile, na.rm = T),
+            mean_simpson = mean(simpson_percentile, na.rm = T),
+            sd_simpson = sd(simpson_percentile, na.rm = T),
+            mean_nsamples = mean(nsamples),
+            nsites = length(unique(site)),
+            prop_skew_high = mean(skew_percentile >= 95),
+            prop_simpson_low = mean(simpson_percentile <= 5),
+            med_skew = median(skew_percentile, na.rm = T),
+            med_simpson = median(simpson_percentile, na.rm = T),
+            skew_25 = quantile(skew_percentile, probs = .25),
+            simpson_75 = quantile(simpson_percentile, probs = .75)) %>%
+  ungroup()
+
+skew_boxplot <- ggplot(data = filter(all_di, nsamples >= 2000), aes(x = singletons, y = skew_percentile, group = singletons)) +
+  # geom_point() +
+  # geom_errorbar(aes(x = singletons, ymin = skew_25, ymax = med_skew)) +
+  # geom_point(data = all_di, aes(x = singletons, y = skew_percentile), size = .5, alpha = .05) +
+  # geom_label(aes(x = singletons, y = 10, label = signif(med_skew, digits = 4))) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_wrap(vars(dat)) +
+  geom_hline(yintercept = 100, linetype = 2, color = "red") +
+  ylim(0, 110) +
+  ggtitle("Skewness, >= 2000 samples")
+skew_boxplot
+
+simpson_boxplot <- ggplot(data = filter(all_di, nsamples >= 2000), aes(x = singletons, y = simpson_percentile, group = singletons)) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_wrap(vars(dat)) +
+  geom_hline(yintercept = 0, linetype = 2, color = "red") +
+  ylim(-10, 100) +
+  ggtitle("Simpson's, >= 2000 samples")
+simpson_boxplot
+
+print(select(di_summary, dat, singletons, mean_nsamples, nsites, prop_skew_high, prop_simpson_low))
+
+skew_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_skew_high, color = singletons, size = as.factor(nsites))) +
+  geom_point() +
+  theme_bw() +
+  ggtitle("Skew") +
+  scale_color_viridis_d(end = .8) +
+  ylim(0, 1) +
+  theme(legend.position = "none")
+
+simpson_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_simpson_low, color = singletons, size = as.factor(nsites))) +
+  geom_point() +
+  theme_bw() +
+  ggtitle("Simpson") +
+  scale_color_viridis_d(end = .8)+
+  ylim(0, 1) +
+  theme(legend.position = "none")
+
+gridExtra::grid.arrange(grobs = list(skew_summary_plot, simpson_summary_plot), nrow = 1)
+
+```
+
+```{r s and n mapping, fig.width = 12, fig.height = 18}
 

### 2019-11-18 analysis/reports/cross_dataset.Rmd
add .05 line

@@
   ylim(0, 1) +
+  geom_hline(yintercept = .05, color = "red") +
   theme(legend.position = "none")
@@
   ylim(0, 1) +
+    geom_hline(yintercept = .05, color = "red") +
+
   theme(legend.position = "none")

### 2019-11-18 analysis/reports/cross_dataset.Rmd
remove plots to force refresh

@@
     geom_hline(yintercept = .05, color = "red") +
-
   theme(legend.position = "none")

### 2020-01-17 analysis/reports/regressions.Rmd
adding some glms, not sure that this is the right statistical appraoch

--- 2019-11-18 analysis/reports/cross_dataset.Rmd
@@
 ---
-title: "Between-dataset comparisons"
+title: "Regressions"
 output: 
@@
 
-```{r summary stats}
+```{r summary plots}
 
@@
   filter(nsamples >= 2000) %>%
-  group_by(dat, singletons) %>%
-  summarize(mean_skew = mean(skew_percentile, na.rm=T),
-            sd_skew = sd(skew_percentile, na.rm = T),
-            mean_simpson = mean(simpson_percentile, na.rm = T),
-            sd_simpson = sd(simpson_percentile, na.rm = T),
-            mean_nsamples = mean(nsamples),
-            nsites = length(unique(site)),
-            prop_skew_high = mean(skew_percentile >= 95),
-            prop_simpson_low = mean(simpson_percentile <= 5),
-            med_skew = median(skew_percentile, na.rm = T),
-            med_simpson = median(simpson_percentile, na.rm = T),
-            skew_25 = quantile(skew_percentile, probs = .25),
-            simpson_75 = quantile(simpson_percentile, probs = .75)) %>%
-  ungroup()
+  mutate(avg_n = n0 / s0,
+         skew_pp = skew_percentile / 100,
+         simp_pp = simpson_percentile/100)
+```
 
-skew_boxplot <- ggplot(data = filter(all_di, nsamples >= 2000), aes(x = singletons, y = skew_percentile, group = singletons)) +
-  # geom_point() +
-  # geom_errorbar(aes(x = singletons, ymin = skew_25, ymax = med_skew)) +
-  # geom_point(data = all_di, aes(x = singletons, y = skew_percentile), size = .5, alpha = .05) +
-  # geom_label(aes(x = singletons, y = 10, label = signif(med_skew, digits = 4))) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(dat)) +
-  geom_hline(yintercept = 100, linetype = 2, color = "red") +
-  ylim(0, 110) +
-  ggtitle("Skewness, >= 2000 samples")
-skew_boxplot
+### Avg abundance
 
-simpson_boxplot <- ggplot(data = filter(all_di, nsamples >= 2000), aes(x = singletons, y = simpson_percentile, group = singletons)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(dat)) +
-  geom_hline(yintercept = 0, linetype = 2, color = "red") +
-  ylim(-10, 100) +
-  ggtitle("Simpson's, >= 2000 samples")
-simpson_boxplot
+```{r avg abundance regression}
 
-print(select(di_summary, dat, singletons, mean_nsamples, nsites, prop_skew_high, prop_simpson_low))
+avgn_skew <- ggplot(data = di_summary, aes(x = avg_n, y = skew_pp)) +
+  geom_point() +
+  stat_smooth(method = "glm",method.args = list(family = binomial)) + 
+  facet_wrap(vars(dat), scales = "free") +
+  theme_bw()
 
-skew_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_skew_high, color = singletons, size = as.factor(nsites))) +
-  geom_point() +
-  theme_bw() +
-  ggtitle("Skew") +
-  scale_color_viridis_d(end = .8) +
-  ylim(0, 1) +
-  theme(legend.position = "none")
+avgn_skew
 
-simpson_summary_plot <- ggplot(data = di_summary, aes(x = dat, y = prop_simpson_low, color = singletons, size = as.factor(nsites))) +
-  geom_point() +
-  theme_bw() +
-  ggtitle("Simpson") +
-  scale_color_viridis_d(end = .8)+
-  ylim(0, 1) +
-  theme(legend.position = "none")
+summary(glm(di_summary, formula = skew_pp ~ avg_n * dat, family = binomial))
 
-gridExtra::grid.arrange(grobs = list(skew_summary_plot, simpson_summary_plot), nrow = 1)
+for(i in unique(di_summary$dat)) {
+  this_dat <- filter(di_summary, dat==i)
+  print(i)
+  print(summary(glm(skew_pp ~ avg_n, family = binomial,
+          data = this_dat)))
+}
 
 ```
-
-```{r s and n mapping, fig.width = 12, fig.height = 18}
-
-all_di <- filter(all_di, !singletons)
-
-skew_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = skew_percentile)) +
-  geom_point(alpha = .1, size = .5) +
-  geom_point(data = filter(all_di, nsamples >= 2000), alpha = .2) +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free", ncol = 2) + 
-  ggtitle("Skewness") +
-  scale_color_viridis_c(option = "plasma", end= .75)
-
-skew_s_n_maps
-
-simpson_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = simpson_percentile)) +
-  geom_point(alpha =  .1, size = .5) +
-  geom_point(data = filter(all_di, nsamples >= 2000), alpha = .2) +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free", ncol = 2)  + 
-  ggtitle("Simpson") +
-  scale_color_viridis_c(option = "plasma", end= .75, direction = -1)
-
-simpson_s_n_maps
-
-```
-
-The less extreme (low skew, high simpson) vectors appear vaguely collected in the lower right for Gentry and BBS.
-Those are the regions with relatively high N/S, aka low average abundance, aka a relatively small feasible set.
-
-Conversely, for MCDB and Misc, it almost looks like the very least skewed elements are way down at tiny abundances?
-
-Do percentiles scan with S/N?
-
-```{r avg abund}
-
-all_di <- mutate(all_di, avg_abund = n0/s0)
-
-skew_avgabund <- ggplot(data = all_di, aes(x = avg_abund, y = skew_percentile)) +
-  geom_point(alpha = .3) +
-  theme_bw() +
-  ggtitle("Skew") +
-  facet_wrap(vars(dat), scales = "free")
-
-skew_avgabund
-
-simpson_avgabund <- ggplot(data = all_di, aes(x = avg_abund, y = simpson_percentile)) +
-  geom_point(alpha = .3) +
-  theme_bw() +
-  ggtitle("Simpson") +
-  facet_wrap(vars(dat), scales = "free")
-
-simpson_avgabund
-
-```
-There is perhaps a constraint, but that might be because you rarely get v high average abundances.
-You seem to rarely get low skewness or high Simpson at high average abundance, which scans with the heatmaps.
-
-Do Simpson and skewness correspond?
-```{r do skew and simp correlate}
-
-ss_plot <- ggplot(data = all_di, aes(x= skew_percentile, y = simpson_percentile, color = dat)) +
-  geom_point(alpha = .1) +
-  scale_color_viridis_d(end = .8) +
-  theme_bw() +
-  ggtitle("Skew v Simp")
-
-ss_plot
-
-ss_facet_plot <- ss_plot +
-  facet_wrap(vars(dat))
-
-ss_facet_plot
-```
-
-There's a weak relationship between Simpson and skewness, but a lot of noise. They are not substitutable.
-
-                Why is Gentry so strangely bimodal? It's like a U, when all the others tend towards one end or the other.
-
-Why are BBS and mammals less frequently squished than Portal?
-
-Looking at range of skewness and Simpsons:
-
-```{r ranges}
-
-skew_range_hist <- ggplot(data = filter(all_di, nsamples > 2000), aes(x = skew_range, y = skew_percentile, color = dat)) +
-  geom_point(alpha = .2) +
-  geom_smooth(method = "lm", se =F) +
-  theme_bw() +
-  scale_color_viridis_d(end = .8) +
-  facet_wrap(vars(dat), scales = "free") + 
-  ggtitle("Skewness")
-
-skew_range_hist
-
-simpson_range_hist <- ggplot(data = filter(all_di, nsamples > 2000), aes(x = simpson_range, y = simpson_percentile, color = dat)) +
-  geom_point(alpha = .2) +
-  geom_smooth(method = "lm", se =F) +
-
-  theme_bw() +
-  scale_color_viridis_d(end = .8) +
-  facet_wrap(vars(dat), scales = "free") +
-  ggtitle("Simpson")
-
-simpson_range_hist
-
-```
-
-I added the ranges because I thought the percentiles might be constrained somewhat by the range of values represented in the feasible set.
-It doesn't look to me like there is a strong relationship between range and %ile.

### 2020-01-20 analysis/reports/kde_report.Rmd
try this on hpg

---
title: "KDE report"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

this_dataset <- "kde"

if(this_dataset == "misc_abund_short") {
  cache_loc = "miscabund"
} else if (this_dataset == "fia_short") {
  cache_loc = "fia" 
} else {
  cache_loc = this_dataset
}

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

all_di <- readd(all_di, cache = cache)

```
# This dataset is `r this_dataset`.

```{r make kde}
di <- filter(all_di, singletons == FALSE)

skew_kde <- data.frame(x = density(filter(di, source == "sampled")$skew)$x,
                       y = density(filter(di, source == "sampled")$skew)$y) %>%
  mutate(y = y / sum(y))

skewplot <- ggplot(data = skew_kde, aes(x = x, y = y)) +
  geom_point() +
  geom_vline(xintercept = filter(di, source == "observed")$skew[1]) +
  theme_bw()
skewplot

skewdensity <- skew_kde$y [ which.min(abs(skew_kde$x - filter(di, source == "observed")$skew[1]))]
skewdensity

simpson_kde <- data.frame(x = density(filter(di, source == "sampled")$simpson, from = 0, to = 1)$x,
                       y = density(filter(di, source == "sampled")$simpson, from = 0, to = 1)$y) %>%
  mutate(y = y / sum(y))

simpsonplot <- ggplot(data = simpson_kde, aes(x = x, y = y)) +
  geom_point() +
  geom_vline(xintercept = filter(di, source == "observed")$simpson[1]) +
  theme_bw()
simpsonplot

simpsondensity <- simpson_kde$y [ which.min(abs(simpson_kde$x - filter(di, source == "observed")$simpson[1]))]
simpsondensity
```

```{r cleanup}

DBI::dbDisconnect(db)
rm(cache)
```

### 2020-01-20 analysis/portal_manip_pipeline.R

@@ -53,8 +53,8 @@ if (interactive())
 
 ## Run the pipeline
 nodename <- Sys.info()["nodename"]
-#if(grepl("ufhpc", nodename)) {
-if(FALSE){
+if(grepl("ufhpc", nodename)) {
+#if(FALSE){
   print("I know I am on the HiPerGator!")
   library(clustermq)
   options(clustermq.scheduler = "slurm", clustermq.template = "slurm_clustermq.tmpl")

### 2020-01-20 analysis/reports/dat_report_template.Rmd
add fxn to assign manips to macd

@@
 
+```{r manip}
+
+if(this_dataset == "macdb") {
+  all_di_manip <- readd(all_di_manip, cache = cache)
+
+  manip_skew_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = skew_percentile, group = studyID)) +
+    geom_line() +
+    theme_bw()
+
+  manip_skew_plot
+
+  manip_simpson_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = simpson_percentile, group = studyID)) +
+    geom_line() +
+    theme_bw()
+
+  manip_simpson_plot
+
+}
+
+```
+
 ```{r cleanup}

### 2020-01-20 analysis/reports/dat_report_template.Rmd
set up to add portal manips

@@
 
-  manip_skew_plot
+  print(manip_skew_plot)
 
@@
 
-  manip_simpson_plot
+  print(manip_simpson_plot)
 
@@
 
+if(this_dataset == "portal_plants_manip") {
+  all_di_manip <- readd(all_di_manip, cache = cache)
+
+  manip_skew_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = skew_percentile)) +
+    geom_point() +
+    facet_wrap(vars(season, singletons)) +
+    theme_bw()
+
+  print(manip_skew_plot)
+
+  manip_simpson_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = simpson_percentile)) +
+    geom_point() +
+    facet_wrap(vars(season, singletons)) +
+    theme_bw()
+
+  print(manip_simpson_plot)
+}
 ```

### 2020-01-20 analysis/portal_manip_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "portal_plants_manip"
 
 sites_list <- list_sites("portal_plants_manip")
-ndraws = 2500
-#sites_list <- sites_list[1:10, ]
+ndraws = 25
+sites_list <- sites_list[1:2, ]
 set.seed(1977)
 
 all <- drake_plan(
@@ -33,7 +33,8 @@ all <- drake_plan(
   di_obs_s = target(dplyr::bind_rows(di_obs),
                     transform = combine(di_obs, .by = singletons)),
   all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
-  report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di_obs, is_template = TRUE, dat_name = !!datasets),
+  all_di_manip = target(assign_portal_manips(all_di_obs)),
+  report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di_manip, is_template = TRUE, dat_name = !!datasets),
                   trigger = trigger(condition = T),
                   hpc = F)
 )

### 2020-01-21 analysis/reports/dat_report_template.Rmd
switch to boxplot

--- 2020-01-20 analysis/reports/dat_report_template.Rmd
@@
 
+if(this_dataset == "portal_plants_manip") {
+  all_di_manip <- readd(all_di_manip, cache = cache)
+
+  manip_skew_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = skew_percentile)) +
+    geom_boxplot() +
+    facet_wrap(vars(season, singletons)) +
+    theme_bw()
+
+  print(manip_skew_plot)
+
+  manip_simpson_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = simpson_percentile)) +
+    geom_boxplot() +
+    facet_wrap(vars(season, singletons)) +
+    theme_bw()
+
+  print(manip_simpson_plot)
+}
 ```

### 2020-01-22 analysis/reports/regressions.Rmd
more regressions and plots

@@
 }
-```
 
-```{r histograms, fig.height = 6, fig.width =6}
-
-skewhists <- ggplot(data = all_di, aes(x = skew_percentile)) +
-  geom_histogram(binwidth = 5, alpha = .3, boundary = 0) +
-  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500), boundary = 0) +
-  theme_bw() +
-  facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
-  ggtitle("Skewness") +
-  geom_vline(xintercept = 95, color = "red")
-skewhists
-
-simpsonhists <- ggplot(data = all_di, aes(x = simpson_percentile)) +
-  geom_histogram(binwidth = 5, alpha = .3, boundary = 0) +
-  geom_histogram(binwidth = 5, data = filter(all_di, nsamples == 2500), boundary = 0) +
-  theme_bw() +
-  facet_grid(rows = vars(dat), cols = vars(singletons), scales = "free_y") +
-  ggtitle("Simpson") +
-  geom_vline(xintercept = 5, color = "red")
-
-simpsonhists
+di_summary <- all_di %>%
+  filter(nsamples >= 2000, !singletons) %>%
+  mutate(avg_n = n0 / s0,
+         skew_pp = skew_percentile / 100.01,
+         simp_pp = simpson_percentile/100.01)
 
@@
 
-Observations from these histograms:
+Filtering to nsamples >= 2000, not singletons.
 
-* FIA really struggles to get 2500 samples
-* Portal is the *most* concentrated of all the datasets.
-* Then MCDB and misc, then gentry, then bbs. FIA is hard to place but looks idiosyncratic.
-* Curious about how variation in %ile maps on to S and N, *particularly* for Gentry and BBS. 
-* Skewness is less extreme than Simpson (more density in the in-between). 
-* Singletons doesn't appear to be terrifically impactful. From now on filtering to *unaltered* vectors.
-* I think it's best to filter to at least 2000 samples.
+### Supposed correlates
 
-Some summary statistics:
+#### Average abundance (N/S)
 
-```{r summary plots}
+```{r avg n}
 
-di_summary <- all_di %>%
-  filter(nsamples >= 2000) %>%
-  mutate(avg_n = n0 / s0,
-         skew_pp = skew_percentile / 100,
-         simp_pp = simpson_percentile/100)
+avg_n_plot <- ggplot(data = di_summary, aes(x = avg_n)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free") +
+  theme_bw() +
+  ggtitle("Average abundance")
+print(avg_n_plot)
+
+avg_n_boxplot <- ggplot(data = di_summary, aes(x= dat, y = avg_n)) +
+  geom_boxplot() +
+  theme_bw() +
+  ggtitle("Average abundance")
+
+print(avg_n_boxplot)
+
+avg_n_boxplot_log <- ggplot(data = di_summary, aes(x= dat, y = log(avg_n))) +
+  geom_boxplot() +
+  theme_bw() +
+  ggtitle("Average abundance")
+
+print(avg_n_boxplot_log)
 ```
 
-### Avg abundance
-
-```{r avg abundance regression}
-
-avgn_skew <- ggplot(data = di_summary, aes(x = avg_n, y = skew_pp)) +
-  geom_point() +
-  stat_smooth(method = "glm",method.args = list(family = binomial)) + 
-  facet_wrap(vars(dat), scales = "free") +
+```{r means and sds}
+skew_mean_plot <- ggplot(data = di_summary, aes(x = dat, y = skew_mean)) +
+  geom_boxplot() +
+  theme_bw()
+skew_sd_plot <- ggplot(data = di_summary, aes(x = dat, y = skew_sd)) +
+  geom_boxplot() +
+  theme_bw()
+skew_m_sd_plot <- ggplot(data = di_summary, aes(x = skew_mean, y = skew_sd, color = dat)) +
+  geom_point(alpha = .2) +
   theme_bw()
 
-avgn_skew
+skew_mean_plot
+skew_sd_plot
+skew_m_sd_plot
 
-summary(glm(di_summary, formula = skew_pp ~ avg_n * dat, family = binomial))
+simpson_mean_plot <- ggplot(data = di_summary, aes(x = dat, y = simpson_mean)) +
+  geom_boxplot() +
+  theme_bw()
+simpson_sd_plot <- ggplot(data = di_summary, aes(x = dat, y = simpson_sd)) +
+  geom_boxplot() +
+  theme_bw()
+simpson_m_sd_plot <- ggplot(data = di_summary, aes(x = simpson_mean, y = simpson_sd, color = dat)) +
+  geom_point(alpha = .2) +
+  theme_bw()
 
-for(i in unique(di_summary$dat)) {
-  this_dat <- filter(di_summary, dat==i)
-  print(i)
-  print(summary(glm(skew_pp ~ avg_n, family = binomial,
-          data = this_dat)))
-}
+simpson_mean_plot
+simpson_sd_plot
+simpson_m_sd_plot
 
 ```
+
+The different datasets are on dramatically different scales of average abundance, although it looks like a lot of that is outliers in misc_abund.
+
+### Correlation plots
+
+#### Average abundance
+```{r avg n vis, fig.dim = c(8,8)}
+
+skew_avgn_plot <- ggplot(data = di_summary, aes(x = avg_n, y = skew_percentile)) +
+  geom_point(size = 1, alpha = .2) +
+  facet_wrap(vars(dat), scales = "free_x") +
+  theme_bw() +
+  ggtitle("Skew v Avg N")
+print(skew_avgn_plot)
+
+simpson_avgn_plot <- ggplot(data = di_summary, aes(x = avg_n, y = simpson_percentile)) +
+  geom_point(size = 1, alpha = .2) +
+  facet_wrap(vars(dat), scales = "free_x") +
+  theme_bw() +
+  ggtitle("Simpson v Avg N")
+print(simpson_avgn_plot)
+
+```
+
+#### Mean and sd
+
+```{r mean sd vis, fix.dim = c(8, 8)}
+
+skew_mean_plot <- ggplot(data = di_summary, aes(x = skew_mean, y = skew_percentile)) +
+  geom_point(size = 1, alpha = .2) +
+  facet_wrap(vars(dat), scales = "free") +
+  theme_bw() +
+  ggtitle("Skew v Mean skew")
+print(skew_mean_plot)
+
+skew_sd_plot <- ggplot(data = di_summary, aes(x = skew_sd, y = skew_percentile)) +
+  geom_point(size = 1, alpha = .2) +
+  facet_wrap(vars(dat), scales = "free") +
+  theme_bw() +
+  ggtitle("Skew v sd skew")
+print(skew_sd_plot)
+
+simpson_mean_plot <- ggplot(data = di_summary, aes(x = simpson_mean, y = simpson_percentile)) +
+  geom_point(size = 1, alpha = .2) +
+  facet_wrap(vars(dat), scales = "free") +
+  theme_bw() +
+  ggtitle("simpson v Mean simpson")
+print(simpson_mean_plot)
+
+simpson_sd_plot <- ggplot(data = di_summary, aes(x = simpson_sd, y = simpson_percentile)) +
+  geom_point(size = 1, alpha = .2) +
+  facet_wrap(vars(dat), scales = "free") +
+  theme_bw() +
+  ggtitle("simpson v sd simpson")
+print(simpson_sd_plot)
+
+```
+
+### Beta regression
+
+#### Average abundance
+
+```{r betareg avg n}
+library(betareg)
+
+di_summary$skew_pp[ which(di_summary$skew_pp == 0)] <- .00000001
+di_summary$simp_pp[ which(di_summary$simp_pp == 0)] <- .00000001
+
+avgn_br_skew <- betareg(skew_pp ~ avg_n + dat, data = di_summary)
+summary(avgn_br_skew)
+plot(avgn_br_skew)
+
+```

### 2020-02-04 analysis/reports/vetting.Rmd
some new analyses

---
title: "Shaking out the idiosyncracies"
output: 
  github_document
params:
  on_hpg: [FALSE]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

if(params$on_hpg) {

  all_di <- list() 
  datasets <- c("bbs", "fia_short", "gentry", "mcdb", "misc_abund_short", "portal_plants")

  #datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

  for(i in 1:length(datasets)) {

    this_dataset = datasets[i]
    if(this_dataset == "misc_abund_short") {
      cache_loc = "miscabund"
    } else if(this_dataset == "fia_short") {

      cache_loc = "fia"
    } else {
      cache_loc = this_dataset
    }

    ## Set up the cache and config
    db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
    cache <- storr::storr_dbi("datatable", "keystable", db)

    all_di[[i]] <- readd(all_di_obs, cache = cache)

    all_di[[i]] <- filter(all_di[[i]], source == "observed")

    this_dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
    sv <- get_statevars(this_dat)
    all_di[[i]] <- left_join(all_di[[i]], sv, by = c("sim", "site", "source", "singletons", "dat"))

    DBI::dbDisconnect(db)
    rm(cache)
    rm(db)
  }

  all_di <- bind_rows(all_di)

  write.csv(all_di, "all_di.csv", row.names = F)
} else {
  all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
}
```

## Number of draws in feasible set

For low values of S and N, we expect to get considerably fewer than 2500 unique draws from the feasible set. Small feasible sets present a couple of problems for this percentile approach:

- In the limit of only one or a handful of possible forms, it's absurd to try and draw meaning from the form of the SAD. In a community of 10 species and 11 individuals, the important thing to understand is not why the SAD is 2-1-1-1-1-1 but why the community has 10 species and 11 individuals. 
- Even when there are a few more possible forms, if there isn't much variation, the %ile statistic will be pretty coarse. 
- I expect the central tendency/dominance by a particular *form* to be weaker when there are fewer possible forms, period. 
- This one isn't necessarily a bug (and it applies to other aspects of S x N space), but I expect combinations of S and N that produce samples to have unusual feasible sets compared to most of S and N space. These are going to be communities with either very low S and N, period, or *very few* individuals relative to S. They will be forced to be more even than ones with more individuals.

It's not clear a priori what actual values of S and N will push us into small-community problems. Again, beyond the really small communities, it really depends on the ratio. Early on I just filtered out anything that gave fewer than 2000 unique draws. This has the advantage that we only end up comparing %ile values with reasonably comparable precision, but it might artificially exclude an important region on S*N space.

```{r draws v sn plots, fig.dim = c(8,8)}

ndraws_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
  geom_point(data = filter(all_di, nsamples >= 2000), color = "grey", alpha = .25) +
    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9)

ndraws_plot

ndraws_onlysmol_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9)

ndraws_onlysmol_plot
```

In these plots, the grey region is nsamples >= 2000. It looks like removing communities with nsamples < 2000 is basically filtering out N < about 100-150. For more nuance we could dip down into lower n for intermediate S (S between 5 and 50), and still be getting pretty good sampling?

Leaving it be for now.

## Percentile value vs. range of variation of FS

This is really hard to get traction on. S and N affect everything.

```{r percent v rov}

ggplot(data = filter(all_di, nsamples >= 2000), aes(x = simpson_sd, y =simpson_percentile, color = simpson_mean)) +
  geom_point(alpha = .05) +
  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)

ggplot(data = filter(all_di, nsamples >= 2000), aes(x = skew_sd, y =skew_percentile, color = skew_mean)) +
  geom_point(alpha = .05) +
  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)

```

## Where the datasets fall

```{r dataset space}
ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = dat)) + 
  geom_point(alpha = .2) +
  scale_color_viridis_d() +
  theme_bw()

ggplot(data = all_di, aes(x = nsamples)) +
  geom_histogram() +
  theme_bw()+
  facet_wrap(vars(dat), scales = "free_y") +
  geom_vline(xintercept = 2000)
```

The datasets overlap but do occupy broadly different regions of S*N space.

FIA, dramatically more than any other dataset, struggles to get even 2000 samples.

## Overall percentile results

```{r overall}

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw()

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw()

```

Effect of singletons

```{r singletons overall}

singletons_effect <- all_di %>%
  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile) %>%
  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples)) %>%
  mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE) %>%
  filter(nsamples_TRUE >= 2000, nsamples_FALSE >= 2000)

ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
  geom_point(alpha = .2) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
    geom_point(alpha = .2) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

```

Adding singletons makes skewness more skewed and simpson less even.

## Broken out by dataset

```{r dataset}

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw()  +
  facet_wrap(vars(dat), scales = "free_y")

```

Effect of singletons

```{r singletons dataset}

singletons_effect <- all_di %>%
  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile) %>%
  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples)) %>%
  mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE) %>%
  filter(nsamples_TRUE >= 2000, nsamples_FALSE >= 2000)

ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
  geom_point(alpha = .2) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
    geom_point(alpha = .2) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

```

# MACD

```{r load macd}
  cache_loc = "macdb"

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

all_di_macd <- readd(all_di_manip, cache = cache)

DBI::dbDisconnect(db)
rm(cache)
```

Nsamples

```{r macd overall}

ggplot(data = all_di_macd, aes(x = nsamples)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_vline(xintercept = 2000)

all_di_macd <- filter(all_di_macd, nsamples >= 2000)

ggplot(data = all_di_macd, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw()

ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw()
```

By treatment - overall

```{r macd trtmt overall}

ggplot(data = all_di_macd, aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(treatment), scales = "free_y")

ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(treatment), scales = "free_y")

```

** I AM REALLY NOT CONFIDENT IN THE DATA HANDLING HERE, NEED TO REVISIT WHEN SHARPER **

```{r macd ctrlcomp}

macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)

colnames(macd_comparisons) <- c("studyID", "control", "site")
macd_comparisons <- macd_comparisons %>%
  mutate(site = as.character(site), control = as.character(control))

cc_di <- all_di_macd %>%
  filter(singletons == FALSE, treatment == "comparison") %>%
  left_join(macd_comparisons, by = c("studyID", "site")) %>%
  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
  rename(comparison = site) %>%
 left_join(select(all_di_macd, skew_percentile, simpson_percentile, site, singletons, nsamples), by = c("control" = "site")) %>%
  distinct() %>%
  rename(comp_skew = skew_percentile.x, comp_simp = simpson_percentile.x,
         control_skew = skew_percentile.y, control_simp = simpson_percentile.y)

ggplot(data = cc_di, aes(x = comp_skew, y = control_skew)) +
  geom_point(alpha = .5) +
#  xlim(0, 100) +
 # ylim(0, 100) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = cc_di, aes(x = comp_simp, y = control_simp)) +
  geom_point(alpha = .5) +
 xlim(0, 100) +
 ylim(0, 100) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

```

### 2020-02-05 analysis/reports/vetting.Rmd
add portal plant manips

@@
 ```
+
+# Portal plant manips
+
+```{r load pp}
+  cache_loc = "portal_plants_manip"
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+
+all_di_p<- readd(all_di_manip, cache = cache)
+
+DBI::dbDisconnect(db)
+rm(cache)
+```
+
+Nsamples, singletons
+
+```{r pp overall}
+
+ggplot(data = all_di_p, aes(x = nsamples)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  geom_vline(xintercept = 2000)
+
+all_di_p <- filter(all_di_p, nsamples >= 2000)
+
+ggplot(data = all_di_p, aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw()
+
+ggplot(data = all_di_p, aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw()
+
+pp_singletons_effect <- all_di_p %>%
+  select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>%
+  tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile"))
+
+ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  theme_bw()
+
+ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  theme_bw()
+```
+
+By treatment, season
+
+```{r portal trtmt}
+ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(season, treatment), scales = "free_y")
+
+ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_wrap(vars(season))
+
+ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(season, treatment), scales = "free_y")
+
+ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_wrap(vars(season))
+```
+
+By year
+
+```{r plants year, fig.height = 25, fig.width = 5}
+
+ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_grid(rows = vars(year), cols = vars(season), scales = "free_y")
+ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_grid(rows = vars(year), cols = vars(season), scales = "free_y")
+```
+
+Trying median
+
+```{r pp median, fig.width = 12, fig.height = 12}
+
+pp_median <- all_di_p %>%
+  filter(singletons == F) %>%
+  group_by(season, year, treatment) %>%
+  summarize(skew_percentile = median(skew_percentile),
+            simpson_percentile = median(simpson_percentile)) %>%
+  ungroup() %>%
+  tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile))
+
+sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Skew Ctrl v Exclosure") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+   xlim(40, 100) +
+   ylim(40, 100)
+
+sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Skew Ctrl v Removal") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+   xlim(40, 100) +
+   ylim(40, 100)
+
+gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2)
+
+sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Simpson Ctrl v Exclosure") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+   xlim(0, 40) +
+   ylim(0, 40)
+
+sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Simpson Ctrl v Removal") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  xlim(0, 40) +
+  ylim(0, 40)
+
+gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2)
+```

### 2020-02-05 analysis/reports/vetting.Rmd
scaled histograms

@@
 ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
+  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
+  theme_bw() +
+  geom_hline(yintercept = .01, linetype = 3)
 
 ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
+  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
+  theme_bw() +
+    geom_hline(yintercept = .01, linetype = 3)
 
+sum(filter(all_di, nsamples >= 2000, singletons == F)$skew_percentile >= 95) / nrow(filter(all_di, nsamples >= 2000, singletons == F))
 ```
@@
 
+## S and N v percentiles
+
+```{r sn percentiles}
+
+ggplot(data = filter(all_di, singletons == FALSE), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .8)
+
+ggplot(data = filter(all_di, singletons == FALSE, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+  geom_point(alpha = .25) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .8)
+
+ggplot(data = filter(all_di, singletons == FALSE), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .8, direction = -1)
+
+ggplot(data = filter(all_di, singletons == FALSE, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .25) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .8, direction = -1)
+```
+
+Even when you get >2k samples, it looks to me like you get *less unusual* observed SADs in the relatively low N/S region, which is also the region I expect to be most even.
+
+```{r avg n percentile}
+
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = simpson_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+```
+
+You really don't get non-extreme percentiles in the high n/s region.
+
+These scatterplots are good for seeing where the variation is but not the density; there's a *lot* of points on top of each other down at 0/up at 100.
+
 # MACD
@@
 ggplot(data = all_di_macd, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
+   geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
+  theme_bw() +
+    geom_hline(yintercept = .01, linetype = 3)
 
 ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
+  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
+  theme_bw() +
+    geom_hline(yintercept = .01, linetype = 3)
 ```
@@
   theme_bw() +
-  facet_wrap(vars(treatment), scales = "free_y")
+  facet_wrap(vars(dat), scales = "free_y")
 
@@
 
-** I AM REALLY NOT CONFIDENT IN THE DATA HANDLING HERE, NEED TO REVISIT WHEN SHARPER **
+<!-- ** I AM REALLY NOT CONFIDENT IN THE DATA HANDLING HERE, NEED TO REVISIT WHEN SHARPER ** -->
 
-```{r macd ctrlcomp}
+<!-- ```{r macd ctrlcomp} -->
 
-macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)
+<!-- macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F) -->
 
-colnames(macd_comparisons) <- c("studyID", "control", "site")
-macd_comparisons <- macd_comparisons %>%
-  mutate(site = as.character(site), control = as.character(control))
+<!-- colnames(macd_comparisons) <- c("studyID", "control", "site") -->
+<!-- macd_comparisons <- macd_comparisons %>% -->
+<!--   mutate(site = as.character(site), control = as.character(control)) -->
 
-cc_di <- all_di_macd %>%
-  filter(singletons == FALSE, treatment == "comparison") %>%
-  left_join(macd_comparisons, by = c("studyID", "site")) %>%
-  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
-  rename(comparison = site) %>%
- left_join(select(all_di_macd, skew_percentile, simpson_percentile, site, singletons, nsamples), by = c("control" = "site")) %>%
-  distinct() %>%
-  rename(comp_skew = skew_percentile.x, comp_simp = simpson_percentile.x,
-         control_skew = skew_percentile.y, control_simp = simpson_percentile.y)
+<!-- cc_di <- all_di_macd %>% -->
+<!--   filter(singletons == FALSE, treatment == "comparison") %>% -->
+<!--   left_join(macd_comparisons, by = c("studyID", "site")) %>% -->
+<!--   select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>% -->
+<!--   rename(comparison = site) %>% -->
+<!--  left_join(select(all_di_macd, skew_percentile, simpson_percentile, site, singletons, nsamples), by = c("control" = "site")) %>% -->
+<!--   distinct() %>% -->
+<!--   rename(comp_skew = skew_percentile.x, comp_simp = simpson_percentile.x, -->
+<!--          control_skew = skew_percentile.y, control_simp = simpson_percentile.y) -->
 
-ggplot(data = cc_di, aes(x = comp_skew, y = control_skew)) +
-  geom_point(alpha = .5) +
-#  xlim(0, 100) +
- # ylim(0, 100) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
+<!-- ggplot(data = cc_di, aes(x = comp_skew, y = control_skew)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!-- #  xlim(0, 100) + -->
+<!--  # ylim(0, 100) + -->
+<!--   theme_bw() + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->
 
-ggplot(data = cc_di, aes(x = comp_simp, y = control_simp)) +
-  geom_point(alpha = .5) +
- xlim(0, 100) +
- ylim(0, 100) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
+<!-- ggplot(data = cc_di, aes(x = comp_simp, y = control_simp)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!--  xlim(0, 100) + -->
+<!--  ylim(0, 100) + -->
+<!--   theme_bw() + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->
 
-```
+<!-- ``` -->
 
@@
 ggplot(data = all_di_p, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
+  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
+  theme_bw() +
+    geom_hline(yintercept = .01, linetype = 3)
 
 ggplot(data = all_di_p, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
+   geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
+  theme_bw() +
+    geom_hline(yintercept = .01, linetype = 3)
 
@@
   theme_bw() +
-  facet_wrap(vars(season, treatment), scales = "free_y")
+  facet_wrap(vars(dat), scales = "free_y")
 

### 2020-02-05 analysis/reports/vetting.Rmd
add analysis text

@@
 
-```{r draws v sn plots, fig.dim = c(8,8)}
+```{r draws v sn plots, fig.dim = c(5,5)}
 
-ndraws_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
   geom_point(data = filter(all_di, nsamples >= 2000), color = "grey", alpha = .25) +
@@
 
-ndraws_plot
-
-ndraws_onlysmol_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
+ ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
     geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
@@
 
-ndraws_onlysmol_plot
 ```
@@
 
-```{r percent v rov}
+```{r Simpson rov, fig.dim=c(4,4)}
 
-ggplot(data = filter(all_di, nsamples >= 2000), aes(x = simpson_sd, y =simpson_percentile, color = simpson_mean)) +
-  geom_point(alpha = .05) +
-  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_mean)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9) +
+  theme(legend.position = "none") +
+  ggtitle("Simpson mean")
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_sd)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)+
+  theme(legend.position = "none") +
+  ggtitle("Simpson sd")
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_range)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)+
+  theme(legend.position = "none") +
+  ggtitle("Simpson range")
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
+  theme(legend.position = "none") +
+  ggtitle("Simpson percentile")
 
-ggplot(data = filter(all_di, nsamples >= 2000), aes(x = skew_sd, y =skew_percentile, color = skew_mean)) +
-  geom_point(alpha = .05) +
-  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = simpson_mean)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9) +
+  theme(legend.position = "none") +
+  ggtitle("Simpson mean")
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = simpson_sd)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)+
+  theme(legend.position = "none") +
+  ggtitle("Simpson sd")
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = simpson_range)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)+
+  theme(legend.position = "none") +
+  ggtitle("Simpson range")
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
+  theme(legend.position = "none") +
+  ggtitle("Simpson percentile")
 
@@
 
+So for Simpson's, the mean, sd, and range of values within the feasible set all clearly vary with S and N.
+There seems to be an edge situation with the percentiles.
+The really high values are all out along the arm and, to a lesser extent, where N/S is relatively small.
+This is *not* a region of pronounced variation in the FS characteristics.
+Also, there is variation that clearly does not map on to the gradients in the FS characteristics.
+
+```{r skew rov, fig.dim=c(4,4)}
+
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_mean)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+  theme(legend.position = "none") +
+  ggtitle("Skew mean")
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_sd)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
+  theme(legend.position = "none") +
+  ggtitle("Skew sd")
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_range)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
+  theme(legend.position = "none") +
+  ggtitle("Skew range")
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)+
+  theme(legend.position = "none") +
+  ggtitle("Skew percentile")
+
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = skew_mean)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+  theme(legend.position = "none") +
+  ggtitle("Skew mean")
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = skew_sd)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
+  theme(legend.position = "none") +
+  ggtitle("Skew sd")
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = skew_range)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
+  theme(legend.position = "none") +
+  ggtitle("Skew range")
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+  geom_point(alpha = .07) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)+
+  theme(legend.position = "none") +
+  ggtitle("Skew percentile")
+
+```
+
+There are similar, if less strong, gradients in skewness over the range of S and N; it's particularly low up the low N/S arm.
+The percentile values are *not* as different in that arm than the rest of the space (unlike with Simpson's).
+The variation in skewness percentile doesn't appear to track the gradients in the characteristics of the feasible set.
+Maybe it does a little?
+But no argument that there's a lot of variation over and above.
+
+I feel like it might be *good* to find some way to test these statements quantitatively, but it's very tricky. Absolutely everything depends on S and N and moves in weird nonlinear ways.
+
+```{r avg n percentile}
+
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = simpson_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+```
+
+You really don't get non-extreme percentiles in the high n/s region.
+
+These scatterplots are good for seeing where the variation is but not the density; there's a *lot* of points on top of each other down at 0/up at 100.
 ## Where the datasets fall
@@
   scale_color_viridis_d() +
-  theme_bw()
+  theme_bw() +
+  geom_point(data = filter(all_di, dat == "I don't exist!")) # for a legend with alpha = 1
 
@@
 
-The datasets overlap but do occupy broadly different regions of S*N space.
+The datasets overlap but do occupy broadly different regions of S*N space. The arm - which is the weirdest region of the percentile values - is, unfortunately, 100% one dataset (Gentry).
+
+For the vast majority of S*N space here, I don't think we can really use dataset as a predictor of percentile, because of the way they occupy different parts of what we know to be a very important range of variation.
+
+We *could* narrow in on the region of maximum overlap/minimum variation and make comparison based on the sites only within that.
 
@@
 
-sum(filter(all_di, nsamples >= 2000, singletons == F)$skew_percentile >= 95) / nrow(filter(all_di, nsamples >= 2000, singletons == F))
 ```
+
+Here, the dotted lines mark the 1%; at random, percentile values should be uniformly distributed with 1% per bin on these histograms.
+
+Both Simpson's and skewness are disproportiately in the extremes: from about the 75th percentile on up for skewness, and maybe the 10th percentile and below for evenness.
+
+It's not ubiquitous!
+Often things are unremarkable compared to the feasible set.
+That said, *more often than we'd expect*, real distributions are highly skewed/highly uneven compared to their feasible sets.
 
@@
 
-Adding singletons makes skewness more skewed and simpson less even.
+The rarefaction-inflated datasets are strongly // the raw vectors.
+They have more extreme skewness and evenness values, relative to their feasible sets, than the raw vectors.
+This is almost always true for evenness, with a little more noise in the skewness signal.
+But either way, very strong.
 
@@
 
-```{r dataset}
+```{r dataset, fig.dim = c(10,10)}
 
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
-   geom_histogram(bins = 100) +
+make_dat_hist <- function(datname, varname, data) {
+
+  if(varname == "skew") {
+
+  dat_hist <- ggplot(data = filter(data, nsamples >= 2000, singletons == FALSE, dat == datname), aes(x = skew_percentile)) 
+  } else if (varname == "simpson") {
+       dat_hist <- ggplot(data = filter(data, nsamples >= 2000, singletons == FALSE, dat == datname), aes(x = simpson_percentile)) 
+    }
+
+  dat_hist <- dat_hist +
+ geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
   theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y")
+  geom_hline(yintercept = .01, linetype = 3) +
+    ggtitle(paste0(datname, ": ", varname))
 
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
-   geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y")
+  return(dat_hist)
+}
+
+simp_hists <- lapply(as.list(unique(all_di$dat)), FUN = make_dat_hist, varname = "simpson", data = all_di)
+
+skew_hists <- lapply(as.list(unique(all_di$dat)), FUN = make_dat_hist, varname = "skew", data = all_di)
+
+gridExtra::grid.arrange(grobs = simp_hists)
+
+gridExtra::grid.arrange(grobs = skew_hists)
 
 ```
+
+Evennes is consistently more concentrated in the extremes than skewness.
+
+Gentry has a weird U going on, where it has a lot of weirdly *low*/*high* values.
+All the others are concentrated as low (evenness) or high (skew).
+BBS and FIA have the most that are in the intermediate zone.
 
@@
 
-## S and N v percentiles
-
-```{r sn percentiles}
-
-ggplot(data = filter(all_di, singletons == FALSE), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .8)
-
-ggplot(data = filter(all_di, singletons == FALSE, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
-  geom_point(alpha = .25) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .8)
-
-ggplot(data = filter(all_di, singletons == FALSE), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .8, direction = -1)
-
-ggplot(data = filter(all_di, singletons == FALSE, nsamples >= 2000), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
-  geom_point(alpha = .25) +
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .8, direction = -1)
-```
-
-Even when you get >2k samples, it looks to me like you get *less unusual* observed SADs in the relatively low N/S region, which is also the region I expect to be most even.
-
-```{r avg n percentile}
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = skew_percentile)) +
-  geom_point(alpha = .1) +
-  theme_bw()
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = simpson_percentile)) +
-  geom_point(alpha = .1) +
-  theme_bw()
-```
-
-You really don't get non-extreme percentiles in the high n/s region.
-
-These scatterplots are good for seeing where the variation is but not the density; there's a *lot* of points on top of each other down at 0/up at 100.
+There's some fuzz, most pronouncedly for BBS and FIA. Those are also the ones with 1) the most points and 2) the most fuzz/uniform-distributed percentile values.
 

### 2020-02-06 analysis/reports/arm.Rmd
render me on hpgnder on hpg

---
title: "Investigating the arm + Gentry U"
output: 
  github_document
params:
  on_hpg: [FALSE]
---

Gentry has an interesting "arm" up where the values get weird, and I'm wondering if that's where the U-shape in the percentile value histograms comes from.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

if(params$on_hpg) {

  all_di <- list() 
  datasets <- c("bbs", "fia_short", "gentry", "mcdb", "misc_abund_short", "portal_plants")

  #datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")

  for(i in 1:length(datasets)) {

    this_dataset = datasets[i]
    if(this_dataset == "misc_abund_short") {
      cache_loc = "miscabund"
    } else if(this_dataset == "fia_short") {

      cache_loc = "fia"
    } else {
      cache_loc = this_dataset
    }

    ## Set up the cache and config
    db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
    cache <- storr::storr_dbi("datatable", "keystable", db)

    all_di[[i]] <- readd(all_di_obs, cache = cache)

    all_di[[i]] <- filter(all_di[[i]], source == "observed")

    this_dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
    sv <- get_statevars(this_dat)
    all_di[[i]] <- left_join(all_di[[i]], sv, by = c("sim", "site", "source", "singletons", "dat"))

    DBI::dbDisconnect(db)
    rm(cache)
    rm(db)
  }

  all_di <- bind_rows(all_di)

  write.csv(all_di, "all_di.csv", row.names = F)
} else {
  all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
}

all_di <- filter(all_di, dat == "gentry")
```

## Number of draws in feasible set

```{r draws v sn plots, fig.dim = c(5,5)}

ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
    geom_point(alpha = .5) + 
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9)

ggplot(data=all_di, aes(x = log(s0), y = log(n0), color = log(n0/s0))) +    geom_point(alpha = .5) + 
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9)

```

The "arm" is well-sampled, but note that log(n0/s0) approaches zero. I'd call anything that's really purple - log(n0/s0) <= 1, let's say - "arm" territory. That's where n0/s0 is down below 2.5:1-ish.

## Percentile value vs. range of variation of FS

```{r Simpson rov, fig.dim=c(4,4)}

ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_mean)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9) +
  theme(legend.position = "top") +
  ggtitle("Simpson mean")
ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_sd)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9)+
  theme(legend.position = "top") +
  ggtitle("Simpson sd")
ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_range)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9)+
  theme(legend.position = "top") +
  ggtitle("Simpson range")
ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
  theme(legend.position = "top") +
  ggtitle("Simpson percentile")

```

```{r skew rov, fig.dim=c(4,4)}

ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_mean)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
  theme(legend.position = "top") +
  ggtitle("Skew mean")
ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_sd)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
  theme(legend.position = "top") +
  ggtitle("Skew sd")
ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_range)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
  theme(legend.position = "top") +
  ggtitle("Skew range")
ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = skew_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9)+
  theme(legend.position = "top") +
  ggtitle("Skew percentile")

```
All of the FS properties get weird up the arm.

Simpson gets high, the sd gets down to almost zero, and the range drops. Skew gets - bizarrely? - *large*. (But absolute skewness values are...slippery and counterintuitive).

The super high evenness percentiles are all up the arm. There's more fuzz in skewness, but most of the low skewness values are also up the arm.

```{r avg n percentile}

ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = skew_percentile)) +
  geom_point(alpha = .5) +
  theme_bw()

ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = simpson_percentile)) +
  geom_point(alpha = .5) +
  theme_bw()
```

There is a constraining-ish envelope where the low skew values are all at low average abundance (log n0/s0 < ~1.6) and the high evenness values are similarly collected (log n0/s0 < ~1.7, mostly < 1).

## Percentile results

```{r overall}

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
  theme_bw() +
  geom_hline(yintercept = .01, linetype = 3)

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
  theme_bw() +
    geom_hline(yintercept = .01, linetype = 3)

```

Let's exclude log n0/s0 < 1.5.

```{r no arm}

all_di <- all_di %>%
  mutate(avgn = log(n0/s0))

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, avgn >= 1.5), aes(x = skew_percentile)) +
  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
  theme_bw() +
  geom_hline(yintercept = .01, linetype = 3)

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, avgn >= 1.5), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
  theme_bw() +
    geom_hline(yintercept = .01, linetype = 3)
```

Well that clears THAT up.

Effect of singletons

```{r singletons overall}

singletons_effect <- all_di %>%
  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile) %>%
  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples)) %>%
  mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE) %>%
  filter(nsamples_TRUE >= 2000, nsamples_FALSE >= 2000)

ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
  geom_point(alpha = .5) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
    geom_point(alpha = .5) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

```

The rarefaction-inflated datasets are strongly // the raw vectors. They have more extreme skewness and evenness values, relative to their feasible sets, than the raw vectors. This is almost always true for evenness, with a little more noise in the skewness signal. But either way, very strong.

Just out of curiousity, removing the arm...

```{r singletons no arm}

singletons_effect_noarm <- all_di %>%
  select(dat, nsamples, site, avgn, singletons, skew_percentile, simpson_percentile) %>%
  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples, avgn)) %>%
  mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE) %>%
  filter(nsamples_TRUE >= 2000, nsamples_FALSE >= 2000,
         avgn_TRUE >= 1.5, avgn_FALSE >= 1.5)

ggplot(data = singletons_effect_noarm, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
  geom_point(alpha = .5) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(data = singletons_effect_noarm, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
    geom_point(alpha = .5) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

```

Huh. Those are tidier, too.

## FS in the arm

Let's look at what the actual feasible sets look like up the arm vs. elsewhere.

```{r fs in the arm}
if(params$on_hpg) {

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-gentry.sqlite"))
cache <- storr::storr_dbi("datatable", "keystable", db)

} else {
## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), "/Users/renatadiaz/Desktop/caches_good/drake-cache-gentry.sqlite")
cache <- storr::storr_dbi("datatable", "keystable", db)
}
loadd(fs_35_FALSE, cache = cache)

ggplot(data = filter(fs_35_FALSE, source == "sampled"), aes(x = rank, y = abund, group = sim)) +
  geom_line(alpha = .05) +
  geom_line(data = filter(fs_35_FALSE, source == "observed"), alpha = 1, color = "green") +
  theme_bw()

loadd(fs_184_FALSE, cache = cache)

ggplot(data = filter(fs_184_FALSE, source == "sampled"), aes(x = rank, y = abund, group = sim)) +
  geom_line(alpha = .05) +
  geom_line(data = filter(fs_184_FALSE, source == "observed"), alpha = 1, color = "green") +
  theme_bw()

max(fs_184_FALSE$sim)
DBI::dbDisconnect(db)
rm(cache)
```

### 2020-02-07 analysis/reports/singletons.Rmd
singletons attribution

--- 2020-02-05 analysis/reports/vetting.Rmd
@@
 ---
-title: "Shaking out the idiosyncracies"
+title: "Singletons"
 output: 
@@
 
-## Number of draws in feasible set
-
-For low values of S and N, we expect to get considerably fewer than 2500 unique draws from the feasible set. Small feasible sets present a couple of problems for this percentile approach:
-
-- In the limit of only one or a handful of possible forms, it's absurd to try and draw meaning from the form of the SAD.
-In a community of 10 species and 11 individuals, the important thing to understand is not why the SAD is 2-1-1-1-1-1 but why the community has 10 species and 11 individuals.
-- Even when there are a few more possible forms, if there isn't much variation, the %ile statistic will be pretty coarse. 
-- I expect the central tendency/dominance by a particular *form* to be weaker when there are fewer possible forms, period. 
-- This one isn't necessarily a bug (and it applies to other aspects of S x N space), but I expect combinations of S and N that produce samples to have unusual feasible sets compared to most of S and N space.
-These are going to be communities with either very low S and N, period, or *very few* individuals relative to S.
-They will be forced to be more even than ones with more individuals.
-
-It's not clear a priori what actual values of S and N will push us into small-community problems.
-Again, beyond the really small communities, it really depends on the ratio.
-Early on I just filtered out anything that gave fewer than 2000 unique draws.
-This has the advantage that we only end up comparing %ile values with reasonably comparable precision, but it might artificially exclude an important region on S*N space.
-
-```{r draws v sn plots, fig.dim = c(8,8)}
-
-ndraws_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
-  geom_point(data = filter(all_di, nsamples >= 2000), color = "grey", alpha = .25) +
-    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .9)
-
-ndraws_plot
-
-ndraws_onlysmol_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
-    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .9)
-
-ndraws_onlysmol_plot
-```
-
-In these plots, the grey region is nsamples >= 2000.
-It looks like removing communities with nsamples < 2000 is basically filtering out N < about 100-150.
-For more nuance we could dip down into lower n for intermediate S (S between 5 and 50), and still be getting pretty good sampling?
-
-Leaving it be for now.
-
-## Percentile value vs. range of variation of FS
-
-This is really hard to get traction on. S and N affect everything.
-
-```{r percent v rov}
-
-ggplot(data = filter(all_di, nsamples >= 2000), aes(x = simpson_sd, y =simpson_percentile, color = simpson_mean)) +
-  geom_point(alpha = .05) +
-  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)
-
-ggplot(data = filter(all_di, nsamples >= 2000), aes(x = skew_sd, y =skew_percentile, color = skew_mean)) +
-  geom_point(alpha = .05) +
-  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)
-
-```
-
-## Where the datasets fall
-
-```{r dataset space}
-ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = dat)) + 
-  geom_point(alpha = .2) +
-  scale_color_viridis_d() +
-  theme_bw()
-
-ggplot(data = all_di, aes(x = nsamples)) +
-  geom_histogram() +
-  theme_bw()+
-  facet_wrap(vars(dat), scales = "free_y") +
-  geom_vline(xintercept = 2000)
-```
-
-The datasets overlap but do occupy broadly different regions of S*N space.
-
-FIA, dramatically more than any other dataset, struggles to get even 2000 samples.
-
-## Overall percentile results
-
-```{r overall}
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-```
-
-Effect of singletons
+# Effect of singletons
 
@@
 
-```{r dataset}
+```{r dataset, fig.dim = c(10,10)}
 
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
+make_dat_hist <- function(datname, varname, data) {
+
+  if(varname == "skew") {
+
+  dat_hist <- ggplot(data = filter(data, nsamples >= 2000, singletons == FALSE, dat == datname), aes(x = skew_percentile)) 
+  } else if (varname == "simpson") {
+       dat_hist <- ggplot(data = filter(data, nsamples >= 2000, singletons == FALSE, dat == datname), aes(x = simpson_percentile)) 
+    }
+
+  dat_hist <- dat_hist +
+ geom_histogram(bins = 100, aes(y = stat(count / sum(count)))) +
   theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y")
+  geom_hline(yintercept = .01, linetype = 3) +
+    ggtitle(paste0(datname, ": ", varname))
 
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()  +
-  facet_wrap(vars(dat), scales = "free_y")
+  return(dat_hist)
+}
+
+simp_hists <- lapply(as.list(unique(all_di$dat)), FUN = make_dat_hist, varname = "simpson", data = all_di)
+
+skew_hists <- lapply(as.list(unique(all_di$dat)), FUN = make_dat_hist, varname = "skew", data = all_di)
+
+gridExtra::grid.arrange(grobs = simp_hists)
+
+gridExtra::grid.arrange(grobs = skew_hists)
 
 ```
+
+Evennes is consistently more concentrated in the extremes than skewness.
+
+Gentry has a weird U going on, where it has a lot of weirdly *low*/*high* values.
+All the others are concentrated as low (evenness) or high (skew).
+BBS and FIA have the most that are in the intermediate zone.
 
@@
 singletons_effect <- all_di %>%
-  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile) %>%
-  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples)) %>%
+  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile, s0, n0) %>%
+  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples, s0, n0)) %>%
   mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
-         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE) %>%
+         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE,
+         nadded = s0_TRUE - s0_FALSE,
+         propadded = (s0_TRUE - s0_FALSE) / s0_FALSE) %>%
   filter(nsamples_TRUE >= 2000, nsamples_FALSE >= 2000)
 
-ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
+ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE, color = log(nadded))) +
   geom_point(alpha = .2) +
@@
   geom_abline(intercept = 0, slope = 1, color = "green") +
-  facet_wrap(vars(dat))
+  facet_wrap(vars(dat)) +
+  scale_color_viridis_c(option = "plasma")
 
-ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
+ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE, color = log(nadded))) +
     geom_point(alpha = .2) +
@@
   geom_abline(intercept = 0, slope = 1, color = "green") +
-  facet_wrap(vars(dat))
+  facet_wrap(vars(dat))+
+  scale_color_viridis_c(option = "plasma")
 
@@
 
-# MACD
+There's some fuzz, most pronouncedly for BBS and FIA. Those are also the ones with 1) the most points and 2) the most fuzz/uniform-distributed percentile values.
 
-```{r load macd}
-  cache_loc = "macdb"
+```{r sv singletons}
 
-## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
-cache <- storr::storr_dbi("datatable", "keystable", db)
-
-all_di_macd <- readd(all_di_manip, cache = cache)
-
-DBI::dbDisconnect(db)
-rm(cache)
-```
-
-Nsamples
-
-```{r macd overall}
-
-ggplot(data = all_di_macd, aes(x = nsamples)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  geom_vline(xintercept = 2000)
-
-all_di_macd <- filter(all_di_macd, nsamples >= 2000)
-
-ggplot(data = all_di_macd, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
+ggplot(data = singletons_effect, aes(x = dat, y = nadded)) +
+  geom_boxplot() +
   theme_bw()
 
-ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
+ggplot(data = singletons_effect, aes(x = dat, y = propadded)) +
+  geom_boxplot() +
   theme_bw()
-```
 
-By treatment - overall
+ggplot(data = singletons_effect, aes(x = log(s0_FALSE), y= log(n0_FALSE), color = log(nadded))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+  theme(legend.position = "top")
 
-```{r macd trtmt overall}
+ggplot(data = singletons_effect, aes(x = log(s0_FALSE), y= log(n0_FALSE), color = log(propadded))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+  theme(legend.position = "top")
 
-ggplot(data = all_di_macd, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
+ggplot(data = filter(singletons_effect, skewdiff < 0), aes(x = log(s0_FALSE), y= log(n0_FALSE), color = skewdiff)) +
+  geom_point(data = singletons_effect, alpha = .07, color = "grey")+
+    geom_point(alpha = .5) + 
+facet_wrap(vars(dat), scales = "free") +
   theme_bw() +
-  facet_wrap(vars(treatment), scales = "free_y")
-
-ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(treatment), scales = "free_y")
+  scale_color_viridis_c(option = "plasma", end = .9, direction = 1) +
+  theme(legend.position = "top")
 
@@
 
-** I AM REALLY NOT CONFIDENT IN THE DATA HANDLING HERE, NEED TO REVISIT WHEN SHARPER **
+Gentry gets a bunch of species added (600?!?!?!?). Otherwise, the number added and the effect doesn't map clearly onto S and N.
 
-```{r macd ctrlcomp}
+Gentry makes things hard to look at and is not the focus here, so I'm removing it. 
+```{r effect x nadded}
 
-macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)
+ggplot(data = singletons_effect, aes(x = nadded, y = skewdiff)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = 'free_x')
 
-colnames(macd_comparisons) <- c("studyID", "control", "site")
-macd_comparisons <- macd_comparisons %>%
-  mutate(site = as.character(site), control = as.character(control))
+ggplot(data = singletons_effect, aes(x = propadded, y = skewdiff)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+    facet_wrap(vars(dat), scales = 'free_x')
 
-cc_di <- all_di_macd %>%
-  filter(singletons == FALSE, treatment == "comparison") %>%
-  left_join(macd_comparisons, by = c("studyID", "site")) %>%
-  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
-  rename(comparison = site) %>%
- left_join(select(all_di_macd, skew_percentile, simpson_percentile, site, singletons, nsamples), by = c("control" = "site")) %>%
-  distinct() %>%
-  rename(comp_skew = skew_percentile.x, comp_simp = simpson_percentile.x,
-         control_skew = skew_percentile.y, control_simp = simpson_percentile.y)
+ggplot(data = singletons_effect, aes(x = nadded, y = simpdiff)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = 'free_x')
 
-ggplot(data = cc_di, aes(x = comp_skew, y = control_skew)) +
-  geom_point(alpha = .5) +
-#  xlim(0, 100) +
- # ylim(0, 100) +
+ggplot(data = singletons_effect, aes(x = propadded, y = simpdiff)) +
+  geom_point(alpha = .1) +
   theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
-
-ggplot(data = cc_di, aes(x = comp_simp, y = control_simp)) +
-  geom_point(alpha = .5) +
- xlim(0, 100) +
- ylim(0, 100) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
+    facet_wrap(vars(dat), scales = 'free_x')
 
@@
 
-# Portal plant manips
+Compared to original skew
 
-```{r load pp}
-  cache_loc = "portal_plants_manip"
+```{r skewFALSE}
 
-## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
-cache <- storr::storr_dbi("datatable", "keystable", db)
+ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skewdiff)) +
+   geom_point(alpha = .1) +
+  theme_bw() +
+  geom_hline(yintercept = 0, color = "red") +
+  geom_smooth(method = "lm", se = F)
 
-all_di_p<- readd(all_di_manip, cache = cache)
+ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skewdiff)) +
+   geom_point(alpha = .1) +
+  theme_bw() +
+  geom_hline(yintercept = 0, color = "red") +
+  geom_smooth(method = "lm", se = F) +
+  facet_wrap(vars(dat), scales = "free")
 
-DBI::dbDisconnect(db)
-rm(cache)
 ```
-
-Nsamples, singletons
-
-```{r pp overall}
-
-ggplot(data = all_di_p, aes(x = nsamples)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  geom_vline(xintercept = 2000)
-
-all_di_p <- filter(all_di_p, nsamples >= 2000)
-
-ggplot(data = all_di_p, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-ggplot(data = all_di_p, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-pp_singletons_effect <- all_di_p %>%
-  select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>%
-  tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile"))
-
-ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) +
-  geom_point(alpha = .1) +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  theme_bw()
-
-ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) +
-  geom_point(alpha = .1) +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  theme_bw()
-```
-
-By treatment, season
-
-```{r portal trtmt}
-ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(season, treatment), scales = "free_y")
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(season))
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(season, treatment), scales = "free_y")
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(season))
-```
-
-By year
-
-```{r plants year, fig.height = 25, fig.width = 5}
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_grid(rows = vars(year), cols = vars(season), scales = "free_y")
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_grid(rows = vars(year), cols = vars(season), scales = "free_y")
-```
-
-Trying median
-
-```{r pp median, fig.width = 12, fig.height = 12}
-
-pp_median <- all_di_p %>%
-  filter(singletons == F) %>%
-  group_by(season, year, treatment) %>%
-  summarize(skew_percentile = median(skew_percentile),
-            simpson_percentile = median(simpson_percentile)) %>%
-  ungroup() %>%
-  tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile))
-
-sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Skew Ctrl v Exclosure") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-   xlim(40, 100) +
-   ylim(40, 100)
-
-sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Skew Ctrl v Removal") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-   xlim(40, 100) +
-   ylim(40, 100)
-
-gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2)
-
-sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Simpson Ctrl v Exclosure") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-   xlim(0, 40) +
-   ylim(0, 40)
-
-sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Simpson Ctrl v Removal") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  xlim(0, 40) +
-  ylim(0, 40)
-
-gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2)
-```

### 2020-02-07 analysis/reports/singletons.Rmd
testing one idea

@@
 ```
+
+```{r remove high skew}
+
+ggplot(data = filter(singletons_effect), aes(x = skewdiff)) +
+  geom_histogram() +
+  theme_bw()
+ggplot(data = filter(singletons_effect, skew_percentile_FALSE <= 75), aes(x = skewdiff)) +
+  geom_histogram() +
+    geom_histogram(data = singletons_effect, alpha = .2) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y") +
+  geom_vline(xintercept = 0)
+
+```
+With the possible exception of gentry, removing the highly skewed sites does not recenter the difference on 0.
+So the reason bbs and fia have so many down below 0 is not "shifting below zero is only possible if skew starts out lowish; bbs and fia are the only ones with a lot of intermediate starting skew values; if we constrain the others to only their intermediate starting skew values, they too will have proportionally lots below zero".

### 2020-02-07 analysis/reports/overlap.Rmd
rough overlap comparison

--- 2020-02-05 analysis/reports/vetting.Rmd
@@
 ---
-title: "Shaking out the idiosyncracies"
+title: "Comparing within overlapping s0-n0 space"
 output: 
@@
 
-## Number of draws in feasible set
-
-For low values of S and N, we expect to get considerably fewer than 2500 unique draws from the feasible set. Small feasible sets present a couple of problems for this percentile approach:
-
-- In the limit of only one or a handful of possible forms, it's absurd to try and draw meaning from the form of the SAD.
-In a community of 10 species and 11 individuals, the important thing to understand is not why the SAD is 2-1-1-1-1-1 but why the community has 10 species and 11 individuals.
-- Even when there are a few more possible forms, if there isn't much variation, the %ile statistic will be pretty coarse. 
-- I expect the central tendency/dominance by a particular *form* to be weaker when there are fewer possible forms, period. 
-- This one isn't necessarily a bug (and it applies to other aspects of S x N space), but I expect combinations of S and N that produce samples to have unusual feasible sets compared to most of S and N space.
-These are going to be communities with either very low S and N, period, or *very few* individuals relative to S.
-They will be forced to be more even than ones with more individuals.
-
-It's not clear a priori what actual values of S and N will push us into small-community problems.
-Again, beyond the really small communities, it really depends on the ratio.
-Early on I just filtered out anything that gave fewer than 2000 unique draws.
-This has the advantage that we only end up comparing %ile values with reasonably comparable precision, but it might artificially exclude an important region on S*N space.
-
-```{r draws v sn plots, fig.dim = c(8,8)}
-
-ndraws_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
-  geom_point(data = filter(all_di, nsamples >= 2000), color = "grey", alpha = .25) +
-    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .9)
-
-ndraws_plot
-
-ndraws_onlysmol_plot <- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
-    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
-  theme_bw() +
-  scale_color_viridis_c(option = "plasma", end = .9)
-
-ndraws_onlysmol_plot
-```
-
-In these plots, the grey region is nsamples >= 2000.
-It looks like removing communities with nsamples < 2000 is basically filtering out N < about 100-150.
-For more nuance we could dip down into lower n for intermediate S (S between 5 and 50), and still be getting pretty good sampling?
-
-Leaving it be for now.
-
-## Percentile value vs. range of variation of FS
-
-This is really hard to get traction on. S and N affect everything.
-
-```{r percent v rov}
-
-ggplot(data = filter(all_di, nsamples >= 2000), aes(x = simpson_sd, y =simpson_percentile, color = simpson_mean)) +
-  geom_point(alpha = .05) +
-  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)
-
-ggplot(data = filter(all_di, nsamples >= 2000), aes(x = skew_sd, y =skew_percentile, color = skew_mean)) +
-  geom_point(alpha = .05) +
-  theme_bw() +  scale_color_viridis_c(option = "plasma", end = .9)
-
-```
-
 ## Where the datasets fall
@@
   scale_color_viridis_d() +
-  theme_bw()
+  theme_bw() +
+  geom_point(data = filter(all_di, dat == "I don't exist!")) # for a legend with alpha = 1
 
-ggplot(data = all_di, aes(x = nsamples)) +
-  geom_histogram() +
-  theme_bw()+
-  facet_wrap(vars(dat), scales = "free_y") +
-  geom_vline(xintercept = 2000)
-```
+ggplot(data = filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) + 
+  geom_point(alpha = .5) +
+  scale_color_viridis_d() +
+  theme_bw() +
+  xlim(2.75, 3.25) +
+  ylim(4.5, 6) +
+  geom_point(data = filter(all_di, dat == "I don't exist!")) # for a legend with alpha = 1 
+ggplot(data = filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) + 
+  geom_point(alpha = .5) +
+  scale_color_viridis_d() +
+  theme_bw() +
+  xlim(2.75, 3.25) +
+  ylim(4.5, 6) +
+  facet_wrap(vars(dat)) +
+  geom_point(data = filter(all_di, dat == "I don't exist!")) # for a legend with alpha = 1
 
-The datasets overlap but do occupy broadly different regions of S*N space.
+overlap_di <- filter(all_di,
+                     log(s0) > 2.75,
+                     log(s0) < 3.25,
+                     log(n0) > 4.5,
+                     log(n0) < 6)
+summary_overlap <- overlap_di %>%
+  filter(singletons == F) %>%
+  group_by(dat) %>%
+  summarize(count = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(prop = count / sum(count))
 
-FIA, dramatically more than any other dataset, struggles to get even 2000 samples.
-
-## Overall percentile results
-
-```{r overall}
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
+summary_overlap
 
@@
 
-Effect of singletons
+The datasets overlap but do occupy broadly different regions of S*N space. The arm - which is the weirdest region of the percentile values - is, unfortunately, 100% one dataset (Gentry).
 
-```{r singletons overall}
+For the vast majority of S*N space here, I don't think we can really use dataset as a predictor of percentile, because of the way they occupy different parts of what we know to be a very important range of variation.
 
-singletons_effect <- all_di %>%
-  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile) %>%
-  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples)) %>%
-  mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
-         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE) %>%
-  filter(nsamples_TRUE >= 2000, nsamples_FALSE >= 2000)
+We *could* narrow in on the region of maximum overlap/minimum variation and make comparison based on the sites only within that.
 
-ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
-  geom_point(alpha = .2) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
+I think there's a plausible comparison between bbs and misc_abund in the subset depicted above.
+You could find other regions of pairwise intersection between the other datasets, but I don't love going down that road (of maximum comparisons).
 
-ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
-    geom_point(alpha = .2) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
+```{r overlap plots}
 
-```
+overlap_di <- overlap_di %>%
+  filter(!singletons,
+         dat %in% c("bbs", "misc_abund_short"))
 
-Adding singletons makes skewness more skewed and simpson less even.
+ggplot(data = overlap_di, aes(x = log(s0), y = log(n0), color = log(n0 / s0))) +
+  geom_point(alpha = .5) +
+  scale_color_viridis_c(option = "plasma", end = .9) +
+  facet_wrap(vars(dat)) +
+  theme_bw()
 
-## Broken out by dataset
-
-```{r dataset}
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_percentile)) +
+ggplot(data = overlap_di, aes(x = skew_percentile)) + 
   geom_histogram(bins = 100) + 
@@
 
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_percentile)) +
+ggplot(data = overlap_di, aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+  geom_point(alpha = .5) +
+  scale_color_viridis_c(option = "plasma", end = .9) +
+  facet_wrap(vars(dat)) +
+  theme_bw()
+
+ggplot(data = overlap_di, aes(x = simpson_percentile)) + 
   geom_histogram(bins = 100) + 
@@
 
+ggplot(data = overlap_di, aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .5) +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+  facet_wrap(vars(dat)) +
+  theme_bw()
+
+ggplot(data = overlap_di, aes(x = log(n0/s0))) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y") +
+  theme_bw()
+
+ggplot(data = overlap_di, aes(x = log(n0 / s0), y = skew_percentile, color = dat)) +
+  geom_point(alpha = .5) +
+  scale_color_viridis_d(end = .8) +
+  theme_bw() +
+  geom_smooth(method = "lm", se =F)
+
+ggplot(data = overlap_di, aes(x = log(n0 / s0), y = simpson_percentile, color = dat)) +
+  geom_point(alpha = .5) +
+  scale_color_viridis_d(end = .8) +
+  theme_bw() +
+  geom_smooth(method = "lm", se =F)
 ```
 
-Effect of singletons
-
-```{r singletons dataset}
-
-singletons_effect <- all_di %>%
-  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile) %>%
-  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples)) %>%
-  mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
-         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE) %>%
-  filter(nsamples_TRUE >= 2000, nsamples_FALSE >= 2000)
-
-ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
-  geom_point(alpha = .2) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  facet_wrap(vars(dat))
-
-ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
-    geom_point(alpha = .2) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  facet_wrap(vars(dat))
-
-```
-
-# MACD
-
-```{r load macd}
-  cache_loc = "macdb"
-
-## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
-cache <- storr::storr_dbi("datatable", "keystable", db)
-
-all_di_macd <- readd(all_di_manip, cache = cache)
-
-DBI::dbDisconnect(db)
-rm(cache)
-```
-
-Nsamples
-
-```{r macd overall}
-
-ggplot(data = all_di_macd, aes(x = nsamples)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  geom_vline(xintercept = 2000)
-
-all_di_macd <- filter(all_di_macd, nsamples >= 2000)
-
-ggplot(data = all_di_macd, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-```
-
-By treatment - overall
-
-```{r macd trtmt overall}
-
-ggplot(data = all_di_macd, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(treatment), scales = "free_y")
-
-ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(treatment), scales = "free_y")
-
-```
-
-** I AM REALLY NOT CONFIDENT IN THE DATA HANDLING HERE, NEED TO REVISIT WHEN SHARPER **
-
-```{r macd ctrlcomp}
-
-macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)
-
-colnames(macd_comparisons) <- c("studyID", "control", "site")
-macd_comparisons <- macd_comparisons %>%
-  mutate(site = as.character(site), control = as.character(control))
-
-cc_di <- all_di_macd %>%
-  filter(singletons == FALSE, treatment == "comparison") %>%
-  left_join(macd_comparisons, by = c("studyID", "site")) %>%
-  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
-  rename(comparison = site) %>%
- left_join(select(all_di_macd, skew_percentile, simpson_percentile, site, singletons, nsamples), by = c("control" = "site")) %>%
-  distinct() %>%
-  rename(comp_skew = skew_percentile.x, comp_simp = simpson_percentile.x,
-         control_skew = skew_percentile.y, control_simp = simpson_percentile.y)
-
-ggplot(data = cc_di, aes(x = comp_skew, y = control_skew)) +
-  geom_point(alpha = .5) +
-#  xlim(0, 100) +
- # ylim(0, 100) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
-
-ggplot(data = cc_di, aes(x = comp_simp, y = control_simp)) +
-  geom_point(alpha = .5) +
- xlim(0, 100) +
- ylim(0, 100) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
-
-```
-
-# Portal plant manips
-
-```{r load pp}
-  cache_loc = "portal_plants_manip"
-
-## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
-cache <- storr::storr_dbi("datatable", "keystable", db)
-
-all_di_p<- readd(all_di_manip, cache = cache)
-
-DBI::dbDisconnect(db)
-rm(cache)
-```
-
-Nsamples, singletons
-
-```{r pp overall}
-
-ggplot(data = all_di_p, aes(x = nsamples)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  geom_vline(xintercept = 2000)
-
-all_di_p <- filter(all_di_p, nsamples >= 2000)
-
-ggplot(data = all_di_p, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-ggplot(data = all_di_p, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw()
-
-pp_singletons_effect <- all_di_p %>%
-  select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>%
-  tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile"))
-
-ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) +
-  geom_point(alpha = .1) +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  theme_bw()
-
-ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) +
-  geom_point(alpha = .1) +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  theme_bw()
-```
-
-By treatment, season
-
-```{r portal trtmt}
-ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(season, treatment), scales = "free_y")
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(season))
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(season, treatment), scales = "free_y")
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(season))
-```
-
-By year
-
-```{r plants year, fig.height = 25, fig.width = 5}
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_grid(rows = vars(year), cols = vars(season), scales = "free_y")
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_grid(rows = vars(year), cols = vars(season), scales = "free_y")
-```
-
-Trying median
-
-```{r pp median, fig.width = 12, fig.height = 12}
-
-pp_median <- all_di_p %>%
-  filter(singletons == F) %>%
-  group_by(season, year, treatment) %>%
-  summarize(skew_percentile = median(skew_percentile),
-            simpson_percentile = median(simpson_percentile)) %>%
-  ungroup() %>%
-  tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile))
-
-sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Skew Ctrl v Exclosure") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-   xlim(40, 100) +
-   ylim(40, 100)
-
-sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Skew Ctrl v Removal") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-   xlim(40, 100) +
-   ylim(40, 100)
-
-gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2)
-
-sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Simpson Ctrl v Exclosure") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-   xlim(0, 40) +
-   ylim(0, 40)
-
-sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
-  theme_bw() +
-  ggtitle("Simpson Ctrl v Removal") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  xlim(0, 40) +
-  ylim(0, 40)
-
-gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2)
-```
+This is a rough comparison all around, but I am not seeing a pronounced difference in behavior between the datasets.

### 2020-02-07 analysis/reports/vetting.Rmd
rough overlap comparison

@@
   scale_color_viridis_c(option = "plasma", end = .9)
+
+ggplot(data=all_di, aes(x = log(s0), y = log(n0), color = log(n0/s0))) +    geom_point(alpha = .5) + 
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)
+
+ggplot(data=all_di, aes(x = log(s0), y = log(n0), color = log(n0/s0))) +    geom_point(alpha = .5) + 
+  geom_point(data = filter(all_di, nsamples >= 2000), color = 'grey', alpha = .1) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9)
+
+ggplot(data = all_di, aes(x = log(n0/s0), y = nsamples)) +
+  geom_point(alpha = .1) +
+  theme_bw()
 

### 2020-02-07 analysis/reports/vetting.Rmd
more plots and tweaks

--- 2020-02-05 analysis/reports/vetting.Rmd
@@
 
-```{r draws v sn plots, fig.dim = c(5,5)}
+```{r draws v sn plots, fig.dim = c(4,4)}
 
@@
 
- ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
-    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
+ggplot(data=all_di, aes(x = log(s0), y = log(n0), color = log(n0/s0))) +    geom_point(alpha = .5) + 
   theme_bw() +
   scale_color_viridis_c(option = "plasma", end = .9)
+ # ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = log(nsamples))) +
+ #    geom_point(data = filter(all_di, nsamples <2000), alpha = .1) + 
+ #  theme_bw() +
+ #  scale_color_viridis_c(option = "plasma", end = .9)
+ #
+
+ggplot(data = all_di, aes(x = log(n0/s0), y = nsamples, color = log(s0))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_hline(yintercept = 2000, color = "black") +
+  scale_color_viridis_c(option = "plasma", end =.9)
+
+ggplot(data = all_di, aes(x = log(n0/s0), y = nsamples, color = log(n0))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_hline(yintercept = 2000, color = "black") +
+  scale_color_viridis_c(option = "plasma", end =.9)
+
+ggplot(data = filter(all_di, log(n0/s0) <= 2), aes(x = log(n0/s0), y = nsamples, color = log(s0))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_hline(yintercept = 2000, color = "black") +
+  scale_color_viridis_c(option = "plasma", end =.9)
+
+ggplot(data = filter(all_di, log(n0/s0) <= 2), aes(x = log(n0/s0), y = nsamples, color = log(n0))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_hline(yintercept = 2000, color = "black") +
+  scale_color_viridis_c(option = "plasma", end =.9)
+
+ggplot(data = all_di, aes(x = log(n0/s0))) +
+  geom_histogram(alpha = .3) +
+  geom_histogram(data = filter(all_di, nsamples <= 2000)) +
+  theme_bw()
 
@@
 
-In these plots, the grey region is nsamples >= 2000.
-It looks like removing communities with nsamples < 2000 is basically filtering out N < about 100-150.
-For more nuance we could dip down into lower n for intermediate S (S between 5 and 50), and still be getting pretty good sampling?
+In the first plot, the grey region is nsamples >= 2000. In the histogram, the light grey is all the samples and the bold is samples where nsamples <= 2000.
 
-Leaving it be for now.
+Looking at log(n0/s0) vs. nsamples,
+
+- the low-sampled points (bold in histogram) are for the most part down where n0/s0 is low. 
+- if S or N is very low, even having a high ratio doesn't help.
+- if S is very high (meaning N can also be fairly high, without having a very high ratio), even if the ratio is low, you might get good sampling.
+
+## Where the datasets fall
+
+```{r dataset space}
+ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = dat)) + 
+  geom_point(alpha = .2) +
+  scale_color_viridis_d() +
+  theme_bw() +
+  geom_point(data = filter(all_di, dat == "I don't exist!")) # for a legend with alpha = 1
+
+ggplot(data = all_di, aes(x = nsamples)) +
+  geom_histogram() +
+  theme_bw()+
+  facet_wrap(vars(dat), scales = "free_y") +
+  geom_vline(xintercept = 2000)
+
+ggplot(data = all_di, aes(x = log(n0/s0))) +
+  geom_histogram(alpha = .3) +
+  geom_histogram(data = filter(all_di, nsamples <= 2000)) +
+  theme_bw()+
+  facet_wrap(vars(dat), scales = "free_y")
+```
+
+The datasets overlap but do occupy broadly different regions of S*N space. The arm - which is the weirdest region of the percentile values - is, unfortunately, 100% one dataset (Gentry).
+
+For the vast majority of S*N space here, I don't think we can really use dataset as a predictor of percentile, because of the way they occupy different parts of what we know to be a very important range of variation.
+
+We *could* narrow in on the region of maximum overlap/minimum variation and make comparison based on the sites only within that.
+
+FIA, dramatically more than any other dataset, struggles to get even 2000 samples.
 
 ## Percentile value vs. range of variation of FS
-
-This is really hard to get traction on. S and N affect everything.
 
@@
   scale_color_viridis_c(option = "plasma", end = .9) +
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Simpson mean")
@@
   scale_color_viridis_c(option = "plasma", end = .9)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Simpson sd")
@@
   scale_color_viridis_c(option = "plasma", end = .9)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Simpson range")
@@
   scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Simpson percentile")
@@
   scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Simpson percentile")
 
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
 ```
@@
   scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Skew mean")
@@
   scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Skew sd")
@@
   scale_color_viridis_c(option = "plasma", end = .9, direction = -1)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Skew range")
@@
   scale_color_viridis_c(option = "plasma", end = .9)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Skew percentile")
@@
   scale_color_viridis_c(option = "plasma", end = .9)+
-  theme(legend.position = "none") +
+  theme(legend.position = "top") +
   ggtitle("Skew percentile")
 
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = simpson_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
 ```
@@
 
-```{r avg n percentile}
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = skew_percentile)) +
-  geom_point(alpha = .1) +
-  theme_bw()
-
-ggplot(data = filter(all_di, nsamples >= 2000, singletons == F), aes(x = log(n0/s0), y = simpson_percentile)) +
-  geom_point(alpha = .1) +
-  theme_bw()
-```
-
-You really don't get non-extreme percentiles in the high n/s region.
-
 These scatterplots are good for seeing where the variation is but not the density; there's a *lot* of points on top of each other down at 0/up at 100.
-## Where the datasets fall
-
-```{r dataset space}
-ggplot(data = all_di, aes(x = log(s0), y = log(n0), color = dat)) + 
-  geom_point(alpha = .2) +
-  scale_color_viridis_d() +
-  theme_bw() +
-  geom_point(data = filter(all_di, dat == "I don't exist!")) # for a legend with alpha = 1
-
-ggplot(data = all_di, aes(x = nsamples)) +
-  geom_histogram() +
-  theme_bw()+
-  facet_wrap(vars(dat), scales = "free_y") +
-  geom_vline(xintercept = 2000)
-```
-
-The datasets overlap but do occupy broadly different regions of S*N space. The arm - which is the weirdest region of the percentile values - is, unfortunately, 100% one dataset (Gentry).
-
-For the vast majority of S*N space here, I don't think we can really use dataset as a predictor of percentile, because of the way they occupy different parts of what we know to be a very important range of variation.
-
-We *could* narrow in on the region of maximum overlap/minimum variation and make comparison based on the sites only within that.
-
-FIA, dramatically more than any other dataset, struggles to get even 2000 samples.
 
@@
   theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y")
+  facet_wrap(vars(season, treatment), scales = "free_y")
 

### 2020-02-11 analysis/reports/vetting.Rmd
more relationships

@@
 
+```{r do fs chars predict perc, fig.dim = c(4,4)}
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_range, y = simpson_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_mean, y = simpson_percentile)) +
+  geom_point(alpha = .05) +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_sd, y = simpson_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_range, y = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_mean, y = skew_percentile)) +
+  geom_point(alpha = .05) +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_sd, y = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw()
+```
+
 Effect of singletons
@@
 BBS and FIA have the most that are in the intermediate zone.
+
+```{r fs chars by dat, fig.dim = c(3,3)}
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_range)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_mean)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_sd)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_percentile)) +
+  geom_boxplot() +
+  theme_bw()
+# Removing low n/s
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_range)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_mean)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_sd)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_percentile)) +
+  geom_boxplot() +
+  theme_bw()
+
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_range)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_mean)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_sd)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_percentile)) +
+  geom_boxplot() +
+  theme_bw()
+# Removing low n/s
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_range)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_mean)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_sd)) +
+  geom_boxplot() +
+  theme_bw()
+ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_percentile)) +
+  geom_boxplot() +
+  theme_bw()
+```
 

### 2020-02-11 analysis/reports/vetting.Rmd
increase macdb samples

@@
 
-<!-- ** I AM REALLY NOT CONFIDENT IN THE DATA HANDLING HERE, NEED TO REVISIT WHEN SHARPER ** -->
+```{r macd ctrlcomp}
 
-<!-- ```{r macd ctrlcomp} -->
+macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)
 
-<!-- macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F) -->
+colnames(macd_comparisons) <- c("studyID", "control", "site")
+macd_comparisons <- macd_comparisons %>%
+  mutate(site = as.character(site), control = as.character(control))
 
-<!-- colnames(macd_comparisons) <- c("studyID", "control", "site") -->
-<!-- macd_comparisons <- macd_comparisons %>% -->
-<!--   mutate(site = as.character(site), control = as.character(control)) -->
+cc_di <- all_di_macd %>%
+  filter(singletons == FALSE, treatment == "comparison") %>%
+  left_join(macd_comparisons, by = c("studyID", "site")) %>%
+  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
+  rename(comparison = site) %>%
+  mutate(ctrl_skew_percentile = NA,
+         ctrl_simpson_percentile = NA)
 
-<!-- cc_di <- all_di_macd %>% -->
-<!--   filter(singletons == FALSE, treatment == "comparison") %>% -->
-<!--   left_join(macd_comparisons, by = c("studyID", "site")) %>% -->
-<!--   select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>% -->
-<!--   rename(comparison = site) %>% -->
-<!--  left_join(select(all_di_macd, skew_percentile, simpson_percentile, site, singletons, nsamples), by = c("control" = "site")) %>% -->
-<!--   distinct() %>% -->
-<!--   rename(comp_skew = skew_percentile.x, comp_simp = simpson_percentile.x, -->
-<!--          control_skew = skew_percentile.y, control_simp = simpson_percentile.y) -->
+for(i in 1:nrow(cc_di)) {
 
-<!-- ggplot(data = cc_di, aes(x = comp_skew, y = control_skew)) + -->
-<!--   geom_point(alpha = .5) + -->
-<!-- #  xlim(0, 100) + -->
-<!--  # ylim(0, 100) + -->
-<!--   theme_bw() + -->
-<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->
+  control_row <- filter(all_di_macd, site == cc_di$control[i], singletons == F) %>%
+    unique()
+  if(nrow(control_row) >0 ) {
+    cc_di$ctrl_simpson_percentile[i] <- control_row$simpson_percentile
+    cc_di$ctrl_skew_percentile[i] <- control_row$skew_percentile
+  }
+}
 
-<!-- ggplot(data = cc_di, aes(x = comp_simp, y = control_simp)) + -->
-<!--   geom_point(alpha = .5) + -->
-<!--  xlim(0, 100) + -->
-<!--  ylim(0, 100) + -->
-<!--   theme_bw() + -->
-<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->
+cc_di <- cc_di %>%
+  mutate(simpson_change = simpson_percentile - ctrl_simpson_percentile,
+         skew_change = skew_percentile - ctrl_skew_percentile)
 
-<!-- ``` -->
+ggplot(data = cc_di, aes(x = skew_percentile, y = ctrl_skew_percentile)) +
+  geom_point(alpha = .5) +
+  #  xlim(0, 100) +
+  # ylim(0, 100) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green")
+
+ggplot(data = cc_di, aes(x = simpson_percentile, y = ctrl_skew_percentile)) +
+  geom_point(alpha = .5) +
+  xlim(0, 100) +
+  ylim(0, 100) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green")
+
+ggplot(data = cc_di, aes(x = simpson_change)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(data = cc_di, aes(x = skew_change)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(data = cc_di, aes(x = ctrl_simpson_percentile, y = simpson_change)) +
+  geom_point(alpha = .3) +
+  geom_hline(yintercept = 0) +
+  theme_bw()
+
+ggplot(data = cc_di, aes(x = ctrl_skew_percentile, y = skew_change)) +
+  geom_point(alpha = .3) +
+  geom_hline(yintercept = 0) +
+  theme_bw()
+
+print(t.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T)
+)
+print(t.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T)
+)
+
+print(wilcox.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T))
+print(wilcox.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T))
+
+```
+
+Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?)
 

### 2020-02-11 analysis/macdb_pipeline.R

@@ -8,7 +8,7 @@ datasets <- "macdb"
 
 sites_list <- list_sites("macdb") %>%
   dplyr::filter(!(site %in% c(164, 166, 167)))
-ndraws = 2500
+ndraws = 1000
 #sites_list <- sites_list[1:5, ]
 set.seed(1981)
 

### 2020-02-12 analysis/reports/vetting.Rmd
use 10k not 1k

@@
 all_di_macd <- readd(all_di_manip, cache = cache) 
+macd_dat <- readd(dat_s_dat_macdb, cache = cache)
 
@@
 rm(cache)
+
+macd_dat <- macd_dat %>%
+  group_by(site, dat, singletons, sim, source) %>%
+  summarize(s0 = max(rank),
+            n0 = sum(abund)) %>%
+  ungroup()
+
+all_di_macd <- left_join(all_di_macd, macd_dat, by = c("site", "dat", "singletons", "sim", "source"))
+
+ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()
+
+ggplot(data = filter(all_di, nsamples >= 2000), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, nsamples >= 2000), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()
+
 ```

### 2020-02-12 analysis/reports/nparts.Rmd
add count elements

---
title: "Nparts"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

```{r fxns}

brute_force_parts <- function(s, n, nsamples = 1000) {
  bunch_of_fs <- feasiblesads::sample_fs(s, n, nsamples)
  colnames(bunch_of_fs) <- 1:s

  bunch_of_fs <- bunch_of_fs %>%
    as.data.frame %>%
    distinct() %>%
    mutate(sim = dplyr::row_number()) %>%
    tidyr::gather(-sim, key = "species", value = "abund") %>%
    arrange(sim)
  return(max(bunch_of_fs$sim)) 
}

# count_parts <- function(s, n, p_table = NULL) {
#   
#   if(is.null(p_table)) {
#     p_table <- feasiblesads::fill_ps(s, n, F)
#   }
#   
#   k_table <- feasiblesads::fill_ks(s, n)
#   
#   
#   ns = 1:k_table[s, n+1] # this differs from `feasiblesads` because 0 is NOT an option
#   
#   n_parts = p_table[s - 1,
#                     n - (s * ns) + 1]
#   total_parts = gmp::sum.bigz(gmp::as.bigz(n_parts))
#   
#   return(as.integer(total_parts))
# }

```

```{r small range}
s = seq(2, 10, by = 2)
n = seq(3, 53, by = 5)

comms <- expand.grid("s" =s , "n" = n) %>%
  filter(n > s) %>%
  mutate(bf_n = NA,
         cp_n = NA)

for(i in 1:nrow(comms)) {
  comms$bf_n[i] <- brute_force_parts(comms$s[i], comms$n[i], nsamples = 1000)
  comms$cp_n[i] <- scadsanalysis::count_elements(comms$s[i], comms$n[i])
}

ggplot(data = comms, aes(x = bf_n, y = cp_n)) +
  geom_point() +
  geom_abline(intercept = 0, slope  = 1) +
  theme_bw()

```
So this function looks pretty good until the size of the fs approaches 2x nb samples.

```{r s and n}
ggplot(data = comms, aes(x = s, y = n, color = cp_n)) +
  geom_point() +
  theme_bw()

```

### 2020-02-12 analysis/portal_pipeline.R

@@ -7,7 +7,7 @@ expose_imports("scadsanalysis")
 datasets <- "portal_plants"
 
 sites_list <- list_sites("portal_plants")
-ndraws = 10000
+ndraws = 2500
 #sites_list <- sites_list[1:15, ]
 set.seed(1977)
 

### 2020-02-12 analysis/reports/dat_report_template.Rmd
new report

@@
 ```{r number of samples}
-
-site_samples <- all_di %>%
-  left_join(select(sv, -source, -sim), by = c("site", "singletons"))
+# 
+# site_samples <- all_di %>%
+#   left_join(select(sv, -source, -sim), by = c("site", "singletons"))
 ```
 
-#### The maximum number of samples achieved is `r max(site_samples$nsamples)`.
+#### The maximum number of samples achieved is `r max(all_di$nsamples)`.
 
 ```{r plot nb samples}
-samples_hist <- ggplot(data = site_samples, aes(x = nsamples)) +
+samples_hist <- ggplot(data = all_di, aes(x = nsamples)) +
   geom_histogram(binwidth = 10) +
@@
   ggtitle("Number of samples achieved")  +
-  xlim(c(-11, max(site_samples$nsamples) + 11))
+  xlim(c(-11, max(all_di$nsamples) + 11))
 
@@
 
-sv_samples_plot <- ggplot(data = site_samples, aes(x = s0, y = n0, color = nsamples)) +
+sv_samples_plot <- ggplot(data = all_di, aes(x = s0, y = n0, color = nsamples)) +
   geom_point(alpha = .5) +
@@
   facet_wrap(vars(singletons), nrow = 1) +
-  scale_color_viridis_c(option = "magma", end = .75, limits = c(0, max(site_samples$nsamples))) +
+  scale_color_viridis_c(option = "magma", end = .75, limits = c(0, max(all_di$nsamples))) +
   ggtitle("Number of samples achieved by state variables")

### 2020-02-18 analysis/reports/dat_report_template.Rmd
remove scruffy manips section from dat report template

@@
 
-```{r manip}
-
-if(this_dataset == "macdb") {
-  all_di_manip <- readd(all_di_manip, cache = cache)
-
-  manip_skew_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = skew_percentile, group = studyID)) +
-    geom_line() +
-    theme_bw()
-
-  print(manip_skew_plot)
-
-  manip_simpson_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = simpson_percentile, group = studyID)) +
-    geom_line() +
-    theme_bw()
-
-  print(manip_simpson_plot)
-
-}
-
-if(this_dataset == "portal_plants_manip") {
-  all_di_manip <- readd(all_di_manip, cache = cache)
-
-  manip_skew_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = skew_percentile)) +
-    geom_boxplot() +
-    facet_wrap(vars(season, singletons)) +
-    theme_bw()
-
-  print(manip_skew_plot)
-
-  manip_simpson_plot <- ggplot(data = all_di_manip, aes(x = treatment, y = simpson_percentile)) +
-    geom_boxplot() +
-    facet_wrap(vars(season, singletons)) +
-    theme_bw()
-
-  print(manip_simpson_plot)
-}
-```
-
 ```{r cleanup}

### 2020-02-18 analysis/reports/synthesis.Rmd
run this

---
title: "Synthesis report"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
```

# Datasets in S and N space

# Number of samples
- How many samples are we achieving
- What % of the FS is this?

#

### 2020-02-18 analysis/bbs_pipeline.R

@@ -43,6 +43,7 @@ all <- dat_plan
 ## Set up the cache and config
 db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-bbs.sqlite"))
 cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
 
 ## View the graph of the plan
 if (interactive())

### 2020-02-18 analysis/fia_pipeline.R

@@ -43,6 +43,7 @@ all <- dat_plan
 ## Set up the cache and config
 db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-fia.sqlite"))
 cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
 
 ## View the graph of the plan
 if (interactive())

### 2020-02-18 analysis/macdb_pipeline.R

@@ -8,7 +8,7 @@ datasets <- "macdb"
 
 sites_list <- list_sites("macdb") %>%
   dplyr::filter(!(site %in% c(164, 166, 167)))
-ndraws = 30000
+ndraws = 4000
 #sites_list <- sites_list[1:5, ]
 set.seed(1981)
 
@@ -45,6 +45,7 @@ all <- dat_plan
 ## Set up the cache and config
 db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-macdb.sqlite"))
 cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
 
 ## View the graph of the plan
 if (interactive())

### 2020-02-18 analysis/miscabund_pipeline.R

@@ -7,7 +7,7 @@ expose_imports("scadsanalysis")
 datasets <- "misc_abund_short"
 
 sites_list <- list_sites("misc_abund_short")
-ndraws = 10000
+ndraws = 4000
 #sites_list <- sites_list[1:15, ]
 set.seed(1981)
 
@@ -43,6 +43,7 @@ all <- dat_plan
 ## Set up the cache and config
 db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-miscabund.sqlite"))
 cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
 
 ## View the graph of the plan
 if (interactive())

### 2020-02-18 analysis/portal_pipeline.R

@@ -7,7 +7,7 @@ expose_imports("scadsanalysis")
 datasets <- "portal_plants"
 
 sites_list <- list_sites("portal_plants")
-ndraws = 10000
+ndraws = 4000
 #sites_list <- sites_list[1:15, ]
 set.seed(1977)
 
@@ -42,6 +42,7 @@ all <- drake_plan(
 ## Set up the cache and config
 db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-portal_plants.sqlite"))
 cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
 
 ## View the graph of the plan
 if (interactive())

### 2020-02-19 analysis/reports/synthesis.Rmd

@@
 all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+
+all_di <- all_di %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples))
 ```
@@
 
+Here is where our communities fall in S and N space:
+
+```{r datasets in s and n space}
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  scale_color_viridis_d()
+
+```
+
+Here is how that translates into the size of the feasible set:
+
+```{r size of fs}
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nparts)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9)
+
+```
+
+Note that the color scale is log transformed, so the largest communities have e^`r max(all_di$log_nparts)`, or `r exp(max(all_di$log_nparts))`, elements in the feasible set!
+
+Here is how the size of the feasible set maps on to N/S:
+
+```{r nparts vs avgn}
+ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = log_nparts, color = log(s0))) +
+  theme_bw() +
+  geom_point(alpha = .2) +
+  scale_color_viridis_c()
+
+```
+
 # Number of samples
-- How many samples are we achieving
-- What % of the FS is this?
+
+Here is how many samples we are achieving:
+
+```{r nsamples}
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9)
+
+ggplot(filter(all_di, singletons == F, nsamples <  max(nsamples)), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9)
+```
+
+Only in the very smallest communities do we get appreciably fewer than `r max(all_di$nsamples)` samples.
+
+Here is how the number of samples we're getting compares to the size of the feasible set:
+
+```{r nsamples vs nparts}
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nsamples - log_nparts)) +
+  geom_point(alpha = .7) +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9, direction = -1) +
+  theme(legend.position = "top")
+
+ggplot(filter(all_di, singletons == F), aes(x = log_nsamples - log_nparts, y = log_nsamples)) +
+  theme_bw() +
+  geom_vline(xintercept = c(log(.95), log(.1))) +
+  geom_point(alpha = .3)
+
+```
+
+The vertical lines are the 10% and 95% marks, from left to right.
+When we got relatively few samples (`r min(all_di$nsamples)`), we had found `r exp(filter(all_di, nsamples == min(nsamples))$log_nsamples -  filter(all_di, nsamples == min(nsamples))$log_nparts)` of that feasible set.
+And there's a clear negative relationship between the proportion of the FS that we've found and the number of samples we got, once we start getting about 10% of the feasible set.
+This makes sense; at that point we have a 1 in 10 chance of drawing one we've already seen.
+But for almost all cases, we're sampling only a miniscule proportion of the feasible set - median of `r median(exp(all_di$log_nsamples - all_di$log_nparts))`!
+- and get no duplicates.
+
+The vastness of the FS poses a limit on our capacity to detect how unlikely a value is.
+We could conservatively round up: scoring in the 100th percentile, when we had 4000 samples, means a maximum of (1 / 4000 + tiny error) chance of getting that score?
 

### 2020-02-19 analysis/reports/cdf.Rmd
cdf exploring

---
title: "Digging into %ile and CDF fxns"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

this_dataset <- "portal_plants"

if(this_dataset == "misc_abund_short") {
  cache_loc = "miscabund"
} else if (this_dataset == "fia_short") {
  cache_loc = "fia" 
} else {
  cache_loc = this_dataset
}

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
cache <- storr::storr_dbi("datatable", "keystable", db)

dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)

a_fs <- readd(di_fs_1991_winter_FALSE, cache = cache)
```

Here is the distribution of skew values in this fs:

```{r raw dists}

ggplot(filter(a_fs, source == "sampled"), aes(x = skew)) + 
  geom_histogram() +
  theme_bw()

```

The percentile ranks as computed by `get_percentile` for the max and minimum sampled values are `r get_percentile(max(filter(a_fs, source == "sampled")$skew), filter(a_fs, source == "sampled")$skew)` and `r get_percentile(min(filter(a_fs, source == "sampled")$skew), filter(a_fs, source == "sampled")$skew)`.

```{r ecdf}

skew_ecdf <- ecdf(filter(a_fs, source == "sampled")$skew)

plot(skew_ecdf)

```

The ecdf function at hte minimum and maximum sampled valures evaluates to `r skew_ecdf(max(filter(a_fs, source == "sampled")$skew))` and `r skew_ecdf(min(filter(a_fs, source == "sampled")$skew))`.

```{r ecdf w infinities}

inf_ecdf <- ecdf(c(filter(a_fs, source == "sampled")$skew, -Inf, Inf))
plot(x = filter(a_fs, source == "sampled")$skew, y = inf_ecdf(filter(a_fs, source == "sampled")$skew))
```

The inf_ecdf function at the minimum and maximum sampled valures evaluates to `r inf_ecdf(max(filter(a_fs, source == "sampled")$skew))` and `r inf_ecdf(min(filter(a_fs, source == "sampled")$skew))`.

```{r cleanup}

DBI::dbDisconnect(db)
rm(cache)
```

### 2020-02-19 analysis/reports/synthesis.Rmd
cdf exploring

@@
   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
-         log_nsamples = log(nsamples))
+         log_nsamples = log(nsamples)) %>%
+  mutate(prop_found = exp(log_nsamples - log_nparts))
 ```
@@
   theme_bw() +
-  scale_color_viridis_d()
+  theme(legend.position = "top") + scale_color_viridis_d()
 
@@
   theme_bw() +
-  scale_color_viridis_c(option = "magma", end = .9)
+  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9)
 
@@
   geom_point(alpha = .2) +
-  scale_color_viridis_c()
+  theme(legend.position = "top") + scale_color_viridis_c()
 
@@
   theme_bw() +
-  scale_color_viridis_c(option = "magma", end = .9)
+  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9)
 ```
@@
 The vertical lines are the 10% and 95% marks, from left to right.
-When we got relatively few samples (`r min(all_di$nsamples)`), we had found `r exp(filter(all_di, nsamples == min(nsamples))$log_nsamples -  filter(all_di, nsamples == min(nsamples))$log_nparts)` of that feasible set.
+When we got relatively few samples (`r min(filter(all_di, singletons == F, nsamples > 1)$nsamples)`), we had found `r 100 * exp(filter(all_di, nsamples == min(filter(all_di, singletons == F, nsamples > 1)$nsamples))$log_nsamples[1] -  filter(all_di, nsamples == min(filter(all_di, singletons == F, nsamples > 1)$nsamples))$log_nparts[1])`% of that feasible set.
 And there's a clear negative relationship between the proportion of the FS that we've found and the number of samples we got, once we start getting about 10% of the feasible set.
@@
 
-#
+# Distribution of percentile values
+
+## Skewness
+```{r skew percentiles}
+ggplot(filter(all_di, singletons == F), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  geom_hline(yintercept = .01)
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0/n0), y = skew_percentile, color = prop_found)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+  theme(legend.position = "top")
+
+all_di$many_found <- all_di$prop_found >= .5
+
+ggplot(filter(all_di, singletons == F), aes(x = skew_percentile)) +
+  theme_bw() +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(many_found))
+
+ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = skew_percentile, color = log(s0))) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  theme(legend.position = "top") + scale_color_viridis_c()
+```
+
+## Simpson
+```{r simpson percentiles}
+ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  geom_hline(yintercept = .01)
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0/n0), y = simpson_percentile, color = prop_found)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+  theme(legend.position = "top")
+
+ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile)) +
+  theme_bw() +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(many_found))
+
+ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = simpson_percentile, color = log(s0))) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  theme(legend.position = "top") + scale_color_viridis_c()
+```
+
+Do S and N predict percentile?

### 2020-02-19 analysis/reports/synthesis.Rmd
updating synthesis w fia

--- 2020-02-18 analysis/reports/synthesis.Rmd
@@
 all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+
+all_di <- all_di %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples)) %>%
+  mutate(prop_found = exp(log_nsamples - log_nparts))
 ```
@@
 
+Here is where our communities fall in S and N space:
+
+```{r datasets in s and n space}
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
+  geom_point(alpha = .8) +
+  theme_bw() +
+  scale_color_viridis_d()
+
+```
+
+Here is how that translates into the size of the feasible set:
+
+```{r size of fs}
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nparts)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+
+```
+
+Note that the color scale is log transformed, so the largest communities have e^`r max(all_di$log_nparts)`, or `r exp(max(all_di$log_nparts))`, elements in the feasible set!
+
+Here is how the size of the feasible set maps on to N/S:
+
+```{r nparts vs avgn}
+ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = log_nparts, color = log(s0))) +
+  theme_bw() +
+  geom_point(alpha = .2) +
+  scale_color_viridis_c()
+
+```
+
 # Number of samples
-- How many samples are we achieving
-- What % of the FS is this?
+
+Here is how many samples we are achieving:
+
+```{r nsamples}
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9)
+
+ggplot(filter(all_di, singletons == F, nsamples <  max(nsamples)), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9)
+```
+
+Only in the very smallest communities do we get appreciably fewer than `r max(all_di$nsamples)` samples.
+
+Here is how the number of samples we're getting compares to the size of the feasible set:
+
+```{r nsamples vs nparts}
+ggplot(filter(all_di, singletons == F), aes(x = prop_found)) +
+  theme_bw() +
+  geom_histogram(bins = 100)
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = prop_found)) +
+  geom_point(alpha = .7) +
+  geom_point(data = filter(all_di, singletons == F, prop_found == 1), color = "grey") +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9, direction = -1) +
+  theme(legend.position = "top")
+
+ggplot(filter(all_di, singletons == F), aes(x = prop_found, y =nsamples)) +
+  theme_bw() +
+  geom_vline(xintercept = c((.95), (.1))) +
+  geom_point(alpha = .3) +
+  geom_point(data = filter(all_di, singletons == F, prop_found == 1), color = "grey")
+
+prop_found_ecdf <- ecdf(filter(all_di,singletons == F)$prop_found)
+
+pf_df <- data.frame(prop_found = seq(0, 1, by = 0.001),
+                    cdf = prop_found_ecdf(seq(0, 1, by = 0.001)))
+
+ggplot(data = pf_df, aes(x = prop_found, y = cdf)) +
+  geom_line() +
+  theme_bw()
+
+```
+
+For about `r 100 * mean(filter(all_di, singletons == F)$prop_found == 1)`% of sites, we found all the elements of the FS. The *vast majority* of this is FIA.
 

### 2020-02-20 analysis/reports/data_cdf.Rmd
cdf plots, not sure what to make of them

---
title: "CDF v percentiles report"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found ==1)
```

## Skewness
```{r skew cds}
ggplot(filter(all_di, singletons == F), aes(x = skew_cd, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = skew_cd)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

ggplot(filter(all_di, singletons == F), aes(x = log(s0/n0), y = skew_cd, color = prop_found)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
  theme(legend.position = "top")

all_di$many_found <- all_di$prop_found >= .5

ggplot(filter(all_di, singletons == F), aes(x = skew_cd)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(many_found))

ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = skew_cd, color = log(s0))) +
  geom_point(alpha = .2) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c()
```

## Simpson
```{r simpson cds}
ggplot(filter(all_di, singletons == F), aes(x = simpson_cd, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_cd)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

ggplot(filter(all_di, singletons == F), aes(x = log(s0/n0), y = simpson_cd, color = prop_found)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
  theme(legend.position = "top")

ggplot(filter(all_di, singletons == F), aes(x = simpson_cd)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(many_found))

ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = simpson_cd, color = log(s0))) +
  geom_point(alpha = .2) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c()
```

### 2020-02-20 analysis/reports/synthesis.Rmd
render on hpg

@@
          log_nsamples = log(nsamples)) %>%
-  mutate(prop_found = exp(log_nsamples - log_nparts))
+  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
+  mutate(found_all = prop_found==1)
 ```
@@
   theme_bw() +
-  scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
 
@@
 
-Here is how the size of the feasible set maps on to N/S:
+Here is how the size of the feasible set maps on to N/S. It increases with n0/s0 and s0.
 
@@
   theme_bw() +
-  scale_color_viridis_c(option = "magma", end = .9)
+  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9)
 
-ggplot(filter(all_di, singletons == F, nsamples <  max(nsamples)), aes(x = log(s0), y = log(n0), color = log_nsamples)) +
-  geom_point() +
-  theme_bw() +
-  scale_color_viridis_c(option = "magma", end = .9)
 ```
 
-Only in the very smallest communities do we get appreciably fewer than `r max(all_di$nsamples)` samples.
+Only in small communities do we get appreciably fewer than `r max(all_di$nsamples)` samples.
 
@@
 
-```{r nsamples vs nparts}
+```{r nsamples vs nparts, fig.dim = c(4,3)}
 ggplot(filter(all_di, singletons == F), aes(x = prop_found)) +
@@
   theme_bw() +
-  scale_color_viridis_c(option = "magma", end = .9, direction = -1) +
-  theme(legend.position = "top")
+  scale_color_viridis_c(option = "magma", end = .9, direction = -1) #+
+#theme(legend.position = "top")
 
@@
 
-For about `r 100 * mean(filter(all_di, singletons == F)$prop_found == 1)`% of sites, we found all the elements of the FS. The *vast majority* of this is FIA.
+For about `r 100 * mean(filter(all_di, singletons == F)$prop_found == 1)`% of sites, we found all the elements of the FS. The *vast majority* of this is FIA - here is what happens if we take out FIA:
 
+```{r prop found no fia, fig.dim = c(4,3)}
+ggplot(filter(all_di, singletons == F, dat != "fia_short"), aes(x = prop_found)) +
+  theme_bw() +
+  geom_histogram(bins = 100)
+
+ggplot(filter(all_di, singletons == F, dat != "fia_short"), aes(x = log(s0), y = log(n0), color = prop_found)) +
+  geom_point(alpha = .7) +
+  geom_point(data = filter(all_di, singletons == F, dat != "fia_short", prop_found == 1), color = "grey") +
+  theme_bw() +
+  scale_color_viridis_c(option = "magma", end = .9, direction = -1)# +
+#theme(legend.position = "top")
+
+ggplot(filter(all_di, singletons == F, dat != "fia_short"), aes(x = prop_found, y =nsamples)) +
+  theme_bw() +
+  geom_vline(xintercept = c((.95), (.1))) +
+  geom_point(alpha = .3) +
+  geom_point(data = filter(all_di, singletons == F, prop_found == 1, dat != "fia_short"), color = "grey")
+
+prop_found_ecdf <- ecdf(filter(all_di,singletons == F, dat != "fia_short")$prop_found)
+
+pf_df <- data.frame(prop_found = seq(0, 1, by = 0.001),
+                    cdf = prop_found_ecdf(seq(0, 1, by = 0.001)))
+
+ggplot(data = pf_df, aes(x = prop_found, y = cdf)) +
+  geom_line() +
+  theme_bw()
+
+```
+
+Without FIA, we find all the samples about `r 100 * mean(filter(all_di, singletons == F, dat != "fia_short")$prop_found == 1)`% of the time.
+
+# Distribution of percentile values
+
+## Skewness
+
+Here is the overall distribution of skewness, and if we split based on whether we found all the samples:
+```{r skew percentiles}
+ggplot(filter(all_di, singletons == F), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  geom_hline(yintercept = .01)
+ggplot(filter(all_di, singletons == F), aes(x = skew_percentile)) +
+  theme_bw() +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(found_all), scales = "free_y")
+```
+
+When we found all the samples, the percentiles are more evenly distributed. I do not read much into the spike at 0 for those communities, because skewness is bizarre for very small communities.
+
+Here is how skewness maps with S and N:
+```{r skew v s and n, fig.dim = c(10,10)}
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)
+
+# ggplot(filter(all_di, singletons == F), aes(x = log(n0/s0), y = skew_percentile, color = prop_found)) +
+#   geom_point() +
+#   theme_bw() +
+#   scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+#   theme(legend.position = "top")
 # 
+# ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = skew_percentile, color = log(s0))) +
+#   geom_point(alpha = .2) +
+#   theme_bw() +
+#   theme(legend.position = "top") + scale_color_viridis_c()
+```
+
+The very low skewness values are down in the very small and very weird communities. There may be variation along S and N elsewhere, but it is hard to parse.
+
+## Simpson
+
+Here is the overall evenness distribution, and split by whether we found 'em all:
+
+```{r simpson percentiles}
+ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  geom_hline(yintercept = .01)
+
+ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile)) +
+  theme_bw() +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(found_all))
+
+```
+
+Simpson is less evenly distributed than skewness. Again, where we found them all, we don't see the disproportionately common low percentile values.
+
+Here is how Simpson behaves in S and N space:
+
+```{r even v s and n, fig.dim = c(10,10)}
+# ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = simpson_percentile, color = log(s0))) +
+#   geom_point(alpha = .2) +
+#   theme_bw() +
+#   theme(legend.position = "top") + scale_color_viridis_c()
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)
+# ggplot(filter(all_di, singletons == F), aes(x = log(s0/n0), y = simpson_percentile, color = prop_found)) +
+#   geom_point() +
+#   theme_bw() +
+#   scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
+#   theme(legend.position = "top")
+```
+
+There is unusual behavior where S is large and N/S is relatively small (log N/S <= 1.5), where evenness is unusually *high*.
+
+For both skew and evenness, we do not see non-extreme percentile values in large communities:
+
+```{r non extremes}
+
+ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = skew_percentile, color = log(n0))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  theme(legend.position = "top") + 
+  scale_color_viridis_c(end = .9)
+
+ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = simpson_percentile, color = log(n0))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  theme(legend.position = "top") + 
+  scale_color_viridis_c(end = .9)
+
+```
+
+## Singletons
+
+Here is how singletons change percentiles, broken out by whether or not we found all the samples:
+
+```{r singletons overall}
+
+singletons_effect <- all_di %>%
+  select(dat, nsamples, site, singletons, skew_percentile, simpson_percentile, found_all) %>%
+  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, nsamples, found_all)) %>%
+  mutate(skewdiff = skew_percentile_TRUE - skew_percentile_FALSE,
+         simpdiff= simpson_percentile_TRUE - simpson_percentile_FALSE,
+         found_all = (found_all_TRUE + found_all_FALSE) == 2)
+
+ggplot(data = singletons_effect, aes(x = skew_percentile_FALSE, y = skew_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  facet_wrap(vars(found_all))
+
+ggplot(data = singletons_effect, aes(x = simpson_percentile_FALSE, y = simpson_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  facet_wrap(vars(found_all))
+
+```
+
+The rarefaction-inflated datasets are strongly // the raw vectors.
+They have more extreme skewness and evenness values, relative to their feasible sets, than the raw vectors.
+This is almost always true for evenness, with a little more noise in the skewness signal.
+But either way, very strong.
+
+# Manipulations
+# MACD
+
+```{r load macd}
+cache_loc = "macdb"
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+
+all_di_macd <- readd(all_di_manip, cache = cache) 
+macd_dat <- readd(dat_s_dat_macdb, cache = cache)
+
+DBI::dbDisconnect(db)
+rm(cache)
+
+macd_dat <- macd_dat %>%
+  group_by(site, dat, singletons, sim, source) %>%
+  summarize(s0 = max(rank),
+            n0 = sum(abund)) %>%
+  ungroup()
+
+all_di_macd <- left_join(all_di_macd, macd_dat, by = c("site", "dat", "singletons", "sim", "source")) %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples)) %>%
+  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
+  mutate(found_all = prop_found==1)
+
+ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()
+
+ggplot(data = filter(all_di, !singletons), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, !singletons), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()
+
+```
+
+Here are the distributions of skew and evenness, overall.
+
+```{r macd overall}
+
+ggplot(data = all_di_macd, aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(found_all), scales = "free_y")
+
+ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(found_all), scales = "free_y")
+```
+
+Here is how manipulation affects things:
+
+```{r macd ctrlcomp, fig.dim = c(4,4)}
+
+macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)
+
+colnames(macd_comparisons) <- c("studyID", "control", "site")
+macd_comparisons <- macd_comparisons %>%
+  mutate(site = as.character(site), control = as.character(control))
+
+cc_di <- all_di_macd %>%
+  filter(singletons == FALSE, treatment == "comparison") %>%
+  left_join(macd_comparisons, by = c("studyID", "site")) %>%
+  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
+  rename(comparison = site) %>%
+  mutate(ctrl_skew_percentile = NA,
+         ctrl_simpson_percentile = NA)
+
+for(i in 1:nrow(cc_di)) {
+
+  control_row <- filter(all_di_macd, site == cc_di$control[i], singletons == F) %>%
+    unique()
+  if(nrow(control_row) >0 ) {
+    cc_di$ctrl_simpson_percentile[i] <- control_row$simpson_percentile
+    cc_di$ctrl_skew_percentile[i] <- control_row$skew_percentile
+  }
+}
+
+cc_di <- cc_di %>%
+  mutate(simpson_change = simpson_percentile - ctrl_simpson_percentile,
+         skew_change = skew_percentile - ctrl_skew_percentile)
+
+ggplot(data = cc_di, aes(x = skew_percentile, y = ctrl_skew_percentile)) +
+  geom_point(alpha = .5) +
+  #  xlim(0, 100) +
+  # ylim(0, 100) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green")
+
+ggplot(data = cc_di, aes(x = simpson_percentile, y = ctrl_skew_percentile)) +
+  geom_point(alpha = .5) +
+  xlim(0, 100) +
+  ylim(0, 100) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green")
+
+ggplot(data = cc_di, aes(x = simpson_change)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(data = cc_di, aes(x = skew_change)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(data = cc_di, aes(x = ctrl_simpson_percentile, y = simpson_change)) +
+  geom_point(alpha = .3) +
+  geom_hline(yintercept = 0) +
+  theme_bw()
+
+ggplot(data = cc_di, aes(x = ctrl_skew_percentile, y = skew_change)) +
+  geom_point(alpha = .3) +
+  geom_hline(yintercept = 0) +
+  theme_bw()
+
+print(t.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T)
+)
+print(t.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T)
+)
+
+print(wilcox.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T))
+print(wilcox.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T))
+
+```
+
+Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?)
+
+# Portal plant manips
+
+```{r load pp}
+cache_loc = "portal_plants_manip"
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+
+all_di_p<- readd(all_di_manip, cache = cache)
+
+all_di_p <- all_di_p %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples)) %>%
+  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
+  mutate(found_all = prop_found==1)
+
+DBI::dbDisconnect(db)
+rm(cache)
+```
+
+Nsamples, singletons
+
+```{r pp overall}
+# 
+# ggplot(data = all_di_p, aes(x = nsamples)) +
+#   geom_histogram(bins = 100) +
+#   theme_bw() +
+#   geom_vline(xintercept = 2000)
+# 
+# all_di_p <- filter(all_di_p, nsamples >= 2000)
+
+ggplot(data = all_di_p, aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(found_all), scales = "free_y")
+
+ggplot(data = all_di_p, aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(found_all), scales = "free_y")
+# 
+# pp_singletons_effect <- all_di_p %>%
+#   select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>%
+#   tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile"))
+# 
+# ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) +
+#   geom_point(alpha = .1) +
+#   geom_abline(intercept = 0, slope = 1, color = "green") +
+#   theme_bw()
+# 
+# 
+# ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) +
+#   geom_point(alpha = .1) +
+#   geom_abline(intercept = 0, slope = 1, color = "green") +
+#   theme_bw()
+```
+
+By treatment, season
+
+```{r portal trtmt}
+ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(season, treatment), scales = "free_y")
+
+ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_wrap(vars(season))
+
+ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(season, treatment), scales = "free_y")
+
+ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
+  geom_boxplot() +
+  theme_bw() +
+  facet_wrap(vars(season))
+```
+
+<!-- By year -->
+
+<!-- ```{r plants year, fig.height = 25, fig.width = 5} -->
+
+<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + -->
+<!--   geom_boxplot() + -->
+<!--   theme_bw() + -->
+<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
+<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + -->
+<!--   geom_boxplot() + -->
+<!--   theme_bw() + -->
+<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
+<!-- ``` -->
+
+Median
+```{r pp median, fig.width = 12, fig.height = 12}
+
+pp_median <- all_di_p %>%
+  filter(singletons == F) %>%
+  group_by(season, year, treatment) %>%
+  summarize(skew_percentile = median(skew_percentile),
+            simpson_percentile = median(simpson_percentile)) %>%
+  ungroup() %>%
+  tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile))
+
+sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Skew Ctrl v Exclosure") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  xlim(40, 100) +
+  ylim(40, 100)
+
+sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Skew Ctrl v Removal") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  xlim(40, 100) +
+  ylim(40, 100)
+
+gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2)
+
+sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Simpson Ctrl v Exclosure") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  xlim(0, 40) +
+  ylim(0, 40)
+
+sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) +
+  geom_point(alpha = .5) +
+  facet_wrap(vars(season)) +
+  theme_bw() +
+  ggtitle("Simpson Ctrl v Removal") +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  xlim(0, 40) +
+  ylim(0, 40)
+
+gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2)
+```

### 2020-02-27 analysis/reports/found_all.Rmd
found all report

---
title: "Synthesis report - found all samples"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1)
```

There is some weird behavior where, for datasets where all samples were found, we do not see the disproportionately common extreme %ile values. I see a couple of reasons for this:
- very small communities are naturally bizarre and not super meaningful
- there's something squirrely with %ile

# Distribution of percentile values

## Skewness

Here is the overall distribution of skewness, and if we split based on whether we found all the samples:
```{r skew percentiles}
ggplot(filter(all_di, singletons == F), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)
ggplot(filter(all_di, singletons == F), aes(x = skew_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(found_all), scales = "free_y")
```

When we found all the samples, the percentiles are more evenly distributed. I do not read much into the spike at 0 for those communities, because skewness is bizarre for very small communities.

Here is how skewness maps with S and N, *filtered to communities where we found all samples*:
```{r skew v s and n}

ggplot(filter(all_di, singletons == F, found_all), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

# ggplot(filter(all_di, singletons == F), aes(x = log(n0/s0), y = skew_percentile, color = prop_found)) +
#   geom_point() +
#   theme_bw() +
#   scale_color_viridis_c(option = "plasma", end = .9, direction = -1) +
#   theme(legend.position = "top")

```

So I'm pretty sure the spike at 0 is the communities with 1 or 2 species, for which we shouldn't be calculating skewness anyway.

Here is how the histogram changes as we bin the lognparts into 5s:

```{r binned nparts, fig.dim = c(10,10)}
all_di <- all_di %>%
  mutate(nparts_binned = as.factor(ceiling(log_nparts / 5) * 5))

ggplot(filter(all_di, !singletons, s0 >= 3), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(nparts_binned), scales = "free_y")

```

## Simpson

Here is the overall evenness distribution, and split by whether we found 'em all:

```{r simpson percentiles}
ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
  geom_histogram(bins = 100) +
  theme_bw() +
  geom_hline(yintercept = .01)

ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile)) +
  theme_bw() +
  geom_histogram(bins = 100) +
  facet_wrap(vars(found_all))

```

Simpson is less evenly distributed than skewness. Again, where we found them all, we don't see the disproportionately common low percentile values.

Here is how Simpson behaves in S and N space where we found them all:

```{r even v s and n, fig.dim = c(10,10)}

ggplot(filter(all_di, singletons == F, found_all), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "plasma", end = .9)

```

There is nothing to learn when s0 = 1 or really 2.

Here is how the histogram changes as we bin the lognparts into 5s:

```{r binned nparts even, fig.dim = c(10,10)}

ggplot(filter(all_di, !singletons, s0 >= 3), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(nparts_binned), scales = "free_y")

```

!!!!! OK SO!!!!!

It is NOT ABOUT whether we found all the samples. It is that the %iles look pretty UNIFORMLY DISTRIBUTED for communities with up to somewhere from `r exp(10)` to `r exp(15)` elements in the feasible set. Then the extremes emerge: high for skew and low for Simpson.

We expect issues of small N, but not for communities even so large. So if there are even 150 elements in the FS, we expect to be able to identify some kind of central tendency.

```{r nparts classification}

all_di <-  mutate(all_di, more_than_10 = log_nparts >= 10)
ggplot(filter(all_di, !singletons), aes(x = log(s0), y = log(n0), color = more_than_10)) +
  geom_point() +
  theme_bw()

```

Communities with more than `r exp(10)` parts in the FS account for about `r 100*mean(filter(all_di, !singletons)$more_than_10)`% of communities.

```{r nparts by dat, fig.dim = c(8,8)}

all_di <-  mutate(all_di, more_than_10 = log_nparts >= 10)
ggplot(filter(all_di, !singletons), aes(x = (s0), y = (n0), color = more_than_10)) +
  geom_point() +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free")

filter(all_di, !singletons, s0 >= 3) %>%
  group_by(dat) %>%
  summarize(prop_more_than_10 = mean(more_than_10),
            nsites = length(unique(site))) %>%
  ungroup() 
```

```{r nparts and dat, fig.dim = c(15,15)}
for(i in 1:nrow(all_di)) {
  if(as.numeric(levels(all_di$nparts_binned)[as.numeric(all_di$nparts_binned[i])]) >= 50) {
    all_di$nparts_binned[i] <- 50
  }
}

all_di$nparts_binned <- as.factor(as.numeric(as.character(all_di$nparts_binned)))

ggplot(filter(all_di, !singletons, s0 >= 3), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(nparts_binned, dat), scales = "free_y", ncol = length(unique(all_di$dat)), drop = F)

ggplot(filter(all_di, !singletons, s0 >= 3), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(nparts_binned, dat), scales = "free_y", ncol = length(unique(all_di$dat)), drop = F)

```

### 2020-02-27 analysis/reports/found_all.Rmd
add fia small

@@
 
-```{r nparts classification}
+```{r nparts classification, fig.dim = c(10, 5)}
 
 all_di <-  mutate(all_di, more_than_10 = log_nparts >= 10)
-ggplot(filter(all_di, !singletons), aes(x = log(s0), y = log(n0), color = more_than_10)) +
+ggplot(filter(all_di, !singletons), aes(x = log(s0), y = log(n0), color = dat)) +
   geom_point() +
-  theme_bw()
+  theme_bw() +
+  scale_color_viridis_d() +
+  facet_wrap(vars(more_than_10), scales = "fixed") +
+  theme(legend.position = "top")
 
@@
 
-```{r nparts and dat, fig.dim = c(15,15)}
+```{r nparts and dat, fig.dim = c(15,15), include = F}
 for(i in 1:nrow(all_di)) {

### 2020-02-27 R/data_handling.R

@@ -58,6 +58,48 @@ filter_fia <- function(storage_path = here::here("working-data", "abund_data"), 
   }
 }
 
+
+#' Filter FIA data - tiny communities
+#'
+#' Following White et al 2012, filtering FIA data to sites with > 10 species. This brings it from 103343 sites to 10355.
+#'
+#' @param min_s0 min s0
+#' @param max_s0 max s0
+#' @param max_comm  max ncommunities
+#' @param storage_path where to put it
+#' @param save save it?
+#'
+#' @return nothing
+#' @export
+#'
+#' @importFrom dplyr filter mutate
+filter_fia_small <- function(min_s0 = 3, max_s0 = 9, max_comm = 10000, storage_path = here::here("working-data", "abund_data"), save = TRUE) {
+
+
+  fia <- load_dataset("fia", storage_path = storage_path)
+
+  fia_sv <- get_statevars(fia) %>%
+    dplyr::filter(s0 >= min_s0) %>%
+    dplyr::filter(s0 <= max_s0)
+
+  if(nrow(fia_sv) > max_comm) {
+    set.seed(1977)
+    fia_sv <- fia_sv[ sample.int(nrow(fia_sv), size = max_comm, replace = F), ]
+  }
+
+
+  fia <- fia %>%
+    dplyr::filter(site %in% fia_sv$site) %>%
+    dplyr::mutate(dat = "fia_small")
+
+  if(save) {
+
+    write.csv(fia, file.path(storage_path, "fia_small_spab.csv"), row.names = F)
+
+  }
+}
+
+
 #' Load a dataset
 #'
 #' @param dataset_name "bbs", "fia", "gentry", "mcdb", "portal_plants", "misc_abund_short", or "misc_abund"

### 2020-02-27 R/download_data.R

@@ -35,12 +35,15 @@ download_data <- function(from_url = FALSE, storage_path = here::here("working-d
 
     filter_miscabund(storage_path = file.path(storage_path, "abund_data"))
     filter_fia(storage_path = file.path(storage_path, "abund_data"))
+    filter_fia_small(storage_path = file.path(storage_path, "abund_data"))
 
   } else {
     file.copy(inst_path, storage_path, recursive = T)
 
     filter_miscabund(storage_path = file.path(storage_path, "abund_data"))
     filter_fia(storage_path = file.path(storage_path, "abund_data"))
+    filter_fia_small(storage_path = file.path(storage_path, "abund_data"))
+
   }
 }
 

### 2020-03-18 analysis/reports/found_all.Rmd
run portal pipeline

@@
 ```{r skew percentiles}
-ggplot(filter(all_di, singletons == F), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
+ggplot(filter(all_di, singletons == F, s0 >= 3), aes(x = skew_percentile, y =..count.. / sum(..count..))) +
   geom_histogram(bins = 100) +
@@
   geom_hline(yintercept = .01)
-ggplot(filter(all_di, singletons == F), aes(x = skew_percentile)) +
+ggplot(filter(all_di, singletons == F, s0 >= 3), aes(x = skew_percentile)) +
   theme_bw() +
@@
 
-ggplot(filter(all_di, singletons == F, found_all), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
+ggplot(filter(all_di, singletons == F, found_all, s0 >= 3), aes(x = log(s0), y = log(n0), color = skew_percentile)) +
   geom_point(alpha = .5) +
@@
 
-So I'm pretty sure the spike at 0 is the communities with 1 or 2 species, for which we shouldn't be calculating skewness anyway.
-
-Here is how the histogram changes as we bin the lognparts into 5s:
+Here is how the histogram changes as we bin the lognparts into 2s:
 
@@
 all_di <- all_di %>%
-  mutate(nparts_binned = as.factor(ceiling(log_nparts / 5) * 5))
+  mutate(nparts_binned = as.factor(ceiling(log_nparts / 2) * 2))
+
+for(i in 1:nrow(all_di)) {
+  if(as.numeric(levels(all_di$nparts_binned)[as.numeric(all_di$nparts_binned[i])]) >= 25) {
+    all_di$nparts_binned[i] <- 26
+  }
+}
 
@@
 ```{r simpson percentiles}
-ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
+ggplot(filter(all_di, singletons == F, s0 >= 2), aes(x = simpson_percentile, y =..count.. / sum(..count..))) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(filter(all_di, singletons == F), aes(x = simpson_percentile)) +
+ggplot(filter(all_di, singletons == F, s0 >= 2), aes(x = simpson_percentile)) +
   theme_bw() +
@@
 
-```{r even v s and n, fig.dim = c(10,10)}
+```{r even v s and n}
 
-ggplot(filter(all_di, singletons == F, found_all), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
+ggplot(filter(all_di, singletons == F, found_all, s0 >= 2), aes(x = log(s0), y = log(n0), color = simpson_percentile)) +
   geom_point(alpha = .5) +
@@
 
-There is nothing to learn when s0 = 1 or really 2.
-
 Here is how the histogram changes as we bin the lognparts into 5s:
@@
 
-ggplot(filter(all_di, !singletons, s0 >= 3), aes(x = simpson_percentile)) +
+ggplot(filter(all_di, !singletons, s0 >= 2), aes(x = simpson_percentile)) +
   geom_histogram(bins = 100) +
@@
 
-```{r nparts and dat, fig.dim = c(15,15), include = F}
+```{r nparts and dat, fig.dim = c(15,15)}
 for(i in 1:nrow(all_di)) {
@@
 ```
+
+```{r nparts variability}
+
+ggplot(filter(all_di, !singletons, s0 >= 3, !is.infinite(skew_sd), !is.infinite(skew_mean), nsamples >2), aes(x = log_nparts, y = (skew_sd/skew_mean), color = skew_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_vline(xintercept = 10) +
+  scale_color_viridis_c() +
+  ylim(-0, 1) +
+  xlim(0, 100)
+
+ggplot(filter(all_di, !singletons, s0 >= 3, !is.infinite(simpson_sd), !is.infinite(simpson_sd), nsamples >2), aes(x = log_nparts, y = (simpson_sd/simpson_mean), color = simpson_percentile)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_vline(xintercept = 10) +
+  scale_color_viridis_c() +
+  xlim(0, 100)
+
+```
+
+```{r mean v sd}
+
+ggplot(filter(all_di, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = skew_mean, y = skew_sd)) +
+  geom_point() +
+  theme_bw()
+
+all_di <- all_di %>%
+  mutate(skew_cv = skew_sd / abs(skew_mean),
+         simpson_cv = simpson_sd / abs(simpson_mean))
+
+ggplot(filter(all_di, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = skew_mean, y = skew_sd)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c()
+
+ggplot(filter(all_di, !is.infinite(simpson_mean), !is.infinite(simpson_sd)), aes(x = simpson_mean, y = simpson_sd)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c()
+
+```
+
+Mean and sd are correlated.
+
+```{r cv in space}
+
+ggplot(filter(all_di, !singletons, !is.infinite(skew_mean), s0 >= 3, !is.infinite(skew_sd), nparts > 2), aes(log(s0), log(n0), color = log(skew_cv))) +
+  geom_point(alpha = .15) +
+  scale_color_viridis_c(option = "plasma", end = .9) +
+  theme_bw() 
+# +
+  # facet_wrap(vars(more_than_10))
+
+ggplot(filter(all_di, !singletons, !is.infinite(simpson_mean), s0 >= 2, !is.infinite(simpson_mean), nparts > 2), aes(log(s0), log(n0), color = log(simpson_cv))) +
+  geom_point(alpha = .15) +
+  scale_color_viridis_c(option = "plasma", end = .9) +
+  theme_bw() 
+# +
+  # facet_wrap(vars(more_than_10))
+```
+
+Coefficients of variation for skewness and evenness follow clear S and N gradients.
+
+```{r cv v nparts}
+ggplot(filter(all_di, !singletons, !is.infinite(skew_mean), s0 >= 3, !is.infinite(skew_sd), nparts > 2), aes(x = log_nparts, y = skew_cv)) +
+  geom_point(alpha = .05) +
+  theme_bw() +
+  geom_vline(xintercept = 10) +
+  xlim(0, 75)
+
+ggplot(filter(all_di, !singletons, !is.infinite(simpson_mean), s0 >= 2, !is.infinite(simpson_mean), nparts > 2), aes(x = log_nparts, y = simpson_cv)) +
+  geom_point(alpha = .05) +
+  theme_bw() +
+  geom_vline(xintercept = 10) +
+  xlim(0, 75)
+```
+
+The CV scans with nparts and drops off suspiciously right around the same place where the threshold shows up for percentile.
+
+```{r cv v percentile}
+all_di <- all_di %>%
+  group_by_all() %>%
+  mutate(log_nparts_thresh = min(log_nparts, 5)) %>%
+  ungroup()
+
+ggplot(filter(all_di, !singletons, !is.infinite(skew_mean), s0 >= 3, !is.infinite(skew_sd), nparts > 2), aes(y = skew_cv, x = skew_percentile, color = log_nparts_thresh)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  facet_wrap(vars(more_than_10)) +
+  scale_color_viridis_c()
+
+ggplot(filter(all_di, !singletons, !is.infinite(simpson_mean), s0 >= 2, !is.infinite(simpson_sd), nparts > 2), aes(y = simpson_cv, x = simpson_percentile, color = log_nparts_thresh)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  facet_wrap(vars(more_than_10)) +
+  scale_color_viridis_c() 
+```

### 2020-03-18 analysis/reports/synthesis.Rmd
run portal pipeline

@@
 
-# Manipulations
-# MACD
+<!-- # Manipulations -->
+<!-- # MACD -->
 
-```{r load macd}
-cache_loc = "macdb"
+<!-- ```{r load macd, include =F} -->
+<!-- cache_loc = "macdb" -->
 
-## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
-cache <- storr::storr_dbi("datatable", "keystable", db)
+<!-- ## Set up the cache and config -->
+<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite"))) -->
+<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->
 
-all_di_macd <- readd(all_di_manip, cache = cache) 
-macd_dat <- readd(dat_s_dat_macdb, cache = cache)
+<!-- all_di_macd <- readd(all_di_obs, cache = cache)  -->
+<!-- all_di_macd_manip <- readd(all_di_manip, cache = cache) -->
+<!-- macd_dat <- readd(dat_s_dat_macdb, cache = cache) -->
 
-DBI::dbDisconnect(db)
-rm(cache)
+<!-- DBI::dbDisconnect(db) -->
+<!-- rm(cache) -->
 
-macd_dat <- macd_dat %>%
-  group_by(site, dat, singletons, sim, source) %>%
-  summarize(s0 = max(rank),
-            n0 = sum(abund)) %>%
-  ungroup()
+<!-- all_di_macd <- all_di_macd %>% -->
+<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
+<!--          log_nsamples = log(nsamples)) %>% -->
+<!--   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
+<!--   mutate(found_all = prop_found==1) -->
+<!-- #  -->
+<!-- # all_di_macd_manip <- all_di_macd_manip %>% -->
+<!-- #   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
+<!-- #          log_nsamples = log(nsamples)) %>% -->
+<!-- #   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
+<!-- #   mutate(found_all = prop_found==1) -->
 
-all_di_macd <- left_join(all_di_macd, macd_dat, by = c("site", "dat", "singletons", "sim", "source")) %>%
-  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
-         log_nsamples = log(nsamples)) %>%
-  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
-  mutate(found_all = prop_found==1)
+<!-- ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw() -->
 
-ggplot(data = all_di, aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = all_di_macd, aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()
+<!-- ggplot(data = filter(all_di, !singletons), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, !singletons), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw() -->
 
-ggplot(data = filter(all_di, !singletons), aes(x = log(s0), y = log(n0))) + geom_point(alpha = .1) + geom_point(data = filter(all_di_macd, !singletons), aes(x = log(s0), y = log(n0)), color = "blue", alpha = .9) + theme_bw()
+<!-- ``` -->
 
-```
+<!-- Here are the distributions of skew and evenness, overall. -->
 
-Here are the distributions of skew and evenness, overall.
+<!-- ```{r macd overall, include =F} -->
 
-```{r macd overall}
+<!-- ggplot(data = all_di_macd, aes(x = skew_percentile)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   theme_bw() + -->
+<!--   facet_wrap(vars(found_all), scales = "free_y") -->
 
-ggplot(data = all_di_macd, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(found_all), scales = "free_y")
+<!-- ggplot(data = all_di_macd, aes(x = simpson_percentile)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   theme_bw() + -->
+<!--   facet_wrap(vars(found_all), scales = "free_y") -->
+<!-- ``` -->
 
-ggplot(data = all_di_macd, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(found_all), scales = "free_y")
-```
+<!-- Here is how manipulation affects things: -->
 
-Here is how manipulation affects things:
+<!-- ```{r macd ctrlcomp, fig.dim = c(4,4), include =F} -->
 
-```{r macd ctrlcomp, fig.dim = c(4,4)}
+<!-- ggplot(data = all_di_macd_manip, aes(x = skew_percentile, y = ctrl_skew_percentile)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!--   #  xlim(0, 100) + -->
+<!--   # ylim(0, 100) + -->
+<!--   theme_bw() + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->
 
-macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)
+<!-- ggplot(data = all_di_macd_manip, aes(x = simpson_percentile, y = ctrl_skew_percentile)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!--   xlim(0, 100) + -->
+<!--   ylim(0, 100) + -->
+<!--   theme_bw() + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") -->
 
-colnames(macd_comparisons) <- c("studyID", "control", "site")
-macd_comparisons <- macd_comparisons %>%
-  mutate(site = as.character(site), control = as.character(control))
+<!-- ggplot(data = all_di_macd_manip, aes(x = simpson_change)) + -->
+<!--   geom_histogram() + -->
+<!--   theme_bw() -->
 
-cc_di <- all_di_macd %>%
-  filter(singletons == FALSE, treatment == "comparison") %>%
-  left_join(macd_comparisons, by = c("studyID", "site")) %>%
-  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
-  rename(comparison = site) %>%
-  mutate(ctrl_skew_percentile = NA,
-         ctrl_simpson_percentile = NA)
+<!-- ggplot(data = all_di_macd_manip, aes(x = skew_change)) + -->
+<!--   geom_histogram() + -->
+<!--   theme_bw() -->
 
-for(i in 1:nrow(cc_di)) {
+<!-- ggplot(data = all_di_macd_manip, aes(x = ctrl_simpson_percentile, y = simpson_change)) + -->
+<!--   geom_point(alpha = .3) + -->
+<!--   geom_hline(yintercept = 0) + -->
+<!--   theme_bw() -->
 
-  control_row <- filter(all_di_macd, site == cc_di$control[i], singletons == F) %>%
-    unique()
-  if(nrow(control_row) >0 ) {
-    cc_di$ctrl_simpson_percentile[i] <- control_row$simpson_percentile
-    cc_di$ctrl_skew_percentile[i] <- control_row$skew_percentile
-  }
-}
+<!-- ggplot(data = all_di_macd_manip, aes(x = ctrl_skew_percentile, y = skew_change)) + -->
+<!--   geom_point(alpha = .3) + -->
+<!--   geom_hline(yintercept = 0) + -->
+<!--   theme_bw() -->
 
-cc_di <- cc_di %>%
-  mutate(simpson_change = simpson_percentile - ctrl_simpson_percentile,
-         skew_change = skew_percentile - ctrl_skew_percentile)
+<!-- print(t.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T) -->
+<!-- ) -->
+<!-- print(t.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T) -->
+<!-- ) -->
 
-ggplot(data = cc_di, aes(x = skew_percentile, y = ctrl_skew_percentile)) +
-  geom_point(alpha = .5) +
-  #  xlim(0, 100) +
-  # ylim(0, 100) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
+<!-- print(wilcox.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T)) -->
+<!-- print(wilcox.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T)) -->
 
-ggplot(data = cc_di, aes(x = simpson_percentile, y = ctrl_skew_percentile)) +
-  geom_point(alpha = .5) +
-  xlim(0, 100) +
-  ylim(0, 100) +
-  theme_bw() +
-  geom_abline(intercept = 0, slope = 1, color = "green")
+<!-- ``` -->
 
-ggplot(data = cc_di, aes(x = simpson_change)) +
-  geom_histogram() +
-  theme_bw()
+<!-- Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?) -->
 
-ggplot(data = cc_di, aes(x = skew_change)) +
-  geom_histogram() +
-  theme_bw()
+<!-- # Portal plant manips -->
 
-ggplot(data = cc_di, aes(x = ctrl_simpson_percentile, y = simpson_change)) +
-  geom_point(alpha = .3) +
-  geom_hline(yintercept = 0) +
-  theme_bw()
+<!-- ```{r load pp, include = F} -->
+<!-- cache_loc = "portal_plants_manip" -->
 
-ggplot(data = cc_di, aes(x = ctrl_skew_percentile, y = skew_change)) +
-  geom_point(alpha = .3) +
-  geom_hline(yintercept = 0) +
-  theme_bw()
+<!-- ## Set up the cache and config -->
+<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite"))) -->
+<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->
 
-print(t.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T)
-)
-print(t.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T)
-)
+<!-- all_di_p<- readd(all_di_manip, cache = cache)  -->
 
-print(wilcox.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T))
-print(wilcox.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T))
+<!-- all_di_p <- all_di_p %>% -->
+<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
+<!--          log_nsamples = log(nsamples)) %>% -->
+<!--   mutate(prop_found = exp(log_nsamples - log_nparts)) %>% -->
+<!--   mutate(found_all = prop_found==1) -->
 
-```
+<!-- DBI::dbDisconnect(db) -->
+<!-- rm(cache) -->
+<!-- ``` -->
 
-Change is going to be bounded at 100 and 0: you can't go up or down from there. (Another argument for increasing the number of samples?)
+<!-- Nsamples, singletons -->
 
-# Portal plant manips
+<!-- ```{r pp overall, include = F} -->
+<!-- #  -->
+<!-- # ggplot(data = all_di_p, aes(x = nsamples)) + -->
+<!-- #   geom_histogram(bins = 100) + -->
+<!-- #   theme_bw() + -->
+<!-- #   geom_vline(xintercept = 2000) -->
+<!-- #  -->
+<!-- # all_di_p <- filter(all_di_p, nsamples >= 2000) -->
 
-```{r load pp}
-cache_loc = "portal_plants_manip"
+<!-- ggplot(data = all_di_p, aes(x = skew_percentile)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   theme_bw() + -->
+<!--   facet_wrap(vars(found_all), scales = "free_y") -->
 
-## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
-cache <- storr::storr_dbi("datatable", "keystable", db)
+<!-- ggplot(data = all_di_p, aes(x = simpson_percentile)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   theme_bw() + -->
+<!--   facet_wrap(vars(found_all), scales = "free_y") -->
+<!-- #  -->
+<!-- # pp_singletons_effect <- all_di_p %>% -->
+<!-- #   select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>% -->
+<!-- #   tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile")) -->
+<!-- #  -->
+<!-- # ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) + -->
+<!-- #   geom_point(alpha = .1) + -->
+<!-- #   geom_abline(intercept = 0, slope = 1, color = "green") + -->
+<!-- #   theme_bw() -->
+<!-- #  -->
+<!-- #  -->
+<!-- # ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) + -->
+<!-- #   geom_point(alpha = .1) + -->
+<!-- #   geom_abline(intercept = 0, slope = 1, color = "green") + -->
+<!-- #   theme_bw() -->
+<!-- ``` -->
 
-all_di_p<- readd(all_di_manip, cache = cache)
+<!-- By treatment, season -->
 
-all_di_p <- all_di_p %>%
-  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
-         log_nsamples = log(nsamples)) %>%
-  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
-  mutate(found_all = prop_found==1)
-
-DBI::dbDisconnect(db)
-rm(cache)
-```
-
-Nsamples, singletons
-
-```{r pp overall}
-# 
-# ggplot(data = all_di_p, aes(x = nsamples)) +
-#   geom_histogram(bins = 100) +
-#   theme_bw() +
-#   geom_vline(xintercept = 2000)
-# 
-# all_di_p <- filter(all_di_p, nsamples >= 2000)
-
-ggplot(data = all_di_p, aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(found_all), scales = "free_y")
-
-ggplot(data = all_di_p, aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(found_all), scales = "free_y")
-# 
-# pp_singletons_effect <- all_di_p %>%
-#   select(singletons, skew_percentile, simpson_percentile, year, plot, treatment, season) %>%
-#   tidyr::pivot_wider(names_from = singletons, values_from = c("skew_percentile", "simpson_percentile"))
-# 
-# ggplot(data = pp_singletons_effect, aes(x = skew_percentile_FALSE, y  = skew_percentile_TRUE)) +
-#   geom_point(alpha = .1) +
-#   geom_abline(intercept = 0, slope = 1, color = "green") +
-#   theme_bw()
-# 
-# 
-# ggplot(data = pp_singletons_effect, aes(x = simpson_percentile_FALSE, y  = simpson_percentile_TRUE)) +
-#   geom_point(alpha = .1) +
-#   geom_abline(intercept = 0, slope = 1, color = "green") +
-#   theme_bw()
-```
-
-By treatment, season
-
-```{r portal trtmt}
-ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(season, treatment), scales = "free_y")
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(season))
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  theme_bw() +
-  facet_wrap(vars(season, treatment), scales = "free_y")
-
-ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) +
-  geom_boxplot() +
-  theme_bw() +
-  facet_wrap(vars(season))
-```
-
-<!-- By year -->
-
-<!-- ```{r plants year, fig.height = 25, fig.width = 5} -->
+<!-- ```{r portal trtmt, include =F} -->
+<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = skew_percentile)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   theme_bw() + -->
+<!--   facet_wrap(vars(season, treatment), scales = "free_y") -->
 
@@
 <!--   theme_bw() + -->
-<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
+<!--   facet_wrap(vars(season)) -->
+
+<!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = simpson_percentile)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   theme_bw() + -->
+<!--   facet_wrap(vars(season, treatment), scales = "free_y") -->
+
 <!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + -->
@@
 <!--   theme_bw() + -->
-<!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") -->
+<!--   facet_wrap(vars(season)) -->
 <!-- ``` -->
 
-Median
-```{r pp median, fig.width = 12, fig.height = 12}
+<!-- <!-- By year --> -->
 
-pp_median <- all_di_p %>%
-  filter(singletons == F) %>%
-  group_by(season, year, treatment) %>%
-  summarize(skew_percentile = median(skew_percentile),
-            simpson_percentile = median(simpson_percentile)) %>%
-  ungroup() %>%
-  tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile))
+<!-- <!-- ```{r plants year, fig.height = 25, fig.width = 5} --> -->
 
-sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
+<!-- <!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = skew_percentile)) + --> -->
+<!-- <!--   geom_boxplot() + --> -->
+<!-- <!--   theme_bw() + --> -->
+<!-- <!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") --> -->
+<!-- <!-- ggplot(data = filter(all_di_p, singletons == F), aes(x = treatment, y = simpson_percentile)) + --> -->
+<!-- <!--   geom_boxplot() + --> -->
+<!-- <!--   theme_bw() + --> -->
+<!-- <!--   facet_grid(rows = vars(year), cols = vars(season), scales = "free_y") --> -->
+<!-- <!-- ``` --> -->
+
+<!-- Median -->
+<!-- ```{r pp median, fig.width = 12, fig.height = 12, include =F} -->
+
+<!-- pp_median <- all_di_p %>% -->
+<!--   filter(singletons == F) %>% -->
+<!--   group_by(season, year, treatment) %>% -->
+<!--   summarize(skew_percentile = median(skew_percentile), -->
+<!--             simpson_percentile = median(simpson_percentile)) %>% -->
+<!--   ungroup() %>% -->
+<!--   tidyr::pivot_wider(names_from = treatment, values_from = c(skew_percentile, simpson_percentile)) -->
+
+<!-- sk_x <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_exclosure)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!--   facet_wrap(vars(season)) + -->
+<!--   theme_bw() + -->
+<!--   ggtitle("Skew Ctrl v Exclosure") + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
+<!--   xlim(40, 100) + -->
+<!--   ylim(40, 100) -->
+
+<!-- sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!--   facet_wrap(vars(season)) + -->
+<!--   theme_bw() + -->
+<!--   ggtitle("Skew Ctrl v Removal") + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
+<!--   xlim(40, 100) + -->
+<!--   ylim(40, 100) -->
+
+<!-- gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2) -->
+
+<!-- sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!--   facet_wrap(vars(season)) + -->
+<!--   theme_bw() + -->
+<!--   ggtitle("Simpson Ctrl v Exclosure") + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
+<!--   xlim(0, 40) + -->
+<!--   ylim(0, 40) -->
+
+<!-- sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) + -->
+<!--   geom_point(alpha = .5) + -->
+<!--   facet_wrap(vars(season)) + -->
+<!--   theme_bw() + -->
+<!--   ggtitle("Simpson Ctrl v Removal") + -->
+<!--   geom_abline(intercept = 0, slope = 1, color = "green") + -->
+<!--   xlim(0, 40) + -->
+<!--   ylim(0, 40) -->
+
+<!-- gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2) -->
+<!-- ``` -->
+
+```{r nparts v rov}
+
+all_di_plot <- filter(all_di, !singletons)
+
+ggplot(all_di_plot, aes(x = log_nparts, y = simpson_mean)) +
+  geom_point(alpha = .1) +
   theme_bw() +
-  ggtitle("Skew Ctrl v Exclosure") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  xlim(40, 100) +
-  ylim(40, 100)
+  geom_vline(xintercept = 10)
 
-sk_r <- ggplot(data = pp_median, aes(x = skew_percentile_control, y = skew_percentile_removal)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
+ggplot(all_di_plot, aes(x = log_nparts, y = simpson_sd)) +
+  geom_point(alpha = .1) +
   theme_bw() +
-  ggtitle("Skew Ctrl v Removal") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  xlim(40, 100) +
-  ylim(40, 100)
+  geom_vline(xintercept = 10)
 
-gridExtra::grid.arrange(grobs = list(sk_x, sk_r), nrow = 2)
+ggplot(all_di_plot, aes(x = log_nparts, y = abs(simpson_sd/simpson_mean))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_vline(xintercept = 10)
 
-sp_x <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_exclosure)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
+ggplot(all_di_plot, aes(x = abs(simpson_sd/simpson_mean), y = simpson_percentile, color = log_nparts > 10)) +
+  geom_point(alpha = .05) +
   theme_bw() +
-  ggtitle("Simpson Ctrl v Exclosure") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  xlim(0, 40) +
-  ylim(0, 40)
+  scale_color_viridis_d(end = .8)
 
-sp_r <- ggplot(data = pp_median, aes(x = simpson_percentile_control, y = simpson_percentile_removal)) +
-  geom_point(alpha = .5) +
-  facet_wrap(vars(season)) +
+ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = skew_mean)) +
+  geom_point(alpha = .1) +
   theme_bw() +
-  ggtitle("Simpson Ctrl v Removal") +
-  geom_abline(intercept = 0, slope = 1, color = "green") +
-  xlim(0, 40) +
-  ylim(0, 40)
+  geom_vline(xintercept = 10)
 
-gridExtra::grid.arrange(grobs = list(sp_x, sp_r), nrow = 2)
+ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = skew_sd)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_vline(xintercept = 10)
+
+ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = log_nparts, y = abs(skew_sd/skew_mean))) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_vline(xintercept = 10)
+
+ggplot(filter(all_di_plot, s0 > 3, !is.infinite(skew_mean), !is.infinite(skew_sd)), aes(x = abs(skew_sd/skew_mean), y = skew_percentile, color = log_nparts > 10)) +
+  geom_point(alpha = .05) +
+  theme_bw() +
+  scale_color_viridis_d(end = .8) +
+  xlim(0,4)
 ```

### 2020-03-19 analysis/reports/rov.Rmd
run make_all_di on hpg

---
title: "ROV report"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(dat == "portal_plants")

all_diffs <- read.csv(here::here("all_diffs.csv"), stringsAsFactors = F)

all_diffs <- all_diffs %>%
  select(-X, -source)

all_di <- left_join(all_di, all_diffs)

all_di <- filter(all_di, s0 > 1)
```

# Datasets in S and N space

Here is where our communities fall in S and N space:

```{r datasets in s and n space}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point(alpha = .8) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_d()

```

Here is how that translates into the size of the feasible set:

```{r size of fs}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nparts)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)

```
And various metrics of the ROV of the feasible set:

```{r fs rov}

rov_long <- all_di %>%
  select(dat, site, singletons, s0, n0, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts) %>%
  tidyr::pivot_longer(cols = starts_with("mean"),
                      names_to = "rov_index",
                      values_to = "val")
rov_plots <- list()

for(i in 1:length(unique(rov_long$rov_index))) {
  rov_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log(s0), log(n0), color = val)) +
    geom_point() +
    theme_bw() +
    scale_color_viridis_c() +
    ggtitle(unique(rov_long$rov_index)[i])
}

gridExtra::grid.arrange(grobs = rov_plots)
```

Here is how ROV corresponds to nparts:

```{r rov lognparts}

rov_nparts_plots <- list()

for(i in 1:length(unique(rov_long$rov_index))) {
  rov_nparts_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val)) +
    geom_point() +
    theme_bw() +
    ggtitle(unique(rov_long$rov_index)[i])
}

gridExtra::grid.arrange(grobs = rov_nparts_plots)

```

### 2020-03-19 analysis/helper_scripts/make_all_di.R

@@ -4,6 +4,7 @@ library(ggplot2)
 library(scadsanalysis)
 
 all_di <- list()
+all_diffs <- list()
 datasets <- c("bbs", "fia_short", "gentry", "mcdb", "misc_abund_short", "portal_plants", "fia_small")
 
 #datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
@@ -28,9 +29,16 @@ for(i in 1:length(datasets)) {
 
   all_di[[i]] <- filter(all_di[[i]], source == "observed")
 
+  if("all_diffs" %in% cached(cache)) {
+    all_diffs[[i]] <- readd(all_diffs, cache = cache)
+
+    all_diffs[[i]] <- select(all_diffs[[i]], -source)
+
+    all_di[[i]] <- left_join(all_di[[i]], all_diffs[[i]])
+  }
   #this_dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
- # sv <- get_statevars(this_dat)
-#  all_di[[i]] <- left_join(all_di[[i]], sv, by = c("sim", "site", "source", "singletons", "dat"))
+  # sv <- get_statevars(this_dat)
+  #  all_di[[i]] <- left_join(all_di[[i]], sv, by = c("sim", "site", "source", "singletons", "dat"))
 
 
   DBI::dbDisconnect(db)

### 2020-03-19 analysis/reports/rov.Rmd
add fia_small

@@
   mutate(found_all = prop_found==1) %>%
-  filter(dat == "portal_plants")
+  filter(dat == "portal_plants") %>% 
+    mutate(binned_nparts = as.factor(ceiling(log_nparts/10)))
 
@@
 ```
+
+Exploring ways we might bin nparts:
+
+```{r nparts distribution}
+
+ggplot(filter(all_di, singletons == F), aes(log_nparts)) +
+  geom_histogram(binwidth = 10, boundary = 0, color = "black", alpha = 0) +
+  theme_bw()
+
+```
+
 And various metrics of the ROV of the feasible set:
@@
 rov_long <- all_di %>%
-  select(dat, site, singletons, s0, n0, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts) %>%
+  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts) %>%
   tidyr::pivot_longer(cols = starts_with("mean"),
@@
     theme_bw() +
-    ggtitle(unique(rov_long$rov_index)[i])
+    ggtitle(unique(rov_long$rov_index)[i]) +
+    geom_vline(xintercept = 10)
 }
@@
 ```
+
+If we bin nparts:
+
+```{r binned nparts ROV}
+
+rov_nparts_binned_plots <- list()
+
+for(i in 1:length(unique(rov_long$rov_index))) {
+  rov_nparts_binned_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(binned_nparts, val)) +
+    geom_boxplot() +
+    theme_bw()
+}
+
+gridExtra::grid.arrange(grobs = rov_nparts_binned_plots)
+```
+
+## Percentile distributions
+
+Overall:
+
+```{r percentiles overall}
+
+ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
+  geom_histogram(bins = 100, boundary = 0) +
+  theme_bw()
+
+ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100, boundary = 0) +
+  theme_bw()
+
+```
+
+Binned:
+
+```{r binned percentiles}
+
+ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
+  geom_histogram(bins = 100, boundary = 0) +
+  theme_bw() +
+  facet_wrap(vars(binned_nparts))
+
+```
+
+OK, these visualiations are pretty hard with this dataset (not very many small communities). Try after adding FIA?

### 2020-03-19 analysis/fia_small_pipeline.R

@@ -28,6 +28,12 @@ dat_plan <- drake_plan(
                                      singletons = !!c(TRUE, FALSE))),
   di = target(add_dis(fs),
               transform = map(fs)),
+  diffs = target(rep_diff_sampler(fs, ndraws = !!nresamples),
+                 transform = map(fs)),
+  diffs_summary = target(summarize_diffs(diffs),
+                         transform = map(diffs)),
+  all_diffs = target(dplyr::bind_rows(diffs_summary),
+                     transform = combine(diffs_summary)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),

### 2020-03-21 analysis/reports/rov.Rmd
run with fia short

@@
 
-all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+dis <- list.files(here::here("analysis", "results"), pattern = "all_di")
+all_di <- lapply(dis, FUN = function(di_df) return(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F)))
+all_di <- bind_rows(all_di)
 
@@
   mutate(found_all = prop_found==1) %>% 
-  filter(dat == "portal_plants") %>% 
     mutate(binned_nparts = as.factor(ceiling(log_nparts/10)))
 
-all_diffs <- read.csv(here::here("all_diffs.csv"), stringsAsFactors = F)
+diffs <- list.files(here::here("analysis", "results"), pattern = "diff_")
+all_diffs <- lapply(diffs, FUN = function(di_df) return(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F)))
+all_diffs <- bind_rows(all_diffs)
 
 all_diffs <- all_diffs %>%
-  select(-X, -source)
+  select(-source)
 

### 2020-03-21 analysis/fia_pipeline.R

@@ -8,6 +8,7 @@ datasets <- "fia_short"
 
 sites_list <- list_sites("fia_short")
 ndraws = 4000
+nresamples <- 4000
 #sites_list <- sites_list[1:2000, ]
 set.seed(1978)
 
@@ -28,6 +29,10 @@ dat_plan <- drake_plan(
                                      singletons = !!c(TRUE, FALSE))),
   di = target(add_dis(fs),
               transform = map(fs)),
+  diffs = target(rep_diff_sampler(fs, ndraws = !!nresamples),
+                 transform = map(fs)),
+  diffs_summary = target(summarize_diffs(diffs),
+                         transform = map(diffs)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),
@@ -74,6 +79,21 @@ if(grepl("ufhpc", nodename)) {
   # Run the pipeline on multiple local cores
   system.time(make(all, cache = cache, cache_log_file = here::here("analysis", "drake", "cache_log_fia.txt"), parallelism = "clustermq", jobs = 2))
 }
+
+
+## make .csv files for easier portability
+summary_targets <- dplyr::filter(dat_plan, substr(target, 0, 8) == "diffs_su")
+diffs_summaries <- list()
+for(i in 1:length(summary_targets$target)) {
+  diffs_summaries[[i]] <- readd(summary_targets$target[i], cache = cache, character_only = T)
+}
+all_summaries <- dplyr::bind_rows(diffs_summaries)
+write.csv(all_summaries, here::here("analysis", "results", "diff_summaries_fia_short.csv"), row.names = F)
+rm(diffs_summaries)
+rm(all_summaries)
+all_di <- readd(all_di_obs, cache = cache)
+write.csv(all_di, here::here("analysis", "results", "all_di_fia_short.csv"), row.names = F)
+rm(all_di)
 
 DBI::dbDisconnect(db)
 rm(cache)

### 2020-03-21 analysis/reports/rov.Rmd
grr

@@
   mutate(found_all = prop_found==1) %>% 
-    mutate(binned_nparts = as.factor(ceiling(log_nparts/10)))
+    mutate(binned_nparts = as.factor(ceiling(log_nparts/5)))
 
@@
 
-ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
+ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
   geom_histogram(bins = 100, boundary = 0) +
@@
 
-ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
+ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram(bins = 100, boundary = 0) +
+  theme_bw() +
+  facet_wrap(vars(binned_nparts))
+
+ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
   geom_histogram(bins = 100, boundary = 0) +

### 2020-03-21 analysis/reports/rov.Rmd
run mcdb, faster than fia

@@
 dis <- list.files(here::here("analysis", "results"), pattern = "all_di")
-all_di <- lapply(dis, FUN = function(di_df) return(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F)))
+all_di <- lapply(dis, FUN = function(di_df) return(mutate(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F), site = as.character(site))))
 all_di <- bind_rows(all_di)
@@
   mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
-  mutate(found_all = prop_found==1) %>% 
-    mutate(binned_nparts = as.factor(ceiling(log_nparts/5)))
+  mutate(found_all = prop_found==1,
+         log_log_nparts = log10(log_nparts)) %>% 
+    mutate(binned_nparts = as.factor(ceiling(log_log_nparts/.75))) %>%
+  filter(nparts > 1)
 
 diffs <- list.files(here::here("analysis", "results"), pattern = "diff_")
-all_diffs <- lapply(diffs, FUN = function(di_df) return(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F)))
+all_diffs <- lapply(diffs, FUN = function(di_df) return(mutate(read.csv(here::here("analysis", "results", di_df), stringsAsFactors = F), site = as.character(site))))
 all_diffs <- bind_rows(all_diffs)
@@
 
-ggplot(filter(all_di, singletons == F), aes(log_nparts)) +
+ggplot(filter(all_di, singletons == F, nparts > 1), aes(log_log_nparts)) +
   geom_histogram(binwidth = 10, boundary = 0, color = "black", alpha = 0) +

### 2020-03-21 analysis/mcdb_pipeline.R

@@ -8,6 +8,8 @@ datasets <- "mcdb"
 
 sites_list <- list_sites("mcdb")
 ndraws = 4000
+nresamples <- 4000
+
 #sites_list <- sites_list[1:15, ]
 set.seed(1980)
 
@@ -29,6 +31,10 @@ all <- drake_plan(
                                      singletons = !!c(TRUE, FALSE))),
   di = target(add_dis(fs),
               transform = map(fs)),
+  diffs = target(rep_diff_sampler(fs, ndraws = !!nresamples),
+                 transform = map(fs)),
+  diffs_summary = target(summarize_diffs(diffs),
+                         transform = map(diffs)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),
@@ -73,6 +79,21 @@ if(grepl("ufhpc", nodename)) {
   # Run the pipeline on multiple local cores
   system.time(make(all, cache = cache, cache_log_file = here::here("analysis", "drake", "cache_log_mcdb.txt"), parallelism = "clustermq", jobs = 2))
 }
+
+
+## make .csv files for easier portability
+summary_targets <- dplyr::filter(dat_plan, substr(target, 0, 8) == "diffs_su")
+diffs_summaries <- list()
+for(i in 1:length(summary_targets$target)) {
+  diffs_summaries[[i]] <- readd(summary_targets$target[i], cache = cache, character_only = T)
+}
+all_summaries <- dplyr::bind_rows(diffs_summaries)
+write.csv(all_summaries, here::here("analysis", "results", "diff_summaries_mcdb.csv"), row.names = F)
+rm(diffs_summaries)
+rm(all_summaries)
+all_di <- readd(all_di_obs, cache = cache)
+write.csv(all_di, here::here("analysis", "results", "all_di_mcdb.csv"), row.names = F)
+rm(all_di)
 
 DBI::dbDisconnect(db)
 rm(cache)

### 2020-03-22 analysis/reports/rov.Rmd
fiddlign w plots

@@
   mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
-  mutate(found_all = prop_found==1,
-         log_log_nparts = log10(log_nparts)) %>% 
-    mutate(binned_nparts = as.factor(ceiling(log_log_nparts/.75))) %>%
-  filter(nparts > 1)
+  mutate(found_all = prop_found==1) %>% 
+    mutate(binned_nparts = (ceiling(log_nparts/4))) %>%
+  filter(nparts > 1) %>%
+  group_by_all() %>%
+  mutate(thresholded_nparts = min(binned_nparts, 5)) %>%
+  ungroup()
 
@@
 
-ggplot(filter(all_di, singletons == F, nparts > 1), aes(log_log_nparts)) +
+ggplot(filter(all_di, singletons == F, nparts > 1), aes(log_nparts)) +
   geom_histogram(binwidth = 10, boundary = 0, color = "black", alpha = 0) +
+  theme_bw()
+
+ggplot(filter(all_di, singletons == F, nparts > 1), aes(binned_nparts)) +
+  geom_histogram(binwidth = 10, boundary = 0, color = "black", alpha = 0) +
+  theme_bw()
+
+ggplot(filter(all_di, singletons == F, nparts > 1), aes(thresholded_nparts)) +
+  geom_histogram(bins = 5, color = "black", alpha = 0) +
   theme_bw()
@@
 for(i in 1:length(unique(rov_long$rov_index))) {
-  rov_nparts_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val)) +
+  rov_nparts_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val, color = dat)) +
     geom_point() +
@@
     ggtitle(unique(rov_long$rov_index)[i]) +
-    geom_vline(xintercept = 10)
+    geom_vline(xintercept = 10) +
+    scale_color_viridis_d() +
+    theme(legend.position = "none")
 }
 
-gridExtra::grid.arrange(grobs = rov_nparts_plots)
+ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val, color = dat)) +
+  geom_point() +
+    scale_color_viridis_d() +
+  xlim(0,0) +
+  ylim(0,0) + 
+  theme_minimal() +
+theme(legend.position=c(.5, .5))
 
+for(i in 1:length(rov_nparts_plots)) {
+  print(rov_nparts_plots[[i]])
+}
 ```
@@
   theme_bw() +
-  facet_wrap(vars(binned_nparts))
+  facet_wrap(vars(thresholded_nparts), scales = "free_y")
 

### 2020-03-22 analysis/reports/rov.Rmd
writing, also omg run this

@@
   group_by_all() %>%
-  mutate(thresholded_nparts = min(binned_nparts, 5)) %>%
+  mutate(thresholded_nparts = min(binned_nparts, 8)) %>%
   ungroup()
@@
 
-all_di <- filter(all_di, s0 > 1)
+all_di <- filter(all_di, s0 > 2)
 ```
@@
 ggplot(filter(all_di, singletons == F, nparts > 1), aes(thresholded_nparts)) +
-  geom_histogram(bins = 5, color = "black", alpha = 0) +
+  geom_histogram(bins = 8, color = "black", alpha = 0) +
   theme_bw()
@@
 rov_long <- all_di %>%
-  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts) %>%
+  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts, thresholded_nparts) %>%
   tidyr::pivot_longer(cols = starts_with("mean"),
@@
                       values_to = "val")
+
+bin_rov <- function(rov_vector, nbins, quantiles = F) {
+
+  cutoffs <- seq(from = min(rov_vector), to = 1.00001 * max(rov_vector), length.out = nbins + 1)
+
+  if(quantiles) {
+    cutoffs <- quantile(rov_vector, probs = seq(0, 1, length.out = nbins + 1))
+    cutoffs[ length(cutoffs)] <- cutoffs[ length(cutoffs)] * 1.00001
+  }
+
+  binned_vect <- rov_vector
+
+  for(i in 1:length(rov_vector)) {
+    binned_vect[i] <- max(which(cutoffs <= rov_vector[i]))
+  }
+
+  return(binned_vect)
+}
+
+rov_long <- rov_long %>%
+  group_by(rov_index) %>%
+  mutate(binned_val = bin_rov(val, nbins =5 ),
+         qbinned_val = bin_rov(val, nbins = 5, quantiles = T)) %>%
+  ungroup()
+
 rov_plots <- list()
@@
   rov_nparts_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val, color = dat)) +
-    geom_point() +
+    geom_point(alpha = .2) +
     theme_bw() +
@@
 
+Gentry behaves somewhat strangely in these plots because it has the high proportion of low N/S communities; for these communities, all elements of the FS are squished into being highly even.
+
 If we bin nparts:
@@
 for(i in 1:length(unique(rov_long$rov_index))) {
-  rov_nparts_binned_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(binned_nparts, val)) +
-    geom_boxplot() +
-    theme_bw()
+  rov_nparts_binned_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val, color = as.factor(thresholded_nparts))) +
+    geom_point(alpha = .1) +
+    theme_bw() +
+    ggtitle(unique(rov_long$rov_index)[i]) +
+    scale_color_viridis_d() +
+    theme(legend.position = "none")
 }
 
-gridExtra::grid.arrange(grobs = rov_nparts_binned_plots)
+for(i in 1:length(rov_nparts_binned_plots)) {
+  print(rov_nparts_binned_plots[[i]]) 
+}
 ```
@@
 
-ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
+ggplot(filter(all_di, !singletons, s0 > 2, dat != "portal_plants"), aes(x = skew_percentile)) +
   geom_histogram(bins = 100, boundary = 0) +
@@
 
-ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
+ggplot(filter(all_di, !singletons,  dat != "portal_plants"), aes(x = simpson_percentile)) +
   geom_histogram(bins = 100, boundary = 0) +
@@
   theme_bw() +
-  facet_wrap(vars(thresholded_nparts), scales = "free_y")
+  facet_wrap(vars(thresholded_nparts), scales = "free_y", nrow = 2)
 
@@
 OK, these visualiations are pretty hard with this dataset (not very many small communities). Try after adding FIA?
+
+Against ROV metrics:
+
+```{r percentile v rov}
+
+ggplot(rov_long, aes(x = val, y = skew_percentile)) +
+  geom_point(alpha = .02) +
+  theme_bw() +
+  facet_wrap(vars(rov_index), scales = "free_x") +
+  ylim(0, 100) +
+  scale_color_viridis_c()
+
+```
+
+```{r bin rov}
+
+ggplot(rov_long, aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(rov_index, binned_val), scales = "free_y")
+
+ggplot(rov_long, aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(rov_index, qbinned_val), scales = "free_y")
+
+ggplot(rov_long, aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(rov_index, binned_val), scales = "free_y")
+
+ggplot(rov_long, aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(rov_index, qbinned_val), scales = "free_y")
+
+```

### 2020-03-22 analysis/bbs_pipeline.R

@@ -30,6 +30,10 @@ dat_plan <- drake_plan(
                                      singletons = !!c(TRUE, FALSE))),
   di = target(add_dis(fs),
               transform = map(fs)),
+  diffs = target(rep_diff_sampler(fs, ndraws = !!nresamples),
+                 transform = map(fs)),
+  diffs_summary = target(summarize_diffs(diffs),
+                         transform = map(diffs)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),

### 2020-03-23 analysis/reports/rov.Rmd
writing and dnew lots

@@
 
-all_di <- filter(all_di, s0 > 2)
+all_di <- filter(all_di, s0 > 2, dat != "portal_plants", !singletons)
+
+rov_long <- all_di %>%
+  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts, thresholded_nparts) %>%
+  tidyr::pivot_longer(cols = starts_with("mean"),
+                      names_to = "rov_index",
+                      values_to = "val")
+
+bin_rov <- function(rov_vector, nbins, quantiles = F, as.fact = F) {
+
+  cutoffs <- seq(from = min(rov_vector), to = 1.00001 * max(rov_vector), length.out = nbins + 1)
+
+  if(quantiles) {
+    cutoffs <- quantile(rov_vector, probs = seq(0, 1, length.out = nbins + 1))
+    cutoffs[ length(cutoffs)] <- cutoffs[ length(cutoffs)] * 1.00001
+  }
+
+  binned_vect <- rov_vector
+
+  for(i in 1:length(rov_vector)) {
+    binned_vect[i] <- max(which(cutoffs <= rov_vector[i]))
+  }
+
+  if(as.fact) {
+    binned_vect <- factor(binned_vect, ordered = T, labels = round(cutoffs[2:length(cutoffs)],digits = 1))
+  }
+
+  return(binned_vect)
+}
+
+rov_long <- rov_long %>%
+  group_by(rov_index) %>%
+  mutate(binned_val = bin_rov(val, nbins =5 ),
+         qbinned_val = bin_rov(val, nbins = 5, quantiles = T),
+         qbinned_lognparts = bin_rov(log_nparts, nbins = 10, quantiles = T, as.fact = T)) %>%
+  ungroup()
+
+all_di <- all_di %>%
+  mutate(qbinned_lognparts = bin_rov(log_nparts, nbins = 10, quantiles = T, as.fact = T))
+
 ```
@@
 ```{r size of fs}
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log_nparts)) +
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log(log_nparts))) +
   geom_point(alpha = .5) +
   theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+  theme(legend.position = "top") + scale_color_viridis_c()
+
+fs_size_panels <- list(
+  ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log_nparts)) +
+    theme_bw() +
+    geom_point(),
+  ggplot(filter(all_di, singletons == F), aes(x = log(n0), y = log_nparts)) +
+    theme_bw() +
+    geom_point(),
+  ggplot(filter(all_di, singletons == F), aes(x = log(n0 / s0), y = log_nparts)) +
+    theme_bw() +
+    geom_point()
+)
+
+gridExtra::grid.arrange(grobs = fs_size_panels)
 
@@
 
-rov_long <- all_di %>%
-  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts, thresholded_nparts) %>%
-  tidyr::pivot_longer(cols = starts_with("mean"),
-                      names_to = "rov_index",
-                      values_to = "val")
-
-bin_rov <- function(rov_vector, nbins, quantiles = F) {
-
-  cutoffs <- seq(from = min(rov_vector), to = 1.00001 * max(rov_vector), length.out = nbins + 1)
-
-  if(quantiles) {
-    cutoffs <- quantile(rov_vector, probs = seq(0, 1, length.out = nbins + 1))
-    cutoffs[ length(cutoffs)] <- cutoffs[ length(cutoffs)] * 1.00001
-  }
-
-  binned_vect <- rov_vector
-
-  for(i in 1:length(rov_vector)) {
-    binned_vect[i] <- max(which(cutoffs <= rov_vector[i]))
-  }
-
-  return(binned_vect)
-}
-
-rov_long <- rov_long %>%
-  group_by(rov_index) %>%
-  mutate(binned_val = bin_rov(val, nbins =5 ),
-         qbinned_val = bin_rov(val, nbins = 5, quantiles = T)) %>%
-  ungroup()
-
 rov_plots <- list()
@@
     ggtitle(unique(rov_long$rov_index)[i]) +
-    geom_vline(xintercept = 10) +
     scale_color_viridis_d() +
@@
 
-If we bin nparts:
-
 ```{r binned nparts ROV}
@@
 for(i in 1:length(unique(rov_long$rov_index))) {
-  rov_nparts_binned_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val, color = as.factor(thresholded_nparts))) +
-    geom_point(alpha = .1) +
+  rov_nparts_binned_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(log_nparts, val, color = log(n0/s0))) +
+    geom_point(alpha = .3) +
     theme_bw() +
     ggtitle(unique(rov_long$rov_index)[i]) +
-    scale_color_viridis_d() +
-    theme(legend.position = "none")
+    scale_color_viridis_c(end = .9) +
+    theme(legend.position = "left")
 }
@@
   print(rov_nparts_binned_plots[[i]]) 
+}
+
+ggplot(rov_long, aes(log_nparts, val, color = log(n0/s0))) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  scale_color_viridis_c() +
+  theme(legend.position = "left") +
+  facet_wrap(vars(rov_index), scales = "free_y")
+```
+
+```{r qbinned nparts ROV}
+
+rov_nparts_qbinned_plots <- list()
+
+for(i in 1:length(unique(rov_long$rov_index))) {
+  rov_nparts_qbinned_plots[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i]), aes(qbinned_lognparts, val, color = log(n0 / s0))) +
+    geom_jitter(alpha = .1) +
+    theme_bw() +
+    ggtitle(unique(rov_long$rov_index)[i]) +
+    scale_color_viridis_c() +
+    theme(legend.position = "none")
+}
+
+for(i in 1:length(rov_nparts_qbinned_plots)) {
+  print(rov_nparts_qbinned_plots[[i]]) 
+}
+```
+
+Remove low N/S:
+
+```{r qbinned nparts ROV}
+
+rov_nparts_qbinned_plots_highn <- list()
+
+for(i in 1:length(unique(rov_long$rov_index))) {
+  rov_nparts_qbinned_plots_highn[[i]] <- ggplot(filter(rov_long, rov_index == unique(rov_long$rov_index)[i], log(n0 / s0) > .7), aes(qbinned_lognparts, val, color = log(n0/s0))) +
+    geom_jitter(alpha = .1) +
+    theme_bw() +
+    ggtitle(unique(rov_long$rov_index)[i]) +
+    scale_color_viridis_c() +
+    theme(legend.position = "none")
+}
+
+for(i in 1:length(rov_nparts_qbinned_plots_highn)) {
+  print(rov_nparts_qbinned_plots_highn[[i]]) 
 }
@@
   facet_wrap(vars(thresholded_nparts), scales = "free_y")
+
+```
+
+Binned by quantile:
+
+```{r qbinned percentiles}
+
+ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram(bins = 100, boundary = 0) +
+  theme_bw() +
+  facet_wrap(vars(qbinned_lognparts), scales = "free_y", nrow = 2)
+
+ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100, boundary = 0) +
+  theme_bw() +
+  facet_wrap(vars(qbinned_lognparts), scales = "free_y", nrow = 2)
 
@@
 ```
+
+```{r report stats}
+
+# proportion of %iles above 95/below 5
+# skew
+mean(all_di$skew_percentile >= 95)
+# simpson
+mean(all_di$simpson_percentile <= 5)
+
+# by nparts
+
+nparts_summary <- all_di %>%
+  group_by(qbinned_lognparts) %>%
+  summarize(high_skew = mean(skew_percentile >= 95),
+            low_simpson = mean(simpson_percentile <= 5)) %>%
+  ungroup()
+
+nparts_summary
+
+eighty_smallest <- filter(all_di, log_nparts <= 8.6)
+mean(eighty_smallest$skew_percentile >= 95)
+
+twenty_largest <- filter(all_di, log_nparts >= 8.6)
+mean(twenty_largest$skew_percentile >= 95)
+
+fifty_smallest <- filter(all_di, log_nparts <= median(log_nparts))
+mean(fifty_smallest$simpson_percentile <= 5)
+fifty_largest <- filter(all_di, log_nparts >= median(log_nparts))
+mean(fifty_largest$simpson_percentile <= 5)
+
+```

### 2020-03-23 analysis/reports/rov.Rmd
plots

@@
 all_di <- left_join(all_di, all_diffs)
+
+all_di_singletons <- filter(all_di, s0 > 2, dat != "portal_plants", singletons)
+
+rov_long_singletons <- all_di_singletons %>%
+  select(dat, site, singletons, s0, n0, skew_percentile, simpson_percentile, mean_r2, mean_cd, mean_prop_off, mean_div, log_nparts, binned_nparts, thresholded_nparts) %>%
+  tidyr::pivot_longer(cols = starts_with("mean"),
+                      names_to = "rov_index",
+                      values_to = "val")
 
@@
 all_di <- all_di %>%
+  mutate(qbinned_lognparts = bin_rov(log_nparts, nbins = 10, quantiles = T, as.fact = T))
+
+rov_long_singletons <- rov_long_singletons %>%
+  group_by(rov_index) %>%
+  mutate(binned_val = bin_rov(val, nbins =5 ),
+         qbinned_val = bin_rov(val, nbins = 5, quantiles = T),
+         qbinned_lognparts = bin_rov(log_nparts, nbins = 10, quantiles = T, as.fact = T)) %>%
+  ungroup()
+
+all_di_singletons <- all_di_singletons %>%
   mutate(qbinned_lognparts = bin_rov(log_nparts, nbins = 10, quantiles = T, as.fact = T))
@@
 
-```{r qbinned nparts ROV}
+```{r qbinned nparts ROV high n}
 
@@
 ```
+
+### Rarefaction
+```{r rarefaction percentiles overall}
+
+ggplot(all_di_singletons, aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw()
+
+ggplot(all_di_singletons, aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw()
+```
+
+```{r rarefaction percentiles binned by nparts}
+
+ggplot(all_di_singletons, aes(x = skew_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(qbinned_lognparts), scales = "free_y", nrow = 2)
+
+ggplot(all_di_singletons, aes(x = simpson_percentile)) +
+  geom_histogram(bins = 100) +
+  theme_bw() +
+  facet_wrap(vars(qbinned_lognparts), scales = "free_y", nrow = 2)
+
+```
+
+```{r rarefaction change}
+
+all_di_change <- select(all_di, dat, site, singletons, s0, n0, log_nparts, qbinned_lognparts, skew_percentile, simpson_percentile) %>%
+  bind_rows(select(all_di_singletons, dat, site, singletons, s0, n0, skew_percentile, simpson_percentile)) %>%
+  tidyr::pivot_wider(names_from = singletons, values_from = c(s0, n0, skew_percentile, simpson_percentile, log_nparts, qbinned_lognparts)) %>%
+  select(-log_nparts_TRUE, -qbinned_lognparts_TRUE) %>%
+  filter(!is.na(s0_FALSE)) %>%
+  mutate(s0_change = s0_TRUE - s0_FALSE,
+         n0_change = n0_TRUE - n0_FALSE,
+         skew_change = skew_percentile_TRUE - skew_percentile_FALSE,
+         even_change = simpson_percentile_TRUE - simpson_percentile_FALSE)
+
+ggplot(all_di_change, aes(skew_percentile_FALSE, skew_percentile_TRUE)) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  xlim(0, 100) +
+  ylim(0, 100) +
+  geom_abline(intercept = 0, slope = 1, color = "orange")
+
+ggplot(all_di_change, aes(log(s0_FALSE), log(n0_FALSE), color = skew_percentile_TRUE < skew_percentile_FALSE)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_d(begin = .1, end = .9) +
+  theme(legend.position = "top")
+
+ggplot(all_di_change, aes(skew_percentile_FALSE, skew_percentile_TRUE)) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  facet_wrap(vars(qbinned_lognparts_FALSE), nrow = 2) +
+  xlim(0, 100) +
+  ylim(0, 100) +
+  geom_abline(intercept = 0, slope = 1, color = "orange")
+
+ggplot(all_di_change, aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  xlim(0, 100) +
+  ylim(0, 100) +
+  geom_abline(intercept = 0, slope = 1, color = "orange")
+ggplot(all_di_change, aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  facet_wrap(vars(qbinned_lognparts_FALSE), nrow = 2) +
+  xlim(0, 100) +
+  ylim(0, 100) +
+  geom_abline(intercept = 0, slope = 1, color = "orange")
+```

### 2020-03-23 analysis/reports/rov.Rmd
rarefaction

@@
 mean(eighty_smallest$skew_percentile >= 95)
+mean(eighty_smallest$simpson_percentile <= 5)
 
@@
 mean(twenty_largest$skew_percentile >= 95)
+mean(twenty_largest$simpson_percentile <= 5)
 
@@
 ```
+
+```{r rarefaction stats}
+# proportion of %iles above 95/below 5
+# skew
+mean(all_di_singletons$skew_percentile >= 95)
+# simpson
+mean(all_di_singletons$simpson_percentile <= 5)
+
+nparts_summary2 <- all_di_singletons %>%
+  group_by(qbinned_lognparts) %>%
+  summarize(high_skew = mean(skew_percentile >= 95),
+            low_simpson = mean(simpson_percentile <= 5)) %>%
+  ungroup()
+
+nparts_summary2
+
+```

### 2020-03-24 analysis/reports/rov.Rmd
weird violin plot

@@
 
+```{r ggplot rov v percentile}
+
+rescaled_long <- rov_long %>%
+  group_by(rov_index) %>%
+  mutate(rescaled_val = scales::rescale(val, c(0, 100))) %>%
+  ungroup() %>%
+  group_by(rov_index, qbinned_lognparts) %>%
+  mutate(high_skew = 100 * mean(skew_percentile >= 95),
+         low_simpson =100 *mean(simpson_percentile <= 5)) %>%
+  ungroup()
+
+ggplot(rescaled_long, aes(x = qbinned_lognparts, y = rescaled_val)) +
+  geom_violin() +
+  geom_point(aes(y = high_skew)) +
+  geom_point(aes(y = low_simpson), color = 'green') +
+  theme_bw() +
+  facet_wrap(vars(rov_index), scales = "free_y") +
+  geom_hline(yintercept = 5)
+
+ggplot(rescaled_long, aes(x = rescaled_val, y = skew_percentile)) +
+  geom_point(alpha = .01) +
+  theme_bw() +
+  facet_wrap(vars(rov_index), scales = "free_y")
+
+```
 ### Rarefaction

### 2020-03-24 analysis/reports/rov.Rmd
scruffy but extant

@@
 ```
+
+```{r map of percentiles}
+ggplot(all_di, aes(log(s0), log(n0), color = skew_percentile)) +
+  geom_point(alpha = .3) +
+  theme_bw() +
+  scale_color_viridis_c(limits = c(0, 100))
+ggplot(all_di, aes(log(s0), log(n0), color = simpson_percentile)) +
+  geom_point(alpha = .2) +
+  theme_bw() +
+  scale_color_viridis_c(limits = c(0, 100))
+
+```

### 2020-04-27 analysis/reports/figs.Rmd
working through dat vs 95 interval

---
title: "Synthesis report"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(s0 >= 2,
         n0 > s0,
         dat != "fia_small")
```

# Datasets in S and N space

Here is where our communities fall in S and N space:

```{r datasets in s and n space}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point(alpha = .8) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_d()

```

Here is how that translates into the size of the feasible set:

```{r size of fs}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log150_nparts)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = ..count..)) +
  geom_density() +
  theme_bw() +
  geom_vline(xintercept = c(10, 15))

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = ..count..)) +
  geom_density() +
  theme_bw() +
  geom_vline(xintercept = c(10, 15)) +
  facet_wrap(vars(dat), scales = "free")

```

The small datasets are basically all FIA.

Note that the color scale is log transformed, so the largest communities have e^`r max(all_di$log_nparts)`, or `r exp(max(all_di$log_nparts))`, elements in the feasible set!

# 95 interval vs nparts

```{r 95 interval}

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_2t)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_2t)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)

```

```{r 95 ratio v nparts scatter}

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_2t, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c()

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_2t, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c()

```

```{r percentiles v 95 interval}

ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_2t, y = skew_percentile)) +
  geom_point(alpha = .05) +
  theme_bw()

ggplot(filter(all_di, !singletons), aes(x = simpson_95_ratio_2t, y = simpson_percentile)) +
  geom_point(alpha = .05) +
  theme_bw()

```

# Binned by ranked nparts and ranked 95 intervals

```{r binned skew}

all_di_skew <- all_di %>%
  filter(!singletons, s0 > 2) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(skew_95_ratio_2t)%>%
  mutate(ratio_rank = row_number(),
         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))

ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(nparts_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("1/10th bins: Nparts")
ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(ratio_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("1/10th bins: 95% interval ratio")
ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(random_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("10 random bins")

```

```{r binned simpson}

all_di_simpson <- all_di %>%
  filter(!singletons) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(simpson_95_ratio_2t)%>%
  mutate(ratio_rank = row_number(),
         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))

ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(nparts_rank_binned), scales = "free") +
  theme_bw() +
    ggtitle("1/10th bins: Nparts")

ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(ratio_rank_binned), scales = "free") +
  theme_bw()+
  ggtitle("1/10th bins: 95% interval ratio")

ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(random_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("10 random bins")

```

```{r relationships in nparts bins}

ggplot(all_di_skew, aes(x = skew_95_ratio_2t, y = skew_percentile)) +
  geom_point(alpha = .05) +
  theme_bw() +
  facet_wrap(vars(nparts_rank_binned), scales = "free")

ggplot(all_di_simpson, aes(x = simpson_95_ratio_2t, y = simpson_percentile)) +
  geom_point(alpha = .05) +
  theme_bw() +
  facet_wrap(vars(nparts_rank_binned), scales = "free")

```

# 95 interval vs nparts

```{r 1t 95 interval}

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)

```

```{r 1t 95 ratio v nparts scatter}

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_1t, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c()

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_1t, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c()

```

```{r 1t percentiles v 95 interval}

ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_1t, y = skew_percentile)) +
  geom_point(alpha = .05) +
  theme_bw()

ggplot(filter(all_di, !singletons), aes(x = simpson_95_ratio_1t, y = simpson_percentile)) +
  geom_point(alpha = .05) +
  theme_bw()

```

# Binned by ranked nparts and ranked 95 intervals

```{r 1t binned skew}

all_di_skew <- all_di %>%
  filter(!singletons, s0 > 2) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(skew_95_ratio_1t)%>%
  mutate(ratio_rank = row_number(),
         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))

ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(nparts_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("1/10th bins: Nparts")
ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(ratio_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("1/10th bins: 95% interval ratio")
ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(random_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("10 random bins")

```

```{r 1t binned simpson}

all_di_simpson <- all_di %>%
  filter(!singletons) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(simpson_95_ratio_1t)%>%
  mutate(ratio_rank = row_number(),
         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))

ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(nparts_rank_binned), scales = "free") +
  theme_bw() +
    ggtitle("1/10th bins: Nparts")

ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(ratio_rank_binned), scales = "free") +
  theme_bw()+
  ggtitle("1/10th bins: 95% interval ratio")

ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(random_rank_binned), scales = "free") +
  theme_bw() +
  ggtitle("10 random bins")

```

```{r 1t relationships in nparts bins}

ggplot(all_di_skew, aes(x = skew_95_ratio_1t, y = skew_percentile)) +
  geom_point(alpha = .05) +
  theme_bw() +
  facet_wrap(vars(nparts_rank_binned), scales = "free")

ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t, y = simpson_percentile)) +
  geom_point(alpha = .05) +
  theme_bw() +
  facet_wrap(vars(nparts_rank_binned), scales = "free")

```

```{r overall relationships}

ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw()

ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw()

```

```{r overall relationships by da t}

ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y")

ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
  geom_histogram() +
  theme_bw()+
  facet_wrap(vars(dat), scales = "free_y")

```

```{r gentry}

ggplot(filter(all_di, dat == "gentry", !singletons), aes(x = log(n0/s0), y = simpson_percentile)) +
  geom_point()

gentry_cat <- filter(all_di, dat == "gentry", !singletons) %>%
  mutate(low_avgn = log(n0/s0) < 1.25)

ggplot(gentry_cat, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(low_avgn), scales = "free_y")

```

### 2020-04-27 analysis/reports/fia_size.Rmd
LOOK AT THIS NONSENSE

--- 2020-04-27 analysis/reports/figs.Rmd
@@
 
-The small datasets are basically all FIA.
+## Resrict to sizes found in FIA
 
-Note that the color scale is log transformed, so the largest communities have e^`r max(all_di$log_nparts)`, or `r exp(max(all_di$log_nparts))`, elements in the feasible set!
+```{r fia limits}
 
-# 95 interval vs nparts
+fia_max_s <- max(filter(all_di, !singletons, dat == "fia_short")$s0)
+fia_max_n <- max(filter(all_di,!singletons,  dat == "fia_short")$n0)
 
-```{r 95 interval}
+fia_sized <- filter(all_di, s0 <= fia_max_s, !singletons, n0 <= fia_max_n) %>%
+  mutate(fia_yn = dat == "fia_short")
 
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_2t)) +
-  geom_point(alpha = .5) +
+ggplot(fia_sized, aes(x = log(s0), y= log(n0), color = dat)) +
+  geom_point() +
   theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+  scale_color_viridis_d()
 
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_2t)) +
-  geom_point(alpha = .5) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+mean(fia_sized$dat == "fia_short")
 
@@
 
-```{r 95 ratio v nparts scatter}
+95% of the datasets with state variables comparable to the FIA ranges are FIA.
 
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_2t, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c()
+```{r fia sized hists}
 
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_2t, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c()
+ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram()
+
+ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+ggplot(filter(fia_sized, s0 > 2), aes(x = simpson_percentile)) +
+  geom_histogram()
+
+ggplot(filter(fia_sized, s0 > 2), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
 
@@
 
-```{r percentiles v 95 interval}
+```{r on map}
 
-ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_2t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
-
-ggplot(filter(all_di, !singletons), aes(x = simpson_95_ratio_2t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
-
-```
-
-# Binned by ranked nparts and ranked 95 intervals
-
-```{r binned skew}
-
-all_di_skew <- all_di %>%
-  filter(!singletons, s0 > 2) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(skew_95_ratio_2t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: Nparts")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: 95% interval ratio")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
-
-```
-
-```{r binned simpson}
-
-all_di_simpson <- all_di %>%
-  filter(!singletons) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(simpson_95_ratio_2t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw() +
-    ggtitle("1/10th bins: Nparts")
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw()+
-  ggtitle("1/10th bins: 95% interval ratio")
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
-
-```
-
-```{r relationships in nparts bins}
-
-ggplot(all_di_skew, aes(x = skew_95_ratio_2t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
-
-ggplot(all_di_simpson, aes(x = simpson_95_ratio_2t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
-
-```
-
-# 95 interval vs nparts
-
-```{r 1t 95 interval}
-
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
-  geom_point(alpha = .5) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
-
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t)) +
-  geom_point(alpha = .5) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
-
-```
-
-```{r 1t 95 ratio v nparts scatter}
-
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_1t, color = log(n0/s0))) +
+ggplot(fia_sized, aes(x = log(s0), y= log(n0), color = skew_percentile)) +
   geom_point() +
   theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
   scale_color_viridis_c()
 
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_1t, color = log(n0/s0))) +
+ggplot(fia_sized, aes(x = log(s0), y= log(n0), color = simpson_percentile)) +
   geom_point() +
   theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
   scale_color_viridis_c()
-
 ```
-
-```{r 1t percentiles v 95 interval}
-
-ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_1t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
-
-ggplot(filter(all_di, !singletons), aes(x = simpson_95_ratio_1t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
-
-```
-
-# Binned by ranked nparts and ranked 95 intervals
-
-```{r 1t binned skew}
-
-all_di_skew <- all_di %>%
-  filter(!singletons, s0 > 2) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(skew_95_ratio_1t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: Nparts")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: 95% interval ratio")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
-
-```
-
-```{r 1t binned simpson}
-
-all_di_simpson <- all_di %>%
-  filter(!singletons) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(simpson_95_ratio_1t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw() +
-    ggtitle("1/10th bins: Nparts")
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw()+
-  ggtitle("1/10th bins: 95% interval ratio")
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
-
-```
-
-```{r 1t relationships in nparts bins}
-
-ggplot(all_di_skew, aes(x = skew_95_ratio_1t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
-
-ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
-
-```
-
-```{r overall relationships}
-
-ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
-  geom_histogram() +
-  theme_bw()
-
-ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
-  geom_histogram() +
-  theme_bw()
-
-```
-
-```{r overall relationships by da t}
-
-ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
-  geom_histogram() +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y")
-
-ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
-  geom_histogram() +
-  theme_bw()+
-  facet_wrap(vars(dat), scales = "free_y")
-
-```
-
-```{r gentry}
-
-ggplot(filter(all_di, dat == "gentry", !singletons), aes(x = log(n0/s0), y = simpson_percentile)) +
-  geom_point()
-
-gentry_cat <- filter(all_di, dat == "gentry", !singletons) %>%
-  mutate(low_avgn = log(n0/s0) < 1.25)
-
-ggplot(gentry_cat, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(low_avgn), scales = "free_y")
-
-```

### 2020-04-28 analysis/reports/fia_size.Rmd
fia size poking around

@@
 all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+all_di_old <- read.csv(here::here("all_di.csv"), stringsAsFactors = F)
+
+fia_small_provisional <- filter(all_di_old, dat == "fia_small")
+
+all_di <- bind_rows(all_di, fia_small_provisional)
 
@@
   filter(s0 >= 2,
-         n0 > s0,
-         dat != "fia_small")
+         n0 > s0) %>%
+  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", "fia", dat))
 ```
@@
 
+## All sites all sizes
+
+```{r percentiles overall}
+
+ggplot(filter(all_di, s0 > 2, !singletons), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  ggtitle("Skew - all sites")
+
+ggplot(filter(all_di, s0 > 2, !singletons), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y") +
+  ggtitle("Skew - all sites")
+
+ggplot(filter(all_di,!singletons), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  ggtitle("Simpson - all sites")
+
+ggplot(filter(all_di,!singletons), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  ggtitle("Simpson - all sites") +
+    facet_wrap(vars(dat), scales = "free_y")
+
+```
+
 ## Resrict to sizes found in FIA
@@
 
-fia_max_s <- max(filter(all_di, !singletons, dat == "fia_short")$s0)
-fia_max_n <- max(filter(all_di,!singletons,  dat == "fia_short")$n0)
+fia_max_s <- max(filter(all_di, !singletons, dat == "fia")$s0)
+fia_max_n <- max(filter(all_di,!singletons,  dat == "fia")$n0)
 
 fia_sized <- filter(all_di, s0 <= fia_max_s, !singletons, n0 <= fia_max_n) %>%
-  mutate(fia_yn = dat == "fia_short")
+  mutate(fia_yn = dat == "fia") %>%
+  mutate(random_5th = as.integer(sample(2, size = n(), replace = T, prob = c(0.035, 0.965))))
 
@@
 
-mean(fia_sized$dat == "fia_short")
+ggplot(fia_sized, aes(x = log(s0), y= log(n0), color = dat)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_d() +
+  facet_wrap(vars(fia_yn), scales = "fixed")
 
+mean(fia_sized$dat == "fia")
+mean(fia_sized$random_5th == "2")
 ```
 
-95% of the datasets with state variables comparable to the FIA ranges are FIA.
+96.5% of the datasets with state variables comparable to the FIA ranges are FIA.
 
@@
 ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
-  geom_histogram()
+  geom_histogram() + theme_bw() +
+  ggtitle("Skew - all sites")
 
 ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
+  geom_histogram() + theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("Skew - FIA true/false")
+# 
+# fia_sized <- fia_sized %>%
+#   mutate(small_n = log(n0) <= 3.5)
+# 
+# ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
+#   geom_histogram() + theme_bw() +
+#   facet_grid(rows = vars(fia_yn), cols = vars(small_n), scales = "free_y") +
+#   ggtitle("Skew - FIA true/false (rows), n <= 20 true/false (cols)")
+# 
+# 
+ggplot(filter(fia_sized, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() + theme_bw() +
+  facet_wrap(vars(random_5th), scales = "free_y") +
+  ggtitle("Skew - randomly pulling out 4%")
 
 ggplot(filter(fia_sized, s0 > 2), aes(x = simpson_percentile)) +
-  geom_histogram()
+  geom_histogram() + theme_bw() +
+  ggtitle("Simpson all sites")
 
 ggplot(filter(fia_sized, s0 > 2), aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
+  geom_histogram() + theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("Simpson - FIA true/false")
+
+ggplot(filter(fia_sized, s0 > 2), aes(x = simpson_percentile)) +
+  geom_histogram() + theme_bw() +
+  facet_wrap(vars(random_5th), scales = "free_y") +
+  ggtitle("Simpson - a random 4%")
 
@@
 
-ggplot(fia_sized, aes(x = log(s0), y= log(n0), color = skew_percentile)) +
+ggplot(filter(fia_sized, s0 > 2), aes(x = log(s0), y= log(n0), color = skew_percentile)) +
   geom_point() +
@@
 ```
+
+Does skew behave differently if n0 <0 `r exp(3.5)`? Just from looking at the map.
+
+```{r skew small n}
+
+fia_sized <- fia_sized %>%
+  mutate(small_n = log(n0) <= 3.5)
+
+fia_sized %>%
+  group_by(small_n) %>%
+  summarize(prop_fia = mean(fia_yn))
+
+ggplot(filter(fia_sized, small_n, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  #facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("Small N")
+
+ggplot(filter(fia_sized, !small_n, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  #facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("NOT Small N")
+
+ggplot(filter(fia_sized, !small_n, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("NOT Small N, FIA true/false")
+
+ggplot(filter(fia_sized, small_n, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("Small N")
+
+```
+
+# simpson
+```{r simpson}
+
+ggplot(filter(fia_sized, small_n, s0 > 2), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  #facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("Small N")
+
+ggplot(filter(fia_sized, !small_n, s0 > 2), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  #facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("NOT Small N")
+
+ggplot(filter(fia_sized, !small_n, s0 > 2), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("NOT Small N, FIA true/false")
+
+ggplot(filter(fia_sized, small_n, s0 > 2), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("Small N")
+
+```
+
+# Remove small N from all (not just fia sized)
+
+```{r full}
+
+ggplot(filter(all_di, s0 > 2, !singletons, n0 >= 3.5), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(filter(all_di, !singletons, n0 >= 3.5), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw()
+
+```

### 2020-05-01 analysis/reports/95_interval_portal.Rmd
try this

---
title: "Synthesis report"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(s0 >= 2,
         n0 > s0,
         dat != "fia_small")
```

# Datasets in S and N space

Here is where our communities fall in S and N space:

```{r datasets in s and n space}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
  geom_point(alpha = .8) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_d()

```

Here is how that translates into the size of the feasible set:

```{r size of fs}
ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log150_nparts)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = ..count..)) +
  geom_density() +
  theme_bw() +
  geom_vline(xintercept = c(10, 15))

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = ..count..)) +
  geom_density() +
  theme_bw() +
  geom_vline(xintercept = c(10, 15)) +
  facet_wrap(vars(dat), scales = "free")

```

The small datasets are basically all FIA.

Note that the color scale is log transformed, so the largest communities have e^`r max(all_di$log_nparts)`, or `r exp(max(all_di$log_nparts))`, elements in the feasible set!

# 95 interval vs nparts

```{r 95 interval}

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio)) +
  geom_point(alpha = .5) +
  theme_bw() +
  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c() +
  facet_wrap(vars(dat), scales = "free")

ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio, color = log(n0/s0))) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(10,15)) +
  scale_color_viridis_c()+
  facet_wrap(vars(dat), scales = "free")

```

# Binned by ranked nparts and ranked 95 intervals

```{r binned skew}

all_di_skew <- all_di %>%
  filter(!singletons, s0 > 2) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(skew_95_ratio)%>%
  mutate(ratio_rank = row_number(),
         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))

ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(nparts_rank_binned), scales = "free") +
  theme_bw()
ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(ratio_rank_binned), scales = "free") +
  theme_bw()

ggplot(all_di_skew, aes(x = skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(random_rank_binned), scales = "free") +
  theme_bw()

```
```{r binned simpson}

all_di_simpson <- all_di %>%
  filter(!singletons) %>%
  arrange(log_nparts) %>%
  mutate(nparts_rank = row_number()) %>%
  arrange(simpson_95_ratio)%>%
  mutate(ratio_rank = row_number()) %>%
  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))))

ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(nparts_rank_binned), scales = "free") +
  theme_bw()
ggplot(all_di_simpson, aes(x = simpson_percentile)) +
  geom_histogram() +
  facet_wrap(vars(ratio_rank_binned), scales = "free") +
  theme_bw()

```

# Small mcdb

```{r small mcdb}
small_di <- filter(all_di, dat == "mcdb", log_nparts < 20)

ggplot(small_di, aes(x = log_nparts, y = skew_95_ratio)) +
  geom_point() +
  theme_bw()

filter(small_di, skew_95_ratio == min(small_di$skew_95_ratio, na.rm = T))

```

```{r load one site}

site = 1879

library(drake)

## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-mcdb.sqlite"))
cache <- storr::storr_dbi("datatable", "keystable", db)
cache$del(key = "lock", namespace = "session")

loadd(di_fs_1879_TRUE, cache = cache)

twosided_interval <- quantile(filter(di_fs_1879_TRUE, source!= "observed")$skew, probs = c(0.025, 0.975))

onesided_interval <- quantile(filter(di_fs_1879_TRUE, source!= "observed")$skew, probs = c(.95))

ggplot(filter(di_fs_1879_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
  geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red")

# 1469 - more middle of the pack

loadd(di_fs_1469_TRUE, cache = cache)

twosided_interval <- quantile(filter(di_fs_1469_TRUE, source!= "observed")$skew, probs = c(0.025, 0.975))

onesided_interval <- quantile(filter(di_fs_1469_TRUE, source!= "observed")$skew, probs = c(.95))

ggplot(filter(di_fs_1469_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
  geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red")

#1218 - very high

loadd(di_fs_1218_TRUE, cache = cache)

twosided_interval <- quantile(filter(di_fs_1218_TRUE, source!= "observed")$skew, probs = c(0.025, 0.975), na.rm=T)

onesided_interval <- quantile(filter(di_fs_1218_TRUE, source!= "observed")$skew, probs = c(.95), na.rm=T)

ggplot(filter(di_fs_1218_TRUE, source != "observed"), aes(x =skew)) +
  geom_density() +
  geom_vline(xintercept = twosided_interval) +
  geom_vline(xintercept = onesided_interval, color = "red")

```

### 2020-05-01 analysis/helper_scripts/mcdb_kernels.R

@@ -1,0 +1,59 @@
+library(drake)
+library(scadsanalysis)
+library(dplyr)
+source(here::here("analysis", "helper_scripts", "kernels.R"))
+sites <- list_sites("mcdb")
+set.seed(1978)
+sites <- sites [ sample.int(nrow(sites), size = 20, replace = F),]
+
+#sites <- data.frame(site = c(1879, 1469, 1218))
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-mcdb.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+
+## Get kernels
+
+skew_kernels <- list()
+
+for(i in 1:nrow(sites)) {
+  fs_name <- paste0("di_fs_", sites$site[i], "_FALSE")
+  this_fs <- readd(fs_name, cache = cache, character_only = T)
+  skew_kernels[[i]] <- get_standardized_kernel(this_fs, nsims = 10000)
+
+}
+
+skew_kernels <- dplyr::bind_rows(skew_kernels)
+
+skew_kernels <- skew_kernels %>%
+  filter(!is.na(val)) %>%
+  mutate(log_nparts = log(as.numeric(nparts)))
+
+library(ggplot2)
+ggplot(skew_kernels, aes(x = index, y = density, group = site, color = twotailed_95)) +
+  geom_line() +
+  theme_bw()
+
+simpson_kernels <- list()
+
+for(i in 1:nrow(sites)) {
+  fs_name <- paste0("di_fs_", sites$site[i], "_FALSE")
+  this_fs <- readd(fs_name, cache = cache, character_only = T)
+  simpson_kernels[[i]] <- get_standardized_kernel(this_fs, nsims = 10000, metric = "simpson")
+
+}
+
+simpson_kernels <- dplyr::bind_rows(simpson_kernels)
+
+simpson_kernels <- simpson_kernels %>%
+  filter(!is.na(val)) %>%
+  mutate(log_nparts = log(as.numeric(nparts)))
+
+ggplot(simpson_kernels, aes(x = index, y = density, group = site, color = onetailed_95)) +
+  geom_line() +
+  theme_bw()
+
+
+ggplot(simpson_kernels, aes(x = index, y = density, group = site, color = twotailed_95)) +
+  geom_line() +
+  theme_bw()

### 2020-05-01 analysis/reports/fia_v_portal.Rmd
make all di

--- 2020-04-28 analysis/reports/fia_size.Rmd
@@
 ```
+
+# Remove fia sized from all
+
+```{r remove fia sized}
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y")
+```

### 2020-05-01 analysis/helper_scripts/make_all_di.R

@@ -5,11 +5,13 @@ library(scadsanalysis)
 
 all_di <- list()
 #datasets <- c("bbs", "fia_short", "gentry", "mcdb", "misc_abund_short", "portal_plants", "fia_small")
-datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "portal_plants")
+datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "portal_plants", "fia_small", "portal_rodents")
 
 #datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
 
 #datasets <- c("portal_plants","gentry", "misc_abund_short" )
+
+
 
 for(i in 1:length(datasets)) {
 

### 2020-05-07 analysis/reports/95_interval_portal.Rmd
run make all

@@
 
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio)) +
+ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  theme(legend.position = "top") + 
+    scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
+  facet_wrap(vars(dat), scales = "free")
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t))+
   geom_point(alpha = .5) +
@@
 
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio)) +
-  geom_point(alpha = .5) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
-  facet_wrap(vars(dat), scales = "free")
-
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio, color = log(n0/s0))) +
+ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_1t, color = log(n0/s0))) +
   geom_point() +
@@
 
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio, color = log(n0/s0))) +
+ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_1t, color = log(n0/s0))) +
   geom_point() +
@@
   mutate(nparts_rank = row_number()) %>%
-  arrange(skew_95_ratio)%>%
+  arrange(skew_95_ratio_1t)%>%
   mutate(ratio_rank = row_number(),
@@
   mutate(nparts_rank = row_number()) %>%
-  arrange(simpson_95_ratio)%>%
+  arrange(simpson_95_ratio_1t)%>%
   mutate(ratio_rank = row_number()) %>%
@@
 
-ggplot(small_di, aes(x = log_nparts, y = skew_95_ratio)) +
+ggplot(small_di, aes(x = log_nparts, y = skew_95_ratio_1t))+
   geom_point() +
@@
 
-filter(small_di, skew_95_ratio == min(small_di$skew_95_ratio, na.rm = T))
+filter(small_di, skew_95_ratio_1t == min(small_di$skew_95_ratio_1t, na.rm = T))
 
@@
   geom_density() +
-  geom_vline(xintercept = twosided_interval) +
-  geom_vline(xintercept = onesided_interval, color = "red")
+ # geom_vline(xintercept = twosided_interval) +
+  geom_vline(xintercept = onesided_interval, color = "red") +
+  theme_bw()
 
@@
   geom_density() +
-  geom_vline(xintercept = twosided_interval) +
-  geom_vline(xintercept = onesided_interval, color = "red")
+#  geom_vline(xintercept = twosided_interval) +
+  geom_vline(xintercept = onesided_interval, color = "red") +
+  theme_bw()
 

### 2020-05-07 analysis/reports/fia_size.Rmd
run make all

@@
          n0 > s0) %>%
-  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", "fia", dat))
+  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", "fia", dat)) %>%
+  filter(dat != "portal_plants", dat != "portal_rodents")
 ```
@@
   geom_histogram() + theme_bw() +
-  ggtitle("Skew - all sites")
+  ggtitle("Skew - all sites within FIA size")
 
@@
   geom_histogram() + theme_bw() +
-  ggtitle("Simpson all sites")
+  ggtitle("Simpson all sites within FIA size")
 
@@
 ```
+
+# Remove fia sized from all
+
+```{r remove fia sized}
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  ggtitle("Skew - all sites larger than FIA")
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  ggtitle("Simpson - all sites larger than FIA")
+
+ggplot(filter(all_di, !singletons, s0 > fia_max_s, n0 > fia_max_n), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y")
+```
+
+```{r onetailed intervals}
+
+ggplot(all_di, aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(end = .9)
+
+ggplot(all_di, aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(end = .9)
+```

### 2020-05-07 analysis/reports/fia_v_portal.Rmd
run make all

@@
 ```
+
+```{r compare fia to portal rodents}
+
+ggplot(filter(fia_sized, dat %in% c("fia", "portal_rodents")), aes(x = log(s0), y = log(n0), color = dat)) +
+  geom_point(alpha = .3) +
+  geom_point(data = filter(all_di, dat == "portal_rodents")) +
+  theme_bw()
+
+ggplot(filter(fia_sized, dat %in% c("fia", "portal_rodents"), s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(dat, small_n), scales = "free_y") +
+  theme_bw()
+
+```

### 2020-05-07 analysis/reports/figs.Rmd
strugggles
run make all

@@
 
+### Remove FIA
+
+```{r overall relationships no fia}
+
+ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw()
+
+ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw()
+
+```
+
 ```{r overall relationships by da t}
@@
 ```
+
+```{r 1t hists}
+
+ggplot(all_di_skew, aes(x = skew_95_ratio_1t))  +
+geom_histogram() +   theme_bw() +
+  facet_wrap(vars(nparts_rank_binned))
+
+ggplot(all_di_skew, aes(x = skew_95_ratio_1t)) +
+  geom_histogram(aes(x = skew_percentile / 100, y = ..count.. * 5), fill = "green", alpha = .5) + geom_histogram(alpha = .5) +  
+theme_bw() +
+  facet_wrap(vars(nparts_rank_binned))
+
+ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t))  +
+geom_histogram() +   theme_bw() +
+  facet_wrap(vars(nparts_rank_binned))
+
+ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t)) +
+  geom_histogram(aes(x = simpson_percentile / 100, y = ..count.. * 5), fill = "green", alpha = .5) + geom_histogram(alpha = .5) +  
+theme_bw() +
+  facet_wrap(vars(nparts_rank_binned))
+
+```

### 2020-05-07 analysis/helper_scripts/make_all_di.R

@@ -5,7 +5,7 @@ library(scadsanalysis)
 
 all_di <- list()
 #datasets <- c("bbs", "fia_short", "gentry", "mcdb", "misc_abund_short", "portal_plants", "fia_small")
-datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "portal_plants", "portal_rodents")
+datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "portal_plants", "portal_rodents", "fia_small")
 
 #datasets <- c("fia", "gentry", "mcdb", "misc_abund_short", "portal_plants")
 

### 2020-05-07 analysis/reports/figs.Rmd
with fia small

@@
   filter(s0 >= 2,
-         n0 > s0,
-         dat != "fia_small")
+         n0 > s0)
 ```
@@
 
-ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = skew_percentile)) +
+ggplot(filter(all_di, !singletons, dat != "fia_short", dat != "fia_small"), aes(x = skew_percentile)) +
   geom_histogram() +
@@
 
-ggplot(filter(all_di, !singletons, dat != "fia_short"), aes(x = simpson_percentile)) +
+ggplot(filter(all_di, !singletons, dat != "fia_short", dat != "fia_small"), aes(x = simpson_percentile)) +
   geom_histogram() +

### 2020-05-17 analysis/reports/figs.Rmd
rewrites

@@
   filter(s0 >= 2,
-         n0 > s0)
+         n0 > s0,
+         dat %in% c("bbs", "gentry", "fia_short", "fia_small", "mcdb", "misc_abund_short")) %>%
+  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", yes = "fia", no = dat))
 ```
@@
 ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
-  geom_point(alpha = .8) +
+  geom_point(alpha = .5) +
   theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_d()
+  theme(legend.position = "top") + scale_color_viridis_d(end = .9)
 
@@
 ```{r size of fs}
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log150_nparts)) +
+ggplot(filter(all_di, log_nparts <= 100, singletons == F), aes(x = log(s0), y = log(n0), color = log_nparts)) +
   geom_point(alpha = .5) +
+  geom_point(data = filter(all_di, log_nparts > 100), color = "yellow", alpha = .5) +
   theme_bw() +
@@
 
-# 95 interval vs nparts
+# 95 interval (one tailed) vs nparts
 
@@
 
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_2t)) +
+skew_1t = ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
   geom_point(alpha = .5) +
@@
 
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_2t)) +
+simpson_1t = ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t)) +
   geom_point(alpha = .5) +
@@
 
-```
-
-```{r 95 ratio v nparts scatter}
-
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_2t, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c()
-
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_2t, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c()
+gridExtra::grid.arrange(grobs = list(skew_1t, simpson_1t), nrow = 1)
 
@@
 
-```{r percentiles v 95 interval}
+# Overall percentile values
 
-ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_2t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
+```{r overall}
 
-ggplot(filter(all_di, !singletons), aes(x = simpson_95_ratio_2t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
+ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  ggtitle("Skew percentile") +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
+  geom_histogram() +
+  theme_bw() +
+  ggtitle("Simpson percentile")+
+  facet_wrap(vars(dat), scales = "free_y")
 

### 2020-05-17 analysis/reports/figs.Rmd
we may have a draft?????

@@
          dat %in% c("bbs", "gentry", "fia_short", "fia_small", "mcdb", "misc_abund_short")) %>%
-  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", yes = "fia", no = dat))
+  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", yes = "fia", no = dat)) %>%
+  mutate(dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))%>%
+  mutate(is_fia = ifelse(substr(dat, 0, 3) == "fia", dat, "other"))
 ```
@@
 ```{r datasets in s and n space}
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
+
+all_dat_to_plot <- filter(all_di, singletons == F) %>%
+  bind_rows(mutate(filter(all_di, singletons == F), dat = "all"))
+
+ggplot(all_dat_to_plot, aes(x = log(s0), y = log(n0), color = dat)) +
   geom_point(alpha = .5) +
   theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_d(end = .9)
+  theme(legend.position = "top") + scale_color_viridis_d(end = .9) +
+  facet_wrap(vars(dat))
 
@@
 
-```
+skew_outcomes <- filter(all_di, !singletons, s0 > 2) %>%
+  group_by(is_fia) %>%
+  summarize(high_skew_prop = mean(skew_percentile >= 95)) %>%
+  ungroup()
 
-# Binned by ranked nparts and ranked 95 intervals
-
-```{r binned skew}
-
-all_di_skew <- all_di %>%
-  filter(!singletons, s0 > 2) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(skew_95_ratio_2t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: Nparts")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: 95% interval ratio")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
+even_outcomes <- filter(all_di, !singletons) %>%
+  group_by(is_fia) %>%
+  summarize(low_even_prop = mean(simpson_percentile <= 5)) %>%
+  ungroup()
 
@@
 
-```{r binned simpson}
+# Within the FIA size range
 
-all_di_simpson <- all_di %>%
-  filter(!singletons) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(simpson_95_ratio_2t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
+```{r within FIA size range}
 
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
+fia_size_range <- filter(all_di, !singletons)
+
+fia_max_s = max(filter(all_di, dat == "fia")$s0)
+fia_max_n = max(filter(all_di, dat == "fia")$n0)
+
+fia_size_range <- filter(fia_size_range,
+                         s0 <= fia_max_s,
+                         n0 <= fia_max_n)
+
+skew_fia <- ggplot(filter(fia_size_range, s0 > 2), aes(x = skew_percentile)) +
   geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
+  facet_wrap(vars(is_fia), scales = "free_y") +
   theme_bw() +
-    ggtitle("1/10th bins: Nparts")
+  ggtitle("Skew percentile - within FIA size range")
 
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
+simpson_fia <- ggplot(filter(fia_size_range), aes(x = simpson_percentile)) +
   geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw()+
-  ggtitle("1/10th bins: 95% interval ratio")
+  facet_wrap(vars(is_fia), scales = "free_y") +
+  theme_bw() +
+  ggtitle("Simpson percentile - within FIA size range")
 
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
+gridExtra::grid.arrange(grobs = list(skew_fia, simpson_fia), nrow = 1)
 
@@
 
-```{r relationships in nparts bins}
+```{r 95 hists}
 
-ggplot(all_di_skew, aes(x = skew_95_ratio_2t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
+all_di <- all_di %>%
+  group_by_all() %>%
+  mutate(is_fia_size = (s0 <= fia_max_s) && (n0 <= fia_max_n)) %>%
+  ungroup()
+
+all_di <- all_di %>%
+  mutate(is_fia_size = ifelse(is_fia_size, "FIA size", "Larger than FIA"))
+
+skew_ratio <- ggplot(filter(all_di, s0 > 2), aes(x = skew_95_ratio_1t)) +
+  geom_histogram() +
   theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
+  facet_wrap(vars(is_fia_size), scales = "free_y") +
+  ggtitle("Narrowness of skewness")
 
-ggplot(all_di_simpson, aes(x = simpson_95_ratio_2t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
+even_ratio <- ggplot(filter(all_di, s0 > 2), aes(x = simpson_95_ratio_1t)) +
+  geom_histogram() +
   theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
+  facet_wrap(vars(is_fia_size), scales = "free_y") +
+  ggtitle("Narrowness of evenness")
+
+gridExtra::grid.arrange(grobs = list(skew_ratio, even_ratio), nrow = 1)
 
@@
 
-# 95 interval vs nparts
+# Rarefaction
 
-```{r 1t 95 interval}
+```{r rarefaction change}
 
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
-  geom_point(alpha = .5) +
+rarefied <- filter(all_di, singletons) %>%
+  select(dat, site, skew_percentile, simpson_percentile) %>%
+  rename(skew_percentile_rarefied = skew_percentile,
+         simpson_percentile_rarefied = simpson_percentile)
+
+rarefied <- right_join(all_di, rarefied)
+
+skew_rare <- ggplot(filter(rarefied, s0 > 2), aes(x = skew_percentile, y = skew_percentile_rarefied)) +
+  geom_point(alpha = .2) +
+  geom_abline(slope = 1, intercept = 0, color = "green") +
   theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+  facet_wrap(vars(dat)) +
+  ggtitle("Skew percentile change with rarefaction")
 
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t)) +
-  geom_point(alpha = .5) +
+even_rare <- ggplot(filter(rarefied), aes(x = simpson_percentile, y = simpson_percentile_rarefied)) +
+  geom_point(alpha = .2) +
+  geom_abline(slope = 1, intercept = 0, color = "green") +
   theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+  facet_wrap(vars(dat)) +
+  ggtitle("Evenness percentile change with rarefaction")
 
+gridExtra::grid.arrange(grobs = list(skew_rare, even_rare), nrow = 1)
+
+skew_rare_outcome <- rarefied %>%
+  filter(s0 > 2) %>%
+  group_by(is_fia) %>%
+  summarize(high_skew = mean(skew_percentile_rarefied >= 95)) %>%
+  ungroup()
+skew_rare_outcome
+
+even_rare_outcome <- rarefied %>%
+  filter(s0 > 2) %>%
+  group_by(is_fia) %>%
+  summarize(low_even = mean(simpson_percentile_rarefied <= 5)) %>%
+  ungroup()
+even_rare_outcome
 ```
-
-```{r 1t 95 ratio v nparts scatter}
-
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_1t, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c()
-
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio_1t, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c()
-
-```
-
-```{r 1t percentiles v 95 interval}
-
-ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_1t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
-
-ggplot(filter(all_di, !singletons), aes(x = simpson_95_ratio_1t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw()
-
-```
-
-# Binned by ranked nparts and ranked 95 intervals
-
-```{r 1t binned skew}
-
-all_di_skew <- all_di %>%
-  filter(!singletons, s0 > 2) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(skew_95_ratio_1t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: Nparts")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("1/10th bins: 95% interval ratio")
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
-
-```
-
-```{r 1t binned simpson}
-
-all_di_simpson <- all_di %>%
-  filter(!singletons) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(simpson_95_ratio_1t)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw() +
-    ggtitle("1/10th bins: Nparts")
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw()+
-  ggtitle("1/10th bins: 95% interval ratio")
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw() +
-  ggtitle("10 random bins")
-
-```
-
-```{r 1t relationships in nparts bins}
-
-ggplot(all_di_skew, aes(x = skew_95_ratio_1t, y = skew_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
-
-ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t, y = simpson_percentile)) +
-  geom_point(alpha = .05) +
-  theme_bw() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free")
-
-```
-
-```{r overall relationships}
-
-ggplot(filter(all_di, !singletons), aes(x = skew_percentile)) +
-  geom_histogram() +
-  theme_bw()
-
-ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
-  geom_histogram() +
-  theme_bw()
-
-```
-
-### Remove FIA
-
-```{r overall relationships no fia}
-
-ggplot(filter(all_di, !singletons, dat != "fia_short", dat != "fia_small"), aes(x = skew_percentile)) +
-  geom_histogram() +
-  theme_bw()
-
-ggplot(filter(all_di, !singletons, dat != "fia_short", dat != "fia_small"), aes(x = simpson_percentile)) +
-  geom_histogram() +
-  theme_bw()
-
-```
-
-```{r overall relationships by da t}
-
-ggplot(filter(all_di, !singletons, s0 > 2), aes(x = skew_percentile)) +
-  geom_histogram() +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y")
-
-ggplot(filter(all_di, !singletons), aes(x = simpson_percentile)) +
-  geom_histogram() +
-  theme_bw()+
-  facet_wrap(vars(dat), scales = "free_y")
-
-```
-
-```{r gentry}
-
-ggplot(filter(all_di, dat == "gentry", !singletons), aes(x = log(n0/s0), y = simpson_percentile)) +
-  geom_point()
-
-gentry_cat <- filter(all_di, dat == "gentry", !singletons) %>%
-  mutate(low_avgn = log(n0/s0) < 1.25)
-
-ggplot(gentry_cat, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(low_avgn), scales = "free_y")
-
-```
-
-```{r 1t hists}
-
-ggplot(all_di_skew, aes(x = skew_95_ratio_1t))  +
-geom_histogram() +   theme_bw() +
-  facet_wrap(vars(nparts_rank_binned))
-
-ggplot(all_di_skew, aes(x = skew_95_ratio_1t)) +
-  geom_histogram(aes(x = skew_percentile / 100, y = ..count.. * 5), fill = "green", alpha = .5) + geom_histogram(alpha = .5) +  
-theme_bw() +
-  facet_wrap(vars(nparts_rank_binned))
-
-ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t))  +
-geom_histogram() +   theme_bw() +
-  facet_wrap(vars(nparts_rank_binned))
-
-ggplot(all_di_simpson, aes(x = simpson_95_ratio_1t)) +
-  geom_histogram(aes(x = simpson_percentile / 100, y = ..count.. * 5), fill = "green", alpha = .5) + geom_histogram(alpha = .5) +  
-theme_bw() +
-  facet_wrap(vars(nparts_rank_binned))
-
-```

### 2020-07-31 analysis/howto.Rmd
working

---
title: "How to run"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installations

You will need to download and install hte package for this research compendium, as well as packages to run the analytical workflow and optionally HPC.

```{r install packages, echo = T, eval  = F}
devtools::install_github("diazrenata/scadsanalysis@clean-and-tests")
install.packages("drake")
install.packages("DBI")
install.packages("storr")
install.packages("clustermq")

```

```{r load}
library(scadsanalysis)

```

# Download and prep data

```{r download data, echo = T, eval = F}
download_data()
```

# Get the p tables

Either copy from directory, or run `analysis/helper_scripts/ptables_plan.R`. RMD runs this on a HPC cluster using `submit_p_pipeline.sbatch`. These are very large files.

# Run plans

Either source one of the pipelines directory or run via sbatch.

### 2020-07-31 analysis/manuscript/reports/95_interval.Rmd
working

--- 2020-05-01 analysis/reports/95_interval_portal.Rmd
@@
          log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
-  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
-  mutate(found_all = prop_found==1) %>%
   filter(s0 >= 2,
-         n0 > s0,
-         dat != "fia_small")
+         n0 > s0)
 ```
@@
 
-Here is how that translates into the size of the feasible set:
+```{r skew intervals by dataset}
 
-```{r size of fs}
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = log150_nparts)) +
-  geom_point(alpha = .5) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_2t)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y")
 
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = ..count..)) +
-  geom_density() +
-  theme_bw() +
-  geom_vline(xintercept = c(10, 15))
-
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = ..count..)) +
-  geom_density() +
-  theme_bw() +
-  geom_vline(xintercept = c(10, 15)) +
-  facet_wrap(vars(dat), scales = "free")
-
+ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_1t)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y")
 ```
-
-The small datasets are basically all FIA.
-
-Note that the color scale is log transformed, so the largest communities have e^`r max(all_di$log_nparts)`, or `r exp(max(all_di$log_nparts))`, elements in the feasible set!
-
-# 95 interval vs nparts
-
-```{r 95 interval}
-
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio)) +
-  geom_point(alpha = .5) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
-  facet_wrap(vars(dat), scales = "free")
-
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio)) +
-  geom_point(alpha = .5) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
-  facet_wrap(vars(dat), scales = "free")
-
-ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log_nparts, y = skew_95_ratio, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c() +
-  facet_wrap(vars(dat), scales = "free")
-
-ggplot(filter(all_di, singletons == F), aes(x = log_nparts, y = simpson_95_ratio, color = log(n0/s0))) +
-  geom_point() +
-  theme_bw() +
-  geom_vline(xintercept = c(10,15)) +
-  scale_color_viridis_c()+
-  facet_wrap(vars(dat), scales = "free")
-
-```
-
-# Binned by ranked nparts and ranked 95 intervals
-
-```{r binned skew}
-
-all_di_skew <- all_di %>%
-  filter(!singletons, s0 > 2) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(skew_95_ratio)%>%
-  mutate(ratio_rank = row_number(),
-         random_rank = sample.int(n = length(nparts_rank), size = length(nparts_rank), replace = F)) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))),
-         random_rank_binned = ceiling(10 * (random_rank / max(random_rank))))
-
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw()
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw()
-
-ggplot(all_di_skew, aes(x = skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(random_rank_binned), scales = "free") +
-  theme_bw()
-
-```
-```{r binned simpson}
-
-all_di_simpson <- all_di %>%
-  filter(!singletons) %>%
-  arrange(log_nparts) %>%
-  mutate(nparts_rank = row_number()) %>%
-  arrange(simpson_95_ratio)%>%
-  mutate(ratio_rank = row_number()) %>%
-  mutate(nparts_rank_binned = ceiling(10 * (nparts_rank / max(nparts_rank))),
-         ratio_rank_binned = ceiling(10 * (ratio_rank / max(ratio_rank))))
-
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(nparts_rank_binned), scales = "free") +
-  theme_bw()
-ggplot(all_di_simpson, aes(x = simpson_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(ratio_rank_binned), scales = "free") +
-  theme_bw()
-
-```
-
-# Small mcdb
-
-```{r small mcdb}
-small_di <- filter(all_di, dat == "mcdb", log_nparts < 20)
-
-ggplot(small_di, aes(x = log_nparts, y = skew_95_ratio)) +
-  geom_point() +
-  theme_bw()
-
-filter(small_di, skew_95_ratio == min(small_di$skew_95_ratio, na.rm = T))
-
-```
-
-```{r load one site}
-
-site = 1879
-
-library(drake)
-
-## Set up the cache and config
-db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-mcdb.sqlite"))
-cache <- storr::storr_dbi("datatable", "keystable", db)
-cache$del(key = "lock", namespace = "session")
-
-loadd(di_fs_1879_TRUE, cache = cache)
-
-twosided_interval <- quantile(filter(di_fs_1879_TRUE, source!= "observed")$skew, probs = c(0.025, 0.975))
-
-onesided_interval <- quantile(filter(di_fs_1879_TRUE, source!= "observed")$skew, probs = c(.95))
-
-ggplot(filter(di_fs_1879_TRUE, source != "observed"), aes(x =skew)) +
-  geom_density() +
-  geom_vline(xintercept = twosided_interval) +
-  geom_vline(xintercept = onesided_interval, color = "red")
-
-# 1469 - more middle of the pack
-
-loadd(di_fs_1469_TRUE, cache = cache)
-
-twosided_interval <- quantile(filter(di_fs_1469_TRUE, source!= "observed")$skew, probs = c(0.025, 0.975))
-
-onesided_interval <- quantile(filter(di_fs_1469_TRUE, source!= "observed")$skew, probs = c(.95))
-
-ggplot(filter(di_fs_1469_TRUE, source != "observed"), aes(x =skew)) +
-  geom_density() +
-  geom_vline(xintercept = twosided_interval) +
-  geom_vline(xintercept = onesided_interval, color = "red")
-
-#1218 - very high
-
-loadd(di_fs_1218_TRUE, cache = cache)
-
-twosided_interval <- quantile(filter(di_fs_1218_TRUE, source!= "observed")$skew, probs = c(0.025, 0.975), na.rm=T)
-
-onesided_interval <- quantile(filter(di_fs_1218_TRUE, source!= "observed")$skew, probs = c(.95), na.rm=T)
-
-ggplot(filter(di_fs_1218_TRUE, source != "observed"), aes(x =skew)) +
-  geom_density() +
-  geom_vline(xintercept = twosided_interval) +
-  geom_vline(xintercept = onesided_interval, color = "red")
-
-```

### 2020-07-31 analysis/manuscript/reports/95_interval_portal.Rmd
working

--- 2020-05-07 analysis/reports/95_interval_portal.Rmd
@@
   theme(legend.position = "top") + 
+    scale_color_viridis_c(option = "magma", end = .9, begin = .1)
+ggplot(filter(all_di, singletons == F, s0 > 2), aes(x = log(s0), y = log(n0), color = skew_95_ratio_1t)) +
+  geom_point(alpha = .5) +
+  theme_bw() +
+  theme(legend.position = "top") + 
     scale_color_viridis_c(option = "magma", end = .9, begin = .1)+
   facet_wrap(vars(dat), scales = "free")
+
+ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = simpson_95_ratio_1t))+
+  geom_point(alpha = .5) +
+  theme_bw() +
+  theme(legend.position = "top") + scale_color_viridis_c(option = "magma", end = .9, begin = .1)
 

### 2020-07-31 analysis/manuscript/reports/figs2.Rmd
working

---
title: "Synthesis report"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
  mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
  mutate(found_all = prop_found==1) %>%
  filter(s0 >= 2,
         n0 > s0,
         dat %in% c("bbs", "gentry", "fia_short", "fia_small", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(substr(dat, 0, 3) == "fia", yes = "fia", no = dat)) %>%
  mutate(dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))%>%
  mutate(is_fia = ifelse(substr(dat, 0, 3) == "fia", dat, "other"))
```

### Datasets in S by N space

```{r datasets in s and n space}

ggplot(filter(all_di, !singletons), aes(log(s0), log(n0), color = dat)) +
  geom_point(alpha = .3) +
  theme_bw() +
  ggtitle("Communities by S and N") +
  scale_color_viridis_d()

```

### Narrowness schematic

Provisionally copied from dissertation proposal.

### Percentile histograms by dataset

```{r percentile by dataset}

ggplot(filter(all_di, !singletons, s0 > 2), aes(skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") +
  geom_vline(xintercept = 95, color = "red", linetype = 3) +
  ggtitle("Observed percentile: Skewness")

ggplot(filter(all_di, !singletons), aes(simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") +
  geom_vline(xintercept = 5, color = "red", linetype = 3) +
  ggtitle("Observed percentile: Evenness")

```

### Rarefaction effect

```{r rarefaction}

rarefact <- all_di %>%
  select(singletons, skew_percentile, simpson_percentile, dat, site, s0) %>%
  tidyr::pivot_wider(names_from = singletons, values_from = c(skew_percentile, simpson_percentile, s0))

gridExtra::grid.arrange(grobs = list(ggplot(filter(rarefact, s0_FALSE  > 3), aes(skew_percentile_FALSE, skew_percentile_TRUE)) + 
  geom_point(alpha = .05) +
  geom_abline(intercept = 0, slope = 1, color = "blue") +
  theme_bw() +
  facet_wrap(vars(dat)) +
  ggtitle("Rarefaction change: Skewness"),

ggplot(rarefact, aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) + 
  geom_point(alpha = .05) +
  geom_abline(intercept = 0, slope = 1, color = "blue") +
  theme_bw() +
  facet_wrap(vars(dat)) +
  ggtitle("Rarefaction change: Evenness")), ncol = 2)

```
### Percentile by S and N

```{r percentile s and n}

fia_s_range <- range(filter(all_di, !singletons, dat == "fia")$s0)
fia_n_range <- range(filter(all_di, !singletons, dat == "fia")$n0)

fia_border <- data.frame(
  s0 = c(0, fia_s_range[2], fia_s_range[2]),
  n0 = c(fia_n_range[2], fia_n_range[2], 0)
)

gridExtra::grid.arrange(grobs = list(
ggplot(filter(all_di, !singletons, s0 > 3), aes(log(s0), log(n0), color = skew_percentile)) +
  geom_point(alpha = .15) +
  geom_path(data = fia_border, aes(log(s0), log(n0)), color = "black") +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .8) +
  ggtitle("Skewness percentile over S and N"),
ggplot(filter(all_di, !singletons), aes(log(s0), log(n0), color = simpson_percentile)) +
  geom_point(alpha = .15) +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .8) +
    geom_path(data = fia_border, aes(log(s0), log(n0)), color = "black") +
  ggtitle("Evenness percentile over S and N")),
ncol= 2)

```

### FIA v other small communities

```{r small community comparison}
small <- filter(all_di, !singletons, s0 <= fia_s_range[2], n0 <= fia_n_range[2])

gridExtra::grid.arrange(grobs = list(
ggplot(filter(small, !singletons, s0 > 2), aes(skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(is_fia), scales = "free_y") +
  geom_vline(xintercept = 95, color = "red", linetype = 3) +
  ggtitle("Small communities percentile: Skewness"),

ggplot(filter(small, !singletons), aes(simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(is_fia), scales = "free_y") +
  geom_vline(xintercept = 5, color = "red", linetype = 3) +
  ggtitle("Small communities percentile: Evenness")), ncol = 1)

```

### 95 interval by S and N

```{r ratio v s and n}

gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, !singletons, s0 > 2), 
         aes(log(s0), log(n0), color = skew_95_ratio_1t)) +
    geom_point(alpha = .2) +
    scale_color_viridis_c() +
    theme_bw() +
    ggtitle("95% ratio: Skewness") +
        geom_path(data = fia_border, aes(log(s0), log(n0)), color = "black") +

    theme(legend.position = "bottom"),
   ggplot(filter(all_di, !singletons), 
         aes(log(s0), log(n0), color = simpson_95_ratio_1t)) +
    geom_point(alpha = .2) +
    scale_color_viridis_c() +
    theme_bw() +
    ggtitle("95% ratio: Evenness") +
        geom_path(data = fia_border, aes(log(s0), log(n0)), color = "black") +

    theme(legend.position = "bottom")
),
ncol = 2)

```

### 2020-07-31 analysis/mcdb_pipeline.R

@@ -7,7 +7,7 @@ expose_imports("scadsanalysis")
 datasets <- "mcdb"
 
 sites_list <- list_sites("mcdb")
-ndraws = 4000
+ndraws = 200
 #sites_list <- sites_list[1:15, ]
 set.seed(1980)
 

### 2020-07-31 analysis/mcdb_pipeline.R
undo accidental folder move

@@ -7,7 +7,7 @@ expose_imports("scadsanalysis")
 datasets <- "mcdb"
 
 sites_list <- list_sites("mcdb")
-ndraws = 200
+ndraws = 4000
 #sites_list <- sites_list[1:15, ]
 set.seed(1980)
 

### 2020-08-01 analysis/reports/manuscript_main.Rmd
k now run it all

--- 2020-07-31 analysis/manuscript/reports/95_interval.Rmd
@@
 ---
-title: "Synthesis report"
+title: "Figures and results for main manuscript"
 output: github_document
@@
 ```
-
-# Datasets in S and N space
-
-Here is where our communities fall in S and N space:
-
-```{r datasets in s and n space}
-ggplot(filter(all_di, singletons == F), aes(x = log(s0), y = log(n0), color = dat)) +
-  geom_point(alpha = .8) +
-  theme_bw() +
-  theme(legend.position = "top") + scale_color_viridis_d()
-
-```
-
-```{r skew intervals by dataset}
-
-ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_2t)) +
-  geom_histogram() +
-  facet_wrap(vars(dat), scales = "free_y")
-
-ggplot(filter(all_di, !singletons), aes(x = skew_95_ratio_1t)) +
-  geom_histogram() +
-  facet_wrap(vars(dat), scales = "free_y")
-```

### 2020-08-01 analysis/mcdb_pipeline.R

@@ -7,8 +7,8 @@ expose_imports("scadsanalysis")
 datasets <- "mcdb"
 
 sites_list <- list_sites("mcdb")
-ndraws = 200
-sites_list <- sites_list[1:30, ]
+ndraws = 4000
+#sites_list <- sites_list[1:30, ]
 set.seed(1980)
 
 

### 2020-08-01 analysis/reports/manuscript_main.Rmd
new para on stat mech
got sidetracked on figures

@@
          log_nsamples = log(nsamples),
-         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
   filter(s0 >= 2,
-         n0 > s0)
+         n0 > s0,
+         !singletons,
+         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
 ```
+
+# Final dataset in S and N space
+
+```{r final dataset s and n space}
+
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
+  geom_point(alpha = .4) +
+  theme_bw() +
+  scale_color_viridis_d() +
+  ggtitle("Communities by S and N")
+
+```
+
+# Illustrations of 95% interval
+
+To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities.
+
+# Skewness and evenness histograms by dataset
+
+```{r res}
+
+ggplot(filter(all_di, s0 > 2), aes(skew_percentile)) +
+  geom_histogram() +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")
+
+ggplot(filter(all_di, s0 > 2, nsamples > 200), aes(skew_percentile)) +
+  geom_histogram() +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >200 samples")
+
+ggplot(filter(all_di, s0 > 2, nsamples > 500), aes(skew_percentile)) +
+  geom_histogram() +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >500 samples")
+
+ggplot(filter(all_di, s0 > 2, nsamples > 1000), aes(skew_percentile)) +
+  geom_histogram() +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >1000 samples")
+
+ggplot(filter(all_di, s0 > 2, nsamples > 2500), aes(skew_percentile)) +
+  geom_histogram() +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >2500 samples")
+
+ggplot(filter(all_di, s0 > 2, nsamples == 4000), aes(skew_percentile)) +
+  geom_histogram() +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, 4000 samples")
+
+```
+# Nsamples cutoff
+
+```{r nsamples cutoff}
+
+samples_cutoffs = seq(0, 4000, by = 100)
+
+samples_cutoff_dfs <- list()
+
+for(i in 1:length(samples_cutoffs)) {
+
+  this_df <- all_di %>%
+    filter(nsamples >= samples_cutoffs[i])
+
+  skew_prop <- filter(this_df, s0 > 2) %>%
+    mutate(skew_above_95 = skew_percentile >= 95) %>%
+    group_by(dat) %>%
+    summarize(prop_skew_high = mean(skew_above_95)) %>%
+    ungroup() %>%
+    mutate(nsamples_cutoff = samples_cutoffs[i])
+
+  simpson_prop <- this_df %>%
+    mutate(simpson_below_05 = simpson_percentile <= 5) %>%
+    group_by(dat) %>%
+    summarize(prop_simpson_low = mean(simpson_below_05)) %>%
+    ungroup() %>%
+    mutate(nsamples_cutoff = samples_cutoffs[i])
+
+  samples_cutoff_dfs[[i]] <- left_join(skew_prop, simpson_prop)
+
+}
+
+samples_cutoffs_df <- bind_rows(samples_cutoff_dfs)
+
+overall <- filter(samples_cutoffs_df, nsamples_cutoff == 0) %>%
+  select(-nsamples_cutoff) %>%
+  rename(overall_high_skew= prop_skew_high ,
+         overall_low_simpson = prop_simpson_low)
+samples_cutoffs_df <- left_join(samples_cutoffs_df, overall)
+
+ggplot(samples_cutoffs_df, aes(nsamples_cutoff, prop_skew_high, color=dat)) +
+  geom_point() +
+  geom_line(aes(y = overall_high_skew)) +
+  theme_bw() +
+  ylim(0, .5) +
+  geom_hline(yintercept = .05) +
+  facet_wrap(vars(dat))
+
+ggplot(samples_cutoffs_df, aes(nsamples_cutoff, prop_simpson_low, color=dat)) +
+  geom_point() +
+  geom_line(aes(y = overall_low_simpson)) +
+  theme_bw() +
+  geom_hline(yintercept = .05) +
+  facet_wrap(vars(dat))
+
+```
+
+If you remove the very smallest FIA communities (those that achieved the very fewest samples) you get a "significant" effect even for very low thresholds.
+
+# 95% interval for small versus large communities
+
+# Comparison of FIA to similarly-sized communities
+
+```{r fia sized}
+fia_max_s <- max(filter(all_di, dat == "fia")$s0)
+fia_max_n <- max(filter(all_di, dat == "fia")$n0)
+
+fia_sized <- filter(all_di, s0 <= fia_max_s,n0 <= fia_max_n) %>%
+  mutate(fia_yn = dat == "fia")
+
+ggplot(filter(fia_sized, s0 > 2), aes(skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+ggplot(filter(fia_sized, s0 > 2, nsamples > 100), aes(skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+ggplot(fia_sized, aes(log_nparts, log_nsamples)) +
+  geom_point()
+```

### 2020-08-03 analysis/reports/manuscript_main.Rmd
some more nparts, nsamples thinking - about to delete

@@
          log_n0 = log(n0)) %>%
-  filter(s0 >= 2,
-         n0 > s0,
+  filter(n0 > s0,
          !singletons,
@@
   facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")
-
-ggplot(filter(all_di, s0 > 2, nsamples > 200), aes(skew_percentile)) +
-  geom_histogram() +
-  geom_vline(xintercept = 95, color = "red") +
-  theme_bw() +
-    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >200 samples")
-
-ggplot(filter(all_di, s0 > 2, nsamples > 500), aes(skew_percentile)) +
-  geom_histogram() +
-  geom_vline(xintercept = 95, color = "red") +
-  theme_bw() +
-    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >500 samples")
-
-ggplot(filter(all_di, s0 > 2, nsamples > 1000), aes(skew_percentile)) +
-  geom_histogram() +
-  geom_vline(xintercept = 95, color = "red") +
-  theme_bw() +
-    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >1000 samples")
-
-ggplot(filter(all_di, s0 > 2, nsamples > 2500), aes(skew_percentile)) +
-  geom_histogram() +
-  geom_vline(xintercept = 95, color = "red") +
-  theme_bw() +
-    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >2500 samples")
-
-ggplot(filter(all_di, s0 > 2, nsamples == 4000), aes(skew_percentile)) +
-  geom_histogram() +
-  geom_vline(xintercept = 95, color = "red") +
-  theme_bw() +
-    facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, 4000 samples")
+# 
+# ggplot(filter(all_di, s0 > 2, nsamples > 200), aes(skew_percentile)) +
+#   geom_histogram() +
+#   geom_vline(xintercept = 95, color = "red") +
+#   theme_bw() +
+#     facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >200 samples")
+# 
+# 
+# ggplot(filter(all_di, s0 > 2, nsamples > 500), aes(skew_percentile)) +
+#   geom_histogram() +
+#   geom_vline(xintercept = 95, color = "red") +
+#   theme_bw() +
+#     facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >500 samples")
+# 
+# 
+# ggplot(filter(all_di, s0 > 2, nsamples > 1000), aes(skew_percentile)) +
+#   geom_histogram() +
+#   geom_vline(xintercept = 95, color = "red") +
+#   theme_bw() +
+#     facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >1000 samples")
+# 
+# ggplot(filter(all_di, s0 > 2, nsamples > 2500), aes(skew_percentile)) +
+#   geom_histogram() +
+#   geom_vline(xintercept = 95, color = "red") +
+#   theme_bw() +
+#     facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, >2500 samples")
+# 
+# 
+# ggplot(filter(all_di, s0 > 2, nsamples == 4000), aes(skew_percentile)) +
+#   geom_histogram() +
+#   geom_vline(xintercept = 95, color = "red") +
+#   theme_bw() +
+#     facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, 4000 samples")
 
@@
 
+# Nparts cutoff
+
+```{r nparts cutoff}
+
+parts_cutoffs = seq(0, 320, by = 2)
+
+parts_cutoff_dfs <- list()
+
+for(i in 1:length(parts_cutoffs)) {
+
+  this_df <- all_di %>%
+    filter(log_nparts >= parts_cutoffs[i])
+
+  skew_prop <- filter(this_df, s0 > 2) %>%
+    mutate(skew_above_95 = skew_percentile >= 95) %>%
+    group_by(dat) %>%
+    summarize(prop_skew_high = mean(skew_above_95),
+              nsites = dplyr::n()) %>%
+    ungroup() %>%
+    mutate(nparts_cutoff = parts_cutoffs[i])
+
+  simpson_prop <- this_df %>%
+    mutate(simpson_below_05 = simpson_percentile <= 5) %>%
+    group_by(dat) %>%
+    summarize(prop_simpson_low = mean(simpson_below_05),
+              nsites = dplyr::n()) %>%
+    ungroup() %>%
+    mutate(nparts_cutoff = parts_cutoffs[i])
+
+  parts_cutoff_dfs[[i]] <- left_join(skew_prop, simpson_prop)
+
+}
+
+parts_cutoffs_df <- bind_rows(parts_cutoff_dfs)
+
+overall <- filter(parts_cutoffs_df, nparts_cutoff == 0) %>%
+  select(-nparts_cutoff) %>%
+  rename(overall_high_skew= prop_skew_high ,
+         overall_low_simpson = prop_simpson_low,
+         total_sites = nsites)
+
+parts_cutoffs_df <- left_join(parts_cutoffs_df, overall) %>%
+  mutate(prop_sites = nsites / total_sites)
+
+ggplot(parts_cutoffs_df, aes(nparts_cutoff, prop_skew_high, color=dat)) +
+  geom_point() +
+  geom_line(aes(y = overall_high_skew)) +
+  geom_line(aes(y = prop_sites), color = "red") +
+  theme_bw() +
+  geom_hline(yintercept = .05) +
+  facet_wrap(vars(dat), scales = "free")
+
+ggplot(parts_cutoffs_df, aes(nparts_cutoff, prop_simpson_low, color=dat)) +
+  geom_point() +
+  geom_line(aes(y = overall_low_simpson)) +
+    geom_line(aes(y = prop_sites), color = "red") +
+  theme_bw() +
+  geom_hline(yintercept = .05) +
+  facet_wrap(vars(dat), scales = "free_x")
+
+ggplot(all_di, aes(x = log_nparts, y = nsamples)) + geom_point() + geom_vline(xintercept = 5) + xlim(0, 15)
+
+```
+
 # 95% interval for small versus large communities
+
+```{r 95 interval}
+
+ggplot(all_di, aes(x = log_nparts, y = skew_95_ratio_1t, color = nsamples)) +
+  geom_point() +
+  facet_wrap(vars(dat)) +
+  xlim(0, 30)
+
+ggplot(all_di, aes(x = log_nparts, y = simpson_95_ratio_1t, color = nsamples)) +
+  geom_point() +
+  facet_wrap(vars(dat))
+
+```
 

### 2020-08-03 analysis/reports/manuscript_main.Rmd
nparts greater thn 10 is impt

--- 2020-08-01 analysis/reports/manuscript_main.Rmd
@@
 title: "Figures and results for main manuscript"
-output: github_document
+output: 
+    github_document:
+       df_print: kable
 ---
@@
          log_nsamples = log(nsamples),
-         log150_nparts = log(gmp:::as.double.bigz(nparts), base = 150)) %>%
-  filter(s0 >= 2,
-         n0 > s0)
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 > s0,
+         !singletons,
+         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
 ```
+
+# Final dataset in S and N space
+
+```{r final dataset s and n space}
+
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
+  geom_point(alpha = .4) +
+  theme_bw() +
+  scale_color_viridis_d() +
+  ggtitle("Communities by S and N")
+
+```
+
+# Illustrations of 95% interval
+
+To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities.
+
+# Skewness and evenness histograms by dataset
+
+```{r first hists}
+
+ggplot(filter(all_di, s0 > 2), aes(skew_percentile)) +
+  geom_histogram(bins = 100) +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")
+
+ggplot(all_di, aes(simpson_percentile)) + 
+ geom_histogram(bins = 100) +
+  geom_vline(xintercept = 5, color = "red") +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
+```
+
+# Proportion of sites with highly skewed or uneven SADs
+
+```{r results table}
+
+overall_skew_results <- all_di %>%
+  filter(s0 > 2) %>%
+  mutate(high_skew = skew_percentile > 95) %>%
+  group_by(dat) %>%
+  summarize(proportion_skew_high = mean(high_skew),
+            nsites_skew = dplyr::n())
+
+overall_simpson_results <- all_di %>%
+  mutate(low_even = simpson_percentile < 5) %>%
+  group_by(dat) %>%
+  summarize(proportion_even_low = mean(low_even),
+            nsites_even = dplyr::n())
+
+overall_results <- left_join(overall_skew_results, overall_simpson_results)
+
+overall_results
+
+```
+
+There are fewer sites for skewness because we exclude sites with only 2 species.
+
+# Size of feasible set for each dataset
+
+```{r fs size hists}
+
+all_di <- all_di %>%
+  mutate(log_nparts_truncated = ifelse(
+    log_nparts > 50,
+    50,
+    log_nparts)
+  )
+
+ggplot(all_di, aes(log_nparts_truncated)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y") +
+  theme_bw()
+
+fs_size_results <- all_di %>%
+  group_by(dat) %>%
+  summarize(prop_smaller_than_5=  mean(log_nparts <= 5),
+            prop_smaller_than_7 =  mean(log_nparts <= 7),
+            prop_smaller_than_10 = mean(log_nparts <= 10))
+fs_size_results
+
+```
+
+FIA is the only dataset that is overwhelmingly dominated by sites with fewer than `r exp(10)` elements in the feasible set.
+MCDB also has many small sites, but these are counterbalanced by larger ones.
+
+62% of the FIA sites have fewer than `r exp(7)` elements in the feasible set, and 30% have fewer than `r exp(5)`.
+
+```{r fs size to s0 and n0, fig.dim = c(3,3)}
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 5)) +
+  geom_point() +
+  theme_bw() +
+  theme(legend.position = "top")
+
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 7)) +
+  geom_point() +
+  theme_bw()+
+  theme(legend.position = "top")
+
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 10)) +
+  geom_point() +
+  theme_bw()+
+  theme(legend.position = "top")
+```
+
+Having fewer than 150 elements ~ fewer than 3 species, or fewer than `r exp(2.75)` individuals  with up to 20 species.
+
+Fewer than 1000 elements ~ fewer than 3 species, or fewer than `r exp(3.25)` individuals with up to 20 species.
+
+Fewer than 20000 elements ~ fewer than 4 species, or fewer than `r exp(4)` individuals.
+
+# 95% interval for small versus large communities
+
+```{r 95 interval}
+
+ggplot(all_di, aes(x = log_nparts, y = skew_95_ratio_1t)) +
+  geom_point(alpha = .2) + theme_bw() + ggtitle("Skewness 95% interval")
+
+ggplot(all_di, aes(x = log_nparts, y = skew_95_ratio_1t)) +
+  geom_point(alpha = .01) +
+  xlim(0, 15) +
+  theme_bw() +
+  ggtitle("Skewness 95% interval - only small feasible sets")
+
+ggplot(all_di, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
+  geom_point(alpha = .2) + theme_bw()+ ggtitle("Evenness 95% interval")
+
+ggplot(all_di, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
+  geom_point(alpha = .05) +
+  xlim(0, 15) +
+  theme_bw()+
+  ggtitle("Evenness 95% interval - only small feasible sets")
+
+```
+
+The 95% ratio decreases for large FS.
+
+For skewness, it is still quite high even up to 20,000 elements in the FS. But it is starting to decline by then?
+
+# Comparison of FIA to similarly-sized communities
+
+```{r fia sized}
+fia_max_s <- max(filter(all_di, dat == "fia")$s0)
+fia_max_n <- max(filter(all_di, dat == "fia")$n0)
+
+fia_sized <- filter(all_di, s0 <= fia_max_s,n0 <= fia_max_n) %>%
+  mutate(fia_yn = dat == "fia") %>%
+  mutate(fia_yn = ifelse(fia_yn, "FIA", "Other datasets"))
+
+ggplot(filter(fia_sized, s0 > 2, nparts > 10), aes(skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+ggplot(filter(fia_sized, s0 > 2, log_nparts > 5, nparts > 10), aes(skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+ggplot(filter(fia_sized, s0 > 2, log_nparts <  5, nparts > 10), aes(skew_percentile)) +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+```
+
+# Removing the smallest communities from FIA
+
+```{r fia no small}
+
+```

### 2020-08-04 analysis/reports/manuscript_main.Rmd
removing smaller than 50 does not change

@@
 ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
-  geom_point(alpha = .4) +
+  geom_point(alpha = .01) +
+  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
   theme_bw() +
@@
 
+ggplot(filter(all_di, s0 > 2, log_nparts > log(50)), aes(skew_percentile)) +
+  geom_histogram(bins = 100) +
+  geom_vline(xintercept = 95, color = "red") +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")
+
 ggplot(all_di, aes(simpson_percentile)) + 
+ geom_histogram(bins = 100) +
+  geom_vline(xintercept = 5, color = "red") +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
+ggplot(filter(all_di, log_nparts > log(50)), aes(simpson_percentile)) + 
  geom_histogram(bins = 100) +
@@
 overall_results
+
+overall_skew_results2 <- all_di %>%
+  filter(s0 > 2, log_nparts > log(50)) %>%
+  mutate(high_skew = skew_percentile > 95) %>%
+  group_by(dat) %>%
+  summarize(proportion_skew_high = mean(high_skew),
+            nsites_skew = dplyr::n())
+
+overall_simpson_results2 <- all_di %>%
+  filter(log_nparts > log(50)) %>%
+  mutate(low_even = simpson_percentile < 5) %>%
+  group_by(dat) %>%
+  summarize(proportion_even_low = mean(low_even),
+            nsites_even = dplyr::n())
+
+overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2)
+
+overall_results2
 
@@
 
-fia_sized <- filter(all_di, s0 <= fia_max_s,n0 <= fia_max_n) %>%
+fia_max_nparts <-max(filter(all_di, dat == "fia")$log_nparts)
+
+fia_sized <- filter(all_di, s0 <= fia_max_s, n0 <= fia_max_n) %>%
   mutate(fia_yn = dat == "fia") %>%
-  mutate(fia_yn = ifelse(fia_yn, "FIA", "Other datasets"))
+  mutate(fia_yn = ifelse(fia_yn, "FIA", "Other datasets")) %>%
+  mutate(right_corner = FALSE)
 
-ggplot(filter(fia_sized, s0 > 2, nparts > 10), aes(skew_percentile)) +
+ggplot(filter(fia_sized, s0 > 2, nparts > 50), aes(skew_percentile)) +
   geom_histogram() +
@@
 
-ggplot(filter(fia_sized, s0 > 2, log_nparts > 5, nparts > 10), aes(skew_percentile)) +
+ggplot(fia_sized, aes(x = log_nparts)) +
   geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  geom_vline(xintercept = log(50))
 
-ggplot(filter(fia_sized, s0 > 2, log_nparts <  5, nparts > 10), aes(skew_percentile)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y")
+ggplot(fia_sized, aes(s0, n0, color = fia_yn)) +
+  geom_point()
 
@@
 
+ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts < exp(7)), aes(skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("50-1,000 parts in FS")
+
+ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(7)), aes(skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("More than 1,000 parts in FS")
+
+ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(10)), aes(skew_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y") +
+  ggtitle("More than 20,000 parts in FS")
 ```

### 2020-08-04 analysis/reports/figs2.Rmd
include incl argument to test effect of less than v less than equal to

--- 2020-07-31 analysis/manuscript/reports/figs2.Rmd
@@
 
-all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "reports", "all_di_old.csv"), stringsAsFactors = F)
 
@@
 gridExtra::grid.arrange(grobs = list(
-ggplot(filter(small, !singletons, s0 > 2), aes(skew_percentile)) +
+ggplot(filter(small, !singletons, s0 > 2, log_nparts > log(50)), aes(skew_percentile)) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(filter(small, !singletons), aes(simpson_percentile)) +
+ggplot(filter(small, !singletons, s0 > 2), aes(skew_percentile)) +
   geom_histogram(bins = 100) +
@@
   facet_wrap(vars(is_fia), scales = "free_y") +
-  geom_vline(xintercept = 5, color = "red", linetype = 3) +
-  ggtitle("Small communities percentile: Evenness")), ncol = 1)
+  geom_vline(xintercept = 95, color = "red", linetype = 3) +
+  ggtitle("Small communities percentile: Skewness")#,
+
+# 
+# ggplot(filter(small, !singletons), aes(simpson_percentile)) +
+#   geom_histogram(bins = 100) +
+#   theme_bw() +
+#   facet_wrap(vars(is_fia), scales = "free_y") +
+#   geom_vline(xintercept = 5, color = "red", linetype = 3) +
+#   ggtitle("Small communities percentile: Evenness")
+), ncol = 1)
+
+small %>%
+  filter(s0 > 2) %>%
+  group_by(is_fia) %>%
+  summarize(prop_skew_high = mean(skew_percentile > 95),
+            nsites = dplyr::n())
+
+small %>%
+  filter(s0 > 2, nparts > 500) %>%
+  group_by(is_fia) %>%
+  summarize(prop_skew_high = mean(skew_percentile > 95),
+            nsites = dplyr::n())
+
+small %>%
+  group_by(is_fia) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            nsites = dplyr::n())
+
+small %>%
+    filter(s0 > 2, nparts > 500) %>%
+  group_by(is_fia) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            nsites = dplyr::n())
 

### 2020-08-04 analysis/reports/manuscript_main.Rmd
include incl argument to test effect of less than v less than equal to

@@
 
-ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(7)), aes(skew_percentile)) +
+ggplot(filter(fia_sized, s0 > 2, nparts >= exp(7), nparts < exp(10)), aes(skew_percentile)) +
   geom_histogram() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("More than 1,000 parts in FS")
+  ggtitle("1,000 - 20,000 parts in FS")
 

### 2020-08-04 R/metrics.R

@@ -37,7 +37,9 @@ add_dis <- function(fs_samples_df) {
     dplyr::filter(source == "observed", sim < 0) %>%
     dplyr::mutate(skew_percentile = get_percentile(skew, a_vector = sim_percentiles$skew),
                   shannon_percentile = get_percentile(shannon, a_vector = sim_percentiles$shannon),
-                  simpson_percentile = get_percentile(simpson, a_vector = sim_percentiles$simpson))
+                  simpson_percentile = get_percentile(simpson, a_vector = sim_percentiles$simpson),
+                  skew_percentile_excl = get_percentile(skew, a_vector = sim_percentiles$skew, incl =F),
+                  simpson_percentile_excl = get_percentile(simpson, a_vector = sim_percentiles$simpson, incl = F))
 
 
   sim_dis <- dplyr::bind_rows(sim_percentiles, sampled_percentile)
@@ -50,15 +52,16 @@ add_dis <- function(fs_samples_df) {
 #' Calculate the percentile values (% of elements in the vector <= a value) for all values in a vector
 #'
 #' @param a_vector Vector of values
+#' @param incl tf lessthan or equal to or just less than
 #'
 #' @return Vector of percentile values for all values in the vector
 #' @export
 #'
-get_percentiles <- function(a_vector) {
+get_percentiles <- function(a_vector, incl = T) {
 
   nvals <- sum(!(is.na(a_vector)))
 
-  percentile_vals <- vapply(as.matrix(a_vector), FUN = count_below, a_vector = a_vector, FUN.VALUE = 100)
+  percentile_vals <- vapply(as.matrix(a_vector), FUN = count_below, a_vector = a_vector, incl = incl, FUN.VALUE = 100)
 
   for(i in 1:length(a_vector)) {
     if(!(is.nan(a_vector[i]))) {
@@ -75,12 +78,17 @@ get_percentiles <- function(a_vector) {
 #'
 #' @param a_value Focal value
 #' @param a_vector Vector for comparison
+#' @param incl include end or not? if true, <=, if false, <
 #'
 #' @return Number of values in vector less than or equal to the focal value
 #' @export
 #'
-count_below <- function(a_value, a_vector) {
+count_below <- function(a_value, a_vector, incl = T) {
+  if(incl) {
   return(sum(a_vector <= a_value, na.rm = T))
+  } else {
+    return(sum(a_vector < a_value, na.rm = T))
+  }
 }
 
[…]

### 2020-08-05 analysis/reports/less_than_equal.Rmd
move old reporst to old_reports directory

--- 2020-08-03 analysis/reports/manuscript_main.Rmd
@@
 
-# Illustrations of 95% interval
+```{r skew change}
 
-To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities.
+ggplot(filter(all_di, s0 > 2), aes(x = skew_percentile_excl, y = skew_percentile, color = nsamples)) +
+  geom_point() +
+  facet_wrap(vars(dat))
 
-# Skewness and evenness histograms by dataset
+all_di <- all_di  %>%
+  mutate(skew_change = skew_percentile - skew_percentile_excl,
+         even_change = simpson_percentile -
+           simpson_percentile_excl)
 
-```{r first hists}
-
-ggplot(filter(all_di, s0 > 2), aes(skew_percentile)) +
-  geom_histogram(bins = 100) +
-  geom_vline(xintercept = 95, color = "red") +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")
-
-ggplot(all_di, aes(simpson_percentile)) + 
- geom_histogram(bins = 100) +
-  geom_vline(xintercept = 5, color = "red") +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
-```
-
-# Proportion of sites with highly skewed or uneven SADs
-
-```{r results table}
-
-overall_skew_results <- all_di %>%
-  filter(s0 > 2) %>%
-  mutate(high_skew = skew_percentile > 95) %>%
-  group_by(dat) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results <- all_di %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(dat) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results <- left_join(overall_skew_results, overall_simpson_results)
-
-overall_results
+ggplot(filter(all_di, s0 > 2), aes(x = log_nparts, y = skew_change)) +
+  geom_point() +
+  xlim(0,15) +
+  facet_wrap(vars(dat))
 
@@
 
-There are fewer sites for skewness because we exclude sites with only 2 species.
-
-# Size of feasible set for each dataset
-
-```{r fs size hists}
-
-all_di <- all_di %>%
-  mutate(log_nparts_truncated = ifelse(
-    log_nparts > 50,
-    50,
-    log_nparts)
-  )
-
-ggplot(all_di, aes(log_nparts_truncated)) +
-  geom_histogram() +
-  facet_wrap(vars(dat), scales = "free_y") +
-  theme_bw()
-
-fs_size_results <- all_di %>%
-  group_by(dat) %>%
-  summarize(prop_smaller_than_5=  mean(log_nparts <= 5),
-            prop_smaller_than_7 =  mean(log_nparts <= 7),
-            prop_smaller_than_10 = mean(log_nparts <= 10))
-fs_size_results
+```{r hists}
 
 ```
-
-FIA is the only dataset that is overwhelmingly dominated by sites with fewer than `r exp(10)` elements in the feasible set.
-MCDB also has many small sites, but these are counterbalanced by larger ones.
-
-62% of the FIA sites have fewer than `r exp(7)` elements in the feasible set, and 30% have fewer than `r exp(5)`.
-
-```{r fs size to s0 and n0, fig.dim = c(3,3)}
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 5)) +
-  geom_point() +
-  theme_bw() +
-  theme(legend.position = "top")
-
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 7)) +
-  geom_point() +
-  theme_bw()+
-  theme(legend.position = "top")
-
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 10)) +
-  geom_point() +
-  theme_bw()+
-  theme(legend.position = "top")
-```
-
-Having fewer than 150 elements ~ fewer than 3 species, or fewer than `r exp(2.75)` individuals  with up to 20 species.
-
-Fewer than 1000 elements ~ fewer than 3 species, or fewer than `r exp(3.25)` individuals with up to 20 species.
-
-Fewer than 20000 elements ~ fewer than 4 species, or fewer than `r exp(4)` individuals.
-
-# 95% interval for small versus large communities
-
-```{r 95 interval}
-
-ggplot(all_di, aes(x = log_nparts, y = skew_95_ratio_1t)) +
-  geom_point(alpha = .2) + theme_bw() + ggtitle("Skewness 95% interval")
-
-ggplot(all_di, aes(x = log_nparts, y = skew_95_ratio_1t)) +
-  geom_point(alpha = .01) +
-  xlim(0, 15) +
-  theme_bw() +
-  ggtitle("Skewness 95% interval - only small feasible sets")
-
-ggplot(all_di, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
-  geom_point(alpha = .2) + theme_bw()+ ggtitle("Evenness 95% interval")
-
-ggplot(all_di, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
-  geom_point(alpha = .05) +
-  xlim(0, 15) +
-  theme_bw()+
-  ggtitle("Evenness 95% interval - only small feasible sets")
-
-```
-
-The 95% ratio decreases for large FS.
-
-For skewness, it is still quite high even up to 20,000 elements in the FS. But it is starting to decline by then?
-
-# Comparison of FIA to similarly-sized communities
-
-```{r fia sized}
-fia_max_s <- max(filter(all_di, dat == "fia")$s0)
-fia_max_n <- max(filter(all_di, dat == "fia")$n0)
-
-fia_sized <- filter(all_di, s0 <= fia_max_s,n0 <= fia_max_n) %>%
-  mutate(fia_yn = dat == "fia") %>%
-  mutate(fia_yn = ifelse(fia_yn, "FIA", "Other datasets"))
-
-ggplot(filter(fia_sized, s0 > 2, nparts > 10), aes(skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
-
-ggplot(filter(fia_sized, s0 > 2, log_nparts > 5, nparts > 10), aes(skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
-
-ggplot(filter(fia_sized, s0 > 2, log_nparts <  5, nparts > 10), aes(skew_percentile)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y")
-
-```
-
-# Removing the smallest communities from FIA
-
-```{r fia no small}
-
-```

### 2020-08-05 analysis/reports/manuscript_main.Rmd
move old reporst to old_reports directory

--- 2020-08-04 analysis/reports/manuscript_main.Rmd
@@
 
+ggplot(filter(fia_sized, s0 > 2, nparts > 50), aes(skew_percentile_excl)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+ggplot(filter(fia_sized, s0 > 2), aes(skew_percentile_excl)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
 ggplot(fia_sized, aes(x = log_nparts)) +
@@
 
-ggplot(fia_sized, aes(s0, n0, color = fia_yn)) +
-  geom_point()
+fia_sized %>%
+  filter(s0 > 2) %>%
+  group_by(fia_yn) %>%
+  summarize(prop_skew_high = mean(skew_percentile > 95),
+            nsites = dplyr::n())
+
+fia_sized %>%
+  filter(s0 > 2, nparts > 50) %>%
+  group_by(fia_yn) %>%
+  summarize(prop_skew_high = mean(skew_percentile > 95),
+            nsites = dplyr::n())
+
+fia_sized %>%
+  group_by(fia_yn) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            nsites = dplyr::n())
+
+fia_sized %>%
+    filter(s0 > 2, nparts > 50) %>%
+  group_by(fia_yn) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            nsites = dplyr::n())
 
@@
 ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts < exp(7)), aes(skew_percentile)) +
-  geom_histogram() +
+  geom_histogram(bins = 50) + theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
@@
 
-ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(7)), aes(skew_percentile)) +
-  geom_histogram() +
+ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts < exp(7)), aes(x = log(s0), y = log(n0), color = fia_yn)) +
+  geom_point(alpha = .2) +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(fia_sized, s0 > 2, nparts >= exp(7), nparts < exp(10)), aes(skew_percentile)) +
+  geom_histogram(bins = 50) + theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("More than 1,000 parts in FS")
+  ggtitle("1,000 - 20,000 parts in FS")
+
+ggplot(filter(fia_sized, s0 > 2, nparts >= exp(7), nparts < exp(10)), aes(x = log(s0), y = log(n0), color = fia_yn)) +
+  geom_point(alpha = .2) +
+  facet_wrap(vars(fia_yn))
 
 ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(10)), aes(skew_percentile)) +
-  geom_histogram() +
+  geom_histogram(bins = 50) + theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
   ggtitle("More than 20,000 parts in FS")
+
+ggplot(filter(fia_sized, s0 > 2, nparts >= exp(7), nparts < exp(10)), aes(x = log(s0), y = log(n0), color = fia_yn)) +
+  geom_point(alpha = .2) +
+  facet_wrap(vars(fia_yn))
 ```

### 2020-08-05 analysis/reports/old_reports/fia_size.Rmd
move old reporst to old_reports directory

--- 2020-05-07 analysis/reports/fia_size.Rmd
@@
 
-all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "reports", "all_di_old.csv"), stringsAsFactors = F)
 all_di_old <- read.csv(here::here("all_di.csv"), stringsAsFactors = F)
@@
 
-fia_sized <- filter(all_di, s0 <= fia_max_s, !singletons, n0 <= fia_max_n) %>%
+fia_sized <- filter(all_di, s0 <= fia_max_s, !singletons, n0 <= fia_max_n, s0 > 2) %>%
   mutate(fia_yn = dat == "fia") %>%

### 2020-08-05 tests/testthat/test05_diversity_indices.R

@@ -116,6 +116,56 @@ test_that("get percentile works if focal value is edge of comparison vector", {
 })
 
 
+
+
+test_that("get percentile works with incl = F", {
+
+  foo <- seq(1, 100, by = 5)
+
+  foo_percentiles <- get_percentiles(foo, incl = F)
+
+  expect_equivalent(foo_percentiles, seq(0, 95, by = 5))
+
+  a_val <- 17
+
+  a_per <- get_percentile(a_val, foo, incl =F)
+
+  by_hand <- 100 * sum(foo < a_val) / length(foo)
+
+  expect_equivalent(by_hand, a_per)
+
+  # Edges of comparison
+
+    foo <- seq(10, 100, by = 5)
+
+  low_focal_value <- 10
+
+  low_per <- get_percentile(low_focal_value, foo, incl = F)
+
+  high_focal_value <- 100
+
+  high_per <- get_percentile(high_focal_value, foo, F)
+
+  # Outside vector
+
+  expect_equivalent(low_per, 0)
+  expect_equivalent(high_per, 100 -  100/length(foo))
+
+  low_focal_value <- 5
+
+  low_per <- get_percentile(low_focal_value, foo, incl =F)
+
+  high_focal_value <- 110
+
+  high_per <- get_percentile(high_focal_value, foo, incl =F)
+
+  expect_equivalent(low_per, 0)
+  expect_equivalent(high_per, 100)
+
+
+})
+
+
 test_that("pull_di works", {
 
   dat <- load_dataset("mcdb")

### 2020-08-05 analysis/reports/less_than_equal.Rmd
working on ltet and add nb of unique skew and even values to pull_di outputs

@@
 ---
-title: "Figures and results for main manuscript"
+title: "Effect of < v <= in percentile definition"
+author: Renata Diaz
+date: "`r Sys.Date()`"
 output: 
@@
 
-all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
-
-all_di <- all_di %>%
-  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
-         log_nsamples = log(nsamples),
-         log_s0 = log(s0),
-         log_n0 = log(n0)) %>%
-  filter(n0 > s0,
-         !singletons,
-         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
-  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
-         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
 ```
 
-# Final dataset in S and N space
+You can define the %ile score as either
 
-```{r final dataset s and n space}
+- the % of values in a comparison vector that are **less than** a focal value
+- the % of values that are **less than or equal to** that value
 
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
-  geom_point(alpha = .01) +
-  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d() +
-  ggtitle("Communities by S and N")
+You see both definitions out in the world.
+
+When I initially coded up the analysis, I used **<**. I didn't think about it much and as I was writing the manuscript I wrote **<=**. So that got me curious if it matters.
+
+It *should not* matter too much as long as there are many unique values in the comparison vector.
+However, if there are only a handful, and the focal value is equal to an element of the comparison vector, using <= will cause the score to jump up.
+The jumps will be in increments of 100/n, with n the number of elements in the comparison vector.
+Meaning if there is only one value, < will give a score of 0 and <= will give a score of 100!
+And if there are ties, and the focal value is equal to the tie value, the jump will be (100 / n) * m, with m the number of elements in the comparison vector equal to the tie value.
+
+#### Demo with toy data
+
+```{r a handful of values, echo = T}
+
+percentile_lt <- function(focal, comparison) {
+  100 * (sum(comparison < focal) / length(comparison))
+}
+
+percentile_ltet <- function(focal, comparison) {
+  100 * (sum(comparison <= focal) / length(comparison))
+}
+
+# Many values
+
+many <- seq(1, 100, by = .1)
+
+focal <- runif(1, 1, 100)
+focal <- round(focal, 1) # rounding so focal == a value in many
+
+percentile_lt(focal, many)
+percentile_ltet(focal, many)
+
+# A few values
+few <- seq(1, 101, by = 20)
+
+focal <- ceiling(focal / 20) * 20 + 1 # again, rounding so focal == a value in few
+
+percentile_lt(focal, few)
+
+percentile_ltet(focal, few)
+
+# A few values with ties
+few_with_ties <- c(seq(1, 81, by = 20), 41)
+
+focal <- 41 # if focal == tie value, you get the largest possible jump
+
+percentile_lt(focal, few_with_ties)
+
+percentile_ltet(focal, few_with_ties)
+
+# Just one value
+
+one <- runif(1, 1, 100)
+
+focal <- one # if there is only 1 element in one, focal MUST be that element
+
+percentile_lt(focal, one)
+percentile_ltet(focal, one)
 
@@
 
-```{r skew change}
+#### For our purposes
 
-ggplot(filter(all_di, s0 > 2), aes(x = skew_percentile_excl, y = skew_percentile, color = nsamples)) +
-  geom_point() +
-  facet_wrap(vars(dat))
+We can expect using <= to give us, if anything, higher percentile scores.
+We can expect this effect to be more pronounced for distributions with relatively few unique values.
+This is probably strongly correlated with the number of unique elements in the feasible set and the number of unique samples we found from the feasible set, but is not necessarily identical to it because two unique samples can have the same values for skewness or evenness.
+This will create **ties**, which can cause quite large jumps.
 
-all_di <- all_di  %>%
-  mutate(skew_change = skew_percentile - skew_percentile_excl,
-         even_change = simpson_percentile -
-           simpson_percentile_excl)
+If the comparison vector is short, and/or has repeated values, we may get noticeably higher scores using <= than using <.
+Usually I think being short has a larger effect than having ties - unless you have a very long vector that is all ties, which doesn't happen in this context - and being short makes ties more impactful.
 
-ggplot(filter(all_di, s0 > 2), aes(x = log_nparts, y = skew_change)) +
-  geom_point() +
-  xlim(0,15) +
-  facet_wrap(vars(dat))
+Especially if the feasible set is small, the focal value is guaranteed to be an element of the comparison vector.
+That is because the comparison vector, for small FS, is an exhaustive account of all possible values for the focal value.
 
-```
+<!-- ```{r real data, include=FALSE} -->
 
-```{r hists}
+<!-- all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F) -->
 
-```
+<!-- all_di <- all_di %>% -->
+<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)), -->
+<!--          log_nsamples = log(nsamples), -->
+<!--          log_s0 = log(s0), -->
+<!--          log_n0 = log(n0)) %>% -->
+<!--   filter(n0 > s0, -->
+<!--          !singletons, -->
+<!--          dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>% -->
+<!--   mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat), -->
+<!--          dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) -->
+<!-- ``` -->
+
+<!-- # Final dataset in S and N space -->
+
+<!-- ```{r final dataset s and n space} -->
+
+<!-- ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) + -->
+<!--   geom_point(alpha = .01) + -->
+<!--   geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) + -->
+<!--   theme_bw() + -->
+<!--   scale_color_viridis_d() + -->
+<!--   ggtitle("Communities by S and N") -->
+
+<!-- ``` -->
+
+<!-- ```{r skew change} -->
+
+<!-- ggplot(filter(all_di, s0 > 2), aes(x = skew_percentile_excl, y = skew_percentile, color = nsamples)) + -->
+<!--   geom_point() + -->
+<!--   facet_wrap(vars(dat)) -->
+
+<!-- all_di <- all_di  %>% -->
+<!--   mutate(skew_change = skew_percentile - skew_percentile_excl, -->
+<!--          even_change = simpson_percentile - -->
+<!--            simpson_percentile_excl) -->
+
+<!-- ggplot(filter(all_di, s0 > 2), aes(x = log_nparts, y = skew_change)) + -->
+<!--   geom_point() + -->
+<!--   xlim(0,15) + -->
+<!--   facet_wrap(vars(dat)) -->
+
+<!-- ``` -->
+
+<!-- ```{r hists} -->
+
+<!-- ``` -->

### 2020-08-05 R/metrics.R

@@ -137,10 +137,8 @@ pull_di <- function(di_df) {
     dplyr::summarize(skew_range = max(skew, na.rm = T) - min(skew, na.rm = T),
                      simpson_range = max(simpson, na.rm = T) - min(simpson, na.rm = T),
                      nsamples = length(unique(sim)),
-                     skew_sd = sd(skew, na.rm = T),
-                     skew_mean = mean(skew, na.rm = T),
-                     simpson_sd = sd(simpson, na.rm = T),
-                     simpson_mean = mean(simpson, na.rm = T),
+                     skew_unique = length(unique(skew, na.rm = T)),
+                     simpson_unique = length(unique(simpson, na.rm = T)),
                      skew_2p5 = quantile(skew, probs = c(0.025), na.rm = T),
                      skew_97p5 = quantile(skew, probs = c(0.975), na.rm = T),
                      skew_95 = quantile(skew, probs = c(0.95), na.rm = T),

### 2020-08-05 analysis/reports/smallness.Rmd
shiny app for size comparisons

---
title: "Size class small comparisons"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

```

```{r real data, include=FALSE}

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         !singletons,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
```

##### Results for small (FIA sized) communities

Here are the results when we try to tell whether FIA communities differ qualitatively from similarly-sized communities from other datasets...

###### Small sites

Note that, even for small sites, "other datasets" are generally larger than FIA....

```{r small, fig.dim = c(4,3)}

fia_max_s = max(filter(all_di, dat == "fia")$s0)
fia_max_n = max(filter(all_di, dat == "fia")$n0)

fia = filter(all_di, dat == "fia")

small_di <- all_di %>%
  filter(s0 <= fia_max_s,
         n0 <= fia_max_n) %>%
  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
         right_corner = FALSE)

for(i in 1:nrow(small_di)) {
  if(small_di$dat[i] != "fia") {
    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])

    max_n0_for_this_s0 = max(fia_match_s0$n0)

    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0

  }
}

small_di <- small_di %>%
  filter(!right_corner)

ggplot(small_di, aes(x = s0, y = n0, color = log_nparts)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .7) +
  facet_wrap(vars(fia_yn)) +
  theme(legend.position = "top")

ggplot(small_di, aes(log_nparts)) +
  geom_histogram(bins = 30) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")

```

###### Skew for small sites
```{r skewness small, fig.dim = c(4, 3)}

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <=")

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <")

small_di %>%
  filter(s0 > 2) %>%
  group_by(fia_yn) %>%
  summarize(prop_skew_high_ltet = mean(skew_percentile > 95),
            prop_skew_high_lt = mean(skew_percentile_excl > 95),
            n_skew_sites = dplyr::n())

```

###### Evenness
```{r evenness result small, fig.dim = c(4, 3)}

ggplot(filter(small_di), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <=")

ggplot(filter(small_di), aes(x = simpson_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <")

small_di %>%
  group_by(fia_yn) %>%
  summarize(prop_even_low_ltet = mean(simpson_percentile < 5),
            prop_even_low_lt = mean(simpson_percentile_excl < 5),
            n_even_sites = dplyr::n())

```

For these comparisons, 
- For skewness, the effect is weak for both FIA and not-FIA (5% and 8% in the extremes, respectively)
- For evenness, the effect is much stronger for not-FIA (8 vs 15%)
- < vs <= matters quite a bit
    - Many of these sites can be quite small. Since we flagged a concern about having fewer than, arbitrarily, 100 elements, let's remove those:

###### Skew for small sites, removing very small
```{r skewness small no tiny, fig.dim = c(4, 3)}

small_di <- small_di %>%
  filter(nparts > 100)

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <=")

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <")

small_di %>%
  filter(s0 > 2) %>%
  group_by(fia_yn) %>%
  summarize(prop_skew_high_ltet = mean(skew_percentile > 95),
            prop_skew_high_lt = mean(skew_percentile_excl > 95),
            n_skew_sites = dplyr::n())

```

###### Evenness
```{r evenness result small no tiny, fig.dim = c(4, 3)}

ggplot(filter(small_di), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <=")

ggplot(filter(small_di), aes(x = simpson_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <")

small_di %>%
  group_by(fia_yn) %>%
  summarize(prop_even_low_ltet = mean(simpson_percentile < 5),
            prop_even_low_lt = mean(simpson_percentile_excl < 5),
            n_even_sites = dplyr::n())

```

Removing sites with fewer than 100 elements in the feasible set

- *eliminates the difference between <= and <*
- We see a difference between FIA and other datasets 
    - For skew, 6 vs 12% in the extremes
    - For even, 10 vs 25% in the extremes

I am skeptical of these comparisons. It may be that FIA is behaving qualitatively differently, but it may also be that, because the other datasets are less concentrated at *very small* FS, the effect of FS size still drives the difference even when we filter like this. On the strength of this filtering I'm not confident arguing *either* that FIA is qualitatively different, independent of size, or that these subsets are behaving the same.

I think a stronger comparison would be to break into size classes based on the number of parts.

### 2020-08-05 analysis/reports/size_comparisons/app.R

@@ -1,0 +1,156 @@
+#
+# This is a Shiny web application. You can run the application by clicking
+# the 'Run App' button above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+library(ggplot2)
+library(dplyr)
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+
+    # Application title
+    titlePanel("Results"),
+
+    # Sidebar with a slider input for number of bins
+    sidebarLayout(
+        sidebarPanel(
+            sliderInput("minparts",
+                        "Minimum number of parts:",
+                        min = 0,
+                        max = 17,
+                        value = 4.6,
+                        step = .001),
+            sliderInput("maxparts",
+                        "Maximum number of parts:",
+                        min = 0,
+                        max = 17,
+                        value = 6.9,
+                        step = .001)
+        ),
+
+        # Show a plot of the generated distribution
+        mainPanel(
+            tableOutput("sizeRange"),
+            plotOutput("windowPlot", width = 400, height = 200),
+            plotOutput("skewPlot", width = 400, height = 200),
+            tableOutput("skewResults"),
+            plotOutput("evenPlot", width = 400, height = 200),
+            tableOutput("evenResults")
+        )
+    )
+)
+
+# Define server logic required to draw a histogram
+server <- function(input, output) {
+
+    all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+
+    all_di <- all_di %>%
+        mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+               log_nsamples = log(nsamples),
+               log_s0 = log(s0),
+               log_n0 = log(n0)) %>%
+        filter(n0 > s0,
+               !singletons,
+               dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
+        mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+               dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
+
+
+    fia_max_s = max(filter(all_di, dat == "fia")$s0)
+    fia_max_n = max(filter(all_di, dat == "fia")$n0)
+
+    fia = filter(all_di, dat == "fia")
+
+    small_di <- all_di %>%
[…]

### 2020-08-05 analysis/reports/smallness.Rmd
gleanings from shiny

@@
 library(ggplot2)
-
+knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE) 
 ```
@@
 
-###### Skew for small sites
-```{r skewness small, fig.dim = c(4, 3)}
+Having played around with the shiny app (size_comparisons), here are some static plots that I think are faithful to what I glean from tinkering with cutoffs.
 
-ggplot(filter(small_di, s0 >2), aes(x = skew_percentile)) +
+##### Trivially small
+
+For a range of about 1-300 elements in the FS, I wouldn't argue for any kind of detectable pattern in any of the results:
+
+```{r trivially small}
+
+minparts = 1
+maxparts = 300
+
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts,
+              s0 > 2), aes(skew_percentile_excl)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Skew, <=")
+  theme_bw()
 
-ggplot(filter(small_di, s0 >2), aes(x = skew_percentile_excl)) +
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Skew, <")
+  theme_bw()
 
 small_di %>%
-  filter(s0 > 2) %>%
+  filter(nparts< maxparts, nparts > minparts,
+         s0 > 2) %>%
   group_by(fia_yn) %>%
-  summarize(prop_skew_high_ltet = mean(skew_percentile > 95),
-            prop_skew_high_lt = mean(skew_percentile_excl > 95),
-            n_skew_sites = dplyr::n())
+  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
+            nskew_sites = dplyr::n())
+
+small_di %>%
+  filter(nparts< maxparts, nparts > minparts) %>% 
+  group_by(fia_yn) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            neven_sites = dplyr::n())
 
@@
 
-###### Evenness
-```{r evenness result small, fig.dim = c(4, 3)}
+##### Small but not trivially small
 
-ggplot(filter(small_di), aes(x = simpson_percentile)) +
+There's one dynamic from a minimum of around 50 to 10000 elements, where:
+
+- Not really anything detectable for skewness
+- A weak effect for evenness for FIA, and quite a strong effect for evenness for other datasets
+
+```{r medium small}
+
+minparts = 50
+maxparts = 10000
+
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts,
+              s0 > 2), aes(skew_percentile_excl)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Even, <=")
+  theme_bw()
 
-ggplot(filter(small_di), aes(x = simpson_percentile_excl)) +
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Even, <")
+  theme_bw()
 
 small_di %>%
+  filter(nparts< maxparts, nparts > minparts,
+         s0 > 2) %>%
   group_by(fia_yn) %>%
-  summarize(prop_even_low_ltet = mean(simpson_percentile < 5),
-            prop_even_low_lt = mean(simpson_percentile_excl < 5),
-            n_even_sites = dplyr::n())
+  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
+            nskew_sites = dplyr::n())
+
+small_di %>%
+  filter(nparts< maxparts, nparts > minparts) %>% 
+  group_by(fia_yn) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            neven_sites = dplyr::n())
 
@@
 
-For these comparisons, 
-- For skewness, the effect is weak for both FIA and not-FIA (5% and 8% in the extremes, respectively)
-- For evenness, the effect is much stronger for not-FIA (8 vs 15%)
-- < vs <= matters quite a bit
-    - Many of these sites can be quite small. Since we flagged a concern about having fewer than, arbitrarily, 100 elements, let's remove those:
+##### Big
 
-###### Skew for small sites, removing very small
-```{r skewness small no tiny, fig.dim = c(4, 3)}
+And then anything over about 1500 elements:
 
-small_di <- small_di %>%
-  filter(nparts > 100)
+- Effects for both skewness and evenness, which only get stronger as you increase the minimum
+- Consistently more pronounced for other datasets for FIA, but the difference decreases as you increase the minimum
 
-ggplot(filter(small_di, s0 >2), aes(x = skew_percentile)) +
+```{r big}
+
+minparts = 1500
+maxparts = exp(30)
+
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts,
+              s0 > 2), aes(skew_percentile_excl)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Skew, <=")
+  theme_bw()
 
-ggplot(filter(small_di, s0 >2), aes(x = skew_percentile_excl)) +
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Skew, <")
+  theme_bw()
 
 small_di %>%
-  filter(s0 > 2) %>%
+  filter(nparts< maxparts, nparts > minparts,
+         s0 > 2) %>%
   group_by(fia_yn) %>%
-  summarize(prop_skew_high_ltet = mean(skew_percentile > 95),
-            prop_skew_high_lt = mean(skew_percentile_excl > 95),
-            n_skew_sites = dplyr::n())
+  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
+            nskew_sites = dplyr::n())
+
+small_di %>%
+  filter(nparts< maxparts, nparts > minparts) %>% 
+  group_by(fia_yn) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            neven_sites = dplyr::n())
 
@@
 
-###### Evenness
-```{r evenness result small no tiny, fig.dim = c(4, 3)}
+##### Really big
 
-ggplot(filter(small_di), aes(x = simpson_percentile)) +
+Such that, over about 10000 elements, FIA looks similar to other datasets.
+
+```{r really big}
+
+minparts = 10000
+maxparts = exp(30)
+
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts,
+              s0 > 2), aes(skew_percentile_excl)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Even, <=")
+  theme_bw()
 
-ggplot(filter(small_di), aes(x = simpson_percentile_excl)) +
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
   geom_histogram(bins = 100) +
-  theme_bw() +
   facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("Even, <")
+  theme_bw()
 
 small_di %>%
+  filter(nparts< maxparts, nparts > minparts,
+         s0 > 2) %>%
   group_by(fia_yn) %>%
-  summarize(prop_even_low_ltet = mean(simpson_percentile < 5),
-            prop_even_low_lt = mean(simpson_percentile_excl < 5),
-            n_even_sites = dplyr::n())
+  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
+            nskew_sites = dplyr::n())
+
+small_di %>%
+  filter(nparts< maxparts, nparts > minparts) %>% 
+  group_by(fia_yn) %>%
+  summarize(prop_even_low = mean(simpson_percentile < 5),
+            neven_sites = dplyr::n())
 
 ```
-
-Removing sites with fewer than 100 elements in the feasible set
-
-- *eliminates the difference between <= and <*
-- We see a difference between FIA and other datasets 
-    - For skew, 6 vs 12% in the extremes
-    - For even, 10 vs 25% in the extremes
-
-I am skeptical of these comparisons.
-It may be that FIA is behaving qualitatively differently, but it may also be that, because the other datasets are less concentrated at *very small* FS, the effect of FS size still drives the difference even when we filter like this.
-On the strength of this filtering I'm not confident arguing *either* that FIA is qualitatively different, independent of size, or that these subsets are behaving the same.
-
-I think a stronger comparison would be to break into size classes based on the number of parts.

### 2020-08-05 analysis/reports/manuscript_main.Rmd
some updates to manusciprt and manuscript figures

--- 2020-08-04 analysis/reports/manuscript_main.Rmd
@@
 
-ggplot(filter(all_di, s0 > 2), aes(skew_percentile)) +
-  geom_histogram(bins = 100) +
-  geom_vline(xintercept = 95, color = "red") +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")
-
-ggplot(filter(all_di, s0 > 2, log_nparts > log(50)), aes(skew_percentile)) +
+ggplot(filter(all_di, s0 > 2), aes(skew_percentile_excl)) +
   geom_histogram(bins = 100) +
@@
   facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
-ggplot(filter(all_di, log_nparts > log(50)), aes(simpson_percentile)) + 
- geom_histogram(bins = 100) +
-  geom_vline(xintercept = 5, color = "red") +
-  theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
+
 ```
@@
   filter(s0 > 2) %>%
-  mutate(high_skew = skew_percentile > 95) %>%
+  mutate(high_skew = skew_percentile_excl > 95) %>%
   group_by(dat) %>%
@@
 overall_skew_results2 <- all_di %>%
-  filter(s0 > 2, log_nparts > log(50)) %>%
-  mutate(high_skew = skew_percentile > 95) %>%
-  group_by(dat) %>%
+  mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
+  filter(s0 > 2) %>%
+  mutate(high_skew = skew_percentile_excl > 95) %>%
+  group_by(fia_yn) %>%
   summarize(proportion_skew_high = mean(high_skew),
@@
 overall_simpson_results2 <- all_di %>%
-  filter(log_nparts > log(50)) %>%
+   mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
   mutate(low_even = simpson_percentile < 5) %>%
-  group_by(dat) %>%
+  group_by(fia_yn) %>%
   summarize(proportion_even_low = mean(low_even),
@@
 
-There are fewer sites for skewness because we exclude sites with only 2 species.
+```{r 95 intervals}
 
-# Size of feasible set for each dataset
+ggplot(all_di, aes(x = log_nparts, y= skew_95_ratio_1t)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  xlim(0, 100)
 
-```{r fs size hists}
-
-all_di <- all_di %>%
-  mutate(log_nparts_truncated = ifelse(
-    log_nparts > 50,
-    50,
-    log_nparts)
-  )
-
-ggplot(all_di, aes(log_nparts_truncated)) +
-  geom_histogram() +
-  facet_wrap(vars(dat), scales = "free_y") +
-  theme_bw()
-
-fs_size_results <- all_di %>%
-  group_by(dat) %>%
-  summarize(prop_smaller_than_5=  mean(log_nparts <= 5),
-            prop_smaller_than_7 =  mean(log_nparts <= 7),
-            prop_smaller_than_10 = mean(log_nparts <= 10))
-fs_size_results
+ggplot(all_di, aes(x = log_nparts, y= simpson_95_ratio_1t)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  xlim(0, 100)
 
 ```
-
-FIA is the only dataset that is overwhelmingly dominated by sites with fewer than `r exp(10)` elements in the feasible set.
-MCDB also has many small sites, but these are counterbalanced by larger ones.
-
-62% of the FIA sites have fewer than `r exp(7)` elements in the feasible set, and 30% have fewer than `r exp(5)`.
-
-```{r fs size to s0 and n0, fig.dim = c(3,3)}
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 5)) +
-  geom_point() +
-  theme_bw() +
-  theme(legend.position = "top")
-
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 7)) +
-  geom_point() +
-  theme_bw()+
-  theme(legend.position = "top")
-
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = log_nparts <= 10)) +
-  geom_point() +
-  theme_bw()+
-  theme(legend.position = "top")
-```
-
-Having fewer than 150 elements ~ fewer than 3 species, or fewer than `r exp(2.75)` individuals  with up to 20 species.
-
-Fewer than 1000 elements ~ fewer than 3 species, or fewer than `r exp(3.25)` individuals with up to 20 species.
-
-Fewer than 20000 elements ~ fewer than 4 species, or fewer than `r exp(4)` individuals.
-
-# 95% interval for small versus large communities
-
-```{r 95 interval}
-
-ggplot(all_di, aes(x = log_nparts, y = skew_95_ratio_1t)) +
-  geom_point(alpha = .2) + theme_bw() + ggtitle("Skewness 95% interval")
-
-ggplot(all_di, aes(x = log_nparts, y = skew_95_ratio_1t)) +
-  geom_point(alpha = .01) +
-  xlim(0, 15) +
-  theme_bw() +
-  ggtitle("Skewness 95% interval - only small feasible sets")
-
-ggplot(all_di, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
-  geom_point(alpha = .2) + theme_bw()+ ggtitle("Evenness 95% interval")
-
-ggplot(all_di, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
-  geom_point(alpha = .05) +
-  xlim(0, 15) +
-  theme_bw()+
-  ggtitle("Evenness 95% interval - only small feasible sets")
-
-```
-
-The 95% ratio decreases for large FS.
-
-For skewness, it is still quite high even up to 20,000 elements in the FS. But it is starting to decline by then?
-
-# Comparison of FIA to similarly-sized communities
-
-```{r fia sized}
-fia_max_s <- max(filter(all_di, dat == "fia")$s0)
-fia_max_n <- max(filter(all_di, dat == "fia")$n0)
-
-fia_max_nparts <-max(filter(all_di, dat == "fia")$log_nparts)
-
-fia_sized <- filter(all_di, s0 <= fia_max_s, n0 <= fia_max_n) %>%
-  mutate(fia_yn = dat == "fia") %>%
-  mutate(fia_yn = ifelse(fia_yn, "FIA", "Other datasets")) %>%
-  mutate(right_corner = FALSE)
-
-ggplot(filter(fia_sized, s0 > 2, nparts > 50), aes(skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
-
-ggplot(fia_sized, aes(x = log_nparts)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  geom_vline(xintercept = log(50))
-
-ggplot(fia_sized, aes(s0, n0, color = fia_yn)) +
-  geom_point()
-
-```
-
-# Removing the smallest communities from FIA
-
-```{r fia no small}
-
-ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts < exp(7)), aes(skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("50-1,000 parts in FS")
-
-ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(7)), aes(skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("More than 1,000 parts in FS")
-
-ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(10)), aes(skew_percentile)) +
-  geom_histogram() +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  ggtitle("More than 20,000 parts in FS")
-```

### 2020-08-05 analysis/reports/smallness.Rmd
some updates to manusciprt and manuscript figures

@@
 
+this_di <- small_di %>%
+            filter(nparts > minparts,
+                   nparts < maxparts)
+
+        ggplot(small_di, aes(x = (s0), y = (n0))) +
+            geom_point() +
+            geom_point(data = this_di, color = "blue") +
+            theme_bw() +
+            facet_wrap(vars(fia_yn))
+
 ggplot(filter(small_di,
@@
 
+ ggplot(small_di, aes(log_nparts)) +
+            geom_histogram(bins = 30) +
+            theme_bw() +
+            facet_wrap(vars(fia_yn), scales = "free_y") +
+            geom_vline(xintercept = c(log(minparts),
+                                      log(maxparts)), color = "red")
+
 ggplot(filter(small_di,
@@
 
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts), aes(skew_95_ratio_1t)) +
+         geom_histogram() +
+         theme_bw()
+
+ggplot(filter(small_di,
+              nparts< maxparts, nparts > minparts), aes(simpson_95_ratio_1t)) +
+         geom_histogram() +
+         theme_bw()
 small_di %>%
@@
   theme_bw()
-
+ ggplot(small_di, aes(log_nparts)) +
+            geom_histogram(bins = 30) +
+            theme_bw() +
+            facet_wrap(vars(fia_yn), scales = "free_y") +
+            geom_vline(xintercept = c(log(minparts),
+                                      log(maxparts)), color = "red")
 ggplot(filter(small_di,
@@
 
+ ggplot(small_di, aes(log_nparts)) +
+            geom_histogram(bins = 30) +
+            theme_bw() +
+            facet_wrap(vars(fia_yn), scales = "free_y") +
+            geom_vline(xintercept = c(log(minparts),
+                                      log(maxparts)), color = "red")
 ggplot(filter(small_di,

### 2020-08-06 analysis/reports/smallness.Rmd
DIRECT COMPARISONS, update di_obs test

--- 2020-08-05 analysis/reports/smallness.Rmd
@@
 
-##### Results for small (FIA sized) communities
+The FIA sites stand out from the other datasets in that, overall, they do not show pronouncedly extreme values. This is especially the case for skewness:
 
-Here are the results when we try to tell whether FIA communities differ qualitatively from similarly-sized communities from other datasets...
+```{r overall hists}
 
-###### Small sites
+ggplot(filter(all_di, s0 > 2), aes(skew_percentile_excl)) +
+  geom_histogram(bins = 20) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y")
 
-Note that, even for small sites, "other datasets" are generally larger than FIA....
+ggplot(filter(all_di), aes(simpson_percentile)) +
+  geom_histogram(bins = 20) +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y")
+```
+
+One possible explanation for this is that the FIA sites tend to have quite small S and N, leading to quite a small feasible set and potentially quite a broad distribution of expected values for skewness and evenness.
+
+It is also possible that the FIA datasets differ qualitatively from other datasets, and that this drives the difference.
+
+We may be able to disentangle these possibilities by
+
+- Comparing the FIA sites to sites from other datasets that are of a similar size
+- Looking at the breadth of the distributions for these sites relative to larger sites
+
+If we compare the FIA sites to sites from other datasets that are of a similar size, the comparison is limited by the fact that our sites are nonuniformly distributed in SxN space, or in terms of the the number of elements in their feasible sets.
+Specifically, the FIA datasets are concentrated towards **especially small** feasible sets compared "other datasets" - even the ones that fall within the general range found in FIA.
 
@@
 
-Having played around with the shiny app (size_comparisons), here are some static plots that I think are faithful to what I glean from tinkering with cutoffs.
+This means that an overall histogram for FIA would be representative more of sites in the 4-7 parts range, while one for "other datasets" would be representative of more of a spread from 3-16 parts.
+Given that we suspect the number of parts is quite important, this is a sticky problem.
 
-##### Trivially small
+One option, which I haven't considered before, is to subsample __FIA__ to match "other datasets". 
+If we subsample so there is equal representation of all S and N combinations between FIA and "other datasets", we end up with 309 combinations represented and a total of 488 comparisons.
 
-For a range of about 1-300 elements in the FS, I wouldn't argue for any kind of detectable pattern in any of the results:
+```{r subsampling}
 
-```{r trivially small}
+not_fia <- filter(small_di, fia_yn != "fia")
+fia = filter(small_di, dat == "fia")
 
-minparts = 1
-maxparts = 300
+small_di_s_n <- small_di %>%
+  select(s0, n0) %>%
+  distinct() %>%
+  mutate(in_fia = FALSE,
+         in_not_fia = FALSE)
 
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts,
-              s0 > 2), aes(skew_percentile_excl)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 
+  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
+
+}
+
+small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
+
+set.seed(1977)
+
+subsamples <- list()
+
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
+
+  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
+  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
+
+  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
+
+}
+
+sub_di <- bind_rows(subsamples)
+# 
+# ggplot(sub_di, aes(log(s0), log(n0), color = fia_yn)) +
+#   geom_point() +
+#   facet_wrap(vars(fia_yn))
+# 
+# 
+# ggplot(sub_di, aes(log_nparts)) +
+#   geom_histogram() +
+#   facet_wrap(vars(fia_yn))
+
+ggplot(small_di, aes(log(s0), log(n0))) +
+  geom_point(color = "gray") +
+  theme_bw() +
+  geom_point(data = sub_di, alpha = 1)
+
+ggplot(sub_di, aes(log_nparts)) +
+  geom_histogram() +
   theme_bw()
+```
 
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  theme_bw()
+The dark dots are the sites for which we can find at least one exact match in s0 and n0 between a FIA site and a site from another dataset.
+The histogram is the distribution of FS sizes represented in the subsample.
 
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts,
-         s0 > 2) %>%
+Here are the results for that subsample:
+
+```{r subsample results}
+
+ggplot(sub_di, aes(skew_percentile_excl)) +
+  geom_histogram()+
+  theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+ggplot(sub_di, aes(simpson_percentile)) +
+  geom_histogram()+
+  theme_bw() +
+  facet_wrap(vars(fia_yn), scales = "free_y")
+
+sub_di %>%
+  filter(s0 > 2) %>%
   group_by(fia_yn) %>%
   summarize(prop_skew_high = mean(skew_percentile_excl > 95),
-            nskew_sites = dplyr::n())
-
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts) %>% 
-  group_by(fia_yn) %>%
-  summarize(prop_even_low = mean(simpson_percentile < 5),
-            neven_sites = dplyr::n())
+            prop_even_low = mean(simpson_percentile < 5),
+            nsites = dplyr::n())
 
@@
 
-##### Small but not trivially small
-
-There's one dynamic from a minimum of around 50 to 10000 elements, where:
-
-- Not really anything detectable for skewness
-- A weak effect for evenness for FIA, and quite a strong effect for evenness for other datasets
-
-```{r medium small}
-
-minparts = 50
-maxparts = 10000
-
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts,
-              s0 > 2), aes(skew_percentile_excl)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  theme_bw()
-
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  theme_bw()
-
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts,
-         s0 > 2) %>%
-  group_by(fia_yn) %>%
-  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
-            nskew_sites = dplyr::n())
-
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts) %>% 
-  group_by(fia_yn) %>%
-  summarize(prop_even_low = mean(simpson_percentile < 5),
-            neven_sites = dplyr::n())
-
-```
-
-##### Big
-
-And then anything over about 1500 elements:
-
-- Effects for both skewness and evenness, which only get stronger as you increase the minimum
-- Consistently more pronounced for other datasets for FIA, but the difference decreases as you increase the minimum
-
-```{r big}
-
-minparts = 1500
-maxparts = exp(30)
-
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts,
-              s0 > 2), aes(skew_percentile_excl)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  theme_bw()
-
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  theme_bw()
-
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts,
-         s0 > 2) %>%
-  group_by(fia_yn) %>%
-  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
-            nskew_sites = dplyr::n())
-
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts) %>% 
-  group_by(fia_yn) %>%
-  summarize(prop_even_low = mean(simpson_percentile < 5),
-            neven_sites = dplyr::n())
-
-```
-
-##### Really big
-
-Such that, over about 10000 elements, FIA looks similar to other datasets.
-
-```{r really big}
-
-minparts = 10000
-maxparts = exp(30)
-
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts,
-              s0 > 2), aes(skew_percentile_excl)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  theme_bw()
-
-ggplot(filter(small_di,
-              nparts< maxparts, nparts > minparts), aes(simpson_percentile)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(fia_yn), scales = "free_y") +
-  theme_bw()
-
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts,
-         s0 > 2) %>%
-  group_by(fia_yn) %>%
-  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
-            nskew_sites = dplyr::n())
-
-small_di %>%
-  filter(nparts< maxparts, nparts > minparts) %>% 
-  group_by(fia_yn) %>%
-  summarize(prop_even_low = mean(simpson_percentile < 5),
-            neven_sites = dplyr::n())
-
-```
+For the subsample that is directly comparable, there is **not a difference** between FIA and other datasets in the distribution of percentile values.
+This is a very small subsample relative to all the sites in both datasets - FIA has 20,000 sites overall, and we are only looking at 500 of them.
+However, given how sensitive results aggregated in this way are to the relative frequency of SxN combinations/FS sizes in the sample, I believe this is the most robust way we can ask whether *being from FIA* causes detectably different outcomes.

### 2020-08-06 analysis/crosscheck.R

@@ -1,97 +1,0 @@
-library(dplyr)
-library(ggplot2)
-all_di <- read.csv(here::here("analysis", "reports", "all_di_old.csv"), stringsAsFactors = F)
-all_di_old <- read.csv(here::here("all_di.csv"), stringsAsFactors = F)
-
-fia_small_provisional <- filter(all_di_old, dat == "fia_small")
-
-all_di_spring <- bind_rows(all_di, fia_small_provisional)
-
-
-rm(all_di)
-rm(all_di_old)
-rm(fia_small_provisional)
-
-all_di_summer <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F) %>%
-  mutate(site = as.character(site))
-
-colnames(all_di_summer)
-colnames(all_di_spring)
-
-check_di <- all_di_spring %>%
-  filter(dat != "portal_rodents", dat != "portal_plants") %>%
-  select(dat, site, singletons, nparts, skew_percentile, simpson_percentile, s0, n0, nsamples, skew_range) %>%
-  rename(         skew_percentile_s = skew_percentile,
-         simpson_percentile_s = simpson_percentile,
-         skew_range_s = skew_range) %>%
-  full_join(select(all_di_summer, dat, site, singletons, nparts, skew_percentile, simpson_percentile, s0, n0, skew_range)) %>%
-  filter(dat != "fia_small") %>% # different set of sites
-  mutate(skew_change = skew_percentile - skew_percentile_s,
-         even_change = simpson_percentile - simpson_percentile_s)
-
-sort(as.numeric(filter(all_di_summer, dat == "fia_small")$site)) == sort(as.numeric(filter(all_di_spring, dat == "fia_small")$site))
-
-head((filter(all_di_summer, dat == "fia_small")$site))
-head((filter(all_di_spring, dat == "fia_small")$site))
-
-ggplot(check_di, aes(skew_percentile_s, skew_percentile, color = nsamples)) + geom_point()
-
-
-ggplot(filter(check_di, log(nparts) > log(20), s0 > 2), aes(skew_percentile_s, skew_percentile, color = nsamples)) + geom_point()
-
-ggplot(filter(check_di, log(nparts) > log(150), s0 > 2), aes(skew_percentile_s, skew_percentile, color = nsamples)) + geom_point()
[…]

### 2020-08-07 analysis/reports/manuscript_main.Rmd
run this

@@
   filter(n0 > s0,
+         s0 > 1,
          !singletons,

### 2020-08-07 analysis/reports/rov_metric.Rmd
run this

---
title: "Explaining and exploring the 95% interval metric"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE) 
```

```{r real data, include=FALSE}

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         !singletons,
         s0 > 1,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
```

One of the crucial threads of reasoning for comparing observations to an emergent statistical expectation is that the expectation be sufficiently specific to allow us to make robust comparisons. *Often*, with sufficiently large systems (also described as sufficiently large scale separation between the subcomponents and the aggregate characteristic of interest; H&L), we can rely on the expectation being extremely narrowly peaked. It is, however, not clear what "sufficiently large" means. We can expect that *some* ecological systems are definitely not large in this sense - if there are only 6 species and 3 individuals, the feasible set is trivially small. Nor is it a given that the expectations do actually get appreciably more peaked with increasing S and N.

We would like to know:

* How the shape, and specifically the narrowness, of the expectation changes over an ecologically-relevant gradient in S and N
* If, as we might expect given the above intuition about larger systems, small systems have less steep peaks: whether the change in the shape of the expectation corresponds with the change in our results. 
    * This is kind of slippery. Ideally we would find a way to measure our statistical power.

To do this we need to establish

* A way of measuring the shape, and specifically the narrowness, of the expectation
* How the shape changes over gradients
* How the shape constrains the kind of deviation we *could* detect (?)
* How the shape maps on to the presence/absence of detected deviations

## Illustrating the expectation

We obtain the expectation by drawing samples from the feasible set and constructing the distribution of values for *summary statistics* for all of those elements.

## Measuring the shape (narrowness)

## Mapping the shape over a gradient in S and N

It can be difficult to interpret the distribution of interval values from our actual datasets, because they are irregularly distributed over S by N space. So we can drop a net over the relevant S by N gradient and sample *regularly* from it.

```{r define net}

all_di_net <- all_di %>%
  select(s0, n0) %>%
  distinct()

ggplot(all_di_net, aes(log(s0), log(n0))) +
  geom_point() +
  geom_vline(xintercept = log(200)) +
  geom_hline(yintercept = c(log(40720)))

net_s0 <- floor(exp(seq(.5, log(200), by = .3))) %>%
  unique()

net_n0 <- 1+ floor(exp(seq(.5, 10, by = .75))) %>%
  unique()

net <- expand.grid(net_s0, net_n0) %>%
  rename(s0 = Var1, n0 = Var2) %>%
  filter(n0 > s0,
         s0 > 1)

ggplot(all_di_net, aes(log(s0), log(n0))) +
  geom_point() +
  geom_vline(xintercept = log(200)) +
  geom_hline(yintercept = c(log(40720))) +
  geom_point(data = net, color = "purple")

```

### 2020-08-07 R/metrics.R

@@ -160,3 +160,45 @@ pull_di <- function(di_df) {
   return(di_observed)
 
 }
+
+#' Summarize just samples
+#'
+#' Extracts summary information about the distribution of shape metric values from the samples from the FS:
+#'
+#' - Number of unique samples found from the FS
+#' - Range, mean, standard deviation, min, max, .25, .95, and .975 quantiles for the distributions of skewness and evenness from the samples
+#' - Ratio of the width of two-tailed and one-tailed 95% intervals to the full range for both skewness and evenness. For skewness, the one-tailed interval is from 0-.95; for evenness, the one-tailed interval is from .05-1. The two-tailed intervals are from .025 to .975.
+#'
+#' @param di_df result of di_wrapper
+#'
+#' @return di_df for ONLY samples
+#' @export
+#'
+#' @importFrom dplyr filter mutate group_by ungroup summarize left_join
+pull_di_net <- function(di_df) {
+
+  di_sampled <- di_df %>%
+    dplyr::group_by(s0, n0,dat, site, nparts) %>%
+    dplyr::summarize(skew_range = max(skew, na.rm = T) - min(skew, na.rm = T),
+                     simpson_range = max(simpson, na.rm = T) - min(simpson, na.rm = T),
+                     nsamples = length(unique(sim)),
+                     skew_unique = length(unique(skew, na.rm = T)),
+                     simpson_unique = length(unique(simpson, na.rm = T)),
+                     skew_2p5 = quantile(skew, probs = c(0.025), na.rm = T),
+                     skew_97p5 = quantile(skew, probs = c(0.975), na.rm = T),
+                     skew_95 = quantile(skew, probs = c(0.95), na.rm = T),
+                     skew_min = min(skew, na.rm = T),
+                     simpson_max = max(simpson, na.rm = T),
+                     simpson_2p5 = quantile(simpson, probs = c(0.025), na.rm = T),
+                     simpson_5 = quantile(simpson, probs = c(.05), na.rm = T),
+                     simpson_97p5 = quantile(simpson, probs = c(0.975), na.rm = T)) %>%
+    dplyr::ungroup() %>%
+    dplyr::mutate(skew_95_ratio_2t = (skew_97p5 - skew_2p5)/skew_range,
+                  simpson_95_ratio_2t = (simpson_97p5 - simpson_2p5)/simpson_range,
+                  skew_95_ratio_1t = (skew_95 - skew_min)/skew_range,
[…]

### 2020-08-07 analysis/reports/rov_comparisons/app.R

@@ -24,14 +24,14 @@ ui <- fluidPage(
                         "Minimum 95 interval: skew",
                         min = 0,
                         max = 1,
-                        value = .01,
-                        step = .001),
+                        value = .95,
+                        step = .01),
             sliderInput("max_skew_interval",
                         "Maximum 95 interval: skew",
                         min = 0,
                         max = 1,
-                        value = .99,
-                        step = .001),
+                        value = 1,
+                        step = .01),
             sliderInput("min_even_interval",
                         "Minimum 95 interval: even",
                         min = 0,
@@ -51,13 +51,13 @@ ui <- fluidPage(
                   plotOutput("skew_intervalHist", width = 400, height = 200),
                   plotOutput("skew_snPlot", width = 400, height = 200),
                   plotOutput("skewPlot", width = 400, height = 200),
-                  tableOutput("skewResults"),
-                  plotOutput("even_intervalPlot", width = 400, height = 200),
-                  plotOutput("even_intervalHist", width = 400, height = 200),
-
-                  plotOutput("even_snPlot", width = 400, height = 200),
-                  plotOutput("evenPlot", width = 400, height = 200),
-                  tableOutput("evenResults")
+                  tableOutput("skewResults")#,
+                  # plotOutput("even_intervalPlot", width = 400, height = 200),
+                  # plotOutput("even_intervalHist", width = 400, height = 200),
+                  #
+                  # plotOutput("even_snPlot", width = 400, height = 200),
+                  # plotOutput("evenPlot", width = 400, height = 200),
+                  # tableOutput("evenResults")
         )
     )
 )
@@ -100,13 +100,11 @@ server <- function(input, output) {
     })
     output$skew_intervalHist <- renderPlot({
 
-        skew_di <- filter(all_di, skew_95_ratio_1t > input$min_skew_interval,
-                          skew_95_ratio_1t < input$max_skew_interval, s0 >2)
-
-        ggplot(skew_di, aes(x = skew_95_ratio_1t)) +
-            geom_histogram() +
+        ggplot(filter(all_di, s0 >2), aes(x = skew_95_ratio_1t)) +
+            geom_histogram(bins = 100) +
             theme_bw()+
-            xlim(0, 1)
+            xlim(0, 1) +
+            geom_vline(xintercept = c(input$max_skew_interval, input$min_skew_interval), color = "red")
     })
[…]

### 2020-08-07 analysis/reports/rov_metric.Rmd
i d o n ' t k n ow

@@
 library(ggplot2)
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
 knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE) 
@@
 
+For example, for a community with 44 species and 13360 individuals, here is the feasible set:
+
+```{r example fs}
+
+net_summary <- readd(all_di_summary, cache = cache)
+
+net_summary <- net_summary %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)))
+
+example_fs <- readd(fs_s_44_n_13360, cache = cache)
+
+example_di <- readd(di_fs_s_44_n_13360, cache =cache)
+
+example_fs <- example_fs %>%
+  left_join(example_di) %>%
+  left_join(net_summary)
+
+example_fs2 <- readd(fs_s_7_n_71, cache = cache)
+
+example_di2 <- readd(di_fs_s_7_n_71, cache =cache)
+
+example_fs2 <- example_fs2 %>%
+  left_join(example_di2) %>%
+  left_join(net_summary)
+
+ggplot(example_fs, aes(rank, abund, group = sim)) +
+  geom_line(alpha = .01) +
+  theme_bw()
+
+```
+
+Every vector in the feasible set can be summarized according to its skewness or evenness value:
+
+```{r example fs skew and even}
+
+ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) +
+  geom_line(alpha = .05) +
+  theme_bw() +
+  scale_color_viridis_c()
+
+ggplot(example_fs, aes(rank, abund, group = sim, color = simpson)) +
+  geom_line(alpha = .05) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .8)
+
+```
+
+We use the distribution of values for skewness and evenness, from our samples from the feasible set, as the expectation for the values of skewness and evenness for an observation.
+
+```{r example dists}
+
+ggplot(example_fs, aes(skew, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw()
+
+ggplot(example_fs, aes(simpson, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw()
+
+```
+
+Here is what this can look like for a smaller feasible set - for example, 7 species and 71 individuals:
+
+```{r smaller example}
+
+ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) +
+  geom_line(alpha = .05) +
+  theme_bw() +
+  scale_color_viridis_c()
+
+ggplot(example_fs2, aes(rank, abund, group = sim, color = simpson)) +
+  geom_line(alpha = .05) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .8)
+
+ggplot(example_fs2, aes(skew, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw()
+
+ggplot(example_fs2, aes(simpson, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw()
+
+```
+
 ## Measuring the shape (narrowness)
+
+The actual values of skewness and evenness change over the gradients of S and N. Also, as evident above, these aren't necessarily normally distributed.
+
+I have computed the ratio of a 95% interval relative to the full range of values. Here is what that looks like.
+
+```{r illustrate 95 interval}
+
+ggplot(example_fs, aes(skew, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw() +
+  geom_vline(xintercept = c(example_fs$skew_2p5[1], example_fs$skew_97p5[1]), color = "red")
+
+ggplot(example_fs, aes(simpson, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw() +
+  geom_vline(xintercept = c(example_fs$simpson_97p5[1], example_fs$simpson_2p5[1]), color = "red")
+
+ggplot(example_fs2, aes(skew, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw() +
+  geom_vline(xintercept = c(example_fs2$skew_2p5[1], example_fs2$skew_97p5[1]), color = "red")
+
+ggplot(example_fs2, aes(simpson, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw() +
+  geom_vline(xintercept = c(example_fs2$simpson_97p5[1], example_fs2$simpson_2p5[1]), color = "red")
+
+```
 
@@
 
-ggplot(all_di_net, aes(log(s0), log(n0))) +
-  geom_point() +
-  geom_vline(xintercept = log(200)) +
-  geom_hline(yintercept = c(log(40720)))
+net <- readd(dat, cache = cache)
 
-net_s0 <- floor(exp(seq(.5, log(200), by = .3))) %>%
-  unique()
-
-net_n0 <- 1+ floor(exp(seq(.5, 10, by = .75))) %>%
-  unique()
-
-net <- expand.grid(net_s0, net_n0) %>%
-  rename(s0 = Var1, n0 = Var2) %>%
-  filter(n0 > s0,
-         s0 > 1)
+net <- net %>%
+  mutate(s0 = rank,
+         n0 = abund)
 
@@
   geom_vline(xintercept = log(200)) +
-  geom_hline(yintercept = c(log(40720))) +
+  geom_hline(yintercept = c(log(404420))) +
   geom_point(data = net, color = "purple")
@@
 ```
+
+```{r nparts}
+
+ggplot(net_summary, aes(x = log_nparts, y = skew_95_ratio_1t)) +
+  geom_point() +
+  theme_bw()
+
+ggplot(net_summary, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
+  geom_point() +
+  theme_bw()
+```

### 2020-08-09 analysis/reports/rov_metric.Rmd
im confused :(

@@
 cache$del(key = "lock", namespace = "session")
-knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE) 
+knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE) 
 ```
@@
 
+example_fs3 <- readd(fs_s_3_n_34, cache = cache)
+
+example_di3 <- readd(di_fs_s_3_n_34, cache =cache)
+
+example_fs3 <- example_fs3 %>%
+  left_join(example_di3) %>%
+  left_join(net_summary)
+
 ggplot(example_fs, aes(rank, abund, group = sim)) +
@@
 
+And for a very small feasible set:
+
+```{r tiny example}
+
+ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) +
+  geom_line(alpha = .05) +
+  theme_bw() +
+  scale_color_viridis_c()
+
+ggplot(example_fs3, aes(rank, abund, group = sim, color = simpson)) +
+  geom_line(alpha = .05) +
+  theme_bw() +
+  scale_color_viridis_c(option = "plasma", end = .8)
+
+ggplot(example_fs3, aes(skew, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw()
+
+ggplot(example_fs3, aes(simpson, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw()
+
+```
+
 ## Measuring the shape (narrowness)
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs$skew_2p5[1], example_fs$skew_97p5[1]), color = "red")
+  geom_vline(xintercept = c(example_fs$skew_2p5[1], example_fs$skew_97p5[1]), color = "red") +
+  ggtitle(paste0("Skew 95% interval: ", round(example_fs$skew_95_ratio_2t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs$simpson_97p5[1], example_fs$simpson_2p5[1]), color = "red")
+  geom_vline(xintercept = c(example_fs$simpson_97p5[1], example_fs$simpson_2p5[1]), color = "red") +
+  ggtitle(paste0("Simpson 95% interval: ", round(example_fs$simpson_95_ratio_2t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs2$skew_2p5[1], example_fs2$skew_97p5[1]), color = "red")
+  geom_vline(xintercept = c(example_fs2$skew_2p5[1], example_fs2$skew_97p5[1]), color = "red") +
+  ggtitle(paste0("Skew 95% interval: ", round(example_fs2$skew_95_ratio_2t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs2$simpson_97p5[1], example_fs2$simpson_2p5[1]), color = "red")
+  geom_vline(xintercept = c(example_fs2$simpson_97p5[1], example_fs2$simpson_2p5[1]), color = "red") +
+  ggtitle(paste0("Simpson 95% interval: ", round(example_fs2$simpson_95_ratio_2t[1], 2)))
+
+ggplot(example_fs3, aes(skew, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw() +
+  geom_vline(xintercept = c(example_fs3$skew_2p5[1], example_fs3$skew_97p5[1]), color = "red") +
+  ggtitle(paste0("Skew 95% interval: ", round(example_fs3$skew_95_ratio_2t[1], 2)))
+
+ggplot(example_fs3, aes(simpson, ..ndensity..)) +
+  geom_density() +
+  geom_histogram(bins = 50) +
+  theme_bw() +
+  geom_vline(xintercept = c(example_fs3$simpson_97p5[1], example_fs3$simpson_2p5[1]), color = "red") +
+  ggtitle(paste0("Simpson 95% interval: ", round(example_fs3$simpson_95_ratio_2t[1], 2)))
+
+hitting_the_ceiling <- example_fs3 %>%
+  select(sim, skew) %>%
+  distinct() %>%
+  mutate(max_skew = max(skew, na.rm = T)) %>%
+  mutate(equals_max = skew == max_skew)
 
@@
 
+Here is how these 95% intervals vary over the *net* of points:
+
+```{r intervals on net}
+
+ggplot(filter(net_summary, s0 > 2, skew_unique > 1), aes(log(s0), log(n0), color = skew_95_ratio_2t)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c()
+
+ggplot(filter(net_summary,simpson_unique > 1), aes(log(s0), log(n0), color = simpson_95_ratio_2t)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(option = "plamsa")
+
+```
+
 ```{r nparts}
 
-ggplot(net_summary, aes(x = log_nparts, y = skew_95_ratio_1t)) +
+ggplot(filter(net_summary, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_2t, color = log(n0/s0))) +
   geom_point() +
@@
 
-ggplot(net_summary, aes(x = log_nparts, y = simpson_95_ratio_1t)) +
+ggplot(net_summary, aes(x = log_nparts, y = simpson_95_ratio_2t, color = log(n0/s0))) +
   geom_point() +
   theme_bw()
+
 ```

### 2020-08-10 analysis/reports/nunique.Rmd

--- 2020-08-07 analysis/reports/rov_metric.Rmd
@@
 ```
-
-One of the crucial threads of reasoning for comparing observations to an emergent statistical expectation is that the expectation be sufficiently specific to allow us to make robust comparisons.
-*Often*, with sufficiently large systems (also described as sufficiently large scale separation between the subcomponents and the aggregate characteristic of interest; H&L), we can rely on the expectation being extremely narrowly peaked.
-It is, however, not clear what "sufficiently large" means.
-We can expect that *some* ecological systems are definitely not large in this sense - if there are only 6 species and 3 individuals, the feasible set is trivially small.
-Nor is it a given that the expectations do actually get appreciably more peaked with increasing S and N.
-
-We would like to know:
-
-* How the shape, and specifically the narrowness, of the expectation changes over an ecologically-relevant gradient in S and N
-* If, as we might expect given the above intuition about larger systems, small systems have less steep peaks: whether the change in the shape of the expectation corresponds with the change in our results.
-    * This is kind of slippery. Ideally we would find a way to measure our statistical power.
-
-To do this we need to establish
-
-* A way of measuring the shape, and specifically the narrowness, of the expectation
-* How the shape changes over gradients
-* How the shape constrains the kind of deviation we *could* detect (?)
-* How the shape maps on to the presence/absence of detected deviations
-
-## Illustrating the expectation
-
-We obtain the expectation by drawing samples from the feasible set and constructing the distribution of values for *summary statistics* for all of those elements.
-
-## Measuring the shape (narrowness)
-
-## Mapping the shape over a gradient in S and N
-
-It can be difficult to interpret the distribution of interval values from our actual datasets, because they are irregularly distributed over S by N space.
-So we can drop a net over the relevant S by N gradient and sample *regularly* from it.
-
-```{r define net}
-
-all_di_net <- all_di %>%
-  select(s0, n0) %>%
-  distinct()
-
-ggplot(all_di_net, aes(log(s0), log(n0))) +
-  geom_point() +
-  geom_vline(xintercept = log(200)) +
-  geom_hline(yintercept = c(log(40720)))
-
-net_s0 <- floor(exp(seq(.5, log(200), by = .3))) %>%
-  unique()
-
-net_n0 <- 1+ floor(exp(seq(.5, 10, by = .75))) %>%
-  unique()
-
-net <- expand.grid(net_s0, net_n0) %>%
-  rename(s0 = Var1, n0 = Var2) %>%
-  filter(n0 > s0,
-         s0 > 1)
-
-ggplot(all_di_net, aes(log(s0), log(n0))) +
-  geom_point() +
-  geom_vline(xintercept = log(200)) +
-  geom_hline(yintercept = c(log(40720))) +
-  geom_point(data = net, color = "purple")
-
-```

### 2020-08-10 analysis/reports/manuscript_main.Rmd
reinstate direct size comparison

@@
 
-ggplot(filter(all_di, s0 > 2), aes(skew_percentile_excl)) +
+ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(all_di, aes(simpson_percentile)) + 
+ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
  geom_histogram(bins = 100) +
@@
 overall_skew_results <- all_di %>%
-  filter(s0 > 2) %>%
+  filter(s0 > 2, skew_unique > 20) %>%
   mutate(high_skew = skew_percentile_excl > 95) %>%
@@
 overall_simpson_results <- all_di %>%
+  filter(simpson_unique > 20) %>%
   mutate(low_even = simpson_percentile < 5) %>%
@@
   mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
-  filter(s0 > 2) %>%
+  filter(s0 > 2, skew_unique > 20) %>%
   mutate(high_skew = skew_percentile_excl > 95) %>%
@@
 overall_simpson_results2 <- all_di %>%
+  filter(simpson_unique > 20) %>%
    mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
@@
 
-ggplot(all_di, aes(x = log_nparts, y= skew_95_ratio_1t)) +
+ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
   geom_point(alpha = .1) +
@@
 
-ggplot(all_di, aes(x = log_nparts, y= simpson_95_ratio_1t)) +
+ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
   geom_point(alpha = .1) +

### 2020-08-10 analysis/reports/nunique.Rmd
reinstate direct size comparison

@@
          dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
+
+ggplot(filter(all_di, s0> 2), aes(skew_percentile_excl)) +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(all_di, s0> 2, skew_unique > 100), aes(skew_percentile_excl)) +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(dat), scales = "free_y")
+
 ```

### 2020-08-10 analysis/reports/smallness.Rmd
reinstate direct size comparison

@@
 
-ggplot(filter(all_di, s0 > 2), aes(skew_percentile_excl)) +
+ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
   geom_histogram(bins = 20) +
@@
 
-ggplot(filter(all_di), aes(simpson_percentile)) +
+ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) +
   geom_histogram(bins = 20) +
@@
 
-ggplot(small_di, aes(log_nparts)) +
+ggplot(filter(small_di), aes(log_nparts)) +
   geom_histogram(bins = 30) +
@@
 
-ggplot(sub_di, aes(skew_percentile_excl)) +
+ggplot(filter(sub_di, skew_unique > 20), aes(skew_percentile_excl)) +
   geom_histogram()+
@@
 
-ggplot(sub_di, aes(simpson_percentile)) +
+ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_percentile)) +
   geom_histogram()+
@@
   facet_wrap(vars(fia_yn), scales = "free_y")
+# 
+# 
+# 
+# ggplot(filter(sub_di), aes(skew_percentile_excl)) +
+#   geom_histogram()+
+#   theme_bw() +
+#   facet_wrap(vars(fia_yn), scales = "free_y")
+# 
+# ggplot(filter(sub_di), aes(simpson_percentile)) +
+#   geom_histogram()+
+#   theme_bw() +
+#   facet_wrap(vars(fia_yn), scales = "free_y")
 
@@
   filter(s0 > 2) %>%
+  group_by_all %>%
+  mutate(skew_percentile_excl = ifelse(skew_unique >= 20, skew_percentile_excl, NA),
+         simpson_percentile = ifelse(simpson_unique >= 20, simpson_percentile, NA)) %>%
+  ungroup() %>%
   group_by(fia_yn) %>%
-  summarize(prop_skew_high = mean(skew_percentile_excl > 95),
-            prop_even_low = mean(simpson_percentile < 5),
-            nsites = dplyr::n())
+  summarize(prop_skew_high = mean(skew_percentile_excl > 95, na.rm = T),
+            prop_even_low = mean(simpson_percentile < 5, na.rm = T),
+            nsites_skew = sum(!is.na(skew_percentile_excl)),
+            nsites_even = sum(!is.na(simpson_percentile)))
 
+sum(sub_di$skew_unique < 20)
+sum(sub_di$simpson_unique < 20)
 ```

### 2020-08-11 analysis/reports/rov_metric.Rmd
manuscript for Morgan

@@
 
-example_fs3 <- readd(fs_s_3_n_34, cache = cache)
+example_fs3 <- readd(fs_s_4_n_34, cache = cache)
 
-example_di3 <- readd(di_fs_s_3_n_34, cache =cache)
+example_di3 <- readd(di_fs_s_4_n_34, cache =cache)
 
@@
 ```
+```{r fig for manuscript, fig.dim = c(3, 9)}
+
+samples_plots <- list(
+
+  ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .25) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle(paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1])), subtitle = paste0(round(exp(example_fs3$log_nparts[1]), 0), " elements in FS")) +
+    theme(legend.position = "top"),
+
+  ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .1) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle(paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1])), subtitle = paste0(round(exp(example_fs2$log_nparts[1]), 0), " elements in FS")) +
+    theme(legend.position = "top"),
+  ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .1) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle(paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1])), subtitle =  paste0(round(exp(example_fs$log_nparts[1]), 0), " elements in FS")) +
+    theme(legend.position = "top")
+)
+
+intervals_plots <- list(
+
+  ggplot(example_fs3, aes(skew, ..ndensity..)) +
+    geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") +
+    ggtitle(paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs3$skew_95_ratio_2t[1]), 2))),
+
+  ggplot(example_fs2, aes(skew, ..ndensity..)) +
+    geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") +
+    ggtitle(paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs2$skew_95_ratio_2t[1]), 2))),
+
+  ggplot(example_fs, aes(skew, ..ndensity..)) +
+    geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") +
+    ggtitle(paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs$skew_95_ratio_2t[1]), 2)))
+
+)
+
+gridExtra::grid.arrange(grobs = samples_plots, ncol = 1)
+gridExtra::grid.arrange(grobs = intervals_plots, ncol = 1)
+
+```
 

### 2020-08-12 analysis/reports/direct_FIA_size_comparison.Rmd
tidying reports

--- 2020-08-10 analysis/reports/smallness.Rmd
@@
 ---
-title: "Size class small comparisons"
+title: "Comparing FIA sites to similarly-sized counterparts"
 author: Renata Diaz
@@
 
-One option, which I haven't considered before, is to subsample __FIA__ to match "other datasets". 
-If we subsample so there is equal representation of all S and N combinations between FIA and "other datasets", we end up with 309 combinations represented and a total of 488 comparisons.
+We can subsample __FIA__ so there is equal representation of all S and N combinations between FIA and "other datasets".
+
+Some details on the subsampling:
+
+* We look for exact matches in S and N, with at least one site from FIA and at least one site from the pool of other datasets. 
+* If there are multiple exact matches (on either side) we randomly draw *the number of sites from the side that has fewer matches* from the side that has more matches.
+So if there are 2 sites in FIA with a particular S and N, and 5 sites in "other datasets" with that S and N, we randomly select 2 of the 5 from "other datasets" to compare to the 2 from FIA.
+* Some of these S and N combinations have feasible sets that give fewer than 20 unique value for skewness or evenness, and we remove those from the histograms and proportion calculations below.
+20 is a somewhat arbitrary (and probably low) cutoff, but if there are fewer than 20 unique values the percentile cannot be above 95 or below 5.
+We end up with 371 comparisons for skewness and 365 for evenness.
 
@@
   facet_wrap(vars(fia_yn), scales = "free_y")
-# 
-# 
-# 
-# ggplot(filter(sub_di), aes(skew_percentile_excl)) +
-#   geom_histogram()+
-#   theme_bw() +
-#   facet_wrap(vars(fia_yn), scales = "free_y")
-# 
-# ggplot(filter(sub_di), aes(simpson_percentile)) +
-#   geom_histogram()+
-#   theme_bw() +
-#   facet_wrap(vars(fia_yn), scales = "free_y")
 
@@
 
-sum(sub_di$skew_unique < 20)
-sum(sub_di$simpson_unique < 20)
 ```
@@
 For the subsample that is directly comparable, there is **not a difference** between FIA and other datasets in the distribution of percentile values.
-This is a very small subsample relative to all the sites in both datasets - FIA has 20,000 sites overall, and we are only looking at 500 of them.
+This is a very small subsample relative to all the sites in both datasets - FIA has 20,000 sites overall, and we are only looking at around 375 of them.
 However, given how sensitive results aggregated in this way are to the relative frequency of SxN combinations/FS sizes in the sample, I believe this is the most robust way we can ask whether *being from FIA* causes detectably different outcomes.
+
+The absence of a difference here implicates the distribution of *sizes* in FIA as driving the difference in pattern.
+In the main manuscript we document that the 95% ratios for both skewness and evenness decrease over large gradients in S and N.
+In the self_similarity supplement, we show that this is also the case for other metrics of self-similarity.

### 2020-08-12 analysis/reports/manuscript_main.Rmd
textual updates
rarefaction

@@
 title: "Figures and results for main manuscript"
+author: Renata Diaz
+date: "`r Sys.Date()`"
 output: 
@@
 
+ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
+geom_histogram() +
+  theme_bw() +
+facet_wrap(vars(dat), scales = "free_y")
+
 ```

### 2020-08-12 analysis/reports/self_similarity.Rmd
begin self similarity

---
title: "Self-similarity of the elements of the feasible set"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE) 
```

We are interested in how the self-similarity of the elements of the feasible set varies over gradients in S and N. The intuition from "common-sense" probability theory, statistical mechanics, law-of-large-numbers intuition is that, as the number of possible arrangements becomes large, the different possible arrangements should become more self-similar. However, we don't know that this is the case for SADs, nor do we know the values for S and N where things really start to converge.

In the manuscript, I use the ratio of the 95% interval of summary statistic values, to the full range of summary statistic values. This can be calculated quickly and without introducing new statistics, etc to the main manuscript. It also directly reflects the distributions to which we are comparing our observations. However, it may not tell the full story: if the summary statistic values are idiosyncratic (skewness in particular can behave counterintuitively), it reflects those idiosyncracies.

With more computing, we can explore how similar the elements of the feasible set are to each other by comparing them to each other directly. Then we can ask whether, as the feasible set gets large, the elements become more similar and converge on a dominant form.

I initially did this analysis in https://github.com/diazrenata/sadspace and am porting the functions and analysis over to this repo for the supplement.

### Directly establishing self-similarity

#### Overview

We can describe how self-similar the elements of a feasible set are via numerous pairwise comparisons. Given a body of samples drawn from a feasible set, we draw two samples and compute some metric that describes how similar these two samples are to each other. We do this many times, making many pairwise comparisons, to generate a distribution of the self-similarity metric for that feasible set. We then compare how self-similar different feasible sets are by comparing the distributions of self-similarity metrics for the different feasible sets.

### 2020-08-12 R/self_similarity_metrics.R

@@ -1,0 +1,155 @@
+#' KL Divergence of two fs
+#'
+#' @param two_fs two fs
+#' @param log log units? idk if htis matters
+#'
+#' @return kl div
+#' @export
+#'
+#' @importFrom entropy KL.empirical
+fs_div <- function(two_fs, log = F) {
+  two_fs <- as.matrix(two_fs)
+
+  if(log) {
+    two_fs <- log(two_fs)
+  }
+
+  entropy::KL.empirical(two_fs[1,], two_fs[2,])
+
+}
+
+#' R2 for FS
+#'
+#' R2 as calculated in White et al (2012) and others (I beleive macroecotools)
+#'
+#' @param two_fs wide dataframe or matrix: 2 rows, nspp columns
+#' @param log use log or no? default F
+#'
+#' @return r2
+#' @export
+#'
+fs_r2 <- function(two_fs, log = F) {
+  two_fs <- as.matrix(two_fs)
+
+  focal <- two_fs[1,]
+  compare <- two_fs[2,]
+
+  if(log) {
+
+    focal <- log(focal)
+    compare <- log(compare)
+  }
+
+  focal_mean <- mean(focal)
+
+  numer <- sum((focal - compare) ^ 2)
+  denom <- sum((focal - focal_mean) ^ 2)
+  1 - (numer/denom)
+}
+
+#' Proportion off
+#'
+#' Prop of individuals allocated differently.
+#'
+#' @param two_fs wide dataframe or matrix: 2 rows, nspp columns
+#'
+#' @return prop diff
+#' @export
+#'
+proportion_off <- function(two_fs) {
+  two_fs <- as.matrix(two_fs)
+
+  abs_diff <- sum(abs(two_fs[1, ] - two_fs[2, ])) / 2
+
+  abs_diff / sum(two_fs[1, ])
+
+}
+
+#' CD (R2) from lm
+#'
+#' @param two_fs wide dataframe or matrix: 2 rows, nspp columns
+#'
+#' @return cd (R2) from lm()
+#' @export
+#'
+fs_cd <- function(two_fs) {
+  two_fs <- as.matrix(two_fs)
+  fs_lm <- lm(two_fs[1, ]  ~ two_fs[2, ])
+  return( summary(fs_lm)$r.squared )
+}
+
+#' Distance metrics sampler
+#'
+#' Randomly draw two elements from FS bank; compute various distance comparisons and return summary.
+#'
[…]

### 2020-08-12 analysis/reports/self_similarity.Rmd
maybe run

@@
 library(ggplot2)
+library(scadsanalysis)
 
@@
 We then compare how self-similar different feasible sets are by comparing the distributions of self-similarity metrics for the different feasible sets.
+
+#### Walkthrough
+
+```{r load net}
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE)
+
+net_summary <- readd(all_di_summary, cache = cache)
+
+net_summary <- net_summary %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)))
+
+example_fs <- readd(fs_s_7_n_71, cache = cache)
+
+example_di <- readd(di_fs_s_7_n_71, cache =cache)
+
+example_fs <- example_fs %>%
+  left_join(example_di) %>%
+  left_join(net_summary)
+```
+
+Here we have a bank of `r length(unique(example_fs$sim))` samples from the feasible set for SADs with 7 species and 71 individuals.
+
+```{r illustrate self similarity}
+
+ggplot(example_fs, aes(x = rank, y = abund, group = sim)) +
+  geom_line(alpha = .1) +
+  theme_bw()
+```
+
+We draw two of these samples to compare.
+
+```{r draw two}
+
+set.seed(1977)
+
+comparison <- fs_diff_sampler(example_fs)
+
+sims <- c(comparison$sim1[1], comparison$sim2[1])
+
+comparison_fs <- filter(example_fs, sim %in% sims) %>%
+  mutate(sim = as.factor(sim))
+
+ggplot(comparison_fs, aes(x = rank, y = abund, color = sim)) +
+  geom_line() +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_d(end = .7)
+
+```
+
+I have implemented 5 metrics of similarity for comparing samples:
+
+* R2
+* R2 on log-transformed abundances
+* The coefficient of determination from a linear model fitting one sample to the other
+* The proportion of individuals allocated to species of differing abundances
+* The estimated Kullbak-Lieber (sp) divergence between the two samples
+
+```{r self similarity metrics}
+
+comparison
+
+```
+
+We repeat this comparison process numerous times to get numerous values for the self-similarity metrics.
+
+```{r rep sampler, fig.dim = c(3,3)}
+
+comparisons <- rep_diff_sampler(example_fs, ndraws = 100)
+
+nrow(
+  comparisons %>%
+    select(sim1, sim2) %>%
+    distinct()
+)
+
+ggplot(comparisons, aes(r2)) +
+  geom_density() +
+  theme_bw()
+
+ggplot(comparisons, aes(r2_log)) +
+  geom_density() +
+  theme_bw()
+
+ggplot(comparisons, aes(cd)) +
+  geom_density() +
+  theme_bw()
+
+ggplot(comparisons, aes(prop_off)) +
+  geom_density() +
+  theme_bw()
+
+ggplot(comparisons, aes(div)) +
+  geom_density() +
+  theme_bw()
+```
+
+We repeat this process for feasible sets with varying S and N, and compare the distribution of the self-similarity metrics across the variation in S and N.

### 2020-08-12 analysis/net_pipeline.R

@@ -11,6 +11,7 @@ net_sites <- net %>%
   select(-rank, -abund)
 
 ndraws = 4000
+ncomparisons = 200
 #net_sites <- net_sites[1:10, ]
 set.seed(1978)
 
@@ -27,11 +28,11 @@ dat_plan <- drake_plan(
    di_summary = target(pull_di_net(di),
                    transform = map(di)),
   all_di_summary = target(dplyr::bind_rows(di_summary),
-                     transform = combine(di_summary))
-  # all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
-  # report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di_obs, is_template = TRUE, dat_name = !!datasets),
-  #                 trigger = trigger(condition = T),
-  #                 hpc = F)
+                     transform = combine(di_summary)),
+  diffs = target(rep_diff_sampler(fs, ndraws = !!ncomparisons),
+                 transform = map(fs)),
+  all_diffs = target(dplyr::bind_rows(diffs),
+                     transform = combine(diffs))
 )
 
 

### 2020-08-12 analysis/reports/self_similarity.Rmd
fix na'

@@
 
-nrow(
-  comparisons %>%
-    select(sim1, sim2) %>%
-    distinct()
-)
-
 ggplot(comparisons, aes(r2)) +
@@
 We repeat this process for feasible sets with varying S and N, and compare the distribution of the self-similarity metrics across the variation in S and N.
+
+```{r comparison 2}
+
+example_fs2 <- readd(fs_s_44_n_13360, cache = cache)
+
+example_di2 <- readd(di_fs_s_44_n_13360, cache =cache)
+
+example_fs2 <- example_fs2 %>%
+  left_join(example_di2) %>%
+  left_join(net_summary)
+
+comparisons2 <- rep_diff_sampler(example_fs2, ndraws = 100)
+
+both_comparisons <- bind_rows(comparisons, comparisons2) %>%
+  mutate(s_and_n = paste0("s_", s0, "_n_", n0))
+
+ggplot(both_comparisons, aes(r2, color = s_and_n)) +
+  geom_density() +
+  theme_bw() +
+  theme(legend.position = "top")
+
+ggplot(both_comparisons, aes(r2_log, color = s_and_n)) +
+  geom_density() +
+  theme_bw() +
+  theme(legend.position = "top")
+
+ggplot(both_comparisons, aes(cd, color = s_and_n)) +
+  geom_density() +
+  theme_bw() +
+  theme(legend.position = "top")
+
+ggplot(both_comparisons, aes(prop_off, color = s_and_n)) +
+  geom_density() +
+  theme_bw() +
+  theme(legend.position = "top")
+
+ggplot(both_comparisons, aes(div, color = s_and_n)) +
+  geom_density() +
+  theme_bw() +
+  theme(legend.position = "top")
+
+```

### 2020-08-13 analysis/reports/self_similarity.Rmd
draft self-similarity report

@@
 
-Here we have a bank of `r length(unique(example_fs$sim))` samples from the feasible set for SADs with 7 species and 71 individuals.
+Here we have a bank of `r length(unique(example_fs$sim))` samples from the feasible set for SADs with 7 species and 71 individuals. We draw two of these samples to compare.
 
@@
   theme_bw()
-```
-
-We draw two of these samples to compare.
-
-```{r draw two}
 
@@
 
-```{r rep sampler, fig.dim = c(3,3)}
+```{r rep sampler, fig.dim = c(2,2)}
 
@@
 
-```{r comparison 2}
+```{r comparison 2, fig.dim = c(2,2)}
 
@@
 ```
+
+### Across a range of S and N
+
+Here we have drawn samples from a "net" of points in S and N space that spans the range present in our datasets.
+For each feasible set we make 200 comparisons of elements (although for small feasible sets, 200 is not necessarily possible).
+Here is how that net is distributed in S and N space, colored by the log() number of elements in the feasible set.
+
+```{r diffs}
+
+loadd(all_diffs, cache= cache)
+
+all_diffs <- all_diffs %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) %>%
+  filter(!is.na(sim1), !is.na(sim2))
+
+ggplot(all_diffs, aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c() +
+  theme(legend.position = "top")
+
+```
+
+#### Heat maps
+
+We can make heat maps of the density distribution of self-similarity metrics and look at how the densities shift over gradients in the size of the feasible set.
+
+There are a couple of nuances to doing this:
+
+* We need to have the same number of comparisons for every feasible set, so that the density distributions will be comparable.
+In order to get a large swatch of S by N space, I've taken 50 comparisons from every feasible set.
+This is pretty low, so it lets us get even small feasible sets.
+Setting the minimum higher does not change the overall impression.
+* The metrics vary in how they are bounded.
+For some of them (R2, log r2) they can have nonsensical long tails towards very low values.
+For visualization, I've filtered out the long tail values (prior to selecting the 50 comparisons).
+The long tails tend to be most dominant in the comparisons made from small feasible sets.
+Removing them therefore makes the small feasible sets look *more* self-similar.
+
+##### R2
+
+Higher R2 values indicate more similarity. R2 can be *very low* but the most meaningful variation is between 0 and 1.
+
+```{r heat maps}
+
+loadd(all_diffs, cache= cache)
+
+# For plotting remove r2 that are EXTREMELY LOW.
+
+all_diffs_r2 <- all_diffs %>%
+    mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) %>%
+  mutate(s_and_n = paste0("s_", s0, "_n_", n0),
+         low_r2 = r2 <= -1) %>%
+  group_by(s_and_n) %>%
+  mutate(prop_small_r2 = mean(low_r2)) %>%
+  filter(r2 > -1) %>%
+  group_by(s_and_n) %>%
+  mutate(ncomparisons = dplyr::n(),
+         comparison_index = dplyr::row_number()) %>%
+  ungroup() %>%
+  filter(ncomparisons > 50, comparison_index <= 50) %>%
+  group_by(s0, n0) %>%
+  mutate(comparisons_included = dplyr::n()) %>%
+  ungroup()
+
+ggplot(all_diffs_r2, aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+# This plot demonstrates that removing comparisons for which r2 < -1 most impacts small FS. So if it distorts the results at all, it makes the small ones look *higher* than they really are.
+# ggplot(all_diffs_r2, aes(log(s0), log(n0), color = prop_small_r2)) +
+#   geom_point() +
+#   theme_bw() +
+#   scale_color_viridis_c() +
+#   theme(legend.position = "top")
+
+ggplot(all_diffs_r2, aes(r2, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+
+```
+
+Here is R2 for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+
+```{r r2 small}
+
+ggplot(filter(all_diffs_r2, log_nparts < 20), aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+ggplot(filter(all_diffs_r2, log_nparts < 20), aes(r2, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+```
+
+##### R2 on logged vectors
+
+Higher R2 values indicate more similarity. R2 can be *very low* but the most meaningful variation is between 0 and 1.
+
+```{r r2 on log}
+
+loadd(all_diffs, cache= cache)
+
+# For plotting remove r2 that are EXTREMELY LOW.
+
+all_diffs_r2_log <- all_diffs %>%
+    mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) %>%
+  mutate(s_and_n = paste0("s_", s0, "_n_", n0),
+         low_r2_log = r2_log <= -1) %>%
+  group_by(s_and_n) %>%
+  mutate(prop_small_r2_log = mean(low_r2_log)) %>%
+  filter(r2_log > -1) %>%
+  group_by(s_and_n) %>%
+  mutate(ncomparisons = dplyr::n(),
+         comparison_index = dplyr::row_number()) %>%
+  ungroup() %>%
+  filter(ncomparisons > 50, comparison_index <= 50) %>%
+  group_by(s0, n0) %>%
+  mutate(comparisons_included = dplyr::n()) %>%
+  ungroup()
+
+ggplot(all_diffs_r2_log, aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+# This plot demonstrates that removing comparisons for which r2 < -1 most impacts small FS. So if it distorts the results at all, it makes the small ones look *higher* than they really are.
+# ggplot(all_diffs_r2, aes(log(s0), log(n0), color = prop_small_r2)) +
+#   geom_point() +
+#   theme_bw() +
+#   scale_color_viridis_c() +
+#   theme(legend.position = "top")
+
+ggplot(all_diffs_r2_log, aes(r2_log, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+
+```
+
+Here is R2 on logged vectors for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+
+```{r r2 log small}
+
+ggplot(filter(all_diffs_r2_log, log_nparts < 20), aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+ggplot(filter(all_diffs_r2_log, log_nparts < 20), aes(r2_log, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+```
+
+##### Coefficient of determination
+
+Higher CD values indicate more similarity. It is bounded 0 to 1.
+
+```{r }
+
+loadd(all_diffs, cache= cache)
+
+# For plotting remove r2 that are EXTREMELY LOW.
+
+all_diffs_cd <- all_diffs %>%
+    mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) %>%
+  mutate(s_and_n = paste0("s_", s0, "_n_", n0),
+         low_cd = cd <= -1) %>%
+  group_by(s_and_n) %>%
+  mutate(prop_small_cd = mean(low_cd)) %>%
+#  filter(cd > -1) %>%
+  group_by(s_and_n) %>%
+  mutate(ncomparisons = dplyr::n(),
+         comparison_index = dplyr::row_number()) %>%
+  ungroup() %>%
+  filter(ncomparisons > 50, comparison_index <= 50) %>%
+  group_by(s0, n0) %>%
+  mutate(comparisons_included = dplyr::n()) %>%
+  ungroup()
+
+ggplot(all_diffs_cd, aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+# This plot demonstrates that removing comparisons for which cd < -1 most impacts small FS. So if it distorts the results at all, it makes the small ones look *higher* than they really are.
+# ggplot(all_diffs_cd, aes(log(s0), log(n0), color = prop_small_cd)) +
+#   geom_point() +
+#   theme_bw() +
+#   scale_color_viridis_c() +
+#   theme(legend.position = "top")
+
+ggplot(all_diffs_cd, aes(cd, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+
+```
+
+Here is cd for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+
+```{r cd small}
+
+ggplot(filter(all_diffs_cd, log_nparts < 20), aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+ggplot(filter(all_diffs_cd, log_nparts < 20), aes(cd, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+```
+
+##### Proportion of individuals allocated to different species
+
+Lower "prop off" values indicate more similarity. It is bounded 0 to 1.
+
+```{r prop off heat maps}
+
+loadd(all_diffs, cache= cache)
+
+# For plotting remove r2 that are EXTREMELY LOW.
+
+all_diffs_prop_off <- all_diffs %>%
+    mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) %>%
+  mutate(s_and_n = paste0("s_", s0, "_n_", n0),
+         low_prop_off = prop_off <= -1) %>%
+  group_by(s_and_n) %>%
+  mutate(prop_small_prop_off = mean(low_prop_off)) %>%
+#  filter(prop_off > -1) %>%
+  group_by(s_and_n) %>%
+  mutate(ncomparisons = dplyr::n(),
+         comparison_index = dplyr::row_number()) %>%
+  ungroup() %>%
+  filter(ncomparisons > 50, comparison_index <= 50) %>%
+  group_by(s0, n0) %>%
+  mutate(comparisons_included = dplyr::n()) %>%
+  ungroup()
+
+ggplot(all_diffs_prop_off, aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+# This plot demonstrates that removing comparisons for which prop_off < -1 most impacts small FS. So if it distorts the results at all, it makes the small ones look *higher* than they really are.
+# ggplot(all_diffs_prop_off, aes(log(s0), log(n0), color = prop_small_prop_off)) +
+#   geom_point() +
+#   theme_bw() +
+#   scale_color_viridis_c() +
+#   theme(legend.position = "top")
+
+ggplot(all_diffs_prop_off, aes(prop_off, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+
+```
+
+Here is prop_off for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+
+```{r prop_off small}
+
+ggplot(filter(all_diffs_prop_off, log_nparts < 20), aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+ggplot(filter(all_diffs_prop_off, log_nparts < 20), aes(prop_off, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+```
+
+##### K-L divergence
+
+Lower divergence  values indicate more similarity. It is bounded 0 to 1.
+
+```{r div heat maps}
+
+loadd(all_diffs, cache= cache)
+
+# For plotting remove r2 that are EXTREMELY LOW.
+
+all_diffs_div <- all_diffs %>%
+    mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) %>%
+  mutate(s_and_n = paste0("s_", s0, "_n_", n0),
+         low_div = div <= -1) %>%
+  group_by(s_and_n) %>%
+  mutate(prop_small_div = mean(low_div)) %>%
+#  filter(div > -1) %>%
+  group_by(s_and_n) %>%
+  mutate(ncomparisons = dplyr::n(),
+         comparison_index = dplyr::row_number()) %>%
+  ungroup() %>%
+  filter(ncomparisons > 50, comparison_index <= 50) %>%
+  group_by(s0, n0) %>%
+  mutate(comparisons_included = dplyr::n()) %>%
+  ungroup()
+
+ggplot(all_diffs_div, aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+# This plot demonstrates that removing comparisons for which div < -1 most impacts small FS. So if it distorts the results at all, it makes the small ones look *higher* than they really are.
+# ggplot(all_diffs_div, aes(log(s0), log(n0), color = prop_small_div)) +
+#   geom_point() +
+#   theme_bw() +
+#   scale_color_viridis_c() +
+#   theme(legend.position = "top")
+
+ggplot(all_diffs_div, aes(div, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+
+```
+
+Here is div for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+
+```{r div small}
+
+ggplot(filter(all_diffs_div, log_nparts < 20), aes(log(s0), log(n0), color = log_nparts)) +
+  geom_point() +
+  theme_bw() +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma") +
+  theme(legend.position = "top")
+
+ggplot(filter(all_diffs_div, log_nparts < 20), aes(div, group = s_and_n, color = log_nparts)) +
+  geom_density(alpha = .4) +
+  theme_bw() +
+  theme(legend.position = "top") +
+  scale_color_viridis_c(direction = -1, end = .8, option = "plasma")
+```

### 2020-08-14 analysis/fia_pipeline.R
remove dataset level reports from pipelines

@@ -32,10 +32,7 @@ dat_plan <- drake_plan(
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),
                     transform = combine(di_obs, .by = singletons)),
-  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
-  report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di_obs, is_template = TRUE, dat_name = !!datasets),
-                  trigger = trigger(condition = T),
-                  hpc = F)
+  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE))
 )
 
 all <- dat_plan

### 2020-08-14 analysis/miscabund_pipeline.R

@@ -32,10 +32,7 @@ dat_plan <- drake_plan(
                                                     transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),
                     transform = combine(di_obs, .by = singletons)),
-  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
-  report = target(render_report(here::here("analysis", "reports", "dat_report_template.Rmd"), dependencies = all_di_obs, is_template = TRUE, dat_name = !!datasets),
-                  trigger = trigger(condition = T),
-                  hpc = F)
+  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE))
 )
 
 all <- dat_plan

### 2020-10-09 analysis/reports/manuscript_main.Rmd
remove render reports from namespace

@@
   ggtitle("Communities by S and N")
+
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
+  geom_point(alpha = .01) +
+  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
+  theme_bw() +
+  scale_color_viridis_d() +
+  ggtitle("Communities by S and N") +
+  facet_wrap(vars(dat), scales = "free") +
+  geom_vline(xintercept = log(40)) +
+  geom_hline(yintercept = log(1000))
 

### 2020-10-09 analysis/demo_analysis/demo_pipeline.R

@@ -1,0 +1,79 @@
+library(drake)
+library(scadsanalysis)
+library(ggplot2)
+
+expose_imports("scadsanalysis")
+
+datasets <- "misc_abund_short"
+
+sites_list <- list_sites("misc_abund_short")
+ndraws = 4000
+#sites_list <- sites_list[1:15, ]
+set.seed(1981)
+
+dat_plan <- drake_plan(
+  dat = target(load_dataset(dataset_name = d),
+               transform = map(
+                 d = !!datasets
+               ),
+               hpc = F
+  ),
+  dat_s = target(add_singletons_dataset(dat),
+                 transform = map(dat),
+                 hpc = F),
+  tall_p = target(readRDS(here::here("analysis", "masterp_tall.Rds")),
+                  hpc = F),
+  fs = target(sample_fs_wrapper(dataset = dat_s_dat_misc_abund_short, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = tall_p, seed = !!sample.int(10^6, size = 1)),
+              transform = cross(s = !!sites_list$site,
+                                singletons = !!c(TRUE, FALSE))),
+  di = target(add_dis(fs),
+              transform = map(fs)),
+  di_obs = target(pull_di(di),
+                                                    transform = map(di)),
+  di_obs_s = target(dplyr::bind_rows(di_obs),
+                    transform = combine(di_obs, .by = singletons)),
+  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE))
+)
+
+all <- dat_plan
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-miscabund.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+
+## View the graph of the plan
+if (interactive())
+{
+  config <- drake_config(all, cache = cache)
+  sankey_drake_graph(config, build_times = "none")  # requires "networkD3" package
+  vis_drake_graph(config, build_times = "none")     # requires "visNetwork" package
+}
+
+## Run the pipeline
+nodename <- Sys.info()["nodename"]
+if(grepl("ufhpc", nodename)) {
+  print("I know I am on the HiPerGator!")
+  library(clustermq)
[…]

### 2020-10-14 analysis/reports/manuscript_main.Rmd
headers for links

--- 2020-08-10 analysis/reports/manuscript_main.Rmd
@@
   mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
-         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+    Dataset = ifelse(Dataset == "fia", "Forest Inventory and Analysis", Dataset),
+        Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+        Dataset = ifelse(Dataset == "mcdb", "Mammal Community DB", Dataset),
+        Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+        Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))
 ```
@@
 
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
-  geom_point(alpha = .01) +
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
+  geom_point(alpha = .1) +
   geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
@@
   scale_color_viridis_d() +
-  ggtitle("Communities by S and N")
+  ggtitle("Communities by S and N") +
+  xlab("Log species richness (S)") +
+  ylab("Log total abundance (N)")
+
+ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
+  geom_point(alpha = .05) +
+  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
+  theme_bw() +
+  scale_color_viridis_d() +
+  ggtitle("Communities by S and N") +
+   facet_wrap(vars(Dataset), scales = "free") +
+  theme(legend.position = "bottom")
+  # geom_vline(xintercept = log(40)) +
+  # geom_hline(yintercept = log(1000))
 
@@
   theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")
+  facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Skewness, all sites") +
+  xlab("Percentile rank of observed skewness value relative to feasible set") +
+  ylab("Number of communities")
 
@@
   theme_bw() +
-  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
+  facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Evenness, all sites") +
+  xlab("Percentile rank of observed evenness value relative to feasible set") +
+  ylab("Number of communities")
 
@@
   mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(dat) %>%
+  group_by(Dataset) %>%
   summarize(proportion_skew_high = mean(high_skew),
@@
   mutate(low_even = simpson_percentile < 5) %>%
-  group_by(dat) %>%
+  group_by(Dataset) %>%
   summarize(proportion_even_low = mean(low_even),
@@
 
-overall_results <- left_join(overall_skew_results, overall_simpson_results)
+overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
+  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
+         "Number of communities analyzed for skewness" = nsites_skew,
+         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
+         "Number of communities analyzed for evenness" = nsites_even)
 
@@
 overall_skew_results2 <- all_di %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
+   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
   filter(s0 > 2, skew_unique > 20) %>%
   mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(fia_yn) %>%
+  group_by(Dataset) %>%
   summarize(proportion_skew_high = mean(high_skew),
@@
   filter(simpson_unique > 20) %>%
-   mutate(fia_yn = ifelse(dat == "fia", "fia", "not fia")) %>%
+   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
   mutate(low_even = simpson_percentile < 5) %>%
-  group_by(fia_yn) %>%
+  group_by(Dataset) %>%
   summarize(proportion_even_low = mean(low_even),
@@
 
-overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2)
+overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
+   rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
+         "Number of communities analyzed for skewness" = nsites_skew,
+         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
+         "Number of communities analyzed for evenness" = nsites_even)
 
@@
 ```
+
+# 95 intervals by size of FS
 
@@
   theme_bw() +
-  xlim(0, 100)
+  xlim(0, 100) +
+  ylim(0,1)+
+  xlab("Log number of elements in the feasible set") +
+  ylab("Narrowness of the distribution of sampled skewness values")
 
@@
   theme_bw() +
-  xlim(0, 100)
+  xlim(0, 100) +
+  ylim(0, 1)+
+  xlab("Log number of elements in the feasible set") +
+  ylab("Narrowness of the distribution of sampled evenness values")
+```
+
+# 95 intervals by dataset
+
+```{r}
+
+ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
+  geom_histogram() +
+  theme_bw() +
+  facet_wrap(vars(Dataset), scales = "free_y") +
+    xlab("Narrowness of the distribution of sampled skewness values") +
+  ylab("Number of communities")
+
+ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
+geom_histogram() +
+  theme_bw() +
+facet_wrap(vars(Dataset), scales = "free_y") +
+    xlab("Narrowness of the distribution of sampled evenness values") +
+  ylab("Number of communities")
 

### 2020-10-14 analysis/reports/direct_FIA_size_comparison.Rmd
update fia

@@
 
-sub_di <- bind_rows(subsamples)
+sub_di <- bind_rows(subsamples) %>%
+   mutate(Dataset = ifelse(fia_yn == "fia", "Forest Inventory and Analysis", "Other datasets"))
 # 
@@
   theme_bw() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
+  facet_wrap(vars(Dataset), scales = "free_y")  +
+  xlab("Percentile rank of observed skewness value relative to feasible set") +
+  ylab("Number of communities")
 
@@
   theme_bw() +
-  facet_wrap(vars(fia_yn), scales = "free_y")
+  facet_wrap(vars(Dataset), scales = "free_y")  +
+  xlab("Percentile rank of observed evenness value relative to feasible set") +
+  ylab("Number of communities")
 
@@
   ungroup() %>%
-  group_by(fia_yn) %>%
+  group_by(Dataset) %>%
   summarize(prop_skew_high = mean(skew_percentile_excl > 95, na.rm = T),
@@
             nsites_skew = sum(!is.na(skew_percentile_excl)),
-            nsites_even = sum(!is.na(simpson_percentile)))
+            nsites_even = sum(!is.na(simpson_percentile))) %>%
+   rename("Proportion of communities with skewness above 95th percentile" = prop_skew_high,
+         "Number of communities analyzed for skewness" = nsites_skew,
+         "Proportion of communities with evenness below 5th percentile" = prop_even_low,
+         "Number of communities analyzed for evenness" = nsites_even)
 

### 2020-11-28 analysis/reports/filtering.Rmd
final hao edits and start filtering vignette

---
title: "Filtering datasets"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

theme_set(theme_bw())
options(ggplot2.discrete.color = scale_color_viridis_d(end = .8))

knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE) 
```

The filtering of datasets to exclude very small or very large communities happens at the very beginning of the analysis, when we download and *process* the data.

```{r}

bbs <- read.csv(here::here("working-data", "abund_data", "bbs_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)

colnames(bbs) <- c("site", "year", "species", "abund")

bbs_statevars <- bbs %>%
  group_by(site) %>%
  summarize(
    nyears = length(unique(year)),
    nspecies = dplyr::n(),
    nind = sum(abund)
  )

ggplot(bbs_statevars, aes(nspecies, nind)) +
  geom_point() +
  geom_hline(yintercept = 40720) +
  geom_vline(xintercept = 200) +
  ggtitle("BBS")

unique(bbs_statevars$nyears)

```

No communities in BBS are outside the maxima. All communities (in this dataset) are only represnted with 1 year.

```{r}

gentry <- read.csv(here::here("working-data", "abund_data", "gentry_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)

colnames(gentry) <- c("site", "year", "species", "abund")

gentry_statevars <- gentry %>%
  group_by(site) %>%
  summarize(
    nyears = length(unique(year)),
    nspecies = dplyr::n(),
    nind = sum(abund)
  ) %>%
  mutate(outside_maxima = (nspecies > 200) | (nind > 40720))

ggplot(gentry_statevars, aes(nspecies, nind, color = outside_maxima)) +
  geom_point() +
  geom_hline(yintercept = 40720) +
  geom_vline(xintercept = 200) +
  ggtitle("gentry")

```

Gentry has `r sum(gentry$outside_maxima)` communities, out of `r nrow(gentry)` communities, outside the maxima. RMD just realized, I left these in because they are still sample-able - they have sufficiently low N.

```{r}

miscabund <- read.csv(here::here("working-data", "abund_data", "misc_abund_spab.csv"))

    miscabund <- miscabund %>%
      dplyr::rename(site = Site_ID,
                    abund = Abundance)

miscabund_statevars <- miscabund %>%
  group_by(site) %>%
  summarize(
    nspecies = dplyr::n(),
    nind = sum(abund),
    nind_na_rm=sum(abund, na.rm = T)
  ) %>%
  mutate(outside_maxima = (nspecies > 200) | (nind > 40720))

ggplot(miscabund_statevars, aes(nspecies, nind, color = outside_maxima)) +
  geom_point() +
  geom_hline(yintercept = 40720) +
  geom_vline(xintercept = 200) +
  ggtitle("miscabund")

sum(is.na(miscabund_statevars$nind))

# how many of those have 0

nrow(filter(miscabund_statevars, is.na(nind), nind_na_rm == 0))

filter(miscabund_statevars, is.na(nind), nind_na_rm >0 )

```

Misc abund has `{r} sum(miscabund_statevars$outside_maxima, na.rm =T)` communities that get removed. They are all removed because they have high numbers of individiuals.

There are 130 datasets where there are a mixture of relative and count abundances included. of those, 124 have 0 individuals in the count. THose were not included. There were **6** that have a mixutre and a nonzero number counted. These were INCLUDED in the initial analysis, with relative abundance species completely removed.

```{r}

miscabund_within <- miscabund_statevars %>%
  filter(nspecies <= 200, nind <= 40720)

miscabund_filtered <- load_dataset("misc_abund_short")

miscabund_sites <- unique(miscabund_within$site)
miscabund_filtered_sites <- unique(miscabund_filtered$site)

included_sites <- as.numeric(miscabund_filtered_sites)

setdiff(included_sites, miscabund_sites)

```

```{r}

fia <- read.csv(here::here("working-data", "abund_data", "fia_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

      colnames(fia) <- c("site", "year", "species", "abund")

fia_statevars <- fia %>%
  group_by(site) %>%
  summarize(
    nspecies = dplyr::n(),
    nind = sum(abund),
    nind_na_rm=sum(abund, na.rm = T)
  ) %>%
  mutate(outside_maxima = (nspecies > 200) | (nind > 40720),
         n_equals_s = nind == nspecies)
sum(fia_statevars$n_equals_s)

ggplot(fia_statevars, aes(nspecies, nind, color = outside_maxima)) +
  geom_point() +
  geom_hline(yintercept = 40720) +
  geom_vline(xintercept = 200) +
  ggtitle("fia")

```

FIA has no extremely large datasets.

```{r}

ggplot(fia_statevars, aes(nspecies, nind, color = outside_maxima)) +
  geom_point() +
  geom_vline(xintercept = 10) +
  ggtitle("fia")

ggplot(fia_statevars, aes(nspecies)) +
  geom_histogram() +
  geom_vline(xintercept = 10)

```

```{r}

mcdb <- read.csv(here::here("working-data", "abund_data", "mcdb_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

      colnames(mcdb) <- c("site", "year", "species", "abund")

mcdb_statevars <- mcdb %>%
  group_by(site) %>%
  summarize(
    nspecies = dplyr::n(),
    nind = sum(abund),
    nind_na_rm=sum(abund, na.rm = T)
  ) %>%
  mutate(outside_maxima = (nspecies > 200) | (nind > 40720),
         n_equals_s = nind == nspecies)

ggplot(mcdb_statevars, aes(nspecies, nind, color = outside_maxima)) +
  geom_point() +
  geom_hline(yintercept = 40720) +
  geom_vline(xintercept = 200) +
  ggtitle("mcdb")

sum(mcdb_statevars$n_equals_s)
```

```{r}

all_statevars <- miscabund_statevars %>%
  select(-nind) %>%
  rename(nind = nind_na_rm) %>%
  bind_rows(bbs_statevars, fia_statevars, gentry_statevars, mcdb_statevars) %>%
  filter(!outside_maxima) %>%
  mutate(n_equals_s = nind == nspecies)

sum(all_statevars$n_equals_s)

```

### 2020-11-30 analysis/reports/filtering.Rmd
still figuring out filtering details

@@
 
+The `download_data` function downloads raw data files from https://github.com/weecology/sad-comparison/ (for BBS, Gentry, Mammal Community  Database, and FIA) and figshare http://figshare.com/files/3097079 (for the Miscellaneous Abundance Database).
+These raw files are stored in `working-data\abund_data` and are not edited.
+
+To filter, we can re-load the raw data files and go through the filtering process step by step.
+In the analysis this is accomplished by running dataset-specific filtering scripts and saving new .csvs, which are then loaded using `load_dataset`.
+
+We filter according to the following limitations:
+* Communities with very large numbers of individuals become computationally intractable.
+We set the upper limit at 40720, because this is the largest community we were able to sample given the available resources.
+This upper limit results in the removal of a total of 6 communities across all the datasets.
+* Communities for which N = S have only 1 possible SAD.
+* Communities with only 1 species have only 1 possible SAD.
+* The Miscellaneous Abundance Database includes communities with abundances reported as relative abundances as well as as counts. We exclude communities with relative abundance data. 
+* We additionally filter the FIA dataset, because it has many more communities than any other dataset and sampling all of them overwhelms our computational pipeline.
+We include all communities with more than 10 species (10,000), and an additional, randomly selected, 10,000 (of a remaining 90,000) with 3-10 species.
+* Communities with only 2 species are removed from analyses for skewness, because `e1071::skewness()` always evaluates to 0 for a vector of length 2.
+
+### BBS
+
 ```{r}
@@
   geom_point() +
-  geom_hline(yintercept = 40720) +
-  geom_vline(xintercept = 200) +
   ggtitle("BBS")
@@
 
+range(bbs_statevars$nspecies)
+range(bbs_statevars$nind)
+
 ```
+All communities in BBS are used.
 
-No communities in BBS are outside the maxima. All communities (in this dataset) are only represnted with 1 year.
+### Gentry
 
@@
     nind = sum(abund)
-  ) %>%
-  mutate(outside_maxima = (nspecies > 200) | (nind > 40720))
+  )
 
-ggplot(gentry_statevars, aes(nspecies, nind, color = outside_maxima)) +
+ggplot(gentry_statevars, aes(nspecies, nind)) +
+  geom_point() +
+  ggtitle("gentry")
+
+range(gentry_statevars$nspecies)
+range(gentry_statevars$nind)
+
+sum(gentry_statevars$nspecies == 2)
+
+```
+
+All Gentry communities are kept. However, `r sum(gentry_statevars$nspecies == 2)` site only has 2 species and will be removed from skewness analyses later in the pipeline.
+
+### Mammal Community Database
+
+```{r}
+
+mcdb <- read.csv(here::here("working-data", "abund_data", "mcdb_spab.csv"), stringsAsFactors = F, header = F, skip = 2)
+
+colnames(mcdb) <- c("site", "year", "species", "abund")
+
+mcdb_statevars <- mcdb %>%
+  group_by(site) %>%
+  summarize(
+    nspecies = dplyr::n(),
+    nind = sum(abund)
+  )
+
+ggplot(mcdb_statevars, aes(nspecies, nind)) +
   geom_point() +
@@
   geom_vline(xintercept = 200) +
-  ggtitle("gentry")
+  ggtitle("mcdb")
+
+range(mcdb_statevars$nspecies)
+range(mcdb_statevars$nind)
 
@@
 
-Gentry has `r sum(gentry$outside_maxima)` communities, out of `r nrow(gentry)` communities, outside the maxima.
-RMD just realized, I left these in because they are still sample-able - they have sufficiently low N.
+`r sum(mcdb_statevars$nspecies == 1)` communities are removed because they have only one species.  Additionally, `r sum(mcdb_statevars$nspecies == 2)
+` have 2 species and will be removed from skewness analyses. These removals happen post-pipeline.
+
+### Miscellaneous Abundance Database
 
@@
   ) %>%
-  mutate(outside_maxima = (nspecies > 200) | (nind > 40720))
+  mutate(outside_maxima = (nind_na_rm > 40720))
 
-ggplot(miscabund_statevars, aes(nspecies, nind, color = outside_maxima)) +
+ggplot(miscabund_statevars, aes(nspecies, nind_na_rm, color = outside_maxima)) +
   geom_point() +
@@
 These were INCLUDED in the initial analysis, with relative abundance species completely removed.
+Upon realizing this we remove these 6 communities from the final analysis.
+Rather than re-run the whole pipeline, we manually remove them when we load the data to make the histograms and summary tables (see manuscript_main.Rmd).
 
-```{r}
-
-miscabund_within <- miscabund_statevars %>%
-  filter(nspecies <= 200, nind <= 40720)
-
-miscabund_filtered <- load_dataset("misc_abund_short")
-
-miscabund_sites <- unique(miscabund_within$site)
-miscabund_filtered_sites <- unique(miscabund_filtered$site)
-
-included_sites <- as.numeric(miscabund_filtered_sites)
-
-setdiff(included_sites, miscabund_sites)
-
-```
+### FIA
 
@@
     nind_na_rm=sum(abund, na.rm = T)
-  ) %>%
-  mutate(outside_maxima = (nspecies > 200) | (nind > 40720),
-         n_equals_s = nind == nspecies)
-sum(fia_statevars$n_equals_s)
+  )
 
-ggplot(fia_statevars, aes(nspecies, nind, color = outside_maxima)) +
+ggplot(fia_statevars, aes(nspecies, nind)) +
   geom_point() +
@@
 FIA has no extremely large datasets.
+However, it has `r nrow(fia_statevars)` communities, of which `r sum(fia_statevars$nspecies < 10)` have fewer than 10 species.
+This many communities overwhelms our computational pipeline.
+We therefore sample all `r sum(fia_statevars$nspecies >= 10)` communities with 10 or more species, and a random subsample of 10,000 communities with 3-9 species.
+We then run these through the pipeline as two separate databases.
+`fia_short` is the communities with 10 or more species, and `fia_small` is the 10,000 communities with 3-9 species.
+
+To go through this we re-load FIA using load_dataset, so we can get the `site` column in the correct format and order such that it will replicate when we run sample.
 
@@
 
-ggplot(fia_statevars, aes(nspecies, nind, color = outside_maxima)) +
-  geom_point() +
-  geom_vline(xintercept = 10) +
-  ggtitle("fia")
+fia <- load_dataset("fia")
 
-ggplot(fia_statevars, aes(nspecies)) +
-  geom_histogram() +
-  geom_vline(xintercept = 10)
+fia_sv_short <- get_statevars(fia) %>%
+    dplyr::filter(s0 >= 10)
 
-```
+fia_short <- fia %>%
+  dplyr::filter(site %in% fia_sv_short$site) %>%
+  dplyr::mutate(dat = "fia_short")
 
-```{r}
-
-mcdb <- read.csv(here::here("working-data", "abund_data", "mcdb_spab.csv"), stringsAsFactors = F, header = F, skip = 2)
-
-      colnames(mcdb) <- c("site", "year", "species", "abund")
-
-mcdb_statevars <- mcdb %>%
+fia_short_statevars <- fia_short %>%
   group_by(site) %>%
@@
   ) %>%
-  mutate(outside_maxima = (nspecies > 200) | (nind > 40720),
-         n_equals_s = nind == nspecies)
+  mutate(site = as.numeric(site))
 
-ggplot(mcdb_statevars, aes(nspecies, nind, color = outside_maxima)) +
+ggplot(fia_short_statevars, aes(nspecies, nind)) +
   geom_point() +
-  geom_hline(yintercept = 40720) +
-  geom_vline(xintercept = 200) +
-  ggtitle("mcdb")
+  ggtitle("fia short")
 
-sum(mcdb_statevars$n_equals_s)
+fia_sv_small <- get_statevars(fia) %>%
+  dplyr::filter(s0 >= 3) %>%
+  dplyr::filter(s0 <= 9)
+
+  set.seed(1977)
+  fia_sv_small <- fia_sv_small[ sample.int(nrow(fia_sv_small), size = 10000, replace = F), ]
+
+fia_small <- fia %>%
+  dplyr::filter(site %in% fia_sv_small$site) %>%
+  dplyr::mutate(dat = "fia_small")
+
+fia_small_statevars <-fia_small  %>%
+  group_by(site) %>%
+  summarize(
+    nspecies = dplyr::n(),
+    nind = sum(abund),
+    nind_na_rm=sum(abund, na.rm = T)
+  )  %>%
+  mutate(site = as.numeric(site))
+
+ggplot(fia_small_statevars, aes(nspecies, nind)) +
+  geom_point() +
+  ggtitle("fia small")
+
+fia_small_loaded <- load_dataset("fia_small")
+
+setdiff(fia_small_loaded$site, fia_small$site)
+
 ```
@@
   rename(nind = nind_na_rm) %>%
-  bind_rows(bbs_statevars, fia_statevars, gentry_statevars, mcdb_statevars) %>%
-  filter(!outside_maxima) %>%
-  mutate(n_equals_s = nind == nspecies)
-
-sum(all_statevars$n_equals_s)
+  bind_rows(bbs_statevars, fia_short_statevars, fia_small_statevars, gentry_statevars, mcdb_statevars) %>%
+  mutate(one_species = nspecies == 1,
+         two_species = nspecies == 2,
+         n_equals_s = nspecies == nind)
 
 ```
+
+Overall there are `r sum(all_statevars$one_species)` removed at the end because they have just 1 species.
+There are `r sum(all_statevars$two_species)` that will be removed from skewness because they ahve 2 species.
+There are `r sum(all_statevars$n_equals_s)` that are removed because N = S.
+
+Note that, in practice, many more small ones end up getting removed because they have very few possible SADs and very few unique values for skewness and evenness.
+
+```{r}
+all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+
+all_di <- all_di %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 > s0,
+         s0 > 1,
+         !singletons,
+         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+    Dataset = ifelse(Dataset == "fia", "Forest Inventory and Analysis", Dataset),
+        Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+        Dataset = ifelse(Dataset == "mcdb", "Mammal Community DB", Dataset),
+        Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+        Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))
+
+nrow(all_di)
+
+filtered_sv <- all_statevars %>%
+  filter(!n_equals_s,
+         !one_species)
+
+nrow(filtered_sv)
+```

### 2020-11-30 analysis/reports/manuscript_main.Rmd
continuing to t r y
still figuring out filtering details

@@
         Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))
+
+miscabund_problems <- c(144, 145, 145, 146, 147, 178, 446)
+
+all_di <- all_di %>%
+  mutate(is.miscabund.problem = ifelse(dat == "misc_abund",
+                                       ifelse(site %in% miscabund_problems, T, F), F)) %>%
+  filter(!is.miscabund.problem) %>%
+  ungroup() %>%
+  select(-is.miscabund.problem)
+
 ```

### 2020-11-30 analysis/reports/accessory/old_reports/cross_dataset.Rmd
tidying and sending docs to SKME

--- 2019-11-18 analysis/reports/cross_dataset.Rmd
@@
 It doesn't look to me like there is a strong relationship between range and %ile.
+
+```{r nyears in mcdb}
+
+mcdb_di <- filter(all_di, dat == "mcdb")
+
+mcdb_sites <- read.csv(here::here("working-data/site_data/mammal_community_db_sites.csv"), stringsAsFactors = F)
+
+mcdb_sites <- mcdb_sites %>%
+  select(site_id, n_years, study_duration) %>%
+  rename(site = site_id) %>%
+  mutate(site = as.character(site))
+
+mcdb_di <- left_join(mcdb_di, mcdb_sites, by = "site")
+
+nyears_hist <- ggplot(data = distinct(select(mcdb_di, site, n_years)), aes(x = n_years)) +
+  geom_histogram(pad = T, boundary = 0) +
+  theme_bw() +
+  ggtitle("Nyears in MCDB")
+
+nyears_hist
+# 
+# duration_hist <-  ggplot(data = distinct(select(mcdb_di, site, study_duration)), aes(x = study_duration)) +
+#   geom_histogram(pad = T, boundary = 0) +
+#   theme_bw() +
+#   ggtitle("Duration in MCDB")
+# 
+# duration_hist
+
+nyears_skew <- ggplot(data = mcdb_di, aes(x = n_years, y = skew_percentile)) +
+  geom_point(alpha = .2) +
+  #facet_wrap(vars(singletons)) +
+  theme_bw() +
+  ggtitle("Skew v nyears (MCDB)")
+
+nyears_skew
+
+nyears_simpson <- ggplot(data = mcdb_di, aes(x = n_years, y = simpson_percentile)) +
+  geom_point(alpha = .2) +
+  #facet_wrap(vars(singletons)) +
+  theme_bw() +
+  ggtitle("Simpson v nyears (MCDB)")
+
+nyears_simpson
+```

### 2020-11-30 analysis/reports/self_similarity.Rmd
remove dataset level reports from pipelines
tidying and sending docs to SKME

@@
 output: 
-    github_document:
+    word_document:
        df_print: kable
@@
 
-### Directly establishing self-similarity
+## Directly establishing self-similarity
 
-#### Overview
+### Overview
 
@@
 
-#### Walkthrough
+### Walkthrough
 
@@
 
-### Across a range of S and N
+## Across a range of S and N
 
@@
 
-#### Heat maps
+### Heat maps
 
@@
 
-##### R2
+#### R2
 
@@
 
-##### R2 on logged vectors
+#### R2 on logged vectors
 
@@
 
-##### Coefficient of determination
+#### Coefficient of determination
 
@@
 
-##### Proportion of individuals allocated to different species
+#### Proportion of individuals allocated to different species
 
@@
 
-##### K-L divergence
+#### K-L divergence
 
@@
 
-Here is div for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+Here is K-L divergence for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
 
@@
 ```
+
+### In summary
+
+Large feasible sets are consistently more self-similar than small ones.

### 2020-12-07 analysis/reports/filtering_presampling.Rmd
filtering report

---
title: "Filtering datasets"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

theme_set(theme_bw())

knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE) 
```

We filter datasets in two stages. First, **prior to trying to sample from the feasible set**, we remove communities that have a combined S and N too high for us to sample the feasible set. We also create a sub-sample of the FIA dataset, because it has so many communities (~100,000) and so many of them are extremely small (~90,000 with fewer than 10 species). Sampling all 100,000 communities overwhelms our computational pipeline, so we create a subsample of 20,000 communities comprising all communities with more than 10 species (approx. 10,000) and 10,000 randomly selected communities with 3-10 species. Second, **after sampling but before we aggregate results across communities**, we remove communities that are problematic for a number of more nuanced reasons. This includes having only 1 possible SAD (S = 1, N = S, or N = S + 1); mixed relative abundance and count data (for the Misc. Abundance Database). We also filter to communities whose sampled feasible sets yield more than 20 unique values for skewness/evenness. We do this because, if there are fewer than 20 unique values in the comparison vector, it's impossible to be in the 5th or 95th percentile. Finally, we remove communities with only 2 species from analyses for skewness, because  `e1071::skewness()` always = 0 if S = 2.

## Pre-sampling

The only filtering at this stage is removing large communities and subsampling the FIA database. Communities with very large numbers of individuals become computationally intractable. We set the upper limit at 40720, because this is the largest community we were able to sample given the available resources. This upper limit results in the removal of a total of 4 communities, all of them from the Miscellaneous Abundance Database.

The `download_data` function downloads raw data files from https://github.com/weecology/sad-comparison/ (for BBS, Gentry, Mammal Community  Database, and FIA) and figshare http://figshare.com/files/3097079 (for the Miscellaneous Abundance Database). These raw files are stored in `working-data\abund_data` and are not edited.

To filter, we can re-load the raw data files and go through the filtering process step by step. In the analysis this is accomplished by running dataset-specific filtering scripts and saving new .csvs, which are then loaded using `load_dataset`. We can manually load the datasets and then compare them to what is returned from `load_dataset`.

### Miscellaneous Abundance Database

- Misc. Abund includes datasets reported as relative abundance in addition to count data. We don't want any communities without counts, so we filter out records where abund = 0. *While preparing this report, RMD noticed that some communities have a __mixture__ of relative abundance and count data. These communities were sampled, but RMD does not believe it is appropriate to compare them to count-data-only communities. We therefore remove these 6 in the second, post-sampling, phase of filtering.*

```{r}

misc_abund_raw <- read.csv(here::here("working-data", "abund_data", "misc_abund_spab.csv"))

misc_abund_raw <- misc_abund_raw %>%
  dplyr::rename(site = Site_ID,
                abund = Abundance)

misc_abund_raw <- misc_abund_raw %>%
  mutate(site = as.character(site),
         dat = "misc_abund",
         singletons = F,
         sim = -99,
         source = "observed") %>%
  filter(abund > 0) %>%
  group_by(site) %>%
  arrange(abund) %>%
  mutate(rank = row_number()) %>%
  ungroup()

misc_abund_loaded <- load_dataset("misc_abund")

```

```{r}
any(!(misc_abund_loaded$abund == misc_abund_raw$abund))
any(!(misc_abund_loaded$site == misc_abund_raw$site))

```

Check community sizes:

```{r}

misc_abund_statevars <- get_statevars(misc_abund_raw)

ggplot(misc_abund_statevars, aes(s0, n0)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = 40720, color = "red")

```

Misc abund has `r sum(misc_abund_statevars$n0 > 40720)` communities that get removed. They are all removed because they have high numbers of individuals.

The filtered database is saved as a .csv and can be loaded with `load_dataset`. We can check that it matches the filtering we have done here:

```{r}

misc_abund_sv_filtered <- misc_abund_statevars %>%
  filter(n0 <= 40720)

misc_abund_filtered <- filter(misc_abund_raw, site %in% misc_abund_sv_filtered$site)

misc_abund_short_loaded <- load_dataset("misc_abund_short")

any(!(misc_abund_short_loaded$abund == misc_abund_filtered$abund))
any(!(misc_abund_short_loaded$site == misc_abund_filtered$site))
```

### FIA

- Load raw FIA data
- Add columns to match what we will get from `load_dataset`
- Load from `load_dataset`

```{r}

fia_raw <- read.csv(here::here("working-data", "abund_data", "fia_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

colnames(fia_raw) <- c("site", "year", "species", "abund")

fia_raw <- fia_raw %>%
  mutate(site = as.character(site),
         dat = "fia",
         singletons = F,
         sim = -99,
         source = "observed") %>%
  filter(abund > 0) %>%
  group_by(site) %>%
  arrange(abund) %>%
  mutate(rank = row_number()) %>%
  ungroup()

fia_loaded <- load_dataset("fia")
```

```{r}
any(!(fia_loaded$abund == fia_raw$abund))
any(!(fia_loaded$site == fia_raw$site))

```

Check community sizes:

```{r}

fia_statevars <- get_statevars(fia_raw)

ggplot(fia_statevars, aes(s0, n0)) +
  geom_point() +
  theme_bw() +
  geom_vline(xintercept = c(1.5, 2.5, 9.5), color = "red")

```

FIA has no extremely large datasets; the largest number of individuals is `r max(fia_statevars$n0)`. However, it has `r nrow(fia_statevars)` communities, of which `r sum(fia_statevars$s0 < 10)` have fewer than 10 species. This many communities overwhelms our computational pipeline. We therefore sample all `r sum(fia_statevars$s0 >= 10)` communities with 10 or more species, and a random subsample of 10,000 communities with 3-9 species. We then run these through the pipeline as two separate databases. `fia_short` is the communities with 10 or more species, and `fia_small` is the 10,000 communities with 3-9 species. We re-combine them as "FIA" for aggregate analyses.

```{r}

fia_sv_short <- fia_statevars %>%
    dplyr::filter(s0 >= 10)

fia_short <- fia_raw %>%
  dplyr::filter(site %in% fia_sv_short$site) %>%
  dplyr::mutate(dat = "fia_short")

fia_short_statevars <- get_statevars(fia_short)

ggplot(fia_short_statevars, aes(s0, n0)) +
  geom_point() +
  ggtitle("fia short, >= 10 species") +
  theme_bw()

fia_sv_small <- fia_statevars %>%
  dplyr::filter(s0 >= 3) %>%
  dplyr::filter(s0 <= 9)

  set.seed(1977)
  fia_sv_small <- fia_sv_small[ sample.int(nrow(fia_sv_small), size = 10000, replace = F), ]

fia_small <- fia_raw %>%
  dplyr::filter(site %in% fia_sv_small$site) %>%
  dplyr::mutate(dat = "fia_small")

fia_small_statevars <- get_statevars(fia_small)

ggplot(fia_small_statevars, aes(s0, n0)) +
  geom_point() +
  ggtitle("fia small, 3-9 species")

```

The "short" and "small" datasets are saved as .csvs and can be loaded using `load_dataset`:

```{r}

fia_small_loaded <- load_dataset("fia_small")

any(!(fia_small_loaded$abund == fia_small$abund))
any(!(fia_small_loaded$site == fia_small$site))

fia_short_loaded <- load_dataset("fia_short")

any(!(fia_short_loaded$abund == fia_short$abund))
any(!(fia_short_loaded$site == fia_short$site))

```

### BBS

- Load raw BBS data
- Add columns to match what we will get from `load_dataset`
- Load from `load_dataset`

```{r}

bbs_raw <- read.csv(here::here("working-data", "abund_data", "bbs_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)

colnames(bbs_raw) <- c("site", "year", "species", "abund")

bbs_raw <- bbs_raw %>%
  mutate(site = as.character(site),
         dat = "bbs",
         singletons = F,
         sim = -99,
         source = "observed") %>%
  group_by(site) %>%
  arrange(abund) %>%
  mutate(rank = row_number()) %>%
  ungroup()

bbs_loaded <- load_dataset("bbs")
```

Compare loaded to raw:

```{r}
any(!(bbs_loaded$abund == bbs_raw$abund))
any(!(bbs_loaded$site == bbs_raw$site))

```

Check community sizes:

```{r}

bbs_statevars <- get_statevars(bbs_raw)

ggplot(bbs_statevars, aes(s0, n0)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = 40720, color = "red")

```

No communities in BBS have more than 40720 individuals, so all are used at this stage.

### Gentry

- Load raw Gentry data
- Add columns to match what we will get from `load_dataset`
- Load from `load_dataset`

```{r}

gentry_raw <- read.csv(here::here("working-data", "abund_data", "gentry_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)

colnames(gentry_raw) <- c("site", "year", "species", "abund")

gentry_raw <- gentry_raw %>%
  mutate(site = as.character(site),
         dat = "gentry",
         singletons = F,
         sim = -99,
         source = "observed") %>%
  group_by(site) %>%
  arrange(abund) %>%
  mutate(rank = row_number()) %>%
  ungroup()

gentry_loaded <- load_dataset("gentry")
```

Compare loaded to raw:

```{r}
any(!(gentry_loaded$abund == gentry_raw$abund))
any(!(gentry_loaded$site == gentry_raw$site))

```

Check community sizes:

```{r}

gentry_statevars <- get_statevars(gentry_raw)

ggplot(gentry_statevars, aes(s0, n0)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = 40720, color = "red")

```

No communities in Gentry have more than 40720 individuals, so all are used at this stage.

### Mammal Community Database

- Load raw MCDB data
- Add columns to match what we will get from `load_dataset`
- Load from `load_dataset`

```{r}

mcdb_raw <- read.csv(here::here("working-data", "abund_data", "mcdb_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)

colnames(mcdb_raw) <- c("site", "year", "species", "abund")

mcdb_raw <- mcdb_raw %>%
  mutate(site = as.character(site),
         dat = "mcdb",
         singletons = F,
         sim = -99,
         source = "observed") %>%
  group_by(site) %>%
  arrange(abund) %>%
  mutate(rank = row_number()) %>%
  ungroup()

mcdb_loaded <- load_dataset("mcdb")
```

Compare loaded to raw:

```{r}
any(!(mcdb_loaded$abund == mcdb_raw$abund))
any(!(mcdb_loaded$site == mcdb_raw$site))

```

Check community sizes:

```{r}

mcdb_statevars <- get_statevars(mcdb_raw)

ggplot(mcdb_statevars, aes(s0, n0)) +
  geom_point() +
  theme_bw() +
  geom_hline(yintercept = 40720, color = "red")

```

No high N communities; so all are included at this stage.

## Post-sampling

We will remove additional communities for more substantive reasons. First we can load `all_di` ("all diversity indices"), which is the combined results across all the communities in all the datasets. Every community that was included for sampling is included in all_di. (Additionally, every community has a "singletons" counterpart, which is the same analysis run adjusted for rarefaction. That analysis is discussed elsewhere, and we ignore the rarefaction-adjusted versions here).

```{r}
all_statevars <- bind_rows(bbs_statevars, fia_short_statevars, fia_small_statevars, gentry_statevars, mcdb_statevars, misc_abund_sv_filtered)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  filter(!singletons) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
    Dataset = ifelse(Dataset == "fia", "Forest Inventory and Analysis", Dataset),
        Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
        Dataset = ifelse(Dataset == "mcdb", "Mammal Community DB", Dataset),
        Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
        Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))

head(all_di)

nrow(all_di) == nrow(all_statevars)
```

We remove communities with only one possible SAD (N = S, N = S + 1, or S = 1) and five communities in the Misc. Abund Database that have mixed count and relative abundance data (there are more than 5 with a mixture, but only 5 that have both the mixture AND make it through the previous filters).

```{r}

all_di %>%
  group_by_all() %>%
  mutate(only_one_sad = sum(s0 == n0, s0 == 1, n0 == (s0 + 1)) > 0) %>%
  ungroup() %>%
  group_by(dat) %>%
  summarize(total_only_one_sad = sum(only_one_sad),
            total_sites = dplyr::n()) %>%
  ungroup() %>%
  mutate(all_sites_one_sad = sum(total_only_one_sad),
         all_sites = sum(total_sites))

all_di_filtered <- all_di %>%
  filter(s0 != n0,
         s0 != 1,
         n0 != (s0 + 1))

nrow(all_di_filtered)

```

Removing those with only one SAD results in the removal of 258 sites total. 176 from FIA, 56 from MCDB, and 26 from Misc. Abund.

```{r}
miscabund_problems <- as.character(c(144, 145, 145, 146, 147, 178, 446))

all_di_filtered <- all_di_filtered %>%
  mutate(is.miscabund.problem = ifelse(dat == "misc_abund",
                                       ifelse(site %in% miscabund_problems, T, F), F))

filter(all_di_filtered, is.miscabund.problem)

all_di_filtered <- all_di_filtered %>%
  filter(!is.miscabund.problem) %>%
  ungroup() %>%
  select(-is.miscabund.problem)

```

Finally, we will restrict aggregate analyses to sites whose feasible sets have more than 20 unique values for whichever shape metric we're interested in, **and** we will restrict analyses with skewness to sites with >2 species. This results in these final totals:

```{r}

all_di_filtered %>%
  filter(simpson_unique > 20) %>%
  group_by(dat) %>%
  summarize(sites_for_evenness = dplyr::n())

all_di_filtered %>%
  filter(skew_unique > 20, s0 > 2) %>%
  group_by(dat) %>%
  summarize(sites_for_skewness = dplyr::n())

```

### 2020-12-07 analysis/reports/manuscript_main.Rmd
filtering report

@@
          log_n0 = log(n0)) %>%
-  filter(n0 > s0,
-         s0 > 1,
+  filter(n0 != s0,
+         s0 != 1,
          !singletons,
-         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
+         n0 != (s0 + 1)) %>%
   mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
@@
 
-To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities.
+To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
 

### 2020-12-17 analysis/reports/appendix1_filtering.Rmd
appendices

--- 2020-12-07 analysis/reports/filtering_presampling.Rmd
@@
 Second, **after sampling but before we aggregate results across communities**, we remove communities that are problematic for a number of more nuanced reasons.
-This includes having only 1 possible SAD (S = 1, N = S, or N = S + 1); mixed relative abundance and count data (for the Misc.
-Abundance Database).
+This includes having only 1 possible SAD (S = 1, N = S, or N = S + 1).
 We also filter to communities whose sampled feasible sets yield more than 20 unique values for skewness/evenness.
@@
 
-- Misc.
-Abund includes datasets reported as relative abundance in addition to count data.
-We don't want any communities without counts, so we filter out records where abund = 0.
-*While preparing this report, RMD noticed that some communities have a __mixture__ of relative abundance and count data.
-These communities were sampled, but RMD does not believe it is appropriate to compare them to count-data-only communities.
-We therefore remove these 6 in the second, post-sampling, phase of filtering.*
+- Misc. Abund includes datasets reported as relative abundance in addition to count data. We don't want any communities without counts, so we filter out records where abund = 0.
 
@@
 
-We remove communities with only one possible SAD (N = S, N = S + 1, or S = 1) and five communities in the Misc.
-Abund Database that have mixed count and relative abundance data (there are more than 5 with a mixture, but only 5 that have both the mixture AND make it through the previous filters).
+We remove communities with only one possible SAD (N = S, N = S + 1, or S = 1).
 
@@
 
-```{r}
-miscabund_problems <- as.character(c(144, 145, 145, 146, 147, 178, 446))
-
-all_di_filtered <- all_di_filtered %>%
-  mutate(is.miscabund.problem = ifelse(dat == "misc_abund",
-                                       ifelse(site %in% miscabund_problems, T, F), F))
-
-filter(all_di_filtered, is.miscabund.problem)
-
-all_di_filtered <- all_di_filtered %>%
-  filter(!is.miscabund.problem) %>%
-  ungroup() %>%
-  select(-is.miscabund.problem)
-
-```
-
 Finally, we will restrict aggregate analyses to sites whose feasible sets have more than 20 unique values for whichever shape metric we're interested in, **and** we will restrict analyses with skewness to sites with >2 species.
@@
   group_by(dat) %>%
-  summarize(sites_for_evenness = dplyr::n())
+  summarize(sites_for_evenness = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(total_sites_for_evenness = sum(sites_for_evenness))
 
@@
   group_by(dat) %>%
-  summarize(sites_for_skewness = dplyr::n())
+  summarize(sites_for_skewness = dplyr::n()) %>%
+  mutate(total_sites_for_skewness = sum(sites_for_skewness))
 

### 2020-12-17 analysis/reports/appendix2_selfsimilarity.Rmd
appendices

--- 2020-11-30 analysis/reports/self_similarity.Rmd
@@
 output: 
-    word_document:
+    github_document:
        df_print: kable

### 2020-12-17 analysis/reports/appendix_s4.Rmd
appendices

---
title: ""
output: 
    word_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))

```

# Table S4. Proportion of sites with highly skewed or uneven SADs

```{r results table, echo = F}

overall_skew_results <- all_di %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  filter(simpson_unique > 20) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
         "Number of communities analyzed for skewness" = nsites_skew,
         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
         "Number of communities analyzed for evenness" = nsites_even)
```

```{r}
overall_results

# 
# overall_skew_results2 <- all_di %>%
#   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
#   filter(s0 > 2, skew_unique > 20) %>%
#   mutate(high_skew = skew_percentile_excl > 95) %>%
#   group_by(Dataset) %>%
#   summarize(proportion_skew_high = mean(high_skew),
#             nsites_skew = dplyr::n())
# 
# overall_simpson_results2 <- all_di %>%
#   filter(simpson_unique > 20) %>%
#   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
#   mutate(low_even = simpson_percentile < 5) %>%
#   group_by(Dataset) %>%
#   summarize(proportion_even_low = mean(low_even),
#             nsites_even = dplyr::n())
# 
# overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
#   rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
#          "Number of communities analyzed for skewness" = nsites_skew,
#          "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
#          "Number of communities analyzed for evenness" = nsites_even)

#overall_results2

```

### 2020-12-17 analysis/reports/manuscript_main.Rmd
misc abund rabbit hole
appendices

--- 2020-10-14 analysis/reports/manuscript_main.Rmd
@@
   mutate(Dataset = dat,
-    Dataset = ifelse(Dataset == "fia", "Forest Inventory and Analysis", Dataset),
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
          Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
-        Dataset = ifelse(Dataset == "mcdb", "Mammal Community DB", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
          Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
-        Dataset = ifelse(Dataset == "misc_abund", "Miscellaneous Abundance DB", Dataset))
-```
-
-# Final dataset in S and N space
-
-```{r final dataset s and n space}
-
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
-  geom_point(alpha = .1) +
-  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d() +
-  ggtitle("Communities by S and N") +
-  xlab("Log species richness (S)") +
-  ylab("Log total abundance (N)")
-
-ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
-  geom_point(alpha = .05) +
-  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d() +
-  ggtitle("Communities by S and N") +
-   facet_wrap(vars(Dataset), scales = "free") +
-  theme(legend.position = "bottom")
-  # geom_vline(xintercept = log(40)) +
-  # geom_hline(yintercept = log(1000))
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))
 
@@
 
-# Illustrations of 95% interval
+# Illustrations of 95% interval (Figure 1)
 
-To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities.
+To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
 
-# Skewness and evenness histograms by dataset
+```{r, fig.dim = c(7,7)}
+library(drake)
 
-```{r first hists}
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+
+net_summary <- readd(all_di_summary, cache = cache)
+
+net_summary <- net_summary %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)))
+
+example_fs <- readd(fs_s_44_n_13360, cache = cache)
+
+example_di <- readd(di_fs_s_44_n_13360, cache =cache)
+
+example_fs <- example_fs %>%
+  left_join(example_di) %>%
+  left_join(net_summary)
+
+example_fs2 <- readd(fs_s_7_n_71, cache = cache)
+
+example_di2 <- readd(di_fs_s_7_n_71, cache =cache)
+
+example_fs2 <- example_fs2 %>%
+  left_join(example_di2) %>%
+  left_join(net_summary)
+
+example_fs3 <- readd(fs_s_4_n_34, cache = cache)
+
+example_di3 <- readd(di_fs_s_4_n_34, cache =cache)
+
+example_fs3 <- example_fs3 %>%
+  left_join(example_di3) %>%
+  left_join(net_summary)
+
+breadth_plots <- list(
+
+  ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .25) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) +
+    theme(legend.position = "right"),
+
+  ggplot(example_fs3, aes(skew, ..ndensity..)) +
+    geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs3$skew_95[1], example_fs3$skew_min[1]), color = "red") +
+    ggtitle("", subtitle = paste0("Breadth index (skewness): ", round((example_fs3$skew_95_ratio_1t[1]), 2))),
+
+  ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .1) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) +
+    theme(legend.position = "right"),
+
+  ggplot(example_fs2, aes(skew, ..ndensity..)) +
+    geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs2$skew_95[1], example_fs2$skew_min[1]), color = "red") +
+    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs2$skew_95_ratio_1t[1]), 2))),
+
+  ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .1) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) +
+    theme(legend.position = "right"),
+
+  ggplot(example_fs, aes(skew, ..ndensity..)) +
+    geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs$skew_95[1], example_fs$skew_min[1]), color = "red") +
+    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs$skew_95_ratio_1t[1]), 2)))
+
+)
+
+fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2)
+
+plot(fig_1)
+
+DBI::dbDisconnect(db)
+rm(cache)
+
+```
+
+# Skewness and evenness histograms by dataset (Figure 2)
+
+```{r first hists, fig.dim = c(7,7)}
+fig_2 <- gridExtra::grid.arrange(grobs = list(
 
@@
     theme_bw() +
-  facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Skewness, all sites") +
-  xlab("Percentile rank of observed skewness value relative to feasible set") +
-  ylab("Number of communities")
+    facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Skewness") +
+    xlab("Percentile rank of observed value relative to feasible set") +
+    ylab("Number of communities"),
 
@@
     theme_bw() +
-  facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Evenness, all sites") +
-  xlab("Percentile rank of observed evenness value relative to feasible set") +
+    facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Evenness") +
+    xlab("Percentile rank of observed value relative to feasible set") +
     ylab("Number of communities")
+))
+
+plot(fig_2)
 
@@
 
-# Proportion of sites with highly skewed or uneven SADs
+# Breadth index by dataset (Figure 3)
 
-```{r results table}
+```{r, fig.dim = c(7,7)}
 
-overall_skew_results <- all_di %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results <- all_di %>%
-  filter(simpson_unique > 20) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
-  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-overall_results
-
-overall_skew_results2 <- all_di %>%
-   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results2 <- all_di %>%
-  filter(simpson_unique > 20) %>%
-   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
-   rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-overall_results2
-
-```
-
-# 95 intervals by size of FS
-
-```{r 95 intervals}
-
-ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  xlim(0, 100) +
-  ylim(0,1)+
-  xlab("Log number of elements in the feasible set") +
-  ylab("Narrowness of the distribution of sampled skewness values")
-
-ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  xlim(0, 100) +
-  ylim(0, 1)+
-  xlab("Log number of elements in the feasible set") +
-  ylab("Narrowness of the distribution of sampled evenness values")
-```
-
-# 95 intervals by dataset
-
-```{r}
-
+fig_3 <- gridExtra::grid.arrange(grobs = list(
   ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
@@
     facet_wrap(vars(Dataset), scales = "free_y") +
-    xlab("Narrowness of the distribution of sampled skewness values") +
-  ylab("Number of communities")
+    xlab("Breadth index") +
+    ylab("Number of communities") +
+    ggtitle("Skewness"),
 
@@
     facet_wrap(vars(Dataset), scales = "free_y") +
-    xlab("Narrowness of the distribution of sampled evenness values") +
-  ylab("Number of communities")
+    xlab("Breadth index") +
+    ylab("Number of communities") +
+    ggtitle("Evenness")
+))
+
+plot(fig_3)
 
 ```
+
+# Comparison of FIA and comparably sized communities (Figure 4)
+
+```{r, fig.dim = c(7,7)}
+
+fia_max_s = max(filter(all_di, dat == "fia")$s0)
+fia_max_n = max(filter(all_di, dat == "fia")$n0)
+
+fia = filter(all_di, dat == "fia")
+
+small_di <- all_di %>%
+  filter(s0 <= fia_max_s,
+         n0 <= fia_max_n) %>%
+  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
+         right_corner = FALSE)
+
+for(i in 1:nrow(small_di)) {
+  if(small_di$dat[i] != "fia") {
+    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
+
+    max_n0_for_this_s0 = max(fia_match_s0$n0)
+
+    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
+
+  }
+}
+
+small_di <- small_di %>%
+  filter(!right_corner)
+not_fia <- filter(small_di, fia_yn != "fia")
+fia = filter(small_di, dat == "fia")
+
+small_di_s_n <- small_di %>%
+  select(s0, n0) %>%
+  distinct() %>%
+  mutate(in_fia = FALSE,
+         in_not_fia = FALSE)
+
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 
+  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
+
+}
+
+small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
+
+set.seed(1977)
+
+subsamples <- list()
+
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
+
+  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
+  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
+
+  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
+
+}
+
+sub_di <- bind_rows(subsamples) %>%
+  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
+
+fig_4 <- gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(sub_di, skew_unique > 20), aes(skew_95_ratio_1t)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Breadth index") +
+    ylab("Number of communities") +
+    ggtitle("Breadth index", subtitle = "Skewness"),
+
+  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_95_ratio_1t)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Breadth index") +
+    ylab("") +
+    ggtitle("", subtitle = "Evenness"),
+
+  ggplot(filter(sub_di, skew_unique > 20), aes(skew_percentile_excl)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Percentile rank") +
+    ylab("Number of communities") +
+    ggtitle("Percentile rank", subtitle = "Skewness"),
+
+  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_percentile)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Percentile rank") +
+    ylab("")+
+    ggtitle("", subtitle = "Evenness")), ncol = 2)
+
+plot(fig_4)
+
+```
+
+```{r}
+pdf("figure_1.pdf")
+plot(fig_1)
+dev.off()
+
+pdf("figure_2.pdf")
+ plot(fig_2)
+ dev.off()
+
+pdf("figure_3.pdf")
+plot(fig_3)
+dev.off()
+
+pdf("figure_4.pdf")
+ plot(fig_4)
+dev.off()
+```

### 2020-12-17 analysis/reports/supporting_figs_and_tables_3to6.Rmd
appendices

---
title: "Figures and results supporting main manuscript"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))

```

## Figure S3. Final dataset in S and N space

```{r final dataset s and n space}

s3_fig1 <- ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
  geom_point(alpha = .1) +
  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
  theme_bw() +
  scale_color_viridis_d(end = .9) +
  ggtitle("Communities by S and N") +
  xlab("Log species richness (S)") +
  ylab("Log total abundance (N)")

plot(s3_fig1)
# ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
#   geom_point(alpha = .05) +
#   geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
#   theme_bw() +
#   scale_color_viridis_d(end = .9) +
#   ggtitle("Communities by S and N") +
#   facet_wrap(vars(Dataset), scales = "free") +
#   theme(legend.position = "bottom")
# # geom_vline(xintercept = log(40)) +
# # geom_hline(yintercept = log(1000))

pdf("figure_s3.pdf")
plot(s3_fig1)
dev.off()
```

# Table S4. Proportion of sites with highly skewed or uneven SADs

```{r results table}

overall_skew_results <- all_di %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results <- all_di %>%
  filter(simpson_unique > 20) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
         "Number of communities analyzed for skewness" = nsites_skew,
         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
         "Number of communities analyzed for evenness" = nsites_even)

overall_results

overall_skew_results2 <- all_di %>%
  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
  filter(s0 > 2, skew_unique > 20) %>%
  mutate(high_skew = skew_percentile_excl > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results2 <- all_di %>%
  filter(simpson_unique > 20) %>%
  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
         "Number of communities analyzed for skewness" = nsites_skew,
         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
         "Number of communities analyzed for evenness" = nsites_even)

#overall_results2

```

# Figure S5. Breadth index by size of FS

```{r 95 intervals}
s3_fig2 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100) +
  ylim(0,1)+
  xlab("Log number of elements in the feasible set") +
  ylab("Breadth index") +
  ggtitle("Breadth index (skewness)"),

ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
  geom_point(alpha = .1) +
  theme_bw() +
  xlim(0, 100) +
  ylim(0, 1)+
  xlab("Log number of elements in the feasible set") +
  ggtitle("Breadth index (evenness)") +
  ylab("Breadth index")
), ncol = 2)

pdf("figure_s5.pdf")
plot(s3_fig2)
dev.off()
```

# Table S6. FIA comparison results

```{r}

fia_max_s = max(filter(all_di, dat == "fia")$s0)
fia_max_n = max(filter(all_di, dat == "fia")$n0)

fia = filter(all_di, dat == "fia")

small_di <- all_di %>%
  filter(s0 <= fia_max_s,
         n0 <= fia_max_n) %>%
  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
         right_corner = FALSE)

for(i in 1:nrow(small_di)) {
  if(small_di$dat[i] != "fia") {
    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])

    max_n0_for_this_s0 = max(fia_match_s0$n0)

    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0

  }
}

small_di <- small_di %>%
  filter(!right_corner)
not_fia <- filter(small_di, fia_yn != "fia")
fia = filter(small_di, dat == "fia")

small_di_s_n <- small_di %>%
  select(s0, n0) %>%
  distinct() %>%
  mutate(in_fia = FALSE,
         in_not_fia = FALSE)

for(i in 1:nrow(small_di_s_n)) {

  this_s0 = small_di_s_n$s0[i]
  this_n0 = small_di_s_n$n0[i]

  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)

  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 
  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0

}

small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)

set.seed(1977)

subsamples <- list()

for(i in 1:nrow(small_di_s_n)) {

  this_s0 = small_di_s_n$s0[i]
  this_n0 = small_di_s_n$n0[i]

  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)

  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)

  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))

  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)

  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))

}

sub_di <- bind_rows(subsamples) %>%
  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))

sub_di %>%
  filter(s0 > 2) %>%
  group_by_all %>%
  mutate(skew_percentile_excl = ifelse(skew_unique >= 20, skew_percentile_excl, NA),
         simpson_percentile = ifelse(simpson_unique >= 20, simpson_percentile, NA)) %>%
  ungroup() %>%
  group_by(Dataset) %>%
  summarize(prop_skew_high = mean(skew_percentile_excl > 95, na.rm = T),
            prop_even_low = mean(simpson_percentile < 5, na.rm = T),
            nsites_skew = sum(!is.na(skew_percentile_excl)),
            nsites_even = sum(!is.na(simpson_percentile))) %>%
   rename("Proportion of communities with skewness above 95th percentile" = prop_skew_high,
         "Number of communities analyzed for skewness" = nsites_skew,
         "Proportion of communities with evenness below 5th percentile" = prop_even_low,
         "Number of communities analyzed for evenness" = nsites_even)

```

### 2020-12-17 analysis/reports/figure_s3.Rmd
reorganizing reports and remove selfsim metrics fromcodecov as they are supplementary

--- 2020-12-17 analysis/reports/supporting_figs_and_tables_3to6.Rmd
@@
 ---
-title: "Figures and results supporting main manuscript"
-author: Renata Diaz
-date: "`r Sys.Date()`"
+title: ""
 output: 
@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, echo = F}
 knitr::opts_chunk$set(echo = FALSE)

### 2020-12-17 analysis/reports/figure_s5.Rmd
reorganizing reports and remove selfsim metrics fromcodecov as they are supplementary

--- 2020-12-17 analysis/reports/supporting_figs_and_tables_3to6.Rmd
@@
 
-## Figure S3. Final dataset in S and N space
-
-```{r final dataset s and n space}
-
-s3_fig1 <- ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
-  geom_point(alpha = .1) +
-  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d(end = .9) +
-  ggtitle("Communities by S and N") +
-  xlab("Log species richness (S)") +
-  ylab("Log total abundance (N)")
-
-plot(s3_fig1)
-# ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
-#   geom_point(alpha = .05) +
-#   geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
-#   theme_bw() +
-#   scale_color_viridis_d(end = .9) +
-#   ggtitle("Communities by S and N") +
-#   facet_wrap(vars(Dataset), scales = "free") +
-#   theme(legend.position = "bottom")
-# # geom_vline(xintercept = log(40)) +
-# # geom_hline(yintercept = log(1000))
-
-pdf("figure_s3.pdf")
-plot(s3_fig1)
-dev.off()
-```
-
-# Table S4. Proportion of sites with highly skewed or uneven SADs
-
-```{r results table}
-
-overall_skew_results <- all_di %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results <- all_di %>%
-  filter(simpson_unique > 20) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
-  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-overall_results
-
-overall_skew_results2 <- all_di %>%
-  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results2 <- all_di %>%
-  filter(simpson_unique > 20) %>%
-  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
-  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-#overall_results2
-
-```
-
 # Figure S5. Breadth index by size of FS
@@
 ```
-
-# Table S6. FIA comparison results
-
-```{r}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-sub_di %>%
-  filter(s0 > 2) %>%
-  group_by_all %>%
-  mutate(skew_percentile_excl = ifelse(skew_unique >= 20, skew_percentile_excl, NA),
-         simpson_percentile = ifelse(simpson_unique >= 20, simpson_percentile, NA)) %>%
-  ungroup() %>%
-  group_by(Dataset) %>%
-  summarize(prop_skew_high = mean(skew_percentile_excl > 95, na.rm = T),
-            prop_even_low = mean(simpson_percentile < 5, na.rm = T),
-            nsites_skew = sum(!is.na(skew_percentile_excl)),
-            nsites_even = sum(!is.na(simpson_percentile))) %>%
-   rename("Proportion of communities with skewness above 95th percentile" = prop_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = prop_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-```

### 2020-12-17 analysis/reports/table_s6.Rmd
reorganizing reports and remove selfsim metrics fromcodecov as they are supplementary

--- 2020-12-17 analysis/reports/supporting_figs_and_tables_3to6.Rmd
@@
 ---
-title: "Figures and results supporting main manuscript"
-author: Renata Diaz
-date: "`r Sys.Date()`"
+title: ""
 output: 
-    github_document:
+    word_document:
        df_print: kable
@@
 
-## Figure S3. Final dataset in S and N space
+# Table S6. Proportion of sites with highly skewed or uneven SADs for a subset of FIA communities compared to matching communities from other datasets
 
-```{r final dataset s and n space}
-
-s3_fig1 <- ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
-  geom_point(alpha = .1) +
-  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d(end = .9) +
-  ggtitle("Communities by S and N") +
-  xlab("Log species richness (S)") +
-  ylab("Log total abundance (N)")
-
-plot(s3_fig1)
-# ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
-#   geom_point(alpha = .05) +
-#   geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
-#   theme_bw() +
-#   scale_color_viridis_d(end = .9) +
-#   ggtitle("Communities by S and N") +
-#   facet_wrap(vars(Dataset), scales = "free") +
-#   theme(legend.position = "bottom")
-# # geom_vline(xintercept = log(40)) +
-# # geom_hline(yintercept = log(1000))
-
-pdf("figure_s3.pdf")
-plot(s3_fig1)
-dev.off()
-```
-
-# Table S4. Proportion of sites with highly skewed or uneven SADs
-
-```{r results table}
-
-overall_skew_results <- all_di %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results <- all_di %>%
-  filter(simpson_unique > 20) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
-  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-overall_results
-
-overall_skew_results2 <- all_di %>%
-  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results2 <- all_di %>%
-  filter(simpson_unique > 20) %>%
-  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
-  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-#overall_results2
-
-```
-
-# Figure S5. Breadth index by size of FS
-
-```{r 95 intervals}
-s3_fig2 <- gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  xlim(0, 100) +
-  ylim(0,1)+
-  xlab("Log number of elements in the feasible set") +
-  ylab("Breadth index") +
-  ggtitle("Breadth index (skewness)"),
-
-ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  xlim(0, 100) +
-  ylim(0, 1)+
-  xlab("Log number of elements in the feasible set") +
-  ggtitle("Breadth index (evenness)") +
-  ylab("Breadth index")
-), ncol = 2)
-
-pdf("figure_s5.pdf")
-plot(s3_fig2)
-dev.off()
-```
-
-# Table S6. FIA comparison results
-
-```{r}
+```{r, include = F, echo = F}
 
@@
 
+```
+```{r}
 sub_di %>%

### 2020-12-17 analysis/reports/manuscript_main.Rmd
tweaks ad updates

@@
     facet_wrap(vars(Dataset), scales = "free_y") +
-    xlab("Breadth index") +
+    xlab("Breadth index (ranges 0-1, with 1 being very broad)") +
     ylab("Number of communities") +
@@
 ```{r}
-pdf("figure_1.pdf")
+pdf("figure_1.pdf", title = "Figure 1")
 plot(fig_1)
@@
 
-pdf("figure_2.pdf")
+pdf("figure_2.pdf", title = "Figure 2")
  plot(fig_2)
@@
 
-pdf("figure_3.pdf")
+pdf("figure_3.pdf", title = "Figure 3")
 plot(fig_3)
@@
 
-pdf("figure_4.pdf")
+pdf("figure_4.pdf", title = "Figure 4")
  plot(fig_4)

### 2020-12-18 analysis/reports/figure_s3.Rmd
rearranging

@@
 
-## Figure S3. Final dataset in S and N space
+# Figure S3
 
-```{r final dataset s and n space}
+```{r final dataset s and n space, echo = F}
 
@@
 
-# Table S4. Proportion of sites with highly skewed or uneven SADs
-
-```{r results table}
-
-overall_skew_results <- all_di %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results <- all_di %>%
-  filter(simpson_unique > 20) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results <- left_join(overall_skew_results, overall_simpson_results) %>%
-  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-overall_results
-
-overall_skew_results2 <- all_di %>%
-  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  filter(s0 > 2, skew_unique > 20) %>%
-  mutate(high_skew = skew_percentile_excl > 95) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_skew_high = mean(high_skew),
-            nsites_skew = dplyr::n())
-
-overall_simpson_results2 <- all_di %>%
-  filter(simpson_unique > 20) %>%
-  mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-  mutate(low_even = simpson_percentile < 5) %>%
-  group_by(Dataset) %>%
-  summarize(proportion_even_low = mean(low_even),
-            nsites_even = dplyr::n())
-
-overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
-  rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-#overall_results2
-
-```
-
-# Figure S5. Breadth index by size of FS
-
-```{r 95 intervals}
-s3_fig2 <- gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  xlim(0, 100) +
-  ylim(0,1)+
-  xlab("Log number of elements in the feasible set") +
-  ylab("Breadth index") +
-  ggtitle("Breadth index (skewness)"),
-
-ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
-  geom_point(alpha = .1) +
-  theme_bw() +
-  xlim(0, 100) +
-  ylim(0, 1)+
-  xlab("Log number of elements in the feasible set") +
-  ggtitle("Breadth index (evenness)") +
-  ylab("Breadth index")
-), ncol = 2)
-
-pdf("figure_s5.pdf")
-plot(s3_fig2)
-dev.off()
-```
-
-# Table S6. FIA comparison results
-
-```{r}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-sub_di %>%
-  filter(s0 > 2) %>%
-  group_by_all %>%
-  mutate(skew_percentile_excl = ifelse(skew_unique >= 20, skew_percentile_excl, NA),
-         simpson_percentile = ifelse(simpson_unique >= 20, simpson_percentile, NA)) %>%
-  ungroup() %>%
-  group_by(Dataset) %>%
-  summarize(prop_skew_high = mean(skew_percentile_excl > 95, na.rm = T),
-            prop_even_low = mean(simpson_percentile < 5, na.rm = T),
-            nsites_skew = sum(!is.na(skew_percentile_excl)),
-            nsites_even = sum(!is.na(simpson_percentile))) %>%
-   rename("Proportion of communities with skewness above 95th percentile" = prop_skew_high,
-         "Number of communities analyzed for skewness" = nsites_skew,
-         "Proportion of communities with evenness below 5th percentile" = prop_even_low,
-         "Number of communities analyzed for evenness" = nsites_even)
-
-```
+**Legend.** Distribution of communities from each dataset in termof total abundance (N) and species richness (S).
+Communities range from few species and individuals (lower left corner) to speciose communities with many individuals (upper right).
+However, datasets are not evenly distributed across this state space due to differences in their sampling intensity, design, and underlying biology (e.g.
+productivity, regional richness, taxonomic group, or other factors that influence the capacity of a community to support large numbers of species and individuals).

### 2020-12-18 analysis/reports/figure_s5.Rmd
rearranging

@@
 
-# Figure S5. Breadth index by size of FS
+# Figure S5.
 
-```{r 95 intervals}
+```{r 95 intervals, fig.dim = c(8,4)}
 s3_fig2 <- gridExtra::grid.arrange(grobs = list(
@@
 ```
+
+**Legend.** The breadth index (defined as the ratio of the width of a one-tailed 95% density interval relative to the full range of a distribution) for the distributions of skewness and evenness obtained from the sampled feasible set declines as the number of elements in the feasible set increases.
+This indicates more narrow and well-resolved statistical baselines for large feasible sets.

### 2020-12-18 analysis/reports/table_s4.Rmd
rearranging

--- 2020-12-17 analysis/reports/appendix_s4.Rmd
@@
 
-# Table S4. Proportion of sites with highly skewed or uneven SADs
+# Table S4
 
@@
 
-# 
-# overall_skew_results2 <- all_di %>%
-#   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-#   filter(s0 > 2, skew_unique > 20) %>%
-#   mutate(high_skew = skew_percentile_excl > 95) %>%
-#   group_by(Dataset) %>%
-#   summarize(proportion_skew_high = mean(high_skew),
-#             nsites_skew = dplyr::n())
-# 
-# overall_simpson_results2 <- all_di %>%
-#   filter(simpson_unique > 20) %>%
-#   mutate(Dataset = ifelse(dat == "fia", "Forest Inventory and Analysis", "Other datasets")) %>%
-#   mutate(low_even = simpson_percentile < 5) %>%
-#   group_by(Dataset) %>%
-#   summarize(proportion_even_low = mean(low_even),
-#             nsites_even = dplyr::n())
-# 
-# overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2) %>%
-#   rename("Proportion of communities with skewness above 95th percentile" = proportion_skew_high,
-#          "Number of communities analyzed for skewness" = nsites_skew,
-#          "Proportion of communities with evenness below 5th percentile" = proportion_even_low,
-#          "Number of communities analyzed for evenness" = nsites_even)
+```
 
-#overall_results2
-
-```
+**Caption**.
+Proportion of communities in each dataset with highly skewed or uneven SADs compared to their sampled feasible sets.
+For most datasets, considerably more communities are extremely skewed and uneven relative to their feasible sets than would be expected by chance: at random, only 5% of communities should fall in these extremes.
+The FIA database differs from all the others in that no more than 5% of its communities are extremely skewed, and only 9% of its communities are highly uneven.

### 2020-12-18 analysis/reports/table_s6.Rmd
rearranging

@@
 
-# Table S6. Proportion of sites with highly skewed or uneven SADs for a subset of FIA communities compared to matching communities from other datasets
+# Table S6
 
@@
 ```
+
+**Caption.** Proportion of sites with highly skewed or uneven SADs for a subset of FIA communities and comparably-sized communities from other datasets.
+We found 371 pairs of communities for which a community from FIA had a counterpart from another dataset with exactly matching S and N.
+For these communities, the proportion of communities whose observed SADs are highly skewed or uneven relative to their sampled feasible sets does not differ between FIA and other datasets.

### 2020-12-18 analysis/reports/appendix2_selfsimilarity.Rmd
filtering edits and data sources

--- 2020-11-30 analysis/reports/self_similarity.Rmd
@@
 ---
-title: "Self-similarity of the elements of the feasible set"
-author: Renata Diaz
-date: "`r Sys.Date()`"
+title: "Appendix 2 - Self-similarity of the elements of the feasible set"
 output: 
@@
 We are interested in how the self-similarity of the elements of the feasible set varies over gradients in S and N.
-The intuition from "common-sense" probability theory, statistical mechanics, law-of-large-numbers intuition is that, as the number of possible arrangements becomes large, the different possible arrangements should become more self-similar.
-However, we don't know that this is the case for SADs, nor do we know the values for S and N where things really start to converge.
+The more self-similar the feasible set is, the less likely it is for us to obtain a SAD that differs from the majority of the feasible set by chance.
+The intuition from "common-sense" probability theory, and a common theme in statistical mechanics (Jaynes 1957) is that as the number of possible arrangements becomes large, the majority of  possible arrangements should become very similar to each other in broad-scale characteristics.
+However, we don't know that this is the case for SADs, nor do we know the values for S and N where this increase in self-similarity begins to occur.
 
-In the manuscript, I use the ratio of the 95% interval of summary statistic values, to the full range of summary statistic values.
-This can be calculated quickly and without introducing new statistics, etc to the main manuscript.
+In the manuscript, we use a breadth index defined as ratio of the 95% interval of summary statistic values : the full range of summary statistic values.
+This can be calculated quickly and is easily interpretable.
 It also directly reflects the distributions to which we are comparing our observations.
-However, it may not tell the full story: if the summary statistic values are idiosyncratic (skewness in particular can behave counterintuitively), it reflects those idiosyncracies.
+However, it is not a widely-used metric.
+Also, if the summary statistic values are idiosyncratic (skewness in particular can behave counterintuitively), it can reflect those idiosyncracies.
 
@@
 
-I initially did this analysis in https://github.com/diazrenata/sadspace and am porting the functions and analysis over to this repo for the supplement.
-
-## Directly establishing self-similarity
-
-### Overview
+## Overview
 
@@
 
-### Walkthrough
+Here we demonstrate this process for an example feasible set, and then present results for feasible sets spanning the range of S and N present in our data.
+
+## Example
 
@@
 
-I have implemented 5 metrics of similarity for comparing samples:
+We have implemented 5 metrics of similarity for comparing samples:
 
-* R2
-* R2 on log-transformed abundances
-* The coefficient of determination from a linear model fitting one sample to the other
-* The proportion of individuals allocated to species of differing abundances
-* The estimated Kullbak-Lieber (sp) divergence between the two samples
+* R2 (`r2`). High R2 indicates higher self-similarity. 
+* R2 on log-transformed abundances (`r2_log`). Higher values indicate higher self-similarity.
+* The coefficient of determination from a linear model fitting one sample to the other (`cd`). Higher values indicate higher self-similarity.
+* The proportion of individuals allocated to species of differing abundances (`prop_off`). **Lower** values indicate greater self-similarity. 
+* The estimated Kullback–Leibler divergence between the two samples (`div`). **Lower** values indicate greater self-similarity.
 
@@
 
-We repeat this comparison process numerous times to get numerous values for the self-similarity metrics.
+We draw numerous pairs of SADs and compare them numerous times to get distributions for the self similarity metrics.
 
@@
 
-We repeat this process for feasible sets with varying S and N, and compare the distribution of the self-similarity metrics across the variation in S and N.
+We repeat this process for feasible sets for different values of S and N, and compare the distributions for the self-similarity metrics for the different feasible sets.
+Here we compare the distributions for the self-similarity metrics for our original feasible set (S = 7, N = 71, "small" in the figure) and for a much larger community (S = 44, N = 13360, "large").
 
-```{r comparison 2, fig.dim = c(2,2)}
+```{r comparison 2, fig.dim = c(8,6)}
 
@@
 both_comparisons <- bind_rows(comparisons, comparisons2) %>%
-  mutate(s_and_n = paste0("s_", s0, "_n_", n0))
+  mutate(community_size = ifelse(n0 > 13000, "large", "small"))
 
-ggplot(both_comparisons, aes(r2, color = s_and_n)) +
+gridExtra::grid.arrange(grobs = list(
+  ggplot(both_comparisons, aes(1, community_size, color = community_size)) +
+    geom_point(size =8) +
+    geom_label(aes(label = community_size), nudge_x = .005, size = 8) +
+    theme_void() +
+  theme(legend.position = "none") +
+  scale_color_viridis_d(end = .8, option = "plasma") +
+    xlim(.99999, 1.006)
+
+    ,
+
+ggplot(both_comparisons, aes(r2, color = community_size)) +
   geom_density() +
   theme_bw() +
-  theme(legend.position = "top")
+  theme(legend.position = "none") +
+  scale_color_viridis_d(end = .8, option = "plasma"),
 
-ggplot(both_comparisons, aes(r2_log, color = s_and_n)) +
+ggplot(both_comparisons, aes(r2_log, color = community_size)) +
   geom_density() +
   theme_bw() +
-  theme(legend.position = "top")
+  theme(legend.position = "none") +
+  scale_color_viridis_d(end = .8, option = "plasma"),
 
-ggplot(both_comparisons, aes(cd, color = s_and_n)) +
+ggplot(both_comparisons, aes(cd, color = community_size)) +
   geom_density() +
   theme_bw() +
-  theme(legend.position = "top")
+  theme(legend.position = "none") +
+  scale_color_viridis_d(end = .8, option = "plasma"),
 
-ggplot(both_comparisons, aes(prop_off, color = s_and_n)) +
+ggplot(both_comparisons, aes(prop_off, color = community_size)) +
   geom_density() +
   theme_bw() +
-  theme(legend.position = "top")
+  theme(legend.position = "none") +
+  scale_color_viridis_d(end = .8, option = "plasma"),
 
-ggplot(both_comparisons, aes(div, color = s_and_n)) +
+ggplot(both_comparisons, aes(div, color = community_size)) +
   geom_density() +
   theme_bw() +
-  theme(legend.position = "top")
+  theme(legend.position = "none") +
+  scale_color_viridis_d(end = .8, option = "plasma")
 
+), ncol = 3)
 ```
+
+For each metric, the large community is more self-similar than the smaller.
+That is, it has consistently higher R2, r2_log, and coefficient of determination values, and lower prop_off and K-L divergence.
 
@@
 
-Here we have drawn samples from a "net" of points in S and N space that spans the range present in our datasets.
+Here we have drawn samples from a set of points in S and N space that spans the range present in our datasets.
 For each feasible set we make 200 comparisons of elements (although for small feasible sets, 200 is not necessarily possible).
-Here is how that net is distributed in S and N space, colored by the log() number of elements in the feasible set.
+Here is how that set is distributed in S and N space, colored by the log() number of elements in the feasible set.
 
@@
 * We need to have the same number of comparisons for every feasible set, so that the density distributions will be comparable.
-In order to get a large swatch of S by N space, I've taken 50 comparisons from every feasible set.
+In order to get a large swatch of S by N space, we have taken 50 comparisons from every feasible set.
 This is pretty low, so it lets us get even small feasible sets.
@@
 For some of them (R2, log r2) they can have nonsensical long tails towards very low values.
-For visualization, I've filtered out the long tail values (prior to selecting the 50 comparisons).
-The long tails tend to be most dominant in the comparisons made from small feasible sets.
+For visualization, we filtered out the long tail values (prior to selecting the 50 comparisons).
+The long tails tend to be most prevalent in the comparisons made from small feasible sets.
 Removing them therefore makes the small feasible sets look *more* self-similar.
@@
 
-Here is R2 for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+Here is R2 for only relatively small feasible sets (those with fewer than $e^20$ elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
 
@@
 
-Here is R2 on logged vectors for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+Here is R2 on logged vectors for only "small" feasible sets. This lets us zoom in on the distributions where they start to broaden out.
 
@@
 
-Here is cd for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+Here is cd for only "small" feasible sets.
 
@@
 
-Here is prop_off for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+Here is prop_off for only "small" feasible sets.
 
@@
 
-Here is K-L divergence for only "small" feasible sets (those with fewer than `r exp(20)` elements in the feasible set). This lets us zoom in on the distributions where they start to broaden out.
+Here is K-L divergence for only "small" feasible sets.
 
@@
 
-### In summary
+## In summary
 
-Large feasible sets are consistently more self-similar than small ones.
+Large feasible sets are consistently more self-similar than small ones, regardless of the metric of self-similarity used.
+
+## References
+
+Jaynes, E.T. (1957). Information Theory and Statistical Mechanics. *Phys. Rev.*, 106, 620–630.

### 2020-12-19 analysis/howto.Rmd
undo accidental folder move

@@
 
-Either source one of the pipelines directory or run via sbatch.
+Either source one of the pipelines directory or run via sbatch. Running directly is going to take a lot of CPU.
+
+The plans render dataset-level reports, but these have not been updated in a while.
+
+# Collect all_di
+
+Run `analysis/helper_scripts/make_all_di.R` to collect the results from each of the pipelines into one dataframe.
+
+# Render manuscript-level reports
+
+Running or knitting (an as-yet-uncompiled) doc will reproduce the figures and results summaries presented in the manuscript.
+
+(rarefaction doc) will reproduce the rarefaction analysis in the supplement.
+
+(range of variation doc) will reproduce the range of variation analysis in the supplement.

### 2020-12-19 analysis/reports/accessory/less_than_equal.Rmd

---
title: "Effect of < v <= in percentile definition"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)

```

You can define the %ile score as either

- the % of values in a comparison vector that are **less than** a focal value
- the % of values that are **less than or equal to** that value

You see both definitions out in the world.

When I initially coded up the analysis, I used **<**. I didn't think about it much and as I was writing the manuscript I wrote **<=**. So that got me curious if it matters.

It *should not* matter too much as long as there are many unique values in the comparison vector. However, if there are only a handful, and the focal value is equal to an element of the comparison vector, using <= will cause the score to jump up. The jumps will be in increments of 100/n, with n the number of elements in the comparison vector. Meaning if there is only one value, < will give a score of 0 and <= will give a score of 100! And if there are ties, and the focal value is equal to the tie value, the jump will be (100 / n) * m, with m the number of elements in the comparison vector equal to the tie value.

#### Demo with toy data

```{r a handful of values, echo = T}

percentile_lt <- function(focal, comparison) {
  100 * (sum(comparison < focal) / length(comparison))
}

percentile_ltet <- function(focal, comparison) {
  100 * (sum(comparison <= focal) / length(comparison))
}

# Many values

many <- seq(1, 100, by = .1)

focal <- runif(1, 1, 100)
focal <- round(focal, 1) # rounding so focal == a value in many

percentile_lt(focal, many)
percentile_ltet(focal, many)

# A few values
few <- seq(1, 101, by = 20)

focal <- ceiling(focal / 20) * 20 + 1 # again, rounding so focal == a value in few

percentile_lt(focal, few)

percentile_ltet(focal, few)

# A few values with ties
few_with_ties <- c(seq(1, 81, by = 20), 41)

focal <- 41 # if focal == tie value, you get the largest possible jump

percentile_lt(focal, few_with_ties)

percentile_ltet(focal, few_with_ties)

# Just one value

one <- runif(1, 1, 100)

focal <- one # if there is only 1 element in one, focal MUST be that element

percentile_lt(focal, one)
percentile_ltet(focal, one)

```

### For our purposes

We can expect using <= to give us, if anything, higher percentile scores. We can expect this effect to be more pronounced for distributions with relatively few unique values. This is probably strongly correlated with the number of unique elements in the feasible set and the number of unique samples we found from the feasible set, but is not necessarily identical to it because two unique samples can have the same values for skewness or evenness. This will create **ties**, which can cause quite large jumps.

If the comparison vector is short, and/or has repeated values, we may get noticeably higher scores using <= than using <. Usually I think being short has a larger effect than having ties - unless you have a very long vector that is all ties, which doesn't happen in this context. Being short also makes ties more impactful.

Especially if the feasible set is small, the focal value is guaranteed to be an element of the comparison vector. That is because the comparison vector, for small FS, is an exhaustive account of all possible values for the focal value.

#### Change in %ile score

```{r real data, include=FALSE}

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 > s0,
         !singletons,
         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
```

##### Skewness
```{r skew change, fig.dim = c(4,3)}

ggplot(filter(all_di, s0 > 2), aes(x = skew_percentile_excl, y = skew_percentile, color = nsamples)) +
  geom_point(alpha = .1) +
  facet_wrap(vars(dat)) +
  scale_color_viridis_c(option = "plasma") +
  theme_bw()

all_di <- all_di  %>%
  mutate(skew_change = skew_percentile - skew_percentile_excl,
         even_change = simpson_percentile -
           simpson_percentile_excl)

ggplot(filter(all_di, s0 > 2), aes(x = nsamples, y = skew_change)) +
  geom_point(alpha = .1) +
  facet_wrap(vars(dat)) +
  theme_bw() +
  geom_vline(xintercept = 150)

```

For skewness,

- Jumps occur and can be quite large, including jumps from 0 to 100!
    - Using < or <= could qualitatively change our interpretation of whether we see overrepresentation in the extremes
    - Because the one-tail for skewness is asking whether observed values are usually **higher** than the comparison vectors, using **<=** will give us a **stronger** apparent effect
- Jumps occur only when the number of samples is low - for the most part, well below 500 and usually below 150 (vertical line on right graph). 
    - So < vs <= is mostly likely to be important for small FS
        - (The number of samples is strongly correlated with the size of the FS, up to a threshold. Currently running an update to `pull_di` to see how the size of FS and # samples is correlated to the # unique values in the comparison vectors.)

##### Evenness
```{r even change, fig.dim = c(4,3)}

ggplot(filter(all_di), aes(x = simpson_percentile_excl, y = simpson_percentile, color = nsamples)) +
  geom_point(alpha = .1) +
  facet_wrap(vars(dat)) +
  scale_color_viridis_c(option = "plasma") +
  theme_bw()

ggplot(filter(all_di), aes(x = nsamples, y = even_change)) +
  geom_point(alpha = .1) +
  facet_wrap(vars(dat)) +
  theme_bw()

```

For evenness, we see the same general outcome as for skewness. However,

- The one-tail for evenness is asking whether the observed values are **lower** than the comparison. So using <= will tend to weaken the effect we perceive.
- The jumps for evenness are confined to even smaller numbers of samples than skewness. 
    - My intuition is that this is because you tend to get ties more often with skewness than with evenness (skewness is a little bit of a strange creature). But I haven't confirmed this.

#### The conservative option

While both <= and < are valid more generally, I think there may be reasoning to prefer one over the other in this context.

Specifically, we want to know how *weird* the observation is. If the observation is equal to a very common value in the comparison vector, it's *not that weird*. So we don't want all those ties to count as values that the observation is more extreme than.

Because we are using less than, and the question for skewness is whether the observation is unusually *high*, the conservative approach for skewness is to use **<**. This will not allow an observation that matches a common tie value to count as more extreme than the ties.

The question for evenness is whether the observation is unusually low. If the observation is equal to a common tie value, using < will put the observation just to the left of those ties, effectively. It will be driven artificially low. Using <=, however, will count those tie elements as values to the left of the observation, and make it look less extreme. Which it is, if it matches all those ties.

So using < for skewness and <= for evenness gives us an appropriately conservative estimate of how weird the focal values are in the case where the focal values match common ties in the comparison vectors.

I am not sure if this logic really addresses the scenario where the comparison vectors do not have ties, but are quite short. My intuition there is that extremely short vectors - roughly on a scale of fewer than 20-100 values - are not very informative in this framework. Using <= and < for skew and even, respectively, is still the conservative tack in terms of detecting deviations.

Also, the impact on "statistical significance" is strongest for very short vectors. That is because, in the absence of ties, the jump increment is 100/n, with n the length of the comparison vector. If we define significance using an arbitrary cutoff of being more extreme than 95% of comparison values, then for the jump to matter it must get you from below 95 to 95 (for skew) or from above 5 to 5 (for even). If there are even 100 values in the comparison vector, the jump should only affect observations landing at the 94th or 6th percentiles. If there are fewer, it becomes more problematic: if there are only 5 values, using the more generous condition will move you from a score of 80 to a score of 100. But if there are only 5 values, this approach is almost certainly not appropriate anyway....(I can't prove it, but I don't think 5 is enough to define an attractor...!)

#### Effects on results

##### Overall results

Here are the overall result histograms and tables using < and <=...

###### Skew
```{r skewness result, fig.dim = c(4, 3)}

ggplot(filter(all_di, s0 >2), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") +
  ggtitle("Skew, <=")

ggplot(filter(all_di, s0 >2), aes(x = skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") +
  ggtitle("Skew, <")

all_di %>%
  filter(s0 > 2) %>%
  group_by(dat) %>%
  summarize(prop_skew_high_ltet = mean(skew_percentile > 95),
            prop_skew_high_lt = mean(skew_percentile_excl > 95),
            n_skew_sites = dplyr::n())

```

###### Evenness
```{r evenness result, fig.dim = c(4, 3)}

ggplot(filter(all_di, s0 >2), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") +
  ggtitle("Even, <=")

ggplot(filter(all_di, s0 >2), aes(x = simpson_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") +
  ggtitle("Even, <")

all_di %>%
  group_by(dat) %>%
  summarize(prop_even_low_ltet = mean(simpson_percentile < 5),
            prop_even_low_lt = mean(simpson_percentile_excl < 5),
            n_even_sites = dplyr::n())

```

**Generally**, we do not see a big difference between < and <= for the overall results. We see the biggest changes for FIA and MCDB:
- For FIA, using the more conservative option (< for skew and <= for even) reduces the % of extreme observations from 7 to 5 for skew and from 11 to 8 for even.
- For MCDB, the reductions are from 16 to 14 for skew and from 39 to 27 for even.

These datasets have the greatest representation of smallish sites. Which leads us to...

##### Results for small (FIA sized) communities

This is most likely to matter for small communities with small FS.

Here are the results when we try to tell whether FIA communities differ qualitatively from similarly-sized communities from other datasets...

###### Small sites

Note that, even for small sites, "other datasets" are generally larger than FIA....

```{r small, fig.dim = c(4,3)}

fia_max_s = max(filter(all_di, dat == "fia")$s0)
fia_max_n = max(filter(all_di, dat == "fia")$n0)

fia = filter(all_di, dat == "fia")

small_di <- all_di %>%
  filter(s0 <= fia_max_s,
         n0 <= fia_max_n) %>%
  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
         right_corner = FALSE)

for(i in 1:nrow(small_di)) {
  if(small_di$dat[i] != "fia") {
    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])

    max_n0_for_this_s0 = max(fia_match_s0$n0)

    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0

  }
}

small_di <- small_di %>%
  filter(!right_corner)

ggplot(small_di, aes(x = s0, y = n0, color = log_nparts)) +
  geom_point() +
  theme_bw() +
  scale_color_viridis_c(option = "plasma", end = .7) +
  facet_wrap(vars(fia_yn)) +
  theme(legend.position = "top")

ggplot(small_di, aes(log_nparts)) +
  geom_histogram(bins = 30) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y")

```

###### Skew for small sites
```{r skewness small, fig.dim = c(4, 3)}

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <=")

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <")

small_di %>%
  filter(s0 > 2) %>%
  group_by(fia_yn) %>%
  summarize(prop_skew_high_ltet = mean(skew_percentile > 95),
            prop_skew_high_lt = mean(skew_percentile_excl > 95),
            n_skew_sites = dplyr::n())

```

###### Evenness
```{r evenness result small, fig.dim = c(4, 3)}

ggplot(filter(small_di), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <=")

ggplot(filter(small_di), aes(x = simpson_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <")

small_di %>%
  group_by(fia_yn) %>%
  summarize(prop_even_low_ltet = mean(simpson_percentile < 5),
            prop_even_low_lt = mean(simpson_percentile_excl < 5),
            n_even_sites = dplyr::n())

```

For these comparisons, 
- For skewness, the effect is weak for both FIA and not-FIA (5% and 8% in the extremes, respectively)
- For evenness, the effect is much stronger for not-FIA (8 vs 15%)
- < vs <= matters quite a bit
    - Many of these sites can be quite small. Since we flagged a concern about having fewer than, arbitrarily, 100 elements, let's remove those:

###### Skew for small sites, removing very small
```{r skewness small no tiny, fig.dim = c(4, 3)}

small_di <- small_di %>%
  filter(nparts > 100)

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <=")

ggplot(filter(small_di, s0 >2), aes(x = skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Skew, <")

small_di %>%
  filter(s0 > 2) %>%
  group_by(fia_yn) %>%
  summarize(prop_skew_high_ltet = mean(skew_percentile > 95),
            prop_skew_high_lt = mean(skew_percentile_excl > 95),
            n_skew_sites = dplyr::n())

```

###### Evenness
```{r evenness result small no tiny, fig.dim = c(4, 3)}

ggplot(filter(small_di), aes(x = simpson_percentile)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <=")

ggplot(filter(small_di), aes(x = simpson_percentile_excl)) +
  geom_histogram(bins = 100) +
  theme_bw() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("Even, <")

small_di %>%
  group_by(fia_yn) %>%
  summarize(prop_even_low_ltet = mean(simpson_percentile < 5),
            prop_even_low_lt = mean(simpson_percentile_excl < 5),
            n_even_sites = dplyr::n())

```

Removing sites with fewer than 100 elements in the feasible set

- *eliminates the difference between <= and <*
- We see a difference between FIA and other datasets 
    - For skew, 6 vs 12% in the extremes
    - For even, 10 vs 25% in the extremes

I am skeptical of these comparisons. It may be that FIA is behaving qualitatively differently, but it may also be that, because the other datasets are less concentrated at *very small* FS, the effect of FS size still drives the difference even when we filter like this. On the strength of this filtering I'm not confident arguing *either* that FIA is qualitatively different, independent of size, or that these subsets are behaving the same.

I think a stronger comparison would be to break into size classes based on the number of parts.

### 2020-12-19 analysis/reports/accessory/rov_metric.Rmd

--- 2020-08-11 analysis/reports/rov_metric.Rmd
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs$skew_2p5[1], example_fs$skew_97p5[1]), color = "red") +
-  ggtitle(paste0("Skew 95% interval: ", round(example_fs$skew_95_ratio_2t[1], 2)))
+  geom_vline(xintercept = c(example_fs$skew_min[1], example_fs$skew_95[1]), color = "red") +
+  ggtitle(paste0("Skew 95% interval: ", round(example_fs$skew_95_ratio_1t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs$simpson_97p5[1], example_fs$simpson_2p5[1]), color = "red") +
-  ggtitle(paste0("Simpson 95% interval: ", round(example_fs$simpson_95_ratio_2t[1], 2)))
+  geom_vline(xintercept = c(example_fs$simpson_max[1], example_fs$simpson_5[1]), color = "red") +
+  ggtitle(paste0("Simpson 95% interval: ", round(example_fs$simpson_95_ratio_1t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs2$skew_2p5[1], example_fs2$skew_97p5[1]), color = "red") +
-  ggtitle(paste0("Skew 95% interval: ", round(example_fs2$skew_95_ratio_2t[1], 2)))
+  geom_vline(xintercept = c(example_fs2$skew_min[1], example_fs2$skew_95[1]), color = "red") +
+  ggtitle(paste0("Skew 95% interval: ", round(example_fs2$skew_95_ratio_1t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs2$simpson_97p5[1], example_fs2$simpson_2p5[1]), color = "red") +
-  ggtitle(paste0("Simpson 95% interval: ", round(example_fs2$simpson_95_ratio_2t[1], 2)))
+  geom_vline(xintercept = c(example_fs2$simpson_max[1], example_fs2$simpson_5[1]), color = "red") +
+  ggtitle(paste0("Simpson 95% interval: ", round(example_fs2$simpson_95_ratio_1t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs3$skew_2p5[1], example_fs3$skew_97p5[1]), color = "red") +
-  ggtitle(paste0("Skew 95% interval: ", round(example_fs3$skew_95_ratio_2t[1], 2)))
+  geom_vline(xintercept = c(example_fs3$skew_min[1], example_fs3$skew_95[1]), color = "red") +
+  ggtitle(paste0("Skew 95% interval: ", round(example_fs3$skew_95_ratio_1t[1], 2)))
 
@@
   theme_bw() +
-  geom_vline(xintercept = c(example_fs3$simpson_97p5[1], example_fs3$simpson_2p5[1]), color = "red") +
-  ggtitle(paste0("Simpson 95% interval: ", round(example_fs3$simpson_95_ratio_2t[1], 2)))
+  geom_vline(xintercept = c(example_fs3$simpson_max[1], example_fs3$simpson_5[1]), color = "red") +
+  ggtitle(paste0("Simpson 95% interval: ", round(example_fs3$simpson_95_ratio_1t[1], 2)))
 
@@
     theme_bw() +
-    geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") +
-    ggtitle(paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs3$skew_95_ratio_2t[1]), 2))),
+    geom_vline(xintercept = c(example_fs3$skew_95[1], example_fs3$skew_min[1]), color = "red") +
+    ggtitle(paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs3$skew_95_ratio_1t[1]), 2))),
 
@@
     theme_bw() +
-    geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") +
-    ggtitle(paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs2$skew_95_ratio_2t[1]), 2))),
+    geom_vline(xintercept = c(example_fs2$skew_95[1], example_fs2$skew_min[1]), color = "red") +
+    ggtitle(paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs2$skew_95_ratio_1t[1]), 2))),
 
@@
     theme_bw() +
-    geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") +
-    ggtitle(paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs$skew_95_ratio_2t[1]), 2)))
+    geom_vline(xintercept = c(example_fs$skew_95[1], example_fs$skew_min[1]), color = "red") +
+    ggtitle(paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1])), subtitle =  paste0("Skew 95% ratio: ", round((example_fs$skew_95_ratio_1t[1]), 2)))
 
@@
 
-ggplot(filter(net_summary, s0 > 2, skew_unique > 1), aes(log(s0), log(n0), color = skew_95_ratio_2t)) +
+ggplot(filter(net_summary, s0 > 2, skew_unique > 1), aes(log(s0), log(n0), color = skew_95_ratio_1t)) +
   geom_point() +
@@
 
-ggplot(filter(net_summary,simpson_unique > 1), aes(log(s0), log(n0), color = simpson_95_ratio_2t)) +
+ggplot(filter(net_summary,simpson_unique > 1), aes(log(s0), log(n0), color = simpson_95_ratio_1t)) +
   geom_point() +
@@
 
-ggplot(filter(net_summary, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_2t, color = log(n0/s0))) +
+ggplot(filter(net_summary, s0 > 2), aes(x = log_nparts, y = skew_95_ratio_1t, color = log(n0/s0))) +
   geom_point() +
@@
 
-ggplot(net_summary, aes(x = log_nparts, y = simpson_95_ratio_2t, color = log(n0/s0))) +
+ggplot(net_summary, aes(x = log_nparts, y = simpson_95_ratio_1t, color = log(n0/s0))) +
   geom_point() +

### 2020-12-19 analysis/reports/appendix1_filtering.Rmd

@@
 We filter datasets in two stages.
-First, **prior to trying to sample from the feasible set**, we remove communities that have a combined S and N too high for us to sample the feasible set.
-We also create a sub-sample of the FIA dataset, because it has so many communities (~100,000) and so many of them are extremely small (~90,000 with fewer than 10 species).
-Sampling all 100,000 communities overwhelms our computational pipeline, so we create a subsample of 20,000 communities comprising all communities with more than 10 species (approx.
-10,000) and 10,000 randomly selected communities with 3-10 species.
-Second, **after sampling but before we aggregate results across communities**, we remove communities that are problematic for a number of more nuanced reasons.
-This includes having only 1 possible SAD (S = 1, N = S, or N = S + 1).
-We also filter to communities whose sampled feasible sets yield more than 20 unique values for skewness/evenness.
-We do this because, if there are fewer than 20 unique values in the comparison vector, it's impossible to be in the 5th or 95th percentile.
-Finally, we remove communities with only 2 species from analyses for skewness, because  `e1071::skewness()` always = 0 if S = 2.
+First, we filter **prior to trying to sample from the feasible set**, in order to remove communities that have a combined S and N too high for us to sample the feasible set, and to reduce the  Forest Inventory and Analysis dataset to a manageable size.
+Second,we filter **after sampling the feasible but before we aggregate results across communities**, to remove cases where mathematical constraints result in uninformative results.
+Below we elaborate on the logic and methods for these filtering processes, including code to allow others to see precisely what was implemented.
 
-## Pre-sampling
-
-The only filtering at this stage is removing large communities and subsampling the FIA database.
-Communities with very large numbers of individuals become computationally intractable.
-We set the upper limit at 40720, because this is the largest community we were able to sample given the available resources.
+## Pre-feasible set sampling
+While our algorithm for sampling the feasible set improved our ability to assess the shape of the feasible set for larger communities, there were still computational limits on what we could do.
+We filtered out all communities with more than 40720 individuals, because this is the largest community we were able to sample given the available resources.
 This upper limit results in the removal of a total of 4 communities, all of them from the Miscellaneous Abundance Database.
 
-The `download_data` function downloads raw data files from https://github.com/weecology/sad-comparison/ (for BBS, Gentry, Mammal Community  Database, and FIA) and figshare http://figshare.com/files/3097079 (for the Miscellaneous Abundance Database).
+For computational reasons, we also created a sub-sample of the FIA dataset, because sampling the feasible set for all 103,343 FIA communities overwhelms our computational pipeline.
+Because the FIA has so many extremely small communities (92,988 with fewer than 10 species), we decided to randomly select a sample of the small communities for analysis.
+Thus our FIA dataset consisted of  ~20 ,000 communities comprising all communities with more than 10 species (10,355) plus 10,000 randomly selected communities with 3-10 species.
+
+Code for downloading the data (and all other analyses) used for this project can be found at www.github.com/diazrenata/scadsanalysis.
+The data download functions are at https://github.com/diazrenata/scadsanalysis/blob/master/R/download_data.R.
+
+### Overview
+
+The `download_data` function downloads raw data files from https://github.com/weecology/sad-comparison/ (for BBS, Gentry, Mammal Community  Database, and FIA; data from Baldridge (2016) and also used in White, Thibault, and Xiao (2012)) and figshare http://figshare.com/files/3097079 (for the Miscellaneous Abundance Database; Baldridge (2015)).
 These raw files are stored in `working-data\abund_data` and are not edited.
 
-To filter, we can re-load the raw data files and go through the filtering process step by step.
-In the analysis this is accomplished by running dataset-specific filtering scripts and saving new .csvs, which are then loaded using `load_dataset`.
-We can manually load the datasets and then compare them to what is returned from `load_dataset`.
+The Miscellaneous Abundance and FIA databases undergo additional filtering steps, implemented in the `filter_misc_abund` and `filter_fia_short` and `filter_fia_small` functions.
+These functions run automatically when the data are downloaded and save new files to `working-data\abund_data`.
 
-### Miscellaneous Abundance Database
+The `load_dataset` function loads either the filtered datasets (if specified, for Misc.
+Abund and FIA) or the raw data (for all others, or if specified for Misc.
+Abund and FIA), and adds additional columns and column types to prepare the data for the computational pipeline.
+The datasets as returned from `load_dataset` are exactly what goes into the analysis.
 
-- Misc. Abund includes datasets reported as relative abundance in addition to count data. We don't want any communities without counts, so we filter out records where abund = 0.
+In the following sections, we load the raw data files (as they were downloaded), perform the filtering process manually (if applicable), and compare the resulting data to the data that are used in the  analysis, i.e.
+the data that we get if we use `load_dataset`.
+
+### BBS (no filtering)
+
+For BBS, and all datasets that are not filtered, we can simply load the data from the file downloaded by `download_data`, add the columns and column formats that are added by `load_data`, and compare the result to the result of `load_data`:
+
+```{r}
+
+bbs_raw <- read.csv(here::here("working-data", "abund_data", "bbs_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)
+
+colnames(bbs_raw) <- c("site", "year", "species", "abund")
+
+bbs_raw <- bbs_raw %>%
+  mutate(site = as.character(site),
+         dat = "bbs",
+         singletons = F,
+         sim = -99,
+         source = "observed") %>%
+  group_by(site) %>%
+  arrange(abund) %>%
+  mutate(rank = row_number()) %>%
+  ungroup()
+
+bbs_loaded <- load_dataset("bbs")
+```
+
+Here we confirm that all values for `abund` and `site` match between the version we get from `load_dataset` and the version we just created from the raw data file:
+
+```{r}
+any(!(bbs_loaded$abund == bbs_raw$abund))
+any(!(bbs_loaded$site == bbs_raw$site))
+
+```
+
+Here we check to confirm that no communities have a total abundance exceeding our upper limit (40720, marked by the horizontal red line):
+
+```{r}
+
+bbs_statevars <- get_statevars(bbs_raw)
+
+ggplot(bbs_statevars, aes(s0, n0)) +
+  geom_point() +
+  theme_bw() +
+  geom_hline(yintercept = 40720, color = "red")
+
+```
+
+No communities in BBS have more than 40720 individuals, so all are initially included in the analysis.
+
+### Gentry (no filtering)
+
+For Gentry, as with BBS, we can simply load the data from the file downloaded by `download_data`, add the columns and column formats that are added by `load_data`, and compare the result to the result of `load_data`:
+
+```{r}
+
+gentry_raw <- read.csv(here::here("working-data", "abund_data", "gentry_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)
+
+colnames(gentry_raw) <- c("site", "year", "species", "abund")
+
+gentry_raw <- gentry_raw %>%
+  mutate(site = as.character(site),
+         dat = "gentry",
+         singletons = F,
+         sim = -99,
+         source = "observed") %>%
+  group_by(site) %>%
+  arrange(abund) %>%
+  mutate(rank = row_number()) %>%
+  ungroup()
+
+gentry_loaded <- load_dataset("gentry")
+```
+
+Here we confirm that all values for `abund` and `site` match between the version we get from `load_dataset` and the version we just created from the raw data file:
+
+```{r}
+any(!(gentry_loaded$abund == gentry_raw$abund))
+any(!(gentry_loaded$site == gentry_raw$site))
+
+```
+
+Here we check to confirm that no communities have a total abundance exceeding our upper limit (40720, marked by the horizontal red line):
+
+```{r}
+
+gentry_statevars <- get_statevars(gentry_raw)
+
+ggplot(gentry_statevars, aes(s0, n0)) +
+  geom_point() +
+  theme_bw() +
+  geom_hline(yintercept = 40720, color = "red")
+
+```
+
+No communities in Gentry have more than 40720 individuals, so all are initially included in the analysis.
+
+### Mammal Community Database (not filtered)
+
+For MCDB, as with BBS and Gentry, we can simply load the data from the file downloaded by `download_data`, add the columns and column formats that are added by `load_data`, and compare the result to the result of `load_data`:
+
+```{r}
+
+mcdb_raw <- read.csv(here::here("working-data", "abund_data", "mcdb_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)
+
+colnames(mcdb_raw) <- c("site", "year", "species", "abund")
+
+mcdb_raw <- mcdb_raw %>%
+  mutate(site = as.character(site),
+         dat = "mcdb",
+         singletons = F,
+         sim = -99,
+         source = "observed") %>%
+  group_by(site) %>%
+  arrange(abund) %>%
+  mutate(rank = row_number()) %>%
+  ungroup()
+
+mcdb_loaded <- load_dataset("mcdb")
+```
+
+Here we confirm that all values for `abund` and `site` match between the version we get from `load_dataset` and the version we just created from the raw data file:
+
+```{r}
+any(!(mcdb_loaded$abund == mcdb_raw$abund))
+any(!(mcdb_loaded$site == mcdb_raw$site))
+
+```
+
+Here we check to confirm that no communities have a total abundance exceeding our upper limit (40720, marked by the horizontal red line):
+
+```{r}
+
+mcdb_statevars <- get_statevars(mcdb_raw)
+
+ggplot(mcdb_statevars, aes(s0, n0)) +
+  geom_point() +
+  theme_bw() +
+  geom_hline(yintercept = 40720, color = "red")
+
+```
+
+No communities in the MCDB have more than 40720 individuals, so all are initially included in the analysis.
+
+### Miscellaneous Abundance Database (filtered)
+
+For the Miscellaneous Abundance Database, we can proceed similarly to with the non-filtered datasets.
+We load the data from the file downloaded by `download_data`, add the columns and column formats that are added by `load_data`, and compare the result to the result of `load_data`.
+
+However, Misc.
+Abund includes datasets reported as relative abundance in addition to count data.
+Relative abundance data is not appropriate for this analysis, so we filter out records where abund = 0 to restrict our analysis to communities with count data.
+Also, because we will eventually filter out some highly abundant communities, at this stage we make sure to load the **unfiltered** version using `load_dataset`.
 
@@
 
+Here we confirm that, if we load the unfiltered dataset using `load_dataset`, the records match the version we have created manually from the raw file:
+
 ```{r}
@@
 
-Check community sizes:
+Here we check whether any communities have more than 40720 individuals (horizontal red line):
 
@@
 
-Misc abund has `r sum(misc_abund_statevars$n0 > 40720)` communities that get removed. They are all removed because they have high numbers of individuals.
-
-The filtered database is saved as a .csv and can be loaded with `load_dataset`. We can check that it matches the filtering we have done here:
+Misc abund has `r sum(misc_abund_statevars$n0 > 40720)` communities with more than 40720 individuals, and these communities are removed:
 
@@
 
+```
+
+We can access the **filtered** version of the dataset, as used in the analysis, using `load_dataset("misc_abund_short")`.
+We then check to confirm that the filtered version of the dataset that we get from `load_dataset` matches the version that we filtered manually:
+
+```{r}
+
 misc_abund_short_loaded <- load_dataset("misc_abund_short")
@@
 
-### FIA
+### FIA (filtered)
 
-- Load raw FIA data
-- Add columns to match what we will get from `load_dataset`
-- Load from `load_dataset`
+Again, we can begin similarly to with the non-filtered datasets.
+We load the data from the file downloaded by `download_data`, add the columns and column formats that are added by `load_data`, and compare the result to the result of `load_data`.
+Because we will remove some communities from FIA, we make sure to load the **unfiltered** version using `load_data`.
 
@@
 fia_statevars <- get_statevars(fia_raw)
-
 ggplot(fia_statevars, aes(s0, n0)) +
@@
   theme_bw() +
-  geom_vline(xintercept = c(1.5, 2.5, 9.5), color = "red")
+  geom_hline(yintercept = 40720, color = "red")
 
@@
 
-FIA has no extremely large datasets; the largest number of individuals is `r max(fia_statevars$n0)`.
-However, it has `r nrow(fia_statevars)` communities, of which `r sum(fia_statevars$s0 < 10)` have fewer than 10 species.
+FIA has no communities with more than 40720 individuals.
+However, it presents additional issues.
+It  it has `r nrow(fia_statevars)` communities, of which `r sum(fia_statevars$s0 < 10)` have fewer than 10 species (vertical red line in the figure below)
+
+```{r}
+ggplot(fia_statevars, aes(s0, n0)) +
+  geom_point() +
+  theme_bw() +
+  geom_vline(xintercept = c(9.5), color = "red")
+
+```
+
 This many communities overwhelms our computational pipeline.
@@
 We re-combine them as "FIA" for aggregate analyses.
+This results in a toal of 20,355 FIA communities in the analysis.
 
@@
 
-The "short" and "small" datasets are saved as .csvs and can be loaded using `load_dataset`:
+The "short" and "small" datasets are saved as .csvs and can be loaded using `load_dataset` as follows. These are the versions that are used in the analysis.
 
@@
 
+fia_short_loaded <- load_dataset("fia_short")
+```
+
+Here we confirm that versions of "fia_short" and "fia_small" that we created manually match the ones we obtain from `load_dataset`:
+
+```{r}
+
 any(!(fia_small_loaded$abund == fia_small$abund))
 any(!(fia_small_loaded$site == fia_small$site))
-
-fia_short_loaded <- load_dataset("fia_short")
 
@@
 
-### BBS
-
-- Load raw BBS data
-- Add columns to match what we will get from `load_dataset`
-- Load from `load_dataset`
-
-```{r}
-
-bbs_raw <- read.csv(here::here("working-data", "abund_data", "bbs_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)
-
-colnames(bbs_raw) <- c("site", "year", "species", "abund")
-
-bbs_raw <- bbs_raw %>%
-  mutate(site = as.character(site),
-         dat = "bbs",
-         singletons = F,
-         sim = -99,
-         source = "observed") %>%
-  group_by(site) %>%
-  arrange(abund) %>%
-  mutate(rank = row_number()) %>%
-  ungroup()
-
-bbs_loaded <- load_dataset("bbs")
-```
-
-Compare loaded to raw:
-
-```{r}
-any(!(bbs_loaded$abund == bbs_raw$abund))
-any(!(bbs_loaded$site == bbs_raw$site))
-
-```
-
-Check community sizes:
-
-```{r}
-
-bbs_statevars <- get_statevars(bbs_raw)
-
-ggplot(bbs_statevars, aes(s0, n0)) +
-  geom_point() +
-  theme_bw() +
-  geom_hline(yintercept = 40720, color = "red")
-
-```
-
-No communities in BBS have more than 40720 individuals, so all are used at this stage.
-
-### Gentry
-
-- Load raw Gentry data
-- Add columns to match what we will get from `load_dataset`
-- Load from `load_dataset`
-
-```{r}
-
-gentry_raw <- read.csv(here::here("working-data", "abund_data", "gentry_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)
-
-colnames(gentry_raw) <- c("site", "year", "species", "abund")
-
-gentry_raw <- gentry_raw %>%
-  mutate(site = as.character(site),
-         dat = "gentry",
-         singletons = F,
-         sim = -99,
-         source = "observed") %>%
-  group_by(site) %>%
-  arrange(abund) %>%
-  mutate(rank = row_number()) %>%
-  ungroup()
-
-gentry_loaded <- load_dataset("gentry")
-```
-
-Compare loaded to raw:
-
-```{r}
-any(!(gentry_loaded$abund == gentry_raw$abund))
-any(!(gentry_loaded$site == gentry_raw$site))
-
-```
-
-Check community sizes:
-
-```{r}
-
-gentry_statevars <- get_statevars(gentry_raw)
-
-ggplot(gentry_statevars, aes(s0, n0)) +
-  geom_point() +
-  theme_bw() +
-  geom_hline(yintercept = 40720, color = "red")
-
-```
-
-No communities in Gentry have more than 40720 individuals, so all are used at this stage.
-
-### Mammal Community Database
-
-- Load raw MCDB data
-- Add columns to match what we will get from `load_dataset`
-- Load from `load_dataset`
-
-```{r}
-
-mcdb_raw <- read.csv(here::here("working-data", "abund_data", "mcdb_spab.csv"),  stringsAsFactors = F, header = F, skip = 2)
-
-colnames(mcdb_raw) <- c("site", "year", "species", "abund")
-
-mcdb_raw <- mcdb_raw %>%
-  mutate(site = as.character(site),
-         dat = "mcdb",
-         singletons = F,
-         sim = -99,
-         source = "observed") %>%
-  group_by(site) %>%
-  arrange(abund) %>%
-  mutate(rank = row_number()) %>%
-  ungroup()
-
-mcdb_loaded <- load_dataset("mcdb")
-```
-
-Compare loaded to raw:
-
-```{r}
-any(!(mcdb_loaded$abund == mcdb_raw$abund))
-any(!(mcdb_loaded$site == mcdb_raw$site))
-
-```
-
-Check community sizes:
-
-```{r}
-
-mcdb_statevars <- get_statevars(mcdb_raw)
-
-ggplot(mcdb_statevars, aes(s0, n0)) +
-  geom_point() +
-  theme_bw() +
-  geom_hline(yintercept = 40720, color = "red")
-
-```
-
-No high N communities; so all are included at this stage.
-
 ## Post-sampling
 
-We will remove additional communities for more substantive reasons.
-First we can load `all_di` ("all diversity indices"), which is the combined results across all the communities in all the datasets.
+Some communities fall into mathematically special spaces where basic constraints prevent informative results. We removed all communities that fell into any of the below cases:
+
+1) When communities have only 1 mathematically possible SAD (S = 1, N = S, or N = S + 1).
+2) When the sampled feasible sets yield fewer than 20 unique values for skewness/evenness.
+If there are fewer than 20 unique values in the comparison vector, it is impossible to be in the 5th or 95th percentile.
+3) When a community consists of only 2 species, we excluded it from analyses using skewness, because e1071::skewness() always evaluates to 0 if S = 2.
+
+Below is the procedure for performing this filtering (after sampling the feasible set).
+First, we load our results from `all_di.csv`.
+This file contains the results of comparing the skewness and evenness for **observed** SADs to the distributions of skewness and evenness obtained from their sampled feasible sets; "all_di" stands for "all diversity indices".
 Every community that was included for sampling is included in all_di.
@@
 
+```
+
+```{r}
 all_di <- all_di %>%
@@
 
+```
+
+Here we confirm that we have the same number of communities in `all_di` as we have in our set of communities included for sampling.
+
+```{r}
 nrow(all_di) == nrow(all_statevars)
@@
 
-We remove communities with only one possible SAD (N = S, N = S + 1, or S = 1).
+Here we remove communities for the first case, only one possible SAD (N = S, N = S + 1, or S = 1).
 
@@
 
-Finally, we will restrict aggregate analyses to sites whose feasible sets have more than 20 unique values for whichever shape metric we're interested in, **and** we will restrict analyses with skewness to sites with >2 species.
-This results in these final totals:
+Finally, we filter for cases 2 and 3.
+That is, for aggregate analyses, we will restrict our analyses to sites whose feasible sets have more than 20 unique values for skewness or evenness (whichever metric we are focused on).
+For analyses with skewness, we will also remove sites with only 2 species.
+This results in these final total numbers of communities included for skewness and evenness.
+
+For skewness:
+
+```{r}
+
+all_di_filtered %>%
+  filter(skew_unique > 20, s0 > 2) %>%
+  group_by(dat) %>%
+  summarize(sites_for_skewness = dplyr::n()) %>%
+  mutate(total_sites_for_skewness = sum(sites_for_skewness))
+
+```
+
+For evenness:
 
@@
 
-all_di_filtered %>%
-  filter(skew_unique > 20, s0 > 2) %>%
-  group_by(dat) %>%
-  summarize(sites_for_skewness = dplyr::n()) %>%
-  mutate(total_sites_for_skewness = sum(sites_for_skewness))
+```
 
-```
+## References
+
+Baldridge, E. (2015). Miscellaneous Abundance Database. figshare. Available at:  MiscAbundanceDB_main. https://doi.org/10.6084/m9.figshare.95843.v4
+
+Baldridge, E., Harris, D.J., Xiao, X.
+& White, E.P.
+(2016).
+Data from An extensive comparison of species-abundance distribution models.
+Zenodo.
+Available at: https://zenodo.org/record/166725.
+Accessed from https://github.com/weecology/sad-comparison.
+
+Meyer, D., Dimitriadou, E., Hornik, K., Weingessel, A. & Leisch, F. (2019). e1071: Misc Functions of the Department of Statistics, Probability Theory Group (Formerly: E1071), TU Wien.
+
+White, E.P., Thibault, K.M. & Xiao, X. (2012). Characterizing species abundance distributions across taxa and ecosystems using a simple maximum entropy model. Ecology, 93, 1772–1778.

### 2021-01-04 analysis/reports/figure_s3.Rmd
Hao's figure comments

@@
 
-s3_fig1 <- ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
+s3_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
   geom_point(alpha = .1) +
@@
   ggtitle("Communities by S and N") +
-  xlab("Log species richness (S)") +
-  ylab("Log total abundance (N)")
+  xlab("Species richness (S); note log scale") +
+  ylab("Total abundance (N); note log scale") +
+  scale_x_log10() +
+  scale_y_log10()
 

### 2021-01-04 analysis/reports/manuscript_main.Rmd
fig edits

@@
 
-  ggplot(example_fs3, aes(skew, ..ndensity..)) +
-    geom_density() +
+  ggplot(example_fs3, aes(skew)) +
+  #  geom_density() +
     geom_histogram(bins = 50) +
@@
 
-  ggplot(example_fs2, aes(skew, ..ndensity..)) +
-    geom_density() +
+  ggplot(example_fs2, aes(skew)) +
+  #  geom_density() +
     geom_histogram(bins = 50) +
@@
     ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) +
-    theme(legend.position = "right"),
+    theme(legend.position = "right") +
+    ylim(0, 5000) +
+    theme(axis.text.y = element_text(size = 6, angle = 60)),
 
-  ggplot(example_fs, aes(skew, ..ndensity..)) +
-    geom_density() +
+  ggplot(example_fs, aes(skew)) +
+   # geom_density() +
     geom_histogram(bins = 50) +

### 2021-01-14 analysis/reports/figure_s4.Rmd
add HY figure and text edits. add algo from ha0ye/feasiblesads, rerendered to match formatting. renumber supplement files, note that they are NOT CORRECTLY NUMBERED in the reports directory but ARE CORRECT in manuscript/Supp

--- 2020-12-18 analysis/reports/figure_s3.Rmd
@@
 
-# Figure S3
+# Figure S4
 
@@
 
-s3_fig1 <- ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
+s4_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
   geom_point(alpha = .1) +
@@
   ggtitle("Communities by S and N") +
-  xlab("Log species richness (S)") +
-  ylab("Log total abundance (N)")
+  xlab("Species richness (S); note log scale") +
+  ylab("Total abundance (N); note log scale") +
+  scale_x_log10() +
+  scale_y_log10()
 
-plot(s3_fig1)
+plot(s4_fig1)
 # ggplot(all_di, aes(x = log_s0, y = log_n0, color = Dataset)) +
@@
 
-pdf("figure_s3.pdf")
-plot(s3_fig1)
+pdf("figure_s4.pdf")
+plot(s4_fig1)
 dev.off()

### 2021-01-14 analysis/reports/manuscript_main.Rmd
add HY figure and text edits. add algo from ha0ye/feasiblesads, rerendered to match formatting. renumber supplement files, note that they are NOT CORRECTLY NUMBERED in the reports directory but ARE CORRECT in manuscript/Supp

--- 2020-12-17 analysis/reports/manuscript_main.Rmd
@@
     ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) +
-    theme(legend.position = "right"),
+    theme(legend.position = "right") +
+    xlab("Rank") +
+    ylab("Abundance"),
 
-  ggplot(example_fs3, aes(skew, ..ndensity..)) +
-    geom_density() +
+  ggplot(example_fs3, aes(skew)) +
+  #  geom_density() +
     geom_histogram(bins = 50) +
@@
     geom_vline(xintercept = c(example_fs3$skew_95[1], example_fs3$skew_min[1]), color = "red") +
-    ggtitle("", subtitle = paste0("Breadth index (skewness): ", round((example_fs3$skew_95_ratio_1t[1]), 2))),
+    ggtitle("", subtitle = paste0("Breadth index: ", round((example_fs3$skew_95_ratio_1t[1]), 2))) +
+    xlab("Skewness") +
+    ylab("Count"),
 
@@
     ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) +
-    theme(legend.position = "right"),
+    theme(legend.position = "right")+
+    xlab("Rank") +
+    ylab("Abundance"),
 
-  ggplot(example_fs2, aes(skew, ..ndensity..)) +
-    geom_density() +
+  ggplot(example_fs2, aes(skew)) +
+  #  geom_density() +
     geom_histogram(bins = 50) +
@@
     geom_vline(xintercept = c(example_fs2$skew_95[1], example_fs2$skew_min[1]), color = "red") +
-    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs2$skew_95_ratio_1t[1]), 2))),
+    ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs2$skew_95_ratio_1t[1]), 2)))+
+    xlab("Skewness") +
+    ylab("Count"),
 
@@
     ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) +
-    theme(legend.position = "right"),
+    theme(legend.position = "right") +
+    ylim(0, 5000) + # Remove a very few very very uneven SADs that make the scale too big to be interpretable
+    theme(axis.text.y = element_text(size = 6, angle = 60))+
+    xlab("Rank") +
+    ylab("Abundance"),
 
-  ggplot(example_fs, aes(skew, ..ndensity..)) +
-    geom_density() +
+  ggplot(example_fs, aes(skew)) +
+   # geom_density() +
     geom_histogram(bins = 50) +
@@
     geom_vline(xintercept = c(example_fs$skew_95[1], example_fs$skew_min[1]), color = "red") +
-    ggtitle("", subtitle =  paste0("Breadth index (skewness): ", round((example_fs$skew_95_ratio_1t[1]), 2)))
+    ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs$skew_95_ratio_1t[1]), 2)))+
+    xlab("Skewness") +
+    ylab("Count")
 
@@
     theme_bw() +
-    facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Skewness") +
-    xlab("Percentile rank of observed value relative to feasible set") +
-    ylab("Number of communities"),
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") +
+    xlab("") +
+    ylab(""),# +
+  #  xlab("Percentile rank of observed value relative to feasible set") +
+    #ylab("Number of communities") ,
 
@@
     theme_bw() +
-    facet_wrap(vars(Dataset), scales = "free_y") + ggtitle("Evenness") +
-    xlab("Percentile rank of observed value relative to feasible set") +
-    ylab("Number of communities")
-))
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
+    xlab("") +
+    ylab("")#+
+    #xlab("Percentile rank of observed value relative to feasible set") +
+  #  ylab("Number of communities")
+), ncol = 2,
+left = "Number of communities",
+bottom = "Percentile rank of observed value relative to feasible set")
 
@@
     theme_bw() +
-    facet_wrap(vars(Dataset), scales = "free_y") +
-    xlab("Breadth index (ranges 0-1, with 1 being very broad)") +
-    ylab("Number of communities") +
-    ggtitle("Skewness"),
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Skewness") +
+    xlim(0, 1),
 
@@
     theme_bw() +
-    facet_wrap(vars(Dataset), scales = "free_y") +
-    xlab("Breadth index (ranges 0-1, with 1 being very broad)") +
-    ylab("Number of communities") +
-    ggtitle("Evenness")
-))
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Evenness") +
+    xlim(0, 1)
+), ncol = 2,
+left = "Number of communities", 
+bottom = "Breadth index (ranges 0-1, with 1 being very broad)")
 
@@
 
+simpson_ks <- filter(sub_di, simpson_unique > 20) %>%
+  select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>% 
+  group_by(Dataset, s0, n0) %>%
+  mutate(pairing = dplyr::row_number()) %>%
+  ungroup() %>%
+  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(simpson_95_ratio_1t, simpson_percentile))
+
+simpson_breadth <- ks.test(simpson_ks$simpson_95_ratio_1t_FIA, simpson_ks$`simpson_95_ratio_1t_Other datasets`)
+
+simpson_percent <- ks.test(simpson_ks$simpson_percentile_FIA, simpson_ks$`simpson_percentile_Other datasets`)
+simpson_breadth
+simpson_percent
+
+skewness_ks <- filter(sub_di, skew_unique > 20) %>%
+  select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>% 
+  group_by(Dataset, s0, n0) %>%
+  mutate(pairing = dplyr::row_number()) %>%
+  ungroup() %>%
+  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(skew_95_ratio_1t, skew_percentile))
+
+skewness_breadth <- ks.test(skewness_ks$skew_95_ratio_1t_FIA, skewness_ks$`skew_95_ratio_1t_Other datasets`)
+
+skewness_percent <- ks.test(skewness_ks$skew_percentile_FIA, skewness_ks$`skew_percentile_Other datasets`)
+skewness_breadth
+skewness_percent
+
 fig_4 <- gridExtra::grid.arrange(grobs = list(

### 2021-01-15 analysis/reports/manuscript_main.Rmd
edits before hy and skme sign off

@@
 ```{r first hists, fig.dim = c(7,7)}
+library(grid)
 fig_2 <- gridExtra::grid.arrange(grobs = list(
@@
 ), ncol = 2,
-left = "Number of communities",
-bottom = "Percentile rank of observed value relative to feasible set")
-
-plot(fig_2)
+left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
 
@@
 ```{r}
-pdf("figure_1.pdf", title = "Figure 1")
+pdf("figure_1.pdf", title = "Figure 1", bg = "white")
 plot(fig_1)
@@
 
-pdf("figure_2.pdf", title = "Figure 2")
- plot(fig_2)
+pdf("figure_2.pdf", title = "Figure 2", bg = "white")
+ gridExtra::grid.arrange(grobs = list(
+
+  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
+    geom_histogram(bins = 100) +
+    geom_vline(xintercept = 95, color = "red") +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") +
+    xlab("") +
+    ylab(""),# +
+  #  xlab("Percentile rank of observed value relative to feasible set") +
+    #ylab("Number of communities") ,
+
+  ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
+    geom_histogram(bins = 100) +
+    geom_vline(xintercept = 5, color = "red") +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
+    xlab("") +
+    ylab("")#+
+    #xlab("Percentile rank of observed value relative to feasible set") +
+  #  ylab("Number of communities")
+), ncol = 2,
+left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
  dev.off()
 
-pdf("figure_3.pdf", title = "Figure 3")
-plot(fig_3)
+pdf("figure_3.pdf", title = "Figure 3", bg = "white")
+gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
+    geom_histogram() +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Skewness") +
+    xlim(0, 1),
+
+  ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
+    geom_histogram() +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Evenness") +
+    xlim(0, 1)
+), ncol = 2,
+left = "Number of communities", 
+bottom = "Breadth index (ranges 0-1, with 1 being very broad)")
+
 dev.off()
 
-pdf("figure_4.pdf", title = "Figure 4")
+pdf("figure_4.pdf", title = "Figure 4", bg = "white")
  plot(fig_4)

### 2021-01-21 analysis/reports/manuscript_main.Rmd
last figure edits

--- 2021-01-14 analysis/reports/manuscript_main.Rmd
@@
 library(ggplot2)
+library(grid)
 
@@
 
-fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2)
+fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white")))
 
@@
 ), ncol = 2,
-left = "Number of communities",
-bottom = "Percentile rank of observed value relative to feasible set")
-
-plot(fig_2)
+top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
 
@@
 ), ncol = 2,
+top = textGrob("Figure 3", gp = gpar(fill = "white")),
 left = "Number of communities", 
@@
     ylab("")+
-    ggtitle("", subtitle = "Evenness")), ncol = 2)
+    ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white")))
 
@@
 ```{r}
-pdf("figure_1.pdf", title = "Figure 1")
-plot(fig_1)
+pdf("figure_1.pdf", title = "Figure 1", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white")))
 dev.off()
 
-pdf("figure_2.pdf", title = "Figure 2")
- plot(fig_2)
+pdf("figure_2.pdf", title = "Figure 2", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+ gridExtra::grid.arrange(grobs = list(
+
+  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
+    geom_histogram(bins = 100) +
+    geom_vline(xintercept = 95, color = "red") +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") +
+    xlab("") +
+    ylab(""),# +
+  #  xlab("Percentile rank of observed value relative to feasible set") +
+    #ylab("Number of communities") ,
+
+  ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
+    geom_histogram(bins = 100) +
+    geom_vline(xintercept = 5, color = "red") +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
+    xlab("") +
+    ylab("")#+
+    #xlab("Percentile rank of observed value relative to feasible set") +
+  #  ylab("Number of communities")
+), ncol = 2,
+top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
  dev.off()
 
-pdf("figure_3.pdf", title = "Figure 3")
-plot(fig_3)
+pdf("figure_3.pdf", title = "Figure 3", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
+    geom_histogram() +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Skewness") +
+    xlim(0, 1),
+
+  ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
+    geom_histogram() +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Evenness") +
+    xlim(0, 1)
+), ncol = 2,
+top = textGrob("Figure 3", gp = gpar(fill = "white")),
+left = "Number of communities", 
+bottom = "Breadth index (ranges 0-1, with 1 being very broad)")
+
 dev.off()
 
-pdf("figure_4.pdf", title = "Figure 4")
- plot(fig_4)
+pdf("figure_4.pdf", title = "Figure 4", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+ gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(sub_di, skew_unique > 20), aes(skew_95_ratio_1t)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Breadth index") +
+    ylab("Number of communities") +
+    ggtitle("Breadth index", subtitle = "Skewness"),
+
+  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_95_ratio_1t)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Breadth index") +
+    ylab("") +
+    ggtitle("", subtitle = "Evenness"),
+
+  ggplot(filter(sub_di, skew_unique > 20), aes(skew_percentile_excl)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Percentile rank") +
+    ylab("Number of communities") +
+    ggtitle("Percentile rank", subtitle = "Skewness"),
+
+  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_percentile)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Percentile rank") +
+    ylab("")+
+    ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white")))
 dev.off()

### 2021-02-13 analysis/rev_prototyping/prop_off.Rmd
modifications to metrics to add prop off actual and nsingletons and shannon

---
title: "Shannon diversity"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())
## Set up the cache and config
db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-mcdb.sqlite"))
cache <- storr::storr_dbi("datatable", "keystable", db)
cache$del(key = "lock", namespace = "session")

loadd(fs_1002_FALSE, cache = cache)

loadd(all_di_obs, cache = cache)

```
```{r}

ggplot(filter(fs_1002_FALSE, source == "observed"), aes(rank, abund)) +
  geom_line()

```

```

### 2021-02-13 analysis/rev_prototyping/shannon.Rmd
modifications to metrics to add prop off actual and nsingletons and shannon

---
title: "Shannon diversity"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))

```

```{r}

  ggplot(filter(all_di), aes(shannon_percentile)) +
    geom_histogram(bins = 100) +
    geom_vline(xintercept = 5, color = "red") +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Shannon's") +
    xlab("") +
    ylab("")

overall_shannon_results <- all_di %>%
  mutate(low_even = shannon_percentile < 5) %>%
  group_by(Dataset) %>%
  summarize(proportion_shannon_low = mean(low_even),
            nsites_even = dplyr::n())

overall_shannon_results

overall_shannon_results <- all_di %>%
  mutate(low_even = shannon_percentile < 5,
         high_even = shannon_percentile > 95) %>%
  group_by(Dataset) %>%
  summarize(proportion_shannon_low = mean(low_even),
            proportion_shannon_high = mean(high_even),
            nsites_even = dplyr::n())

overall_shannon_results
```

This is really interesting.

- Shannon's is consistently low for most of the datasets. As with skewness and evenness, FIA has the lowest % of extremes.
- However, Gentry is actually more pronouncedly too **high** - 30% of sites are above the 95th.

```{r}
all_di <- all_di %>%
  mutate(shannon_cat = ifelse(
    shannon_percentile < 5, "low", 
    ifelse(
      shannon_percentile > 95, "high", "int"
    )
  ))

ggplot(all_di, aes(s0, n0, color = shannon_cat)) +
  theme_bw()+
  scale_x_log10() +
  scale_y_log10() +
  scale_color_viridis_d(begin = .7) +
  geom_point(data = filter(all_di, is.na(shannon_cat)), aes(s0, n0), inherit.aes = F, alpha = .05, color = "grey") +
    geom_point(alpha = .5)

ggplot(all_di, aes(s0, n0, color = shannon_cat)) +
  theme_bw()+
  scale_x_log10() +
  scale_y_log10() +
  scale_color_viridis_d(begin = .7) +
  geom_point(data = filter(all_di, is.na(shannon_cat)), aes(s0, n0), inherit.aes = F, alpha = .1, color = "grey") +
    geom_point(alpha = .5)+
  facet_wrap(vars(Dataset))
```

The ones that come out as high are concentrated in the small region of FIA and the region of Gentry where N is closest to S. These Gentry plots are also responsible for similar behavior (not discussed in the main ms) in the other metrics.

That is, for these datasets where N/S is relatively small, the observed SADs are tending to be more even than the feasible set.

To look at the

- breadth index
- number of unique Shannon values

we need to re-load the samples from the feasible set. These are best done as modifications to add_all_di.

### 2021-02-13 R/metrics.R

@@ -20,11 +20,16 @@ add_dis <- function(fs_samples_df) {
 
   groupvars <- colnames(fs_samples_df)[ which(!(colnames(fs_samples_df) %in% c("abund", "rank")))]
 
+  actual <- filter(fs_samples_df, sim == -99)
+
+
   sim_dis <- fs_samples_df %>%
     dplyr::group_by_at(.vars = groupvars) %>%
     dplyr::summarize(skew = e1071::skewness(abund),
                      shannon = vegan::diversity(abund, index = "shannon", base = exp(1)),
-                     simpson = vegan::diversity(abund, index = "simpson")) %>%
+                     simpson = vegan::diversity(abund, index = "simpson"),
+                     nsingletons = sum(abund == 1),
+                    prop_off_actual = proportion_off(t(cbind(actual$abund, abund)))) %>%
     dplyr::ungroup()
 
   sim_percentiles <- sim_dis %>%
@@ -39,7 +44,13 @@ add_dis <- function(fs_samples_df) {
                   shannon_percentile = get_percentile(shannon, a_vector = sim_percentiles$shannon),
                   simpson_percentile = get_percentile(simpson, a_vector = sim_percentiles$simpson),
                   skew_percentile_excl = get_percentile(skew, a_vector = sim_percentiles$skew, incl =F),
-                  simpson_percentile_excl = get_percentile(simpson, a_vector = sim_percentiles$simpson, incl = F))
+                  simpson_percentile_excl = get_percentile(simpson, a_vector = sim_percentiles$simpson, incl = F),
+                  nsingletons_percentile = get_percentile(nsingletons, a_vector = sim_percentiles$nsingletons),
+                  nsingletons_percentile_excl = get_percentile(nsingletons,
+                                                               a_vector = sim_percentiles$nsingletons, incl =F),
+                  mean_prop_off_actual = mean(sim_percentiles$prop_off_actual),
+                  prop_off_actual_2p5 = quantile( sim_percentiles$prop_off_actual, probs = 0.025, na.rm = T),
+                  prop_off_actual_97p5 = quantile( sim_percentiles$prop_off_actual, probs = .975, na.rm = T))
 
 
   sim_dis <- dplyr::bind_rows(sim_percentiles, sampled_percentile)
@@ -139,11 +150,18 @@ pull_di <- function(di_df) {
                      nsamples = length(unique(sim)),
[…]

### 2021-02-14 analysis/rev_prototyping/jackknife.Rmd
run

---
title: "Jackknife"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())
library(scadsanalysis)

```
```{r}
mcdb <- load_dataset("mcdb")

mcdb_sv <- get_statevars(mcdb)

a_site <- filter(mcdb, site == 1270)
```

Using community 1270 from MCDB because with S = 8, N = 542 it's not miniscule but it's small enough that things will run easily locally. Results might be on the small end.

```{r}

```
```{r, echo = T}

make_ind_pool_species <- function(a_vect) {

  rep(a_vect[1], times = a_vect[2])

}

sample_ind_pool <- function(ind_pool, nind_to_sample) {
 species = sample(ind_pool, size = nind_to_sample, replace = FALSE)

 return(data.frame(species = species))
}

jacknife <- function(site_df, prop_of_ind = .6, nsims = 10) {

  nind <- sum(site_df$abund)

  nind_to_sample <- ceiling(prop_of_ind * nind)

  nspp <- nrow(site_df)

  # ind_pool_mat <- as.matrix(dplyr::select(site_df, rank, abund))
  # 
  # ind_pool <- unlist(apply(ind_pool_mat, MARGIN = 1, FUN = make_ind_pool_species))
  # 
  # sampled_ind <- replicate(n = nsims, expr = sample_ind_pool(ind_pool, nind_to_sample), simplify = F)
  # 
  sampled_ind <- rmultinom(n = nsims, size = nind_to_sample, prob = site_df$abund)

  sampled_ind_df <- as.data.frame(sampled_ind) %>%
    dplyr::mutate(species = dplyr::row_number()) %>%
    tidyr::pivot_longer(-species, names_to = "sim", values_to = "abund") %>%
    filter(abund > 0) %>%
    dplyr::group_by(sim) %>%
    dplyr::arrange(abund) %>%
    dplyr::mutate(rank = dplyr::row_number()) %>%
    dplyr::ungroup() %>%
    dplyr::arrange(sim, rank) %>%
    dplyr::mutate(sim = substr(sim, 2, nchar(sim))) %>%
    dplyr::select(-species)

  site_df_identifiers <- site_df %>%
    select(dat, site, singletons, source) %>%
    distinct()

  sampled_ind_df <- sampled_ind_df %>%
    cbind(site_df_identifiers) %>%
    dplyr::mutate(site = paste0(site, "_jacknife_", sim)) %>%
    dplyr::mutate(sim = -99)

  return(sampled_ind_df)

  }

set.seed(1977)

a_site_jk <- jacknife(a_site)

```

```{r, fig.dim= c(4,3)}

ggplot(a_site, aes(rank, abund)) +
  geom_point() +
  geom_line() +
  ggtitle("Actual")

ggplot(a_site_jk, aes(rank, abund, group = site)) +
  geom_line(alpha = .3) +
  geom_point(alpha = .3) +
  ggtitle("Resamples")

```
```{r}

jacknife_whole_dataset <- function(dataset, prop_of_ind = .6, nsims = 10) {

  sites_list <- unique(dataset$site)

  all_sites <- lapply(sites_list, FUN = function(which_site, whole_dataset) return(dplyr::filter(whole_dataset, site == which_site)), whole_dataset = dataset)

  all_jacknifes <- lapply(all_sites, FUN = jacknife, prop_of_ind = prop_of_ind, nsims = nsims)

  all_jacknifes <- dplyr::bind_rows(all_jacknifes)

  return(all_jacknifes)
}

mcdb_jacknifes <- jacknife_whole_dataset(mcdb)

write.csv(mcdb_jacknifes, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "mcdb_jk.csv"), row.names = F)

```

### 2021-02-14 analysis/rev_prototyping/jackknife.Rmd
fixese

@@
 
-  # ind_pool_mat <- as.matrix(dplyr::select(site_df, rank, abund))
+  ind_pool_mat <- as.matrix(dplyr::select(site_df, rank, abund))
+
+  ind_pool <- unlist(apply(ind_pool_mat, MARGIN = 1, FUN = make_ind_pool_species))
+
+  sampled_ind <- replicate(n = nsims, expr = sample_ind_pool(ind_pool, nind_to_sample), simplify = F)
+
+  sampled_ind = unique(sampled_ind)
+
 # 
-  # ind_pool <- unlist(apply(ind_pool_mat, MARGIN = 1, FUN = make_ind_pool_species))
-  # 
-  # sampled_ind <- replicate(n = nsims, expr = sample_ind_pool(ind_pool, nind_to_sample), simplify = F)
-  # 
-  sampled_ind <- rmultinom(n = nsims, size = nind_to_sample, prob = site_df$abund)
+#   sampled_ind <- rmultinom(n = nsims, size = nind_to_sample, prob = site_df$abund)
 
-  sampled_ind_df <- as.data.frame(sampled_ind) %>%
-    dplyr::mutate(species = dplyr::row_number()) %>%
-    tidyr::pivot_longer(-species, names_to = "sim", values_to = "abund") %>%
-    filter(abund > 0) %>%
+  sampled_ind_df <- dplyr::bind_rows(sampled_ind, .id = "sim") %>%
+    dplyr::group_by(sim, species) %>%
+    dplyr::summarize(abund = dplyr::n()) %>%
+    dplyr::ungroup() %>%
+    dplyr::filter(abund > 0) %>%
+    dplyr::select(-species) %>%
     dplyr::group_by(sim) %>%
@@
     dplyr::ungroup() %>%
-    dplyr::arrange(sim, rank) %>%
-    dplyr::mutate(sim = substr(sim, 2, nchar(sim))) %>%
-    dplyr::select(-species)
+    dplyr::arrange(sim, rank)
 

### 2021-02-14 R/metrics.R

@@ -12,7 +12,7 @@
 #' @importFrom e1071 skewness
 #' @importFrom dplyr group_by_at summarize ungroup filter mutate
 #' @importFrom vegan diversity
-add_dis <- function(fs_samples_df) {
+add_dis <- function(fs_samples_df, sim_props_off = NULL) {
 
   if(is.null(fs_samples_df)) {
     return(NA)
@@ -43,6 +43,7 @@ add_dis <- function(fs_samples_df) {
                   shannon_percentile = get_percentiles(shannon),
                   simpson_percentile = get_percentiles(simpson))
 
+
   sampled_percentile <- sim_dis %>%
     dplyr::filter(source == "observed", sim < 0) %>%
     dplyr::mutate(skew_percentile = get_percentile(skew, a_vector = sim_percentiles$skew),
@@ -57,8 +58,19 @@ add_dis <- function(fs_samples_df) {
                   nsingletons_95 = quantile(sim_percentiles$nsingletons, probs = 0.95, na.rm =T),
                   mean_prop_off_actual = mean(sim_percentiles$prop_off_actual),
                   prop_off_actual_2p5 = quantile( sim_percentiles$prop_off_actual, probs = 0.025, na.rm = T),
-                  prop_off_actual_97p5 = quantile( sim_percentiles$prop_off_actual, probs = .975, na.rm = T))
+                  prop_off_actual_97p5 = quantile( sim_percentiles$prop_off_actual, probs = .975, na.rm = T),
+                  prop_off_actual_5 = quantile(sim_percentiles$prop_off_actual, probs = .05, na.rm = T),
+                  prop_off_actual_95 = quantile(sim_percentiles$prop_off_actual, probs = .95, na.rm = T)
+                  )
 
+
+  if(!(is.null(sim_props_off))) {
+
+    sampled_percentile <- sampled_percentile %>%
+      dplyr::mutate(prop_off_sim_95 = quantile(sim_props_off$prop_off, probs = .95, na.rm = T),
+                    mean_prop_off_sim = mean(sim_props_off$prop_off, na.rm = T),
+                    prop_off_sim_95_1t = (quantile(sim_props_off$prop_off, probs = .95, na.rm = T) - min(sim_props_off$prop_off))/(max(sim_props_off$prop_off) - min(sim_props_off$prop_off)))
+}
 
[…]

### 2021-02-14 analysis/local_pipeline.R

@@ -27,8 +27,10 @@ all <- drake_plan(
   fs = target(sample_fs_wrapper(dataset = dat_s_dat_mcdb, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = mamm_p, seed = !!sample.int(10^6, size = 1)),
               transform = cross(s = !!sites_list$site,
                                 singletons = !!c(TRUE, FALSE))),
-  di = target(add_dis(fs),
-              transform = map(fs)),
+  fs_diffs = target(get_fs_diffs(fs),
+                    transform = map(fs)),
+  di = target(add_dis(fs, fs_diffs),
+              transform = map(fs, fs_diffs)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),

### 2021-02-14 analysis/mcdb_pipeline_jk.R

@@ -7,7 +7,7 @@ expose_imports("scadsanalysis")
 
 dataset <- read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "mcdb_jk.csv"))
 
-max_n_sites = 1000
+max_n_sites = 50
 
 sites_list <- dataset %>%
   select(site, dat) %>%
@@ -35,8 +35,10 @@ all <- drake_plan(
                   hpc = F),
   fs = target(sample_fs_wrapper(dataset = dat, site_name = s, singletonsyn = FALSE, n_samples = ndraws, p_table = mamm_p, seed = !!sample.int(10^6, size = 1)),
               transform = map(s = !!sites_list$site)),
-  di = target(add_dis(fs),
-              transform = map(fs)),
+  fs_diffs = target(get_fs_diffs(fs),
+                    transform = map(fs)),
+  di = target(add_dis(fs, fs_diffs),
+              transform = map(fs, fs_diffs)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   all_di_obs = target(dplyr::bind_rows(di_obs),

### 2021-02-15 analysis/rev_prototyping/jackknife_mcdb_results.Rmd

---
title: "Jackknife"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())
library(scadsanalysis)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

jk_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_jk_di.csv"))

jk_di <- jk_di %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup()

all_di <- all_di %>%
  filter(dat == "mcdb") %>%
  mutate(site = as.character(site)) %>%
  filter(site %in% jk_di$site_source) %>%
  filter(!singletons)

```

## actual

```{r}

ggplot(all_di, aes(skew_percentile)) +
  geom_histogram()

ggplot(all_di, aes(simpson_percentile)) +
  geom_histogram()

```

```{r}

all_di <- all_di %>%
  select(-sim, -source, -singletons) %>%
  rename(site_source = site)

colnames(all_di)[3:48] <- paste0(colnames(all_di)[3:48], "_actual")

change_key <- data.frame(change = c(0:2), description = c("both F", "change T to F", "both T"))

wide_di <- left_join(jk_di, all_di) %>%
  group_by(site_source) %>%
  mutate(mean_skew_percentile_excl = mean(skew_percentile_excl),
         mean_simpson_percentile = mean(simpson_percentile),
         mean_nparts = mean(nparts)) %>%
  ungroup() %>%
  mutate(actual_sig_skew = skew_percentile_excl_actual > 95,
         actual_sig_even = simpson_percentile_actual < 5,
         mean_sig_skew = mean_skew_percentile_excl > 95,
         mean_sig_even = mean_simpson_percentile < 5) %>%
  mutate(skew_change = paste0("actual", actual_sig_skew, "_jk", mean_sig_skew),
         even_change = paste0("actual", actual_sig_even,"_jk", mean_sig_even))

```

```{r}

ggplot(wide_di, aes(site_source, skew_percentile_excl, color = skew_percentile_excl_actual > 95)) +
  geom_boxplot() +
  geom_point(aes(site_source, skew_percentile_excl_actual)) +
  theme(legend.position = "top") +
  geom_hline(yintercept = 95)

ggplot(wide_di, aes(site_source, simpson_percentile, color = simpson_percentile_actual <5)) +
  geom_boxplot() +
  geom_point(aes(site_source, simpson_percentile_actual)) +
  theme(legend.position = "top") +
  geom_hline(yintercept = 5)

ggplot(wide_di, aes(s0_actual, n0_actual, color = skew_change)) +
  geom_point()

ggplot(wide_di, aes(s0_actual, n0_actual, color = even_change)) +
  geom_point()

ggplot(wide_di, aes(nparts_actual, mean_nparts, color = skew_change)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  geom_line(aes(nparts_actual, nparts_actual), color = "black")

```

So for these 50 communities, resampling does not change the outcome for the 6-10 largest communities. It changes it for a handful of smaller communities. RMD suspects this is because the jacknifed samples, with 60% as many individuals, count as "small" in a way that the observed sample does not. However, it could also be that in drawing a smaller number of individuals you have more error, as in you aren't doing as good a job replicating the larger distribution?

```{r, fig.dim = c(3,8)}

mcdb <- load_dataset("mcdb")

actual_sads <- filter(mcdb, site %in% wide_di$site_source)

jacknife_sads <- read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "mcdb_jk.csv"))

interesting_sites <- filter(wide_di, skew_change != "actualFALSE_jkFALSE")

actual_sad_plots <- ggplot(filter(actual_sads, site %in% interesting_sites$site_source), aes(rank, abund)) + geom_point() + geom_line() + facet_wrap(vars(site), scales = "free", ncol = 1)+ theme(legend.position = "none")

jacknife_sads <- left_join(jacknife_sads, select(wide_di, site, site_source, skew_change, even_change))

jacknife_sad_plots <- ggplot(filter(jacknife_sads, site_source %in% interesting_sites$site_source), aes(rank, abund, color = skew_change, group = site)) +geom_line() + facet_wrap(vars(site_source), scales = "free", ncol = 1) + theme(legend.position = "none")
actual_sad_plots
jacknife_sad_plots
```

I want to wait until I get results back from a larger sample of the MCDB. At the moment it seems pretty cool that a) it doesn't change much for high N communities but b) it super does for the small ones.

One interesting question is, whether it's the **tininess of the new sample** doing a poor job replicating the original shape, or whether it's the tininess of the new sample getting down to a fuzzy FS space. I'm not sure if you can take these apart, but it's fun to think about.

### 2021-02-15 analysis/rev_prototyping/nsingletons_prelim_results.Rmd
prelim resluts

---
title: "Prop off"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())

all_di <- read.csv(here::here("miscabund_di.csv"))

all_di <- all_di %>%
  filter(s0 > 1,
         s0 != n0,
         n0 != s0 + 1)

```

```{r}
di_10 <- read.csv(here::here("misc_10_di.csv"))

ggplot(filter(di_10, source == "sampled"), aes(nsingletons)) +
  geom_histogram() +
  geom_vline(xintercept = filter(di_10, source == "observed")$nsingletons)

di_11 <- read.csv(here::here("misc_11_di.csv"))

ggplot(filter(di_11, source == "sampled"), aes(nsingletons)) +
  geom_histogram() +
  geom_vline(xintercept = filter(di_11, source == "observed")$nsingletons)

di_22 <- read.csv(here::here("misc_22_di.csv"))

ggplot(filter(di_22, source == "sampled"), aes(nsingletons)) +
  geom_histogram() +
  geom_vline(xintercept = filter(di_22, source == "observed")$nsingletons)

filter(all_di, site %in% c(10, 11, 22), !singletons)  %>%
  select(site, nsingletons_percentile, nsingletons_percentile_excl)

```

### 2021-02-15 analysis/rev_prototyping/prop_off_prelim_results.Rmd
prelim resluts

---
title: "Prop off"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())

all_di <- read.csv(here::here("miscabund_di.csv"))

all_di <- all_di %>%
  filter(s0 > 1,
         s0 != n0,
         n0 != s0 + 1) %>%
  mutate(prop_off_sig_mean = mean_prop_off_actual >= prop_off_sim_95,
         prop_off_sig_5pc = prop_off_actual_5 >= prop_off_sim_95)

```
```{r}

ggplot(all_di, aes(prop_off_sim_95, mean_prop_off_actual, color = log(nparts))) +
  geom_point() +
  geom_line(aes(prop_off_sim_95, prop_off_sim_95))

all_di %>%
  group_by(singletons) %>%
  summarize(prop_off_m = mean(prop_off_sig_mean),
            prop_off_f = mean(prop_off_sig_5pc))

all_di %>%
  filter(prop_off_sig_mean) %>%
  group_by(singletons) %>%
  summarize(diff = mean(mean_prop_off_actual - mean_prop_off_sim))

ggplot(all_di, aes(nparts, prop_off_sim_95_1t)) +
  geom_point() +
  scale_x_log10()

ggplot(all_di, aes(nparts, prop_off_sim_95_1t)) +
  geom_point() +
  scale_x_log10() +
  xlim(0, 10000)

```

### One where both are significant

```{r}
di_10 <- read.csv(here::here("misc_10_di.csv"))
diffs_10 <- read.csv(here::here("misc_10_diffs.csv"))

po_10 <- data.frame(
  actual = di_10$prop_off_actual[1:nrow(diffs_10)],
  sim = diffs_10$prop_off
)

po_long_10 <- po_10%>%
  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")

ggplot(po_long_10, aes(prop_off, color = source)) +
  geom_density()

filter(di_10, source == "observed") %>%
  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)

ecdfs_10 <- data.frame(
  actual = ecdf(po_10$actual)(seq(0, 1, length.out = 100)),
  sim = ecdf(po_10$sim)(seq(0, 1, length.out = 100)),
  val = seq(0, 1, length.out = 100)
) %>%
  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")

ggplot(ecdfs_10, aes(val, ecdf, color = source)) +
  geom_line()

ks.test(po_10$actual, po_10$sim, alternative = "less")
t.test(po_10$actual, po_10$sim)

glm_10 <- (glm(prop_off ~ source, data = po_long_10, family = Gamma))

summary(glm_10)

predict(glm_10, newdata = data.frame(source = c('actual', 'sim')), type = "response")

```

### One where mean is and 95 is not

```{r}
di_11 <- read.csv(here::here("misc_11_di.csv"))
diffs_11 <- read.csv(here::here("misc_11_diffs.csv"))

po_11 <- data.frame(
  actual = di_11$prop_off_actual[1:nrow(diffs_11)],
  sim = diffs_11$prop_off
)

po_long_11 <- po_11%>%
  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")

ggplot(po_long_11, aes(prop_off, color = source)) +
  geom_density()

filter(di_11, source == "observed") %>%
  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)

ecdfs_11 <- data.frame(
  actual = ecdf(po_11$actual)(seq(0, 1, length.out = 100)),
  sim = ecdf(po_11$sim)(seq(0, 1, length.out = 100)),
  val = seq(0, 1, length.out = 100)
) %>%
  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")

ggplot(ecdfs_11, aes(val, ecdf, color = source)) +
  geom_line()

ks.test(po_11$actual, po_11$sim, alternative = "less")
t.test(po_11$actual, po_11$sim)

glm_11 <- (glm(prop_off ~ source, data = po_long_11, family = Gamma))

summary(glm_11)

predict(glm_11, newdata = data.frame(source = c('actual', 'sim')), type = "response")

```

### One where neither is

```{r}
di_22 <- read.csv(here::here("misc_22_di.csv"))
diffs_22 <- read.csv(here::here("misc_22_diffs.csv"))

po_22 <- data.frame(
  actual = di_22$prop_off_actual[1:nrow(diffs_22)],
  sim = diffs_22$prop_off
)

po_long_22 <- po_22%>%
  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")

ggplot(po_long_22, aes(prop_off, color = source)) +
  geom_density()

filter(di_22, source == "observed") %>%
  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)

ecdfs_22 <- data.frame(
  actual = ecdf(po_22$actual)(seq(0, 1, length.out = 100)),
  sim = ecdf(po_22$sim)(seq(0, 1, length.out = 100)),
  val = seq(0, 1, length.out = 100)
) %>%
  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")

ggplot(ecdfs_22, aes(val, ecdf, color = source)) +
  geom_line()

ks.test(po_22$actual, po_22$sim, alternative = "less")

t.test(po_22$actual, po_22$sim)

glm_22 <- (glm(prop_off ~ source, data = po_long_22, family = Gamma))

summary(glm_22)

predict(glm_22, newdata = data.frame(source = c('actual', 'sim')), type = "response")

```

The KS test finds even very small differences. Ditto t tests and Wilcox and GLMs.

Is it valid to compare the **mean** of the actual to the **95%** of the sims? I raise this because comparing the 5% to the 95% seems awfully conservative. But I'm not sure.

### 2021-02-16 analysis/rev_prototyping/jackknife.Rmd
run som stuffs

@@
 
+misc <- load_dataset("misc_abund_short")
+
+misc_jacknifes <- jacknife_whole_dataset(misc)
+
+write.csv(misc_jacknifes, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "misc_jk.csv"), row.names = F)
+
+bbs <- load_dataset("bbs")
+
+bbs_jacknifes <- jacknife_whole_dataset(bbs)
+
+write.csv(bbs_jacknifes, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "bbs_jk.csv"), row.names = F)
+
+gentry <- load_dataset("gentry")
+
+gentry_jacknifes <- jacknife_whole_dataset(gentry)
+
+write.csv(gentry_jacknifes, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "gentry_jk.csv"), row.names = F)
+
 ```

### 2021-02-16 analysis/rev_prototyping/jackknife_mcdb_results.Rmd
run som stuffs

@@
 
-jk_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_jk_di.csv"))
+jk_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_di_jk.csv"))
 
@@
          mean_simpson_percentile = mean(simpson_percentile),
+         mean_shannon_percentile = mean(shannon_percentile),
          mean_nparts = mean(nparts)) %>%
@@
          mean_sig_skew = mean_skew_percentile_excl > 95,
-         mean_sig_even = mean_simpson_percentile < 5) %>%
+         mean_sig_even = mean_simpson_percentile < 5,
+         actual_sig_shannon = shannon_percentile_actual < 5,
+         mean_sig_shannon=  mean_shannon_percentile < 5) %>%
   mutate(skew_change = paste0("actual", actual_sig_skew, "_jk", mean_sig_skew),
-         even_change = paste0("actual", actual_sig_even,"_jk", mean_sig_even))
+         even_change = paste0("actual", actual_sig_even,"_jk", mean_sig_even),
+         shannon_change = paste0("actual", actual_sig_shannon, "_jk", mean_sig_shannon))
 
@@
 ```{r}
+
+wide_di_small <- wide_di %>%
+  select(site_source, mean_skew_percentile_excl, mean_simpson_percentile, s0, n0, mean_nparts, skew_change, even_change, actual_sig_skew, actual_sig_even, mean_sig_skew, mean_sig_even, mean_shannon_percentile, actual_sig_shannon, mean_sig_shannon, shannon_change) %>%
+  filter(s0 > 2,
+         s0 != n0,
+         n0 != s0 + 1) %>%
+  distinct()
+
+ggplot(wide_di_small, aes(mean_skew_percentile_excl)) +
+  geom_histogram()
+
+ggplot(wide_di_small, aes(mean_simpson_percentile)) +
+  geom_histogram()
+
+ggplot(wide_di_small, aes(mean_shannon_percentile)) +
+  geom_histogram()
+
+mean(wide_di_small$actual_sig_skew)
+mean(wide_di_small$mean_sig_skew)
+
+mean(wide_di_small$actual_sig_shannon)
+mean(wide_di_small$mean_sig_shannon)
+
+mean(wide_di_small$actual_sig_even)
+mean(wide_di_small$mean_sig_even)
+
+wide_di_small %>%
+  group_by(even_change) %>%
+  tally()
 
@@
 ggplot(wide_di, aes(s0_actual, n0_actual, color = skew_change)) +
-  geom_point()
+  geom_point() +
+  facet_wrap(vars(skew_change))
 
@@
 ggplot(wide_di, aes(nparts_actual, mean_nparts, color = skew_change)) +
-  geom_point() +
+  geom_point(alpha = .5) +
   scale_x_log10() +

### 2021-02-16 analysis/rev_prototyping/nsingletons_prelim_results.Rmd
run som stuffs

@@
 
-all_di <- read.csv(here::here("miscabund_di.csv"))
+all_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_di.csv"))
 
@@
          s0 != n0,
-         n0 != s0 + 1)
+         n0 != s0 + 1,
+         !singletons)
+
+sum(all_di$nsingeltons_median == all_di$nsingletons_95)
+
+ggplot(filter(all_di, nsingletons_95 > nsingeltons_median), aes(nsingletons_percentile)) +
+  geom_histogram()
+
+ggplot(filter(all_di, nsingletons_95 > nsingeltons_median), aes(nsingletons_percentile_excl)) +
+  geom_histogram()
 

### 2021-02-16 analysis/bbs_pipeline_jk.R

@@ -1,0 +1,86 @@
+library(drake)
+library(scadsanalysis)
+library(ggplot2)
+library(dplyr)
+
+expose_imports("scadsanalysis")
+
+dataset <- read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "bbs_jk.csv"))
+
+max_n_sites = 1000
+
+sites_list <- dataset %>%
+  select(site, dat) %>%
+  distinct() %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup()
+
+sites_list <- sites_list %>%
+  filter(site_source %in% unique(sites_list$site_source)[1:max_n_sites]) %>%
+  select(-site_source)
+
+ndraws = 4000
+
+
+#sites_list <- sites_list[1:5, ]
+set.seed(1980)
+
+
+all <- drake_plan(
+  dat = target(read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "bbs_jk.csv")),
+               hpc = F
+  ),
+  wide_p = target(readRDS(here::here("analysis", "masterp_wide.Rds")),
+                  hpc = F),
+  fs = target(sample_fs_wrapper(dataset = dat, site_name = s, singletonsyn = FALSE, n_samples = ndraws, p_table = wide_p, seed = !!sample.int(10^6, size = 1)),
+              transform = map(s = !!sites_list$site)),
+  fs_diffs = target(get_fs_diffs(fs),
+                    transform = map(fs)),
+  di = target(add_dis(fs, fs_diffs),
+              transform = map(fs, fs_diffs)),
+  di_obs = target(pull_di(di),
+                  transform = map(di)),
+  all_di_obs = target(dplyr::bind_rows(di_obs),
+                    transform = combine(di_obs))
+)
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-bbs-jk.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+#
+# ## View the graph of the plan
+# if (interactive())
+# {
+#   config <- drake_config(all, cache = cache)
+#   sankey_drake_graph(config, build_times = "none")  # requires "networkD3" package
+#   vis_drake_graph(config, build_times = "none")     # requires "visNetwork" package
+# }
+#
[…]

### 2021-02-16 analysis/gentry_pipeline_jk.R

@@ -1,0 +1,86 @@
+library(drake)
+library(scadsanalysis)
+library(ggplot2)
+library(dplyr)
+
+expose_imports("scadsanalysis")
+
+dataset <- read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "gentry_jk.csv"))
+
+max_n_sites = 1000
+
+sites_list <- dataset %>%
+  select(site, dat) %>%
+  distinct() %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup()
+
+sites_list <- sites_list %>%
+  filter(site_source %in% unique(sites_list$site_source)[1:max_n_sites]) %>%
+  select(-site_source)
+
+ndraws = 4000
+
+
+#sites_list <- sites_list[1:5, ]
+set.seed(1980)
+
+
+all <- drake_plan(
+  dat = target(read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "gentry_jk.csv")),
+               hpc = F
+  ),
+  wide_p = target(readRDS(here::here("analysis", "masterp_wide.Rds")),
+                  hpc = F),
+  fs = target(sample_fs_wrapper(dataset = dat, site_name = s, singletonsyn = FALSE, n_samples = ndraws, p_table = wide_p, seed = !!sample.int(10^6, size = 1)),
+              transform = map(s = !!sites_list$site)),
+  fs_diffs = target(get_fs_diffs(fs),
+                    transform = map(fs)),
+  di = target(add_dis(fs, fs_diffs),
+              transform = map(fs, fs_diffs)),
+  di_obs = target(pull_di(di),
+                  transform = map(di)),
+  all_di_obs = target(dplyr::bind_rows(di_obs),
+                    transform = combine(di_obs))
+)
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-gentry-jk.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+#
+# ## View the graph of the plan
+# if (interactive())
+# {
+#   config <- drake_config(all, cache = cache)
+#   sankey_drake_graph(config, build_times = "none")  # requires "networkD3" package
+#   vis_drake_graph(config, build_times = "none")     # requires "visNetwork" package
+# }
+#
[…]

### 2021-02-17 analysis/rev_prototyping/prop_off_prelim_results.Rmd
change pipeline structure

@@
 ```
+
 ```{r}
 
-ggplot(all_di, aes(prop_off_sim_95, mean_prop_off_actual, color = log(nparts))) +
+ggplot(filter(all_di, n_po_comparisons > 20), aes(mean_po_comparison_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(singletons), scales = "free_y")
+
+ggplot(filter(all_di, n_po_comparisons > 20), aes(n_po_comparisons)) +
+  geom_histogram()
+
+all_di %>% group_by(singletons) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))
+
+ggplot(all_di, aes(mean_po_comparison_95, mean_po_comparison, color = log(nparts))) +
   geom_point() +
-  geom_line(aes(prop_off_sim_95, prop_off_sim_95))
+  geom_line(aes(mean_po_comparison_95, mean_po_comparison_95))
 
 all_di %>%
+  filter(mean_po_comparison_percentile > 95) %>%
   group_by(singletons) %>%
-  summarize(prop_off_m = mean(prop_off_sig_mean),
-            prop_off_f = mean(prop_off_sig_5pc))
+  summarize(diff = mean(mean_po_comparison - mean_po_comparison_95))
 
-all_di %>%
-  filter(prop_off_sig_mean) %>%
-  group_by(singletons) %>%
-  summarize(diff = mean(mean_prop_off_actual - mean_prop_off_sim))
-
-ggplot(all_di, aes(nparts, prop_off_sim_95_1t)) +
+ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t)) +
   geom_point() +
@@
 
-ggplot(all_di, aes(nparts, prop_off_sim_95_1t)) +
+ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t)) +
   geom_point() +
@@
 ```
-
-### One where both are significant
-
-```{r}
-di_10 <- read.csv(here::here("misc_10_di.csv"))
-diffs_10 <- read.csv(here::here("misc_10_diffs.csv"))
-
-po_10 <- data.frame(
-  actual = di_10$prop_off_actual[1:nrow(diffs_10)],
-  sim = diffs_10$prop_off
-)
-
-po_long_10 <- po_10%>%
-  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")
-
-ggplot(po_long_10, aes(prop_off, color = source)) +
-  geom_density()
-
-filter(di_10, source == "observed") %>%
-  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)
-
-ecdfs_10 <- data.frame(
-  actual = ecdf(po_10$actual)(seq(0, 1, length.out = 100)),
-  sim = ecdf(po_10$sim)(seq(0, 1, length.out = 100)),
-  val = seq(0, 1, length.out = 100)
-) %>%
-  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")
-
-ggplot(ecdfs_10, aes(val, ecdf, color = source)) +
-  geom_line()
-
-ks.test(po_10$actual, po_10$sim, alternative = "less")
-t.test(po_10$actual, po_10$sim)
-
-glm_10 <- (glm(prop_off ~ source, data = po_long_10, family = Gamma))
-
-summary(glm_10)
-
-predict(glm_10, newdata = data.frame(source = c('actual', 'sim')), type = "response")
-
-```
-
-### One where mean is and 95 is not
-
-```{r}
-di_11 <- read.csv(here::here("misc_11_di.csv"))
-diffs_11 <- read.csv(here::here("misc_11_diffs.csv"))
-
-po_11 <- data.frame(
-  actual = di_11$prop_off_actual[1:nrow(diffs_11)],
-  sim = diffs_11$prop_off
-)
-
-po_long_11 <- po_11%>%
-  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")
-
-ggplot(po_long_11, aes(prop_off, color = source)) +
-  geom_density()
-
-filter(di_11, source == "observed") %>%
-  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)
-
-ecdfs_11 <- data.frame(
-  actual = ecdf(po_11$actual)(seq(0, 1, length.out = 100)),
-  sim = ecdf(po_11$sim)(seq(0, 1, length.out = 100)),
-  val = seq(0, 1, length.out = 100)
-) %>%
-  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")
-
-ggplot(ecdfs_11, aes(val, ecdf, color = source)) +
-  geom_line()
-
-ks.test(po_11$actual, po_11$sim, alternative = "less")
-t.test(po_11$actual, po_11$sim)
-
-glm_11 <- (glm(prop_off ~ source, data = po_long_11, family = Gamma))
-
-summary(glm_11)
-
-predict(glm_11, newdata = data.frame(source = c('actual', 'sim')), type = "response")
-
-```
-
-### One where neither is
-
-```{r}
-di_22 <- read.csv(here::here("misc_22_di.csv"))
-diffs_22 <- read.csv(here::here("misc_22_diffs.csv"))
-
-po_22 <- data.frame(
-  actual = di_22$prop_off_actual[1:nrow(diffs_22)],
-  sim = diffs_22$prop_off
-)
-
-po_long_22 <- po_22%>%
-  tidyr::pivot_longer(c(actual, sim), names_to = "source", values_to = "prop_off")
-
-ggplot(po_long_22, aes(prop_off, color = source)) +
-  geom_density()
-
-filter(di_22, source == "observed") %>%
-  select(mean_prop_off_actual, prop_off_actual_5, prop_off_sim_95, prop_off_sim_95_1t)
-
-ecdfs_22 <- data.frame(
-  actual = ecdf(po_22$actual)(seq(0, 1, length.out = 100)),
-  sim = ecdf(po_22$sim)(seq(0, 1, length.out = 100)),
-  val = seq(0, 1, length.out = 100)
-) %>%
-  tidyr::pivot_longer(-val, names_to = "source", values_to = "ecdf")
-
-ggplot(ecdfs_22, aes(val, ecdf, color = source)) +
-  geom_line()
-
-ks.test(po_22$actual, po_22$sim, alternative = "less")
-
-t.test(po_22$actual, po_22$sim)
-
-glm_22 <- (glm(prop_off ~ source, data = po_long_22, family = Gamma))
-
-summary(glm_22)
-
-predict(glm_22, newdata = data.frame(source = c('actual', 'sim')), type = "response")
-
-```
-
-The KS test finds even very small differences. Ditto t tests and Wilcox and GLMs.
-
-Is it valid to compare the **mean** of the actual to the **95%** of the sims? I raise this because comparing the 5% to the 95% seems awfully conservative. But I'm not sure.

### 2021-02-17 R/metrics.R

@@ -12,7 +12,7 @@
 #' @importFrom e1071 skewness
 #' @importFrom dplyr group_by_at summarize ungroup filter mutate left_join
 #' @importFrom vegan diversity
-add_dis <- function(fs_samples_df, sim_props_off = NULL) {
+add_dis <- function(fs_samples_df, sim_props_off = NULL, props_comparison = NULL) {
 
   if(is.null(fs_samples_df)) {
     return(NA)
@@ -28,6 +28,13 @@ add_dis <- function(fs_samples_df, sim_props_off = NULL) {
     actual <- dplyr::filter(fs_samples_df, sim == min(fs_samples_df$sim, na.rm  = T))
   }
 
+  if(is.null(props_comparison)) {
+
+    props_comparison <- lapply(unique(fs_samples_df$sim), FUN = compare_props_off, fs_df = fs_samples_df, ncomps = 1000) %>%
+      dplyr::bind_rows()
+  }
+
+
   sim_dis <- fs_samples_df %>%
     dplyr::group_by_at(.vars = groupvars) %>%
     dplyr::summarize(skew = e1071::skewness(abund),
@@ -37,8 +44,6 @@ add_dis <- function(fs_samples_df, sim_props_off = NULL) {
                      prop_off_actual = proportion_off(t(cbind(actual$abund, abund)))) %>%
     dplyr::ungroup()
 
-  props_comparison <- lapply(unique(fs_samples_df$sim), FUN = compare_props_off, fs_df = fs_samples_df, ncomps = 1000) %>%
-    dplyr::bind_rows()
 
   sim_dis <- dplyr::left_join(sim_dis, props_comparison, by = c("sim" = "focal_sim"))
 
@@ -68,7 +73,8 @@ add_dis <- function(fs_samples_df, sim_props_off = NULL) {
                   prop_off_actual_97p5 = quantile( sim_percentiles$prop_off_actual, probs = .975, na.rm = T),
                   prop_off_actual_5 = quantile(sim_percentiles$prop_off_actual, probs = .05, na.rm = T),
                   prop_off_actual_95 = quantile(sim_percentiles$prop_off_actual, probs = .95, na.rm = T),
-                  mean_po_comparison_percentile = get_percentile(mean_po_comparison, a_vector = sim_percentiles$mean_po_comparison)
[…]

### 2021-02-17 analysis/local_pipeline.R

@@ -27,10 +27,12 @@ all <- drake_plan(
   fs = target(sample_fs_wrapper(dataset = dat_s_dat_mcdb, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = mamm_p, seed = !!sample.int(10^6, size = 1)),
               transform = cross(s = !!sites_list$site,
                                 singletons = !!c(TRUE, FALSE))),
-  fs_diffs = target(get_fs_diffs(fs),
-                    transform = map(fs)),
-  di = target(add_dis(fs, fs_diffs),
-              transform = map(fs, fs_diffs)),
+ # fs_diffs = target(get_fs_diffs(fs),
+ #                   transform = map(fs)),
+  fs_pc = target(compare_props_fs(fs),
+                 transform = map(fs)),
+  di = target(add_dis(fs, props_comparison = fs_pc),
+              transform = map(fs, fs_pc)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),

### 2021-02-17 analysis/mcdb_pipeline.R

@@ -27,10 +27,12 @@ all <- drake_plan(
   fs = target(sample_fs_wrapper(dataset = dat_s_dat_mcdb, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = mamm_p, seed = !!sample.int(10^6, size = 1)),
               transform = cross(s = !!sites_list$site,
                                 singletons = !!c(TRUE, FALSE))),
-  fs_diffs = target(get_fs_diffs(fs),
-                    transform = map(fs)),
-  di = target(add_dis(fs, fs_diffs),
-              transform = map(fs, fs_diffs)),
+   fs_diffs = target(get_fs_diffs(fs),
+                     transform = map(fs)),
+  fs_pc = target(compare_props_fs(fs),
+                 transform = map(fs)),
+  di = target(add_dis(fs, props_comparison = fs_pc),
+              transform = map(fs, fs_pc)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),

### 2021-02-17 analysis/miscabund_pipeline.R

@@ -26,10 +26,12 @@ dat_plan <- drake_plan(
   fs = target(sample_fs_wrapper(dataset = dat_s_dat_misc_abund_short, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = tall_p, seed = !!sample.int(10^6, size = 1)),
               transform = cross(s = !!sites_list$site,
                                 singletons = !!c(TRUE, FALSE))),
-  fs_diffs = target(get_fs_diffs(fs),
-                    transform = map(fs)),
-  di = target(add_dis(fs, fs_diffs),
-              transform = map(fs, fs_diffs)),
+   fs_diffs = target(get_fs_diffs(fs),
+                     transform = map(fs)),
+  fs_pc = target(compare_props_fs(fs),
+                 transform = map(fs)),
+  di = target(add_dis(fs, props_comparison = fs_pc),
+              transform = map(fs, fs_pc)),
   di_obs = target(pull_di(di),
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),

### 2021-02-22 analysis/rev_prototyping/additional_metrics_results.Rmd
prelim stuff

--- 2021-02-17 analysis/rev_prototyping/prop_off_prelim_results.Rmd
@@
 ---
-title: "Prop off"
+title: "Other metrics"
 author: Renata Diaz
@@
        df_print: kable
+       toc: true
+
 ---
@@
 
-all_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_di.csv"))
+all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))
 
@@
          s0 != n0,
-         n0 != s0 + 1) %>%
-  mutate(prop_off_sig_mean = mean_prop_off_actual >= prop_off_sim_95,
-         prop_off_sig_5pc = prop_off_actual_5 >= prop_off_sim_95)
+         n0 != s0 + 1)
 
@@
 
+## Proportion off
+
 ```{r}
 
-ggplot(filter(all_di, n_po_comparisons > 20), aes(mean_po_comparison_percentile)) +
+ggplot(filter(all_di), aes(mean_po_comparison_percentile)) +
   geom_histogram() +
-  facet_wrap(vars(singletons), scales = "free_y")
+  facet_wrap(vars(dat, singletons), scales = "free_y")
 
-ggplot(filter(all_di, n_po_comparisons > 20), aes(n_po_comparisons)) +
-  geom_histogram()
-
-all_di %>% group_by(singletons) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))
+all_di %>% group_by(singletons, dat) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))
 
@@
 ```
+
+```{r}
+
+ggplot(all_di, aes(mean_po_comparison_sims, mean_po_comparison, color = mean_po_comparison_percentile > 95)) +
+  geom_point(alpha = .3) +
+  facet_wrap(vars(dat, singletons))
+
+ggplot(all_di, aes(mean_po_comparison - mean_po_comparison_sims, color = mean_po_comparison_percentile > 95)) +
+  geom_histogram(alpha = .3) +
+  facet_wrap(vars(dat, singletons))
+
+```
+
+## Number of singletons
+
+## Shannon diversity

### 2021-02-22 analysis/rev_prototyping/jacknife_results.Rmd
prelim stuff

---
title: "Jackknife"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 3, fig.height = 6)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())
library(scadsanalysis)

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

jk_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))

jk_di <- jk_di %>%
  group_by_all() %>%
  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
  ungroup() %>%
  select(dat, site, site_source, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

jk_di_means <- jk_di %>%
  group_by(dat, site_source) %>%
  summarise_at(vars(-group_cols(), -site), mean)

all_di_actual <- all_di %>%
    filter(!singletons) %>%
  mutate(site_source = as.character(site)) %>%
  select(dat, site_source, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)

colnames(all_di_actual)[ 3:19] <- paste0(colnames(all_di_actual)[ 3:19], "_actual")

jk_di_results <- left_join(jk_di, all_di_actual)
jk_di_mean_results <- left_join(jk_di_means, all_di_actual)

jk_di_mean_results <- jk_di_mean_results %>%
  mutate(skew_actual_sig = skew_percentile_excl_actual > 95,
         skew_sig = skew_percentile_excl > 95) %>%
  mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig))

```

<!-- ## S and N -->

<!-- ```{r} -->

<!-- ggplot(jk_di_mean_results, aes(s0_actual, s0)) + -->
<!--   geom_point() + -->
<!--   geom_line(aes(s0_actual, s0_actual)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->

<!-- ggplot(jk_di_mean_results, aes(n0_actual, n0)) + -->
<!--   geom_point() + -->
<!--   geom_line(aes(n0_actual, n0_actual)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->

<!-- ``` -->

## Skewness

```{r}
ggplot(filter(jk_di_mean_results, s0 > 2), aes(skew_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results, s0 > 2), aes(skew_percentile_excl_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
 filter(s0 > 2) %>%
  group_by(dat) %>%
  summarize(prop_skew_high_jk = mean(skew_percentile_excl > 95),
            prop_skew_high_raw = mean(skew_percentile_excl_actual > 95),
            nsites_included = dplyr::n())
```

## Evenness

```{r}
ggplot(filter(jk_di_mean_results), aes(simpson_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

ggplot(filter(jk_di_mean_results), aes(simpson_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_simpson_high_jk = mean(simpson_percentile < 5),
            prop_simpson_high_raw = mean(simpson_percentile_actual < 5),
            nsites_included = dplyr::n())

```

## Shannon

```{r}
ggplot(filter(jk_di_mean_results), aes(shannon_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

ggplot(filter(jk_di_mean_results), aes(shannon_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 5)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_shannon_high_jk = mean(shannon_percentile < 5),
            prop_shannon_high_raw = mean(shannon_percentile_actual < 5),
            nsites_included = dplyr::n())

```

## Percent off

```{r}
ggplot(filter(jk_di_mean_results), aes(mean_po_comparison_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results), aes(mean_po_comparison_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile > 95),
            prop_mean_po_comparison_high_raw = mean(mean_po_comparison_percentile_actual > 95),
            nsites_included = dplyr::n())

```

## Nsingletons

```{r}
ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile > 95),
            prop_nsingletons_high_raw = mean(nsingletons_percentile_actual > 95),
            nsites_included = dplyr::n())

```

## Nsingletons excl

```{r}
ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_excl_actual)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
  geom_vline(xintercept = 95)

jk_di_mean_results  %>% 
  group_by(dat) %>%
  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile_excl > 95),
            prop_nsingletons_high_raw = mean(nsingletons_percentile_excl_actual > 95),
            nsites_included = dplyr::n())

```

### 2021-02-22 analysis/rev_prototyping/old/nsingletons.Rmd
prelim stuff

---
title: "Shannon diversity"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)

all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         #!singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))

```
```{r}

ggplot(all_di, aes(nsingletons_percentile)) +
  geom_histogram() +
  facet_wrap(vars(dat, singletons), scales = "free_y") +
  xlim(0, 100)

ggplot(all_di, aes(nsingletons_95, nsingletons)) +
  geom_point(alpha = .2) +
  geom_line(aes(nsingletons_95, nsingletons_95)) +
  facet_wrap(vars(dat, singletons), scales = "free")

all_di <- all_di %>%
  mutate(prop_singles_actual = nsingletons / s0,
         sim_prop_singles_95 = nsingletons_95 / s0,
         sim_prop_singles_mean = nsingletons_mean / s0) %>%
  mutate(
            actual_minus_95_prop = prop_singles_actual - sim_prop_singles_95)

all_di %>%
  mutate(high_singles=nsingletons >= nsingletons_95,
         high_singles_ex = nsingletons > nsingletons_95,
         high_singles_mean = nsingletons > nsingletons_mean) %>%
  group_by(dat, singletons) %>%
  summarize(prop_high_singles = mean(high_singles),
            prop_high_singles_ex = mean(high_singles_ex),
            prop_high_singles_mean = mean(high_singles_mean),
            nsites= dplyr::n()) %>%
  ungroup()

```

<!-- ```{r} -->

<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons_mean, nsingletons)) + -->
<!--   geom_point(alpha = .2) + -->
<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
<!--     geom_line(aes(nsingletons_95, nsingletons_95)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->

<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons, nsingletons-nsingletons_95)) + -->
<!--   geom_point(alpha = .2) + -->
<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->
<!-- ``` -->

### 2021-02-22 analysis/rev_prototyping/old/prop_off.Rmd
prelim stuff

--- 2021-02-22 analysis/rev_prototyping/old/nsingletons.Rmd
@@
 
+ggplot(all_di, aes(skew_percentile > 95, mean_prop_off_actual)) +
+  geom_boxplot() +
+  facet_wrap(vars(dat, singletons))
+
+ggplot(all_di, aes(simpson_percentile < 5, mean_prop_off_actual)) +
+  geom_boxplot() +
+  facet_wrap(vars(dat, singletons))
+
+ggplot(all_di, aes(shannon_percentile < 5, mean_prop_off_actual)) +
+  geom_boxplot() +
+  facet_wrap(vars(dat, singletons))
+```
+
+```{r}
+
 ggplot(all_di, aes(nsingletons_percentile)) +
@@
   facet_wrap(vars(dat, singletons), scales = "free")
-
-all_di <- all_di %>%
-  mutate(prop_singles_actual = nsingletons / s0,
-         sim_prop_singles_95 = nsingletons_95 / s0,
-         sim_prop_singles_mean = nsingletons_mean / s0) %>%
-  mutate(
-            actual_minus_95_prop = prop_singles_actual - sim_prop_singles_95)
 

### 2021-02-23 analysis/rev_prototyping/jackknife.Rmd
fia

@@
 
+fia <- load_dataset("fia_short")
+
+fia_sites <- list_sites("fia_short")
+
+fia_to_jk <- sample(fia_sites$site, size = 100, replace = F)
+
+fia <- filter(fia, site %in% fia_to_jk)
+
+fia_jacknives <-jacknife_whole_dataset(fia)
+
+write.csv(fia_jacknives, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "fia_jk.csv"), row.names = F)
+
+fia_small <- load_dataset("fia_small")
+
+fia_small_sites <- list_sites("fia_small")
+
+fia_small_to_jk <- sample(fia_small_sites$site, size = 100, replace = F)
+
+fia_small <- filter(fia_small, site %in% fia_small)
+
+fia_small_jacknives <-jacknife_whole_dataset(fia_small)
+
+write.csv(fia_small_jacknives, here::here("analysis", "rev_prototyping", "jacknifed_datasets", "fia_small_jk.csv"), row.names = F)
+
 ```

### 2021-02-23 analysis/fia_small_pipeline_jk.R

@@ -1,0 +1,90 @@
+library(drake)
+library(scadsanalysis)
+library(ggplot2)
+library(dplyr)
+
+expose_imports("scadsanalysis")
+
+dataset <- read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "fia_small_jk.csv"))
+
+max_n_sites = 1000
+
+sites_list <- dataset %>%
+  select(site, dat) %>%
+  distinct() %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup()
+
+sites_list <- sites_list %>%
+  filter(site_source %in% unique(sites_list$site_source)[1:max_n_sites]) %>%
+  select(-site_source)
+
+ndraws = 4000
+
+
+#sites_list <- sites_list[1:5, ]
+set.seed(1980)
+
+
+all <- drake_plan(
+  dat = target(read.csv(here::here("analysis", "rev_prototyping", "jacknifed_datasets", "fia_small_jk.csv")),
+               hpc = F
+  ),
+  mamm_p = target(readRDS(here::here("analysis", "masterp_mamm.Rds")),
+                  hpc = F),
+  fs = target(sample_fs_wrapper(dataset = dat, site_name = s, singletonsyn = FALSE, n_samples = ndraws, p_table = mamm_p, seed = !!sample.int(10^6, size = 1)),
+              transform = map(s = !!sites_list$site)),
+ # fs_diffs = target(get_fs_diffs(fs),
+  #                  transform = map(fs)),
+  fs_pc = target(compare_props_fs(fs),
+                 transform = map(fs)),
+  di = target(add_dis(fs, props_comparison = fs_pc),
+              transform = map(fs, fs_pc)),
+  di_obs = target(pull_di(di),
+                  transform = map(di)),
+  all_di_obs = target(dplyr::bind_rows(di_obs),
+                    transform = combine(di_obs))
+)
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-fia_small-jk.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+#
+# ## View the graph of the plan
+# if (interactive())
+# {
+#   config <- drake_config(all, cache = cache)
+#   sankey_drake_graph(config, build_times = "none")  # requires "networkD3" package
[…]

### 2021-02-23 analysis/rev_prototyping/nsingletons.Rmd
single and shannon

---
title: "Shannon diversity"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)

theme_set(theme_bw())

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))

```
```{r}

ggplot(all_di, aes(nsingletons_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat, singletons), scales = "free_y") +
  xlim(0, 100)

ggplot(all_di, aes(nsingletons_percentile_excl)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(dat, singletons), scales = "free_y") +
  xlim(0, 100)

all_di <- all_di %>%
  mutate(prop_singles_actual = nsingletons / s0,
         sim_prop_singles_95 = nsingletons_95 / s0,
         sim_prop_singles_mean = nsingletons_mean / s0) %>%
  mutate(actual_minus_95_prop = prop_singles_actual - sim_prop_singles_95) %>%
  mutate(high_singles=nsingletons_percentile > 95,
         high_singles_ex = nsingletons_percentile_excl > 95,
         low_singles = nsingletons_percentile < 5,
         low_singles_ex = nsingletons_percentile_excl < 5) %>%
  mutate(singles_desc = ifelse(high_singles_ex, "high", ifelse(low_singles, "low", "int")))

```

```{r, fig.dim = c(8,8)}

ggplot(all_di, aes(s0, n0, color = singles_desc)) +
  geom_point(alpha = .3) +
  facet_wrap(vars(dat), scales = "free") +
  scale_x_log10()+ 
  scale_y_log10()

all_di %>%
  group_by(dat, singletons) %>%
  summarize(prop_high_singles = mean(high_singles),
            prop_high_singles_ex = mean(high_singles_ex),
            prop_low_singles = mean(low_singles),
            prop_low_singles_ex = mean(low_singles_ex),
            nsites= dplyr::n()) %>%
  ungroup()

```

```{r, echo = T}

ggplot(all_di, aes(n0/s0, nsingletons_percentile_excl, color = singles_desc)) +
  geom_point() +
  facet_wrap(vars(dat), scales = "free") +
  scale_x_log10() +
  geom_vline(xintercept = c(3, 5, 10))

ggplot(all_di, aes(n0/s0, nsingletons_percentile_excl, color = singles_desc)) +
  geom_point(data = filter(all_di, singles_desc != "int")) +
  geom_point(alpha = .1, color = "grey") +
  facet_wrap(vars(dat), scales = "free") +
  scale_x_log10() +
  geom_vline(xintercept = c(3, 5, 10))

all_di %>%
  filter(n0/s0 < 3) %>%
  group_by(dat, singletons) %>%
  summarize(prop_high_singles = mean(high_singles),
            prop_high_singles_ex = mean(high_singles_ex),
            prop_low_singles = mean(low_singles),
            prop_low_singles_ex = mean(low_singles_ex),
            nsites= dplyr::n()) %>%
  ungroup()

all_di %>%
  filter(n0/s0 > 10) %>%
  group_by(dat, singletons) %>%
  summarize(prop_high_singles = mean(high_singles),
            prop_high_singles_ex = mean(high_singles_ex),
            prop_low_singles = mean(low_singles),
            prop_low_singles_ex = mean(low_singles_ex),
            nsites= dplyr::n()) %>%
  ungroup()

```

<!-- ```{r} -->

<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons_mean, nsingletons)) + -->
<!--   geom_point(alpha = .2) + -->
<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
<!--     geom_line(aes(nsingletons_95, nsingletons_95)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->

<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons, nsingletons-nsingletons_95)) + -->
<!--   geom_point(alpha = .2) + -->
<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
<!--   facet_wrap(vars(dat), scales = "free") -->
<!-- ``` -->

### 2021-02-23 analysis/rev_prototyping/jackknife.Rmd
fia small jks

@@
 
-fia_to_jk <- sample(fia_sites$site, size = 100, replace = F)
+fia_to_jk <- sample(fia_sites$site, size = nrow(fia_sites), replace = F)
+
+fia_to_jk <- fia_to_jk[1:1000]
 
@@
 
-fia_small_to_jk <- sample(fia_small_sites$site, size = 100, replace = F)
+fia_small_to_jk <- sample(fia_small_sites$site, size = nrow(fia_small_sites), replace = F)
 
-fia_small <- filter(fia_small, site %in% fia_small)
+fia_small_to_jk <- fia_small_to_jk[1:1000]
+
+fia_small <- filter(fia_small, site %in% fia_small_to_jk)
 

### 2021-02-23 analysis/reports/manuscript_main.Rmd
jk results

--- 2021-01-14 analysis/reports/manuscript_main.Rmd
@@
 
-  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(skew_percentile_excl)) +
+  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(skew_percentile_excl)) +
     geom_histogram(bins = 100) +
@@
 
-  ggplot(filter(all_di, simpson_unique > 20), aes(simpson_percentile)) + 
+  ggplot(filter(all_di, nparts > 20), aes(simpson_percentile)) + 
     geom_histogram(bins = 100) +
@@
 fig_3 <- gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
+  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) +
     geom_histogram() +
@@
 
-  ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
+  ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) +
     geom_histogram() +
@@
 
-simpson_ks <- filter(sub_di, simpson_unique > 20) %>%
+simpson_ks <- filter(sub_di, nparts > 20) %>%
   select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>% 
@@
 
-skewness_ks <- filter(sub_di, skew_unique > 20) %>%
+skewness_ks <- filter(sub_di, nparts > 20) %>%
   select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>% 
@@
 fig_4 <- gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(sub_di, skew_unique > 20), aes(skew_95_ratio_1t)) +
+  ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) +
     geom_histogram()+
@@
 
-  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_95_ratio_1t)) +
+  ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) +
     geom_histogram()+
@@
 
-  ggplot(filter(sub_di, skew_unique > 20), aes(skew_percentile_excl)) +
+  ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) +
     geom_histogram()+
@@
 
-  ggplot(filter(sub_di, simpson_unique > 20), aes(simpson_percentile)) +
+  ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) +
     geom_histogram()+
@@
 ```{r}
-pdf("figure_1.pdf", title = "Figure 1")
-plot(fig_1)
+pdf("figure_1.pdf", title = "Figure 1", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white")))
 dev.off()
 
-pdf("figure_2.pdf", title = "Figure 2")
- plot(fig_2)
+pdf("figure_2.pdf", title = "Figure 2", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+ gridExtra::grid.arrange(grobs = list(
+
+  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(skew_percentile_excl)) +
+    geom_histogram(bins = 100) +
+    geom_vline(xintercept = 95, color = "red") +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") +
+    xlab("") +
+    ylab(""),# +
+  #  xlab("Percentile rank of observed value relative to feasible set") +
+    #ylab("Number of communities") ,
+
+  ggplot(filter(all_di, nparts > 20), aes(simpson_percentile)) + 
+    geom_histogram(bins = 100) +
+    geom_vline(xintercept = 5, color = "red") +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") + 
+    xlab("") +
+    ylab("")#+
+    #xlab("Percentile rank of observed value relative to feasible set") +
+  #  ylab("Number of communities")
+), ncol = 2,
+top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
  dev.off()
 
-pdf("figure_3.pdf", title = "Figure 3")
-plot(fig_3)
+pdf("figure_3.pdf", title = "Figure 3", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) +
+    geom_histogram() +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Skewness") +
+    xlim(0, 1),
+
+  ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) +
+    geom_histogram() +
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) +
+    xlab("") +
+    ylab("") +
+    ggtitle("Evenness") +
+    xlim(0, 1)
+), ncol = 2,
+top = textGrob("Figure 3", gp = gpar(fill = "white")),
+left = "Number of communities", 
+bottom = "Breadth index (ranges 0-1, with 1 being very broad)")
+
 dev.off()
 
-pdf("figure_4.pdf", title = "Figure 4")
- plot(fig_4)
+pdf("figure_4.pdf", title = "Figure 4", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+ gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Breadth index") +
+    ylab("Number of communities") +
+    ggtitle("Breadth index", subtitle = "Skewness"),
+
+  ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Breadth index") +
+    ylab("") +
+    ggtitle("", subtitle = "Evenness"),
+
+  ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Percentile rank") +
+    ylab("Number of communities") +
+    ggtitle("Percentile rank", subtitle = "Skewness"),
+
+  ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) +
+    geom_histogram()+
+    theme_bw() +
+    facet_wrap(vars(Dataset), scales = "free_y")  +
+    xlab("Percentile rank") +
+    ylab("")+
+    ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white")))
 dev.off()

### 2021-02-23 analysis/rev_prototyping/jacknife_results.Rmd
jk results

@@
 
-all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F) %>%
+  filter(n0 != s0,
+         s0 != 1,
+         !singletons,
+         n0 != (s0 + 1))
 
-jk_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
+jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
 
-jk_di <- jk_di %>%
+jk_di <- jk_di_full %>%
   group_by_all() %>%
@@
   ungroup() %>%
-  select(dat, site, site_source, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingeltons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
 
@@
   mutate(site_source = as.character(site)) %>%
-  select(dat, site_source, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
+  select(dat, site_source, s0, n0, skew_percentile_excl, skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons,nsingeltons_median,  nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
 
-colnames(all_di_actual)[ 3:19] <- paste0(colnames(all_di_actual)[ 3:19], "_actual")
+colnames(all_di_actual)[ 3:ncol(all_di_actual)] <- paste0(colnames(all_di_actual)[3:ncol(all_di_actual)], "_actual")
 
@@
          skew_sig = skew_percentile_excl > 95) %>%
-  mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig))
+  mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig)) %>%
+  filter(nparts > 20)
 
@@
 ```{r}
-ggplot(filter(jk_di_mean_results, s0 > 2), aes(skew_percentile_excl)) +
+ggplot(filter(jk_di_mean_results, s0 > 2, nparts > 20), aes(skew_percentile_excl)) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(filter(jk_di_mean_results, s0 > 2), aes(skew_percentile_excl_actual)) +
+ggplot(filter(jk_di_mean_results, s0 > 2, nparts > 20), aes(skew_percentile_excl_actual)) +
   geom_histogram(bins = 100) +
@@
 jk_di_mean_results  %>% 
- filter(s0 > 2) %>%
+  filter(s0 > 2, nparts > 20) %>%
   group_by(dat) %>%
@@
             prop_skew_high_raw = mean(skew_percentile_excl_actual > 95),
+            prop_skew_low_jk = mean(skew_percentile < 5),
+            prop_skew_low_raw = mean(skew_percentile_actual < 5),
             nsites_included = dplyr::n())
@@
 ```{r}
-ggplot(filter(jk_di_mean_results), aes(simpson_percentile)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(simpson_percentile)) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(filter(jk_di_mean_results), aes(simpson_percentile_actual)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(simpson_percentile_actual)) +
   geom_histogram(bins = 100) +
@@
   group_by(dat) %>%
-  summarize(prop_simpson_high_jk = mean(simpson_percentile < 5),
-            prop_simpson_high_raw = mean(simpson_percentile_actual < 5),
+  filter(nparts > 20) %>%
+  summarize(prop_simpson_high_jk = mean(simpson_percentile_excl > 95),
+            prop_simpson_high_raw = mean(simpson_percentile_excl_actual > 95),
+            prop_simpson_low_jk = mean(simpson_percentile< 5),
+            prop_simpson_low_raw = mean(simpson_percentile_actual < 5),
             nsites_included = dplyr::n())
@@
 ```{r}
-ggplot(filter(jk_di_mean_results), aes(shannon_percentile)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(shannon_percentile)) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(filter(jk_di_mean_results), aes(shannon_percentile_actual)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(shannon_percentile_actual)) +
   geom_histogram(bins = 100) +
@@
   group_by(dat) %>%
-  summarize(prop_shannon_high_jk = mean(shannon_percentile < 5),
-            prop_shannon_high_raw = mean(shannon_percentile_actual < 5),
+  filter(nparts > 20) %>%
+  summarize(prop_shannon_high_jk = mean(shannon_percentile > 95),
+            prop_shannon_high_raw = mean(shannon_percentile_actual > 95),
+            prop_shannon_low_jk = mean(shannon_percentile< 5),
+            prop_shannon_low_raw = mean(shannon_percentile_actual < 5),
             nsites_included = dplyr::n())
@@
 ```{r}
-ggplot(filter(jk_di_mean_results), aes(mean_po_comparison_percentile)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(mean_po_comparison_percentile)) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(filter(jk_di_mean_results), aes(mean_po_comparison_percentile_actual)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(mean_po_comparison_percentile_actual)) +
   geom_histogram(bins = 100) +
@@
   group_by(dat) %>%
+  filter(nparts > 20) %>%
   summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile > 95),
@@
 
-## Nsingletons
+<!-- ## Nsingletons -->
+
+<!-- ```{r} -->
+<!-- ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_excl)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   facet_wrap(vars(dat), scales = "free_y", ncol = 1) + -->
+<!--   geom_vline(xintercept = 95) -->
+
+<!-- ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_actual)) + -->
+<!--   geom_histogram(bins = 100) + -->
+<!--   facet_wrap(vars(dat), scales = "free_y", ncol = 1) + -->
+<!--   geom_vline(xintercept = 95) -->
+
+<!-- jk_di_mean_results  %>%  -->
+<!--   group_by(dat) %>% -->
+<!--   summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile > 95), -->
+<!--             prop_nsingletons_high_raw = mean(nsingletons_percentile_actual > 95), -->
+<!--             nsites_included = dplyr::n()) -->
+
+<!-- ``` -->
+
+## Nsingletons excl
+
+Visualization and analysis of nsingletons has a little more nuance than the others, because there are often relatively few values for nsingletons at all.
+80% of sites have fewer than 20 singletons as the 95th percentile, which is just a rough way of saying that a **lot** of these are going to be sensitive to whether you define the percentiles as > or >=.
+
+In general the strict > percentile will give you an (appropriately) conservative estimate of how many are extraordinarily **high** and the >= will give you an appropriate estimate of how many are unusually **low**.
+For most metrics it doesn't really matter, writ large, which you use, because ties are rare.
+For this one, you get large numbers of sites where a lot of values are = to the observed values, and the >= decision will therefore give you a jump of a lot of percentile scores.
+
+For the "proportions high/low" calculations, we use *the > percentile for high* and *the >= percentile for low*.
+For visualization, because we are interested in both unusually high and unusually low scores, we can't just pick one or the other.
+The histogram using >= is reliable at the high end but has a misleading spike at 0, and vice versa.
+I am making these plots using the *mean*, which doesn't have the misleading spikes at the extremes but does smear things out a little bit.
+
+```{r, fig.dim = c(5,5)}
+
+jk_di_mean_results <- jk_di_mean_results %>%
+  group_by_all() %>%
+  mutate(singletons_percentile_jump = nsingletons_percentile - nsingletons_percentile_excl,
+         singletons_percentile_jump_actual = nsingletons_percentile_actual - nsingletons_percentile_excl_actual,
+         nsingletons_percentile_mean = sum(nsingletons_percentile, nsingletons_percentile_excl) / 2,
+         nsingletons_percentile_mean_actual = sum(nsingletons_percentile_actual, nsingletons_percentile_excl_actual)/2) %>%
+  ungroup()
+
+```
 
 ```{r}
-ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_mean)) +
   geom_histogram(bins = 100) +
@@
 
-ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_actual)) +
+ggplot(filter(jk_di_mean_results, nparts > 20), aes(nsingletons_percentile_mean_actual)) +
   geom_histogram(bins = 100) +
@@
   group_by(dat) %>%
-  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile > 95),
-            prop_nsingletons_high_raw = mean(nsingletons_percentile_actual > 95),
+  filter(nparts > 20) %>%
+  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile_excl > 95),
+            prop_nsingletons_high_raw = mean(nsingletons_percentile_excl_actual > 95),
+         #   prop_nsingletons_mean_high_raw = mean(nsingletons_percentile_mean_actual > 95),
+      #      prop_nsingletons_mean_high_jk = mean(nsingletons_percentile_mean > 95),
+            prop_nsingletons_low_jk = mean(nsingletons_percentile < 5),
+            prop_nsingletons_low_raw = mean(nsingletons_percentile_actual  < 5),
             nsites_included = dplyr::n())
@@
 
-## Nsingletons excl
+<!-- ```{r, fig.dim = c(6,6)} -->
 
-```{r}
-ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_excl)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
-  geom_vline(xintercept = 95)
+<!-- jk_di_mean_results <- jk_di_mean_results %>% -->
+<!--  #select(-singletons_percentile_excl_high_insig, -singletons_percentile_low_insig) -->
+<!--   group_by_all() %>% -->
+<!--   mutate(prop_singletons = nsingletons / s0, -->
+<!--          prop_singletons_actual = nsingletons_actual / s0, -->
+<!--          singletons_percentile_high_change = paste0("actual", (nsingletons_percentile_excl_actual > 95), "_jk", (nsingletons_percentile_excl > 95)), -->
+<!--          singletons_percentile_low_change = paste0("actual", (nsingletons_percentile_actual <5), "_jk", (nsingletons_percentile < 5))) %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(prop_singletons_change = prop_singletons - prop_singletons_actual) -->
 
-ggplot(filter(jk_di_mean_results), aes(nsingletons_percentile_excl_actual)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
-  geom_vline(xintercept = 95)
+<!-- ggplot(jk_di_mean_results, aes(prop_singletons_actual, prop_singletons, color =singletons_percentile_high_change)) + geom_point() + geom_line(aes(prop_singletons_actual,prop_singletons_actual), inherit.aes = F) -->
 
-jk_di_mean_results  %>% 
-  group_by(dat) %>%
-  summarize(prop_nsingletons_high_jk = mean(nsingletons_percentile_excl > 95),
-            prop_nsingletons_high_raw = mean(nsingletons_percentile_excl_actual > 95),
-            nsites_included = dplyr::n())
+<!-- ggplot(jk_di_mean_results, aes(nsingletons_actual, nsingletons,color = singletons_percentile_high_change)) + geom_point() + geom_line(aes(nsingletons_actual,nsingletons_actual), inherit.aes = F) +facet_wrap(vars(dat), scales = "free") + theme(legend.position = "top") -->
 
-```
+<!-- ggplot(jk_di_mean_results, aes(s0,n0, color =  -->
+<!-- ggplot(jk_di_mean_results, aes(nsingletons_actual, nsingletons,color = singletons_percentile_high_change)) + geom_point() + geom_line(aes(nsingletons_actual,nsingletons_actual), inherit.aes = F) +facet_wrap(vars(dat), scales = "free") + theme(legend.position = "top") -->
+<!-- )) + geom_point() +scale_x_log10() +scale_y_log10() + -->
+<!--   facet_wrap(vars(dat), scales = "free") + -->
+<!--   theme(legend.position = "top") -->
+
+<!-- ggplot(jk_di_mean_results, aes(s0,n0, color = singletons_percentile_low_change)) + geom_point() +scale_x_log10() +scale_y_log10()+ -->
+<!--   facet_wrap(vars(dat), scales = "free") + -->
+<!--   theme(legend.position = "top") -->
+
+<!-- ggplot(jk_di_mean_results, aes(n0/s0, nsingletons_percentile_excl, color = singletons_percentile_high_change)) + geom_point()+ -->
+<!--   facet_wrap(vars(dat), scales = "free") + -->
+<!--   theme(legend.position = "top") -->
+<!-- ``` -->

### 2021-02-23 analysis/rev_prototyping/nsingletons.Rmd
jk results

@@
          Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
-         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
 
@@
   geom_histogram(bins = 100) +
-  facet_wrap(vars(dat, singletons), scales = "free_y") +
-  xlim(0, 100)
+  facet_wrap(vars(dat, singletons), scales = "free_y")
 

### 2021-02-24 analysis/rev_prototyping/nsingletons.Rmd
get fia jks and restart fia not jk runs

--- 2021-02-23 analysis/rev_prototyping/nsingletons.Rmd
@@
 
-all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
 
@@
 ```
+```{r}
 
-<!-- ```{r} -->
+all_di <- all_di %>%
+  mutate(singletons_change = (nsingletons - nsingletons_95) / s0)
 
-<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons_mean, nsingletons)) + -->
-<!--   geom_point(alpha = .2) + -->
-<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
-<!--     geom_line(aes(nsingletons_95, nsingletons_95)) + -->
-<!--   facet_wrap(vars(dat), scales = "free") -->
+ggplot(filter(all_di, high_singles_ex), aes(singletons_change)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free")
 
-<!-- ggplot(filter(all_di, nsingletons >= nsingletons_95), aes(nsingletons, nsingletons-nsingletons_95)) + -->
-<!--   geom_point(alpha = .2) + -->
-<!-- #  geom_line(aes(nsingletons_mean, nsingletons_mean)) + -->
-<!--   facet_wrap(vars(dat), scales = "free") -->
-<!-- ``` -->
+all_di %>%
+  filter(high_singles_ex) %>%
+  group_by(dat) %>%
+  summarize(mean_singles_change = mean(singletons_change),
+            n = dplyr::n())
+
+```

### 2021-02-24 analysis/helper_scripts/make_all_di_jk.R

@@ -7,7 +7,7 @@ library(scadsanalysis)
 
 all_di <- list()
 #datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "fia_small")
-datasets <- c( "gentry-jk", "mcdb-jk", "bbs-jk","misc-jk" )
+datasets <- c( "gentry-jk", "mcdb-jk", "bbs-jk","misc-jk", "fia_small-jk", "fia_short-jk" )
 
 
 

### 2021-02-24 analysis/reports/table_1.Rmd
add HY figure and text edits. add algo from ha0ye/feasiblesads, rerendered to match formatting. renumber supplement files, note that they are NOT CORRECTLY NUMBERED in the reports directory but ARE CORRECT in manuscript/Supp

--- 2020-12-18 analysis/reports/table_s4.Rmd
@@
 
-# Table S4
+# Table 1
 
@@
 overall_skew_results <- all_di %>%
-  filter(s0 > 2, skew_unique > 20) %>%
+  filter(s0 > 2, nparts > 20) %>%
   mutate(high_skew = skew_percentile_excl > 95) %>%
@@
 overall_simpson_results <- all_di %>%
-  filter(simpson_unique > 20) %>%
+  filter(nparts > 20) %>%
   mutate(low_even = simpson_percentile < 5) %>%

### 2021-02-24 analysis/rev_prototyping/old/shannon.Rmd

--- 2021-02-13 analysis/rev_prototyping/shannon.Rmd
@@
 
-all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)
 
@@
   facet_wrap(vars(Dataset))
+
+ggplot(all_di, aes(n0/s0, shannon_percentile, color = shannon_cat)) +
+  theme_bw()+
+  scale_x_log10() +
+    geom_point()+
+  facet_wrap(vars(Dataset), scales = "free")
 ```

### 2021-02-24 analysis/rev_prototyping/jacknife_results.Rmd
fia results

@@
 
+```{r, fig.dim = c(8,8)}
+
+fia_max_n = 150
+fia_max_s = 21
+
+ggplot(jk_di_mean_results, aes(s0, n0, color = dat)) +
+  geom_point(aes(s0_actual, n0_actual), color = "grey", alpha  = .2)+
+    geom_point(aes(s0, n0, color = dat), alpha = .5) +
+  theme_bw() +
+  scale_x_log10() +
+  scale_y_log10() +
+  facet_wrap(vars(dat)) +
+  geom_vline(xintercept = fia_max_s) +
+  geom_hline(yintercept = fia_max_n) +
+  theme(legend.position = "top")
+
+jk_di_mean_results <- jk_di_mean_results %>%
+  group_by_all() %>%
+  mutate(fiasized = (s0 <= fia_max_s) && (n0 <= fia_max_n),
+         fiasized_acutal =(s0_actual <= fia_max_s) && (n0_actual <= fia_max_n) ) %>%
+  ungroup()
+
+jk_di_mean_results %>%
+  group_by(dat) %>%
+  summarize(jk_small = mean(fiasized), actual_small = mean(fiasized_acutal), nsites = dplyr::n())
+
+jk_di_mean_results %>%
+  group_by(dat, fiasized) %>%
+  summarize( nsingletons_high  = mean(nsingletons_percentile_excl > 95), nsites = dplyr::n())
+
+```
 <!-- ```{r, fig.dim = c(6,6)} -->

### 2021-02-24 analysis/rev_prototyping/rarefaction.Rmd
some updates to di

---
title: "Effects of rarefaction"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

all_di <- all_di %>%
   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))
```

It is often not possible to exhaustively sample all the species and individuals present in a real system. Therefore empirical observations of SADs may be missing species and individuals that are part of the true distribution.

We explored whether our results change if we adjust for for the species and individuals that might be missed via sampling. We used species richness estimators to estimate the true number of species for a community given the observed SAD, and re-ran our analytical pipeline on SADs adjusted to match the estimated richness.

### Adjusting for rarefaction

For an observed SAD, we take the estimated species richness from the bias-corrected Chao and ACE estimators (as implemented in `vegan::estimateR`) as the estimated "true" number of species in the community. To err on the side of overestimating the number of species missed via sampling, we used the estimated mean + 1 standard deviation as the estimate for each estimator. We take the mean of these two estimates, rounded up to the next integer, as the estimated true richness for that community. We adjusted the raw SAD to match this estimated richness by adding the appropriate number of species with an abundance of 1 individual each. We reason that species that are missed during sampling are likely to be rare, so adding them as rare species is appropriate. This also allows us to explore the effects of rarefaction while making the smallest possible changes to S and N.

```{r show an observed vector and adjusted for singletons}

dat <- load_dataset("mcdb")
dat <- dat %>%
  dplyr::filter(site == "1010")

dat$rank <- nrow(dat):1

dats <- add_singletons(dat, use_max = T)

dats$rank <- nrow(dats):1

dat_combined <- bind_rows(dat, dats) %>%
  mutate(adjusted = ifelse(singletons, "adjustment", "raw"))

ggplot(dat_combined, aes(x = rank, y = abund, color =adjusted)) +
  geom_point() +
  geom_point(data = filter(dat_combined, !singletons)) + 
  geom_line() +
  theme_bw() +
  scale_color_viridis_d(end = .8, direction = -1) +
  theme(legend.position = "top") +
  ggtitle("Raw and adjusted SADs")

```

The green points are the species we added to match the estimated species richness for the raw SAD (purple points).

### Adjusted vs. raw results

```{r skew}

adjusted_comparison <- all_di %>%
  select(dat, site, singletons, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile_excl, nsingletons_percentile, mean_po_comparison_percentile, log_nparts) %>%
  tidyr::pivot_wider(id_cols = c(dat, site), names_from = singletons, values_from = c(s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile_excl, nsingletons_percentile, mean_po_comparison_percentile, log_nparts))

overall_skew_results <- adjusted_comparison %>%
  filter(s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20) %>%
  mutate(high_skew_raw = skew_percentile_excl_FALSE > 95,
         high_skew_adjusted = skew_percentile_excl_TRUE > 95) %>%
  group_by(dat) %>%
  summarize(proportion_skew_high_raw = mean(high_skew_raw),
            proportion_skew_high_adjusted = mean(high_skew_adjusted),
            nsites_skew = dplyr::n())

overall_simpson_results <- adjusted_comparison %>%
   filter(simpson_unique_TRUE > 20, simpson_unique_FALSE > 20) %>%
  mutate(low_simpson_raw = simpson_percentile_FALSE < 5,
         low_simpson_adjusted = simpson_percentile_TRUE < 5) %>%
  group_by(dat) %>%
  summarize(proportion_simpson_low_raw = mean(low_simpson_raw),
            proportion_simpson_low_adjusted = mean(low_simpson_adjusted),
            nsites_simpson = dplyr::n())

overall_results <- left_join(overall_skew_results, overall_simpson_results)

ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat))

overall_skew_results

ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green")

ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
  geom_point(alpha = .1) +
  theme_bw() +
  geom_abline(intercept = 0, slope = 1, color = "green") +
  facet_wrap(vars(dat)) 
overall_simpson_results
```

In all cases, adjusting for rarefaction increases the proportion of extreme values. Most adjusted SADs have more extreme values than their non-adjusted counterparts.

This makes sense given that we add species at low abundance (and are more likely to fail to observe rare species). Adding rare species would tend to increase skewness and decrease evenness.

If anything, missing species due to the limitations on empirical sampling causes us to **underestimate** the extreme-ness of observed SADs relative to their feasible sets.

### 2021-02-24 R/metrics.R

@@ -18,15 +18,37 @@ add_dis <- function(fs_samples_df, sim_props_off = NULL, props_comparison = NULL
     return(NA)
   }
 
-  groupvars <- colnames(fs_samples_df)[ which(!(colnames(fs_samples_df) %in% c("abund", "rank")))]
-
-  if("observed" %in% fs_samples_df$source) {
-
-    actual <- dplyr::filter(fs_samples_df, sim < 0)
-
-  } else {
-    actual <- dplyr::filter(fs_samples_df, sim == min(fs_samples_df$sim, na.rm  = T))
+  if(fs_samples_df$dat[1] == "net") {
+    fs_samples_df <- fs_samples_df %>%
+      dplyr::filter(!is.na(sim))
   }
+
+  groupvars <- colnames(fs_samples_df)[ which(!(colnames(fs_samples_df) %in% c("abund", "rank")))]
+#
+#   if("observed" %in% fs_samples_df$source) {
+#
+#     actual <- dplyr::filter(fs_samples_df, sim < 0)
+#
+#
+#     sim_dis <- fs_samples_df %>%
+#       dplyr::group_by_at(.vars = groupvars) %>%
+#       dplyr::summarize(skew = e1071::skewness(abund),
+#                        shannon = vegan::diversity(abund, index = "shannon", base = exp(1)),
+#                        simpson = vegan::diversity(abund, index = "simpson"),
+#                        nsingletons = sum(abund == 1),
+#                        prop_off_actual = proportion_off(t(cbind(actual$abund, abund)))) %>%
+#       dplyr::ungroup()
+#
+#   } else {
+#
+#     sim_dis <- fs_samples_df %>%
+#       dplyr::group_by_at(.vars = groupvars) %>%
+#       dplyr::summarize(skew = e1071::skewness(abund),
+#                        shannon = vegan::diversity(abund, index = "shannon", base = exp(1)),
+#                        simpson = vegan::diversity(abund, index = "simpson"),
+#                        nsingletons = sum(abund == 1),
+#                        prop_off_actual = proportion_off(t(cbind(actual$abund, abund)))) %>%
+#       dplyr::ungroup()  }
 
   if(is.null(props_comparison)) {
 
@@ -35,15 +57,15 @@ add_dis <- function(fs_samples_df, sim_props_off = NULL, props_comparison = NULL
   }
 
 
+
   sim_dis <- fs_samples_df %>%
[…]

### 2021-02-24 analysis/rev_prototyping/rarefaction.Rmd
fix pipeline

@@
 
-overall_skew_results <- adjusted_comparison %>%
-  filter(s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20) %>%
+overall_results <- adjusted_comparison %>%
+  filter(s0_FALSE > 2, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)) %>%
   mutate(high_skew_raw = skew_percentile_excl_FALSE > 95,
-         high_skew_adjusted = skew_percentile_excl_TRUE > 95) %>%
+         high_skew_adjusted = skew_percentile_excl_TRUE > 95,
+         low_even_raw = simpson_percentile_FALSE < 5,
+         low_even_adjusted = simpson_percentile_TRUE < 5,
+         low_shannon_raw = shannon_percentile_FALSE <5,
+         low_shannon_adjusted = shannon_percentile_TRUE < 5,
+         high_singletons_raw = nsingletons_percentile_excl_FALSE > 95,
+         high_singletons_adjusted = nsingletons_percentile_excl_TRUE > 95,
+         low_singletons_raw = nsingletons_percentile_FALSE < 5,
+         low_singletons_adjusted = nsingletons_percentile_TRUE < 5,
+         high_po_raw = mean_po_comparison_percentile_FALSE > 95,
+         high_po_adjusted = mean_po_comparison_percentile_TRUE > 95)
+
+summary_vars <- colnames(overall_results)[ c(which(grepl("raw", colnames(overall_results))), which(grepl("adjusted", colnames(overall_results))))]
+
+overall_results <- overall_results %>%
   group_by(dat) %>%
-  summarize(proportion_skew_high_raw = mean(high_skew_raw),
-            proportion_skew_high_adjusted = mean(high_skew_adjusted),
-            nsites_skew = dplyr::n())
+  summarize_at(summary_vars, mean)
 
-overall_simpson_results <- adjusted_comparison %>%
-   filter(simpson_unique_TRUE > 20, simpson_unique_FALSE > 20) %>%
-  mutate(low_simpson_raw = simpson_percentile_FALSE < 5,
-         low_simpson_adjusted = simpson_percentile_TRUE < 5) %>%
-  group_by(dat) %>%
-  summarize(proportion_simpson_low_raw = mean(low_simpson_raw),
-            proportion_simpson_low_adjusted = mean(low_simpson_adjusted),
-            nsites_simpson = dplyr::n())
+# overall_simpson_results <- adjusted_comparison %>%
+#    filter(log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)) %>%
+#   mutate(low_simpson_raw = simpson_percentile_FALSE < 5,
+#          low_simpson_adjusted = simpson_percentile_TRUE < 5) %>%
+#   group_by(dat) %>%
+#   summarize(proportion_simpson_low_raw = mean(low_simpson_raw),
+#             proportion_simpson_low_adjusted = mean(low_simpson_adjusted),
+#             nsites_simpson = dplyr::n())
+# 
+# overall_results <- left_join(overall_skew_results, overall_simpson_results)
 
-overall_results <- left_join(overall_skew_results, overall_simpson_results)
+overall_results
 
-ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
+ggplot(filter(adjusted_comparison, s0_FALSE > 2, log_nparts_TRUE > log(20), log_nparts_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
   geom_point(alpha = .1) +
@@
 
-ggplot(filter(adjusted_comparison, s0_FALSE > 2, skew_unique_TRUE > 20, skew_unique_FALSE > 20), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
+ggplot(filter(adjusted_comparison, s0_FALSE > 2, log_nparts_TRUE > 20, log_nparts_FALSE > log(20)), aes(skew_percentile_excl_FALSE, skew_percentile_excl_TRUE)) +
   geom_point(alpha = .1) +
@@
 
-overall_skew_results
-
-ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
   geom_point(alpha = .1) +
@@
 
-ggplot(filter(adjusted_comparison, simpson_unique_TRUE > 20, simpson_unique_FALSE > 20), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(simpson_percentile_FALSE, simpson_percentile_TRUE)) +
   geom_point(alpha = .1) +
@@
   facet_wrap(vars(dat))
-overall_simpson_results
+
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(shannon_percentile_FALSE, shannon_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green")
+
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(shannon_percentile_FALSE, shannon_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  facet_wrap(vars(dat))
+
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(nsingletons_percentile_excl_FALSE, nsingletons_percentile_excl_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green")
+
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(nsingletons_percentile_excl_FALSE, nsingletons_percentile_excl_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  facet_wrap(vars(dat))
+
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green")
+
+ggplot(filter(adjusted_comparison, log_nparts_TRUE > log(20), log_nparts_FALSE > log(20)), aes(mean_po_comparison_percentile_FALSE, mean_po_comparison_percentile_TRUE)) +
+  geom_point(alpha = .1) +
+  theme_bw() +
+  geom_abline(intercept = 0, slope = 1, color = "green") +
+  facet_wrap(vars(dat))
+
 ```

### 2021-02-24 analysis/mcdb_pipeline.R

@@ -27,8 +27,8 @@ all <- drake_plan(
   fs = target(sample_fs_wrapper(dataset = dat_s_dat_mcdb, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = mamm_p, seed = !!sample.int(10^6, size = 1)),
               transform = cross(s = !!sites_list$site,
                                 singletons = !!c(TRUE, FALSE))),
-   fs_diffs = target(get_fs_diffs(fs),
-                     transform = map(fs)),
+  # fs_diffs = target(get_fs_diffs(fs),
+  #                   transform = map(fs)),
   fs_pc = target(compare_props_fs(fs),
                  transform = map(fs)),
   di = target(add_dis(fs, props_comparison = fs_pc),
@@ -66,7 +66,7 @@ if(grepl("ufhpc", nodename)) {
        cache_log_file = here::here("analysis", "drake", "cache_log_mcdb.txt"),
        verbose = 1,
        parallelism = "clustermq",
-       jobs = 20,
+       jobs = 100,
        caching = "master",
       memory_strategy = "autoclean",
       garbage_collection = TRUE) # Important for DBI caches!

### 2021-02-24 analysis/rev_prototyping/additional_metrics_results.Rmd
some updates to di
run

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, fig.dim =c(6,6))
 library(drake)
@@
 
+mcdb_new_di <-read.csv(here::here("mcdb_new_di.csv"))
+
 all_di <- all_di %>%
@@
          s0 != n0,
-         n0 != s0 + 1)
+         n0 != s0 + 1,
+         !singletons)
 
@@
 
+Defined as the proportion of individuals allocated to species of different abundances. Most intuitive as a graph - here are two hypothetical SADs for a community with 7 species and 71 individuals:
+
 ```{r}
 
-ggplot(filter(all_di), aes(mean_po_comparison_percentile)) +
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE)
+
+example_fs <- readd(fs_s_7_n_71, cache = cache) %>%
+  filter(sim %in% c(1, 2)) %>%
+  mutate(sim = paste0("sim_", sim))
+
+example_fs_wide <- example_fs %>%
+  select(sim, abund, rank) %>%
+  tidyr::pivot_wider(id_cols = rank, names_from = sim, values_from = abund)
+
+ggplot(example_fs_wide, aes(rank, sim_1)) +
+  geom_point() +
+  geom_line() +
+  geom_point(aes(rank, sim_2), color = "blue") +
+  geom_line(aes(rank, sim_2), color = "blue") +
+  geom_ribbon(aes(rank, ymin = sim_1, ymax = sim_2), fill = "grey", alpha = .2) +
+  ylab("abund")
+```
+
+We take the grey area - the area of difference between the two SADs - and divide it by 2 (because every individual allocated to a different species will count twice), and divide that total by the total number of individuals in the community.
+In principle this metric ranges from 0 to 1, with 0 being no individuals allocated differently and 1 being all individuals allocated differently, although note that neither 0 nor 1 can actually be achieved.
+
+Here are those calculations:
+
+```{r, echo = T}
+(sum(abs(example_fs_wide$sim_1 - example_fs_wide$sim_2)) / 2) / sum(example_fs_wide$sim_1)
+
+fs_mat <- select(example_fs_wide, sim_1, sim_2) %>% t()
+
+scadsanalysis::proportion_off(fs_mat)
+
+```
+
+This is a metric of dissimiliarty defined for *two* focal vectors.
+We want to know whether the observed SAD is more unlike the elements of its feasible set than the elements of the feasible set are unlike each other.
+To do this, we calculate the proportion off between the observed SAD and a large number of samples from the feasible set, and take the mean score of all these comparisons.
+This tells us how different, on average, the observed SAD is from samples.
+We then repeat this process many times, but instead of the observed SAD we select a random sample from the feasible set as focal sample, compare this focal sample to many other samples, and take the mean.
+The distribution of these scores can then be compared directly to the score from the observed sample.
+
+```{r}
+ggplot(filter(all_di, nparts > 20), aes(mean_po_comparison_percentile)) +
   geom_histogram() +
@@
 
-all_di %>% group_by(singletons, dat) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))
+all_di %>% filter(nparts >20) %>% group_by(singletons, dat) %>% summarize(high_proportion_off = mean(mean_po_comparison_percentile > 95))
 
-ggplot(all_di, aes(mean_po_comparison_95, mean_po_comparison, color = log(nparts))) +
-  geom_point() +
-  geom_line(aes(mean_po_comparison_95, mean_po_comparison_95))
+```
+
+Because the units for this metric do not depend on S and N, we can also estimate the effect size as the difference in the proportion off between the observed SAD compared to the feasible set and the proportion off for elements of the feasible set compared to each other.
+
+Looking at those communities where the observed SAD is much more unlike the elements of the feasible set, than the elements of the FS are unlike each other, we can ask how much *more* dissimilar the SAD is than the 95th percentile of unlikeness from the feasible set:
+
+```{r}
 
@@
   filter(mean_po_comparison_percentile > 95) %>%
-  group_by(singletons) %>%
-  summarize(diff = mean(mean_po_comparison - mean_po_comparison_95))
+  group_by(singletons, dat) %>%
+  summarize(diff_from_95 = mean(mean_po_comparison - mean_po_comparison_95))
 
-ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t)) +
-  geom_point() +
-  scale_x_log10()
-
-ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t)) +
-  geom_point() +
-  scale_x_log10() +
-  xlim(0, 10000)
+ggplot(filter(all_di, mean_po_comparison_percentile > 95), aes( mean_po_comparison - mean_po_comparison_95)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y")
 
@@
 
+That is, e.g. for BBS, the significant deviation is that the observed-to-FS dissimilarity is on average .07 higher than the 95th percentile of FS-to-FS dissimilarity.
+
+We can examine how a one-tailed 95% breadth index changes over the size of the feasible set:
+
 ```{r}
 
-ggplot(all_di, aes(mean_po_comparison_sims, mean_po_comparison, color = mean_po_comparison_percentile > 95)) +
-  geom_point(alpha = .3) +
-  facet_wrap(vars(dat, singletons))
-
-ggplot(all_di, aes(mean_po_comparison - mean_po_comparison_sims, color = mean_po_comparison_percentile > 95)) +
-  geom_histogram(alpha = .3) +
-  facet_wrap(vars(dat, singletons))
+ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t, color = dat)) +
+  geom_point(alpha= .2) +
+  scale_x_log10() +
+  theme(legend.position = "top")
+# 
+# 
+# ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t, color = dat)) +
+#   geom_point(alpha= .8) +
+#   scale_x_log10() +
+#   xlim(c(0, 30000))+
+#   theme(legend.position = "top")
+# 
+# 
+# ggplot(all_di, aes(nparts, mean_po_comparison_95_ratio_1t, color = dat)) +
+#   geom_point(alpha= .8) +
+#   scale_x_log10() +
+#   xlim(c(0, 2000))+
+#   theme(legend.position = "top")
 
 ```
+
+<!-- Or we can ask what the difference in dissimilarity scores is on average: -->
+
+<!-- ```{r} -->
+<!-- all_di %>% -->
+<!--   group_by(singletons, dat) %>% -->
+<!--   summarize(mean_actual = mean(mean_po_comparison), -->
+<!--             mean_sims = mean(mean_po_comparison_sims), -->
+<!--             mean_diff = mean(mean_po_comparison - mean_po_comparison_sims)) -->
+
+<!-- ggplot(filter(all_di), aes(mean_po_comparison_sims, mean_po_comparison, color =  mean_po_comparison_percentile > 95)) + -->
+<!--   geom_point() + -->
+<!--   facet_wrap(vars(dat)) + -->
+<!--   geom_abline(slope = 1, intercept = 0) + -->
+<!--   theme(legend.position = "top") -->
+<!-- #  -->
+<!-- # po_long <- all_di %>% -->
+<!-- #   select(dat, singletons, mean_po_comparison, mean_po_comparison_sims) %>% -->
+<!-- #   tidyr::pivot_longer(cols = c("mean_po_comparison", "mean_po_comparison_sims"), names_to = "comp", values_to = "val")  %>% -->
+<!-- #   mutate(source = ifelse(grepl("sims", comp), "fs_to_fs", "obs_to_fs")) -->
+<!-- #  -->
+<!-- # ggplot(po_long, aes(source, val)) + -->
+<!-- #   geom_boxplot() + -->
+
+<!-- ggplot(filter(all_di), aes( mean_po_comparison - mean_po_comparison_sims)) + -->
+<!--   geom_histogram() + -->
+<!--   facet_wrap(vars(dat), scales = "free_y") -->
+
+<!-- ``` -->
+
+<!-- ```{r} -->
+
+<!-- ggplot(all_di, aes(mean_po_comparison_sims, mean_po_comparison, color = mean_po_comparison_percentile > 95)) + -->
+<!--   geom_point(alpha = .3) + -->
+<!--   facet_wrap(vars(dat, singletons)) -->
+
+<!-- ggplot(all_di, aes(mean_po_comparison - mean_po_comparison_sims, color = mean_po_comparison_percentile > 95)) + -->
+<!--   geom_histogram(alpha = .3) + -->
+<!--   facet_wrap(vars(dat, singletons)) -->
+
+<!-- ``` -->
 

### 2021-02-24 analysis/fia_pipeline.R

@@ -67,7 +67,7 @@ if(grepl("ufhpc", nodename)) {
        cache_log_file = here::here("analysis", "drake", "cache_log_fia.txt"),
        verbose = 1,
        parallelism = "clustermq",
-       jobs = 50,
+       jobs = 100,
        caching = "master",
        memory_strategy = "autoclean",
        garbage_collection = TRUE) # Important for DBI caches!

### 2021-02-24 analysis/gentry_pipeline.R

@@ -66,7 +66,7 @@ if(grepl("ufhpc", nodename)) {
        cache_log_file = here::here("analysis", "drake", "cache_log_gentry.txt"),
        verbose = 1,
        parallelism = "clustermq",
-       jobs = 20,
+       jobs = 100,
        caching = "master",
        memory_strategy = "autoclean",
        garbage_collection = TRUE) # Important for DBI caches!

### 2021-02-24 analysis/miscabund_pipeline.R

@@ -67,7 +67,7 @@ if(grepl("ufhpc", nodename)) {
        cache_log_file = here::here("analysis", "drake", "cache_log_miscabund.txt"),
        verbose = 1,
        parallelism = "clustermq",
-       jobs = 20,
+       jobs = 100,
        caching = "master",
        memory_strategy = "autoclean",
        garbage_collection = TRUE) # Important for DBI caches!

### 2021-02-24 analysis/rev_prototyping/additional_metrics_results.Rmd
im tird

@@
 
-That is, e.g. for BBS, the significant deviation is that the observed-to-FS dissimilarity is on average .07 higher than the 95th percentile of FS-to-FS dissimilarity.
+That is, e.g.
+for BBS, the significant deviation is that the observed-to-FS dissimilarity is on average .07 higher than the 95th percentile of FS-to-FS dissimilarity.
+I am not 100% sure that this is the best way to make this comparison....
 
@@
 
-<!-- Or we can ask what the difference in dissimilarity scores is on average: -->
-
-<!-- ```{r} -->
-<!-- all_di %>% -->
-<!--   group_by(singletons, dat) %>% -->
-<!--   summarize(mean_actual = mean(mean_po_comparison), -->
-<!--             mean_sims = mean(mean_po_comparison_sims), -->
-<!--             mean_diff = mean(mean_po_comparison - mean_po_comparison_sims)) -->
-
-<!-- ggplot(filter(all_di), aes(mean_po_comparison_sims, mean_po_comparison, color =  mean_po_comparison_percentile > 95)) + -->
-<!--   geom_point() + -->
-<!--   facet_wrap(vars(dat)) + -->
-<!--   geom_abline(slope = 1, intercept = 0) + -->
-<!--   theme(legend.position = "top") -->
-<!-- #  -->
-<!-- # po_long <- all_di %>% -->
-<!-- #   select(dat, singletons, mean_po_comparison, mean_po_comparison_sims) %>% -->
-<!-- #   tidyr::pivot_longer(cols = c("mean_po_comparison", "mean_po_comparison_sims"), names_to = "comp", values_to = "val")  %>% -->
-<!-- #   mutate(source = ifelse(grepl("sims", comp), "fs_to_fs", "obs_to_fs")) -->
-<!-- #  -->
-<!-- # ggplot(po_long, aes(source, val)) + -->
-<!-- #   geom_boxplot() + -->
-
-<!-- ggplot(filter(all_di), aes( mean_po_comparison - mean_po_comparison_sims)) + -->
-<!--   geom_histogram() + -->
-<!--   facet_wrap(vars(dat), scales = "free_y") -->
-
-<!-- ``` -->
-
-<!-- ```{r} -->
-
-<!-- ggplot(all_di, aes(mean_po_comparison_sims, mean_po_comparison, color = mean_po_comparison_percentile > 95)) + -->
-<!--   geom_point(alpha = .3) + -->
-<!--   facet_wrap(vars(dat, singletons)) -->
-
-<!-- ggplot(all_di, aes(mean_po_comparison - mean_po_comparison_sims, color = mean_po_comparison_percentile > 95)) + -->
-<!--   geom_histogram(alpha = .3) + -->
-<!--   facet_wrap(vars(dat, singletons)) -->
-
-<!-- ``` -->
-
 ## Number of singletons

### 2021-02-24 analysis/rev_prototyping/old/shannon.Rmd
im tird

@@
          !singletons,
-         n0 != (s0 + 1)) %>%
+         n0 != (s0 + 1),
+         nparts > 20) %>%
   mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),

### 2021-02-25 analysis/rev_prototyping/additional_metrics_results.Rmd

@@
 
-mcdb_new_di <-read.csv(here::here("mcdb_new_di.csv"))
-
 all_di <- all_di %>%
-  filter(s0 > 1,
-         s0 != n0,
-         n0 != s0 + 1,
-         !singletons)
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 != s0,
+         s0 != 1,
+         !singletons,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
 
 ```
+
+All of these currently exclude FIA because those are still running.
 
@@
 
+Visualization and analysis of nsingletons has a little more nuance than the others, because there are often relatively few values for nsingletons at all.
+80% of sites have fewer than 20 singletons as the 95th percentile, which is just a rough way of saying that a **lot** of these are going to be sensitive to whether you define the percentiles as > or >=.
+
+In general the strict > percentile will give you an (appropriately) conservative estimate of how many are extraordinarily **high** and the >= will give you an appropriate estimate of how many are unusually **low**.
+For most metrics it doesn't really matter, writ large, which you use, because ties are rare.
+For this one, you get large numbers of sites where a lot of values are = to the observed values, and the >= decision will therefore give you a jump of a lot of percentile scores.
+
+For the "proportions high/low" calculations, we use *the > percentile for high* and *the >= percentile for low*.
+For visualization, because we are interested in both unusually high and unusually low scores, we can't just pick one or the other.
+The histogram using >= is reliable at the high end but has a misleading spike at 0, and vice versa.
+I am making these plots using the *mean*, which doesn't have the misleading spikes at the extremes but does smear things out a little bit.
+
+```{r, fig.dim = c(5,5)}
+
+nsingletons_results <- all_di %>%
+  group_by_all() %>%
+  mutate(singletons_percentile_jump = nsingletons_percentile - nsingletons_percentile_excl,
+         nsingletons_percentile_mean = sum(nsingletons_percentile, nsingletons_percentile_excl) / 2) %>%
+  ungroup() %>%
+  mutate(prop_singles_actual = nsingletons / s0,
+         sim_prop_singles_95 = nsingletons_95 / s0,
+         sim_prop_singles_mean = nsingletons_mean / s0) %>%
+  mutate(actual_minus_95_prop = prop_singles_actual - sim_prop_singles_95) %>%
+  mutate(high_singles=nsingletons_percentile > 95,
+         high_singles_ex = nsingletons_percentile_excl > 95,
+         low_singles = nsingletons_percentile < 5,
+         low_singles_ex = nsingletons_percentile_excl < 5) %>%
+  mutate(singles_desc = ifelse(high_singles_ex, "high", ifelse(low_singles, "low", "int")))
+
+```
+
+BBS, MCDB, and Misc have too many rare species, while Gentry has too few:
+
+```{r}
+ggplot(filter(nsingletons_results, nparts > 20), aes(nsingletons_percentile_mean)) +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
+  geom_vline(xintercept = 95)
+
+nsingletons_results  %>% 
+  group_by(dat) %>%
+  filter(nparts > 20) %>%
+  summarize(            prop_nsingletons_high_raw = mean(nsingletons_percentile_excl > 95),
+         #   prop_nsingletons_mean_high_raw = mean(nsingletons_percentile_mean_actual > 95),
+      #      prop_nsingletons_mean_high_jk = mean(nsingletons_percentile_mean > 95),
+            prop_nsingletons_low_raw = mean(nsingletons_percentile  < 5),
+            nsites_included = dplyr::n())
+
+```
+
+_Of sites where the nsingletons value is extreme_, we're looking at - for example, in MCDB - an increase of .2 in the proportion of singleton species in the observed vector over the 95th percentile of scores for the proportion of singleton species for the feasible set:
+
+```{r}
+
+nsingletons_results <- nsingletons_results %>%
+  mutate(singletons_change = (nsingletons - nsingletons_95) / s0)
+
+ggplot(filter(nsingletons_results, high_singles_ex), aes(singletons_change)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free")
+
+nsingletons_results %>%
+  filter(high_singles_ex) %>%
+  group_by(dat) %>%
+  summarize(mean_singles_change = mean(singletons_change),
+            n = dplyr::n())
+
+```
+
+Broken out by N/S, you can see that the low values are concentrated in the Gentry where N/S < 3, and that high values are most common as N/S > 10:
+
+```{r}
+
+ggplot(nsingletons_results, aes(n0/s0, nsingletons_percentile_excl, color = singles_desc)) +
+  geom_point(data = filter(nsingletons_results, singles_desc != "int")) +
+  geom_point(alpha = .1, color = "grey") +
+  facet_wrap(vars(dat), scales = "free") +
+  scale_x_log10() +
+  geom_vline(xintercept = c(3, 10))
+
+```
+
+For N/S < 3:
+
+```{r}
+nsingletons_results %>%
+  filter(n0/s0 < 3) %>%
+  group_by(dat, singletons) %>%
+  summarize(
+            prop_high_singles_ex = mean(high_singles_ex),
+            prop_low_singles = mean(low_singles),
+            nsites= dplyr::n()) %>%
+  ungroup()
+
+```
+
+For N/S  > 10:
+
+```{r}
+
+nsingletons_results %>%
+  filter(n0/s0 > 10) %>%
+  group_by(dat, singletons) %>%
+  summarize(
+            prop_high_singles_ex = mean(high_singles_ex),
+            prop_low_singles = mean(low_singles),
+            nsites= dplyr::n()) %>%
+  ungroup()
+
+```
+
+Working on a breadth index here (stuff needs to run).
+
 ## Shannon diversity
+
+Most datasets have very low Shannon diversity, except for Gentry:
+
+```{r}
+
+ggplot(filter(all_di, nparts > 20), aes(shannon_percentile)) +
+  geom_histogram(bins = 100) +
+  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
+  geom_vline(xintercept = 5)
+
+all_di  %>% 
+  group_by(dat) %>%
+  filter(nparts > 20) %>%
+  summarize(
+            prop_shannon_high_raw = mean(shannon_percentile > 95),
+            prop_shannon_low_raw = mean(shannon_percentile < 5),
+            nsites_included = dplyr::n())
+```
+
+Working on the breadth index (stuff needs to run).

### 2021-02-25 analysis/rev_prototyping/additional_metrics_results.Rmd
breadth indices

@@
 
-Working on a breadth index here (stuff needs to run).
+Breadth index - note use of 2 tailed because of interest in low numbers of singletons for Gentry.
+
+I haven't fully groked the breadth index, but I think...
+
+- It declines with increasing size of the feasible set, but not as dramatically as the other indices.
+- The Gentry region (low N/S tail on the right) is not remarkable for the size of the FS or the (2-tailed) breadth index, but has an extremely high median propotion of singletons.
+
+```{r}
+
+ggplot(all_di, aes(nparts, nsingletons_95_ratio_2t, color = dat)) +
+  geom_point(alpha = .3) +
+  scale_x_log10()
+
+# 
+# ggplot(all_di, aes(s0, n0, color = nsingletons_95_ratio_2t)) +
+#   geom_point(alpha = .3) +
+#   scale_x_log10() +
+#   scale_y_log10() +
+#   scale_color_viridis_c()
+# 
+# 
+# ggplot(all_di, aes(n0/s0, nsingletons_95_ratio_2t, color = dat)) +
+#   geom_point(alpha = .3) +
+#   scale_x_log10()
+# 
+# 
+# ggplot(all_di, aes(n0/s0, nparts, color = dat)) +
+#   geom_point(alpha = .3) +
+#   scale_x_log10() +
+#   scale_y_log10()
+
+ggplot(all_di, aes(s0, n0, color = nsingletons_median / s0)) +
+  geom_point(alpha = .3) +
+  scale_x_log10() +
+  scale_y_log10() +
+  scale_color_viridis_c()
+
+# 
+# ggplot(all_di, aes(s0, n0, color = nsingletons / s0)) +
+#   geom_point(alpha = .3) +
+#   scale_x_log10() +
+#   scale_y_log10() +
+#   scale_color_viridis_c()
+
+```
 
@@
 
-Working on the breadth index (stuff needs to run).
+```{r}
+
+ggplot(all_di, aes(nparts, shannon_95_ratio_2t, color = dat)) +
+  geom_point(alpha = .3) +
+  scale_x_log10()
+
+ggplot(all_di, aes(nparts, shannon_95_ratio_2t, color = dat)) +
+  geom_point(alpha = .3) +
+  scale_x_log10() +
+  xlim(0, 100000)
+
+```
+
+## 2 tailed breadth indices
+
+```{r}
+
+ggplot(all_di, aes(nparts, shannon_95_ratio_2t, color = dat)) +
+  geom_point(alpha = .3) +
+  scale_x_log10()
+
+ggplot(all_di, aes(nparts, skew_95_ratio_2t, color = dat)) +
+  geom_point(alpha = .3) +
+  scale_x_log10()
+
+ggplot(all_di, aes(nparts, simpson_95_ratio_2t, color = dat)) +
+  geom_point(alpha = .3) +
+  scale_x_log10()
+
+ggplot(all_di, aes(nparts, nsingletons_95_ratio_2t, color = dat)) +
+  geom_point(alpha = .3) +
+  scale_x_log10()
+
+```

### 2021-02-25 analysis/rev_prototyping/additional_metrics_results.Rmd
figuregit add --allgit add --all

@@
   summarize(
-            prop_shannon_high_raw = mean(shannon_percentile > 95),
+            prop_shannon_high_raw = mean(shannon_percentile_excl > 95),
             prop_shannon_low_raw = mean(shannon_percentile < 5),
@@
 ```
+
+## Epic synthesizing figure
+
+```{r, fig.dim = c(5, 10)}
+
+all_di_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))
+
+jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
+
+jk_di <- jk_di_full %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup() %>%
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingeltons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
+
+jk_di_means <- jk_di %>%
+  group_by(dat, site_source) %>%
+  summarise_at(vars(-group_cols(), -site), mean) %>%
+  mutate(resampling = "jacknife") %>%
+  mutate(site = as.integer(site_source)) %>%
+  select(-site_source) %>%
+  filter(n0 != s0,
+         s0 != 1,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
+
+all_di_with_resamples <- all_di_with_resamples %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 != s0,
+         s0 != 1,
+       #  !singletons,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20) %>%
+  mutate(resampling = ifelse(singletons, "rarefaction", "none")) %>%
+  bind_rows(jk_di_means)
+
+prop_results <- all_di_with_resamples %>%
+ # filter(!singletons) %>%
+  group_by(Dataset, resampling) %>%
+  summarize(
+    skew_high = mean(skew_percentile_excl > 97.5),
+    skew_low = mean(skew_percentile < 2.5),
+    even_high = mean(simpson_percentile_excl > 97.5),
+    even_low = mean(simpson_percentile < 2.5),
+    shannon_high = mean(shannon_percentile > 97.5),
+    shannon_low = mean(shannon_percentile < 2.5),
+    nsingletons_high = mean(nsingletons_percentile_excl > 97.5),
+    nsingletons_low = mean(nsingletons_percentile < 2.5),
+    po_high = mean(mean_po_comparison_percentile > 97.5),
+    po_low = mean(mean_po_comparison_percentile < 2.5)
+  ) %>%
+  ungroup() %>%
+  tidyr::pivot_longer((-c("Dataset","resampling")), names_to = "metric", values_to = "value") %>%
+  mutate(ometric = ordered(metric, levels = c("skew_high", "skew_low", "even_low", "even_high", "shannon_low", "shannon_high", "nsingletons_high", "nsingletons_low", "po_high", "po_low")),
+         ometric2 = ordered(metric, levels = c("skew_high",  "even_low",  "shannon_low",  "nsingletons_high", "po_high", "skew_low","even_high","shannon_high", "nsingletons_low", "po_low"))) %>%
+  mutate(weird_dir = as.numeric(ometric2) > 5)
+
+# 
+# ggplot(prop_results, aes(Dataset, value, color = resampling)) +
+#   geom_point() +
+#   geom_point(data = filter(prop_results, resampling == "none"), color = "black", size = 2) +
+#   geom_hline(yintercept = .025) +
+#   facet_wrap(vars(ometric), ncol = 2, scales = "free_y") +
+#   theme(legend.position = "top")
+
+ggplot(prop_results, aes(ometric2, value, color = resampling)) +
+  geom_point() +
+  geom_point(data = filter(prop_results, resampling == "none"), color = "black", size = 2) +
+  geom_hline(yintercept = .025) +
+  facet_grid(rows = vars(Dataset), cols = vars(weird_dir), scales = "free_x", switch = "y") +
+  theme(legend.position = "top") +
+  theme(axis.text.x = element_text(angle = 75, hjust= 1))
+```
+
+This is an EPIC figure.
+
+Specs:
+
+- The row panels are different datasets. 
+- The left column of panels is the "usual" direction of the effect - the way most datasets behave. The right column is the "reverse" direction - the way Gentry behaves.
+- The x axis is different metrics.
+- The y axis is the proportion of sites with an extreme value (> 97.5 or < 2.5 percentile, depending on if the metric is "high" or "low" respectively) for that metric. 
+- The horizontal line is 2.5. Because this is now making a 2tailed comparison, the 2.5 cutoff is the proportion of percentile values we would expect to be in this range at random.
+- The BLACK points are for raw SADs. The BLUE dots are for SADs corrected for nondetection of rare species. The RED dots are for SADs resampled via jacknife resampling.
+- Note that a lot of FIA stuff hasn't finished running, so don't take those panels seriously.
+
+Interpretation:
+
+- All datasets (except maybe FIA) have extreme values more often than usual for almost all metrics.
+- Adjusting for rare species always increases this effect if it has any impact at all.
+- Jacknife resampling decreases it, but only to no significance for BBS and MCDB # of singletons.
+- While Gentry often has extreme values in the same direction as the other datasets, it also has them very strongly in the *opposite* direction.

### 2021-03-02 analysis/rev_prototyping/additional_metrics_results.Rmd
updated with fia done

@@
 
-all_di %>% filter(nparts >20) %>% group_by(singletons, dat) %>% summarize(high_proportion_off = mean(mean_po_comparison_percentile > 95))
+all_di %>% filter(nparts >20) %>% group_by(singletons, dat) %>% summarize(high_proportion_off = mean(mean_po_comparison_percentile_excl > 95))
 
@@
 
-ggplot(filter(all_di, mean_po_comparison_percentile > 95), aes( mean_po_comparison - mean_po_comparison_95)) +
+ggplot(filter(all_di, mean_po_comparison_percentile_excl > 95), aes( mean_po_comparison - mean_po_comparison_95)) +
   geom_histogram() +
@@
   ungroup() %>%
-  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingeltons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_percentile_excl, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
 
@@
     even_low = mean(simpson_percentile < 2.5),
-    shannon_high = mean(shannon_percentile > 97.5),
+    shannon_high = mean(shannon_percentile_excl > 97.5),
     shannon_low = mean(shannon_percentile < 2.5),
@@
     nsingletons_low = mean(nsingletons_percentile < 2.5),
-    po_high = mean(mean_po_comparison_percentile > 97.5),
+    po_high = mean(mean_po_comparison_percentile_excl > 97.5),
     po_low = mean(mean_po_comparison_percentile < 2.5)

### 2021-03-05 analysis/rev_prototyping/jacknife_results.Rmd

--- 2021-02-23 analysis/rev_prototyping/jacknife_results.Rmd
@@
          !singletons,
-         n0 != (s0 + 1))
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
 
-jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
+jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv")) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
 
@@
   ungroup() %>%
-  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingeltons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile,shannon_percentile_excl,  nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims,mean_po_comparison_percentile_excl, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
 
@@
   mutate(site_source = as.character(site)) %>%
-  select(dat, site_source, s0, n0, skew_percentile_excl, skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, nsingletons_percentile, nsingletons_percentile_excl, nsingletons,nsingeltons_median,  nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
+  select(dat, site_source, s0, n0, skew_percentile_excl, skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl, nsingletons,  nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_95,mean_po_comparison_percentile_excl, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
 
@@
 
-jk_di_mean_results <- jk_di_mean_results %>%
-  mutate(skew_actual_sig = skew_percentile_excl_actual > 95,
-         skew_sig = skew_percentile_excl > 95) %>%
-  mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig)) %>%
-  filter(nparts > 20)
+# jk_di_mean_results <- jk_di_mean_results %>%
+#   mutate(skew_actual_sig = skew_percentile_excl_actual > 95,
+#          skew_sig = skew_percentile_excl > 95) %>%
+#   mutate(skew_change = paste0("actual", skew_actual_sig, "_jk", skew_sig)) %>%
+#   filter(nparts > 20)
 
@@
   filter(nparts > 20) %>%
-  summarize(prop_shannon_high_jk = mean(shannon_percentile > 95),
-            prop_shannon_high_raw = mean(shannon_percentile_actual > 95),
+  summarize(prop_shannon_high_jk = mean(shannon_percentile_excl > 95),
+            prop_shannon_high_raw = mean(shannon_percentile_excl > 95),
             prop_shannon_low_jk = mean(shannon_percentile< 5),
@@
   filter(nparts > 20) %>%
-  summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile > 95),
-            prop_mean_po_comparison_high_raw = mean(mean_po_comparison_percentile_actual > 95),
+  summarize(prop_mean_po_comparison_high_jk = mean(mean_po_comparison_percentile_excl > 95),
+            prop_mean_po_comparison_high_raw = mean(mean_po_comparison_percentile_excl_actual > 95),
             nsites_included = dplyr::n())
@@
 
+<!-- ```{r, fig.dim = c(8,8)} -->
+
+<!-- fia_max_n = 150 -->
+<!-- fia_max_s = 21 -->
+
+<!-- ggplot(jk_di_mean_results, aes(s0, n0, color = dat)) + -->
+<!--   geom_point(aes(s0_actual, n0_actual), color = "grey", alpha  = .2)+ -->
+<!--     geom_point(aes(s0, n0, color = dat), alpha = .5) + -->
+<!--   theme_bw() + -->
+<!--   scale_x_log10() + -->
+<!--   scale_y_log10() + -->
+<!--   facet_wrap(vars(dat)) + -->
+<!--   geom_vline(xintercept = fia_max_s) + -->
+<!--   geom_hline(yintercept = fia_max_n) + -->
+<!--   theme(legend.position = "top") -->
+
+<!-- jk_di_mean_results <- jk_di_mean_results %>% -->
+<!--   group_by_all() %>% -->
+<!--   mutate(fiasized = (s0 <= fia_max_s) && (n0 <= fia_max_n), -->
+<!--          fiasized_acutal =(s0_actual <= fia_max_s) && (n0_actual <= fia_max_n) ) %>% -->
+<!--   ungroup() -->
+
+<!-- jk_di_mean_results %>% -->
+<!--   group_by(dat) %>% -->
+<!--   summarize(jk_small = mean(fiasized), actual_small = mean(fiasized_acutal), nsites = dplyr::n()) -->
+
+<!-- jk_di_mean_results %>% -->
+<!--   group_by(dat, fiasized) %>% -->
+<!--   summarize( nsingletons_high  = mean(nsingletons_percentile_excl > 95), nsites = dplyr::n()) -->
+
+<!-- ``` -->
 <!-- ```{r, fig.dim = c(6,6)} -->

### 2021-03-08 analysis/rev_prototyping/ct.Rmd
hm

---
title: "Comparing to lognormal, Poisson, exponential"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)

theme_set(theme_bw())
compare_props_off2 <- function(focal_sim, fs_df, ncomps = 100) {

  fs_df$sim_char = as.character(fs_df$sim)

  if(focal_sim != -99) {
    fs_df <- dplyr::filter(fs_df, sim > 0)
  }

  nsims <- unique(fs_df$sim_char)[ which(unique(fs_df$sim_char) != as.character(focal_sim))]

  if(length(nsims) == 0) {
    return(data.frame(focal_sim = focal_sim, mean_po_comparison = NA, n_po_comparisons = 0))
  }

  focal_sad <- dplyr::filter(fs_df, sim == focal_sim)

  compare_sims <- sample(nsims, size = min(length(nsims), ncomps), replace =F)

  compare_sads <- dplyr::filter(fs_df, sim_char %in% compare_sims)

  compare_props <- compare_sads %>%
    dplyr::group_by(sim) %>%
    dplyr::summarize(prop_off = proportion_off(t(data.frame(abund, focal_sad$abund)))) %>%
    dplyr::ungroup()

  return(compare_props)
}

```

```{r}

fs <- read.csv(here::here("analysis", "rev_prototyping", "gentry_82_fs.csv"))
fs_pc <- read.csv(here::here("analysis", "rev_prototyping", "fs_pc_fs_82.csv"))

ct_sim <- filter(fs_pc, mean_po_comparison == min(fs_pc$mean_po_comparison))

ggplot(filter(fs, sim %in% fs_pc$focal_sim), aes(rank, abund, group = sim)) +
  geom_line() + scale_y_log10() + geom_line(data = filter(fs, sim ==ct_sim$focal_sim[1]), color = "red")

ct_sad <- filter(fs, sim == ct_sim$focal_sim[1])
real_sad <- filter(fs, sim < 0)
ggplot(ct_sad, aes(rank, abund)) +
  geom_line() +
  geom_line(data = real_sad, inherit.aes = T, color='blue')

real_po <- proportion_off(t(data.frame(real_sad$abund, ct_sad$abund)))
sim_po <- compare_props_off2(ct_sad$sim[1], fs, ncomps = 3999)

ggplot(sim_po, aes(prop_off)) +
  geom_histogram() +
  geom_vline(xintercept = real_po)
```

```{r}

po_central_tendency <- function(fs_df, fs_po_df) {

  ct_sim <- dplyr::filter(fs_po_df, mean_po_comparison == min(fs_po_df$mean_po_comparison))$focal_sim[1]

  ct_pos <- compare_props_off_full(ct_sim, fs_df, ncomps = length(unique(fs_df$sim)) - 2) %>%
    dplyr::distinct()

  real_po <- proportion_off(t(data.frame(dplyr::filter(fs_df, source == "observed")$abund, dplyr::filter(fs_df, sim == ct_sim)$abund)))

  out <- fs_df %>%
    dplyr::filter(source == "observed") %>%
    dplyr::select(source, dat, site, singletons, s0, n0, sim, nparts) %>%
    dplyr::distinct() %>%
    dplyr::mutate(
      real_po = real_po,
      best_po_sim = ct_sim,
      sim_devs_from_best = mean(ct_pos$prop_off),
      ncomparisons = nrow(ct_pos),
      real_po_percentile = get_percentile(real_po, ct_pos$prop_off),
      real_po_percentile_excl = get_percentile(real_po, ct_pos$prop_off, incl = F)
    )

}

```

### 2021-03-08 analysis/rev_prototyping/distinguish.Rmd
hm

---
title: "Comparing to lognormal, Poisson, exponential"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)

theme_set(theme_bw())

```

```{r}

tiny_sad_draws <- feasiblesads::sample_fs(3, 10, 1)
# 
# tiny_sad_tally <- feasiblesads::tally_sets(tiny_sad_draws)
# 
# count_if_species_distinguishable <- function(sad) {
#   
#   tallies <- data.frame(
#     species = unique(sad)
#   )
#   
#   for(i in 1:nrow(tallies)) {
#   tallies$abund[i] = sum(sad == tallies$species[i])
#   }
#   
#   uniques <- data.frame(
#     abund = unique(tallies$abund)
#   )
# 
#   for(i in 1:nrow(uniques)) {
#     uniques$nspp[i] = sum(tallies$abund == uniques$abund[i])
#   }
#   
#   ties <- filter(uniques, nspp > 1)
#     
#   
#   for(i in 1:nrow(ties)) {
#     ties$norders <- factorial(ties$nspp)
#   }
#   
#   nways <- 
# }

```

Say we care which species has which abundance, and to start, we can tell them apart even if they have different abundances. 
Then each element of the feasible set can be reshuffled however many ways there are to order S things, which is S!.

1,2,7
1,7,2
2,1,7
2,7,1
7,1,2
7,2,1

but also

2,4,4
2,4,4
4,2,4
4,2,4
4,4,2
4,4,2

If we can't tell them apart if they have different abundances...
you need to do some offset based on the number of ties.

2,4,4
4,2,4
4,4,2

Within a feasible set this would down-weight hte probability of landing on a FS with ties in species' abundances. Depending on whether those elements are more commonly the ones with long rare tails, or ones with lots of abundant species - which I think may depend on N/S - this would push things to be more or less even.

### 2021-03-08 R/metrics.R

@@ -182,6 +182,43 @@ compare_props_off <- function(focal_sim, fs_df, ncomps = 100) {
   return(data.frame(focal_sim = focal_sim, mean_po_comparison = mean(compare_props$prop_off, na.rm = T), n_po_comparisons = nrow(compare_props)))
 }
 
+#' Compare proportion off of two sims
+#'
+#' @param focal_sim index of sim
+#' @param fs_df samples from FS
+#' @param ncomps how many comparisons
+#'
+#' @return mean proportion off of focal sim vs ncomparisons sims from fs_df
+#' @export
+#'
+#' @importFrom dplyr filter group_by summarize
+compare_props_off_full <- function(focal_sim, fs_df, ncomps = 100) {
+
+  fs_df$sim_char = as.character(fs_df$sim)
+
+  if(focal_sim != -99) {
+    fs_df <- dplyr::filter(fs_df, sim > 0)
+  }
+
+  nsims <- unique(fs_df$sim_char)[ which(unique(fs_df$sim_char) != as.character(focal_sim))]
+
+  if(length(nsims) == 0) {
+    return(data.frame(sim = focal_sim, prop_off = NA))
+  }
+
+  focal_sad <- dplyr::filter(fs_df, sim == focal_sim)
+
+  compare_sims <- sample(nsims, size = min(length(nsims), ncomps), replace =F)
+
+  compare_sads <- dplyr::filter(fs_df, sim_char %in% compare_sims)
+
+  compare_props <- compare_sads %>%
+    dplyr::group_by(sim) %>%
+    dplyr::summarize(prop_off = proportion_off(t(data.frame(abund, focal_sad$abund)))) %>%
+    dplyr::ungroup()
+
+  return(compare_props)
+}
 #' Get FS diff metrics
 #'
 #' @param fs_df samples
@@ -399,5 +436,39 @@ pull_di_net <- function(di_df) {
     )
 
   return(di_sampled)
+
+}
+
+
+#' PO CT
+#'
+#' @param fs_df fs
+#' @param fs_po_df pcs
+#'
+#' @return df
+#' @export
+#'
+#' @importFrom dplyr filter select distinct mutate
+po_central_tendency <- function(fs_df, fs_po_df) {
+
+  ct_sim <- dplyr::filter(fs_po_df, mean_po_comparison == min(fs_po_df$mean_po_comparison))$focal_sim[1]
+
[…]

### 2021-03-08 analysis/mcdb_pipeline.R

@@ -37,7 +37,11 @@ all <- drake_plan(
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),
                     transform = combine(di_obs, .by = singletons)),
-  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE))
+  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
+  cts = target(po_central_tendency(fs, fs_pc),
+               transform = map(fs, fs_pc)),
+  all_cts = target(dplyr::bind_rows(cts),
+                   transform = combine(cts))
 )
 
 ## Set up the cache and config

### 2021-03-08 analysis/rev_prototyping/ct.Rmd
helps if you return the output

@@
 ```{r}
+# 
+# po_central_tendency <- function(fs_df, fs_po_df) {
+#   
+#   ct_sim <- dplyr::filter(fs_po_df, mean_po_comparison == min(fs_po_df$mean_po_comparison))$focal_sim[1]
+#   
+#   ct_pos <- compare_props_off_full(ct_sim, fs_df, ncomps = length(unique(fs_df$sim)) - 2) %>%
+#     dplyr::distinct()
+#   
+#   real_po <- proportion_off(t(data.frame(dplyr::filter(fs_df, source == "observed")$abund, dplyr::filter(fs_df, sim == ct_sim)$abund)))
+# 
+#   out <- fs_df %>%
+#     dplyr::filter(source == "observed") %>%
+#     dplyr::select(source, dat, site, singletons, s0, n0, sim, nparts) %>%
+#     dplyr::distinct() %>%
+#     dplyr::mutate(
+#       real_po = real_po,
+#       best_po_sim = ct_sim,
+#       sim_devs_from_best = mean(ct_pos$prop_off),
+#       ncomparisons = nrow(ct_pos),
+#       real_po_percentile = get_percentile(real_po, ct_pos$prop_off),
+#       real_po_percentile_excl = get_percentile(real_po, ct_pos$prop_off, incl = F)
+#     )
+# 
+# }
 
-po_central_tendency <- function(fs_df, fs_po_df) {
-
-  ct_sim <- dplyr::filter(fs_po_df, mean_po_comparison == min(fs_po_df$mean_po_comparison))$focal_sim[1]
-
-  ct_pos <- compare_props_off_full(ct_sim, fs_df, ncomps = length(unique(fs_df$sim)) - 2) %>%
-    dplyr::distinct()
-
-  real_po <- proportion_off(t(data.frame(dplyr::filter(fs_df, source == "observed")$abund, dplyr::filter(fs_df, sim == ct_sim)$abund)))
-
-  out <- fs_df %>%
-    dplyr::filter(source == "observed") %>%
-    dplyr::select(source, dat, site, singletons, s0, n0, sim, nparts) %>%
-    dplyr::distinct() %>%
-    dplyr::mutate(
-      real_po = real_po,
-      best_po_sim = ct_sim,
-      sim_devs_from_best = mean(ct_pos$prop_off),
-      ncomparisons = nrow(ct_pos),
-      real_po_percentile = get_percentile(real_po, ct_pos$prop_off),
-      real_po_percentile_excl = get_percentile(real_po, ct_pos$prop_off, incl = F)
-    )
-
-}
+po_central_tendency(fs, fs_pc)
 

### 2021-03-08 R/metrics.R

@@ -471,4 +471,6 @@ po_central_tendency <- function(fs_df, fs_po_df) {
       real_po_percentile_excl = get_percentile(real_po, ct_pos$prop_off, incl = F)
     )
 
+  return(out)
+
 }

### 2021-03-09 analysis/rev_prototyping/ct_mcdb.Rmd
use median

--- 2021-02-24 analysis/rev_prototyping/nsingletons.Rmd
@@
 ---
-title: "Shannon diversity"
+title: "Comparing to lognormal, Poisson, exponential"
 author: Renata Diaz
@@
 library(ggplot2)
-library(grid)
+library(scadsanalysis)
+
+knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)
 
@@
 all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+
+mcdb_ct <- read.csv(here::here("mcdb_cts.csv"))
 
@@
          Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
-  filter(nparts > 20)
+  filter(nparts > 20) %>%
+  filter(dat == "mcdb") %>%
+  left_join(mcdb_ct)
+```
+
+```{r}
+
+ggplot(all_di, aes(sim_pos_from_best)) +
+  geom_histogram()
+
+ggplot(all_di, aes(sim_pos_from_best, real_po)) +
+  geom_point() +
+  geom_line(aes(sim_pos_from_best, sim_pos_from_best))
 
 ```
-```{r}
-
-ggplot(all_di, aes(nsingletons_percentile)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(dat, singletons), scales = "free_y")
-
-ggplot(all_di, aes(nsingletons_percentile_excl)) +
-  geom_histogram(bins = 100) +
-  facet_wrap(vars(dat, singletons), scales = "free_y")
-
-all_di <- all_di %>%
-  mutate(prop_singles_actual = nsingletons / s0,
-         sim_prop_singles_95 = nsingletons_95 / s0,
-         sim_prop_singles_mean = nsingletons_mean / s0) %>%
-  mutate(actual_minus_95_prop = prop_singles_actual - sim_prop_singles_95) %>%
-  mutate(high_singles=nsingletons_percentile > 95,
-         high_singles_ex = nsingletons_percentile_excl > 95,
-         low_singles = nsingletons_percentile < 5,
-         low_singles_ex = nsingletons_percentile_excl < 5) %>%
-  mutate(singles_desc = ifelse(high_singles_ex, "high", ifelse(low_singles, "low", "int")))
-
-```
-
-```{r, fig.dim = c(8,8)}
-
-ggplot(all_di, aes(s0, n0, color = singles_desc)) +
-  geom_point(alpha = .3) +
-  facet_wrap(vars(dat), scales = "free") +
-  scale_x_log10()+ 
-  scale_y_log10()
-
-all_di %>%
-  group_by(dat, singletons) %>%
-  summarize(prop_high_singles = mean(high_singles),
-            prop_high_singles_ex = mean(high_singles_ex),
-            prop_low_singles = mean(low_singles),
-            prop_low_singles_ex = mean(low_singles_ex),
-            nsites= dplyr::n()) %>%
-  ungroup()
-
-```
-
-```{r, echo = T}
-
-ggplot(all_di, aes(n0/s0, nsingletons_percentile_excl, color = singles_desc)) +
-  geom_point() +
-  facet_wrap(vars(dat), scales = "free") +
-  scale_x_log10() +
-  geom_vline(xintercept = c(3, 5, 10))
-
-ggplot(all_di, aes(n0/s0, nsingletons_percentile_excl, color = singles_desc)) +
-  geom_point(data = filter(all_di, singles_desc != "int")) +
-  geom_point(alpha = .1, color = "grey") +
-  facet_wrap(vars(dat), scales = "free") +
-  scale_x_log10() +
-  geom_vline(xintercept = c(3, 5, 10))
-
-all_di %>%
-  filter(n0/s0 < 3) %>%
-  group_by(dat, singletons) %>%
-  summarize(prop_high_singles = mean(high_singles),
-            prop_high_singles_ex = mean(high_singles_ex),
-            prop_low_singles = mean(low_singles),
-            prop_low_singles_ex = mean(low_singles_ex),
-            nsites= dplyr::n()) %>%
-  ungroup()
-
-all_di %>%
-  filter(n0/s0 > 10) %>%
-  group_by(dat, singletons) %>%
-  summarize(prop_high_singles = mean(high_singles),
-            prop_high_singles_ex = mean(high_singles_ex),
-            prop_low_singles = mean(low_singles),
-            prop_low_singles_ex = mean(low_singles_ex),
-            nsites= dplyr::n()) %>%
-  ungroup()
-
-```
-```{r}
-
-all_di <- all_di %>%
-  mutate(singletons_change = (nsingletons - nsingletons_95) / s0)
-
-ggplot(filter(all_di, high_singles_ex), aes(singletons_change)) +
-  geom_histogram() +
-  facet_wrap(vars(dat), scales = "free")
-
-all_di %>%
-  filter(high_singles_ex) %>%
-  group_by(dat) %>%
-  summarize(mean_singles_change = mean(singletons_change),
-            n = dplyr::n())
-
-```

### 2021-03-09 analysis/rev_prototyping/ct_mcdb.Rmd
ct
run gentry and mcdb

@@
 
+ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram()
+
+ggplot(all_di, aes(nparts, sim_pos_from_best)) +
+  geom_point() +
+  scale_x_log10()
+
 ```
+
+```{r}
+
+ggplot(all_di, aes(sim_r2_from_best_median)) +
+  geom_histogram()
+
+ggplot(all_di, aes(sim_r2_from_best_median, real_r2)) +
+  geom_point() +
+  geom_line(aes(sim_r2_from_best_median, sim_r2_from_best_median)) +
+  ylim(0,1)
+
+ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram()
+
+ggplot(all_di, aes(nparts, sim_r2_from_best_median)) +
+  geom_point() +
+  scale_x_log10()
+
+```

### 2021-03-09 analysis/gentry_pipeline.R

@@ -37,7 +37,11 @@ all <- drake_plan(
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),
                     transform = combine(di_obs, .by = singletons)),
-  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE))
+  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
+ cts = target(po_central_tendency(fs, fs_pc),
+              transform = map(fs, fs_pc)),
+ all_cts = target(dplyr::bind_rows(cts),
+                  transform = combine(cts))
 )
 
 ## Set up the cache and config
@@ -52,30 +56,30 @@ if (interactive())
   sankey_drake_graph(config, build_times = "none")  # requires "networkD3" package
   vis_drake_graph(config, build_times = "none")     # requires "visNetwork" package
 }
-
-## Run the pipeline
-nodename <- Sys.info()["nodename"]
-if(grepl("ufhpc", nodename)) {
-  print("I know I am on the HiPerGator!")
-  library(clustermq)
-  options(clustermq.scheduler = "slurm", clustermq.template = here::here("slurm_clustermq.tmpl"))
-  ## Run the pipeline parallelized for HiPerGator
-  make(all,
-       force = TRUE,
-       cache = cache,
-       cache_log_file = here::here("analysis", "drake", "cache_log_gentry.txt"),
-       verbose = 1,
-       parallelism = "clustermq",
-       jobs = 100,
-       caching = "master",
-       memory_strategy = "autoclean",
-       garbage_collection = TRUE) # Important for DBI caches!
-} else {
-  library(clustermq)
-  options(clustermq.scheduler = "multicore")
+#
+# ## Run the pipeline
+# nodename <- Sys.info()["nodename"]
+# if(grepl("ufhpc", nodename)) {
+#   print("I know I am on the HiPerGator!")
+#   library(clustermq)
+#   options(clustermq.scheduler = "slurm", clustermq.template = here::here("slurm_clustermq.tmpl"))
+#   ## Run the pipeline parallelized for HiPerGator
+#   make(all,
+#        force = TRUE,
+#        cache = cache,
+#        cache_log_file = here::here("analysis", "drake", "cache_log_gentry.txt"),
+#        verbose = 1,
+#        parallelism = "clustermq",
+#        jobs = 100,
+#        caching = "master",
[…]

### 2021-03-09 analysis/miscabund_pipeline.R

@@ -36,7 +36,11 @@ dat_plan <- drake_plan(
                   transform = map(di)),
   di_obs_s = target(dplyr::bind_rows(di_obs),
                     transform = combine(di_obs, .by = singletons)),
-  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE))
+  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
+  cts = target(po_central_tendency(fs, fs_pc),
+               transform = map(fs, fs_pc)),
+  all_cts = target(dplyr::bind_rows(cts),
+                   transform = combine(cts))
 )
 
 all <- dat_plan
@@ -55,28 +59,28 @@ if (interactive())
 }
 
 ## Run the pipeline
-nodename <- Sys.info()["nodename"]
-if(grepl("ufhpc", nodename)) {
-  print("I know I am on the HiPerGator!")
-  library(clustermq)
-  options(clustermq.scheduler = "slurm", clustermq.template = here::here("slurm_clustermq.tmpl"))
-  ## Run the pipeline parallelized for HiPerGator
-  make(all,
-       force = TRUE,
-       cache = cache,
-       cache_log_file = here::here("analysis", "drake", "cache_log_miscabund.txt"),
-       verbose = 1,
-       parallelism = "clustermq",
-       jobs = 100,
-       caching = "master",
-       memory_strategy = "autoclean",
-       garbage_collection = TRUE) # Important for DBI caches!
-} else {
-  library(clustermq)
-  options(clustermq.scheduler = "multicore")
+# nodename <- Sys.info()["nodename"]
+# if(grepl("ufhpc", nodename)) {
+#   print("I know I am on the HiPerGator!")
+#   library(clustermq)
+#   options(clustermq.scheduler = "slurm", clustermq.template = here::here("slurm_clustermq.tmpl"))
+#   ## Run the pipeline parallelized for HiPerGator
+#   make(all,
+#        force = TRUE,
+#        cache = cache,
+#        cache_log_file = here::here("analysis", "drake", "cache_log_miscabund.txt"),
+#        verbose = 1,
+#        parallelism = "clustermq",
+#        jobs = 100,
+#        caching = "master",
+#        memory_strategy = "autoclean",
+#        garbage_collection = TRUE) # Important for DBI caches!
+# } else {
+#   library(clustermq)
+#   options(clustermq.scheduler = "multicore")
[…]

### 2021-03-09 analysis/rev_prototyping/ct_mcdb.Rmd
methods

@@
 
-ggplot(all_di, aes(sim_pos_from_best, real_po)) +
+ggplot(all_di, aes(sim_pos_from_best, real_po, color = real_po_percentile_excl > 95)) +
   geom_point() +
-  geom_line(aes(sim_pos_from_best, sim_pos_from_best))
+  geom_line(aes(sim_pos_from_best, sim_pos_from_best)) +
+  theme(legend.position = "top")
 

### 2021-03-11 analysis/rev_prototyping/ct.Rmd
less memory

@@
 theme_set(theme_bw())
-compare_props_off2 <- function(focal_sim, fs_df, ncomps = 100) {
-
-  fs_df$sim_char = as.character(fs_df$sim)
-
-  if(focal_sim != -99) {
-    fs_df <- dplyr::filter(fs_df, sim > 0)
-  }
-
-  nsims <- unique(fs_df$sim_char)[ which(unique(fs_df$sim_char) != as.character(focal_sim))]
-
-  if(length(nsims) == 0) {
-    return(data.frame(focal_sim = focal_sim, mean_po_comparison = NA, n_po_comparisons = 0))
-  }
-
-  focal_sad <- dplyr::filter(fs_df, sim == focal_sim)
-
-  compare_sims <- sample(nsims, size = min(length(nsims), ncomps), replace =F)
-
-  compare_sads <- dplyr::filter(fs_df, sim_char %in% compare_sims)
-
-  compare_props <- compare_sads %>%
-    dplyr::group_by(sim) %>%
-    dplyr::summarize(prop_off = proportion_off(t(data.frame(abund, focal_sad$abund)))) %>%
-    dplyr::ungroup()
-
-  return(compare_props)
-}
 
@@
 real_po <- proportion_off(t(data.frame(real_sad$abund, ct_sad$abund)))
-sim_po <- compare_props_off2(ct_sad$sim[1], fs, ncomps = 3999)
+sim_po <- compare_props_off_full(ct_sad$sim[1], fs, ncomps = 3999)
 

### 2021-03-11 analysis/rev_prototyping/old/mete.Rmd
less memory

---
title: "Comparing to lognormal, Poisson, exponential"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)

theme_set(theme_bw())

```
FIA 16059000010 - 7, 50. Small

BBS 4229 - 50, 709. High n

Gentry 82 - 214, 333. High n but low N/S

```{r}

fia_small <- load_dataset("fia_small")

small <- fia_small %>%
  filter(!singletons, site == "16059000010")

bbs <- load_dataset("bbs")

big <- bbs %>%
  filter(site == "4229")

gentry <- load_dataset("gentry")

wide <- gentry %>% filter(site == "82")

small_fs <- read.csv(here::here("analysis", "rev_prototyping", "fia_16059000010_fs.csv"))
big_fs <- read.csv(here::here("analysis", "rev_prototyping", "bbs_4229_fs.csv"))
wide_fs <- read.csv(here::here("analysis", "rev_prototyping", "gentry_82_fs.csv"))

ggplot(small, aes(rank, abund)) + 
  geom_line(data = small_fs, aes(rank, abund, group = sim), alpha = .01) +   geom_point(color = "red")

ggplot(big, aes(rank, abund)) + 
  geom_point()

ggplot(big, aes(rank, abund)) + 
  geom_line(data = big_fs, aes(rank, abund, group = sim), alpha = .01) +  geom_point(color = "red")

ggplot(wide, aes(rank, abund)) + 
  geom_point()

ggplot(wide, aes(rank, abund)) + 
  geom_line(data = wide_fs, aes(rank, abund, group = sim), alpha = .01) +  geom_point(color = "red") + ylim(0, 40)

```

```{r}
library(MASS)

small_exp <- fitdistr(small$abund, "exponential")

small_exp_preds <- replicate(n = 4000, expr = sort(round(rexp(nrow(small), rate = small_exp$estimate))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund") %>%
  group_by(sim) %>%
  mutate(skewness = e1071::skewness(abund),
         evenness = vegan::diversity(abund, index = "shannon")) %>%
  ungroup()

ggplot(small, aes(rank, abund))+   geom_line(data = small_exp_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red")

small_fs <- small_fs %>% 
  group_by(sim) %>%
  mutate(skewness = e1071::skewness(abund),
         evenness = vegan::diversity(abund, index = "shannon")) %>%
  ungroup()

ggplot(small_exp_preds, aes(skewness)) +
  geom_histogram() + 
  geom_vline(xintercept = e1071::skewness(small$abund))

ggplot(filter(small_fs, sim > 0), aes(skewness)) +
  geom_histogram() + 
  geom_vline(xintercept = e1071::skewness(small$abund))

big_exp <- fitdistr(big$abund, "exponential")

big_exp_preds <- replicate(n = 4000, expr = sort(round(rexp(nrow(big), rate = big_exp$estimate))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")

ggplot(big, aes(rank, abund))+   geom_line(data = big_exp_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red")

wide_exp <- fitdistr(wide$abund, "exponential")

wide_exp_preds <- replicate(n = 4000, expr = sort(round(rexp(nrow(wide), rate = wide_exp$estimate))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")

ggplot(wide, aes(rank, abund))+   geom_line(data = wide_exp_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red") 
```

```{r}

small_pois <- fitdistr(small$abund, "poisson")

small_pois_preds <- replicate(n = 4000, expr = sort(round(rpois(nrow(small), lambda = small_pois$estimate))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")

ggplot(small, aes(rank, abund))+   geom_line(data = small_pois_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red")

big_pois <- fitdistr(big$abund, "poisson")

big_pois_preds <- replicate(n = 4000, expr = sort(round(rpois(nrow(big), lambda = big_pois$estimate))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")

ggplot(big, aes(rank, abund))+   geom_line(data = big_pois_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red")

wide_pois <- fitdistr(wide$abund, "poisson")

wide_pois_preds <- replicate(n = 4000, expr = sort(round(rpois(nrow(wide), lambda = wide_pois$estimate))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")

ggplot(wide, aes(rank, abund))+   geom_line(data = wide_pois_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red") 
```

```{r}

small_lnorm <- fitdistr(small$abund, "lognormal")

small_lnorm_preds <- replicate(n = 4000, expr = sort(round(rlnorm(nrow(small), meanlog = small_lnorm$estimate["meanlog"], sdlog = small_lnorm$estimate["sdlog"]))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")

ggplot(small, aes(rank, abund))+   geom_line(data = small_lnorm_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red") + ylim(0, 50)

big_lnorm <- fitdistr(big$abund, "lognormal")

big_lnorm_preds <- replicate(n = 4000, expr = sort(round(rlnorm(nrow(big), meanlog = big_lnorm$estimate["meanlog"], sdlog = big_lnorm$estimate["sdlog"]))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")
ggplot(big, aes(rank, abund))+   geom_line(data = big_lnorm_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red") + ylim(0, 250)

wide_lnorm <- fitdistr(wide$abund, "lognormal")

wide_lnorm_preds <- replicate(n = 4000, expr = sort(round(rlnorm(nrow(wide), meanlog = wide_lnorm$estimate["meanlog"], sdlog = wide_lnorm$estimate["sdlog"]))), simplify = T) %>%
  as.data.frame() %>%
  mutate(rank = dplyr::row_number()) %>%
  tidyr::pivot_longer(-rank, names_to = "sim", values_to = "abund")

ggplot(wide, aes(rank, abund))+   geom_line(data = wide_lnorm_preds, aes(rank, abund, group = sim), alpha = .01)  + geom_point(color = "red") 
```

### 2021-03-11 analysis/rev_prototyping/revision_results.Rmd
less memory

---
title: "Updated results"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)

theme_set(theme_bw())

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

all_ct <-  read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"), stringsAsFactors = F)

fia_ct <- read.csv(here::here("fia_cts.csv"))

all_ct <- rbind(all_ct, fia_ct)

all_ct <- all_ct %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
  filter(nparts > 20) %>%
  left_join(all_ct)

all_di <- all_di %>%
  group_by_all() %>%
  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl)) %>%
  ungroup()

all_di <- all_di %>%
  mutate(in_fia = ifelse(Dataset == "FIA", "FIA", "Other datasets"))

```

## Comparing observed to the baseline

### Central tendency

```{r}
# 
# ggplot(all_di, aes(sim_pos_from_best)) +
#   geom_histogram() +
#   facet_wrap(vars(dat), scales = "free_y") 
# 
# ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram() +
#   facet_wrap(vars(dat), scales = "free_y") + geom_vline(xintercept = 95)

ggplot(all_di, aes(real_po_percentile_mean)) + geom_histogram() +
  facet_wrap(vars(dat), scales = "free_y") + geom_vline(xintercept = 95)

all_di %>%
  group_by(dat) %>%
  summarize(prop_high_po = mean(real_po_percentile_excl > 95, na.rm = T),
            nsites = dplyr::n())

all_di %>%
  group_by(in_fia) %>%
  summarize(prop_high_po = mean(real_po_percentile_excl > 95, na.rm = T),
            nsites = dplyr::n())

ggplot(all_di, aes(sim_pos_from_best, real_po, color = real_po_percentile_excl > 95)) +
  geom_point(alpha = .3) +
  geom_abline(slope = 1, intercept = 0) +
  theme(legend.position = "top") +
  scale_color_viridis_d(end = .8) +
  facet_wrap(vars(dat), scales = "fixed")

ggplot(all_di, aes(sim_pos_from_best, real_po, color = real_po_percentile_excl > 95)) +
  geom_point(alpha = .3) +
  geom_abline(slope = 1, intercept = 0) +
  theme(legend.position = "top") +
  scale_color_viridis_d(end = .8)# +
#  facet_wrap(vars(dat), scales = "fixed")

filter(all_di, real_po_percentile_excl > 95) %>%
  mutate(real_to_mean_sim_po_ratio = real_po / sim_pos_from_best,
         real_to_mean_sim_po_difference = real_po - sim_pos_from_best,
         real_to_mean_sim_po_logratio = log(real_po / sim_pos_from_best)) %>%
  select(real_to_mean_sim_po_ratio, real_to_mean_sim_po_difference) %>%
  summarize_all(.funs = list(min = min,max = max))
```

### Shape metrics

```{r, fig.dim = c(12,12)}

all_di_shapes_long <- all_di  %>%
  filter(nparts > 40) %>%
  select(dat, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
  rename(skew = skew_percentile,
         skewX = skew_percentile_excl,
         simp = simpson_percentile,
         simpX = simpson_percentile_excl,
         shan = shannon_percentile,
         shanX = shannon_percentile_excl,
         nsng = nsingletons_percentile,
         nsngX = nsingletons_percentile_excl) %>%
  mutate(skewM = (skew + skewX) / 2,
         simpM = (simp+ simpX)/2,
         shanM = (shan+ shanX)/2,
         nsngM = (nsng+ nsngX)/2) %>%
  tidyr::pivot_longer(-dat, names_to = "metric", values_to = "value") %>%
  mutate(metric_name = substr(metric, 0, 4),
         metric_mod = ifelse(substr(metric, 5, 5) == "X", "excl", ifelse(substr(metric, 5,5) == "M", "mean", "incl")))

ggplot(filter(all_di_shapes_long, metric_mod == "mean"), aes(value)) +
  geom_histogram(bins = 40) +
  #facet_grid(rows = vars(dat), cols = vars(metric_name), scales = "free", switch = "y") +
  facet_wrap(vars(metric_name, dat), scales = "free", ncol = 5) +
  geom_vline(xintercept = c(2.5, 97.5))

all_di_shapes_high <- all_di_shapes_long %>%
  filter(metric_mod == "excl") %>%
  group_by(dat, metric_name) %>%
  summarize(proportion_high = mean(value > 95))

all_di_shapes_high %>%
  tidyr::pivot_wider(id_cols = dat, names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")

all_di_shapes_low <- all_di_shapes_long %>%
  filter(metric_mod == "incl") %>%
  group_by(dat, metric_name) %>%
  summarize(proportion_low = mean(value <5))

all_di_shapes_low %>%
  tidyr::pivot_wider(id_cols = dat, names_from = metric_name, values_from = proportion_low) %>%
  mutate(dir = "LOW")

```
<!-- ``` -->
<!-- ```{r} -->

<!-- ggplot(all_di, aes((real_po / sim_pos_from_best), real_po_percentile_excl, color =  real_po_percentile_excl > 95)) + -->
<!--   geom_point(alpha = .3)  -->

<!-- all_di %>% -->
<!--   mutate(rat = real_po / sim_pos_from_best, -->
<!--          dev = real_po_percentile_excl > 95) %>% -->
<!--   group_by(dev) %>% -->
<!--   summarize(minrat = min(rat), -->
<!--             maxrat = max(rat), -->
<!--             meanrat = mean(rat), -->
<!--             mindis = min(real_po - sim_pos_from_best), -->
<!--             maxdis = max(real_po - sim_pos_from_best)) -->

<!-- ggplot(all_di, aes(nparts, sim_pos_from_best)) + -->
<!--   geom_point() + -->
<!--   scale_x_log10() -->

<!-- ggplot(all_di, aes(nparts, sim_pos_from_best, color = dat)) + -->
<!--   geom_point() + -->
<!--   scale_x_log10()  + -->
<!--   scale_color_viridis_d() + -->
<!--   theme(legend.position = "top") -->

<!-- ggplot(all_di, aes(s0, n0, color =  sim_pos_from_best)) + -->
<!--   geom_point() + -->
<!--   scale_x_log10()  + -->
<!--   scale_y_log10() + -->
<!--   scale_color_viridis_c() + -->
<!--   theme(legend.position = "top") -->
<!-- ``` -->

### 2021-03-12 analysis/reports/manuscript_main.Rmd
get cts without ones that haven't run eyt

@@
 
-simpson_ks <- filter(sub_di, nparts > 20) %>%
+simpson_ks <- filter(sub_di, nparts > 40) %>%
   select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>% 
@@
 
-skewness_ks <- filter(sub_di, nparts > 20) %>%
+skewness_ks <- filter(sub_di, nparts > 40) %>%
   select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>% 

### 2021-03-12 analysis/rev_prototyping/revision_results.Rmd
get cts without ones that haven't run eyt

@@
   filter(nparts > 40) %>%
+  mutate(dat = ifelse(nparts < 1000, paste0(dat, "_small"), dat)) %>%
   select(dat, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
@@
   group_by(dat, metric_name) %>%
-  summarize(proportion_high = mean(value > 95))
+  summarize(proportion_high = mean(value > 95),
+            n = dplyr::n())
 
 all_di_shapes_high %>%
-  tidyr::pivot_wider(id_cols = dat, names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")
+  tidyr::pivot_wider(id_cols = c(dat, n), names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")
 
@@
 
+all_di_shapes_high <- all_di_shapes_long %>%
+  mutate(in_fia = ifelse(dat == "fia", "FIA", "Other")) %>%
+  filter(metric_mod == "excl") %>%
+  group_by(in_fia, metric_name) %>%
+  summarize(proportion_high = mean(value >95))
+
+all_di_shapes_high %>%
+  tidyr::pivot_wider(id_cols = in_fia, names_from = metric_name, values_from = proportion_high) %>%
+  mutate(dir = "high")
+
+all_di_shapes_low <- all_di_shapes_long %>%
+  mutate(in_fia = ifelse(grepl("fia", dat), "FIA", "Other")) %>%
+  filter(metric_mod == "incl") %>%
+  group_by(in_fia, metric_name) %>%
+  summarize(proportion_low = mean(value <5))
+
+all_di_shapes_low %>%
+  tidyr::pivot_wider(id_cols = in_fia, names_from = metric_name, values_from = proportion_low) %>%
+  mutate(dir = "LOW")
+
 ```
-<!-- ``` -->
-<!-- ```{r} -->
 
-<!-- ggplot(all_di, aes((real_po / sim_pos_from_best), real_po_percentile_excl, color =  real_po_percentile_excl > 95)) + -->
-<!--   geom_point(alpha = .3)  -->
+## Narrowness of the expectation
 
-<!-- all_di %>% -->
-<!--   mutate(rat = real_po / sim_pos_from_best, -->
-<!--          dev = real_po_percentile_excl > 95) %>% -->
-<!--   group_by(dev) %>% -->
-<!--   summarize(minrat = min(rat), -->
-<!--             maxrat = max(rat), -->
-<!--             meanrat = mean(rat), -->
-<!--             mindis = min(real_po - sim_pos_from_best), -->
-<!--             maxdis = max(real_po - sim_pos_from_best)) -->
+### Central tendency
 
-<!-- ggplot(all_di, aes(nparts, sim_pos_from_best)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10() -->
+```{r}
+ggplot(all_di, aes(nparts, sim_pos_from_best, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10() +
+  scale_color_viridis_c(option = "plasma")
 
-<!-- ggplot(all_di, aes(nparts, sim_pos_from_best, color = dat)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10()  + -->
-<!--   scale_color_viridis_d() + -->
-<!--   theme(legend.position = "top") -->
+```
 
-<!-- ggplot(all_di, aes(s0, n0, color =  sim_pos_from_best)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10()  + -->
-<!--   scale_y_log10() + -->
-<!--   scale_color_viridis_c() + -->
-<!--   theme(legend.position = "top") -->
-<!-- ``` -->
+```{r, fig.dim = c(3,6)}
+
+all_di <- all_di %>%
+  mutate(tiny = nparts < 2000)
+
+ggplot(all_di, aes(sim_pos_from_best)) +
+geom_histogram(bins = 100) +
+  facet_wrap(vars(tiny), scales = "free_y", ncol = 1)
+
+```
+
+### Shape metric
+
+```{r}
+
+ggplot(filter(all_di, nparts < 1e56, s0 > 2), aes(nparts, skew_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10() +
+  scale_color_viridis_c(option = "plasma")
+
+ggplot(filter(all_di, nparts < 1e56), aes(nparts, simpson_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10() +
+  scale_color_viridis_c(option = "plasma")
+
+ggplot(filter(all_di, nparts < 1e56), aes(nparts, shannon_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10() +
+  scale_color_viridis_c(option = "plasma")
+
+ggplot(filter(all_di, nparts < 1e56), aes(nparts, nsingletons_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10() +
+  scale_color_viridis_c(option = "plasma")
+
+```
+
+```{r, fig.dim = c(4, 6)}
+
+ggplot(filter(all_di), aes(sim_pos_from_best)) +
+geom_histogram() +
+  facet_wrap(vars(tiny), scales = "free_y", ncol = 1)
+ggplot(filter(all_di, s0 > 2), aes(skew_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny), scales = "free_y", ncol = 1)
+
+ggplot(filter(all_di), aes(simpson_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny), scales = "free_y", ncol = 1)
+
+ggplot(filter(all_di), aes(shannon_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny), scales = "free_y", ncol = 1)
+
+ggplot(filter(all_di), aes(nsingletons_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny), scales = "free_y", ncol = 1)
+```
+
+```{r, fig.dim = c(3, 6)}
+
+ggplot(filter(all_di, dat  %in% c("fia", "mcdb", "misc_abund")), aes(sim_pos_from_best)) +
+geom_histogram() +
+  facet_wrap(vars(tiny, dat), scales = "free_y", ncol = 3)
+ggplot(filter(all_di, s0 > 2, dat  %in% c("fia", "mcdb", "misc_abund")), aes(skew_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny, dat), scales = "free_y", ncol = 3)
+
+ggplot(filter(all_di, dat  %in% c("fia", "mcdb", "misc_abund")), aes(simpson_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny, dat), scales = "free_y", ncol = 3)
+
+ggplot(filter(all_di, dat  %in% c("fia", "mcdb", "misc_abund")), aes(shannon_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny, dat), scales = "free_y", ncol = 3)
+
+ggplot(filter(all_di, dat  %in% c("fia", "mcdb", "misc_abund")), aes(nsingletons_95_ratio_2t)) +
+geom_histogram() +
+  facet_wrap(vars(tiny, dat), scales = "free_y", ncol = 3)
+
+```
+
+```{r, fig.dim = c(7,7)}
+library(grid)
+
+fia_max_s = max(filter(all_di, dat == "fia")$s0)
+fia_max_n = max(filter(all_di, dat == "fia")$n0)
+
+fia = filter(all_di, dat == "fia")
+
+small_di <- all_di %>%
+  filter(s0 <= fia_max_s,
+         n0 <= fia_max_n) %>%
+  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
+         right_corner = FALSE)
+
+for(i in 1:nrow(small_di)) {
+  if(small_di$dat[i] != "fia") {
+    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
+
+    max_n0_for_this_s0 = max(fia_match_s0$n0)
+
+    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
+
+  }
+}
+
+small_di <- small_di %>%
+  filter(!right_corner)
+not_fia <- filter(small_di, fia_yn != "fia")
+fia = filter(small_di, dat == "fia")
+
+small_di_s_n <- small_di %>%
+  select(s0, n0) %>%
+  distinct() %>%
+  mutate(in_fia = FALSE,
+         in_not_fia = FALSE)
+
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 
+  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
+
+}
+
+small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
+
+set.seed(1977)
+
+subsamples <- list()
+
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
+
+  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
+  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
+
+  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
+
+}
+
+sub_di <- bind_rows(subsamples) %>%
+  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
+
+simpson_ks <- filter(sub_di, nparts > 40) %>%
+  select(simpson_95_ratio_2t, Dataset, simpson_percentile, s0, n0) %>% 
+  group_by(Dataset, s0, n0) %>%
+  mutate(pairing = dplyr::row_number()) %>%
+  ungroup() %>%
+  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(simpson_95_ratio_2t, simpson_percentile))
+
+simpson_breadth <- ks.test(simpson_ks$simpson_95_ratio_2t_FIA, simpson_ks$`simpson_95_ratio_2t_Other datasets`)
+
+simpson_percent <- ks.test(simpson_ks$simpson_percentile_FIA, simpson_ks$`simpson_percentile_Other datasets`)
+simpson_breadth
+simpson_percent
+
+skewness_ks <- filter(sub_di, nparts > 40) %>%
+  select(skew_95_ratio_2t, Dataset, skew_percentile_excl, s0, n0) %>% 
+  group_by(Dataset, s0, n0) %>%
+  mutate(pairing = dplyr::row_number()) %>%
+  ungroup() %>%
+  tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(skew_95_ratio_2t, skew_percentile_excl))
+
+skewness_breadth <- ks.test(skewness_ks$skew_95_ratio_2t_FIA, skewness_ks$`skew_95_ratio_2t_Other datasets`)
+
+skewness_percent <- ks.test(skewness_ks$skew_percentile_excl_FIA, skewness_ks$`skew_percentile_excl_Other datasets`)
+skewness_breadth
+skewness_percent
+
+ggplot(filter(sub_di, nparts > 40), aes(real_po_percentile_excl)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 40), aes(sim_pos_from_best)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 40), aes(skew_percentile_excl)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 40), aes(skew_95_ratio_2t)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 40), aes(nsingletons_percentile_excl)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 40), aes(nsingletons_95_ratio_2t)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 40), aes(simpson_95_ratio_2t)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+ggplot(filter(sub_di, nparts > 40), aes(shannon_percentile)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+ggplot(filter(sub_di, nparts > 40), aes(shannon_95_ratio_2t)) +
+  geom_histogram() +
+  facet_wrap(vars(fia_yn))
+
+```
+
+```{r}
+# 
+# fig_4 <- gridExtra::grid.arrange(grobs = list(
+#   ggplot(filter(sub_di, nparts > 40), aes(skew_95_ratio_2t)) +
+#     geom_histogram()+
+#     theme_bw() +
+#     facet_wrap(vars(Dataset), scales = "free_y")  +
+#     xlab("Breadth index") +
+#     ylab("Number of communities") +
+#     ggtitle("Breadth index", subtitle = "Skewness"),
+#   
+#   ggplot(filter(sub_di, nparts > 40), aes(simpson_95_ratio_2t)) +
+#     geom_histogram()+
+#     theme_bw() +
+#     facet_wrap(vars(Dataset), scales = "free_y")  +
+#     xlab("Breadth index") +
+#     ylab("") +
+#     ggtitle("", subtitle = "Evenness"),
+#   
+#   ggplot(filter(sub_di, nparts > 40), aes(skew_percentile_excl)) +
+#     geom_histogram()+
+#     theme_bw() +
+#     facet_wrap(vars(Dataset), scales = "free_y")  +
+#     xlab("Percentile rank") +
+#     ylab("Number of communities") +
+#     ggtitle("Percentile rank", subtitle = "Skewness"),
+#   
+#   
+#   ggplot(filter(sub_di, nparts > 40), aes(simpson_percentile)) +
+#     geom_histogram()+
+#     theme_bw() +
+#     facet_wrap(vars(Dataset), scales = "free_y")  +
+#     xlab("Percentile rank") +
+#     ylab("")+
+#     ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white")))
+# 
+# plot(fig_4)
+```
+
+```{r}
+
+all_di <- all_di %>%
+  mutate(tiny = nparts < exp(10))
+
+ggplot(filter(all_di, nparts > 40, s0 > 2), aes(sim_pos_from_best, color = tiny)) +
+  geom_density()
+ggplot(filter(all_di, nparts > 40, s0 > 2), aes(skew_95_ratio_2t, color = tiny)) +
+  geom_density()
+
+ggplot(filter(all_di, nparts > 40), aes(simpson_95_ratio_2t, color = tiny)) +
+  geom_density()
+
+ggplot(filter(all_di, nparts > 40), aes(shannon_95_ratio_2t, color = tiny)) +
+  geom_density()
+```
+
+```{r}
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE)
+
+net_summary <- readd(all_di_summary, cache = cache)
+
+net_summary <- net_summary %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)))
+
+ggplot(net_summary, aes(log_nparts, skew_95_ratio_2t)) +
+  geom_point()
+
+```

### 2021-03-12 analysis/helper_scripts/make_all_ct_jk.R

@@ -1,0 +1,43 @@
+# This is a wrapper script to combine the results from each dataset-level pipeline into a single data frame.
+
+library(drake)
+library(dplyr)
+library(ggplot2)
+library(scadsanalysis)
+
+all_ct <- list()
+#datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "fia_small")
+# datasets <- c( "gentry-jk", "mcdb-jk", "bbs-jk","misc-jk", "fia_small-jk", "fia_short-jk" )
+datasets <- c( "gentry-jk",  "bbs-jk","fia_small-jk", "fia_short-jk" )
+
+
+for(i in 1:length(datasets)) {
+
+  this_dataset = datasets[i]
+  if(this_dataset == "misc_abund_short") {
+    cache_loc = "misc_jk"
+  } else if(this_dataset == "fia_short") {
+
+    cache_loc = "fia"
+  } else {
+    cache_loc = this_dataset
+  }
+
+  ## Set up the cache and config
+  db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", paste0("drake-cache-", cache_loc, ".sqlite")))
+  cache <- storr::storr_dbi("datatable", "keystable", db)
+
+  all_ct[[i]] <- readd(all_cts, cache = cache)
+
+  all_ct[[i]] <- filter(all_ct[[i]], source == "observed")
+
+
+  DBI::dbDisconnect(db)
+  rm(cache)
+  rm(db)
+}
+
+
+all_ct <- bind_rows(all_ct)
+
+write.csv(all_ct, here::here("analysis", "rev_prototyping", "all_ct_jk.csv"), row.names = F)

### 2021-03-13 analysis/rev_prototyping/revision_results.Rmd

--- 2021-03-11 analysis/rev_prototyping/revision_results.Rmd
@@
 all_ct <- rbind(all_ct, fia_ct)
-
 all_ct <- all_ct %>%
@@
   filter(nparts > 40) %>%
+  #mutate(dat = ifelse(nparts < 1000, paste0(dat, "_small"), dat)) %>%
   select(dat, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
@@
 
-ggplot(filter(all_di_shapes_long, metric_mod == "mean"), aes(value)) +
-  geom_histogram(bins = 40) +
-  #facet_grid(rows = vars(dat), cols = vars(metric_name), scales = "free", switch = "y") +
-  facet_wrap(vars(metric_name, dat), scales = "free", ncol = 5) +
-  geom_vline(xintercept = c(2.5, 97.5))
-
 all_di_shapes_high <- all_di_shapes_long %>%
@@
   group_by(dat, metric_name) %>%
-  summarize(proportion_high = mean(value > 95))
+  summarize(proportion_high = mean(value > 97.5),
+            n = dplyr::n())
 
 all_di_shapes_high %>%
-  tidyr::pivot_wider(id_cols = dat, names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")
+  tidyr::pivot_wider(id_cols = c(dat, n), names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")
 
@@
   group_by(dat, metric_name) %>%
-  summarize(proportion_low = mean(value <5))
+  summarize(proportion_low = mean(value <2.5))
 
@@
 
+all_di_shapes_high <- all_di_shapes_long %>%
+  mutate(in_fia = ifelse(dat == "fia", "FIA", "Other")) %>%
+  filter(metric_mod == "excl") %>%
+  group_by(in_fia, metric_name) %>%
+  summarize(proportion_high = mean(value >97.5))
+
+all_di_shapes_high %>%
+  tidyr::pivot_wider(id_cols = in_fia, names_from = metric_name, values_from = proportion_high) %>%
+  mutate(dir = "high")
+
+all_di_shapes_low <- all_di_shapes_long %>%
+  mutate(in_fia = ifelse(grepl("fia", dat), "FIA", "Other")) %>%
+  filter(metric_mod == "incl") %>%
+  group_by(in_fia, metric_name) %>%
+  summarize(proportion_low = mean(value <2.5))
+
+all_di_shapes_low %>%
+  tidyr::pivot_wider(id_cols = in_fia, names_from = metric_name, values_from = proportion_low) %>%
+  mutate(dir = "LOW")
+
 ```
-<!-- ``` -->
-<!-- ```{r} -->
 
-<!-- ggplot(all_di, aes((real_po / sim_pos_from_best), real_po_percentile_excl, color =  real_po_percentile_excl > 95)) + -->
-<!--   geom_point(alpha = .3)  -->
+### For very small communities
 
-<!-- all_di %>% -->
-<!--   mutate(rat = real_po / sim_pos_from_best, -->
-<!--          dev = real_po_percentile_excl > 95) %>% -->
-<!--   group_by(dev) %>% -->
-<!--   summarize(minrat = min(rat), -->
-<!--             maxrat = max(rat), -->
-<!--             meanrat = mean(rat), -->
-<!--             mindis = min(real_po - sim_pos_from_best), -->
-<!--             maxdis = max(real_po - sim_pos_from_best)) -->
+```{r}
+all_di <- all_di %>%
+  mutate(very_small = nparts < 2000)
 
-<!-- ggplot(all_di, aes(nparts, sim_pos_from_best)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10() -->
+```
 
-<!-- ggplot(all_di, aes(nparts, sim_pos_from_best, color = dat)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10()  + -->
-<!--   scale_color_viridis_d() + -->
-<!--   theme(legend.position = "top") -->
+#### Central tendency
 
-<!-- ggplot(all_di, aes(s0, n0, color =  sim_pos_from_best)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10()  + -->
-<!--   scale_y_log10() + -->
-<!--   scale_color_viridis_c() + -->
-<!--   theme(legend.position = "top") -->
-<!-- ``` -->
+```{r}
+
+all_di %>%
+  filter(nparts > 20) %>%
+  group_by(dat, very_small) %>%
+  summarize(prop_high_po = mean(real_po_percentile_excl > 97.5, na.rm = T),
+            nsites = dplyr::n()) %>%
+  tidyr::pivot_wider(id_cols = dat, names_from = very_small, values_from = c(prop_high_po, nsites))
+
+ggplot(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund"), nparts > 20), aes(real_po_percentile_mean)) +
+  geom_histogram(bins = 40) +
+  facet_wrap(vars(dat, very_small), scales = "free_y", ncol = 2)
+```
+#### Shape metrics
+
+```{r}
+
+all_di_shapes_long <- all_di  %>%
+  filter(nparts > 40, dat %in% c("mcdb", "misc_abund", "fia")) %>%
+  #mutate(dat = ifelse(nparts < 1000, paste0(dat, "_small"), dat)) %>%
+  select(dat, very_small, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
+  rename(skew = skew_percentile,
+         skewX = skew_percentile_excl,
+         simp = simpson_percentile,
+         simpX = simpson_percentile_excl,
+         shan = shannon_percentile,
+         shanX = shannon_percentile_excl,
+         nsng = nsingletons_percentile,
+         nsngX = nsingletons_percentile_excl) %>%
+  mutate(skewM = (skew + skewX) / 2,
+         simpM = (simp+ simpX)/2,
+         shanM = (shan+ shanX)/2,
+         nsngM = (nsng+ nsngX)/2) %>%
+  tidyr::pivot_longer(c(-dat, -very_small), names_to = "metric", values_to = "value") %>%
+  mutate(metric_name = substr(metric, 0, 4),
+         metric_mod = ifelse(substr(metric, 5, 5) == "X", "excl", ifelse(substr(metric, 5,5) == "M", "mean", "incl")))
+
+ggplot(filter(all_di_shapes_long, metric_mod == "mean"), aes(value)) +
+  geom_histogram(bins = 40) +
+  #facet_grid(rows = vars(dat), cols = vars(metric_name), scales = "free", switch = "y") +
+  facet_wrap(vars(metric_name, dat, very_small), scales = "free", ncol = 5) +
+  geom_vline(xintercept = c(2.5, 97.5))
+
+all_di_shapes_high <- all_di_shapes_long %>%
+  filter(metric_mod == "excl") %>%
+  group_by(dat, metric_name, very_small) %>%
+  summarize(proportion_high = mean(value > 97.5),
+            n = dplyr::n())
+
+all_di_shapes_high %>%
+  tidyr::pivot_wider(id_cols = c(dat, n, very_small), names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")
+
+all_di_shapes_low <- all_di_shapes_long %>%
+  filter(metric_mod == "incl") %>%
+  group_by(dat, metric_name, very_small) %>%
+  summarize(proportion_low = mean(value <2.5),
+            n = dplyr::n())
+
+all_di_shapes_low %>%
+  tidyr::pivot_wider(id_cols = c(dat, n, very_small), names_from = metric_name, values_from = proportion_low) %>%
+  mutate(dir = "LOW")
+
+```
+
+## Narrowness of the expectation
+
+### Central tendency
+
+```{r}
+
+ggplot(filter(all_di, nparts > 20), aes(nparts, sim_pos_from_best, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10()
+# 
+# ggplot(filter(all_di, nparts > 20, nparts < 1000), aes(nparts, sim_pos_from_best, color = log(n0/s0))) +
+#   geom_point() +
+#   scale_x_log10() +
+#   theme(legend.position = "top")
+# 
+# ggplot(filter(all_di, nparts > 10, nparts < 100000), aes(nparts, sim_pos_from_best, color = log(n0/s0))) +
+#   geom_point() +
+#   scale_x_log10() +
+#   theme(legend.position = "top")
+# 
+# 
+# ggplot(filter(all_di, nparts > 10, nparts > 100000), aes(nparts, sim_pos_from_best, color = log(n0/s0))) +
+#   geom_point() +
+#   scale_x_log10() +
+#   theme(legend.position = "top")
+```
+
+### Shape metrics
+
+```{r}
+
+ggplot(filter(all_di, nparts > 40, s0 > 2), aes(nparts, skew_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10()
+
+ggplot(filter(all_di, nparts > 40), aes(nparts, simpson_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10()
+
+ggplot(filter(all_di, nparts > 40), aes(nparts, shannon_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10()
+
+ggplot(filter(all_di, nparts > 40), aes(nparts, nsingletons_95_ratio_2t, color = log(n0/s0))) +
+  geom_point() +
+  scale_x_log10()
+
+```
+
+## Resampling
+
+### Undersampling of rare species
+
+#### Central tendency
+
+```{r}
+
+all_di_singletons <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F) %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 != s0,
+         s0 != 1,
+         singletons,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20) %>%
+  left_join(all_ct) %>%
+  mutate(in_fia = ifelse(Dataset == "FIA", "FIA", "Other datasets")) %>%
+  right_join(select(all_di, dat, site))
+
+all_di_singletons %>%
+  group_by(dat) %>%
+  summarize(prop_high_po = mean(real_po_percentile_excl > 95, na.rm = T),
+            nsites = dplyr::n()) %>%
+  left_join(
+    all_di %>%
+       group_by(dat) %>%
+  summarize(prop_high_po_real = mean(real_po_percentile_excl > 95, na.rm = T),
+            nsites_real = dplyr::n())
+  )
+
+```
+
+#### Shape metrics
+
+```{r}
+
+all_di_shapes_long <- all_di  %>%
+  filter(nparts > 40) %>%
+  #mutate(dat = ifelse(nparts < 1000, paste0(dat, "_small"), dat)) %>%
+  select(dat, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
+  rename(skew = skew_percentile,
+         skewX = skew_percentile_excl,
+         simp = simpson_percentile,
+         simpX = simpson_percentile_excl,
+         shan = shannon_percentile,
+         shanX = shannon_percentile_excl,
+         nsng = nsingletons_percentile,
+         nsngX = nsingletons_percentile_excl) %>%
+  mutate(skewM = (skew + skewX) / 2,
+         simpM = (simp+ simpX)/2,
+         shanM = (shan+ shanX)/2,
+         nsngM = (nsng+ nsngX)/2) %>%
+  tidyr::pivot_longer(-dat, names_to = "metric", values_to = "value") %>%
+  mutate(metric_name = substr(metric, 0, 4),
+         metric_mod = ifelse(substr(metric, 5, 5) == "X", "excl", ifelse(substr(metric, 5,5) == "M", "mean", "incl")))
+
+all_di_shapes_high <- all_di_shapes_long %>%
+  filter(metric_mod == "excl") %>%
+  group_by(dat, metric_name) %>%
+  summarize(proportion_high = mean(value > 97.5),
+            n = dplyr::n())
+all_di_shapes_low <- all_di_shapes_long %>%
+  filter(metric_mod == "incl") %>%
+  group_by(dat, metric_name) %>%
+  summarize(proportion_low = mean(value <2.5),
+            n = dplyr::n())
+
+all_di_shapes_long_s <- all_di_singletons  %>%
+  right_join(select(filter(all_di, nparts > 40), dat, site)) %>%
+  #mutate(dat = ifelse(nparts < 1000, paste0(dat, "_small"), dat)) %>%
+  select(dat, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
+  rename(skew = skew_percentile,
+         skewX = skew_percentile_excl,
+         simp = simpson_percentile,
+         simpX = simpson_percentile_excl,
+         shan = shannon_percentile,
+         shanX = shannon_percentile_excl,
+         nsng = nsingletons_percentile,
+         nsngX = nsingletons_percentile_excl) %>%
+  mutate(skewM = (skew + skewX) / 2,
+         simpM = (simp+ simpX)/2,
+         shanM = (shan+ shanX)/2,
+         nsngM = (nsng+ nsngX)/2) %>%
+  tidyr::pivot_longer(-dat, names_to = "metric", values_to = "value") %>%
+  mutate(metric_name = substr(metric, 0, 4),
+         metric_mod = ifelse(substr(metric, 5, 5) == "X", "excl", ifelse(substr(metric, 5,5) == "M", "mean", "incl")))
+
+all_di_shapes_high_s <- all_di_shapes_long_s %>%
+  filter(metric_mod == "excl") %>%
+  group_by(dat, metric_name) %>%
+  summarize(proportion_high = mean(value > 97.5),
+            n = dplyr::n())
+all_di_shapes_low_s <- all_di_shapes_long_s %>%
+  filter(metric_mod == "incl") %>%
+  group_by(dat, metric_name) %>%
+  summarize(proportion_low = mean(value <2.5),
+            n = dplyr::n())
+
+all_di_shapes_high %>%
+  tidyr::pivot_wider(id_cols = c(dat, n), names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH", adj = F) %>%
+  bind_rows(all_di_shapes_high_s %>%
+  tidyr::pivot_wider(id_cols = c(dat, n), names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH", adj = T)) %>%
+  arrange(dat, adj)
+
+all_di_shapes_low %>%
+  tidyr::pivot_wider(id_cols = c(dat, n), names_from = metric_name, values_from = proportion_low) %>%
+  mutate(dir = "LOW", adj = F) %>%
+  bind_rows(all_di_shapes_low_s %>%
+       tidyr::pivot_wider(id_cols = c(dat, n), names_from = metric_name, values_from = proportion_low) %>% mutate(dir = "LOW", adj = T)) %>%
+  arrange(dat, adj)
+
+```
+
+### Jackknife resampling
+
+```{r}
+
+jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv")) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
+
+jk_cts <- read.csv(here::here("analysis", "rev_prototyping", "all_ct_jk.csv")) %>%
+
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
+
+jk_di <- jk_di_full %>%
+  left_join(jk_cts) %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup() %>%
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile,shannon_percentile_excl,  nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95_ratio_2t, skew_95_ratio_2t, simpson_95_ratio_2t, shannon_95_ratio_2t, sim_pos_from_best, real_po_percentile, real_po_percentile_excl, nparts)
+
+jk_di_means <- jk_di %>%
+  group_by(dat, site_source) %>%
+  summarise_at(vars(-group_cols(), -site), mean)
+
+all_di_actual <- all_di %>%
+  filter(!singletons) %>%
+  mutate(site_source = as.character(site)) %>%
+  select(dat, site_source,  s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile,shannon_percentile_excl,  nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_95_ratio_2t, skew_95_ratio_2t, simpson_95_ratio_2t, shannon_95_ratio_2t, sim_pos_from_best, real_po_percentile, real_po_percentile_excl, nparts)
+
+colnames(all_di_actual)[ 3:ncol(all_di_actual)] <- paste0(colnames(all_di_actual)[3:ncol(all_di_actual)], "_actual")
+
+jk_di_results <- left_join(jk_di, all_di_actual)
+jk_di_mean_results <- left_join(jk_di_means, all_di_actual)
+
+```
+
+#### Central tendency
+
+```{r}
+jk_di_mean_results %>%
+  filter(nparts > 20) %>%
+  select(dat, real_po_percentile_excl, real_po_percentile_excl_actual) %>%
+  group_by(dat) %>%
+  summarize(high_dissimilarity_actual = mean(real_po_percentile_excl_actual > 95, na.rm = T),
+            high_dissimilarity_jk = mean(real_po_percentile_excl > 95, na.rm= T),
+            n = dplyr::n())
+
+```
+
+#### Shape metrics
+
+```{r}
+
+shapecols <- c(colnames(jk_di_mean_results)[ grepl("skew", colnames(jk_di_mean_results))],
+               colnames(jk_di_mean_results)[ grepl("simpson", colnames(jk_di_mean_results))],
+               colnames(jk_di_mean_results)[ grepl("shannon", colnames(jk_di_mean_results))],
+               colnames(jk_di_mean_results)[ grepl("nsingletons", colnames(jk_di_mean_results))])
+
+shapecols <- shapecols[ grepl("percentile", shapecols)]
+
+shapecols_high <- shapecols[ grepl("excl", shapecols)]
+
+is.high <- function(x) {
+  return(x > 97.5)
+}
+
+jk_shapes_high <- jk_di_mean_results %>%
+  filter(nparts > 40, nparts_actual > 40) %>%
+  select(dat, (shapecols_high)) %>%
+  mutate_at(vars(shapecols_high), .funs = is.high) %>%
+  group_by(dat) %>%
+  summarize_at(vars(shapecols_high), .funs = mean) %>%
+  mutate(dir = "HIGH")
+
+shapecols_low <- shapecols[ !grepl("excl", shapecols)]
+jk_shapes_high
+is.low <- function(x) {
+  return(x < 2.5)
+}
+
+jk_shapes_low <- jk_di_mean_results %>%
+    filter(nparts > 40, nparts_actual > 40) %>%
+
+  select(dat, (shapecols_low)) %>%
+  mutate_at(vars(shapecols_low), .funs = is.low) %>%
+  group_by(dat) %>%
+  summarize_at(vars(shapecols_low), .funs = mean) %>%
+  mutate(dir = "LOW")
+jk_shapes_low
+```
+
+### Narrowness
+
+```{r}
+
+ggplot(jk_di_mean_results, aes(sim_pos_from_best_actual)) +
+  geom_histogram(alpha = .5) +
+  geom_histogram(aes(sim_pos_from_best), fill="blue", alpha = .5) +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(jk_di_mean_results, s0 > 2, nparts > 40, nparts_actual > 40), aes(skew_95_ratio_2t_actual)) +
+  geom_histogram(alpha = .5) +
+  geom_histogram(aes(skew_95_ratio_2t), fill="blue", alpha = .5) +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(jk_di_mean_results, nparts > 40, nparts_actual > 40), aes(simpson_95_ratio_2t_actual)) +
+  geom_histogram(alpha = .5) +
+  geom_histogram(aes(simpson_95_ratio_2t), fill="blue", alpha = .5) +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(jk_di_mean_results, nparts > 40, nparts_actual > 40), aes(shannon_95_ratio_2t_actual)) +
+  geom_histogram(alpha = .5) +
+  geom_histogram(aes(shannon_95_ratio_2t), fill="blue", alpha = .5) +
+  facet_wrap(vars(dat), scales = "free_y")
+
+ggplot(filter(jk_di_mean_results, nparts > 40, nparts_actual > 40), aes(nsingletons_95_ratio_2t_actual)) +
+  geom_histogram(alpha = .5) +
+  geom_histogram(aes(nsingletons_95_ratio_2t), fill="blue", alpha = .5) +
+  facet_wrap(vars(dat), scales = "free_y")
+
+```

### 2021-03-16 analysis/rev_prototyping/manuscript_main_rev.Rmd
whoff

---
title: "Figures and results for main manuscript"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)

all_ct <-  read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"), stringsAsFactors = F)

fia_ct <- read.csv(here::here("fia_cts.csv"))

all_ct <- rbind(all_ct, fia_ct)
all_ct <- all_ct %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))

all_di <- all_di %>%
  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
         log_nsamples = log(nsamples),
         log_s0 = log(s0),
         log_n0 = log(n0)) %>%
  filter(n0 != s0,
         s0 != 1,
         !singletons,
         n0 != (s0 + 1)) %>%
  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
  mutate(Dataset = dat,
         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
  filter(nparts > 20) %>%
  left_join(all_ct)

all_di <- all_di %>%
  group_by_all() %>%
  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl),
         skew_percentile_mean = mean(skew_percentile, skew_percentile_excl),
        simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl),
         shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl),
         nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl),) %>%
  ungroup()

all_di <- all_di %>%
  mutate(in_fia = ifelse(Dataset == "FIA", "FIA", "Other datasets"))

```

# Datasets by S and N (Figure 1)

```{r, fig.dim = c(7,7)}

s4_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
  geom_point(alpha = .1) +
  geom_point(data = filter(all_di), alpha = .4) +
  theme_bw() +
  scale_color_viridis_d(end = .9) +
  ggtitle("Communities by S and N") +
  xlab("Species richness (S); note log scale") +
  ylab("Total abundance (N); note log scale") +
  scale_x_log10() +
  scale_y_log10()

plot(s4_fig1)
```

# Illustrations of 95% interval (Figure 2)

To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.

<!-- ```{r, fig.dim = c(7,7)} -->
<!-- library(drake) -->

<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite")) -->
<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->
<!-- cache$del(key = "lock", namespace = "session") -->

<!-- net_summary <- readd(all_di_summary, cache = cache) -->

<!-- net_summary <- net_summary %>% -->
<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) -->

<!-- example_fs <- readd(fs_s_44_n_13360, cache = cache) -->

<!-- example_di <- readd(di_fs_s_44_n_13360, cache =cache) -->

<!-- example_fs <- example_fs %>% -->
<!--   left_join(example_di) %>% -->
<!--   left_join(net_summary) -->

<!-- example_fs2 <- readd(fs_s_13_n_315, cache = cache) -->

<!-- example_di2 <- readd(di_fs_s_13_n_315, cache =cache) -->

<!-- example_fs2 <- example_fs2 %>% -->
<!--   left_join(example_di2) %>% -->
<!--   left_join(net_summary) -->

<!-- example_fs3 <- readd(fs_s_4_n_34, cache = cache) -->

<!-- example_di3 <- readd(di_fs_s_4_n_34, cache =cache) -->

<!-- example_fs3 <- example_fs3 %>% -->
<!--   left_join(example_di3) %>% -->
<!--   left_join(net_summary) -->

<!-- breadth_plots <- list( -->

<!--   ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) + -->
<!--     geom_line(alpha = .25) + -->
<!--     theme_bw() + -->
<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
<!--     ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) + -->
<!--     theme(legend.position = "right") + -->
<!--     xlab("Rank") + -->
<!--     ylab("Abundance"), -->

<!--   ggplot(example_fs3, aes(skew)) + -->
<!--   #  geom_density() + -->
<!--     geom_histogram(bins = 50) + -->
<!--     theme_bw() + -->
<!--     geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") + -->
<!--     ggtitle("", subtitle = paste0("Breadth index: ", round((example_fs3$skew_95_ratio_2t[1]), 2))) + -->
<!--     xlab("Skewness") + -->
<!--     ylab("Count"), -->

<!--   ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) + -->
<!--     geom_line(alpha = .1) + -->
<!--     theme_bw() + -->
<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
<!--     ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) + -->
<!--     theme(legend.position = "right")+ -->
<!--     xlab("Rank") + -->
<!--     ylab("Abundance") + -->
<!--     ylim(0, 200), # Remove 3 sads that make the axes too big to be interpretable -->

<!--   ggplot(example_fs2, aes(skew)) + -->
<!--   #  geom_density() + -->
<!--     geom_histogram(bins = 50) + -->
<!--     theme_bw() + -->
<!--     geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") + -->
<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs2$skew_95_ratio_1t[1]), 2)))+ -->
<!--     xlab("Skewness") + -->
<!--     ylab("Count"), -->

<!--   ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) + -->
<!--     geom_line(alpha = .1) + -->
<!--     theme_bw() + -->
<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
<!--     ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) + -->
<!--     theme(legend.position = "right") + -->
<!--     ylim(0, 4000) + # Remove a very few very very uneven SADs that make the scale too big to be interpretable -->
<!--     theme(axis.text.y = element_text(size = 6, angle = 60))+ -->
<!--     xlab("Rank") + -->
<!--     ylab("Abundance"), -->

<!--   ggplot(example_fs, aes(skew)) + -->
<!--    # geom_density() + -->
<!--     geom_histogram(bins = 50) + -->
<!--     theme_bw() + -->
<!--     geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") + -->
<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs$skew_95_ratio_1t[1]), 2)))+ -->
<!--     xlab("Skewness") + -->
<!--     ylab("Count") -->

<!-- ) -->

<!-- fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->

<!-- plot(fig_1) -->

<!-- DBI::dbDisconnect(db) -->
<!-- rm(cache) -->
<!-- rm(db) -->
<!-- ``` -->

# Dissimilarity (Supplement)

```{r, fig.dim = c(3, 6)}
plot_percentile_hist <- function(di_df, col_name, plot_name, tails = 2, facetvar = "Dataset", min_s0 = 0) {

  if(tails == 2) {
    cutoff_percentiles = c(2.5, 97.5)
    min_nparts = 40
  } else if (tails== 1) {
    cutoff_percentiles = c(95)
    min_nparts = 20
  }

  di_df <- di_df %>%
    mutate(response = (di_df[[col_name]]),
           facetvar = di_df[[facetvar]])

  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
    geom_histogram(bins = 40, boundary = 100) +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_vline(xintercept = cutoff_percentiles, color = "red") +
    ggtitle( plot_name) +
    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+ 
    theme(plot.title = element_text(size=10))

}

all_di <- all_di %>%
  mutate(`Observed \npercentile score` = ifelse(real_po_percentile_excl > 95, "High (> 95)", "Less than 95"))

```

```{r, fig.dim = c(4, 4)}
ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
  geom_point(alpha = .3) + 
  geom_point(data = filter(all_di, s0 < 0)) +
  geom_abline(slope = 1, intercept = 0) +
  scale_color_viridis_d(end = .8, direction = -1) +
  xlab("Mean of elements from feasible set") +
  ylab("Observed value") +
 ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")#,
# 
# 
# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
#   geom_point(alpha = .3) + 
#   geom_point(data = filter(all_di, s0 < 0)) +
#   scale_color_viridis_d(end = .9) +
#   xlab("Number of elements in the feasible set") +
#   ylab("Mean dissimilarity of feasible set to central tendency") +
#   scale_x_log10() +
#   ggtitle("Over the size of the feasible set")
# ), ncol = 1,
#top = textGrob("Dissimilarity to central tendency"))

```

# Metric histograms by dataset (Figure 4)

```{r first hists, fig.dim = c(9,5)}

fig_2 <- gridExtra::grid.arrange(grobs = list(

plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
  plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
   plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset")#,
  # plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
  ), ncol = 4,
top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
```

# Results table

```{r}
diss_results <- all_di %>%
  filter(nparts > 20) %>%
  group_by(Dataset) %>%
  summarize(high_diss = mean(real_po_percentile_excl > 95),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
  select(-nsites)

skew_results <- all_di %>%
  filter(nparts > 40, s0 > 2) %>%
   group_by(Dataset) %>%
  summarize(high_skew = mean(skew_percentile_excl > 97.5),
            low_skew = mean(skew_percentile < 2.5),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
  select(-nsites)

metric_results <- all_di %>%
  filter(nparts > 40) %>%
   group_by(Dataset) %>%
  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
            low_simpson = mean(simpson_percentile < 2.5),
            high_shannon = mean(shannon_percentile_excl > 97.5),
            low_shannon = mean(shannon_percentile < 2.5),
            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
            low_nsingletons = mean(nsingletons_percentile < 2.5),
            nsites = dplyr::n()) %>%
  ungroup() %>%
  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
  select(-nsites)

all_results <- left_join(diss_results, skew_results) %>%
  left_join(metric_results)

cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")

all_results %>%
  select(cols1)

cols2 <- c("Dataset", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")

all_results %>%
  select(cols2)

```

# Narrowness

```{r, fig.dim = c(3, 6)}

plot_narrowness <- function(di_df, yvar, yvar_name) {

  if(grepl("sim_pos", yvar)) {
    min_nparts = 20
  } else {
    min_nparts = 40
  }

  di_df <- di_df %>%
    mutate(response = (di_df[[yvar]])) %>%
    filter(nparts > min_nparts,
           nparts < 10 ^ 50)

  ggplot(di_df, aes(nparts, response, color = Dataset)) +
  geom_point(alpha = .3) +
  geom_point(data = filter(di_df, s0 < 0)) +
  scale_color_viridis_d(end = .9) +
  xlab("") +
  ylab("") +
  scale_x_log10() +
  ggtitle(yvar_name) + 
    theme(legend.position = "none")+ 
    theme(plot.title = element_text(size=10))
}

plot_narrowness_legend <- function(di_df) {

  legend_df <- di_df %>%
    select(Dataset) %>%
    distinct() %>%
    mutate(ymark = dplyr::row_number())

    ggplot(legend_df, aes(1, ymark, color = Dataset)) +
      geom_label(aes(x = 2, y = ymark, label = Dataset)) +
      geom_point(size = 4) +
  scale_color_viridis_d(end = .9) +
  xlab("") +
  ylab("") +
    theme(legend.position = "none") +
      xlim(1, 3) + theme(
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
      ) +
      ggtitle("Dataset")

}
# 
# gridExtra::grid.arrange(grobs = list(
#   plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity to central tendency"),
#   plot_narrowness_legend(all_di)),
#   ncol = 1)
```

```{r, fig.dim = c(7,4)}

gridExtra::grid.arrange(grobs = list(
  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .5, r = 0, t = 0, l = 0, unit = "in")
), gridExtra::grid.arrange(grobs = list(
  plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
  plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness"),
    plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity"),
    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species")
  ), ncol = 2)), ncol = 2, widths = c(2, 4))

```

<!-- # Breadth index by dataset (Figure 3) -->

<!-- ```{r, fig.dim = c(7,7)} -->

<!-- fig_3 <- gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Skewness") + -->
<!--     xlim(0, 1), -->

<!--   ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Evenness") + -->
<!--     xlim(0, 1) -->
<!-- ), ncol = 2, -->
<!-- top = textGrob("Figure 3", gp = gpar(fill = "white")), -->
<!-- left = "Number of communities",  -->
<!-- bottom = "Breadth index (ranges 0-1, with 1 being very broad)") -->

<!-- plot(fig_3) -->

<!-- ``` -->

<!-- # Comparison of FIA and comparably sized communities (Figure 4) -->

<!-- ```{r, fig.dim = c(7,7)} -->

<!-- fia_max_s = max(filter(all_di, dat == "fia")$s0) -->
<!-- fia_max_n = max(filter(all_di, dat == "fia")$n0) -->

<!-- fia = filter(all_di, dat == "fia") -->

<!-- small_di <- all_di %>% -->
<!--   filter(s0 <= fia_max_s, -->
<!--          n0 <= fia_max_n) %>% -->
<!--   mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"), -->
<!--          right_corner = FALSE) -->

<!-- for(i in 1:nrow(small_di)) { -->
<!--   if(small_di$dat[i] != "fia") { -->
<!--     fia_match_s0 = filter(fia, s0 >= small_di$s0[i]) -->

<!--     max_n0_for_this_s0 = max(fia_match_s0$n0) -->

<!--     small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0 -->

<!--   } -->
<!-- } -->

<!-- small_di <- small_di %>% -->
<!--   filter(!right_corner) -->
<!-- not_fia <- filter(small_di, fia_yn != "fia") -->
<!-- fia = filter(small_di, dat == "fia") -->

<!-- small_di_s_n <- small_di %>% -->
<!--   select(s0, n0) %>% -->
<!--   distinct() %>% -->
<!--   mutate(in_fia = FALSE, -->
<!--          in_not_fia = FALSE) -->

<!-- for(i in 1:nrow(small_di_s_n)) { -->

<!--   this_s0 = small_di_s_n$s0[i] -->
<!--   this_n0 = small_di_s_n$n0[i] -->

<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->

<!--   small_di_s_n$in_fia[i] = nrow(fia_matches) > 0  -->
<!--   small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0  -->

<!-- } -->

<!-- small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia) -->

<!-- set.seed(1977) -->

<!-- subsamples <- list() -->

<!-- for(i in 1:nrow(small_di_s_n)) { -->

<!--   this_s0 = small_di_s_n$s0[i] -->
<!--   this_n0 = small_di_s_n$n0[i] -->

<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->

<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->

<!--   n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches)) -->

<!--   fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F) -->
<!--   not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F) -->

<!--   subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ])) -->

<!-- } -->

<!-- sub_di <- bind_rows(subsamples) %>% -->
<!--   mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets")) -->

<!-- simpson_ks <- filter(sub_di, nparts > 40) %>% -->
<!--   select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>%  -->
<!--   group_by(Dataset, s0, n0) %>% -->
<!--   mutate(pairing = dplyr::row_number()) %>% -->
<!--   ungroup() %>% -->
<!--   tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(simpson_95_ratio_1t, simpson_percentile)) -->

<!-- simpson_breadth <- ks.test(simpson_ks$simpson_95_ratio_1t_FIA, simpson_ks$`simpson_95_ratio_1t_Other datasets`) -->

<!-- simpson_percent <- ks.test(simpson_ks$simpson_percentile_FIA, simpson_ks$`simpson_percentile_Other datasets`) -->
<!-- simpson_breadth -->
<!-- simpson_percent -->

<!-- skewness_ks <- filter(sub_di, nparts > 40) %>% -->
<!--   select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>%  -->
<!--   group_by(Dataset, s0, n0) %>% -->
<!--   mutate(pairing = dplyr::row_number()) %>% -->
<!--   ungroup() %>% -->
<!--   tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(skew_95_ratio_1t, skew_percentile)) -->

<!-- skewness_breadth <- ks.test(skewness_ks$skew_95_ratio_1t_FIA, skewness_ks$`skew_95_ratio_1t_Other datasets`) -->

<!-- skewness_percent <- ks.test(skewness_ks$skew_percentile_FIA, skewness_ks$`skew_percentile_Other datasets`) -->
<!-- skewness_breadth -->
<!-- skewness_percent -->

<!-- fig_4 <- gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Breadth index", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("") + -->
<!--     ggtitle("", subtitle = "Evenness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Percentile rank", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("")+ -->
<!--     ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white"))) -->

<!-- plot(fig_4) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- pdf("figure_1.pdf", title = "Figure 1", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!-- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->
<!-- dev.off() -->

<!-- pdf("figure_2.pdf", title = "Figure 2", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!--  gridExtra::grid.arrange(grobs = list( -->

<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(skew_percentile_excl)) + -->
<!--     geom_histogram(bins = 100) + -->
<!--     geom_vline(xintercept = 95, color = "red") + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") + -->
<!--     xlab("") + -->
<!--     ylab(""),# + -->
<!--   #  xlab("Percentile rank of observed value relative to feasible set") + -->
<!--     #ylab("Number of communities") , -->

<!--   ggplot(filter(all_di, nparts > 20), aes(simpson_percentile)) +  -->
<!--     geom_histogram(bins = 100) + -->
<!--     geom_vline(xintercept = 5, color = "red") + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") +  -->
<!--     xlab("") + -->
<!--     ylab("")#+ -->
<!--     #xlab("Percentile rank of observed value relative to feasible set") + -->
<!--   #  ylab("Number of communities") -->
<!-- ), ncol = 2, -->
<!-- top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
<!--  dev.off() -->

<!-- pdf("figure_3.pdf", title = "Figure 3", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!-- gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Skewness") + -->
<!--     xlim(0, 1), -->

<!--   ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) + -->
<!--     geom_histogram() + -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
<!--     xlab("") + -->
<!--     ylab("") + -->
<!--     ggtitle("Evenness") + -->
<!--     xlim(0, 1) -->
<!-- ), ncol = 2, -->
<!-- top = textGrob("Figure 3", gp = gpar(fill = "white")), -->
<!-- left = "Number of communities",  -->
<!-- bottom = "Breadth index (ranges 0-1, with 1 being very broad)") -->

<!-- dev.off() -->

<!-- pdf("figure_4.pdf", title = "Figure 4", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
<!--  gridExtra::grid.arrange(grobs = list( -->
<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Breadth index", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Breadth index") + -->
<!--     ylab("") + -->
<!--     ggtitle("", subtitle = "Evenness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("Number of communities") + -->
<!--     ggtitle("Percentile rank", subtitle = "Skewness"), -->

<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) + -->
<!--     geom_histogram()+ -->
<!--     theme_bw() + -->
<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
<!--     xlab("Percentile rank") + -->
<!--     ylab("")+ -->
<!--     ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white"))) -->
<!-- dev.off() -->
<!-- ``` -->

### 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
figs

@@
        df_print: kable
+       toc: true
 ---
@@
 
-```{r first hists, fig.dim = c(9,5)}
+```{r first hists, fig.dim = c(10,5)}
 
@@
   plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-   plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset")#,
-  # plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-  ), ncol = 4,
+  plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
 top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
@@
     min_nparts = 20
+    ylabel = "Mean dissimilarity"
   } else {
     min_nparts = 40
+    ylabel = "Breadth index"
   }
@@
     xlab("") +
-  ylab("") +
+    ylab(ylabel) +
     scale_x_log10() +
@@
 gridExtra::grid.arrange(grobs = list(
-  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .5, r = 0, t = 0, l = 0, unit = "in")
-), gridExtra::grid.arrange(grobs = list(
+  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")),
+  gridExtra::grid.arrange(grobs = list(
     plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
-  plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness"),
-    plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity"),
-    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species")
-  ), ncol = 2)), ncol = 2, widths = c(2, 4))
+    plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
+    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species"),
+       plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
+  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"))
 
@@
 
-<!-- # Breadth index by dataset (Figure 3) -->
+```{r}
 
-<!-- ```{r, fig.dim = c(7,7)} -->
+plot_narrowness_hist <- function(di_df, col_name, plot_name, facetvar = "Dataset", min_s0 = 0) {
 
-<!-- fig_3 <- gridExtra::grid.arrange(grobs = list( -->
-<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) + -->
-<!--     geom_histogram() + -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
-<!--     xlab("") + -->
-<!--     ylab("") + -->
-<!--     ggtitle("Skewness") + -->
-<!--     xlim(0, 1), -->
+  if(grepl("sim_pos", col_name)) {
+    xvarname = "Mean dissimilarity"
+    min_nparts = 40
+  } else {
+    min_nparts = 20
+    xvarname = "Breadth index"
+  }
 
-<!--   ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) + -->
-<!--     geom_histogram() + -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
-<!--     xlab("") + -->
-<!--     ylab("") + -->
-<!--     ggtitle("Evenness") + -->
-<!--     xlim(0, 1) -->
-<!-- ), ncol = 2, -->
-<!-- top = textGrob("Figure 3", gp = gpar(fill = "white")), -->
-<!-- left = "Number of communities",  -->
-<!-- bottom = "Breadth index (ranges 0-1, with 1 being very broad)") -->
+  di_df <- di_df %>%
+    mutate(response = (di_df[[col_name]]),
+           facetvar = di_df[[facetvar]])
 
-<!-- plot(fig_3) -->
+  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
+    geom_histogram(bins = 40, boundary = 100) +
+    theme_bw() +
+    ylab("") +
+    xlab(xvarname) +
+    ggtitle( plot_name) +
+    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+ 
+    theme(plot.title = element_text(size=10))
 
-<!-- ``` -->
+}
 
-<!-- # Comparison of FIA and comparably sized communities (Figure 4) -->
+```
 
-<!-- ```{r, fig.dim = c(7,7)} -->
+```{r, fig.dim = c(10,5)}
 
-<!-- fia_max_s = max(filter(all_di, dat == "fia")$s0) -->
-<!-- fia_max_n = max(filter(all_di, dat == "fia")$n0) -->
+fig_2 <- gridExtra::grid.arrange(grobs = list(
 
-<!-- fia = filter(all_di, dat == "fia") -->
+  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
+  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
+ left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
 
-<!-- small_di <- all_di %>% -->
-<!--   filter(s0 <= fia_max_s, -->
-<!--          n0 <= fia_max_n) %>% -->
-<!--   mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"), -->
-<!--          right_corner = FALSE) -->
+```
 
-<!-- for(i in 1:nrow(small_di)) { -->
-<!--   if(small_di$dat[i] != "fia") { -->
-<!--     fia_match_s0 = filter(fia, s0 >= small_di$s0[i]) -->
+# Comparison of FIA and comparably sized communities (Figure 4)
 
-<!--     max_n0_for_this_s0 = max(fia_match_s0$n0) -->
+```{r, fig.dim = c(10, 5)}
 
-<!--     small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0 -->
+fia_max_s = max(filter(all_di, dat == "fia")$s0)
+fia_max_n = max(filter(all_di, dat == "fia")$n0)
 
-<!--   } -->
-<!-- } -->
+fia = filter(all_di, dat == "fia")
 
-<!-- small_di <- small_di %>% -->
-<!--   filter(!right_corner) -->
-<!-- not_fia <- filter(small_di, fia_yn != "fia") -->
-<!-- fia = filter(small_di, dat == "fia") -->
+small_di <- all_di %>%
+  filter(s0 <= fia_max_s,
+         n0 <= fia_max_n) %>%
+  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
+         right_corner = FALSE)
 
-<!-- small_di_s_n <- small_di %>% -->
-<!--   select(s0, n0) %>% -->
-<!--   distinct() %>% -->
-<!--   mutate(in_fia = FALSE, -->
-<!--          in_not_fia = FALSE) -->
+for(i in 1:nrow(small_di)) {
+  if(small_di$dat[i] != "fia") {
+    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
 
-<!-- for(i in 1:nrow(small_di_s_n)) { -->
+    max_n0_for_this_s0 = max(fia_match_s0$n0)
 
-<!--   this_s0 = small_di_s_n$s0[i] -->
-<!--   this_n0 = small_di_s_n$n0[i] -->
+    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
 
-<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
-<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->
+  }
+}
 
-<!--   small_di_s_n$in_fia[i] = nrow(fia_matches) > 0  -->
-<!--   small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0  -->
+small_di <- small_di %>%
+  filter(!right_corner)
+not_fia <- filter(small_di, fia_yn != "fia")
+fia = filter(small_di, dat == "fia")
 
-<!-- } -->
+small_di_s_n <- small_di %>%
+  select(s0, n0) %>%
+  distinct() %>%
+  mutate(in_fia = FALSE,
+         in_not_fia = FALSE)
 
-<!-- small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia) -->
+for(i in 1:nrow(small_di_s_n)) {
 
-<!-- set.seed(1977) -->
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
 
-<!-- subsamples <- list() -->
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
 
-<!-- for(i in 1:nrow(small_di_s_n)) { -->
+  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
+  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
 
-<!--   this_s0 = small_di_s_n$s0[i] -->
-<!--   this_n0 = small_di_s_n$n0[i] -->
+}
 
-<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
+small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
 
-<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->
+set.seed(1977)
 
-<!--   n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches)) -->
+subsamples <- list()
 
-<!--   fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F) -->
-<!--   not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F) -->
+for(i in 1:nrow(small_di_s_n)) {
 
-<!--   subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ])) -->
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
 
-<!-- } -->
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
 
-<!-- sub_di <- bind_rows(subsamples) %>% -->
-<!--   mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets")) -->
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
 
-<!-- simpson_ks <- filter(sub_di, nparts > 40) %>% -->
-<!--   select(simpson_95_ratio_1t, Dataset, simpson_percentile, s0, n0) %>%  -->
-<!--   group_by(Dataset, s0, n0) %>% -->
-<!--   mutate(pairing = dplyr::row_number()) %>% -->
-<!--   ungroup() %>% -->
-<!--   tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(simpson_95_ratio_1t, simpson_percentile)) -->
+  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
 
-<!-- simpson_breadth <- ks.test(simpson_ks$simpson_95_ratio_1t_FIA, simpson_ks$`simpson_95_ratio_1t_Other datasets`) -->
+  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
+  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
 
-<!-- simpson_percent <- ks.test(simpson_ks$simpson_percentile_FIA, simpson_ks$`simpson_percentile_Other datasets`) -->
-<!-- simpson_breadth -->
-<!-- simpson_percent -->
+  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
 
-<!-- skewness_ks <- filter(sub_di, nparts > 40) %>% -->
-<!--   select(skew_95_ratio_1t, Dataset, skew_percentile, s0, n0) %>%  -->
-<!--   group_by(Dataset, s0, n0) %>% -->
-<!--   mutate(pairing = dplyr::row_number()) %>% -->
-<!--   ungroup() %>% -->
-<!--   tidyr::pivot_wider(id_cols = c(s0, n0, pairing), names_from = Dataset, values_from = c(skew_95_ratio_1t, skew_percentile)) -->
+}
 
-<!-- skewness_breadth <- ks.test(skewness_ks$skew_95_ratio_1t_FIA, skewness_ks$`skew_95_ratio_1t_Other datasets`) -->
+sub_di <- bind_rows(subsamples) %>%
+  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
 
-<!-- skewness_percent <- ks.test(skewness_ks$skew_percentile_FIA, skewness_ks$`skew_percentile_Other datasets`) -->
-<!-- skewness_breadth -->
-<!-- skewness_percent -->
+fia_di <- filter(sub_di, fia_yn == "fia")
+other_di <- filter(sub_di, fia_yn != "fia")
 
-<!-- fig_4 <- gridExtra::grid.arrange(grobs = list( -->
-<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Breadth index") + -->
-<!--     ylab("Number of communities") + -->
-<!--     ggtitle("Breadth index", subtitle = "Skewness"), -->
+ks_compare <- function(fia_df, other_df, compare_var) {
 
-<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Breadth index") + -->
-<!--     ylab("") + -->
-<!--     ggtitle("", subtitle = "Evenness"), -->
+  if(grepl("skew", compare_var)) {
+    fia_df <- filter(fia_df, s0 > 2)
+    other_df <- filter(fia_df, s0 >2)
+  }
 
-<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Percentile rank") + -->
-<!--     ylab("Number of communities") + -->
-<!--     ggtitle("Percentile rank", subtitle = "Skewness"), -->
+  if(grepl("sim_pos", compare_var)) {
+    fia_df <- filter(fia_df, nparts > 20)
+    other_df <- filter(other_df, nparts > 20)
+  } else {
+      fia_df <- filter(fia_df, nparts > 40)
+    other_df <- filter(other_df, nparts > 40)
+  }
 
-<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Percentile rank") + -->
-<!--     ylab("")+ -->
-<!--     ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white"))) -->
+  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])
 
-<!-- plot(fig_4) -->
+  return(data.frame(
+    var = compare_var,
+    d = kstest$statistic,
+    p = kstest$p.value
+  ))
+}
 
-<!-- ``` -->
+simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
+skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
+shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
+nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
+diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
 
-<!-- ```{r} -->
-<!-- pdf("figure_1.pdf", title = "Figure 1", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
-<!-- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->
-<!-- dev.off() -->
+bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
 
-<!-- pdf("figure_2.pdf", title = "Figure 2", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
-<!--  gridExtra::grid.arrange(grobs = list( -->
+simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
+skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
+shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
+nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
+diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
 
-<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(skew_percentile_excl)) + -->
-<!--     geom_histogram(bins = 100) + -->
-<!--     geom_vline(xintercept = 95, color = "red") + -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Skewness") + -->
-<!--     xlab("") + -->
-<!--     ylab(""),# + -->
-<!--   #  xlab("Percentile rank of observed value relative to feasible set") + -->
-<!--     #ylab("Number of communities") , -->
+bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
 
-<!--   ggplot(filter(all_di, nparts > 20), aes(simpson_percentile)) +  -->
-<!--     geom_histogram(bins = 100) + -->
-<!--     geom_vline(xintercept = 5, color = "red") + -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + ggtitle("Evenness") +  -->
-<!--     xlab("") + -->
-<!--     ylab("")#+ -->
-<!--     #xlab("Percentile rank of observed value relative to feasible set") + -->
-<!--   #  ylab("Number of communities") -->
-<!-- ), ncol = 2, -->
-<!-- top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
-<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
-<!--  dev.off() -->
+fig_2 <- gridExtra::grid.arrange(grobs = list(
 
-<!-- pdf("figure_3.pdf", title = "Figure 3", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
-<!-- gridExtra::grid.arrange(grobs = list( -->
-<!--   ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x= skew_95_ratio_1t)) + -->
-<!--     geom_histogram() + -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
-<!--     xlab("") + -->
-<!--     ylab("") + -->
-<!--     ggtitle("Skewness") + -->
-<!--     xlim(0, 1), -->
+  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
+  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
+top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
 
-<!--   ggplot(filter(all_di, nparts > 20), aes(x = simpson_95_ratio_1t)) + -->
-<!--     geom_histogram() + -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y", ncol = 1) + -->
-<!--     xlab("") + -->
-<!--     ylab("") + -->
-<!--     ggtitle("Evenness") + -->
-<!--     xlim(0, 1) -->
-<!-- ), ncol = 2, -->
-<!-- top = textGrob("Figure 3", gp = gpar(fill = "white")), -->
-<!-- left = "Number of communities",  -->
-<!-- bottom = "Breadth index (ranges 0-1, with 1 being very broad)") -->
+fig_2 <- gridExtra::grid.arrange(grobs = list(
 
-<!-- dev.off() -->
+  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
+  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
+ left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
 
-<!-- pdf("figure_4.pdf", title = "Figure 4", bg = "white", paper = "letter", width = 6.5, height = 6.5) -->
-<!--  gridExtra::grid.arrange(grobs = list( -->
-<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_95_ratio_1t)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Breadth index") + -->
-<!--     ylab("Number of communities") + -->
-<!--     ggtitle("Breadth index", subtitle = "Skewness"), -->
+diss_results <- sub_di %>%
+  filter(nparts > 20) %>%
+  group_by(Dataset) %>%
+  summarize(high_diss = mean(real_po_percentile_excl > 95),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
 
-<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_95_ratio_1t)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Breadth index") + -->
-<!--     ylab("") + -->
-<!--     ggtitle("", subtitle = "Evenness"), -->
+skew_results <- sub_di %>%
+  filter(nparts > 40, s0 > 2) %>%
+  group_by(Dataset) %>%
+  summarize(high_skew = mean(skew_percentile_excl > 97.5),
+            low_skew = mean(skew_percentile < 2.5),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
+         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
 
-<!--   ggplot(filter(sub_di, nparts > 20), aes(skew_percentile_excl)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Percentile rank") + -->
-<!--     ylab("Number of communities") + -->
-<!--     ggtitle("Percentile rank", subtitle = "Skewness"), -->
+metric_results <- sub_di %>%
+  filter(nparts > 40) %>%
+  group_by(Dataset) %>%
+  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
+            low_simpson = mean(simpson_percentile < 2.5),
+            high_shannon = mean(shannon_percentile_excl > 97.5),
+            low_shannon = mean(shannon_percentile < 2.5),
+            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
+            low_nsingletons = mean(nsingletons_percentile < 2.5),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
+         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
+         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
+         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
+         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
+         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
 
-<!--   ggplot(filter(sub_di, nparts > 20), aes(simpson_percentile)) + -->
-<!--     geom_histogram()+ -->
-<!--     theme_bw() + -->
-<!--     facet_wrap(vars(Dataset), scales = "free_y")  + -->
-<!--     xlab("Percentile rank") + -->
-<!--     ylab("")+ -->
-<!--     ggtitle("", subtitle = "Evenness")), ncol = 2, top = textGrob("Figure 4", gp = gpar(fill = "white"))) -->
-<!-- dev.off() -->
-<!-- ``` -->
+all_results <- left_join(diss_results, skew_results) %>%
+  left_join(metric_results)
+
+cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+
+all_results %>%
+  select(cols1)
+
+```

### 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
gentry

@@
 
+# Gentry
+
+```{r}
+
+gentry_di <- filter(all_di, Dataset == "Gentry")
+
+gentry_di <- gentry_di %>%
+  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
+
+fig_2 <- gridExtra::grid.arrange(grobs = list(
+
+  plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"),
+  plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3),
+  plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"),
+  plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund")
+), ncol = 2,
+ left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
+
+```
+
 # Comparison of FIA and comparably sized communities (Figure 4)

### 2021-03-18 analysis/rev_prototyping/manuscript_main_rev.Rmd
get cts

@@
 ```
+
+# Resampling
+
+```{r}
+
+all_di_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))
+
+jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
+
+jk_di <- jk_di_full %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup() %>%
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl, nsingletons, nsingletons_median, nsingletons_95, mean_po_comparison_percentile, mean_po_comparison_sims, mean_po_comparison_percentile_excl, mean_po_comparison_95, skew_95_ratio_1t, simpson_95_ratio_1t, shannon_95_ratio_1t, mean_po_comparison_95_ratio_1t, nparts)
+
+jk_di_means <- jk_di %>%
+  group_by(dat, site_source) %>%
+  summarise_at(vars(-group_cols(), -site), mean) %>%
+  mutate(resampling = "jacknife") %>%
+  mutate(site = as.integer(site_source)) %>%
+  select(-site_source) %>%
+  filter(n0 != s0,
+         s0 != 1,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20)
+
+all_di_with_resamples <- all_di_with_resamples %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 != s0,
+         s0 != 1,
+       #  !singletons,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20) %>%
+  mutate(resampling = ifelse(singletons, "rarefaction", "none")) %>%
+  bind_rows(jk_di_means)
+
+prop_results <- all_di_with_resamples %>%
+ # filter(!singletons) %>%
+  group_by(Dataset, resampling) %>%
+  summarize(
+    skew_high = mean(skew_percentile_excl > 97.5),
+    skew_low = mean(skew_percentile < 2.5),
+    even_high = mean(simpson_percentile_excl > 97.5),
+    even_low = mean(simpson_percentile < 2.5),
+    shannon_high = mean(shannon_percentile_excl > 97.5),
+    shannon_low = mean(shannon_percentile < 2.5),
+    nsingletons_high = mean(nsingletons_percentile_excl > 97.5),
+    nsingletons_low = mean(nsingletons_percentile < 2.5),
+    po_high = mean(mean_po_comparison_percentile_excl > 97.5),
+    po_low = mean(mean_po_comparison_percentile < 2.5)
+  ) %>%
+  ungroup() %>%
+  tidyr::pivot_longer((-c("Dataset","resampling")), names_to = "metric", values_to = "value")
+
+```

### 2021-03-18 analysis/helper_scripts/make_all_ct.R

@@ -6,9 +6,9 @@ library(ggplot2)
 library(scadsanalysis)
 
 all_ct <- list()
-#datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "fia_small")
+datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "fia_small")
 #datasets <- c( "gentry", "mcdb", "misc_abund_short", "bbs")
-datasets <- c("bbs",  "gentry", "mcdb", "misc_abund_short", "fia_small")
+#datasets <- c("bbs",  "gentry", "mcdb", "misc_abund_short", "fia_small")
 
 
 for(i in 1:length(datasets)) {

### 2021-03-18 analysis/helper_scripts/make_all_ct_jk.R

@@ -7,8 +7,8 @@ library(scadsanalysis)
 
 all_ct <- list()
 #datasets <- c("bbs",  "gentry", "fia_short", "mcdb", "misc_abund_short", "fia_small")
-# datasets <- c( "gentry-jk", "mcdb-jk", "bbs-jk","misc-jk", "fia_small-jk", "fia_short-jk" )
-datasets <- c( "gentry-jk",  "bbs-jk","fia_small-jk", "fia_short-jk" )
+ datasets <- c( "gentry-jk", "mcdb-jk", "bbs-jk","misc-jk", "fia_small-jk", "fia_short-jk" )
+#datasets <- c( "gentry-jk",  "bbs-jk","fia_small-jk", "fia_short-jk" )
 
 
 for(i in 1:length(datasets)) {

### 2021-03-18 analysis/rev_prototyping/manuscript_main_rev.Rmd
today

--- 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 
-fia_ct <- read.csv(here::here("fia_cts.csv"))
+#fia_ct <- read.csv(here::here("fia_cts.csv"))
 
-all_ct <- rbind(all_ct, fia_ct)
+#all_ct <- rbind(all_ct, fia_ct)
 all_ct <- all_ct %>%
@@
 ```
+
+# Very small communities
+
+```{r}
+
+all_di <- all_di %>%
+  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000", "More than 2000"))
+diss_results <- all_di %>%
+  filter(nparts > 20) %>%
+  group_by(Dataset,  `Number of elements` ) %>%
+  summarize(high_diss = mean(real_po_percentile_excl > 95),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
+
+skew_results <- all_di %>%
+  filter(nparts > 40, s0 > 2) %>%
+  group_by(Dataset,  `Number of elements` ) %>%
+  summarize(high_skew = mean(skew_percentile_excl > 97.5),
+            low_skew = mean(skew_percentile < 2.5),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
+         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
+
+metric_results <- all_di %>%
+  filter(nparts > 40) %>%
+  group_by(Dataset,  `Number of elements` ) %>%
+  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
+            low_simpson = mean(simpson_percentile < 2.5),
+            high_shannon = mean(shannon_percentile_excl > 97.5),
+            low_shannon = mean(shannon_percentile < 2.5),
+            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
+            low_nsingletons = mean(nsingletons_percentile < 2.5),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
+         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
+         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
+         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
+         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
+         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
+
+all_results <- left_join(diss_results, skew_results) %>%
+  left_join(metric_results)
+
+cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+
+all_results %>%
+  select(cols1)
+
+plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "real_po_percentile_mean", "Dissimilarity") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_95_ratio_2t", "Number of rare species") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_percentile_mean", "Number of rare species") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_95_ratio_2t", "Simpson") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_percentile_mean", "Simpson") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_95_ratio_2t", "Shannon") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_percentile_mean", "Shannon") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+ggplot(all_di, aes(s0, n0, color = `Number of elements`)) +
+  geom_point() +
+  xlim(0, 30) +
+  ylim(0,150)
+
+```
+
+```{r}
+
+all_di <- all_di %>%
+  mutate( `Number of elements` = ifelse(nparts < 1000, "Less than 1000", "More than 1000"))
+diss_results <- all_di %>%
+  filter(nparts > 20) %>%
+  group_by(Dataset,  `Number of elements`) %>%
+  summarize(high_diss = mean(real_po_percentile_excl > 95),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
+ggplot(filter(all_di, dat == "mcdb"), aes(skew_95_ratio_2t)) + 
+  geom_histogram() +
+  facet_wrap(vars(`Number of elements`), scales = "free_y")
+
+skew_results <- all_di %>%
+  filter(nparts > 40, s0 > 2) %>%
+  group_by(Dataset,  `Number of elements`) %>%
+  summarize(high_skew = mean(skew_percentile_excl > 97.5),
+            low_skew = mean(skew_percentile < 2.5),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
+         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
+
+metric_results <- all_di %>%
+  filter(nparts > 40) %>%
+  group_by(Dataset, `Number of elements`) %>%
+  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
+            low_simpson = mean(simpson_percentile < 2.5),
+            high_shannon = mean(shannon_percentile_excl > 97.5),
+            low_shannon = mean(shannon_percentile < 2.5),
+            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
+            low_nsingletons = mean(nsingletons_percentile < 2.5),
+            nsites = dplyr::n()) %>%
+  ungroup() %>%
+  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
+         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
+         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
+         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
+         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
+         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
+  select(-nsites)
+
+all_results <- left_join(diss_results, skew_results) %>%
+  left_join(metric_results)
+
+cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+
+all_results %>%
+  select(cols1)
+
+```
+
+# Resampling
+
+```{r}
+
+all_di_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))
+
+jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
+
+all_ct_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"))
+
+jk_ct <- read.csv(here::here("analysis", "rev_prototyping", "all_ct_jk.csv"))
+
+jk_di_full <- left_join(jk_di_full, jk_ct)
+
+all_di_with_resamples <- left_join(all_di_with_resamples, all_ct_with_resamples)
+
+jk_di <- jk_di_full %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup() %>%
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl, real_po_percentile, real_po_percentile_excl, sim_pos_from_best, skew_95_ratio_2t, simpson_95_ratio_2t, shannon_95_ratio_2t, nparts)
+
+skewcols <- colnames(jk_di)[ grepl("skew", colnames(jk_di))]
+
+jk_di[ which(jk_di$s0 < 3), skewcols] <- NA
+
+jk_di_means <- jk_di %>%
+  filter(n0 != s0,
+         s0 != 1,
+         n0 != (s0 + 1)) %>%
+  group_by(dat, site_source) %>%
+  mutate(njks = dplyr::n(),
+         njks_skew = sum(!is.na(skew_percentile)))%>%
+  summarise_at(vars(-group_cols(), -site), mean, na.rm =  T) %>%
+  mutate(resampling = "Subsampling") %>%
+  mutate(site = as.numeric(site_source)) %>%
+#  select(-site_source) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20,
+         njks == 10) %>%
+  ungroup()
+
+jk_di[ which(jk_di$njks_skew < 10), skewcols] <- NA
+
+skewcols <- colnames(all_di_with_resamples[ which(grepl("skew", colnames(all_di_with_resamples)))])
+
+all_di_with_resamples[ which(all_di_with_resamples$s0 < 3), skewcols] <- NA
+
+all_di_with_resamples <- all_di_with_resamples %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 != s0,
+         s0 != 1,
+       #  !singletons,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20) %>%
+  mutate(resampling = ifelse(singletons, "Rare species", "Raw")) %>%
+  bind_rows(jk_di_means)
+
+metric_rs_results <- all_di_with_resamples %>%
+  group_by(Dataset, resampling) %>%
+  summarize(
+    skew_high = mean(skew_percentile_excl > 97.5, na.rm = T),
+    skew_low = mean(skew_percentile < 2.5, na.rm = T),
+    even_high = mean(simpson_percentile_excl > 97.5, na.rm = T),
+    even_low = mean(simpson_percentile < 2.5, na.rm = T),
+    shannon_high = mean(shannon_percentile_excl > 97.5, na.rm = T),
+    shannon_low = mean(shannon_percentile < 2.5, na.rm = T),
+    nsingletons_high = mean(nsingletons_percentile_excl > 97.5, na.rm = T),
+    nsingletons_low = mean(nsingletons_percentile < 2.5, na.rm = T),
+    nskew = sum(!is.na(skew_percentile)),
+    nother = dplyr::n()
+  ) %>%
+  ungroup()
+
+diss_rs_results <- all_di_with_resamples %>%
+  filter(nparts > 40) %>%
+  group_by(Dataset, resampling) %>%
+  summarize(dissimilarity_high = mean(real_po_percentile_excl > 95, na.rm = T),
+            ndiss = sum(!is.na(real_po_percentile_excl))) %>%
+  ungroup()
+
+rs_results <- left_join(metric_rs_results, diss_rs_results)
+
+#metric_cols <- colnames(rs_results [ grepl("_", colnames(rs_results))])
+
+as.perc <- function(x) {
+  return((signif(100 * x, digits = 2)))
+}
+
+rs_results_desc <- rs_results %>%
+  mutate(`High dissimilarity` = paste0(as.perc(dissimilarity_high), "%; n =", ndiss),
+         `High proportion of rare species` = paste0(as.perc(nsingletons_high), "%; n =", nother),
+         `High skew` = paste0(as.perc(skew_high), "%; n = ", nskew),
+         `Low Simpson` = paste0(as.perc(even_low), "%; n = ", nother),
+         `Low Shannon` = paste0(as.perc(shannon_low), "%; n = ", nother),
+         `Low proportion of rare species` = paste0(as.perc(nsingletons_low), "%; n =", nother),
+         `Low skew` = paste0(as.perc(skew_low), "%; n = ", nskew),
+         `High Simpson` = paste0(as.perc(even_high), "%; n = ", nother),
+         `High Shannon` = paste0(as.perc(shannon_high), "%; n = ", nother),
+         `Resampling scheme` = ordered(resampling, levels = c("Raw", "Subsampling", "Rare species"))) %>%
+  arrange(Dataset, `Resampling scheme`)
+
+cols1 <- c("Dataset", "Resampling scheme", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+
+cols2 <- c("Dataset","Resampling scheme",  "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
+
+rs_results_desc %>%
+  select(cols1)
+
+rs_results_desc %>%
+  select(cols2)
+```
+```{r, fig.dim = c(6,4)}
+rs_results_long <- rs_results %>% 
+  tidyr::pivot_longer((-c("Dataset","resampling")), names_to = "metric", values_to = "value") %>%
+  filter(grepl("_", metric)) %>%
+  mutate(ometric = ordered(metric, levels = c("skew_high", "skew_low", "even_low", "even_high", "shannon_low", "shannon_high", "nsingletons_high", "nsingletons_low", "dissimilarity_high")),
+         ometric2 = ordered(metric, levels = c("dissimilarity_high",  "nsingletons_high", "skew_high",  "even_low",  "shannon_low",  "nsingletons_low","skew_low","even_high","shannon_high"))) %>%
+  mutate(weird_dir = as.numeric(ometric2) > 5,
+         percentile_cutoff = ifelse(grepl("diss", metric), .05, .025),`Resampling scheme` = ordered(resampling, levels = c("Raw", "Subsampling", "Rare species")))
+
+metric_names <- rs_results_long %>%
+  select(ometric2) %>%
+  distinct() %>%
+  arrange(ometric2) %>%
+  mutate(metric_desc =(c("High dissimilarity", "High proportion \nof rare species", "High skew", "Low Simpson", "Low Shannon", "Low proportion \nof rare species", "Low skew", "High Simpson", "High Shannon"))) %>%
+  mutate(metric_desc = ordered(metric_desc))
+
+rs_results_long <- left_join(rs_results_long, metric_names)
+# 
+# ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+#   geom_point() +
+#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 1) +
+#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+#   scale_color_viridis_d(end = .8) +
+#   ylab("Proportion of extreme observed values") +
+#   xlab("")
+
+gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("Proportion of extreme observed values") +ylim(0, .7) +
+  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
+  ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("") +
+  xlab("") + ylim(0, .7) +
+  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
+
+gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("Proportion of extreme observed values") +ylim(0, .7) +
+  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
+  ggplot(filter(rs_results_long, grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("") +
+  xlab("") + ylim(0, .7) +
+  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
+
+```
+
+```{r, fig.dim = c(10,5)}
+
+all_di_with_resamples <- all_di_with_resamples %>%
+  group_by_all() %>%
+  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl, na.rm = T),
+         skew_percentile_mean = mean(skew_percentile, skew_percentile_excl, na.rm = T),
+         simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl, na.rm = T),
+         shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl, na.rm = T),
+         nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl)) %>%
+  ungroup()
+
+fig_2 <- gridExtra::grid.arrange(grobs = list(
+
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
+top = textGrob("Subsampling results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
+
+fig_2 <- gridExtra::grid.arrange(grobs = list(
+
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
+top = textGrob("Adjusted for rare species results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
+```

### 2021-03-22 analysis/rev_prototyping/draft_reports/appendices/s5_results_weird_direction.Rmd
rev draft

--- 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 ---
-title: "Figures and results for main manuscript"
+title: "Proportions of extreme values the unusual direction"
 author: Renata Diaz
@@
 output: 
-    github_document:
+    # github_document:
+    #    df_print: kable
+    #    toc: true
+    word_document:
         df_print: kable
-       toc: true
+        toc: false
 ---
@@
 ```
-
-# Datasets by S and N (Figure 1)
-
-```{r, fig.dim = c(7,7)}
-
-s4_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
-  geom_point(alpha = .1) +
-  geom_point(data = filter(all_di), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d(end = .9) +
-  ggtitle("Communities by S and N") +
-  xlab("Species richness (S); note log scale") +
-  ylab("Total abundance (N); note log scale") +
-  scale_x_log10() +
-  scale_y_log10()
-
-plot(s4_fig1)
-```
-
-# Illustrations of 95% interval (Figure 2)
-
-To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
-
-<!-- ```{r, fig.dim = c(7,7)} -->
-<!-- library(drake) -->
-
-<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite")) -->
-<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->
-<!-- cache$del(key = "lock", namespace = "session") -->
-
-<!-- net_summary <- readd(all_di_summary, cache = cache) -->
-
-<!-- net_summary <- net_summary %>% -->
-<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) -->
-
-<!-- example_fs <- readd(fs_s_44_n_13360, cache = cache) -->
-
-<!-- example_di <- readd(di_fs_s_44_n_13360, cache =cache) -->
-
-<!-- example_fs <- example_fs %>% -->
-<!--   left_join(example_di) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- example_fs2 <- readd(fs_s_13_n_315, cache = cache) -->
-
-<!-- example_di2 <- readd(di_fs_s_13_n_315, cache =cache) -->
-
-<!-- example_fs2 <- example_fs2 %>% -->
-<!--   left_join(example_di2) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- example_fs3 <- readd(fs_s_4_n_34, cache = cache) -->
-
-<!-- example_di3 <- readd(di_fs_s_4_n_34, cache =cache) -->
-
-<!-- example_fs3 <- example_fs3 %>% -->
-<!--   left_join(example_di3) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- breadth_plots <- list( -->
-
-<!--   ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .25) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
-
-<!--   ggplot(example_fs3, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle = paste0("Breadth index: ", round((example_fs3$skew_95_ratio_2t[1]), 2))) + -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
-
-<!--   ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) + -->
-<!--     theme(legend.position = "right")+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance") + -->
-<!--     ylim(0, 200), # Remove 3 sads that make the axes too big to be interpretable -->
-
-<!--   ggplot(example_fs2, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs2$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
-
-<!--   ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     ylim(0, 4000) + # Remove a very few very very uneven SADs that make the scale too big to be interpretable -->
-<!--     theme(axis.text.y = element_text(size = 6, angle = 60))+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
-
-<!--   ggplot(example_fs, aes(skew)) + -->
-<!--    # geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count") -->
-
-<!-- ) -->
-
-<!-- fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->
-
-<!-- plot(fig_1) -->
-
-<!-- DBI::dbDisconnect(db) -->
-<!-- rm(cache) -->
-<!-- rm(db) -->
-<!-- ``` -->
-
-# Dissimilarity (Supplement)
-
-```{r, fig.dim = c(3, 6)}
-plot_percentile_hist <- function(di_df, col_name, plot_name, tails = 2, facetvar = "Dataset", min_s0 = 0) {
-
-  if(tails == 2) {
-    cutoff_percentiles = c(2.5, 97.5)
-    min_nparts = 40
-  } else if (tails== 1) {
-    cutoff_percentiles = c(95)
-    min_nparts = 20
-  }
-
-  di_df <- di_df %>%
-    mutate(response = (di_df[[col_name]]),
-           facetvar = di_df[[facetvar]])
-
-  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
-    geom_histogram(bins = 40, boundary = 100) +
-    theme_bw() +
-    xlab("") +
-    ylab("") +
-    geom_vline(xintercept = cutoff_percentiles, color = "red") +
-    ggtitle( plot_name) +
-    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+ 
-    theme(plot.title = element_text(size=10))
-
-}
-
-all_di <- all_di %>%
-  mutate(`Observed \npercentile score` = ifelse(real_po_percentile_excl > 95, "High (> 95)", "Less than 95"))
-
-```
-
-```{r, fig.dim = c(4, 4)}
-ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
-  geom_point(alpha = .3) + 
-  geom_point(data = filter(all_di, s0 < 0)) +
-  geom_abline(slope = 1, intercept = 0) +
-  scale_color_viridis_d(end = .8, direction = -1) +
-  xlab("Mean of elements from feasible set") +
-  ylab("Observed value") +
-  ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")#,
-# 
-# 
-# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
-#   geom_point(alpha = .3) + 
-#   geom_point(data = filter(all_di, s0 < 0)) +
-#   scale_color_viridis_d(end = .9) +
-#   xlab("Number of elements in the feasible set") +
-#   ylab("Mean dissimilarity of feasible set to central tendency") +
-#   scale_x_log10() +
-#   ggtitle("Over the size of the feasible set")
-# ), ncol = 1,
-#top = textGrob("Dissimilarity to central tendency"))
-
-```
-
-# Metric histograms by dataset (Figure 4)
-
-```{r first hists, fig.dim = c(10,5)}
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-```
-
-# Results table
 
@@
   left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
+# 
+# cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+# 
+# all_results %>%
+#   select(cols1)
 
@@
 
-# Narrowness
-
-```{r, fig.dim = c(3, 6)}
-
-plot_narrowness <- function(di_df, yvar, yvar_name) {
-
-  if(grepl("sim_pos", yvar)) {
-    min_nparts = 20
-    ylabel = "Mean dissimilarity"
-  } else {
-    min_nparts = 40
-    ylabel = "Breadth index"
-  }
-
-  di_df <- di_df %>%
-    mutate(response = (di_df[[yvar]])) %>%
-    filter(nparts > min_nparts,
-           nparts < 10 ^ 50)
-
-  ggplot(di_df, aes(nparts, response, color = Dataset)) +
-    geom_point(alpha = .3) +
-    geom_point(data = filter(di_df, s0 < 0)) +
-    scale_color_viridis_d(end = .9) +
-    xlab("") +
-    ylab(ylabel) +
-    scale_x_log10() +
-    ggtitle(yvar_name) + 
-    theme(legend.position = "none")+ 
-    theme(plot.title = element_text(size=10))
-}
-
-plot_narrowness_legend <- function(di_df) {
-
-  legend_df <- di_df %>%
-    select(Dataset) %>%
-    distinct() %>%
-    mutate(ymark = dplyr::row_number())
-
-  ggplot(legend_df, aes(1, ymark, color = Dataset)) +
-    geom_label(aes(x = 2, y = ymark, label = Dataset)) +
-    geom_point(size = 4) +
-    scale_color_viridis_d(end = .9) +
-    xlab("") +
-    ylab("") +
-    theme(legend.position = "none") +
-    xlim(1, 3) + theme(
-      panel.grid.major.x = element_blank(),
-      panel.grid.minor.x = element_blank(),
-      panel.grid.major.y = element_blank(),
-      panel.grid.minor.y = element_blank(),
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank()
-    ) +
-    ggtitle("Dataset")
-
-}
-# 
-# gridExtra::grid.arrange(grobs = list(
-#   plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity to central tendency"),
-#   plot_narrowness_legend(all_di)),
-#   ncol = 1)
-```
-
-```{r, fig.dim = c(7,4)}
-
-gridExtra::grid.arrange(grobs = list(
-  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")),
-  gridExtra::grid.arrange(grobs = list(
-    plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
-    plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
-    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species"),
-       plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
-  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"))
-
-```
-
-```{r}
-
-plot_narrowness_hist <- function(di_df, col_name, plot_name, facetvar = "Dataset", min_s0 = 0) {
-
-  if(grepl("sim_pos", col_name)) {
-    xvarname = "Mean dissimilarity"
-    min_nparts = 40
-  } else {
-    min_nparts = 20
-    xvarname = "Breadth index"
-  }
-
-  di_df <- di_df %>%
-    mutate(response = (di_df[[col_name]]),
-           facetvar = di_df[[facetvar]])
-
-  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
-    geom_histogram(bins = 40, boundary = 100) +
-    theme_bw() +
-    ylab("") +
-    xlab(xvarname) +
-    ggtitle( plot_name) +
-    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+ 
-    theme(plot.title = element_text(size=10))
-
-}
-
-```
-
-```{r, fig.dim = c(10,5)}
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-```
-
-# Gentry
-
-```{r}
-
-gentry_di <- filter(all_di, Dataset == "Gentry")
-
-gentry_di <- gentry_di %>%
-  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3),
-  plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund")
-), ncol = 2,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-```
-
-# Comparison of FIA and comparably sized communities (Figure 4)
-
-```{r, fig.dim = c(10, 5)}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-fia_di <- filter(sub_di, fia_yn == "fia")
-other_di <- filter(sub_di, fia_yn != "fia")
-
-ks_compare <- function(fia_df, other_df, compare_var) {
-
-  if(grepl("skew", compare_var)) {
-    fia_df <- filter(fia_df, s0 > 2)
-    other_df <- filter(fia_df, s0 >2)
-  }
-
-  if(grepl("sim_pos", compare_var)) {
-    fia_df <- filter(fia_df, nparts > 20)
-    other_df <- filter(other_df, nparts > 20)
-  } else {
-      fia_df <- filter(fia_df, nparts > 40)
-    other_df <- filter(other_df, nparts > 40)
-  }
-
-  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])
-
-  return(data.frame(
-    var = compare_var,
-    d = kstest$statistic,
-    p = kstest$p.value
-  ))
-}
-
-simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
-skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
-shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
-nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
-
-bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
-
-simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
-skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
-shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
-nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
-diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
-
-bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-diss_results <- sub_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- sub_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- sub_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
-```
+**Table ST5.** Proportions of extreme values for percentile scores for observed SADs compared to samples from the feasible set, for the less-usual direction of effects.
+This is the proportion of scores <2.5 or >97.5; by chance ~2.5% of scores should be in either extreme.
+n refers to the number of communities included for each dataset for each metric.

### 2021-03-22 analysis/rev_prototyping/draft_reports/appendices/s6_breadth_index_fig.Rmd
rev draft

--- 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 ---
-title: "Figures and results for main manuscript"
+title: "Distribution of dissimilarity and breadth indices within each dataset"
 author: Renata Diaz
@@
 
-# Datasets by S and N (Figure 1)
-
-```{r, fig.dim = c(7,7)}
-
-s4_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
-  geom_point(alpha = .1) +
-  geom_point(data = filter(all_di), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d(end = .9) +
-  ggtitle("Communities by S and N") +
-  xlab("Species richness (S); note log scale") +
-  ylab("Total abundance (N); note log scale") +
-  scale_x_log10() +
-  scale_y_log10()
-
-plot(s4_fig1)
-```
-
-# Illustrations of 95% interval (Figure 2)
-
-To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
-
-<!-- ```{r, fig.dim = c(7,7)} -->
-<!-- library(drake) -->
-
-<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite")) -->
-<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->
-<!-- cache$del(key = "lock", namespace = "session") -->
-
-<!-- net_summary <- readd(all_di_summary, cache = cache) -->
-
-<!-- net_summary <- net_summary %>% -->
-<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) -->
-
-<!-- example_fs <- readd(fs_s_44_n_13360, cache = cache) -->
-
-<!-- example_di <- readd(di_fs_s_44_n_13360, cache =cache) -->
-
-<!-- example_fs <- example_fs %>% -->
-<!--   left_join(example_di) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- example_fs2 <- readd(fs_s_13_n_315, cache = cache) -->
-
-<!-- example_di2 <- readd(di_fs_s_13_n_315, cache =cache) -->
-
-<!-- example_fs2 <- example_fs2 %>% -->
-<!--   left_join(example_di2) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- example_fs3 <- readd(fs_s_4_n_34, cache = cache) -->
-
-<!-- example_di3 <- readd(di_fs_s_4_n_34, cache =cache) -->
-
-<!-- example_fs3 <- example_fs3 %>% -->
-<!--   left_join(example_di3) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- breadth_plots <- list( -->
-
-<!--   ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .25) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
-
-<!--   ggplot(example_fs3, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle = paste0("Breadth index: ", round((example_fs3$skew_95_ratio_2t[1]), 2))) + -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
-
-<!--   ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) + -->
-<!--     theme(legend.position = "right")+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance") + -->
-<!--     ylim(0, 200), # Remove 3 sads that make the axes too big to be interpretable -->
-
-<!--   ggplot(example_fs2, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs2$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
-
-<!--   ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     ylim(0, 4000) + # Remove a very few very very uneven SADs that make the scale too big to be interpretable -->
-<!--     theme(axis.text.y = element_text(size = 6, angle = 60))+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
-
-<!--   ggplot(example_fs, aes(skew)) + -->
-<!--    # geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count") -->
-
-<!-- ) -->
-
-<!-- fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->
-
-<!-- plot(fig_1) -->
-
-<!-- DBI::dbDisconnect(db) -->
-<!-- rm(cache) -->
-<!-- rm(db) -->
-<!-- ``` -->
-
-# Dissimilarity (Supplement)
-
-```{r, fig.dim = c(3, 6)}
-plot_percentile_hist <- function(di_df, col_name, plot_name, tails = 2, facetvar = "Dataset", min_s0 = 0) {
-
-  if(tails == 2) {
-    cutoff_percentiles = c(2.5, 97.5)
-    min_nparts = 40
-  } else if (tails== 1) {
-    cutoff_percentiles = c(95)
-    min_nparts = 20
-  }
-
-  di_df <- di_df %>%
-    mutate(response = (di_df[[col_name]]),
-           facetvar = di_df[[facetvar]])
-
-  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
-    geom_histogram(bins = 40, boundary = 100) +
-    theme_bw() +
-    xlab("") +
-    ylab("") +
-    geom_vline(xintercept = cutoff_percentiles, color = "red") +
-    ggtitle( plot_name) +
-    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+ 
-    theme(plot.title = element_text(size=10))
-
-}
-
-all_di <- all_di %>%
-  mutate(`Observed \npercentile score` = ifelse(real_po_percentile_excl > 95, "High (> 95)", "Less than 95"))
-
-```
-
-```{r, fig.dim = c(4, 4)}
-ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
-  geom_point(alpha = .3) + 
-  geom_point(data = filter(all_di, s0 < 0)) +
-  geom_abline(slope = 1, intercept = 0) +
-  scale_color_viridis_d(end = .8, direction = -1) +
-  xlab("Mean of elements from feasible set") +
-  ylab("Observed value") +
-  ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")#,
-# 
-# 
-# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
-#   geom_point(alpha = .3) + 
-#   geom_point(data = filter(all_di, s0 < 0)) +
-#   scale_color_viridis_d(end = .9) +
-#   xlab("Number of elements in the feasible set") +
-#   ylab("Mean dissimilarity of feasible set to central tendency") +
-#   scale_x_log10() +
-#   ggtitle("Over the size of the feasible set")
-# ), ncol = 1,
-#top = textGrob("Dissimilarity to central tendency"))
-
-```
-
-# Metric histograms by dataset (Figure 4)
-
-```{r first hists, fig.dim = c(10,5)}
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-```
-
-# Results table
-
-```{r}
-diss_results <- all_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- all_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- all_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
-cols2 <- c("Dataset", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
-
-all_results %>%
-  select(cols2)
-
-```
-
-# Narrowness
-
 ```{r, fig.dim = c(3, 6)}
@@
   ggplot(di_df, aes(nparts, response, color = Dataset)) +
-    geom_point(alpha = .3) +
+    geom_point(data = filter(di_df, dat == "fia"), alpha = .1) +
+    geom_point(data = filter(di_df, dat != "fia"), alpha = .1) +
     geom_point(data = filter(di_df, s0 < 0)) +
@@
 #   ncol = 1)
-```
-
-```{r, fig.dim = c(7,4)}
-
-gridExtra::grid.arrange(grobs = list(
-  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")),
-  gridExtra::grid.arrange(grobs = list(
-    plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
-    plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
-    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species"),
-       plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
-  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"))
-
 ```
@@
 
-# Gentry
-
-```{r}
-
-gentry_di <- filter(all_di, Dataset == "Gentry")
-
-gentry_di <- gentry_di %>%
-  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3),
-  plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund")
-), ncol = 2,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-```
-
-# Comparison of FIA and comparably sized communities (Figure 4)
-
-```{r, fig.dim = c(10, 5)}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-fia_di <- filter(sub_di, fia_yn == "fia")
-other_di <- filter(sub_di, fia_yn != "fia")
-
-ks_compare <- function(fia_df, other_df, compare_var) {
-
-  if(grepl("skew", compare_var)) {
-    fia_df <- filter(fia_df, s0 > 2)
-    other_df <- filter(fia_df, s0 >2)
-  }
-
-  if(grepl("sim_pos", compare_var)) {
-    fia_df <- filter(fia_df, nparts > 20)
-    other_df <- filter(other_df, nparts > 20)
-  } else {
-      fia_df <- filter(fia_df, nparts > 40)
-    other_df <- filter(other_df, nparts > 40)
-  }
-
-  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])
-
-  return(data.frame(
-    var = compare_var,
-    d = kstest$statistic,
-    p = kstest$p.value
-  ))
-}
-
-simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
-skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
-shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
-nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
-
-bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
-
-simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
-skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
-shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
-nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
-diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
-
-bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-diss_results <- sub_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- sub_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- sub_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
-```
+**Figure S6**.
+Partially because of the uneven distribution of S and N among the different datasets, the narrowness of the feasible sets - defined either as the mean dissimilarity of samples from the feasible set to the central tendency of the feasible set, or using a breadth index for specific metrics - varies among different datasets.
+In particular, the FIA dataset, and subsets of the Mammal Community and Miscellaneous Abundance databases, often have highly variable, broadly-defined statistical baselines derived from the feasible set.

### 2021-03-22 analysis/rev_prototyping/draft_reports/appendices/s7_complete_resampling_results.Rmd
rev draft

--- 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 ---
-title: "Figures and results for main manuscript"
+title: "Complete results of resampling"
 author: Renata Diaz
@@
 
-# Datasets by S and N (Figure 1)
-
-```{r, fig.dim = c(7,7)}
-
-s4_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
-  geom_point(alpha = .1) +
-  geom_point(data = filter(all_di), alpha = .4) +
-  theme_bw() +
-  scale_color_viridis_d(end = .9) +
-  ggtitle("Communities by S and N") +
-  xlab("Species richness (S); note log scale") +
-  ylab("Total abundance (N); note log scale") +
-  scale_x_log10() +
-  scale_y_log10()
-
-plot(s4_fig1)
-```
-
-# Illustrations of 95% interval (Figure 2)
-
-To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
-
-<!-- ```{r, fig.dim = c(7,7)} -->
-<!-- library(drake) -->
-
-<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite")) -->
-<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->
-<!-- cache$del(key = "lock", namespace = "session") -->
-
-<!-- net_summary <- readd(all_di_summary, cache = cache) -->
-
-<!-- net_summary <- net_summary %>% -->
-<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) -->
-
-<!-- example_fs <- readd(fs_s_44_n_13360, cache = cache) -->
-
-<!-- example_di <- readd(di_fs_s_44_n_13360, cache =cache) -->
-
-<!-- example_fs <- example_fs %>% -->
-<!--   left_join(example_di) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- example_fs2 <- readd(fs_s_13_n_315, cache = cache) -->
-
-<!-- example_di2 <- readd(di_fs_s_13_n_315, cache =cache) -->
-
-<!-- example_fs2 <- example_fs2 %>% -->
-<!--   left_join(example_di2) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- example_fs3 <- readd(fs_s_4_n_34, cache = cache) -->
-
-<!-- example_di3 <- readd(di_fs_s_4_n_34, cache =cache) -->
-
-<!-- example_fs3 <- example_fs3 %>% -->
-<!--   left_join(example_di3) %>% -->
-<!--   left_join(net_summary) -->
-
-<!-- breadth_plots <- list( -->
-
-<!--   ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .25) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
-
-<!--   ggplot(example_fs3, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle = paste0("Breadth index: ", round((example_fs3$skew_95_ratio_2t[1]), 2))) + -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
-
-<!--   ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) + -->
-<!--     theme(legend.position = "right")+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance") + -->
-<!--     ylim(0, 200), # Remove 3 sads that make the axes too big to be interpretable -->
-
-<!--   ggplot(example_fs2, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs2$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
-
-<!--   ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     ylim(0, 4000) + # Remove a very few very very uneven SADs that make the scale too big to be interpretable -->
-<!--     theme(axis.text.y = element_text(size = 6, angle = 60))+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
-
-<!--   ggplot(example_fs, aes(skew)) + -->
-<!--    # geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count") -->
-
-<!-- ) -->
-
-<!-- fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->
-
-<!-- plot(fig_1) -->
-
-<!-- DBI::dbDisconnect(db) -->
-<!-- rm(cache) -->
-<!-- rm(db) -->
-<!-- ``` -->
-
-# Dissimilarity (Supplement)
-
 ```{r, fig.dim = c(3, 6)}
@@
 
-```{r, fig.dim = c(4, 4)}
-ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
-  geom_point(alpha = .3) + 
-  geom_point(data = filter(all_di, s0 < 0)) +
-  geom_abline(slope = 1, intercept = 0) +
-  scale_color_viridis_d(end = .8, direction = -1) +
-  xlab("Mean of elements from feasible set") +
-  ylab("Observed value") +
-  ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")#,
-# 
-# 
-# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
-#   geom_point(alpha = .3) + 
-#   geom_point(data = filter(all_di, s0 < 0)) +
-#   scale_color_viridis_d(end = .9) +
-#   xlab("Number of elements in the feasible set") +
-#   ylab("Mean dissimilarity of feasible set to central tendency") +
-#   scale_x_log10() +
-#   ggtitle("Over the size of the feasible set")
-# ), ncol = 1,
-#top = textGrob("Dissimilarity to central tendency"))
-
-```
-
-# Metric histograms by dataset (Figure 4)
-
-```{r first hists, fig.dim = c(10,5)}
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-```
-
-# Results table
-
-```{r}
-diss_results <- all_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- all_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- all_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
-cols2 <- c("Dataset", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
-
-all_results %>%
-  select(cols2)
-
-```
-
-# Narrowness
-
 ```{r, fig.dim = c(3, 6)}
@@
 
-```{r, fig.dim = c(7,4)}
-
-gridExtra::grid.arrange(grobs = list(
-  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")),
-  gridExtra::grid.arrange(grobs = list(
-    plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
-    plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
-    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species"),
-       plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
-  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"))
-
-```
-
 ```{r}
@@
 
+# Resampling
+
+```{r}
+
+all_di_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))
+
+jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
+
+all_ct_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"))
+
+jk_ct <- read.csv(here::here("analysis", "rev_prototyping", "all_ct_jk.csv"))
+
+jk_di_full <- left_join(jk_di_full, jk_ct)
+
+all_di_with_resamples <- left_join(all_di_with_resamples, all_ct_with_resamples)
+
+jk_di <- jk_di_full %>%
+  group_by_all() %>%
+  mutate(site_source = unlist(strsplit(site, "_")[[1]][[1]])) %>%
+  ungroup() %>%
+  select(dat, site, site_source, s0, n0, skew_percentile_excl,skew_percentile, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl, real_po_percentile, real_po_percentile_excl, sim_pos_from_best, skew_95_ratio_2t, simpson_95_ratio_2t, shannon_95_ratio_2t, nparts)
+
+skewcols <- colnames(jk_di)[ grepl("skew", colnames(jk_di))]
+
+jk_di[ which(jk_di$s0 < 3), skewcols] <- NA
+
+jk_di_means <- jk_di %>%
+  filter(n0 != s0,
+         s0 != 1,
+         n0 != (s0 + 1)) %>%
+  group_by(dat, site_source) %>%
+  mutate(njks = dplyr::n(),
+         njks_skew = sum(!is.na(skew_percentile)))%>%
+  summarise_at(vars(-group_cols(), -site), mean, na.rm =  T) %>%
+  mutate(resampling = "Subsampling") %>%
+  mutate(site = as.numeric(site_source)) %>%
+#  select(-site_source) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20,
+         njks == 10) %>%
+  ungroup()
+
+jk_di[ which(jk_di$njks_skew < 10), skewcols] <- NA
+
+skewcols <- colnames(all_di_with_resamples[ which(grepl("skew", colnames(all_di_with_resamples)))])
+
+all_di_with_resamples[ which(all_di_with_resamples$s0 < 3), skewcols] <- NA
+
+all_di_with_resamples <- all_di_with_resamples %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 != s0,
+         s0 != 1,
+       #  !singletons,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20) %>%
+  mutate(resampling = ifelse(singletons, "Rare species", "Raw")) %>%
+  bind_rows(jk_di_means)
+
+metric_rs_results <- all_di_with_resamples %>%
+  group_by(Dataset, resampling) %>%
+  summarize(
+    skew_high = mean(skew_percentile_excl > 97.5, na.rm = T),
+    skew_low = mean(skew_percentile < 2.5, na.rm = T),
+    even_high = mean(simpson_percentile_excl > 97.5, na.rm = T),
+    even_low = mean(simpson_percentile < 2.5, na.rm = T),
+    shannon_high = mean(shannon_percentile_excl > 97.5, na.rm = T),
+    shannon_low = mean(shannon_percentile < 2.5, na.rm = T),
+    nsingletons_high = mean(nsingletons_percentile_excl > 97.5, na.rm = T),
+    nsingletons_low = mean(nsingletons_percentile < 2.5, na.rm = T),
+    nskew = sum(!is.na(skew_percentile)),
+    nother = dplyr::n()
+  ) %>%
+  ungroup()
+
+diss_rs_results <- all_di_with_resamples %>%
+  filter(nparts > 40) %>%
+  group_by(Dataset, resampling) %>%
+  summarize(dissimilarity_high = mean(real_po_percentile_excl > 95, na.rm = T),
+            ndiss = sum(!is.na(real_po_percentile_excl))) %>%
+  ungroup()
+
+rs_results <- left_join(metric_rs_results, diss_rs_results)
+
+#metric_cols <- colnames(rs_results [ grepl("_", colnames(rs_results))])
+
+as.perc <- function(x) {
+  return((signif(100 * x, digits = 2)))
+}
+
+rs_results_desc <- rs_results %>%
+  mutate(`High dissimilarity` = paste0(as.perc(dissimilarity_high), "%; n =", ndiss),
+         `High proportion of rare species` = paste0(as.perc(nsingletons_high), "%; n =", nother),
+         `High skew` = paste0(as.perc(skew_high), "%; n = ", nskew),
+         `Low Simpson` = paste0(as.perc(even_low), "%; n = ", nother),
+         `Low Shannon` = paste0(as.perc(shannon_low), "%; n = ", nother),
+         `Low proportion of rare species` = paste0(as.perc(nsingletons_low), "%; n =", nother),
+         `Low skew` = paste0(as.perc(skew_low), "%; n = ", nskew),
+         `High Simpson` = paste0(as.perc(even_high), "%; n = ", nother),
+         `High Shannon` = paste0(as.perc(shannon_high), "%; n = ", nother),
+         `Resampling scheme` = ordered(resampling, levels = c("Raw", "Subsampling", "Rare species"))) %>%
+  arrange(Dataset, `Resampling scheme`)
+
+cols1 <- c("Dataset", "Resampling scheme", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+
+cols2 <- c("Dataset","Resampling scheme",  "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
+
+```
+```{r, fig.dim = c(6,4)}
+rs_results_long <- rs_results %>%
+  tidyr::pivot_longer((-c("Dataset","resampling")), names_to = "metric", values_to = "value") %>%
+  filter(grepl("_", metric)) %>%
+  mutate(ometric = ordered(metric, levels = c("skew_high", "skew_low", "even_low", "even_high", "shannon_low", "shannon_high", "nsingletons_high", "nsingletons_low", "dissimilarity_high")),
+         ometric2 = ordered(metric, levels = c("dissimilarity_high",  "nsingletons_high", "skew_high",  "even_low",  "shannon_low",  "nsingletons_low","skew_low","even_high","shannon_high"))) %>%
+  mutate(weird_dir = as.numeric(ometric2) > 5,
+         percentile_cutoff = ifelse(grepl("diss", metric), .05, .025),`Resampling scheme` = ordered(resampling, levels = c("Raw", "Subsampling", "Rare species")))
+
+metric_names <- rs_results_long %>%
+  select(ometric2) %>%
+  distinct() %>%
+  arrange(ometric2) %>%
+  mutate(metric_desc =(c("High dissimilarity", "High proportion \nof rare species", "High skew", "Low Simpson", "Low Shannon", "Low proportion \nof rare species", "Low skew", "High Simpson", "High Shannon"))) %>%
+  mutate(metric_desc = ordered(metric_desc))
+
+rs_results_long <- left_join(rs_results_long, metric_names)
+#
+# ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+#   geom_point() +
+#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 1) +
+#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+#   scale_color_viridis_d(end = .8) +
+#   ylab("Proportion of extreme observed values") +
+#   xlab("")
+```
+
+# Percentile histograms
+
+## Subsampling
+
+```{r, fig.dim = c(10,5)}
+
+all_di_with_resamples <- all_di_with_resamples %>%
+  group_by_all() %>%
+  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl, na.rm = T),
+         skew_percentile_mean = mean(skew_percentile, skew_percentile_excl, na.rm = T),
+         simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl, na.rm = T),
+         shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl, na.rm = T),
+         nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl)) %>%
+  ungroup()
+
+fig_2 <- gridExtra::grid.arrange(grobs = list(
+
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
+top = textGrob("Subsampling results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
+```
+
+## Adjusting for rare species
+
 ```{r, fig.dim = c(10,5)}
@@
 
-  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
 ), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
+top = textGrob("Adjusted for rare species results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
+```
+
+# Summary of effects on proportion of extreme values
+
+## Usual direction
+
+```{r}
+gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("Proportion of extreme observed values") +ylim(0, .7) +
+  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
+  ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("") +
+  xlab("") + ylim(0, .7) +
+  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
+```
+
+## Unusual direction
+
+```{r}
+gridExtra::grid.arrange(grobs = list(
+  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("Proportion of extreme observed values") +ylim(0, .7) +
+  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
+  ggplot(filter(rs_results_long, grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  geom_point() +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
+  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+  scale_color_viridis_d(end = .8) +
+  ylab("") +
+  xlab("") + ylim(0, .7) +
+  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
 
@@
 
-# Gentry
+# Table of proportions of extreme values
+
+## Usual direction
 
@@
 
-gentry_di <- filter(all_di, Dataset == "Gentry")
-
-gentry_di <- gentry_di %>%
-  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3),
-  plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund")
-), ncol = 2,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
+rs_results_desc %>%
+  select(cols1)
 
@@
 
-# Comparison of FIA and comparably sized communities (Figure 4)
+## Unusual direction
 
-```{r, fig.dim = c(10, 5)}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-fia_di <- filter(sub_di, fia_yn == "fia")
-other_di <- filter(sub_di, fia_yn != "fia")
-
-ks_compare <- function(fia_df, other_df, compare_var) {
-
-  if(grepl("skew", compare_var)) {
-    fia_df <- filter(fia_df, s0 > 2)
-    other_df <- filter(fia_df, s0 >2)
-  }
-
-  if(grepl("sim_pos", compare_var)) {
-    fia_df <- filter(fia_df, nparts > 20)
-    other_df <- filter(other_df, nparts > 20)
-  } else {
-      fia_df <- filter(fia_df, nparts > 40)
-    other_df <- filter(other_df, nparts > 40)
-  }
-
-  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])
-
-  return(data.frame(
-    var = compare_var,
-    d = kstest$statistic,
-    p = kstest$p.value
-  ))
-}
-
-simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
-skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
-shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
-nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
-
-bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
-
-simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
-skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
-shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
-nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
-diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
-
-bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-diss_results <- sub_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- sub_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- sub_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
+```{r}
+rs_results_desc %>%
+  select(cols2)
 ```

### 2021-03-22 analysis/rev_prototyping/old/ct_all.Rmd
rev draft

--- 2021-03-11 analysis/rev_prototyping/revision_results.Rmd
@@
 ---
-title: "Updated results"
+title: "Central tendency"
 author: Renata Diaz
@@
        df_print: kable
-       toc: true
 ---
@@
 
-knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)
+knitr::opts_chunk$set(fig.width=6, fig.height=6, warning = FALSE, message = FALSE)
 
@@
   left_join(all_ct)
-
-all_di <- all_di %>%
-  group_by_all() %>%
-  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl)) %>%
-  ungroup()
-
-all_di <- all_di %>%
-  mutate(in_fia = ifelse(Dataset == "FIA", "FIA", "Other datasets"))
-
 ```
 
-## Comparing observed to the baseline
+```{r}
 
-### Central tendency
+ggplot(all_di, aes(sim_pos_from_best)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y")
 
-```{r}
-# 
-# ggplot(all_di, aes(sim_pos_from_best)) +
-#   geom_histogram() +
-#   facet_wrap(vars(dat), scales = "free_y") 
-# 
-# ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram() +
-#   facet_wrap(vars(dat), scales = "free_y") + geom_vline(xintercept = 95)
-
-ggplot(all_di, aes(real_po_percentile_mean)) + geom_histogram() +
+ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram() +
   facet_wrap(vars(dat), scales = "free_y") + geom_vline(xintercept = 95)
@@
   group_by(dat) %>%
-  summarize(prop_high_po = mean(real_po_percentile_excl > 95, na.rm = T),
-            nsites = dplyr::n())
-
-all_di %>%
-  group_by(in_fia) %>%
   summarize(prop_high_po = mean(real_po_percentile_excl > 95, na.rm = T),
@@
 
-ggplot(all_di, aes(sim_pos_from_best, real_po, color = real_po_percentile_excl > 95)) +
-  geom_point(alpha = .3) +
-  geom_abline(slope = 1, intercept = 0) +
-  theme(legend.position = "top") +
-  scale_color_viridis_d(end = .8)# +
-#  facet_wrap(vars(dat), scales = "fixed")
+ggplot(all_di, aes((real_po / sim_pos_from_best), real_po_percentile_excl, color =  real_po_percentile_excl > 95)) +
+  geom_point(alpha = .3)
 
-filter(all_di, real_po_percentile_excl > 95) %>%
-  mutate(real_to_mean_sim_po_ratio = real_po / sim_pos_from_best,
-         real_to_mean_sim_po_difference = real_po - sim_pos_from_best,
-         real_to_mean_sim_po_logratio = log(real_po / sim_pos_from_best)) %>%
-  select(real_to_mean_sim_po_ratio, real_to_mean_sim_po_difference) %>%
-  summarize_all(.funs = list(min = min,max = max))
+all_di %>%
+  mutate(rat = real_po / sim_pos_from_best,
+         dev = real_po_percentile_excl > 95) %>%
+  group_by(dev) %>%
+  summarize(minrat = min(rat),
+            maxrat = max(rat),
+            meanrat = mean(rat),
+            mindis = min(real_po - sim_pos_from_best),
+            maxdis = max(real_po - sim_pos_from_best))
+
+ggplot(all_di, aes(nparts, sim_pos_from_best)) +
+  geom_point() +
+  scale_x_log10()
+
+ggplot(all_di, aes(nparts, sim_pos_from_best, color = dat)) +
+  geom_point() +
+  scale_x_log10()  +
+  scale_color_viridis_d() +
+  theme(legend.position = "top")
+
+ggplot(all_di, aes(s0, n0, color =  sim_pos_from_best)) +
+  geom_point() +
+  scale_x_log10()  +
+  scale_y_log10() +
+  scale_color_viridis_c() +
+  theme(legend.position = "top")
 ```
 
-### Shape metrics
-
-```{r, fig.dim = c(12,12)}
-
-all_di_shapes_long <- all_di  %>%
-  filter(nparts > 40) %>%
-  select(dat, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
-  rename(skew = skew_percentile,
-         skewX = skew_percentile_excl,
-         simp = simpson_percentile,
-         simpX = simpson_percentile_excl,
-         shan = shannon_percentile,
-         shanX = shannon_percentile_excl,
-         nsng = nsingletons_percentile,
-         nsngX = nsingletons_percentile_excl) %>%
-  mutate(skewM = (skew + skewX) / 2,
-         simpM = (simp+ simpX)/2,
-         shanM = (shan+ shanX)/2,
-         nsngM = (nsng+ nsngX)/2) %>%
-  tidyr::pivot_longer(-dat, names_to = "metric", values_to = "value") %>%
-  mutate(metric_name = substr(metric, 0, 4),
-         metric_mod = ifelse(substr(metric, 5, 5) == "X", "excl", ifelse(substr(metric, 5,5) == "M", "mean", "incl")))
-
-ggplot(filter(all_di_shapes_long, metric_mod == "mean"), aes(value)) +
-  geom_histogram(bins = 40) +
-  #facet_grid(rows = vars(dat), cols = vars(metric_name), scales = "free", switch = "y") +
-  facet_wrap(vars(metric_name, dat), scales = "free", ncol = 5) +
-  geom_vline(xintercept = c(2.5, 97.5))
-
-all_di_shapes_high <- all_di_shapes_long %>%
-  filter(metric_mod == "excl") %>%
-  group_by(dat, metric_name) %>%
-  summarize(proportion_high = mean(value > 95))
-
-all_di_shapes_high %>%
-  tidyr::pivot_wider(id_cols = dat, names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")
-
-all_di_shapes_low <- all_di_shapes_long %>%
-  filter(metric_mod == "incl") %>%
-  group_by(dat, metric_name) %>%
-  summarize(proportion_low = mean(value <5))
-
-all_di_shapes_low %>%
-  tidyr::pivot_wider(id_cols = dat, names_from = metric_name, values_from = proportion_low) %>%
-  mutate(dir = "LOW")
-
-```
-<!-- ``` -->
 <!-- ```{r} -->
 
-<!-- ggplot(all_di, aes((real_po / sim_pos_from_best), real_po_percentile_excl, color =  real_po_percentile_excl > 95)) + -->
-<!--   geom_point(alpha = .3)  -->
+<!-- ggplot(all_di, aes(sim_r2_from_best_median)) + -->
+<!--   geom_histogram() -->
 
-<!-- all_di %>% -->
-<!--   mutate(rat = real_po / sim_pos_from_best, -->
-<!--          dev = real_po_percentile_excl > 95) %>% -->
-<!--   group_by(dev) %>% -->
-<!--   summarize(minrat = min(rat), -->
-<!--             maxrat = max(rat), -->
-<!--             meanrat = mean(rat), -->
-<!--             mindis = min(real_po - sim_pos_from_best), -->
-<!--             maxdis = max(real_po - sim_pos_from_best)) -->
+<!-- ggplot(all_di, aes(sim_r2_from_best_median, real_r2)) + -->
+<!--   geom_point() + -->
+<!--   geom_line(aes(sim_r2_from_best_median, sim_r2_from_best_median)) + -->
+<!--   ylim(0,1) -->
 
-<!-- ggplot(all_di, aes(nparts, sim_pos_from_best)) + -->
+<!-- ggplot(all_di, aes(real_po_percentile_excl)) + geom_histogram() -->
+
+<!-- ggplot(all_di, aes(nparts, sim_r2_from_best_median)) + -->
 <!--   geom_point() + -->
@@
 
-<!-- ggplot(all_di, aes(nparts, sim_pos_from_best, color = dat)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10()  + -->
-<!--   scale_color_viridis_d() + -->
-<!--   theme(legend.position = "top") -->
-
-<!-- ggplot(all_di, aes(s0, n0, color =  sim_pos_from_best)) + -->
-<!--   geom_point() + -->
-<!--   scale_x_log10()  + -->
-<!--   scale_y_log10() + -->
-<!--   scale_color_viridis_c() + -->
-<!--   theme(legend.position = "top") -->
 <!-- ``` -->

### 2021-03-22 analysis/rev_prototyping/old/revision_results.Rmd
rev draft

--- 2021-03-13 analysis/rev_prototyping/revision_results.Rmd
@@
   mutate(in_fia = ifelse(Dataset == "FIA", "FIA", "Other datasets"))
+
+```
+
+## Datasets
+
+```{r, fig.dim = c(8,6)}
+
+ggplot(all_di, aes(s0, n0, color = Dataset)) +
+  geom_point(alpha = .3) +
+  scale_x_log10() +
+  scale_y_log10() +
+  scale_color_viridis_d(end = .8)
 
@@
 
+ggplot(filter(all_di_shapes_long, metric_mod == "mean"), aes(value)) +
+  geom_histogram(bins = 40) +
+  #facet_grid(rows = vars(dat), cols = vars(metric_name), scales = "free", switch = "y") +
+  facet_wrap(vars(metric_name, dat), scales = "free", ncol = 5) +
+  geom_vline(xintercept = c(2.5, 97.5))
+
 all_di_shapes_high <- all_di_shapes_long %>%
@@
 ```
+
 #### Shape metrics
@@
          metric_mod = ifelse(substr(metric, 5, 5) == "X", "excl", ifelse(substr(metric, 5,5) == "M", "mean", "incl")))
-
-ggplot(filter(all_di_shapes_long, metric_mod == "mean"), aes(value)) +
-  geom_histogram(bins = 40) +
-  #facet_grid(rows = vars(dat), cols = vars(metric_name), scales = "free", switch = "y") +
-  facet_wrap(vars(metric_name, dat, very_small), scales = "free", ncol = 5) +
-  geom_vline(xintercept = c(2.5, 97.5))
 
@@
 
+misc_jk_ct <- read.csv(here::here("misc_jk_cts.csv"))
+mcdb_jk_ct <- read.csv(here::here("mcbd_jk_cts.csv"))
+
 jk_cts <- read.csv(here::here("analysis", "rev_prototyping", "all_ct_jk.csv")) %>%
-
+  bind_rows(misc_jk_ct) %>%
+  bind_rows(mcdb_jk_ct) %>%
   mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
@@
 ```
+
+## Gentry
+
+```{r}
+
+all_di <- all_di %>%
+  mutate(low_avgn = n0/s0 < 3)
+
+ggplot(filter(all_di, nparts > 40, dat == "gentry"), aes( nsingletons_percentile)) + 
+geom_histogram() +
+  facet_wrap(vars(low_avgn), scales = "free_y")
+
+all_di %>%
+  filter(nparts > 40, dat == "gentry") %>%
+  group_by(low_avgn) %>%
+  summarize(low_nsingles = mean(nsingletons_percentile < 2.5),
+            high_even = mean(simpson_percentile_excl > 97.5),
+            high_shannon = mean(shannon_percentile_excl > 97.5),
+            low_skew = mean(skew_percentile < 2.5),
+            n = dplyr::n())
+
+ggplot(filter(all_di, nparts > 40), aes(nsingletons_median / s0)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
+  xlab("Median proportion of rare species")
+
+ggplot(filter(all_di, nparts > 40), aes(nsingletons_median / s0)) +
+  geom_histogram() +
+  facet_wrap(vars(dat), scales = "free_y", ncol = 1) +
+  xlab("Median proportion of rare species")
+
+ggplot(filter(all_di, nparts > 40, dat == "gentry"), aes(nsingletons_median / s0)) +
+  geom_histogram() +
+  facet_wrap(vars(low_avgn), scales = "free_y", ncol = 1) +
+  xlab("Median proportion of rare species")
+
+ggplot(filter(all_di, nparts > 40, dat == "gentry"), aes(s0, n0, color = low_avgn)) +
+  geom_point()
+
+ggplot(filter(all_di, nparts > 40), aes(s0, n0, color = nsingletons_median / s0, shape = Dataset)) +
+  geom_point() +
+  scale_x_log10() +
+  scale_y_log10() +
+  theme(legend.position = "top")
+
+ggplot(filter(all_di, nparts > 40, dat == "gentry"), aes((n0/s0), nsingletons_percentile)) + 
+  geom_point() +
+  scale_x_log10() +
+  geom_hline(yintercept = 2.5)
+
+```
+
+## Comparison of FIA to other small communities
+
+```{r}
+
+fia_max_s = max(filter(all_di, dat == "fia")$s0)
+fia_max_n = max(filter(all_di, dat == "fia")$n0)
+
+fia = filter(all_di, dat == "fia")
+
+small_di <- all_di %>%
+  filter(s0 <= fia_max_s,
+         n0 <= fia_max_n) %>%
+  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
+         right_corner = FALSE)
+
+for(i in 1:nrow(small_di)) {
+  if(small_di$dat[i] != "fia") {
+    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
+
+    max_n0_for_this_s0 = max(fia_match_s0$n0)
+
+    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
+
+  }
+}
+
+small_di <- small_di %>%
+  filter(!right_corner)
+not_fia <- filter(small_di, fia_yn != "fia")
+fia = filter(small_di, dat == "fia")
+
+small_di_s_n <- small_di %>%
+  select(s0, n0) %>%
+  distinct() %>%
+  mutate(in_fia = FALSE,
+         in_not_fia = FALSE)
+
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 
+  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
+
+}
+
+small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
+
+set.seed(1977)
+
+subsamples <- list()
+
+for(i in 1:nrow(small_di_s_n)) {
+
+  this_s0 = small_di_s_n$s0[i]
+  this_n0 = small_di_s_n$n0[i]
+
+  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
+
+  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
+
+  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
+
+  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
+  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
+
+  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
+
+}
+
+sub_di <- bind_rows(subsamples) %>%
+  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
+
+fia_di <- filter(sub_di, Dataset == "FIA")
+other_di <- filter(sub_di, Dataset != "FIA")
+
+```
+
+### Central tendency
+
+```{r}
+filter(sub_di, nparts > 20) %>%
+  group_by(Dataset) %>%
+  summarize(high_diss = mean(real_po_percentile_excl > 95))
+
+ggplot(sub_di, aes(real_po_percentile_excl)) +
+  geom_histogram() +
+  facet_wrap(vars(Dataset))
+ks.test(fia_di$real_po_percentile_excl, other_di$real_po_percentile_excl)
+
+ggplot(sub_di, aes(sim_pos_from_best)) +
+  geom_histogram() +
+  facet_wrap(vars(Dataset))
+
+ks.test(fia_di$sim_pos_from_best, other_di$sim_pos_from_best)
+
+```
+
+### Shape metrics
+
+```{r, fig.dim = c(7, 4)}
+
+sub_di_shapes_long <- sub_di  %>%
+  filter(nparts > 40) %>%
+  #mutate(Dataset = ifelse(nparts < 1000, paste0(Dataset, "_small"), Dataset)) %>%
+  select(Dataset, skew_percentile, skew_percentile_excl, simpson_percentile, simpson_percentile_excl, shannon_percentile, shannon_percentile_excl, nsingletons_percentile, nsingletons_percentile_excl) %>%
+  rename(skew = skew_percentile,
+         skewX = skew_percentile_excl,
+         simp = simpson_percentile,
+         simpX = simpson_percentile_excl,
+         shan = shannon_percentile,
+         shanX = shannon_percentile_excl,
+         nsng = nsingletons_percentile,
+         nsngX = nsingletons_percentile_excl) %>%
+  mutate(skewM = (skew + skewX) / 2,
+         simpM = (simp+ simpX)/2,
+         shanM = (shan+ shanX)/2,
+         nsngM = (nsng+ nsngX)/2) %>%
+  tidyr::pivot_longer(-Dataset, names_to = "metric", values_to = "value") %>%
+  mutate(metric_name = substr(metric, 0, 4),
+         metric_mod = ifelse(substr(metric, 5, 5) == "X", "excl", ifelse(substr(metric, 5,5) == "M", "mean", "incl")))
+
+ggplot(filter(sub_di_shapes_long, metric_mod == "mean"), aes(value)) +
+  geom_histogram(bins = 40) +
+  #facet_grid(rows = vars(dat), cols = vars(metric_name), scales = "free", switch = "y") +
+  facet_wrap(vars(metric_name, Dataset), scales = "free", ncol = 2) +
+  geom_vline(xintercept = c(2.5, 97.5))
+
+sub_di_shapes_high <- sub_di_shapes_long %>%
+  filter(metric_mod == "excl") %>%
+  group_by(Dataset, metric_name) %>%
+  summarize(proportion_high = mean(value > 97.5),
+            n = dplyr::n())
+
+sub_di_shapes_high %>%
+  tidyr::pivot_wider(id_cols = c(Dataset, n), names_from = metric_name, values_from = proportion_high) %>% mutate(dir = "HIGH")
+
+sub_di_shapes_low <- sub_di_shapes_long %>%
+  filter(metric_mod == "incl") %>%
+  group_by(Dataset, metric_name) %>%
+  summarize(proportion_low = mean(value <2.5))
+
+sub_di_shapes_low %>%
+  tidyr::pivot_wider(id_cols = Dataset, names_from = metric_name, values_from = proportion_low) %>%
+  mutate(dir = "LOW")
+
+ks.test(fia_di$nsingletons_percentile_excl, other_di$nsingletons_percentile_excl)
+ks.test(fia_di$skew_percentile_excl, other_di$skew_percentile_excl)
+ks.test(fia_di$simpson_percentile, other_di$simpson_percentile)
+ks.test(fia_di$shannon_percentile, other_di$shannon_percentile)
+
+```

### 2021-04-02 analysis/rev_prototyping/draft_reports/appendices/s10_very_small_results.Rmd
set up to run cts for jks not in par, low resources

--- 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 ---
-title: "Figures and results for main manuscript"
+title: "Complete results for very small (<2000 possible SADs) communities"
 author: Renata Diaz
@@
        toc: true
+    word_document:
+        df_print: kable
+        toc: false
 ---
@@
 
-```{r, fig.dim = c(10,5)}
+# Proportions of extreme values
 
-fig_2 <- gridExtra::grid.arrange(grobs = list(
+```{r, fig.dim = c(6,8)}
 
-  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-```
-
-# Gentry
-
-```{r}
-
-gentry_di <- filter(all_di, Dataset == "Gentry")
-
-gentry_di <- gentry_di %>%
-  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3),
-  plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund")
-), ncol = 2,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-```
-
-# Comparison of FIA and comparably sized communities (Figure 4)
-
-```{r, fig.dim = c(10, 5)}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-fia_di <- filter(sub_di, fia_yn == "fia")
-other_di <- filter(sub_di, fia_yn != "fia")
-
-ks_compare <- function(fia_df, other_df, compare_var) {
-
-  if(grepl("skew", compare_var)) {
-    fia_df <- filter(fia_df, s0 > 2)
-    other_df <- filter(fia_df, s0 >2)
-  }
-
-  if(grepl("sim_pos", compare_var)) {
-    fia_df <- filter(fia_df, nparts > 20)
-    other_df <- filter(other_df, nparts > 20)
-  } else {
-      fia_df <- filter(fia_df, nparts > 40)
-    other_df <- filter(other_df, nparts > 40)
-  }
-
-  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])
-
-  return(data.frame(
-    var = compare_var,
-    d = kstest$statistic,
-    p = kstest$p.value
-  ))
-}
-
-simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
-skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
-shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
-nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
-
-bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
-
-simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
-skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
-shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
-nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
-diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
-
-bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-diss_results <- sub_di %>%
+all_di <- all_di %>%
+  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000", "More than 2000"))
+diss_results <- all_di %>%
   filter(nparts > 20) %>%
-  group_by(Dataset) %>%
+  group_by(Dataset,  `Number of elements` ) %>%
   summarize(high_diss = mean(real_po_percentile_excl > 95),
@@
 
-skew_results <- sub_di %>%
+skew_results <- all_di %>%
   filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
+  group_by(Dataset,  `Number of elements` ) %>%
   summarize(high_skew = mean(skew_percentile_excl > 97.5),
@@
 
-metric_results <- sub_di %>%
+metric_results <- all_di %>%
   filter(nparts > 40) %>%
-  group_by(Dataset) %>%
+  group_by(Dataset,  `Number of elements` ) %>%
   summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
@@
 
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+all_di %>%
+  filter(dat %in% c("fia", "mcdb", "misc_abund")) %>%
+  group_by(Dataset) %>%
+  summarize(`Proportion with nparts < 2000` = mean(nparts < 2000))
 
 all_results %>%
+  filter(Dataset %in% c("FIA", "Mammal Communities", "Misc. Abundance")) %>%
   select(cols1)
+```
+
+# Distributions of breadth indices and percentile scores
+
+Breadth indices (top) and percentile scores (bottom) for communities with fewer than 2000 possible SADs, or more than 2000 possible SADs, from FIA, Mammal Community, and Misc. Abundance datasets.
+
+```{r, fig.dim = c(6,8)}
+
+nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity to the central tendency") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
+  xlab("Mean dissimilarity of elements of feasible set to central tendency") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+phist <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "real_po_percentile_mean", "Dissimilarity to the central tendency") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
+  xlab("Percentile rank of observed value relative to feasible set") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+nskew <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Breadth index") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+pskew <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Percentile rank of observed value relative to feasible set") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+nrare <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_95_ratio_2t", "Number of rare species") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Breadth index") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+prare <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_percentile_mean", "Number of rare species") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Percentile rank of observed value relative to feasible set") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+nsimp <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_95_ratio_2t", "Simpson") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Breadth index") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+psimp <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_percentile_mean", "Simpson") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Percentile rank of observed value relative to feasible set") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+nshan <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_95_ratio_2t", "Shannon") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Breadth index") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+pshan <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_percentile_mean", "Shannon") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
+  xlab("Percentile rank of observed value relative to feasible set") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2, top = textGrob("Dissimilarity to the central tendency"))
+
+gridExtra::grid.arrange(grobs = list(nskew, pskew), nrow = 2, top = textGrob("Skewness"))
+
+gridExtra::grid.arrange(grobs = list(nrare, prare), nrow = 2, top = textGrob("Number of rare species"))
+
+gridExtra::grid.arrange(grobs = list(nsimp, psimp), nrow = 2, top = textGrob("Simpson"))
+
+gridExtra::grid.arrange(grobs = list(nshan, pshan), nrow = 2, top = textGrob("Shannon"))
 

### 2021-04-13 analysis/reports/submission1/accessory/old_reports/synthesis.Rmd
reorganize branch

--- 2020-02-20 analysis/reports/synthesis.Rmd
@@
 
-all_di_macd <- readd(all_di_manip, cache = cache) 
+all_di_macd <- readd(all_di_obs, cache = cache) 
+all_di_macd_manip <- readd(all_di_manip, cache = cache)
 macd_dat <- readd(dat_s_dat_macdb, cache = cache)
@@
 
-macd_dat <- macd_dat %>%
-  group_by(site, dat, singletons, sim, source) %>%
-  summarize(s0 = max(rank),
-            n0 = sum(abund)) %>%
-  ungroup()
-
-all_di_macd <- left_join(all_di_macd, macd_dat, by = c("site", "dat", "singletons", "sim", "source")) %>%
+all_di_macd <- all_di_macd %>%
   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
@@
   mutate(found_all = prop_found==1)
+# 
+# all_di_macd_manip <- all_di_macd_manip %>%
+#   mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+#          log_nsamples = log(nsamples)) %>%
+#   mutate(prop_found = exp(log_nsamples - log_nparts)) %>%
+#   mutate(found_all = prop_found==1)
 
@@
 
-macd_comparisons <- read.csv(here::here("working-data", "macdb_data", "orderedcomparisons.csv"), header = F, stringsAsFactors = F)
-
-colnames(macd_comparisons) <- c("studyID", "control", "site")
-macd_comparisons <- macd_comparisons %>%
-  mutate(site = as.character(site), control = as.character(control))
-
-cc_di <- all_di_macd %>%
-  filter(singletons == FALSE, treatment == "comparison") %>%
-  left_join(macd_comparisons, by = c("studyID", "site")) %>%
-  select(dat, site, skew_percentile, simpson_percentile, studyID, control) %>%
-  rename(comparison = site) %>%
-  mutate(ctrl_skew_percentile = NA,
-         ctrl_simpson_percentile = NA)
-
-for(i in 1:nrow(cc_di)) {
-
-  control_row <- filter(all_di_macd, site == cc_di$control[i], singletons == F) %>%
-    unique()
-  if(nrow(control_row) >0 ) {
-    cc_di$ctrl_simpson_percentile[i] <- control_row$simpson_percentile
-    cc_di$ctrl_skew_percentile[i] <- control_row$skew_percentile
-  }
-}
-
-cc_di <- cc_di %>%
-  mutate(simpson_change = simpson_percentile - ctrl_simpson_percentile,
-         skew_change = skew_percentile - ctrl_skew_percentile)
-
-ggplot(data = cc_di, aes(x = skew_percentile, y = ctrl_skew_percentile)) +
+ggplot(data = all_di_macd_manip, aes(x = skew_percentile, y = ctrl_skew_percentile)) +
   geom_point(alpha = .5) +
@@
 
-ggplot(data = cc_di, aes(x = simpson_percentile, y = ctrl_skew_percentile)) +
+ggplot(data = all_di_macd_manip, aes(x = simpson_percentile, y = ctrl_skew_percentile)) +
   geom_point(alpha = .5) +
@@
 
-ggplot(data = cc_di, aes(x = simpson_change)) +
+ggplot(data = all_di_macd_manip, aes(x = simpson_change)) +
   geom_histogram() +
@@
 
-ggplot(data = cc_di, aes(x = skew_change)) +
+ggplot(data = all_di_macd_manip, aes(x = skew_change)) +
   geom_histogram() +
@@
 
-ggplot(data = cc_di, aes(x = ctrl_simpson_percentile, y = simpson_change)) +
+ggplot(data = all_di_macd_manip, aes(x = ctrl_simpson_percentile, y = simpson_change)) +
   geom_point(alpha = .3) +
@@
 
-ggplot(data = cc_di, aes(x = ctrl_skew_percentile, y = skew_change)) +
+ggplot(data = all_di_macd_manip, aes(x = ctrl_skew_percentile, y = skew_change)) +
   geom_point(alpha = .3) +
@@
 
-print(t.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T)
+print(t.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T)
 )
-print(t.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T)
+print(t.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T)
 )
 
-print(wilcox.test(cc_di$skew_percentile, cc_di$ctrl_skew_percentile, paired = T))
-print(wilcox.test(cc_di$simpson_percentile, cc_di$ctrl_simpson_percentile, paired = T))
+print(wilcox.test(all_di_macd_manip$skew_percentile, all_di_macd_manip$ctrl_skew_percentile, paired = T))
+print(wilcox.test(all_di_macd_manip$simpson_percentile, all_di_macd_manip$ctrl_simpson_percentile, paired = T))
 

### 2021-04-13 analysis/reports/submission1/accessory/rarefaction.Rmd
reorganize branch

--- 2021-02-24 analysis/rev_prototyping/rarefaction.Rmd
@@
          log_n0 = log(n0)) %>%
-  filter(n0 != s0,
-         s0 != 1,
-         n0 != (s0 + 1)) %>%
+  filter(n0 > s0,
+         s0 > 1,
+         dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
   mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
-         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
-  mutate(Dataset = dat,
-         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
-         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
-         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
-         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
-         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset))
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
 ```
@@
 adjusted_comparison <- all_di %>%
-  select(dat, site, singletons, s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile_excl, nsingletons_percentile, mean_po_comparison_percentile, log_nparts) %>%
-  tidyr::pivot_wider(id_cols = c(dat, site), names_from = singletons, values_from = c(s0, n0, skew_percentile_excl, simpson_percentile, shannon_percentile, nsingletons_percentile_excl, nsingletons_percentile, mean_po_comparison_percentile, log_nparts))
+  select(dat, site, singletons, s0, n0, skew_percentile_excl, simpson_percentile, log_nparts, simpson_unique, skew_unique) %>%
+  tidyr::pivot_wider(id_cols = c(dat, site), names_from = singletons, values_from = c(s0, n0, skew_percentile_excl, simpson_percentile, log_nparts, simpson_unique, skew_unique))
 

### 2021-04-13 analysis/reports/submission1/figure_s5.Rmd
reorganize branch

--- 2020-12-18 analysis/reports/figure_s5.Rmd
@@
 s3_fig2 <- gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
+  ggplot(filter(all_di, s0 > 2, nparts > 20), aes(x = log_nparts, y= skew_95_ratio_1t)) +
   geom_point(alpha = .1) +
@@
 
-ggplot(filter(all_di, simpson_unique > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
+ggplot(filter(all_di, nparts > 20), aes(x = log_nparts, y= simpson_95_ratio_1t)) +
   geom_point(alpha = .1) +
@@
 
-pdf("figure_s5.pdf")
+pdf("figure_s5.pdf", bg = "white")
 plot(s3_fig2)

### 2021-04-13 analysis/reports/submission1/table_s6.Rmd
reorganize branch

--- 2020-12-18 analysis/reports/table_s6.Rmd
@@
   group_by_all %>%
-  mutate(skew_percentile_excl = ifelse(skew_unique >= 20, skew_percentile_excl, NA),
-         simpson_percentile = ifelse(simpson_unique >= 20, simpson_percentile, NA)) %>%
+  mutate(skew_percentile_excl = ifelse(nparts >= 20, skew_percentile_excl, NA),
+         simpson_percentile = ifelse(nparts >= 20, simpson_percentile, NA)) %>%
   ungroup() %>%

### 2021-04-13 analysis/reports/submission2/appendices/s10_very_small_results.Rmd
reorganize branch

--- 2021-04-02 analysis/rev_prototyping/draft_reports/appendices/s10_very_small_results.Rmd
@@
 output: 
-    github_document:
-       df_print: kable
-       toc: true
+    # github_document:
+    #    df_print: kable
+    #    toc: true
     word_document:

### 2021-04-13 analysis/reports/submission2/appendices/s4_dissimilarity_fig.Rmd
reorganize branch

--- 2021-04-02 analysis/rev_prototyping/draft_reports/appendices/s10_very_small_results.Rmd
@@
 ---
-title: "Complete results for very small (<2000 possible SADs) communities"
+title: "Dissimilarity of FS vs. actual"
 author: Renata Diaz
@@
 
-```{r, fig.dim = c(3, 6)}
+```{r}
 plot_percentile_hist <- function(di_df, col_name, plot_name, tails = 2, facetvar = "Dataset", min_s0 = 0) {
@@
 
-```{r, fig.dim = c(3, 6)}
-
-plot_narrowness <- function(di_df, yvar, yvar_name) {
-
-  if(grepl("sim_pos", yvar)) {
-    min_nparts = 20
-    ylabel = "Mean dissimilarity"
-  } else {
-    min_nparts = 40
-    ylabel = "Breadth index"
-  }
-
-  di_df <- di_df %>%
-    mutate(response = (di_df[[yvar]])) %>%
-    filter(nparts > min_nparts,
-           nparts < 10 ^ 50)
-
-  ggplot(di_df, aes(nparts, response, color = Dataset)) +
-    geom_point(data = filter(di_df, dat == "fia"), alpha = .1) +
-    geom_point(data = filter(di_df, dat != "fia"), alpha = .1) +
-    geom_point(data = filter(di_df, s0 < 0)) +
-    scale_color_viridis_d(end = .9) +
-    xlab("") +
-    ylab(ylabel) +
-    scale_x_log10() +
-    ggtitle(yvar_name) +
-    theme(legend.position = "none")+
-    theme(plot.title = element_text(size=10))
-}
-
-plot_narrowness_legend <- function(di_df) {
-
-  legend_df <- di_df %>%
-    select(Dataset) %>%
-    distinct() %>%
-    mutate(ymark = dplyr::row_number())
-
-  ggplot(legend_df, aes(1, ymark, color = Dataset)) +
-    geom_label(aes(x = 2, y = ymark, label = Dataset)) +
-    geom_point(size = 4) +
-    scale_color_viridis_d(end = .9) +
-    xlab("") +
-    ylab("") +
-    theme(legend.position = "none") +
-    xlim(1, 3) + theme(
-      panel.grid.major.x = element_blank(),
-      panel.grid.minor.x = element_blank(),
-      panel.grid.major.y = element_blank(),
-      panel.grid.minor.y = element_blank(),
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank()
-    ) +
-    ggtitle("Dataset")
-
-}
+```{r, fig.dim = c(7,7)}
+ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
+  geom_point(alpha = .3) +
+  geom_point(data = filter(all_di, s0 < 0)) +
+  geom_abline(slope = 1, intercept = 0) +
+  scale_color_viridis_d(end = .8, direction = -1) +
+  xlab("Mean of elements from feasible set") +
+  ylab("Observed value") +
+  ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")+
+  facet_wrap(vars(Dataset))
+#,
 #
-# gridExtra::grid.arrange(grobs = list(
-#   plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity to central tendency"),
-#   plot_narrowness_legend(all_di)),
-#   ncol = 1)
-```
-
-```{r}
-
-plot_narrowness_hist <- function(di_df, col_name, plot_name, facetvar = "Dataset", min_s0 = 0) {
-
-  if(grepl("sim_pos", col_name)) {
-    xvarname = "Mean dissimilarity"
-    min_nparts = 40
-  } else {
-    min_nparts = 20
-    xvarname = "Breadth index"
-  }
-
-  di_df <- di_df %>%
-    mutate(response = (di_df[[col_name]]),
-           facetvar = di_df[[facetvar]])
-
-  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
-    geom_histogram(bins = 40, boundary = 100) +
-    theme_bw() +
-    ylab("") +
-    xlab(xvarname) +
-    ggtitle( plot_name) +
-    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
-    theme(plot.title = element_text(size=10))
-
-}
+#
+# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
+#   geom_point(alpha = .3) +
+#   geom_point(data = filter(all_di, s0 < 0)) +
+#   scale_color_viridis_d(end = .9) +
+#   xlab("Number of elements in the feasible set") +
+#   ylab("Mean dissimilarity of feasible set to central tendency") +
+#   scale_x_log10() +
+#   ggtitle("Over the size of the feasible set")
+# ), ncol = 1,
+#top = textGrob("Dissimilarity to central tendency"))
 
@@
 
-# Proportions of extreme values
-
-```{r, fig.dim = c(6,8)}
-
-all_di <- all_di %>%
-  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000", "More than 2000"))
-diss_results <- all_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset,  `Number of elements` ) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- all_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset,  `Number of elements` ) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- all_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset,  `Number of elements` ) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-all_di %>%
-  filter(dat %in% c("fia", "mcdb", "misc_abund")) %>%
-  group_by(Dataset) %>%
-  summarize(`Proportion with nparts < 2000` = mean(nparts < 2000))
-
-all_results %>%
-  filter(Dataset %in% c("FIA", "Mammal Communities", "Misc. Abundance")) %>%
-  select(cols1)
-```
-
-# Distributions of breadth indices and percentile scores
-
-Breadth indices (top) and percentile scores (bottom) for communities with fewer than 2000 possible SADs, or more than 2000 possible SADs, from FIA, Mammal Community, and Misc. Abundance datasets.
-
-```{r, fig.dim = c(6,8)}
-
-nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity to the central tendency") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
-  xlab("Mean dissimilarity of elements of feasible set to central tendency") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-phist <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "real_po_percentile_mean", "Dissimilarity to the central tendency") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
-  xlab("Percentile rank of observed value relative to feasible set") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-nskew <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Breadth index") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-pskew <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Percentile rank of observed value relative to feasible set") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-nrare <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_95_ratio_2t", "Number of rare species") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Breadth index") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-prare <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_percentile_mean", "Number of rare species") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Percentile rank of observed value relative to feasible set") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-nsimp <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_95_ratio_2t", "Simpson") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Breadth index") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-psimp <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_percentile_mean", "Simpson") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Percentile rank of observed value relative to feasible set") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-nshan <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_95_ratio_2t", "Shannon") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Breadth index") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-pshan <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_percentile_mean", "Shannon") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)+
-  xlab("Percentile rank of observed value relative to feasible set") +
-  ylab("Number of communities") +
-  ggtitle("")
-
-gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2, top = textGrob("Dissimilarity to the central tendency"))
-
-gridExtra::grid.arrange(grobs = list(nskew, pskew), nrow = 2, top = textGrob("Skewness"))
-
-gridExtra::grid.arrange(grobs = list(nrare, prare), nrow = 2, top = textGrob("Number of rare species"))
-
-gridExtra::grid.arrange(grobs = list(nsimp, psimp), nrow = 2, top = textGrob("Simpson"))
-
-gridExtra::grid.arrange(grobs = list(nshan, pshan), nrow = 2, top = textGrob("Shannon"))
-
-```
+**Figure S4**.
+Observed SADs are often much more dissimilar to the central tendency of their feasible sets (y-axis) than the mean dissimilarity of samples from the feasible set and the central tendency (x-axis).
+Dissimilarity can range from 0-1.
+The black line is the 1:1 line.
+Of observed SADs that are more disssimilar to the central tendency than are 95% of samples from the feasible set (green points), the absolute increase in dissimlarity ranges from .04 to .6.
+These observed SADs are from 1.4 to 9.7 times more dissimilar to the central tendency than the maen of samples from the feasible set.

### 2021-04-13 analysis/reports/submission2/appendices/s8_gentry.Rmd
reorganize branch

--- 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 ---
-title: "Figures and results for main manuscript"
+title: "Unusual Gentry communities"
 author: Renata Diaz
@@
 
-```{r, fig.dim = c(10,5)}
+The Gentry communities are extreme relative to hte other datasets (in grey), in that they have high species richness and low abundance.
+Of these, the most extreme communities have extremely low average abundance (e.g.
+N/S < 3).
 
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-```
-
-# Gentry
-
-```{r}
+```{r, fig.dim = c(7,7)}
 
@@
 gentry_di <- gentry_di %>%
-  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
+  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3")) %>%
+  mutate(`Low average \nabundance` = low_avg_abund)
 
+ggplot(gentry_di, aes(s0, n0, color = `Low average \nabundance`)) +
+  geom_point(data = all_di, inherit.aes = F, aes(s0, n0), color = "grey", alpha = .1) +  geom_point() +
+scale_x_log10() + scale_y_log10() + xlab("Species richness (S); note log scale") + ylab("Total abundance (N); note log scale") + ggtitle("Gentry communities", subtitle = "(in color)")
+
+```
+
+These low-average-abundance communities account for most of the signal of extreme values in the unusual direction for various metrics - that is, a **low** number of rare species and **low** skewness, and **high** Shannon and Simpson evenness.
+Gentry communities with average abundance > 3 tend to show the signal in the same direction as most other communities.
+
+```{r, fig.dim = c(7,7)}
 fig_2 <- gridExtra::grid.arrange(grobs = list(
@@
 ```
-
-# Comparison of FIA and comparably sized communities (Figure 4)
-
-```{r, fig.dim = c(10, 5)}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-fia_di <- filter(sub_di, fia_yn == "fia")
-other_di <- filter(sub_di, fia_yn != "fia")
-
-ks_compare <- function(fia_df, other_df, compare_var) {
-
-  if(grepl("skew", compare_var)) {
-    fia_df <- filter(fia_df, s0 > 2)
-    other_df <- filter(fia_df, s0 >2)
-  }
-
-  if(grepl("sim_pos", compare_var)) {
-    fia_df <- filter(fia_df, nparts > 20)
-    other_df <- filter(other_df, nparts > 20)
-  } else {
-      fia_df <- filter(fia_df, nparts > 40)
-    other_df <- filter(other_df, nparts > 40)
-  }
-
-  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])
-
-  return(data.frame(
-    var = compare_var,
-    d = kstest$statistic,
-    p = kstest$p.value
-  ))
-}
-
-simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
-skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
-shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
-nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
-
-bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
-
-simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
-skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
-shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
-nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
-diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
-
-bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-diss_results <- sub_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- sub_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- sub_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
-```

### 2021-04-13 analysis/reports/submission2/appendices/s9_fia_comparison.Rmd
reorganize branch

--- 2021-03-17 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 ---
-title: "Figures and results for main manuscript"
+title: "Comparison of FIA and equally-sized communities"
 author: Renata Diaz
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = F, warning  = F)
 library(drake)
@@
 ```
-
-```{r, fig.dim = c(10,5)}
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-```
-
-# Gentry
-
-```{r}
-
-gentry_di <- filter(all_di, Dataset == "Gentry")
-
-gentry_di <- gentry_di %>%
-  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3),
-  plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund")
-), ncol = 2,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-```
-
-# Comparison of FIA and comparably sized communities (Figure 4)
 
@@
 
-simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
-skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
-shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
-nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
+```
 
-bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
+We identified ~330 communities in FIA with exact matches, in terms of S and N, among communities from other datasets.
+We then compared the distributions of percentile scores and breadth indices of FIA communities to communities from other datasets, visually and using Kolmogorov-Smirnov tests.
 
-simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
-skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
-shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
-nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
-diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
+## Percentile scores
 
-bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
+### Histograms
 
+```{r, fig.dim = c(8,4)}
 fig_2 <- gridExtra::grid.arrange(grobs = list(
@@
 
-fig_2 <- gridExtra::grid.arrange(grobs = list(
+```
 
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
+### Proportions of extreme percentile scores
+
+```{r}
 
@@
 ```
+### K-S test results
+
+```{r}
+simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
+skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
+shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
+nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
+diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
+
+bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks) %>%
+  select(var, d, p) %>%
+  mutate(Variable = c("Simpson", "Skew", "Shannon", "Number of rare species", "Dissimilarity to central tendency")) %>%
+  select(Variable, d, p) %>%
+  rename(`K-S D` = d,
+         `p-value` = p)
+
+```
+
+## Breadth indices
+
+### Histograms
+
+```{r, fig.dim = c(8,4)}
+fig_2 <- gridExtra::grid.arrange(grobs = list(
+
+  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
+  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
+  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
+  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
+), ncol = 5,
+ left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
+```
+
+### K-S test results
+
+```{r}
+
+simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
+skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
+shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
+nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
+diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
+
+bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks) %>%
+  select(var, d, p) %>%
+  mutate(Variable = c("Simpson", "Skew", "Shannon", "Number of rare species", "Dissimilarity to central tendency")) %>%
+  select(Variable, d, p) %>%
+  rename(`K-S D` = d,
+         `p-value` = p) 
+```

### 2021-04-13 analysis/reports/submission2/manuscript_main_rev.Rmd
reorganize branch

--- 2021-03-18 analysis/rev_prototyping/manuscript_main_rev.Rmd
@@
 
-```{r, fig.dim = c(7,7)}
+```{r, fig.dim = c(7,5)}
 
 s4_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
-  geom_point(alpha = .1) +
-  geom_point(data = filter(all_di), alpha = .4) +
+   geom_point(data = filter(all_di, dat == "fia"), alpha = .1) +
+   geom_point(data = filter(all_di, dat != "fia"), alpha = .2) +
+     geom_point(data = filter(all_di, dat == "points for legend"), alpha = 1) +
+
   theme_bw() +
@@
 
-# Illustrations of 95% interval (Figure 2)
-
-To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
+<!-- # Illustrations of 95% interval (Figure 2) -->
+
+<!-- To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md. -->
 
@@
 
-<!-- fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 1", gp = gpar(fill = "white"))) -->
+<!-- fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 2", gp = gpar(fill = "white"))) -->
 
 <!-- plot(fig_1) -->
+
+<!-- signif(as.numeric(example_di$nparts), digits = 2) -->
+<!-- (as.numeric(example_di2$nparts)) -->
+<!-- as.numeric(example_di3$nparts) -->
 
@@
 
-```{r, fig.dim = c(4, 4)}
-ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
-  geom_point(alpha = .3) + 
-  geom_point(data = filter(all_di, s0 < 0)) +
-  geom_abline(slope = 1, intercept = 0) +
-  scale_color_viridis_d(end = .8, direction = -1) +
-  xlab("Mean of elements from feasible set") +
-  ylab("Observed value") +
-  ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")#,
-# 
-# 
-# ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) +
-#   geom_point(alpha = .3) + 
-#   geom_point(data = filter(all_di, s0 < 0)) +
-#   scale_color_viridis_d(end = .9) +
-#   xlab("Number of elements in the feasible set") +
-#   ylab("Mean dissimilarity of feasible set to central tendency") +
-#   scale_x_log10() +
-#   ggtitle("Over the size of the feasible set")
-# ), ncol = 1,
-#top = textGrob("Dissimilarity to central tendency"))
-
-```
+<!-- ```{r, fig.dim = c(4, 4)} -->
+<!-- ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) + -->
+<!--   geom_point(alpha = .3) + -->
+<!--   geom_point(data = filter(all_di, s0 < 0)) + -->
+<!--   geom_abline(slope = 1, intercept = 0) + -->
+<!--   scale_color_viridis_d(end = .8, direction = -1) + -->
+<!--   xlab("Mean of elements from feasible set") + -->
+<!--   ylab("Observed value") + -->
+<!--   ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")#, -->
+<!-- # -->
+<!-- # -->
+<!-- # ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) + -->
+<!-- #   geom_point(alpha = .3) + -->
+<!-- #   geom_point(data = filter(all_di, s0 < 0)) + -->
+<!-- #   scale_color_viridis_d(end = .9) + -->
+<!-- #   xlab("Number of elements in the feasible set") + -->
+<!-- #   ylab("Mean dissimilarity of feasible set to central tendency") + -->
+<!-- #   scale_x_log10() + -->
+<!-- #   ggtitle("Over the size of the feasible set") -->
+<!-- # ), ncol = 1, -->
+<!-- #top = textGrob("Dissimilarity to central tendency")) -->
+
+<!-- ``` -->
 
@@
 
-```{r first hists, fig.dim = c(10,5)}
+```{r, fig.dim = c(10,5)}
 
@@
 ), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+top = textGrob("Figure 3", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
 bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
@@
 
-```{r, fig.dim = c(10,5)}
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-```
-
-# Gentry
-
-```{r}
-
-gentry_di <- filter(all_di, Dataset == "Gentry")
-
-gentry_di <- gentry_di %>%
-  mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3),
-  plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"),
-  plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund")
-), ncol = 2,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-```
-
-# Comparison of FIA and comparably sized communities (Figure 4)
-
-```{r, fig.dim = c(10, 5)}
-
-fia_max_s = max(filter(all_di, dat == "fia")$s0)
-fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
-fia = filter(all_di, dat == "fia")
-
-small_di <- all_di %>%
-  filter(s0 <= fia_max_s,
-         n0 <= fia_max_n) %>%
-  mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"),
-         right_corner = FALSE)
-
-for(i in 1:nrow(small_di)) {
-  if(small_di$dat[i] != "fia") {
-    fia_match_s0 = filter(fia, s0 >= small_di$s0[i])
-
-    max_n0_for_this_s0 = max(fia_match_s0$n0)
-
-    small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0
-
-  }
-}
-
-small_di <- small_di %>%
-  filter(!right_corner)
-not_fia <- filter(small_di, fia_yn != "fia")
-fia = filter(small_di, dat == "fia")
-
-small_di_s_n <- small_di %>%
-  select(s0, n0) %>%
-  distinct() %>%
-  mutate(in_fia = FALSE,
-         in_not_fia = FALSE)
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  small_di_s_n$in_fia[i] = nrow(fia_matches) > 0
-  small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0
-
-}
-
-small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia)
-
-set.seed(1977)
-
-subsamples <- list()
-
-for(i in 1:nrow(small_di_s_n)) {
-
-  this_s0 = small_di_s_n$s0[i]
-  this_n0 = small_di_s_n$n0[i]
-
-  fia_matches = filter(fia, s0 == this_s0, n0 == this_n0)
-
-  not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0)
-
-  n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches))
-
-  fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F)
-  not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F)
-
-  subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ]))
-
-}
-
-sub_di <- bind_rows(subsamples) %>%
-  mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets"))
-
-fia_di <- filter(sub_di, fia_yn == "fia")
-other_di <- filter(sub_di, fia_yn != "fia")
-
-ks_compare <- function(fia_df, other_df, compare_var) {
-
-  if(grepl("skew", compare_var)) {
-    fia_df <- filter(fia_df, s0 > 2)
-    other_df <- filter(fia_df, s0 >2)
-  }
-
-  if(grepl("sim_pos", compare_var)) {
-    fia_df <- filter(fia_df, nparts > 20)
-    other_df <- filter(other_df, nparts > 20)
-  } else {
-      fia_df <- filter(fia_df, nparts > 40)
-    other_df <- filter(other_df, nparts > 40)
-  }
-
-  kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]])
-
-  return(data.frame(
-    var = compare_var,
-    d = kstest$statistic,
-    p = kstest$p.value
-  ))
-}
-
-simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t")
-skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t")
-shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t")
-nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
-
-bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks)
-
-simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile")
-skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl")
-shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile")
-nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl")
-diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl")
-
-bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks)
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
- left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
-
-diss_results <- sub_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-skew_results <- sub_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- sub_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
-```
+<!-- ```{r, fig.dim = c(10,5)} -->
+
+<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
+
+<!--   plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"), -->
+<!--   plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"), -->
+<!--   plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
+<!--   plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"), -->
+<!--   plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset") -->
+<!-- ), ncol = 5, -->
+<!--  left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white")) -->
+
+<!-- ``` -->
+
+<!-- # Gentry -->
+
+<!-- ```{r} -->
+
+<!-- gentry_di <- filter(all_di, Dataset == "Gentry") -->
+
+<!-- gentry_di <- gentry_di %>% -->
+<!--   mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3")) -->
+
+<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
+
+<!--   plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"), -->
+<!--   plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3), -->
+<!--   plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"), -->
+<!--   plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund") -->
+<!-- ), ncol = 2, -->
+<!--  left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
+<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
+
+<!-- ``` -->
+
+<!-- # Comparison of FIA and comparably sized communities (Figure 4) -->
+
+<!-- ```{r, fig.dim = c(10, 5)} -->
+
+<!-- fia_max_s = max(filter(all_di, dat == "fia")$s0) -->
+<!-- fia_max_n = max(filter(all_di, dat == "fia")$n0) -->
+
+<!-- fia = filter(all_di, dat == "fia") -->
+
+<!-- small_di <- all_di %>% -->
+<!--   filter(s0 <= fia_max_s, -->
+<!--          n0 <= fia_max_n) %>% -->
+<!--   mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"), -->
+<!--          right_corner = FALSE) -->
+
+<!-- for(i in 1:nrow(small_di)) { -->
+<!--   if(small_di$dat[i] != "fia") { -->
+<!--     fia_match_s0 = filter(fia, s0 >= small_di$s0[i]) -->
+
+<!--     max_n0_for_this_s0 = max(fia_match_s0$n0) -->
+
+<!--     small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0 -->
+
+<!--   } -->
+<!-- } -->
+
+<!-- small_di <- small_di %>% -->
+<!--   filter(!right_corner) -->
+<!-- not_fia <- filter(small_di, fia_yn != "fia") -->
+<!-- fia = filter(small_di, dat == "fia") -->
+
+<!-- small_di_s_n <- small_di %>% -->
+<!--   select(s0, n0) %>% -->
+<!--   distinct() %>% -->
+<!--   mutate(in_fia = FALSE, -->
+<!--          in_not_fia = FALSE) -->
+
+<!-- for(i in 1:nrow(small_di_s_n)) { -->
+
+<!--   this_s0 = small_di_s_n$s0[i] -->
+<!--   this_n0 = small_di_s_n$n0[i] -->
+
+<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
+<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->
+
+<!--   small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 -->
+<!--   small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0 -->
+
+<!-- } -->
+
+<!-- small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia) -->
+
+<!-- set.seed(1977) -->
+
+<!-- subsamples <- list() -->
+
+<!-- for(i in 1:nrow(small_di_s_n)) { -->
+
+<!--   this_s0 = small_di_s_n$s0[i] -->
+<!--   this_n0 = small_di_s_n$n0[i] -->
+
+<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
+
+<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->
+
+<!--   n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches)) -->
+
+<!--   fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F) -->
+<!--   not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F) -->
+
+<!--   subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ])) -->
+
+<!-- } -->
+
+<!-- sub_di <- bind_rows(subsamples) %>% -->
+<!--   mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets")) -->
+
+<!-- fia_di <- filter(sub_di, fia_yn == "fia") -->
+<!-- other_di <- filter(sub_di, fia_yn != "fia") -->
+
+<!-- ks_compare <- function(fia_df, other_df, compare_var) { -->
+
+<!--   if(grepl("skew", compare_var)) { -->
+<!--     fia_df <- filter(fia_df, s0 > 2) -->
+<!--     other_df <- filter(fia_df, s0 >2) -->
+<!--   } -->
+
+<!--   if(grepl("sim_pos", compare_var)) { -->
+<!--     fia_df <- filter(fia_df, nparts > 20) -->
+<!--     other_df <- filter(other_df, nparts > 20) -->
+<!--   } else { -->
+<!--       fia_df <- filter(fia_df, nparts > 40) -->
+<!--     other_df <- filter(other_df, nparts > 40) -->
+<!--   } -->
+
+<!--   kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]]) -->
+
+<!--   return(data.frame( -->
+<!--     var = compare_var, -->
+<!--     d = kstest$statistic, -->
+<!--     p = kstest$p.value -->
+<!--   )) -->
+<!-- } -->
+
+<!-- simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t") -->
+<!-- skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t") -->
+<!-- shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t") -->
+<!-- nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t") -->
+<!-- diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best") -->
+
+<!-- bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks) -->
+
+<!-- simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile") -->
+<!-- skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl") -->
+<!-- shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile") -->
+<!-- nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl") -->
+<!-- diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl") -->
+
+<!-- bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks) -->
+
+<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
+
+<!--   plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1), -->
+<!--   plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"), -->
+<!--   plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
+<!--   plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"), -->
+<!--   plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset") -->
+<!-- ), ncol = 5, -->
+<!-- top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
+<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
+
+<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
+
+<!--   plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"), -->
+<!--   plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"), -->
+<!--   plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
+<!--   plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"), -->
+<!--   plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset") -->
+<!-- ), ncol = 5, -->
+<!--  left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white")) -->
+
+<!-- diss_results <- sub_di %>% -->
+<!--   filter(nparts > 20) %>% -->
+<!--   group_by(Dataset) %>% -->
+<!--   summarize(high_diss = mean(real_po_percentile_excl > 95), -->
+<!--             nsites = dplyr::n()) %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>% -->
+<!--   select(-nsites) -->
+
+<!-- skew_results <- sub_di %>% -->
+<!--   filter(nparts > 40, s0 > 2) %>% -->
+<!--   group_by(Dataset) %>% -->
+<!--   summarize(high_skew = mean(skew_percentile_excl > 97.5), -->
+<!--             low_skew = mean(skew_percentile < 2.5), -->
+<!--             nsites = dplyr::n()) %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites), -->
+<!--          `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>% -->
+<!--   select(-nsites) -->
+
+<!-- metric_results <- sub_di %>% -->
+<!--   filter(nparts > 40) %>% -->
+<!--   group_by(Dataset) %>% -->
+<!--   summarize(high_simpson = mean(simpson_percentile_excl > 97.5), -->
+<!--             low_simpson = mean(simpson_percentile < 2.5), -->
+<!--             high_shannon = mean(shannon_percentile_excl > 97.5), -->
+<!--             low_shannon = mean(shannon_percentile < 2.5), -->
+<!--             high_nsingletons = mean(nsingletons_percentile_excl > 97.5), -->
+<!--             low_nsingletons = mean(nsingletons_percentile < 2.5), -->
+<!--             nsites = dplyr::n()) %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites), -->
+<!--          `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites), -->
+<!--          `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites), -->
+<!--          `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites), -->
+<!--          `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites), -->
+<!--          `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>% -->
+<!--   select(-nsites) -->
+
+<!-- all_results <- left_join(diss_results, skew_results) %>% -->
+<!--   left_join(metric_results) -->
+
+<!-- cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon") -->
+
+<!-- all_results %>% -->
+<!--   select(cols1) -->
+
+<!-- ``` -->
 
@@
 
-```{r}
+```{r, fig.dim = c(6,8)}
 
@@
 
-plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "real_po_percentile_mean", "Dissimilarity") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_95_ratio_2t", "Number of rare species") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_percentile_mean", "Number of rare species") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_95_ratio_2t", "Simpson") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_percentile_mean", "Simpson") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_95_ratio_2t", "Shannon") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_percentile_mean", "Shannon") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-ggplot(all_di, aes(s0, n0, color = `Number of elements`)) +
-  geom_point() +
-  xlim(0, 30) +
-  ylim(0,150)
-
+all_di %>%
+  filter(dat %in% c("fia", "mcdb", "misc_abund")) %>%
+  group_by(Dataset) %>%
+  summarize(`Proportion with nparts < 2000` = mean(nparts < 2000))
+
+nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity to the central tendency") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
+  xlab("Mean dissimilarity of elements of feasible set to central tendency") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+phist <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "real_po_percentile_mean", "Dissimilarity to the central tendency") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
+  xlab("Percentile rank of observed value relative to feasible set") +
+  ylab("Number of communities") +
+  ggtitle("")
+
+gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2, top = textGrob("Dissimilarity to the central tendency"))
+
+# 
+# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+# 
+# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+
+# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_95_ratio_2t", "Number of rare species") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+# 
+# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_percentile_mean", "Number of rare species") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+# 
+# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_95_ratio_2t", "Simpson") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+# 
+# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_percentile_mean", "Simpson") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+# 
+# 
+# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_95_ratio_2t", "Shannon") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
+# 
+# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_percentile_mean", "Shannon") +
+#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
 ```
 
-```{r}
-
-all_di <- all_di %>%
-  mutate( `Number of elements` = ifelse(nparts < 1000, "Less than 1000", "More than 1000"))
-diss_results <- all_di %>%
-  filter(nparts > 20) %>%
-  group_by(Dataset,  `Number of elements`) %>%
-  summarize(high_diss = mean(real_po_percentile_excl > 95),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-ggplot(filter(all_di, dat == "mcdb"), aes(skew_95_ratio_2t)) + 
-  geom_histogram() +
-  facet_wrap(vars(`Number of elements`), scales = "free_y")
-
-skew_results <- all_di %>%
-  filter(nparts > 40, s0 > 2) %>%
-  group_by(Dataset,  `Number of elements`) %>%
-  summarize(high_skew = mean(skew_percentile_excl > 97.5),
-            low_skew = mean(skew_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites),
-         `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-metric_results <- all_di %>%
-  filter(nparts > 40) %>%
-  group_by(Dataset, `Number of elements`) %>%
-  summarize(high_simpson = mean(simpson_percentile_excl > 97.5),
-            low_simpson = mean(simpson_percentile < 2.5),
-            high_shannon = mean(shannon_percentile_excl > 97.5),
-            low_shannon = mean(shannon_percentile < 2.5),
-            high_nsingletons = mean(nsingletons_percentile_excl > 97.5),
-            low_nsingletons = mean(nsingletons_percentile < 2.5),
-            nsites = dplyr::n()) %>%
-  ungroup() %>%
-  mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites),
-         `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites),
-         `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites),
-         `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites),
-         `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites),
-         `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>%
-  select(-nsites)
-
-all_results <- left_join(diss_results, skew_results) %>%
-  left_join(metric_results)
-
-cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
-
-all_results %>%
-  select(cols1)
-
-```
+<!-- ```{r, fig.dim = c(8,3)} -->
+<!-- ggplot(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), aes(s0, n0, color = `Number of elements`)) + -->
+<!--   geom_point(alpha = .1) + -->
+<!--   xlim(0, 30) + -->
+<!--   ylim(0,150) + -->
+<!--     facet_wrap(vars(Dataset), nrow = 1) -->
+<!-- ggplot(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund"), nparts > 2000, nparts < 1e+20), aes(nparts)) + -->
+<!--   geom_histogram() + -->
+<!--   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y") + -->
+<!--   scale_x_log10() -->
+
+<!-- ggplot(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund"), nparts < 2000), aes(nparts)) + -->
+<!--   geom_histogram() + -->
+<!--   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y") + -->
+<!--   scale_x_log10() -->
+
+<!-- ``` -->
+
+<!-- ```{r} -->
+
+<!-- all_di <- all_di %>% -->
+<!--   mutate( `Number of elements` = ifelse(nparts < 1000, "Less than 1000", "More than 1000")) -->
+<!-- diss_results <- all_di %>% -->
+<!--   filter(nparts > 20) %>% -->
+<!--   group_by(Dataset,  `Number of elements`) %>% -->
+<!--   summarize(high_diss = mean(real_po_percentile_excl > 95), -->
+<!--             nsites = dplyr::n()) %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>% -->
+<!--   select(-nsites) -->
+<!-- ggplot(filter(all_di, dat == "mcdb"), aes(skew_95_ratio_2t)) + -->
+<!--   geom_histogram() + -->
+<!--   facet_wrap(vars(`Number of elements`), scales = "free_y") -->
+
+<!-- skew_results <- all_di %>% -->
+<!--   filter(nparts > 40, s0 > 2) %>% -->
+<!--   group_by(Dataset,  `Number of elements`) %>% -->
+<!--   summarize(high_skew = mean(skew_percentile_excl > 97.5), -->
+<!--             low_skew = mean(skew_percentile < 2.5), -->
+<!--             nsites = dplyr::n()) %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites), -->
+<!--          `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>% -->
+<!--   select(-nsites) -->
+
+<!-- metric_results <- all_di %>% -->
+<!--   filter(nparts > 40) %>% -->
+<!--   group_by(Dataset, `Number of elements`) %>% -->
+<!--   summarize(high_simpson = mean(simpson_percentile_excl > 97.5), -->
+<!--             low_simpson = mean(simpson_percentile < 2.5), -->
+<!--             high_shannon = mean(shannon_percentile_excl > 97.5), -->
+<!--             low_shannon = mean(shannon_percentile < 2.5), -->
+<!--             high_nsingletons = mean(nsingletons_percentile_excl > 97.5), -->
+<!--             low_nsingletons = mean(nsingletons_percentile < 2.5), -->
+<!--             nsites = dplyr::n()) %>% -->
+<!--   ungroup() %>% -->
+<!--   mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites), -->
+<!--          `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites), -->
+<!--          `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites), -->
+<!--          `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites), -->
+<!--          `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites), -->
+<!--          `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>% -->
+<!--   select(-nsites) -->
+
+<!-- all_results <- left_join(diss_results, skew_results) %>% -->
+<!--   left_join(metric_results) -->
+
+<!-- cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon") -->
+
+<!-- all_results %>% -->
+<!--   select(cols1) -->
+
+<!-- ``` -->
 
@@
 
-```{r, fig.dim = c(10,5)}
-
-all_di_with_resamples <- all_di_with_resamples %>%
-  group_by_all() %>%
-  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl, na.rm = T),
-         skew_percentile_mean = mean(skew_percentile, skew_percentile_excl, na.rm = T),
-         simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl, na.rm = T),
-         shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl, na.rm = T),
-         nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl)) %>%
-  ungroup()
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Subsampling results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-fig_2 <- gridExtra::grid.arrange(grobs = list(
-
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Adjusted for rare species results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-```
+<!-- ```{r, fig.dim = c(10,5)} -->
+
+<!-- all_di_with_resamples <- all_di_with_resamples %>% -->
+<!--   group_by_all() %>% -->
+<!--   mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl, na.rm = T), -->
+<!--          skew_percentile_mean = mean(skew_percentile, skew_percentile_excl, na.rm = T), -->
+<!--          simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl, na.rm = T), -->
+<!--          shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl, na.rm = T), -->
+<!--          nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl)) %>% -->
+<!--   ungroup() -->
+
+<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
+
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset") -->
+<!-- ), ncol = 5, -->
+<!-- top = textGrob("Subsampling results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
+<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
+
+<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
+
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"), -->
+<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset") -->
+<!-- ), ncol = 5, -->
+<!-- top = textGrob("Adjusted for rare species results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
+<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
+<!-- ``` -->

### 2021-04-13 analysis/reports/submission2/table1_extreme_values.Rmd
reorganize branch

--- 2021-03-22 analysis/rev_prototyping/draft_reports/appendices/s5_results_weird_direction.Rmd
@@
   left_join(metric_results)
+
+cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+
+all_results %>%
+  select(cols1)
+
 # 
-# cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+# cols2 <- c("Dataset", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
 # 
 # all_results %>%
-#   select(cols1)
-
-cols2 <- c("Dataset", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
-
-all_results %>%
-  select(cols2)
+#   select(cols2)
 
@@
 
-**Table ST5.** Proportions of extreme values for percentile scores for observed SADs compared to samples from the feasible set, for the less-usual direction of effects.
-This is the proportion of scores <2.5 or >97.5; by chance ~2.5% of scores should be in either extreme.
+**Table 1.** Proportions of extreme values for percentile scores for observed SADs compared to samples from the feasible set.
+For dissimilarity, this is the proportion of percentile scores >95; by chance, ~5% of scores should be in this extreme.
+For all other metrics, this is the proportion <2.5 or >97.5; by chance ~2.5% of scores should be in either extreme.
 n refers to the number of communities included for each dataset for each metric.

### 2021-04-13 analysis/helper_scripts/make_all_ct.R

@@ -40,4 +40,4 @@ for(i in 1:length(datasets)) {
 
 all_ct <- bind_rows(all_ct)
 
-write.csv(all_ct, here::here("analysis", "rev_prototyping", "all_ct.csv"), row.names = F)
+write.csv(all_ct, here::here("analysis", "reports", "submission2","all_ct.csv"), row.names = F)

### 2021-04-13 analysis/helper_scripts/make_all_ct_jk.R

@@ -40,4 +40,4 @@ for(i in 1:length(datasets)) {
 
 all_ct <- bind_rows(all_ct)
 
-write.csv(all_ct, here::here("analysis", "rev_prototyping", "all_ct_jk.csv"), row.names = F)
+write.csv(all_ct, here::here("analysis", "reports", "submission2", "all_ct_jk.csv"), row.names = F)

### 2021-04-13 analysis/helper_scripts/make_all_di.R

@@ -40,4 +40,4 @@ for(i in 1:length(datasets)) {
 
 all_di <- bind_rows(all_di)
 
-write.csv(all_di, here::here("analysis", "rev_prototyping", "all_di.csv"), row.names = F)
+write.csv(all_di, here::here("analysis", "reports", "submission2", "all_di.csv"), row.names = F)

### 2021-04-13 analysis/helper_scripts/make_all_di_jk.R

@@ -40,4 +40,4 @@ for(i in 1:length(datasets)) {
 
 all_di <- bind_rows(all_di)
 
-write.csv(all_di, here::here("analysis", "rev_prototyping", "all_di_jk.csv"), row.names = F)
+write.csv(all_di, here::here("analysis", "reports", "submission2", "all_di_jk.csv"), row.names = F)

### 2021-04-13 analysis/reports/accessory/old_reports/rov_comparisons/app.R

@@ -1,185 +1,0 @@
-#
-# This is a Shiny web application. You can run the application by clicking
-# the 'Run App' button above.
-#
-# Find out more about building applications with Shiny here:
-#
-#    http://shiny.rstudio.com/
-#
-
-library(shiny)
-library(ggplot2)
-library(dplyr)
-
-# Define UI for application that draws a histogram
-ui <- fluidPage(
-
-    # Application title
-    titlePanel("Results"),
-
-    # Sidebar with a slider input for number of bins
-    sidebarLayout(
-        sidebarPanel(
-            sliderInput("min_skew_interval",
-                        "Minimum 95 interval: skew",
-                        min = 0,
-                        max = 1,
-                        value = .95,
-                        step = .01),
-            sliderInput("max_skew_interval",
-                        "Maximum 95 interval: skew",
-                        min = 0,
-                        max = 1,
-                        value = 1,
-                        step = .01),
-            sliderInput("min_even_interval",
-                        "Minimum 95 interval: even",
-                        min = 0,
-                        max = 1,
-                        value = .01,
-                        step = .001),
-            sliderInput("max_even_interval",
-                        "Maximum 95 interval: even",
-                        min = 0,
-                        max = 1,
-                        value = .99,
-                        step = .001)
-        ),
-
-        # Show a plot of the generated distribution
-        mainPanel(plotOutput("skew_intervalPlot", width = 400, height = 200),
-                  plotOutput("skew_intervalHist", width = 400, height = 200),
-                  plotOutput("skew_snPlot", width = 400, height = 200),
-                  plotOutput("skewPlot", width = 400, height = 200),
-                  tableOutput("skewResults")#,
-                  # plotOutput("even_intervalPlot", width = 400, height = 200),
-                  # plotOutput("even_intervalHist", width = 400, height = 200),
-                  #
-                  # plotOutput("even_snPlot", width = 400, height = 200),
-                  # plotOutput("evenPlot", width = 400, height = 200),
-                  # tableOutput("evenResults")
-        )
-    )
-)
-
-# Define server logic required to draw a histogram
[…]

### 2021-04-13 analysis/reports/accessory/old_reports/size_comparisons/app.R

@@ -1,169 +1,0 @@
-#
-# This is a Shiny web application. You can run the application by clicking
-# the 'Run App' button above.
-#
-# Find out more about building applications with Shiny here:
-#
-#    http://shiny.rstudio.com/
-#
-
-library(shiny)
-library(ggplot2)
-library(dplyr)
-
-# Define UI for application that draws a histogram
-ui <- fluidPage(
-
-    # Application title
-    titlePanel("Results"),
-
-    # Sidebar with a slider input for number of bins
-    sidebarLayout(
-        sidebarPanel(
-            sliderInput("minparts",
-                        "Minimum number of parts:",
-                        min = 0,
-                        max = 17,
-                        value = 4.6,
-                        step = .001),
-            sliderInput("maxparts",
-                        "Maximum number of parts:",
-                        min = 0,
-                        max = 17,
-                        value = 6.9,
-                        step = .001)
-        ),
-
-        # Show a plot of the generated distribution
-        mainPanel(
-            tableOutput("sizeRange"),
-            plotOutput("snPlot", width = 400, height = 200),
-            plotOutput("windowPlot", width = 400, height = 200),
-            plotOutput("skewPlot", width = 400, height = 200),
-            tableOutput("skewResults"),
-            plotOutput("evenPlot", width = 400, height = 200),
-            tableOutput("evenResults")
-        )
-    )
-)
-
-# Define server logic required to draw a histogram
-server <- function(input, output) {
-
-    all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
-
-    all_di <- all_di %>%
-        mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
-               log_nsamples = log(nsamples),
-               log_s0 = log(s0),
-               log_n0 = log(n0)) %>%
-        filter(n0 > s0,
-               !singletons,
-               dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
-        mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
-               dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
-
-
-    fia_max_s = max(filter(all_di, dat == "fia")$s0)
-    fia_max_n = max(filter(all_di, dat == "fia")$n0)
-
[…]

### 2021-04-13 analysis/reports/submission1/accessory/old_reports/size_comparisons/app.R

@@ -1,0 +1,169 @@
+#
+# This is a Shiny web application. You can run the application by clicking
+# the 'Run App' button above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+library(ggplot2)
+library(dplyr)
+
+# Define UI for application that draws a histogram
+ui <- fluidPage(
+
+    # Application title
+    titlePanel("Results"),
+
+    # Sidebar with a slider input for number of bins
+    sidebarLayout(
+        sidebarPanel(
+            sliderInput("minparts",
+                        "Minimum number of parts:",
+                        min = 0,
+                        max = 17,
+                        value = 4.6,
+                        step = .001),
+            sliderInput("maxparts",
+                        "Maximum number of parts:",
+                        min = 0,
+                        max = 17,
+                        value = 6.9,
+                        step = .001)
+        ),
+
+        # Show a plot of the generated distribution
+        mainPanel(
+            tableOutput("sizeRange"),
+            plotOutput("snPlot", width = 400, height = 200),
+            plotOutput("windowPlot", width = 400, height = 200),
+            plotOutput("skewPlot", width = 400, height = 200),
+            tableOutput("skewResults"),
+            plotOutput("evenPlot", width = 400, height = 200),
+            tableOutput("evenResults")
+        )
+    )
+)
+
+# Define server logic required to draw a histogram
+server <- function(input, output) {
+
+    all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+
+    all_di <- all_di %>%
+        mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+               log_nsamples = log(nsamples),
+               log_s0 = log(s0),
+               log_n0 = log(n0)) %>%
+        filter(n0 > s0,
+               !singletons,
+               dat %in% c("bbs", "fia_short", "fia_small", "gentry", "mcdb", "misc_abund_short")) %>%
+        mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+               dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
+
+
+    fia_max_s = max(filter(all_di, dat == "fia")$s0)
+    fia_max_n = max(filter(all_di, dat == "fia")$n0)
+
[…]

### 2021-04-13 analysis/reports/submission2/appendices/s9_fia_comparison.Rmd

@@
 output: 
-    # github_document:
+    github_document:
+       df_print: kable
+       toc: true
+    # word_document:
     #     df_print: kable
-    #    toc: true
-    word_document:
-        df_print: kable
-        toc: false
+    #     toc: false
 ---

### 2021-04-14 analysis/howto.Rmd
reorganize branch
reprex

--- 2020-07-31 analysis/howto.Rmd
@@
 title: "How to run"
-output: github_document
+output: 
+    github_document:
+       df_print: kable
+       toc: true
 ---
@@
 
-# Installations
+# To explore results
 
-You will need to download and install hte package for this research compendium, as well as packages to run the analytical workflow and optionally HPC.
+Re-running the whole sampling analysis takes at least a week and requires a supercomputer. If you would like to just load the results from the analysis for exploration:
+
+- Clone or download `diazrenata/scadsanalysis` or the Zenodo archive.
+- Run the snippet in `analysis/helper_scripts/load_results_for_exploring.R`. 
+- This will give you a dataframe called `all_di`. This is the main dataframe for results. It has a lot of columns, descriptions for which are [below](#all_di_cols).
+
+If you would like to re-create the figures for the manuscript, you can re-render the reports in `analysis/reports/submission2`.
+`manuscript_main_rev.Rmd` is the figures and tables in the main text, and the reports in the `appendices` folder render each of the supplementary documents.
+
+# To re-run the analyses
+
+The full analytical pipeline can be replicated by installing `scadsanalysis` as an R package and running a series of scripts.
+It requires large amounts of memory and storage (terabytes), and needs parallelization to run in a reasonable amount of time.
+We run it on the UF HiPerGator, and you'd need to change the settings to work with a different cluster.
+
+For those interested in replicating a subset of the analyses with less compute, we have included instructions for running a subset locally.
+
+## Installations
+
+You will need to download and install the package for this research compendium, as well as packages to run the analytical workflow and optionally HPC.
 
 ```{r install packages, echo = T, eval  = F}
-devtools::install_github("diazrenata/scadsanalysis@clean-and-tests")
+remotes::install_github("diazrenata/scadsanalysis")
 install.packages("drake")
@@
 install.packages("storr")
-install.packages("clustermq")
+install.packages("clustermq") # Only if you are running on HPC
 
@@
 
-# Download and prep data
+## Download and prep data
+
+To download and prep the main datasets:
 
@@
 
-# Get the p tables
+To subsample the main datasets (subsampling was added after the core analyses were completed), render `analysis/helper_scripts/jacknife.Rmd`.
+You may need to create a directory called `analysis/rev_prototyping/jacknifed_datasets`.
 
-Either copy from directory, or run `analysis/helper_scripts/ptables_plan.R`. RMD runs this on a HPC cluster using `submit_p_pipeline.sbatch`. These are very large files.
+## Get the p tables
 
-# Run plans
+For sampling, you will need tables listing the number of possible SADs for combinations of S and N.
+This analysis uses 3 tables covering different swaths of SxN space.
+The first two can be created by running `analysis/helper_scripts/make_p_wide.R` and `analysis/helper_scripts/make_p_mamm.R`, and the largest one by running `analysis/helper_scripts/ptables_plan.R` (RMD ran this on a HPC cluster using `submit_p_pipeline.sbatch`).
+The files are too large for GitHub, but will be uploaded to Zenodo and made available for download there.
 
-Either source one of the pipelines directory or run via sbatch.
+To run a subset locally, you can just run `analysis/helper_scripts/make_p_mamm.R` or download `masterp_mamm.Rds` to the `analysis` directory.
+
+## Run plans
+
+Each dataset is run in its own (identical) pipeline, and we collect the results at the end.
+Either source one of the pipelines directly or run via sbatch.
+Running one of the pipeline files locally is not recommended.
+
+To run on the HiperGator, ssh in and run:
+
+`sbatch submit_bbs_pipeline.sbatch`, substituting whatever dataset name you want to run.
+
+Running on a different HPC cluster would take some setup.
+On the HiPerGator, we're using `drake` and SQLite caches to manage the pipelines, and `clustermq` to handle parallelization with the SLURM scheduler.
+
+To run a subset locally, you can run `mcdb_pipeline_demo.R`.
+This will run the pipeline on the first 100 communities in the Mammal Community Database.
+It takes [time] on a MacBook Air with 8GB memory and creates a [size] cache file.
+
+## Collect results
+
+Run `analysis/helper_scripts/make_all_di.R`, `analysis/helper_scripts/make_all_di_jk.R`, `analysis/helper_scripts/make_all_ct.R` and `analysis/helper_scripts/make_all_ct_jk.R` to collect the results from each of the pipelines into dataframes.
+If you ran the pipelines on a HPC cluster, run these scripts and copy the .csvs they create (currently stored at `analysis/reports/submission2/all_di.csv`, `all_di_jk.csv`, etc) to your local computer for viewing.
+
+For the local subset, you can run `analysis/helper_scripts/make_all_di_demo.R`. This will create the analogous results files for just the subset you ran.
+
+If you want to explore the results (and not re-run the actual analyses) these files are stored in GitHub/Zenodo at the paths above. You can just download the archive and work from these .csvs.
+
+## Render reports
+
+RMarkdown files for generating all of the figures and tables in the manuscript & supplements are at `analysis/reports/submission2`.
+`manuscript_main_rev.Rmd` renders the figures in the main text, and the .Rmd files in `analysis/reports/submission2/appendices` renders each of the supplementary documents.
+Once you have run the `make_all_X` scripts, or downloaded the results files, you can render any of these reports.
+
+To load the results for further exploration, you can start from the code in `analysis/helper_scripts/load_results_for_exploring.R`. This is the same setup snippet as begins the .Rmd files.
+
+<a id="all_di_cols"></a>
+
+### all_di columns
+
+`all_di` will be your main dataframe for exploring. It has a lot of columns, here is what they mean:
+
+```{r}
+
+column_descriptions <- read.csv(here::here("analysis", "reports", "submission2", "all_di_columns.csv" ))
+
+column_descriptions
+
+```

### 2021-04-14 analysis/reports/submission2/manuscript_main_rev.Rmd
reprex

@@
 
-all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)
-
-all_ct <-  read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"), stringsAsFactors = F)
-
-#fia_ct <- read.csv(here::here("fia_cts.csv"))
-
-#all_ct <- rbind(all_ct, fia_ct)
+all_di <- read.csv(here::here("analysis", "reports", "submission2", "all_di.csv"), stringsAsFactors = F)
+
+all_ct <-  read.csv(here::here("analysis",  "reports", "submission2","all_ct.csv"), stringsAsFactors = F)
+
 all_ct <- all_ct %>%

### 2021-04-14 R/load_results_for_exploring.R

@@ -1,0 +1,42 @@
+library(dplyr)
+
+all_di <- read.csv(here::here("analysis", "reports", "submission2", "all_di.csv"), stringsAsFactors = F)
+
+all_ct <-  read.csv(here::here("analysis",  "reports", "submission2","all_ct.csv"), stringsAsFactors = F)
+
+
+all_ct <- all_ct %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
+
+all_di <- all_di %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
+         log_nsamples = log(nsamples),
+         log_s0 = log(s0),
+         log_n0 = log(n0)) %>%
+  filter(n0 != s0,
+         s0 != 1,
+         !singletons,
+         n0 != (s0 + 1)) %>%
+  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
+         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
+  mutate(Dataset = dat,
+         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
+         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
+         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
+         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
+         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
+  filter(nparts > 20) %>%
+  left_join(all_ct)
+
+all_di <- all_di %>%
+  group_by_all() %>%
+  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl),
+         skew_percentile_mean = mean(skew_percentile, skew_percentile_excl),
+         simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl),
+         shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl),
+         nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl),) %>%
+  ungroup()
+
+all_di <- all_di %>%
+  mutate(in_fia = ifelse(Dataset == "FIA", "FIA", "Other datasets"))

### 2021-04-14 analysis/mcdb_pipeline_demo.R

@@ -1,0 +1,78 @@
+library(drake)
+library(scadsanalysis)
+library(ggplot2)
+
+expose_imports("scadsanalysis")
+
+datasets <- "mcdb"
+
+sites_list <- list_sites("mcdb")
+ndraws = 4000
+sites_list <- sites_list[1:100, ]
+set.seed(1980)
+
+
+all <- drake_plan(
+  dat = target(load_dataset(dataset_name = d),
+               transform = map(
+                 d = !!datasets
+               ),
+               hpc = F
+  ),
+  dat_s = target(add_singletons_dataset(dat),
+                 transform = map(dat),
+                 hpc = F),
+  mamm_p = target(readRDS(here::here("analysis", "masterp_mamm.Rds")),
+                  hpc = F),
+  fs = target(sample_fs_wrapper(dataset = dat_s_dat_mcdb, site_name = s, singletonsyn = singletons, n_samples = ndraws, p_table = mamm_p, seed = !!sample.int(10^6, size = 1)),
+              transform = cross(s = !!sites_list$site,
+                                singletons = !!c(TRUE, FALSE))),
+  # fs_diffs = target(get_fs_diffs(fs),
+  #                   transform = map(fs)),
+  fs_pc = target(compare_props_fs(fs),
+                 transform = map(fs)),
+  di = target(add_dis(fs, props_comparison = fs_pc),
+              transform = map(fs, fs_pc)),
+  di_obs = target(pull_di(di),
+                  transform = map(di)),
+  di_obs_s = target(dplyr::bind_rows(di_obs),
+                    transform = combine(di_obs, .by = singletons)),
+  all_di_obs = target(dplyr::bind_rows(di_obs_s_TRUE, di_obs_s_FALSE)),
+  cts = target(po_central_tendency(fs, fs_pc),
+               transform = map(fs, fs_pc)),
+  all_cts = target(dplyr::bind_rows(cts),
+                   transform = combine(cts))
+)
+
+## Set up the cache and config
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-mcdb-demo.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
+#
+# ## Run the pipeline
+# nodename <- Sys.info()["nodename"]
+# if(grepl("ufhpc", nodename)) {
+#  print("I know I am on the HiPerGator!")
[…]

### 2021-04-14 analysis/reports/submission2/appendices/s10_very_small_results.Rmd
fixing paths

--- 2021-04-02 analysis/rev_prototyping/draft_reports/appendices/s10_very_small_results.Rmd
@@
 
-all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "reports", "submission2", "all_di.csv"), stringsAsFactors = F)
 
-all_ct <-  read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"), stringsAsFactors = F)
+all_ct <-  read.csv(here::here("analysis", "reports", "submission2", "all_ct.csv"), stringsAsFactors = F)
 

### 2021-04-14 analysis/reports/submission2/appendices/s7_complete_resampling_results.Rmd
fixing paths

--- 2021-03-22 analysis/rev_prototyping/draft_reports/appendices/s7_complete_resampling_results.Rmd
@@
 
-all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis","reports", "submission2", "all_di.csv"), stringsAsFactors = F)
 
-all_ct <-  read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"), stringsAsFactors = F)
+all_ct <-  read.csv(here::here("analysis", "reports", "submission2", "all_ct.csv"), stringsAsFactors = F)
 
@@
 
-all_di_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))
+all_di_with_resamples <- read.csv(here::here("analysis", "reports", "submission2","all_di.csv"))
 
-jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
+jk_di_full <- read.csv(here::here("analysis", "reports", "submission2", "all_di_jk.csv"))
 
-all_ct_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"))
+all_ct_with_resamples <- read.csv(here::here("analysis", "reports", "submission2", "all_ct.csv"))
 
-jk_ct <- read.csv(here::here("analysis", "rev_prototyping", "all_ct_jk.csv"))
+jk_ct <- read.csv(here::here("analysis", "reports", "submission2", "all_ct_jk.csv"))
 

### 2021-04-14 analysis/reports/submission2/appendices/s8_gentry.Rmd
fixing paths

@@
 
-all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "reports", "submission2", "all_di.csv"), stringsAsFactors = F)
 
-all_ct <-  read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"), stringsAsFactors = F)
+all_ct <-  read.csv(here::here("analysis","reports", "submission2", "all_ct.csv"), stringsAsFactors = F)
 

### 2021-04-14 analysis/reports/submission2/manuscript_main_rev.Rmd
fixing paths

@@
 
-all_di_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))
-
-jk_di_full <- read.csv(here::here("analysis", "rev_prototyping", "all_di_jk.csv"))
-
-all_ct_with_resamples <- read.csv(here::here("analysis", "rev_prototyping", "all_ct.csv"))
-
-jk_ct <- read.csv(here::here("analysis", "rev_prototyping", "all_ct_jk.csv"))
+all_di_with_resamples <- read.csv(here::here("analysis", "reports", "submission2", "all_di.csv"))
+
+jk_di_full <- read.csv(here::here("analysis", "reports", "submission2", "all_di_jk.csv"))
+
+all_ct_with_resamples <- read.csv(here::here("analysis", "reports", "submission2", "all_ct.csv"))
+
+jk_ct <- read.csv(here::here("analysis", "reports", "submission2", "all_ct_jk.csv"))
 

### 2021-04-14 R/load_results_for_exploring.R

@@ -1,42 +1,0 @@
-library(dplyr)
-
-all_di <- read.csv(here::here("analysis", "reports", "submission2", "all_di.csv"), stringsAsFactors = F)
-
-all_ct <-  read.csv(here::here("analysis",  "reports", "submission2","all_ct.csv"), stringsAsFactors = F)
-
-
-all_ct <- all_ct %>%
-  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
-         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat))
-
-all_di <- all_di %>%
-  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)),
-         log_nsamples = log(nsamples),
-         log_s0 = log(s0),
-         log_n0 = log(n0)) %>%
-  filter(n0 != s0,
-         s0 != 1,
-         !singletons,
-         n0 != (s0 + 1)) %>%
-  mutate(dat = ifelse(grepl(dat, pattern = "fia"), "fia", dat),
-         dat = ifelse(dat == "misc_abund_short", "misc_abund", dat)) %>%
-  mutate(Dataset = dat,
-         Dataset = ifelse(Dataset == "fia", "FIA", Dataset),
-         Dataset = ifelse(Dataset == "bbs", "Breeding Bird Survey", Dataset),
-         Dataset = ifelse(Dataset == "mcdb", "Mammal Communities", Dataset),
-         Dataset = ifelse(Dataset == "gentry", "Gentry", Dataset),
-         Dataset = ifelse(Dataset == "misc_abund", "Misc. Abundance", Dataset)) %>%
-  filter(nparts > 20) %>%
-  left_join(all_ct)
-
-all_di <- all_di %>%
-  group_by_all() %>%
-  mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl),
-         skew_percentile_mean = mean(skew_percentile, skew_percentile_excl),
-         simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl),
-         shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl),
-         nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl),) %>%
-  ungroup()
-
-all_di <- all_di %>%
-  mutate(in_fia = ifelse(Dataset == "FIA", "FIA", "Other datasets"))

### 2021-04-14 analysis/reports/submission2/manuscript_main_rev.Rmd
maybe?

@@
 
-<!-- ```{r, fig.dim = c(4, 4)} -->
-<!-- ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) + -->
-<!--   geom_point(alpha = .3) + -->
-<!--   geom_point(data = filter(all_di, s0 < 0)) + -->
-<!--   geom_abline(slope = 1, intercept = 0) + -->
-<!--   scale_color_viridis_d(end = .8, direction = -1) + -->
-<!--   xlab("Mean of elements from feasible set") + -->
-<!--   ylab("Observed value") + -->
-<!--   ggtitle("Dissimilarity to the central tendency") +  theme(legend.position = "bottom")#, -->
-<!-- # -->
-<!-- # -->
-<!-- # ggplot(filter(all_di, nparts < 10 ^ 50), aes(nparts, sim_pos_from_best, color = Dataset)) + -->
-<!-- #   geom_point(alpha = .3) + -->
-<!-- #   geom_point(data = filter(all_di, s0 < 0)) + -->
-<!-- #   scale_color_viridis_d(end = .9) + -->
-<!-- #   xlab("Number of elements in the feasible set") + -->
-<!-- #   ylab("Mean dissimilarity of feasible set to central tendency") + -->
-<!-- #   scale_x_log10() + -->
-<!-- #   ggtitle("Over the size of the feasible set") -->
-<!-- # ), ncol = 1, -->
-<!-- #top = textGrob("Dissimilarity to central tendency")) -->
-
-<!-- ``` -->
-
 # Metric histograms by dataset (Figure 4)
@@
 }
-#
-# gridExtra::grid.arrange(grobs = list(
-#   plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity to central tendency"),
-#   plot_narrowness_legend(all_di)),
-#   ncol = 1)
+
 ```
@@
 ```
-
-<!-- ```{r, fig.dim = c(10,5)} -->
-
-<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
-
-<!--   plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"), -->
-<!--   plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"), -->
-<!--   plot_narrowness_hist(all_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
-<!--   plot_narrowness_hist(all_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"), -->
-<!--   plot_narrowness_hist(all_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset") -->
-<!-- ), ncol = 5, -->
-<!--  left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white")) -->
-
-<!-- ``` -->
-
-<!-- # Gentry -->
-
-<!-- ```{r} -->
-
-<!-- gentry_di <- filter(all_di, Dataset == "Gentry") -->
-
-<!-- gentry_di <- gentry_di %>% -->
-<!--   mutate(low_avg_abund = ifelse(n0/s0 < 3, "N:S < 3", "N:S > 3")) -->
-
-<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
-
-<!--   plot_percentile_hist(gentry_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "low_avg_abund"), -->
-<!--   plot_percentile_hist(gentry_di, "skew_percentile_mean", "\nSkewness", facetvar = "low_avg_abund", min_s0 = 3), -->
-<!--   plot_percentile_hist(gentry_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "low_avg_abund"), -->
-<!--   plot_percentile_hist(gentry_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "low_avg_abund") -->
-<!-- ), ncol = 2, -->
-<!--  left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
-<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
-
-<!-- ``` -->
-
-<!-- # Comparison of FIA and comparably sized communities (Figure 4) -->
-
-<!-- ```{r, fig.dim = c(10, 5)} -->
-
-<!-- fia_max_s = max(filter(all_di, dat == "fia")$s0) -->
-<!-- fia_max_n = max(filter(all_di, dat == "fia")$n0) -->
-
-<!-- fia = filter(all_di, dat == "fia") -->
-
-<!-- small_di <- all_di %>% -->
-<!--   filter(s0 <= fia_max_s, -->
-<!--          n0 <= fia_max_n) %>% -->
-<!--   mutate(fia_yn = ifelse(dat == "fia", "fia", "other datasets"), -->
-<!--          right_corner = FALSE) -->
-
-<!-- for(i in 1:nrow(small_di)) { -->
-<!--   if(small_di$dat[i] != "fia") { -->
-<!--     fia_match_s0 = filter(fia, s0 >= small_di$s0[i]) -->
-
-<!--     max_n0_for_this_s0 = max(fia_match_s0$n0) -->
-
-<!--     small_di$right_corner[i] = small_di$n0[i] > max_n0_for_this_s0 -->
-
-<!--   } -->
-<!-- } -->
-
-<!-- small_di <- small_di %>% -->
-<!--   filter(!right_corner) -->
-<!-- not_fia <- filter(small_di, fia_yn != "fia") -->
-<!-- fia = filter(small_di, dat == "fia") -->
-
-<!-- small_di_s_n <- small_di %>% -->
-<!--   select(s0, n0) %>% -->
-<!--   distinct() %>% -->
-<!--   mutate(in_fia = FALSE, -->
-<!--          in_not_fia = FALSE) -->
-
-<!-- for(i in 1:nrow(small_di_s_n)) { -->
-
-<!--   this_s0 = small_di_s_n$s0[i] -->
-<!--   this_n0 = small_di_s_n$n0[i] -->
-
-<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
-<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->
-
-<!--   small_di_s_n$in_fia[i] = nrow(fia_matches) > 0 -->
-<!--   small_di_s_n$in_not_fia[i] = nrow(not_fia_matches) > 0 -->
-
-<!-- } -->
-
-<!-- small_di_s_n <- filter(small_di_s_n, in_fia, in_not_fia) -->
-
-<!-- set.seed(1977) -->
-
-<!-- subsamples <- list() -->
-
-<!-- for(i in 1:nrow(small_di_s_n)) { -->
-
-<!--   this_s0 = small_di_s_n$s0[i] -->
-<!--   this_n0 = small_di_s_n$n0[i] -->
-
-<!--   fia_matches = filter(fia, s0 == this_s0, n0 == this_n0) -->
-
-<!--   not_fia_matches = filter(not_fia, s0 == this_s0, n0 == this_n0) -->
-
-<!--   n_to_draw = min(nrow(fia_matches), nrow(not_fia_matches)) -->
-
-<!--   fia_draw = sample.int(n = nrow(fia_matches), size = n_to_draw, replace = F) -->
-<!--   not_fia_draw = sample.int(n = nrow(not_fia_matches), size = n_to_draw, replace = F) -->
-
-<!--   subsamples[[i]] <- (bind_rows(fia_matches[fia_draw,], not_fia_matches[not_fia_draw, ])) -->
-
-<!-- } -->
-
-<!-- sub_di <- bind_rows(subsamples) %>% -->
-<!--   mutate(Dataset = ifelse(fia_yn == "fia", "FIA", "Other datasets")) -->
-
-<!-- fia_di <- filter(sub_di, fia_yn == "fia") -->
-<!-- other_di <- filter(sub_di, fia_yn != "fia") -->
-
-<!-- ks_compare <- function(fia_df, other_df, compare_var) { -->
-
-<!--   if(grepl("skew", compare_var)) { -->
-<!--     fia_df <- filter(fia_df, s0 > 2) -->
-<!--     other_df <- filter(fia_df, s0 >2) -->
-<!--   } -->
-
-<!--   if(grepl("sim_pos", compare_var)) { -->
-<!--     fia_df <- filter(fia_df, nparts > 20) -->
-<!--     other_df <- filter(other_df, nparts > 20) -->
-<!--   } else { -->
-<!--       fia_df <- filter(fia_df, nparts > 40) -->
-<!--     other_df <- filter(other_df, nparts > 40) -->
-<!--   } -->
-
-<!--   kstest <- ks.test(fia_df[[compare_var]], other_df[[compare_var]]) -->
-
-<!--   return(data.frame( -->
-<!--     var = compare_var, -->
-<!--     d = kstest$statistic, -->
-<!--     p = kstest$p.value -->
-<!--   )) -->
-<!-- } -->
-
-<!-- simpson_rat_ks <- ks_compare(fia_di, other_di, "simpson_95_ratio_2t") -->
-<!-- skew_rat_ks <- ks_compare(fia_di, other_di, "skew_95_ratio_2t") -->
-<!-- shannon_rat_ks <- ks_compare(fia_di, other_di, "shannon_95_ratio_2t") -->
-<!-- nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t") -->
-<!-- diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best") -->
-
-<!-- bind_rows(simpson_rat_ks, skew_rat_ks, shannon_rat_ks, nsingletons_rat_ks, diss_rat_ks) -->
-
-<!-- simpson_perc_ks <- ks_compare(fia_di, other_di, "simpson_percentile") -->
-<!-- skew_perc_ks <- ks_compare(fia_di, other_di, "skew_percentile_excl") -->
-<!-- shannon_perc_ks <- ks_compare(fia_di, other_di, "shannon_percentile") -->
-<!-- nsingletons_perc_ks <- ks_compare(fia_di, other_di, "nsingletons_percentile_excl") -->
-<!-- diss_perc_ks <- ks_compare(fia_di, other_di, "real_po_percentile_excl") -->
-
-<!-- bind_rows(simpson_perc_ks, skew_perc_ks, shannon_perc_ks, nsingletons_perc_ks, diss_perc_ks) -->
-
-<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
-
-<!--   plot_percentile_hist(sub_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1), -->
-<!--   plot_percentile_hist(sub_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"), -->
-<!--   plot_percentile_hist(sub_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
-<!--   plot_percentile_hist(sub_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"), -->
-<!--   plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset") -->
-<!-- ), ncol = 5, -->
-<!-- top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
-<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
-
-<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
-
-<!--   plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"), -->
-<!--   plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"), -->
-<!--   plot_narrowness_hist(sub_di, "skew_95_ratio_2t", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
-<!--   plot_narrowness_hist(sub_di, "simpson_95_ratio_2t", "\nSimpson evenness", facetvar = "Dataset"), -->
-<!--   plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset") -->
-<!-- ), ncol = 5, -->
-<!--  left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white")) -->
-
-<!-- diss_results <- sub_di %>% -->
-<!--   filter(nparts > 20) %>% -->
-<!--   group_by(Dataset) %>% -->
-<!--   summarize(high_diss = mean(real_po_percentile_excl > 95), -->
-<!--             nsites = dplyr::n()) %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>% -->
-<!--   select(-nsites) -->
-
-<!-- skew_results <- sub_di %>% -->
-<!--   filter(nparts > 40, s0 > 2) %>% -->
-<!--   group_by(Dataset) %>% -->
-<!--   summarize(high_skew = mean(skew_percentile_excl > 97.5), -->
-<!--             low_skew = mean(skew_percentile < 2.5), -->
-<!--             nsites = dplyr::n()) %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites), -->
-<!--          `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>% -->
-<!--   select(-nsites) -->
-
-<!-- metric_results <- sub_di %>% -->
-<!--   filter(nparts > 40) %>% -->
-<!--   group_by(Dataset) %>% -->
-<!--   summarize(high_simpson = mean(simpson_percentile_excl > 97.5), -->
-<!--             low_simpson = mean(simpson_percentile < 2.5), -->
-<!--             high_shannon = mean(shannon_percentile_excl > 97.5), -->
-<!--             low_shannon = mean(shannon_percentile < 2.5), -->
-<!--             high_nsingletons = mean(nsingletons_percentile_excl > 97.5), -->
-<!--             low_nsingletons = mean(nsingletons_percentile < 2.5), -->
-<!--             nsites = dplyr::n()) %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites), -->
-<!--          `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites), -->
-<!--          `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites), -->
-<!--          `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites), -->
-<!--          `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites), -->
-<!--          `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>% -->
-<!--   select(-nsites) -->
-
-<!-- all_results <- left_join(diss_results, skew_results) %>% -->
-<!--   left_join(metric_results) -->
-
-<!-- cols1 <- c("Dataset", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon") -->
-
-<!-- all_results %>% -->
-<!--   select(cols1) -->
-
-<!-- ``` -->
 
@@
 gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2, top = textGrob("Dissimilarity to the central tendency"))
-
-# 
-# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-# 
-# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-
-# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_95_ratio_2t", "Number of rare species") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-# 
-# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "nsingletons_percentile_mean", "Number of rare species") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-# 
-# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_95_ratio_2t", "Simpson") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-# 
-# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "simpson_percentile_mean", "Simpson") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-# 
-# 
-# plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_95_ratio_2t", "Shannon") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
-# 
-# plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "shannon_percentile_mean", "Shannon") +
-#   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3)
 ```
-
-<!-- ```{r, fig.dim = c(8,3)} -->
-<!-- ggplot(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), aes(s0, n0, color = `Number of elements`)) + -->
-<!--   geom_point(alpha = .1) + -->
-<!--   xlim(0, 30) + -->
-<!--   ylim(0,150) + -->
-<!--     facet_wrap(vars(Dataset), nrow = 1) -->
-<!-- ggplot(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund"), nparts > 2000, nparts < 1e+20), aes(nparts)) + -->
-<!--   geom_histogram() + -->
-<!--   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y") + -->
-<!--   scale_x_log10() -->
-
-<!-- ggplot(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund"), nparts < 2000), aes(nparts)) + -->
-<!--   geom_histogram() + -->
-<!--   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y") + -->
-<!--   scale_x_log10() -->
-
-<!-- ``` -->
-
-<!-- ```{r} -->
-
-<!-- all_di <- all_di %>% -->
-<!--   mutate( `Number of elements` = ifelse(nparts < 1000, "Less than 1000", "More than 1000")) -->
-<!-- diss_results <- all_di %>% -->
-<!--   filter(nparts > 20) %>% -->
-<!--   group_by(Dataset,  `Number of elements`) %>% -->
-<!--   summarize(high_diss = mean(real_po_percentile_excl > 95), -->
-<!--             nsites = dplyr::n()) %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(`High dissimilarity` = paste0(signif(100 * high_diss, 2), "%; n = ", nsites)) %>% -->
-<!--   select(-nsites) -->
-<!-- ggplot(filter(all_di, dat == "mcdb"), aes(skew_95_ratio_2t)) + -->
-<!--   geom_histogram() + -->
-<!--   facet_wrap(vars(`Number of elements`), scales = "free_y") -->
-
-<!-- skew_results <- all_di %>% -->
-<!--   filter(nparts > 40, s0 > 2) %>% -->
-<!--   group_by(Dataset,  `Number of elements`) %>% -->
-<!--   summarize(high_skew = mean(skew_percentile_excl > 97.5), -->
-<!--             low_skew = mean(skew_percentile < 2.5), -->
-<!--             nsites = dplyr::n()) %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(`High skew` = paste0(signif(100 * high_skew, 2), "%; n = ", nsites), -->
-<!--          `Low skew` = paste0(signif(100 * low_skew, 2), "%; n = ", nsites)) %>% -->
-<!--   select(-nsites) -->
-
-<!-- metric_results <- all_di %>% -->
-<!--   filter(nparts > 40) %>% -->
-<!--   group_by(Dataset, `Number of elements`) %>% -->
-<!--   summarize(high_simpson = mean(simpson_percentile_excl > 97.5), -->
-<!--             low_simpson = mean(simpson_percentile < 2.5), -->
-<!--             high_shannon = mean(shannon_percentile_excl > 97.5), -->
-<!--             low_shannon = mean(shannon_percentile < 2.5), -->
-<!--             high_nsingletons = mean(nsingletons_percentile_excl > 97.5), -->
-<!--             low_nsingletons = mean(nsingletons_percentile < 2.5), -->
-<!--             nsites = dplyr::n()) %>% -->
-<!--   ungroup() %>% -->
-<!--   mutate(`High Simpson` = paste0(signif(100 * high_simpson, 2), "%; n = ", nsites), -->
-<!--          `Low Simpson` = paste0(signif(100 * low_simpson, 2), "%; n = ", nsites), -->
-<!--          `High Shannon` = paste0(signif(100 * high_shannon, 2), "%; n = ", nsites), -->
-<!--          `Low Shannon` = paste0(signif(100 * low_shannon, 2), "%; n = ", nsites), -->
-<!--          `High proportion of rare species` = paste0(signif(100 * high_nsingletons, 2), "%; n = ", nsites), -->
-<!--          `Low proportion of rare species` = paste0(signif(100 * low_nsingletons, 2), "%; n = ", nsites)) %>% -->
-<!--   select(-nsites) -->
-
-<!-- all_results <- left_join(diss_results, skew_results) %>% -->
-<!--   left_join(metric_results) -->
-
-<!-- cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon") -->
-
-<!-- all_results %>% -->
-<!--   select(cols1) -->
-
-<!-- ``` -->
 

### 2021-04-14 analysis/reports/submission2/table1_extreme_values.Rmd
maybe?

@@
 ---
-title: "Proportions of extreme values the unusual direction"
+title: "Proportions of extreme values the usual direction"
 author: Renata Diaz
@@
 output: 
-    # github_document:
-    #    df_print: kable
-    #    toc: true
+    github_document:
+       df_print: kable
+       toc: true
     word_document:

### 2021-04-17 analysis/howto.Rmd
stop using gh actions, rerender main figs

@@
 To run a subset locally, you can run `mcdb_pipeline_demo.R`.
-This will run the pipeline on the first 100 communities in the Mammal Community Database.
-It takes [time] on a MacBook Air with 8GB memory and creates a [size] cache file.
+This will run the pipeline on the first 50 communities in the Mammal Community Database, drawing up to 200 samples from each feasible set.
+It takes about 20 minutes on a MacBook Air with 8GB memory and creates a 51 MB cache file.
 

### 2021-04-17 analysis/reports/submission2/table1_extreme_values.Rmd
stop using gh actions, rerender main figs

@@
        toc: true
-    word_document:
-        df_print: kable
-        toc: false
+    # word_document:
+    #     df_print: kable
+    #     toc: false
 ---

### 2021-04-17 analysis/reports/submission2/appendices/s4_dissimilarity_fig.Rmd
manuscript dir updated

@@
 ---
-title: "Dissimilarity of FS vs. actual"
-author: Renata Diaz
+title: "Figure S4"
+#author: Renata Diaz
 date: "`r Sys.Date()`"
@@
         toc: false
+        reference_docx: style_reference.docx
 ---
@@
 **Figure S4**.
+Dissimilarity of observed and sampled SADs to the central tendency of the feasible set.
 Observed SADs are often much more dissimilar to the central tendency of their feasible sets (y-axis) than the mean dissimilarity of samples from the feasible set and the central tendency (x-axis).

### 2021-04-17 analysis/reports/submission2/appendices/s6_breadth_index_fig.Rmd
manuscript dir updated

@@
 ---
-title: "Distribution of dissimilarity and breadth indices within each dataset"
-author: Renata Diaz
+title: "Figure S6"
+#author: Renata Diaz
 date: "`r Sys.Date()`"

### 2021-04-17 analysis/reports/submission2/appendices/s7_complete_resampling_results.Rmd
manuscript dir updated

@@
 ---
-title: "Complete results of resampling"
-author: Renata Diaz
+title: "Appendix A7: Complete results of resampling"
+#author: Renata Diaz
 date: "`r Sys.Date()`"
@@
 
-# Resampling
-
 ```{r}
@@
 
-# Percentile histograms
+## Percentile histograms
 
-## Subsampling
+### Subsampling
 
-```{r, fig.dim = c(10,5)}
+```{r, fig.dim = c(8,8)}
 
@@
   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
+), ncol = 3,
 top = textGrob("Subsampling results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
@@
 
-## Adjusting for rare species
+### Adjusting for rare species
 
-```{r, fig.dim = c(10,5)}
+```{r, fig.dim = c(8,8)}
 
@@
   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
+), ncol =3,
 top = textGrob("Adjusted for rare species results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
@@
 
-# Summary of effects on proportion of extreme values
+## Summary of effects on proportion of extreme values
 
-## Usual direction
+### Usual direction
 
-```{r}
+```{r, fig.dim = c(8,6)}
 gridExtra::grid.arrange(grobs = list(
@@
 
-## Unusual direction
+### Unusual direction
 
-```{r}
+```{r, fig.dim = c(8,6)}
 gridExtra::grid.arrange(grobs = list(
@@
 
-# Table of proportions of extreme values
+## Table of proportions of extreme values
 
-## Usual direction
+### Usual direction
 
@@
 
-## Unusual direction
+### Unusual direction
 

### 2021-04-17 analysis/reports/submission2/appendices/s9_fia_comparison.Rmd
manuscript dir updated

@@
 title: "Comparison of FIA and equally-sized communities"
-author: Renata Diaz
+#author: Renata Diaz
 date: "`r Sys.Date()`"
 output: 
-    github_document:
+    # github_document:
+    #    df_print: kable
+    #    toc: true
+   word_document:
         df_print: kable
-       toc: true
-    # word_document:
-    #     df_print: kable
-    #     toc: false
+        toc: false
+        reference_docx: style_reference.docx
 ---

### 2021-04-17 analysis/reports/submission2/table1_extreme_values.Rmd
manuscript dir updated

--- 2021-04-14 analysis/reports/submission2/table1_extreme_values.Rmd
@@
 ---
-title: "Proportions of extreme values the usual direction"
-author: Renata Diaz
+title: "Table 1"
+#author: Renata Diaz
 date: "`r Sys.Date()`"
 output: 
-    github_document:
-       df_print: kable
-       toc: true
+    # github_document:
+    #    df_print: kable
+    #    toc: true
     word_document:
@@
 n refers to the number of communities included for each dataset for each metric.
+The proportions shown are for the directions of effects observed for most datasets; for the opposite-direction effects, see Table S5.

### 2021-04-19 analysis/reports/submission1/accessory/compare_zenodo_data.Rmd

---
title: "Check that files from Zenodo match files from GitHub"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
library(dplyr)
library(ggplot2)

```

Download from Zenodo (https://zenodo.org/record/166725)

```{r}

zip_download_dest  <- "~/Documents/sad-comparison.zip"

download.file("https://zenodo.org/record/166725/files/weecology/sad-comparison-peerj.2.zip?download=1",zip_download_dest , quiet = TRUE, mode = "wb")
unzip("~/Documents/sad-comparison.zip", exdir = "~/Documents/sad-comparison")
file.remove(zip_download_dest)

```

Load data files from Zenodo downloads

```{r}

zenodo_dir <- list.dirs("~/Documents/sad-comparison/", full.names = T)

zenodo_dir <- zenodo_dir[ which(grepl("sad-data", zenodo_dir))]
```

BBS:

```{r}
bbs_zenodo <- read.csv(file.path(zenodo_dir, "bbs_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

bbs_github <- read.csv(here::here("working-data", "abund_data", "bbs_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

any(!(bbs_github == bbs_zenodo))

```

FIA:

```{r}
fia_zenodo <- read.csv(file.path(zenodo_dir, "fia_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

fia_github <- read.csv(here::here("working-data", "abund_data", "fia_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

any(!(fia_github == fia_zenodo))

```

Gentry:

```{r}
gentry_zenodo <- read.csv(file.path(zenodo_dir, "gentry_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

gentry_github <- read.csv(here::here("working-data", "abund_data", "gentry_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

any(!(gentry_github == gentry_zenodo), na.rm = T)

any(!(which(is.na(gentry_github)) == which(is.na(gentry_zenodo))))

```
MCDB:

```{r}
mcdb_zenodo <- read.csv(file.path(zenodo_dir, "mcdb_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

mcdb_github <- read.csv(here::here("working-data", "abund_data", "mcdb_spab.csv"), stringsAsFactors = F, header = F, skip = 2)

any(!(mcdb_github == mcdb_zenodo))

```

All the data files downloaded from GitHub exactly match their counterparts on Zenodo. (This is not surprising but good to check).

The analyses for this manuscript were done using the files downloaded from GitHub. RMD doesn't think it's necessary (or really appropriate) to re-write `download_data` to download from Zenodo instead. This report demonstrates that the analyses should be replicable using the data files from Zenodo, should that be the only/the preferred option in the future.

### 2021-04-19 analysis/reports/submission1/accessory/misc_abund_mixes.Rmd

---
title: "Filtering datasets"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(drake)
library(dplyr)
library(ggplot2)
library(scadsanalysis)

theme_set(theme_bw())

knitr::opts_chunk$set(fig.width=3, fig.height=2.5, warning = FALSE, message = FALSE) 
```

While preparing the filtering report, RMD noticed that some communities in Misc. Abund have a **mixture** of relative abundance and count data. This is a report to record that rabbit hole. It turned out not to be problematic.

Here we can also identify which of the Misc Abund communities have the *mixture* of relative and count data.

```{r}

misc_abund_raw <- read.csv(here::here("working-data", "abund_data", "misc_abund_spab.csv"))

misc_abund_raw <- misc_abund_raw %>%
  dplyr::rename(site = Site_ID,
                abund = Abundance)

misc_abund_raw <- misc_abund_raw %>%
  mutate(site = as.character(site),
         dat = "misc_abund",
         singletons = F,
         sim = -99,
         source = "observed") %>%
  filter(abund > 0) %>%
  group_by(site) %>%
  arrange(abund) %>%
  mutate(rank = row_number()) %>%
  ungroup()

misc_abund_statevars <- get_statevars(misc_abund_raw)

misc_abund_sv_filtered <- misc_abund_statevars %>%
  filter(n0 <= 40720)

misc_abund_filtered <- filter(misc_abund_raw, site %in% misc_abund_sv_filtered$site)

misc_abund <- read.csv(here::here("working-data", "abund_data", "misc_abund_spab.csv"))

misc_abund <- misc_abund %>%
  dplyr::rename(site = Site_ID,
                abund = Abundance)

miscabund_issues <- misc_abund %>%
  group_by(site) %>%
  summarize(
    nspecies = dplyr::n(),
    nas.in.count = sum(is.na(abund)),
    n.nonzero.species = sum(abund > 0, na.rm = T)
  )

filter(miscabund_issues, nas.in.count > 0, n.nonzero.species > 0)

```

There are 6 sites for Misc Abund that have **both** NA's recorded for counted abundance **and** any non-0, non-NA records for counted abundance. So that is, they have **some** actual count data (not 100% relative abundance), but they also have NA's for the counts.

For four of these - 144, 145, 146, and 147 - this appears to be because reptiles are recorded in counts and arachnids are recorded as relative abundances. Therefore, for these sites, the SAD we end up working with is just the one for reptiles. For example:

```{r}
filter(misc_abund, site == 145)
filter(misc_abund_filtered, site == "145")
```

Given that this appears to reflect different conventions for very different **taxa** (and not a mix of data currencies for what we would in other contexts consider the same community), RMD is comfortable leaving these 4 sites in.

For 178 and 446, there are individual species (one at each site) with "NA" and not 0 for abundance. RMD is leaving these in; it should have no impact on the final results.

```{r}

filter(misc_abund, site == 178, is.na(abund))

filter(misc_abund, site == 446, is.na(abund))

```

### 2021-04-19 analysis/reports/submission1/accessory/old_reports/figs2.Rmd

--- 2020-08-04 analysis/reports/figs2.Rmd
@@
 small %>%
-  filter(s0 > 2, nparts > 500) %>%
+  filter(s0 > 2, nparts > 50) %>%
   group_by(is_fia) %>%
@@
 small %>%
-    filter(s0 > 2, nparts > 500) %>%
+    filter(s0 > 2, nparts > 50) %>%
   group_by(is_fia) %>%

### 2021-04-19 analysis/reports/submission1/appendix1_filtering.Rmd

--- 2020-12-19 analysis/reports/appendix1_filtering.Rmd
@@
 These raw files are stored in `working-data\abund_data` and are not edited.
+
+The datasets downloaded from GitHub exactly match the corresponding data files in the Zenodo archive for Baldridge (2016), available here: (https://zenodo.org/record/166725).
+If in the future it is preferred or necessary to use the archival versions, they can be downloaded and stored in `working-data\abund_data` and the rest of the analysis should run just as if they had been downloaded from GitHub.
 
@@
 
-head(all_di)
+#head(all_di)
 

### 2021-04-19 analysis/reports/submission2/appendices/s10_very_small_results.Rmd

@@
 ---
-title: "Complete results for very small (<2000 possible SADs) communities"
-author: Renata Diaz
+title: "Appendix A10: Complete results for very small communities"
+# author: Renata Diaz
 date: "`r Sys.Date()`"
 output: 
-    github_document:
-       df_print: kable
-       toc: true
+    # github_document:
+    #    df_print: kable
+    #    toc: true
     word_document:
@@
         toc: false
+        reference_docx: style_reference.docx
 ---
+
+We compare the results for very small communities (fewer than 2000 possible SADs in the feasible set) to larger communities within each dataset.
 
@@
 
-# Proportions of extreme values
+Only three of our datasets - Mammal Communities, Misc.
+Abundance, and FIA - have appreciable numbers of very small communities.
+We use 2000 possible SADs as a cutoff because it splits these datasets into reasonably large subsets of both "large" and "small" communities.
+
+Proportions of communities in these datasets with fewer than 2000 possible SADs:
 
@@
 cols1 <- c("Dataset", "Number of elements", "High dissimilarity", "High proportion of rare species", "High skew", "Low Simpson", "Low Shannon")
+
+cols2 <- c("Dataset", "Number of elements", "Low proportion of rare species", "Low skew", "High Simpson", "High Shannon")
 all_di %>%
@@
   group_by(Dataset) %>%
-  summarize(`Proportion with nparts < 2000` = mean(nparts < 2000))
+  summarize(`Proportion with < 2000 possible SADs` = mean(nparts < 2000))
+```
 
+## Proportions of communities with extreme percentile scores
+
+The proportions of communities with >/< 2000 possible SADs with extreme percentile scores for each dataset.
+
+For dissimilarity, approximately 5% of communities would have extreme scores by chance. For all other metrics, this would be approximately 2.5%.
+
+In the direction of effects usually seen:
+
+```{r}
 all_results %>%
@@
 
-# Distributions of breadth indices and percentile scores
+In the opposite direction:
+
+```{r}
+all_results %>%
+  filter(Dataset %in% c("FIA", "Mammal Communities", "Misc. Abundance")) %>%
+  select(cols2)
+```
+
+## Plots of breadth indices and percentile scores
 

### 2021-04-19 analysis/reports/submission2/manuscript_main_rev.Rmd

@@
 
-```{r, fig.dim = c(7,5)}
+```{r f1, fig.dim = c(7,5)}
 
-s4_fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
+fig1 <- ggplot(all_di, aes(x = s0, y = n0, color = Dataset)) +
    geom_point(data = filter(all_di, dat == "fia"), alpha = .1) +
@@
 
-plot(s4_fig1)
+fig1_with_top = gridExtra::grid.arrange(grobs = list(fig1), 
+top = textGrob("Figure 1"))
+
+# 
+# pdf("figure_1.pdf", bg = "white", paper = "letter", width = 6.5, height = 6.5)
+# gridExtra::grid.arrange(grobs = list(fig1), 
+# top = textGrob("Figure 1"))
+# dev.off()
+
+ggsave("figure_1.pdf", plot = fig1_with_top, device = "pdf", width = 6.5, height = 6.5, units = "in")
+
 ```
 
-<!-- # Illustrations of 95% interval (Figure 2) -->
+# Illustrations of 95% interval (Figure 2)
 
-<!-- To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md. -->
+To show the 95% interval, we need to load the distribution of shape metric values from the samples from the feasible set for a few communities. See rov_metric.md.
 
-<!-- ```{r, fig.dim = c(7,7)} -->
-<!-- library(drake) -->
+```{r f2, fig.dim = c(7,7)}
+library(drake)
 
-<!-- db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite")) -->
-<!-- cache <- storr::storr_dbi("datatable", "keystable", db) -->
-<!-- cache$del(key = "lock", namespace = "session") -->
+db <- DBI::dbConnect(RSQLite::SQLite(), here::here("analysis", "drake", "drake-cache-net.sqlite"))
+cache <- storr::storr_dbi("datatable", "keystable", db)
+cache$del(key = "lock", namespace = "session")
 
-<!-- net_summary <- readd(all_di_summary, cache = cache) -->
+net_summary <- readd(all_di_summary, cache = cache)
 
-<!-- net_summary <- net_summary %>% -->
-<!--   mutate(log_nparts = log(gmp:::as.double.bigz(nparts))) -->
+net_summary <- net_summary %>%
+  mutate(log_nparts = log(gmp:::as.double.bigz(nparts)))
 
-<!-- example_fs <- readd(fs_s_44_n_13360, cache = cache) -->
+example_fs <- readd(fs_s_44_n_13360, cache = cache)
 
-<!-- example_di <- readd(di_fs_s_44_n_13360, cache =cache) -->
+example_di <- readd(di_fs_s_44_n_13360, cache =cache)
 
-<!-- example_fs <- example_fs %>% -->
-<!--   left_join(example_di) %>% -->
-<!--   left_join(net_summary) -->
+example_fs <- example_fs %>%
+  left_join(example_di) %>%
+  left_join(net_summary)
 
-<!-- example_fs2 <- readd(fs_s_13_n_315, cache = cache) -->
+example_fs2 <- readd(fs_s_13_n_315, cache = cache)
 
-<!-- example_di2 <- readd(di_fs_s_13_n_315, cache =cache) -->
+example_di2 <- readd(di_fs_s_13_n_315, cache =cache)
 
-<!-- example_fs2 <- example_fs2 %>% -->
-<!--   left_join(example_di2) %>% -->
-<!--   left_join(net_summary) -->
+example_fs2 <- example_fs2 %>%
+  left_join(example_di2) %>%
+  left_join(net_summary)
 
-<!-- example_fs3 <- readd(fs_s_4_n_34, cache = cache) -->
+example_fs3 <- readd(fs_s_4_n_34, cache = cache)
 
-<!-- example_di3 <- readd(di_fs_s_4_n_34, cache =cache) -->
+example_di3 <- readd(di_fs_s_4_n_34, cache =cache)
 
-<!-- example_fs3 <- example_fs3 %>% -->
-<!--   left_join(example_di3) %>% -->
-<!--   left_join(net_summary) -->
+example_fs3 <- example_fs3 %>%
+  left_join(example_di3) %>%
+  left_join(net_summary)
 
-<!-- breadth_plots <- list( -->
+breadth_plots <- list(
 
-<!--   ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .25) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
+  ggplot(example_fs3, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .25) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle("Small community", subtitle = paste0("S = ", (example_fs3$s0), "; N = ", (example_fs3$n0[1]))) +
+    theme(legend.position = "right") +
+    xlab("Rank") +
+    ylab("Abundance"),
 
-<!--   ggplot(example_fs3, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle = paste0("Breadth index: ", round((example_fs3$skew_95_ratio_2t[1]), 2))) + -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
+  ggplot(example_fs3, aes(skew)) +
+  #  geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs3$skew_97p5[1], example_fs3$skew_2p5[1]), color = "red") +
+    ggtitle("", subtitle = paste0("Breadth index: ", round((example_fs3$skew_95_ratio_2t[1]), 2))) +
+    xlab("Skewness") +
+    ylab("Count"),
 
-<!--   ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) + -->
-<!--     theme(legend.position = "right")+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance") + -->
-<!--     ylim(0, 200), # Remove 3 sads that make the axes too big to be interpretable -->
+  ggplot(example_fs2, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .1) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle("Medium community", subtitle = paste0("S = ", (example_fs2$s0), "; N = ", (example_fs2$n0[1]))) +
+    theme(legend.position = "right")+
+    xlab("Rank") +
+    ylab("Abundance") +
+    ylim(0, 200), # Remove 3 sads that make the axes too big to be interpretable
 
-<!--   ggplot(example_fs2, aes(skew)) + -->
-<!--   #  geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs2$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count"), -->
+  ggplot(example_fs2, aes(skew)) +
+  #  geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs2$skew_97p5[1], example_fs2$skew_2p5[1]), color = "red") +
+    ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs2$skew_95_ratio_1t[1]), 2)))+
+    xlab("Skewness") +
+    ylab("Count"),
 
-<!--   ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) + -->
-<!--     geom_line(alpha = .1) + -->
-<!--     theme_bw() + -->
-<!--     scale_color_viridis_c(option = "plasma", end = .8) + -->
-<!--     ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) + -->
-<!--     theme(legend.position = "right") + -->
-<!--     ylim(0, 4000) + # Remove a very few very very uneven SADs that make the scale too big to be interpretable -->
-<!--     theme(axis.text.y = element_text(size = 6, angle = 60))+ -->
-<!--     xlab("Rank") + -->
-<!--     ylab("Abundance"), -->
+  ggplot(example_fs, aes(rank, abund, group = sim, color = skew)) +
+    geom_line(alpha = .1) +
+    theme_bw() +
+    scale_color_viridis_c(option = "plasma", end = .8) +
+    ggtitle("Large community", subtitle = paste0("S = ", (example_fs$s0), "; N = ", (example_fs$n0[1]))) +
+    theme(legend.position = "right") +
+    ylim(0, 4000) + # Remove a very few very very uneven SADs that make the scale too big to be interpretable
+    theme(axis.text.y = element_text(size = 6, angle = 60))+
+    xlab("Rank") +
+    ylab("Abundance"),
 
-<!--   ggplot(example_fs, aes(skew)) + -->
-<!--    # geom_density() + -->
-<!--     geom_histogram(bins = 50) + -->
-<!--     theme_bw() + -->
-<!--     geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") + -->
-<!--     ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs$skew_95_ratio_1t[1]), 2)))+ -->
-<!--     xlab("Skewness") + -->
-<!--     ylab("Count") -->
+  ggplot(example_fs, aes(skew)) +
+   # geom_density() +
+    geom_histogram(bins = 50) +
+    theme_bw() +
+    geom_vline(xintercept = c(example_fs$skew_97p5[1], example_fs$skew_2p5[1]), color = "red") +
+    ggtitle("", subtitle =  paste0("Breadth index: ", round((example_fs$skew_95_ratio_1t[1]), 2)))+
+    xlab("Skewness") +
+    ylab("Count")
 
-<!-- ) -->
+)
 
-<!-- fig_1 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 2", gp = gpar(fill = "white"))) -->
+fig_2 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 2", gp = gpar(fill = "white")))
 
-<!-- plot(fig_1) -->
+ggsave("figure_2.pdf", plot = fig_2, device = "pdf", width = 8, height = 8, units = "in")
 
-<!-- signif(as.numeric(example_di$nparts), digits = 2) -->
-<!-- (as.numeric(example_di2$nparts)) -->
-<!-- as.numeric(example_di3$nparts) -->
+signif(as.numeric(example_di$nparts), digits = 2)
+(as.numeric(example_di2$nparts))
+as.numeric(example_di3$nparts)
 
-<!-- DBI::dbDisconnect(db) -->
-<!-- rm(cache) -->
-<!-- rm(db) -->
-<!-- ``` -->
+DBI::dbDisconnect(db)
+rm(cache)
+rm(db)
+```
 
@@
 
-# Metric histograms by dataset (Figure 4)
+# Metric histograms by dataset (Figure 3)
 
-```{r, fig.dim = c(10,5)}
+```{r f3, fig.dim = c(11,5)}
 
-fig_2 <- gridExtra::grid.arrange(grobs = list(
+fig_3 <- gridExtra::grid.arrange(grobs = list(
 
   plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"),
+  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nProportion of rare species", facetvar = "Dataset"),
   plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
@@
   plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
+), ncol = 3,
 top = textGrob("Figure 3", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
 bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
+
+# 
+# 
+# pdf("figure_3.pdf", bg = "white", paper = "letter", width = 8, height = 4)
+# gridExtra::grid.arrange(grobs = list(fig_3), 
+# top = textGrob("Figure 3"))
+# dev.off()
+
+fig_3
+
+ggsave("figure_3.pdf", plot = fig_3, device = "pdf", width = 8, height = 8, units = "in")
+
 ```
@@
 
-```{r}
+```{r t1}
 diss_results <- all_di %>%
@@
 
-```{r, fig.dim = c(7,4)}
+```{r f4, fig.dim = c(7,4)}
 
-gridExtra::grid.arrange(grobs = list(
+fig_4 <- gridExtra::grid.arrange(grobs = list(
   plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")),
@@
     plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
-    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species"),
+    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nProportion of rare species"),
        plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
-  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"))
+  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"), top = textGrob("Figure 4"))
 
+fig_4
+# 
+# pdf("figure_4.pdf", bg = "white", paper = "letter", width = 8, height = 5)
+# fig_4
+# dev.set(dev.next())
+# while (!is.null(dev.list()))  dev.off()
+
+ggsave("figure_4.pdf", plot = fig_4, device = "pdf", width = 8, height = 5, units = "in")
 ```
@@
 
-```{r, fig.dim = c(6,8)}
+```{r f6, fig.dim = c(6,8)}
 
@@
 
-nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity to the central tendency") +
+nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
-  xlab("Mean dissimilarity of elements of feasible set to central tendency") +
+  xlab("Breadth index") +
   ylab("Number of communities") +
-  ggtitle("")
+  ggtitle("Skewness")
 
-phist <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "real_po_percentile_mean", "Dissimilarity to the central tendency") +
+phist <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness") +
   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
@@
   ylab("Number of communities") +
-  ggtitle("")
+  ggtitle("Skewness")
 
-gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2, top = textGrob("Dissimilarity to the central tendency"))
+fig_6 <- gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2, top = textGrob("Figure 6"))
+
+fig_6
+
+ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 6, height = 8, units = "in")
+
 ```
@@
 ```
-```{r, fig.dim = c(6,4)}
+```{r f5, fig.dim = c(6,4)}
 rs_results_long <- rs_results %>%
@@
 
-gridExtra::grid.arrange(grobs = list(
+fig_5 <- gridExtra::grid.arrange(grobs = list(
   ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
@@
   xlab("") + ylim(0, .7) +
-  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
+  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"), top = textGrob("Figure 5"))
 
-gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-  geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
-  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
-  ylab("Proportion of extreme observed values") +ylim(0, .7) +
-  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
-  ggplot(filter(rs_results_long, grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-  geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
-  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
-  ylab("") +
-  xlab("") + ylim(0, .7) +
-  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
+#fig_5
+
+ggsave("figure_5.pdf", device = "pdf", plot = fig_5, width = 6, height = 5, units = "in")
+# 
+# pdf("figure_5.pdf", bg = "white", paper = "letter", width = 6, height = 5)
+# fig_5
+# dev.set(dev.next())
+# while (!is.null(dev.list()))  dev.off()
+#
+
+# 
+# gridExtra::grid.arrange(grobs = list(
+#   ggplot(filter(rs_results_long, !grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+#   geom_point() +
+#   facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+#   scale_color_viridis_d(end = .8) +
+#   ylab("Proportion of extreme observed values") +ylim(0, .7) +
+#   xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
+#   ggplot(filter(rs_results_long, grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+#   geom_point() +
+#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
+#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+#   scale_color_viridis_d(end = .8) +
+#   ylab("") +
+#   xlab("") + ylim(0, .7) +
+#   theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
 
 ```
-
-<!-- ```{r, fig.dim = c(10,5)} -->
-
-<!-- all_di_with_resamples <- all_di_with_resamples %>% -->
-<!--   group_by_all() %>% -->
-<!--   mutate(real_po_percentile_mean = mean(real_po_percentile, real_po_percentile_excl, na.rm = T), -->
-<!--          skew_percentile_mean = mean(skew_percentile, skew_percentile_excl, na.rm = T), -->
-<!--          simpson_percentile_mean = mean(simpson_percentile,simpson_percentile_excl, na.rm = T), -->
-<!--          shannon_percentile_mean = mean(shannon_percentile, shannon_percentile_excl, na.rm = T), -->
-<!--          nsingletons_percentile_mean = mean(nsingletons_percentile, nsingletons_percentile_excl)) %>% -->
-<!--   ungroup() -->
-
-<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
-
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Subsampling"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset") -->
-<!-- ), ncol = 5, -->
-<!-- top = textGrob("Subsampling results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
-<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
-
-<!-- fig_2 <- gridExtra::grid.arrange(grobs = list( -->
-
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "nsingletons_percentile_mean", "\nNumber of rare species", facetvar = "Dataset"), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"), -->
-<!--   plot_percentile_hist(filter(all_di_with_resamples, resampling == "Rare species"), "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset") -->
-<!-- ), ncol = 5, -->
-<!-- top = textGrob("Adjusted for rare species results", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), -->
-<!-- bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white")) -->
-<!-- ``` -->

### 2021-04-19 analysis/rev_prototyping/old/prop_off_prelim_results.Rmd

--- 2021-02-17 analysis/rev_prototyping/prop_off_prelim_results.Rmd
@@
 
-ggplot(filter(all_di, n_po_comparisons > 20), aes(mean_po_comparison_percentile)) +
+ggplot(filter(all_di), aes(mean_po_comparison_percentile)) +
   geom_histogram() +
-  facet_wrap(vars(singletons), scales = "free_y")
+  facet_wrap(vars(dat, singletons), scales = "free_y")
 
-ggplot(filter(all_di, n_po_comparisons > 20), aes(n_po_comparisons)) +
-  geom_histogram()
-
-all_di %>% group_by(singletons) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))
+all_di %>% group_by(singletons, dat) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))
 
@@
 ```
+
+```{r}
+
+ggplot(all_di, aes(mean_po_comparison_sims, mean_po_comparison, color = mean_po_comparison_percentile > 95)) +
+  geom_point(alpha = .3) +
+  facet_wrap(vars(dat, singletons))
+
+ggplot(all_di, aes(mean_po_comparison - mean_po_comparison_sims, color = mean_po_comparison_percentile > 95)) +
+  geom_histogram(alpha = .3) +
+  facet_wrap(vars(dat, singletons))
+
+```

### 2021-04-19 analysis/rev_prototyping/old/rarefaction.Rmd

--- 2021-02-24 analysis/rev_prototyping/rarefaction.Rmd
@@
 knitr::opts_chunk$set(fig.width=4, fig.height=3, warning = FALSE, message = FALSE)
+
+theme_set(theme_bw())
 
@@
 
+overall_results_long <- overall_results %>%
+  tidyr::pivot_longer(-dat, names_to = "varname", values_to = "proportion") %>%
+  group_by_all() %>%
+  mutate(direction = unlist(strsplit(varname, "_"))[[1]],
+         metric = unlist(strsplit(varname, "_"))[[2]],
+         adjusted = unlist(strsplit(varname, "_"))[[3]]) %>%
+  ungroup() %>%
+  mutate(dir_metric = paste(direction, metric, sep= "_"))
+
 # overall_simpson_results <- adjusted_comparison %>%
@@
 # overall_results <- left_join(overall_skew_results, overall_simpson_results)
-
-overall_results
 
@@
   facet_wrap(vars(dat)) 
+```
+
+```{r, fig.dim = c(8,8)}
+
+overall_results
+ggplot(overall_results_long, aes(adjusted, proportion, color = adjusted)) +
+  geom_point() +
+  facet_grid(cols = vars(dir_metric), rows = vars(dat), scales = "free", switch = "y") +
+  theme(legend.position = "top")
 

### 2021-05-08 analysis/reports/finaledit/appendices/s10_very_small_results.Rmd
UGH i hate figures

--- 2021-04-19 analysis/reports/submission2/appendices/s10_very_small_results.Rmd
@@
 
-nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity to the central tendency") +
+nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best_95", "Dissimilarity to the central tendency") +
   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
-  xlab("Mean dissimilarity of elements of feasible set to central tendency") +
+  xlab("95th percentile of scores for dissimilarity to the central tendency \nfor elements of the feasible set") +
   ylab("Number of communities") +

### 2021-05-08 analysis/reports/finaledit/appendices/s5_results_unusual_direction.Rmd
UGH i hate figures

--- 2021-04-14 analysis/reports/submission2/appendices/s5_results_weird_direction.Rmd
@@
 title: "Proportions of extreme values the unusual direction"
-author: Renata Diaz
+#author: Renata Diaz
 date: "`r Sys.Date()`"
@@
 
-**Table ST5.** Proportions of extreme values for percentile scores for observed SADs compared to samples from the feasible set, for the less-usual direction of effects.
+**Table S5.** Proportions of extreme values for percentile scores for observed SADs compared to samples from the feasible set, for the less-usual direction of effects.
 This is the proportion of scores <2.5 or >97.5; by chance ~2.5% of scores should be in either extreme.

### 2021-05-08 analysis/reports/finaledit/appendices/s6_breadth_index_fig.Rmd
UGH i hate figures

--- 2021-04-17 analysis/reports/submission2/appendices/s6_breadth_index_fig.Rmd
@@
 
-  plot_narrowness_hist(all_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
+  plot_narrowness_hist(all_di, "sim_pos_from_best_95", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
   plot_narrowness_hist(all_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
@@
 **Figure S6**.
-Partially because of the uneven distribution of S and N among the different datasets, the narrowness of the feasible sets - defined either as the mean dissimilarity of samples from the feasible set to the central tendency of the feasible set, or using a breadth index for specific metrics - varies among different datasets.
+Partially because of the uneven distribution of S and N among the different datasets, the narrowness of the feasible sets - defined either as the 95th percentile of scores for the dissimilarity of samples from the feasible set to the central tendency of the feasible set, or using a breadth index for specific metrics - varies among different datasets.
 In particular, the FIA dataset, and subsets of the Mammal Community and Miscellaneous Abundance databases, often have highly variable, broadly-defined statistical baselines derived from the feasible set.

### 2021-05-08 analysis/reports/finaledit/manuscript_main_rev.Rmd
UGH i hate figures

--- 2021-04-19 analysis/reports/submission2/manuscript_main_rev.Rmd
@@
   scale_x_log10() +
-  scale_y_log10()
+  scale_y_log10()  +
+  theme(legend.position = c(.3,.8), legend.justification = "center", legend.background = element_blank(), legend.text	= element_text(size = 8), legend.title = element_text(size = 9), legend.key.size = unit(2, units = "mm"), axis.text = element_text(size = 7))
 
-fig1_with_top = gridExtra::grid.arrange(grobs = list(fig1), 
-top = textGrob("Figure 1"))
-
-# 
-# pdf("figure_1.pdf", bg = "white", paper = "letter", width = 6.5, height = 6.5)
-# gridExtra::grid.arrange(grobs = list(fig1), 
-# top = textGrob("Figure 1"))
-# dev.off()
-
-ggsave("figure_1.pdf", plot = fig1_with_top, device = "pdf", width = 6.5, height = 6.5, units = "in")
+ggsave("figure_1.pdf", plot = fig1, device = "pdf", width = 80, height = 80, units = "mm")
 
@@
 
-fig_2 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2, top = textGrob("Figure 2", gp = gpar(fill = "white")))
+fig_2 <- gridExtra::grid.arrange(grobs = breadth_plots, ncol = 2)
 
-ggsave("figure_2.pdf", plot = fig_2, device = "pdf", width = 8, height = 8, units = "in")
-
-signif(as.numeric(example_di$nparts), digits = 2)
-(as.numeric(example_di2$nparts))
-as.numeric(example_di3$nparts)
+ggsave("figure_2.pdf", plot = fig_2, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")
+# 
+signif(as.numeric(example_di$nparts), digits = 2)[1]
+(as.numeric(example_di2$nparts))[1]
+as.numeric(example_di3$nparts)[1]
 
@@
   ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
-    geom_histogram(bins = 40, boundary = 100) +
+    geom_histogram(bins = 100, boundary = 100) +
     theme_bw() +
@@
     ggtitle( plot_name) +
+    #geom_text(data = distinct(select(di_df, Dataset)), aes(x = 45, y = 100, label = Dataset)) +
     facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
-    theme(plot.title = element_text(size=10))
+    theme(plot.title = element_text(size=9), plot.margin=unit(c(1, 0, -5, -3), units = "mm"), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
+    scale_y_continuous(n.breaks = 3)
 
@@
 
-  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset", tails = 1),
-  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "\nProportion of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "skew_percentile_mean", "\nSkewness", facetvar = "Dataset", min_s0 = 3),
-  plot_percentile_hist(all_di, "simpson_percentile_mean", "\nSimpson evenness", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
+  plot_percentile_hist(all_di, "real_po_percentile_mean", "Dissimilarity", facetvar = "Dataset", tails = 1),
+  plot_percentile_hist(all_di, "nsingletons_percentile_mean", "Proportion of rare species", facetvar = "Dataset"),
+  plot_percentile_hist(all_di, "skew_percentile_mean", "Skewness", facetvar = "Dataset", min_s0 = 3) + theme(plot.margin = unit(c(1, 2, -5, -5), units = "mm")),
+  plot_percentile_hist(all_di, "simpson_percentile_mean", "Simpson evenness", facetvar = "Dataset"),
+  plot_percentile_hist(all_di, "shannon_percentile_mean", "Shannon diversity", facetvar = "Dataset")
 ), ncol = 3, 
-top = textGrob("Figure 3", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
-bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
-
-# 
-# 
-# pdf("figure_3.pdf", bg = "white", paper = "letter", width = 8, height = 4)
-# gridExtra::grid.arrange(grobs = list(fig_3), 
-# top = textGrob("Figure 3"))
-# dev.off()
+left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+bottom = textGrob("Percentile rank of observed value relative to feasible set"), 
+gp = gpar(fill = "white"))
 
@@
 
-ggsave("figure_3.pdf", plot = fig_3, device = "pdf", width = 8, height = 8, units = "in")
+ggsave("figure_3.pdf", plot = fig_3, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")
 
@@
     theme(legend.position = "none")+
-    theme(plot.title = element_text(size=10))
+    theme(plot.title = element_text(size=10)) +
+    theme(legend.text = element_text(size = 7), plot.margin = unit(c(0, 10, 0, 0), units = "mm"), axis.text = element_text(size = 7))
 }
@@
   ggplot(legend_df, aes(1, ymark, color = Dataset)) +
-    geom_label(aes(x = 2, y = ymark, label = Dataset)) +
+    geom_text(aes(x = 2, y = ymark, label = Dataset)) +
     geom_point(size = 4) +
@@
 
+# 
+# fig_4 <- gridExtra::grid.arrange(grobs = list(
+#   plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity \nto central tendency") + ylab("Dissimilarity \n95th percentile") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = 40, r = 0, t = 10, l = 0, unit = "mm")),
+#   gridExtra::grid.arrange(grobs = list(
+#     plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
+#     plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
+#     plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nProportion of rare species"),
+#        plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
+#   ), ncol = 2)), ncol = 2, widths = c( 2, 4),bottom = textGrob("Number of elements in the feasible set"))
+
 fig_4 <- gridExtra::grid.arrange(grobs = list(
-  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")),
-  gridExtra::grid.arrange(grobs = list(
-    plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
-    plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
-    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nProportion of rare species"),
-       plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
-  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"), top = textGrob("Figure 4"))
+  plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity") + ylab("Dissimilarity \n95th percentile") + theme(legend.position = c(.65, .8), legend.justification = "center", legend.direction = "horizontal", legend.background = element_blank(), legend.key = element_blank(), legend.key.size = unit(.25, units = "mm"), legend.title = element_text(size =7)),
+    plot_narrowness(all_di, "skew_95_ratio_2t", "Skewness") + ylab("\nBreadth index"),
+    plot_narrowness(all_di, "simpson_95_ratio_2t", "Simpson evenness")+ ylab("\nBreadth index"),
+    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "Proportion of rare species")+ ylab("\nBreadth index"),
+       plot_narrowness(all_di, "shannon_95_ratio_2t", "Shannon diversity")+ ylab("\nBreadth index")), ncol = 1, bottom = textGrob("Number of elements in the feasible set"))
 
-fig_4
+#fig_4
 # 
@@
 
-ggsave("figure_4.pdf", plot = fig_4, device = "pdf", width = 8, height = 5, units = "in")
+ggsave("figure_4.pdf", plot = fig_4, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")
 ```
@@
   ylab("Number of communities") +
-  ggtitle("Skewness")
+  ggtitle("Skewness") + theme(plot.margin = unit(c(5,5,5,5), units = "mm"))
 
@@
   ylab("Number of communities") +
-  ggtitle("Skewness")
+  ggtitle("Skewness")+ theme(plot.margin = unit(c(5,5,5,5), units = "mm"))
 
-fig_6 <- gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2, top = textGrob("Figure 6"))
+fig_6 <- gridExtra::grid.arrange(grobs = list(nhist, phist), nrow = 2)
 
@@
 
-ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 6, height = 8, units = "in")
+ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")
 
@@
 #   xlab("")
+# 
+# fig_5 <- gridExtra::grid.arrange(grobs = list(
+#   ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+#   geom_point() +
+#   facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+#   scale_color_viridis_d(end = .8, option = "plasma") +
+#   ylab("Proportion of extreme observed values") +ylim(0, .7) +
+#   xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
+#   ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+#   geom_point() +
+#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
+#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
+#   scale_color_viridis_d(end = .8, option = "plasma") +
+#   ylab("") +
+#   xlab("") + ylim(0, .7) +
+#   theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"), top = textGrob("Figure 5"))
 
 fig_5 <- gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
   geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol =5) +
   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
+  scale_color_viridis_d(end = .8, option = "plasma") +
   ylab("Proportion of extreme observed values") +ylim(0, .7) +
-  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
-  ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-  geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
-  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
-  ylab("") +
-  xlab("") + ylim(0, .7) +
-  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"), top = textGrob("Figure 5"))
+  xlab("Metric") + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(60, 0, 0, 0), units = "mm"))))
 
-#fig_5
-
-ggsave("figure_5.pdf", device = "pdf", plot = fig_5, width = 6, height = 5, units = "in")
+ggsave("figure_5.pdf", device = "pdf", plot = fig_5, width = 180, height =
+180, dpi = 800, units = "mm")
 # 

### 2021-05-08 analysis/reports/submission2/appendices/graphical_abstract.Rmd
fixed f4

---
title: "Graphical abstract"
#author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true
   # word_document:
   #      df_print: kable
   #      toc: false
   #      reference_docx: style_reference.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(drake)
library(dplyr)
library(ggplot2)
library(grid)
theme_set(theme_bw())
library(scadsanalysis)

```

```{r}
# 
# mcdb <- load_dataset("mcdb")
# 
# set.seed(1977)
# p <- filter(mcdb, site == 1944)
# 
# p_samples <- sample_fs_wrapper(p, site_name = 1944, F, 200)
# 
# p_di <- add_dis(p_samples)
# 
# write.csv(p_di, "portal_di.csv")
# write.csv(p_samples, "portal_samples.csv")
portal_samples <- read.csv("portal_samples.csv") %>%
  select(-X)
portal_di <- read.csv("portal_di.csv") %>%
  select(-X)
```

```{r, fig.dim = c(2,2)}

portal_samples <- left_join(portal_samples, portal_di)

portal_samples <- portal_samples %>%
  mutate(`Simpson's evenness` = simpson)

ga <- ggplot(filter(portal_samples, source == "sampled"), aes(rank, abund, group = sim, color = `Simpson's evenness`)) +
  geom_line(alpha = .1) +
  geom_line(data = filter(portal_samples, source == "observed"), size = 1.) +   scale_color_viridis_c(option = "plasma", end = .8, direction = -1) +
  theme(legend.justification = c(0,1.65), legend.position = c(0.01,1)) +
  ggtitle("Observed SAD v. statistical baseline") +
  ylab("Abundance") +
  xlab("Rank") +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(size = 8),  panel.grid = element_blank(),
        axis.title = element_text(size =7), plot.title.position = "plot",
        legend.text	= element_blank(), legend.title = element_blank(), legend.direction = "horizontal", legend.key.height = unit(1, units = "mm"), legend.background = element_blank()) +
  geom_text(data = NULL, aes(x = 1.8, y = 210, label = "Evenness"), inherit.aes = F, color = "black", alpha = .01, size = 2.5, hjust = 0)  +
  geom_text(data = NULL, aes(x = 1.8, y = 175, label = "low"), inherit.aes = F, color = "black", alpha = .01, size = 2.5, hjust = 0) +
  geom_text(data = NULL, aes(x = 9, y = 175, label = "high"), inherit.aes = F, color = "black", alpha = .01, size = 2.5, hjust = 0)

ga
ggsave("graphical_abstract.pdf", plot = ga, device = "pdf", width = 50, height = 50, units = "mm")

```

While the classic "hollow curve" form of the SAD emerges from randomly dividing individuals between species, observed SADs are consistently much more uneven than the majority of forms that emerge at random. These deviations between observations and the statistical baseline may reflect biological processes shaping the SAD, and provide new leverage for using the SAD to evaluate and refine ecological theory.

### 2021-05-08 analysis/reports/submission2/appendices/s4_dissimilarity_fig.Rmd
fixed f4

@@
   scale_color_viridis_d(end = .8, direction = -1) +
-  xlab("Mean of elements from feasible set") +
+  xlab("Mean for elements from feasible set") +
   ylab("Observed value") +

### 2021-05-08 analysis/reports/submission2/appendices/s8_gentry.Rmd
fixed f4

@@
 
-```{r, fig.dim = c(7,7)}
+```{r, fig.dim = c(4,4)}
 
@@
   geom_point(data = all_di, inherit.aes = F, aes(s0, n0), color = "grey", alpha = .1) +  geom_point() +
-scale_x_log10() + scale_y_log10() + xlab("Species richness (S); note log scale") + ylab("Total abundance (N); note log scale") + ggtitle("Gentry communities", subtitle = "(in color)")
+scale_x_log10() + scale_y_log10() + xlab("Species richness (S); note log scale") + ylab("Total abundance (N); note log scale") + ggtitle("Gentry communities", subtitle = "(in color)") + theme(legend.position = "bottom")
 
@@
 
-These low-average-abundance communities account for most of the signal of extreme values in the unusual direction for various metrics - that is, a **low** number of rare species and **low** skewness, and **high** Shannon and Simpson evenness.
+This figure shows all of the communities across all our datasets in terms of S and N. Gentry communities are in color, color coded by whether they have low average abundance (N/S < 3).
+
+These low-average-abundance communities - the red dots in the plot above - account for most of the signal of extreme values in the unusual direction for various metrics - that is, a **low** number of rare species and **low** skewness, and **high** Shannon and Simpson evenness.
 Gentry communities with average abundance > 3 tend to show the signal in the same direction as most other communities.

### 2021-05-08 analysis/reports/submission2/appendices/s9_fia_comparison.Rmd
fixed f4

@@
 
-  plot_narrowness_hist(sub_di, "sim_pos_from_best", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
+  plot_narrowness_hist(sub_di, "sim_pos_from_best_95", "Dissimilarity to the \ncentral tendency", facetvar = "Dataset"),
   plot_narrowness_hist(sub_di, "nsingletons_95_ratio_2t", "\nNumber of rare species", facetvar = "Dataset"),
@@
 nsingletons_rat_ks <- ks_compare(fia_di, other_di, "nsingletons_95_ratio_2t")
-diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best")
+diss_rat_ks <- ks_compare(fia_di, other_di, "sim_pos_from_best_95")
 

### 2021-05-08 analysis/reports/submission2/manuscript_main_rev.Rmd
fixed f4

@@
   filter(nparts > 20) %>%
-  left_join(all_ct)
+  left_join(all_ct) %>%
+  mutate(Dataset_short = ifelse(Dataset == "FIA", "FIA", 
+                                ifelse(Dataset == "Breeding Bird Survey", "BBS", 
+                                       ifelse(Dataset == "Mammal Communities", "Mammals", ifelse(Dataset == "Gentry", "Gentry", "Misc.")))))
 
@@
 
-plot_narrowness <- function(di_df, yvar, yvar_name) {
+plot_narrowness <- function(di_df, yvar, yvar_name, use_short = T) {
 
@@
 
+  if(use_short) {
+    di_df <- di_df %>%
+      mutate(Dataset = Dataset_short)
+  }
+
   ggplot(di_df, aes(nparts, response, color = Dataset)) +
@@
     theme(legend.position = "none")+
-    theme(plot.title = element_text(size=10))
-}
-
-plot_narrowness_legend <- function(di_df) {
-
-  legend_df <- di_df %>%
-    select(Dataset) %>%
-    distinct() %>%
-    mutate(ymark = dplyr::row_number())
-
-  ggplot(legend_df, aes(1, ymark, color = Dataset)) +
-    geom_label(aes(x = 2, y = ymark, label = Dataset)) +
-    geom_point(size = 4) +
-    scale_color_viridis_d(end = .9) +
-    xlab("") +
-    ylab("") +
-    theme(legend.position = "none") +
-    xlim(1, 3) + theme(
-      panel.grid.major.x = element_blank(),
-      panel.grid.minor.x = element_blank(),
-      panel.grid.major.y = element_blank(),
-      panel.grid.minor.y = element_blank(),
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank()
-    ) +
-    ggtitle("Dataset")
-
+    theme(plot.title = element_text(size=10)) +
+    theme(legend.text = element_text(size = 8), plot.margin = unit(c(0, 10, 0, 0), units = "mm"), axis.text = element_text(size = 7))
 }
@@
 
+# 
+# fig_4 <- gridExtra::grid.arrange(grobs = list(
+#   plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity \nto central tendency") + ylab("Dissimilarity \n95th percentile") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = 40, r = 0, t = 10, l = 0, unit = "mm")),
+#   gridExtra::grid.arrange(grobs = list(
+#     plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
+#     plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
+#     plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nProportion of rare species"),
+#        plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
+#   ), ncol = 2)), ncol = 2, widths = c( 2, 4),bottom = textGrob("Number of elements in the feasible set"))
+
 fig_4 <- gridExtra::grid.arrange(grobs = list(
-  plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity \nto central tendency") + ylab("Mean dissimilarity") + theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .25, r = 0, t = 0, l = 0, unit = "in")),
-  gridExtra::grid.arrange(grobs = list(
-    plot_narrowness(all_di, "skew_95_ratio_2t", "\nSkewness"),
-    plot_narrowness(all_di, "simpson_95_ratio_2t", "\nSimpson evenness")+ ylab(""),
-    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "\nProportion of rare species"),
-       plot_narrowness(all_di, "shannon_95_ratio_2t", "\nShannon diversity") + ylab("")
-  ), ncol = 2)), ncol = 2, widths = c( 2, 4), bottom = textGrob("Number of elements in the feasible set"), top = textGrob("Figure 4"))
+  plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity") + ylab("Dissimilarity \n95th percentile"),
+    plot_narrowness(all_di, "skew_95_ratio_2t", "Skewness") + ylab("\nBreadth index"),
+    plot_narrowness(all_di, "simpson_95_ratio_2t", "Simpson evenness")+ ylab("\nBreadth index"),
+    plot_narrowness(all_di, "nsingletons_95_ratio_2t", "Proportion of rare species")+ ylab("\nBreadth index"),
+       plot_narrowness(all_di, "shannon_95_ratio_2t", "Shannon diversity")+ ylab("\nBreadth index")+ theme(legend.position = "bottom", legend.direction = "horizontal", legend.key = element_blank(), legend.margin = margin(-.3,0,0,0, unit = "in"),legend.key.size = unit(.25, units = "mm"), legend.title = element_text(size = 8))), ncol = 1, bottom = textGrob("Number of elements in the feasible set"))
 
-fig_4
+#fig_4
 # 
@@
 
-ggsave("figure_4.pdf", plot = fig_4, device = "pdf", width = 8, height = 5, units = "in")
+ggsave("figure_4.pdf", plot = fig_4, device = "pdf", width = 80, height = 180, dpi = 800, units = "mm")
 ```

### 2021-05-08 analysis/reports/submission2/manuscript_main_rev.Rmd
I think I want to revert fig 6, idk

@@
 
-ggsave("figure_2.pdf", plot = fig_2, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")
+ggsave("figure_2.pdf", plot = fig_2, device = "pdf", width = 180, height = 120, dpi = 800, units = "mm")
 # 
@@
 ```{r f6, fig.dim = c(6,8)}
+plot_percentile_hist_small <- function(di_df, col_name, plot_name, tails = 2, facetvar = "Dataset", min_s0 = 0) {
 
+  if(tails == 2) {
+    cutoff_percentiles = c(2.5, 97.5)
+    min_nparts = 40
+  } else if (tails== 1) {
+    cutoff_percentiles = c(95)
+    min_nparts = 20
+  }
+
+  di_df <- di_df %>%
+    mutate(response = (di_df[[col_name]]),
+           facetvar = di_df[[facetvar]])
+
+  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
+    geom_histogram(bins = 40, boundary = 100) +
+    theme_bw() +
+    xlab("") +
+    ylab("") +
+    geom_vline(xintercept = cutoff_percentiles, color = "red") +
+    ggtitle( plot_name) +
+    #geom_text(data = distinct(select(di_df, Dataset)), aes(x = 45, y = 100, label = Dataset)) +
+    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
+    theme(plot.title = element_text(size=9), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
+    scale_y_continuous(n.breaks = 3)
+
+}
 all_di <- all_di %>%
@@
 
-nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
+nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb")), "skew_95_ratio_2t", "Skewness") +
+  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
   xlab("Breadth index") +
   ylab("Number of communities") +
-  ggtitle("Skewness") + theme(plot.margin = unit(c(5,5,5,5), units = "mm"))
+  ggtitle("Skewness") + theme(plot.margin = unit(c(0,5,0,2), units = "mm"), axis.text = element_text(size = 6) ,strip.text = element_text(size = 7), strip.placement = "inside")
 
-phist <- plot_percentile_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness") +
-  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
-  xlab("Percentile rank of observed value relative to feasible set") +
+phist <- plot_percentile_hist_small(filter(all_di, dat %in% c("fia", "mcdb")), "skew_percentile_mean", "Skewness")  +
+  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
+  xlab("Percentile rank of observed value \nrelative to feasible set") +
   ylab("Number of communities") +
-  ggtitle("Skewness")+ theme(plot.margin = unit(c(5,5,5,5), units = "mm"))
+  ggtitle("Skewness")+ theme(plot.margin = unit(c(0,5,5,2), units = "mm"), plot.title = element_text(size = 10))
 
@@
 
-ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 180, height = 180, dpi = 800, units = "mm")
+ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 80, height = 150, dpi = 800, units = "mm")
 

### 2021-05-09 analysis/reports/submission2/appendices/s10_very_small_results.Rmd
this looks good to me

@@
   if(grepl("sim_pos", col_name)) {
-    xvarname = "Mean dissimilarity"
+xvarname = "95th percentile \nof dissimilarity scores"
 min_nparts = 40
@@
 
-```{r, fig.dim = c(6,8)}
+```{r, fig.dim = c(5,6)}
 
@@
 
-```{r, fig.dim = c(6,8)}
+```{r, fig.dim = c(5,6)}
 
-nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best", "Dissimilarity to the central tendency") +
+nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "sim_pos_from_best_95", "Dissimilarity to the central tendency") +
   facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
-  xlab("Mean dissimilarity of elements of feasible set to central tendency") +
+  xlab("95th percentile of scores for dissimilarity to the central tendency \nfor elements of the feasible set") +
   ylab("Number of communities") +

### 2021-05-09 analysis/reports/submission2/appendices/s4_dissimilarity_fig.Rmd
this looks good to me

--- 2021-04-17 analysis/reports/submission2/appendices/s4_dissimilarity_fig.Rmd
@@
 
-```{r, fig.dim = c(7,7)}
-ggplot(all_di, aes(sim_pos_from_best, real_po, color = `Observed \npercentile score`)) +
-  geom_point(alpha = .3) +
+```{r, fig.dim = c(7,5)}
+ggplot(all_di, aes(sim_pos_from_best, real_po)) +
+  geom_point(alpha = .05) +
   geom_point(data = filter(all_di, s0 < 0)) +
@@
   scale_color_viridis_d(end = .8, direction = -1) +
-  xlab("Mean of elements from feasible set") +
+  xlab("95th percentile for elements from feasible set") +
   ylab("Observed value") +
@@
 #top = textGrob("Dissimilarity to central tendency"))
-
+increase <- all_di %>% filter(real_po_percentile_excl > 95) %>% mutate(difference = real_po - sim_pos_from_best_95, ratio = real_po / sim_pos_from_best_95)
 ```
@@
 Dissimilarity of observed and sampled SADs to the central tendency of the feasible set.
-Observed SADs are often much more dissimilar to the central tendency of their feasible sets (y-axis) than the mean dissimilarity of samples from the feasible set and the central tendency (x-axis).
+Observed SADs are often much more dissimilar to the central tendency of their feasible sets (y-axis) than the 95th percentile dissimilarity of samples from the feasible set and the central tendency (x-axis).
 Dissimilarity can range from 0-1.
 The black line is the 1:1 line.
-Of observed SADs that are more disssimilar to the central tendency than are 95% of samples from the feasible set (green points), the absolute increase in dissimlarity ranges from .04 to .6.
-These observed SADs are from 1.4 to 9.7 times more dissimilar to the central tendency than the maen of samples from the feasible set.
+Of observed SADs that are more disssimilar to the central tendency than are 95% of samples from the feasible set, the absolute increase in dissimlarity ranges from ```r round(min(increase$difference), 4)``` to ```r round(max(increase$difference), 3)```.
+These observed SADs are from ```r round(min(increase$ratio), 3)``` to ```r round(max(increase$ratio), 2)``` times more dissimilar to the central tendency than the 95th percentile of dissimilarity scores for samples from the feasible set.

### 2021-05-09 analysis/reports/submission2/appendices/s6_breadth_index_fig.Rmd
this looks good to me

@@
   if(grepl("sim_pos", col_name)) {
-    xvarname = "Mean dissimilarity"
+    xvarname = "95th percentile \nof dissimilarity scores"
     min_nparts = 40
@@
     min_nparts = 20
-    xvarname = "Breadth index"
+    xvarname = "Breadth index \n"
   }
@@
 
-```{r, fig.dim = c(10,5)}
+```{r, fig.dim = c(10,5.5)}
 
@@
 **Figure S6**.
-Partially because of the uneven distribution of S and N among the different datasets, the narrowness of the feasible sets - defined either as the mean dissimilarity of samples from the feasible set to the central tendency of the feasible set, or using a breadth index for specific metrics - varies among different datasets.
+Partially because of the uneven distribution of S and N among the different datasets, the narrowness of the feasible sets - defined either as the 95th percentile of scores for the dissimilarity of samples from the feasible set compared to the central tendency of the feasible set, or using a breadth index for specific metrics - varies among different datasets.
 In particular, the FIA dataset, and subsets of the Mammal Community and Miscellaneous Abundance databases, often have highly variable, broadly-defined statistical baselines derived from the feasible set.

### 2021-05-09 analysis/reports/submission2/appendices/s7_complete_resampling_results.Rmd
this looks good to me

@@
   filter(nparts > 20) %>%
-  left_join(all_ct)
+  left_join(all_ct)  %>%
+  mutate(Dataset_short = ifelse(Dataset == "FIA", "FIA", 
+                                ifelse(Dataset == "Breeding Bird Survey", "BBS", 
+                                       ifelse(Dataset == "Mammal Communities", "Mammals", ifelse(Dataset == "Gentry", "Gentry", "Misc.")))))
 
@@
     facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
-    theme(plot.title = element_text(size=10))
+    theme(plot.title = element_text(size=9), plot.margin=unit(c(1, 0, -5, -1), units = "mm"), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
+    scale_y_continuous(n.breaks = 3)
 
@@
     theme(legend.position = "none")+
-    theme(plot.title = element_text(size=10))
+    theme(plot.title = element_text(size=10)) +
+    scale_y_continuous(nbreaks =3)
 }
-
-plot_narrowness_legend <- function(di_df) {
-
-  legend_df <- di_df %>%
-    select(Dataset) %>%
-    distinct() %>%
-    mutate(ymark = dplyr::row_number())
-
-  ggplot(legend_df, aes(1, ymark, color = Dataset)) +
-    geom_label(aes(x = 2, y = ymark, label = Dataset)) +
-    geom_point(size = 4) +
-    scale_color_viridis_d(end = .9) +
-    xlab("") +
-    ylab("") +
-    theme(legend.position = "none") +
-    xlim(1, 3) + theme(
-      panel.grid.major.x = element_blank(),
-      panel.grid.minor.x = element_blank(),
-      panel.grid.major.y = element_blank(),
-      panel.grid.minor.y = element_blank(),
-      axis.text.x = element_blank(),
-      axis.ticks.x = element_blank(),
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank()
-    ) +
-    ggtitle("Dataset")
-
-}
-#
-# gridExtra::grid.arrange(grobs = list(
-#   plot_narrowness(all_di, "sim_pos_from_best", "Dissimilarity to central tendency"),
-#   plot_narrowness_legend(all_di)),
-#   ncol = 1)
-```
-
-```{r}
-
-plot_narrowness_hist <- function(di_df, col_name, plot_name, facetvar = "Dataset", min_s0 = 0) {
-
-  if(grepl("sim_pos", col_name)) {
-    xvarname = "Mean dissimilarity"
-    min_nparts = 40
-  } else {
-    min_nparts = 20
-    xvarname = "Breadth index"
-  }
-
-  di_df <- di_df %>%
-    mutate(response = (di_df[[col_name]]),
-           facetvar = di_df[[facetvar]])
-
-  ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
-    geom_histogram(bins = 40, boundary = 100) +
-    theme_bw() +
-    ylab("") +
-    xlab(xvarname) +
-    ggtitle( plot_name) +
-    facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
-    theme(plot.title = element_text(size=10))
-
-}
-
 ```
@@
 
-```{r, fig.dim = c(8,6)}
+```{r, fig.dim = c(8,4)}
 gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
   geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol =5) +
   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
-  ylab("Proportion of extreme observed values") +ylim(0, .7) +
-  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
-  ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-  geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
-  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
-  ylab("") +
-  xlab("") + ylim(0, .7) +
-  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
+  scale_color_viridis_d(end = .8, option = "plasma") +
+  ylab("Proportion of extreme \nobserved values") + xlab("") +ylim(0, .7) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(5, 5, 2, 2), units = "mm"))))
+
 ```
@@
 
-```{r, fig.dim = c(8,6)}
+```{r, fig.dim = c(8,4)}
 gridExtra::grid.arrange(grobs = list(
-  ggplot(filter(rs_results_long, !grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
+  ggplot(filter(rs_results_long, weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
   geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
+  facet_wrap(vars(Dataset), scales = "fixed", ncol =5) +
   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
-  ylab("Proportion of extreme observed values") +ylim(0, .7) +
-  xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
-  ggplot(filter(rs_results_long, grepl("Misc", Dataset), weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-  geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
-  geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-  scale_color_viridis_d(end = .8) +
-  ylab("") +
-  xlab("") + ylim(0, .7) +
-  theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"))
+  scale_color_viridis_d(end = .8, option = "plasma") +
+  ylab("Proportion of extreme \nobserved values") + xlab("") +ylim(0, .7) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(5, 5, 2, 2), units = "mm"))))
 

### 2021-05-09 analysis/reports/submission2/manuscript_main_rev.Rmd
this looks good to me

@@
   ggplot(filter(di_df, nparts > min_nparts, s0 >= min_s0), aes(response)) +
-    geom_histogram(bins = 100, boundary = 100) +
+    geom_histogram(bins = 40, boundary = 100) +
     theme_bw() +
@@
     ggtitle( plot_name) +
-    #geom_text(data = distinct(select(di_df, Dataset)), aes(x = 45, y = 100, label = Dataset)) +
     facet_wrap(vars(facetvar), ncol = 1, scales = "free_y")+
-    theme(plot.title = element_text(size=9), plot.margin=unit(c(1, 0, -5, -3), units = "mm"), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
+    theme(plot.title = element_text(size=9), plot.margin=unit(c(1, 0, -5, -1), units = "mm"), axis.text = element_text(size = 6), strip.text = element_text(size = 7), strip.placement = "inside") +
     scale_y_continuous(n.breaks = 3)
@@
   plot_percentile_hist(all_di, "nsingletons_percentile_mean", "Proportion of rare species", facetvar = "Dataset"),
-  plot_percentile_hist(all_di, "skew_percentile_mean", "Skewness", facetvar = "Dataset", min_s0 = 3) + theme(plot.margin = unit(c(1, 2, -5, -5), units = "mm")),
+  plot_percentile_hist(all_di, "skew_percentile_mean", "Skewness", facetvar = "Dataset", min_s0 = 3) + theme(plot.margin =unit(c(1, 3, -5, -1), units = "mm")),
   plot_percentile_hist(all_di, "simpson_percentile_mean", "Simpson evenness", facetvar = "Dataset"),
@@
     theme(plot.title = element_text(size=10)) +
-    theme(legend.text = element_text(size = 8), plot.margin = unit(c(0, 10, 0, 0), units = "mm"), axis.text = element_text(size = 7))
+    theme(legend.text = element_text(size = 8), plot.margin = unit(c(0, 10, 0, 2), units = "mm"), axis.text = element_text(size = 7))
 }
@@
 fig_4 <- gridExtra::grid.arrange(grobs = list(
-  plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity") + ylab("Dissimilarity \n95th percentile"),
+  plot_narrowness(all_di, "sim_pos_from_best_95", "Dissimilarity") + ylab("Dissimilarity \n95th percentile") + theme(plot.margin =unit(c(1, 10, 0, 2), units = "mm") ),
     plot_narrowness(all_di, "skew_95_ratio_2t", "Skewness") + ylab("\nBreadth index"),
@@
 all_di <- all_di %>%
-  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000", "More than 2000"))
+  mutate( `Number of elements` = ifelse(nparts < 2000, "Less than 2000 possible SADs", "More than 2000 possible SADs"))
 diss_results <- all_di %>%
@@
 
-nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb")), "skew_95_ratio_2t", "Skewness") +
-  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
+nhist <- plot_narrowness_hist(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_95_ratio_2t", "Skewness") +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
   xlab("Breadth index") +
@@
 
-phist <- plot_percentile_hist_small(filter(all_di, dat %in% c("fia", "mcdb")), "skew_percentile_mean", "Skewness")  +
-  facet_wrap(vars(`Number of elements`, Dataset_short), scales = "free_y", nrow = 2, ncol = 2) +
+phist <- plot_percentile_hist_small(filter(all_di, dat %in% c("fia", "mcdb", "misc_abund")), "skew_percentile_mean", "Skewness")  +
+  facet_wrap(vars(`Number of elements`, Dataset), scales = "free_y", nrow = 2, ncol = 3) +
   xlab("Percentile rank of observed value \nrelative to feasible set") +
@@
 
-ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 80, height = 150, dpi = 800, units = "mm")
+ggsave("figure_6.pdf", plot = fig_6, device = "pdf", width = 180, height = 150, dpi = 800, units = "mm")
 
@@
 
-rs_results_long <- left_join(rs_results_long, metric_names)
-#
-# ggplot(filter(rs_results_long, !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-#   geom_point() +
-#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 1) +
-#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-#   scale_color_viridis_d(end = .8) +
-#   ylab("Proportion of extreme observed values") +
-#   xlab("")
-# 
-# fig_5 <- gridExtra::grid.arrange(grobs = list(
-#   ggplot(filter(rs_results_long, !grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-#   geom_point() +
-#   facet_wrap(vars(Dataset), scales = "fixed", ncol =2) +
-#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-#   scale_color_viridis_d(end = .8, option = "plasma") +
-#   ylab("Proportion of extreme observed values") +ylim(0, .7) +
-#   xlab("") + theme(legend.position = "none", axis.text.x = element_text(angle = 90)) ,
-#   ggplot(filter(rs_results_long, grepl("Misc", Dataset), !weird_dir), aes(metric_desc, value, color = `Resampling scheme`)) +
-#   geom_point() +
-#   facet_wrap(vars(Dataset), scales = "fixed", ncol = 2) +
-#   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
-#   scale_color_viridis_d(end = .8, option = "plasma") +
-#   ylab("") +
-#   xlab("") + ylim(0, .7) +
-#   theme(legend.position = "bottom", legend.direction = "vertical" , legend.margin = margin(b = .3, r = 0, t = 0, l = 0, unit = "in"), axis.text.x = element_text(angle = 90))), ncol = 2, widths = c( 4,2), bottom = textGrob("Metric"), top = textGrob("Figure 5"))
+rs_results_long <- left_join(rs_results_long, metric_names) %>%
+  mutate(Dataset_short = ifelse(Dataset == "FIA", "FIA", 
+                                ifelse(Dataset == "Breeding Bird Survey", "BBS", 
+                                       ifelse(Dataset == "Mammal Communities", "Mammals", ifelse(Dataset == "Gentry", "Gentry", "Misc.")))))
 
@@
   geom_point() +
-  facet_wrap(vars(Dataset), scales = "fixed", ncol =5) +
+  facet_wrap(vars(Dataset_short), scales = "fixed", ncol =5) +
   geom_point(aes(y = percentile_cutoff), shape = 95, color = "black", size = 10) +
   scale_color_viridis_d(end = .8, option = "plasma") +
-  ylab("Proportion of extreme observed values") +ylim(0, .7) +
-  xlab("Metric") + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(60, 0, 0, 0), units = "mm"))))
+  ylab("Proportion of extreme \nobserved values") + xlab("") +ylim(0, .7) + theme(legend.position = "bottom", axis.text.x = element_text(angle = 90), plot.margin = unit(c(5, 5, 2, 2), units = "mm"))))
 
 ggsave("figure_5.pdf", device = "pdf", plot = fig_5, width = 180, height =
-180, dpi = 800, units = "mm")
+80, dpi = 800, units = "mm")
 # 

### 2021-05-09 analysis/reports/submission2/appendices/appendix1_filtering.Rmd

--- 2021-04-19 analysis/reports/submission1/appendix1_filtering.Rmd
@@
        df_print: kable
+       reference_docx: style_reference.docx
+
 ---
@@
 1) When communities have only 1 mathematically possible SAD (S = 1, N = S, or N = S + 1).
-2) When the sampled feasible sets yield fewer than 20 unique values for skewness/evenness.
-If there are fewer than 20 unique values in the comparison vector, it is impossible to be in the 5th or 95th percentile.
+2) When there are fewer than 20 (for the dissimilarity metric) or 40 (for all other metrics) possible SADs. In these cases, it is not possible to fall in the 95th or 97.5/2.5th percentiles.
 3) When a community consists of only 2 species, we excluded it from analyses using skewness, because e1071::skewness() always evaluates to 0 if S = 2.
@@
 
-all_di <- read.csv(here::here("analysis", "reports", "all_di.csv"), stringsAsFactors = F)
+all_di <- read.csv(here::here("analysis", "reports", "submission2", "all_di.csv"), stringsAsFactors = F)
 
@@
 Finally, we filter for cases 2 and 3.
-That is, for aggregate analyses, we will restrict our analyses to sites whose feasible sets have more than 20 unique values for skewness or evenness (whichever metric we are focused on).
+That is, for aggregate analyses, we will restrict our analyses to sites whose feasible sets have more than 20 unique values for the dissimilarity metric, and 40 for all others.
 For analyses with skewness, we will also remove sites with only 2 species.
-This results in these final total numbers of communities included for skewness and evenness.
+This results in these final total numbers of communities included for dissimilarity, skewness, and all other metrics:
+
+For dissimilarity:
+
+```{r}
+
+all_di_filtered %>%
+  filter(nparts > 20) %>%
+  group_by(dat) %>%
+  summarize(sites_for_diss = dplyr::n()) %>%
+  mutate(total_sites_for_diss = sum(sites_for_diss))
+
+```
 
@@
 all_di_filtered %>%
-  filter(skew_unique > 20, s0 > 2) %>%
+  filter(nparts > 40, s0 > 2) %>%
   group_by(dat) %>%
@@
 
-For evenness:
+For all other metrics:
 
@@
 all_di_filtered %>%
-  filter(simpson_unique > 20) %>%
+  filter(nparts > 40) %>%
   group_by(dat) %>%
-  summarize(sites_for_evenness = dplyr::n()) %>%
+  summarize(sites_for_others = dplyr::n()) %>%
   ungroup() %>%
-  mutate(total_sites_for_evenness = sum(sites_for_evenness))
+  mutate(total_sites_for_others = sum(sites_for_others))
 

### 2021-05-09 analysis/reports/submission2/appendices/s8_gentry.Rmd

@@
 title: "Unusual Gentry communities"
-author: Renata Diaz
+#author: Renata Diaz
 date: "`r Sys.Date()`"
@@
 
-The Gentry communities are extreme relative to hte other datasets (in grey), in that they have high species richness and low abundance.
+The Gentry communities are extreme relative to the other datasets (in grey), in that they have high species richness and low abundance.
 Of these, the most extreme communities have extremely low average abundance (e.g.
@@
   geom_point(data = all_di, inherit.aes = F, aes(s0, n0), color = "grey", alpha = .1) +  geom_point() +
-scale_x_log10() + scale_y_log10() + xlab("Species richness (S); note log scale") + ylab("Total abundance (N); note log scale") + ggtitle("Gentry communities", subtitle = "(in color)") + theme(legend.position = "bottom")
+scale_x_log10() + scale_y_log10() + xlab("Species richness (S); note log scale") + ylab("Total abundance (N); note log scale") + ggtitle("Gentry communities", subtitle = "(in color)") + theme(legend.position = "bottom") + scale_color_viridis_d(end = .8)
 
@@
 
-These low-average-abundance communities - the red dots in the plot above - account for most of the signal of extreme values in the unusual direction for various metrics - that is, a **low** number of rare species and **low** skewness, and **high** Shannon and Simpson evenness.
+These low-average-abundance communities - the dark purple dots in the plot above - account for most of the signal of extreme values in the unusual direction for various metrics - that is, a **low** number of rare species and **low** skewness, and **high** Shannon and Simpson evenness.
 Gentry communities with average abundance > 3 tend to show the signal in the same direction as most other communities.
@@
 ```
+
+These low-average abundance communities have unusual statistical baselines. For example, samples from these feasible sets have a very high proportion of rare species:
+
+```{r, fig.dim = c(4.5,4)}
+
+all_di <- all_di %>%
+  mutate(`Average proportion of rare species \nin the feasible set` = nsingletons_mean / s0)
+
+ggplot(all_di, aes(s0, n0, color = `Average proportion of rare species \nin the feasible set`)) +
+  geom_point(alpha = .4) +
+scale_x_log10() + 
+  scale_y_log10() + 
+  scale_color_viridis_c(option = "plasma", end = .8) +
+  xlab("Species richness (S); note log scale") + ylab("Total abundance (N); note log scale") + 
+  theme(legend.position = "bottom", plot.margin =unit(c(4,4,4,4), units = "mm"))
+
+```

### 2021-05-09 analysis/reports/submission2/appendices/s9_fia_comparison.Rmd

@@
   if(grepl("sim_pos", col_name)) {
-    xvarname = "Mean dissimilarity"
+    xvarname = "95th percentile \nof dissimilarity scores"    
     min_nparts = 40
@@
 
-```{r, fig.dim = c(8,4)}
+```{r, fig.dim = c(8,8)}
 fig_2 <- gridExtra::grid.arrange(grobs = list(
@@
   plot_percentile_hist(sub_di, "shannon_percentile_mean", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
-top = textGrob("Figure 2", gp = gpar(fill = "white")), left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
+), ncol = 3,
+left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")),
 bottom = textGrob("Percentile rank of observed value relative to feasible set"), gp = gpar(fill = "white"))
@@
   plot_narrowness_hist(sub_di, "shannon_95_ratio_2t", "\nShannon diversity", facetvar = "Dataset")
-), ncol = 5,
+), ncol = 3,
 left = textGrob("Number of communities", rot = 90, gp = gpar(fill = "black")), gp = gpar(fill = "white"))
